### 2014-12-29 Analysis.Rmd
First commit - trying again.

---
title: '100 Years of Social Work Research: A Data Science Perspective'
output: pdf_document
---

# Overview of data

The original data were from a search of PsychInfo using Ebsco Host platform (December 23, 2014). The following search operators and limiters were used:

+ SO "social work" OR SO "social welfare" OR SO "social casework" OR SO "social services"

+ Limiters - Document Type: Journal Article

+ Search modes - Boolean/Phrase	Interface - EBSCOhost Research Databases

+ Search Screen - Advanced Search

+ Database - PsycINFO

The search results were exported in the _Generic bibliographic format_.  This format is a text (*.txt) file that is processed with the `BibWrangleR` functions.

# Initialize workspace and functions for data wrangling

This section processes raw data.  This section of code is executed only one time to transform the raw data into an analyzable format.  When new data are obtained for this study (i.e., updated search results), this section should be re-run by changing `echo=FALSE` to `echo=TRUE` in the knitr markdown argument.

```{r initialization, warning=FALSE, message=FALSE, eval=FALSE}
# Clear workspace
rm(list=ls())

# Read BWR functions
source("/Users/beperron/Git/BibWrangleR/functions/piWrangleR.R")
source("/Users/beperron/Git/BibWrangleR/functions/packages.R")

# Set the path where original raw data are stored
setwd("/Users/beperron/Git/SocialWorkResearch")

# Set the working directory to store files created by BWR functions
my.path <- "/Users/beperron/Git/SocialWorkResearch"

# Wrangle the data with the BWR function suite
#piBWR.f(csv=FALSE, path=my.path)
#save(pi.df, file = "piArticles.R")
```

# Initialize workspace and functions for analaysis

All the analyses performed involve the data that have been processed with the `BibWrangleR` functions.  This section reads the processed data, loads the required packages, and does a quick quality check to ensure that the same number of articles (i.e., records) contained in the original search match the number of articles in the transformed data.

```{r message=FALSE, warning=FALSE, comment=NA}
rm(list=ls())
load("piArticles.R")
library(dplyr)
library(ggplot2)
library(gridExtra)

# Dimensions of the data file (Rows X Columns)
dim(pi.df)

#Variables of the data file
names(pi.df)

# How many unique article titles?  Ebsco Results of most current search is $n=24,314$. Do not proceed with analysis if the output does not match this result.  
length(which(pi.df$attributes == "TI"))
```

# Overall number and name of unique journal titles?

```{r}
unique.titles <- filter(pi.df, attributes == "SO")

#Number of unique titles
length(unique(unique.titles$record))

#Unique titles
unique(unique.titles$record)
```

# Number of unique journal titles by year

```{r message=FALSE, comment=NA, warning=FALSE, fig.height=2, fig.height=4}
journals.year <- tbl_df(pi.df)
year <- journals.year %>%
        filter(attributes == "YR") %>%
        select(id = articleID, year = record)

journals <- journals.year %>%
        filter(attributes == "SO") %>%
        select(id = articleID, journal.title = record)

n.journals.year <- journals %>% 
        left_join(year) %>%
        group_by(year) %>%
        distinct(journal.title) %>%
        summarise(n = n())

journal.count <- ggplot(n.journals.year, aes(as.numeric(year), y=n, group=1)) + 
    geom_line(colour="black") +
    #geom_point(colour="red") + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
    xlab("year") + 
    ylab("frequency") + 
    ggtitle("Number of Journals by Year") + 
    scale_x_continuous(breaks=seq(1914, 2014, 5))

journal.count
```

# What journals published the most number of articles

```{r}

n.so.yr <- filter(pi.df, attributes == "SO" | attributes == "YR")
n.so <- filter(pi.df, attributes == "SO") %>% mutate(title = record) %>% select(-attributes, -record)
n.yr <- filter(pi.df, attributes == "YR") %>% mutate(year = record ) %>% select(-attributes, -record)
n.so.yr <- left_join(n.so, n.yr) %>%
    group_by(title) %>%
    summarise(
        first = min(year),
        last = max(year),
        n.to.date = n()
        ) %>%
    arrange(desc(n.to.date))

#10 highest number of publications
head(n.so.yr, 10)
```

# What is the lifespan of journals?  
```{r}
#10 longest running journals 
longest.running <- n.so.yr %>%
       mutate(last = as.numeric(last), first = as.numeric(first),year.diff = last - first) %>%
       arrange(desc(year.diff)) %>%
       select(title, first, last, year.diff)
head(longest.running, 10)

#10 shortest running journals
shortest.running <- longest.running %>% arrange(year.diff, first, last)
head(shortest.running, 20)
```
#Number of articles per year

```{r}
n.articles.year <- filter(pi.df, attributes == "YR") 
year.split <- split(n.articles.year, n.articles.year$record)
year.count <- unlist(lapply(year.split, nrow))
year.count <- year.count[order(names(year.count))]
years <- names(year.count)

df <- data.frame(years, year.count)
rownames(df) <- NULL

head(df, 10)
tail(df,10)

plot.article.count <- ggplot(df, aes(as.factor(years), y= year.count, group=1)) + 
    geom_line(colour="black") +
    #geom_point(colour="red") + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
    xlab("year") + 
    ylab("count") + 
    ggtitle("Number of Studies by Year") +
    scale_x_discrete(breaks=c(seq(1914, 2014, 10))) +
    scale_y_continuous(breaks = c(seq(0, 2000, 250)))

df$years <- as.numeric(as.character(df$years))
plot.article.cumulative <- ggplot(df, aes(x = years, y = cumsum(year.count))) + 
    geom_line() + 
    theme(axis.text.x = element_text(angle=45, hjust=1)) +
    scale_x_continuous(breaks=pretty(df$years)) +
    xlab("year") +  
    ylab("count") +
    scale_x_continuous(breaks = c(seq(1914,2014,10))) +
    scale_y_continuous(breaks = c(seq(0, 25000, 2500))) + 
    ggtitle("Cumulative Frequency")

grid.arrange(plot.article.count, plot.article.cumulative, ncol=2)
```

# Topic areas (by Subject Terms)

It is easy to explore some of the different fields within the PsychInfo data frame.  For example, each record has one or more subject terms (from the article keywords).  The total number, unique number, and most frequently occuring key words can be easily computed.

```{r comment=NA, warning=FALSE, message=FALSE}

df.2 <- filter(pi.df, attributes == "SU")

subject.terms <- stringr::str_split(df.2$record, pattern = ";")
subject.terms <- unlist(lapply(subject.terms, function(x) gsub(" ", "", x)))
subject.terms.total <- length(unlist(lapply(subject.terms, function(x) gsub(" ", "", x))))
subject.terms.unique <- length(unique(subject.terms))

subject.terms.l <- list(subject.terms.total = subject.terms.total,
                      subject.terms.unique = subject.terms.unique)

most.frequent <- as.data.frame(table(subject.terms))

most.frequent <- arrange(most.frequent, desc(Freq))
most.frequent.t <- head(most.frequent, 50)

print(subject.terms.l)
print(most.frequent.t)

```

## Most Frequent Subject Terms Over Time (by 5 years)

```{r}
decade <- filter(pi.df, attributes == "YR") %>%
    mutate(year = as.numeric(record)) %>% select(-record, -attributes)

decade$year <- cut(decade$year, breaks = 20, labels = c(1:20))

keywords <- pi.df %>%
        filter(attributes == "SU") %>%
        select(articleID = articleID, keywords = record)

keywords.decade <- keywords %>% 
         left_join(decade)

library(plyr)
keywords.data.split <- dlply(keywords.decade, .(year))
detach(package:plyr)

terms.f <- function(x){
    split.terms <- stringr::str_split(x[,"keywords"], pattern =";")
    clean.terms <- lapply(split.terms, function(x) gsub(" ", "", x))
    }

keywords.decade <- lapply(keywords.data.split, terms.f)
keywords.decade <- lapply(keywords.decade, unlist)
lapply(keywords.decade, function(x) length(unique(x)))

temp <- lapply(keywords.decade, function(x) data.frame(table(x)))
temp <- lapply(temp, function(x) arrange(x, desc(Freq)))
lapply(temp, function(x) head(x,10))    
```

# Author defined keywords

It is easy to explore some of the different fields within the PsychInfo data frame.  For example, each record has one or more subject terms (from the article keywords).  The total number, unique number, and most frequently occuring key words can be easily computed.

```{r comment=NA, warning=FALSE, message=FALSE}

kp.df <- filter(pi.df, attributes == "KP")

subject.terms <- stringr::str_split(kp.df$record, pattern = ";")
subject.terms <- unlist(lapply(subject.terms, function(x) gsub(" ", "", x)))
subject.terms.total <- length(unlist(lapply(subject.terms, function(x) gsub(" ", "", x))))
subject.terms.unique <- length(unique(subject.terms))

subject.terms.l <- list(subject.terms.total = subject.terms.total,
                      subject.terms.unique = subject.terms.unique)

most.frequent <- as.data.frame(table(subject.terms))

most.frequent <- arrange(most.frequent, desc(Freq))
most.frequent.t <- head(most.frequent, 50)

print(subject.terms.l)
print(most.frequent.t)

```

## Most Frequent Author Keywords

```{r}
decade <- filter(pi.df, attributes == "YR") %>%
    mutate(year = as.numeric(record)) %>% select(-record, -attributes)

decade$year <- cut(decade$year, breaks = 20, labels = c(1:20))

keywords <- pi.df %>%
        filter(attributes == "KP") %>%
        select(articleID = articleID, keywords = record)

keywords.decade <- keywords %>% 
         left_join(decade)

library(plyr)
keywords.data.split <- dlply(keywords.decade, .(year))
detach(package:plyr)

terms.f <- function(x){
    split.terms <- stringr::str_split(x[,"keywords"], pattern =";")
    clean.terms <- lapply(split.terms, function(x) gsub(" ", "", x))
    }

keywords.decade <- lapply(keywords.data.split, terms.f)
keywords.decade <- lapply(keywords.decade, unlist)
lapply(keywords.decade, function(x) length(unique(x)))

temp <- lapply(keywords.decade, function(x) data.frame(table(x)))
temp <- lapply(temp, function(x) arrange(x, desc(Freq)))
lapply(temp, function(x) head(x,10))    
```

# Location

It is easy to explore some of the different fields within the PsychInfo data frame.  For example, each record has one or more subject terms (from the article keywords).  The total number, unique number, and most frequently occuring key words can be easily computed.

```{r comment=NA, warning=FALSE, message=FALSE}

LO.df <- filter(pi.df, attributes == "LO")

subject.terms <- stringr::str_split(LO.df$record, pattern = ";")
subject.terms <- unlist(lapply(subject.terms, function(x) gsub(" ", "", x)))
subject.terms.total <- length(unlist(lapply(subject.terms, function(x) gsub(" ", "", x))))
subject.terms.unique <- length(unique(subject.terms))

subject.terms.l <- list(subject.terms.total = subject.terms.total,
                      subject.terms.unique = subject.terms.unique)

most.frequent <- as.data.frame(table(subject.terms))

most.frequent <- arrange(most.frequent, desc(Freq))
most.frequent.t <- head(most.frequent, 50)

print(subject.terms.l)
print(most.frequent.t)

most.frequent

```

## Location over time

```{r}
decade <- filter(pi.df, attributes == "YR") %>%
    mutate(year = as.numeric(record)) %>% select(-record, -attributes)

decade$year <- cut(decade$year, breaks = 20, labels = c(1:20))

keywords <- pi.df %>%
        filter(attributes == "LO") %>%
        select(articleID = articleID, keywords = record)

keywords.decade <- keywords %>% 
         left_join(decade)

library(plyr)
keywords.data.split <- dlply(keywords.decade, .(year))
detach(package:plyr)

terms.f <- function(x){
    split.terms <- stringr::str_split(x[,"keywords"], pattern =";")
    clean.terms <- lapply(split.terms, function(x) gsub(" ", "", x))
    }

keywords.decade <- lapply(keywords.data.split, terms.f)
keywords.decade <- lapply(keywords.decade, unlist)
lapply(keywords.decade, function(x) length(unique(x)))

temp <- lapply(keywords.decade, function(x) data.frame(table(x)))
temp <- lapply(temp, function(x) arrange(x, desc(Freq)))
lapply(temp, function(x) head(x,10))    
```

# Methodology

It is easy to explore some of the different fields within the PsychInfo data frame.  For example, each record has one or more subject terms (from the article keywords).  The total number, unique number, and most frequently occuring key words can be easily computed.

```{r comment=NA, warning=FALSE, message=FALSE}

MD.df <- filter(pi.df, attributes == "MD")

subject.terms <- stringr::str_split(MD.df$record, pattern = ";")
subject.terms <- unlist(lapply(subject.terms, function(x) gsub(" ", "", x)))
subject.terms.total <- length(unlist(lapply(subject.terms, function(x) gsub(" ", "", x))))
subject.terms.unique <- length(unique(subject.terms))

subject.terms.l <- list(subject.terms.total = subject.terms.total,
                      subject.terms.unique = subject.terms.unique)

most.frequent <- as.data.frame(table(subject.terms))

most.frequent <- arrange(most.frequent, desc(Freq))
most.frequent.t <- head(most.frequent, 50)

print(subject.terms.l)
print(most.frequent.t)

```

## Methodology

```{r}
decade <- filter(pi.df, attributes == "YR") %>%
    mutate(year = as.numeric(record)) %>% select(-record, -attributes)

decade$year <- cut(decade$year, breaks = 20, labels = c(1:20))

keywords <- pi.df %>%
        filter(attributes == "MD") %>%
        select(articleID = articleID, keywords = record)

keywords.decade <- keywords %>% 
         left_join(decade)

library(plyr)
keywords.data.split <- dlply(keywords.decade, .(year))
detach(package:plyr)

terms.f <- function(x){
    split.terms <- stringr::str_split(x[,"keywords"], pattern =";")
    clean.terms <- lapply(split.terms, function(x) gsub(" ", "", x))
    }

keywords.decade <- lapply(keywords.data.split, terms.f)
keywords.decade <- lapply(keywords.decade, unlist)
lapply(keywords.decade, function(x) length(unique(x)))

temp <- lapply(keywords.decade, function(x) data.frame(table(x)))
temp <- lapply(temp, function(x) arrange(x, desc(Freq)))
lapply(temp, function(x) head(x,10))    
```

## Number of authors
```{r comment=NA, message=FALSE, warning=FALSE}
n.authors.article <- pi.df %>% 
    filter(attributes == "AU") %>%
    select(id = articleID, author= record) %>%
    mutate(id = as.numeric(id))

n_authors <- n.authors.article %>% 
        group_by(id) %>%
        summarise(n = n())

ggplot(n_authors, aes(x = factor(n))) + 
    geom_bar() + 
    stat_bin(binwidth=1) +
    xlab("Number of Listed Authors") + 
    ylab("Number of Articles")

summary(n_authors$n)
```

## Number of authors over time

This figure shows the average number of authors, along with the standard deviation as the ribbon around the average.  Note that there is a possible problem in these data, with a single article listing a huge number.  That can be corrected at a later time.

```{r message=FALSE, comment=NA, warning=FALSE, fig.height=2, fig.height=4}
df.2 <- tbl_df(pi.df)
year <- df.2 %>%
        filter(attributes == "YR") %>%
        select(id = articleID, year = record)

authors <- df.2 %>%
        filter(attributes == "AU") %>%
        select(id = articleID, author = record)

n_authors <- authors %>%
        group_by(id) %>%
        summarise(n=n())

n_authors <- n_authors %>% 
        left_join(year) %>%
        group_by(year) %>%
        summarise(median.n = median(n),
                  average.n = mean(n),
                  min.n = min(n),
                  max.n = max(n),
                  std.dev  = sd(n) )

plot.author.count2 <- ggplot(n_authors, aes(as.numeric(year), y=average.n, group=1)) + 
    geom_line(colour="black") + 
    geom_ribbon(aes(ymin = average.n-std.dev, ymax=average.n+std.dev), alpha=.2)

head(n_authors, 20)
tail(n_authors, 20)
plot.author.count2
```

# How Many International Contributors?

This section shows a proof of concept -- that is, we can potentially extract all the countries from the author affiliation `AF` tag in the data set.  This involves using a set of regular expressions for the extraction.  Here I have hard-coded a few countries, but I can obtain a file of all countries and use that to automate the process.  We will need to look at the raw data to ensure that the author affiliations have remained in a consistent format throughtout the entirety of the study.

```{r}
df.affiliations <- pi.df %>%
                filter(attributes == "AF")

us.aff <- ifelse(grepl("US", df.affiliations$record, perl=TRUE) == TRUE, "US", 
          ifelse(grepl("Canada", df.affiliations$record, perl=TRUE ) == TRUE, "Canada", 
          ifelse(grepl("Kong", df.affiliations$record, perl=TRUE ) == TRUE, "Hong Kong", 
          ifelse(grepl("China", df.affiliations$record, perl=TRUE) == TRUE, "China", 
          ifelse(grepl("Israel", df.affiliations$record, perl=TRUE) == TRUE, "Israel", "Other" )))))

affiliations <- data.frame(cbind(df.affiliations,us.aff))

ggplot(data=df.affiliations, aes(x = factor(us.aff))) + geom_bar()
```

### 2014-12-30 Analysis.Rmd
Updated notes.

@@
 
-The search results were exported in the _Generic bibliographic format_.  This format is a text (*.txt) file that is processed with the `BibWrangleR` functions.
+The search results were exported in a _generic bibliographic format_, which is an unstructured text (*.txt) file.The text file was processed using the `BibWrangleR` function created by the first author.
 
@@
 This section processes raw data.
-This section of code is executed only one time to transform the raw data into an analyzable format.
+This section of code is executed only one time to transform raw text data into an analyzable format.
 When new data are obtained for this study (i.e., updated search results), this section should be re-run by changing `echo=FALSE` to `echo=TRUE` in the knitr markdown argument.
 
-```{r initialization, warning=FALSE, message=FALSE, eval=FALSE}
+```{r initialization_dataprocessing, warning=FALSE, message=FALSE, eval=FALSE}
 # Clear workspace
@@
 
-# Read BWR functions
+# Read BWR functions for Mac OS
 source("/Users/beperron/Git/BibWrangleR/functions/piWrangleR.R")
@@
 
-```{r message=FALSE, warning=FALSE, comment=NA}
+```{r initialization_analysis, message=FALSE, warning=FALSE, comment=NA}
 rm(list=ls())
@@
 
-# Dimensions of the data file (Rows X Columns)
+# Inspect dimensions of the data file (Rows X Columns)
 dim(pi.df)
 
-#Variables of the data file
+# Inspect variable names of the data file
 names(pi.df)
@@
 
-# Overall number and name of unique journal titles?
+## What is the overall number and names of journal titles?
 
-```{r}
+```{r unique_titles}
 unique.titles <- filter(pi.df, attributes == "SO")
 
-#Number of unique titles
+# Number of unique titles
 length(unique(unique.titles$record))
 
-#Unique titles
+# Unique titles
 unique(unique.titles$record)
@@
 
-# Number of unique journal titles by year
+## Number of unique journal titles by year
 
-```{r message=FALSE, comment=NA, warning=FALSE, fig.height=2, fig.height=4}
+```{r unique_titles_year, message=FALSE, comment=NA, warning=FALSE, fig.height=2, fig.height=4}
 journals.year <- tbl_df(pi.df)
+
 year <- journals.year %>%
@@
 
-# What journals published the most number of articles
+## What journals published the most number of articles
 
-```{r}
+```{r journal_output}
 
 n.so.yr <- filter(pi.df, attributes == "SO" | attributes == "YR")
-n.so <- filter(pi.df, attributes == "SO") %>% mutate(title = record) %>% select(-attributes, -record)
-n.yr <- filter(pi.df, attributes == "YR") %>% mutate(year = record ) %>% select(-attributes, -record)
+
+n.so <- filter(pi.df, attributes == "SO") %>% mutate(title = record) %>% 
+        select(-attributes, -record)
+
+n.yr <- filter(pi.df, attributes == "YR") %>% mutate(year = record ) %>% 
+        select(-attributes, -record)
+
 n.so.yr <- left_join(n.so, n.yr) %>%
     group_by(title) %>%
-    summarise(
-        first = min(year),
-        last = max(year),
-        n.to.date = n()
-        ) %>%
+    summarise(first = min(year), last = max(year), n.to.date = n()) %>%
     arrange(desc(n.to.date))
 
-#10 highest number of publications
+# 10 highest number of publications
 head(n.so.yr, 10)
@@
 
-# What is the lifespan of journals?  
-```{r}
+## What is the lifespan of journals?
+
+```{r journal_lifespan}
 #10 longest running journals 
 longest.running <- n.so.yr %>%
-       mutate(last = as.numeric(last), first = as.numeric(first),year.diff = last - first) %>%
+       mutate(last = as.numeric(last), first = as.numeric(first), 
+              year.diff = last - first) %>%
        arrange(desc(year.diff)) %>%
        select(title, first, last, year.diff)
+
 head(longest.running, 10)
@@
 ```
-#Number of articles per year
 
-```{r}
+## What is the number of articles published per year
+
+```{r articles_per_year}
 n.articles.year <- filter(pi.df, attributes == "YR") 
@@
 
-head(df, 10)
-tail(df,10)
-
-plot.article.count <- ggplot(df, aes(as.factor(years), y= year.count, group=1)) + 
+plot.article.count <- ggplot(df, aes(as.factor(years), 
+                    y = year.count, group=1)) + 
     geom_line(colour="black") +
@@
 df$years <- as.numeric(as.character(df$years))
+
 plot.article.cumulative <- ggplot(df, aes(x = years, y = cumsum(year.count))) + 
@@
 grid.arrange(plot.article.count, plot.article.cumulative, ncol=2)
+
+# Print most recent ten years
+head(df, 10)
 ```
 
-# Topic areas (by Subject Terms)
+# What are the topic areas (by Subject Terms)?
 
-It is easy to explore some of the different fields within the PsychInfo data frame.
-For example, each record has one or more subject terms (from the article keywords).
-The total number, unique number, and most frequently occuring key words can be easily computed.
+```{r subject_terms_overall, comment=NA, warning=FALSE, message=FALSE}
 
-```{r comment=NA, warning=FALSE, message=FALSE}
+su.df <- filter(pi.df, attributes == "SU")
 
-df.2 <- filter(pi.df, attributes == "SU")
+subject.terms <- stringr::str_split(su.df$record, pattern = ";")
+subject.terms <- unlist(lapply(subject.terms, function(x) gsub(" ", "", x)))
 
-subject.terms <- stringr::str_split(df.2$record, pattern = ";")
-subject.terms <- unlist(lapply(subject.terms, function(x) gsub(" ", "", x)))
-subject.terms.total <- length(unlist(lapply(subject.terms, function(x) gsub(" ", "", x))))
+subject.terms.total <- length(unlist(lapply(subject.terms, 
+                        function(x) gsub(" ", "", x))))
+
 subject.terms.unique <- length(unique(subject.terms))
@@
 most.frequent <- arrange(most.frequent, desc(Freq))
-most.frequent.t <- head(most.frequent, 50)
 
-print(subject.terms.l)
-print(most.frequent.t)
+# Print summary statistics in list form
+subject.terms.l
+
+# Print 25 most commmon terms
+head(most.frequent, 25)
 
@@
 
-## Most Frequent Subject Terms Over Time (by 5 years)
+## What are the topic areas over time (by Subject terms)?
 
-```{r}
+```{r subject_terms_overtime}
 decade <- filter(pi.df, attributes == "YR") %>%
@@
 
-# Author defined keywords
-
-It is easy to explore some of the different fields within the PsychInfo data frame.
-For example, each record has one or more subject terms (from the article keywords).
-The total number, unique number, and most frequently occuring key words can be easily computed.
+# What are topic areas over time (by author specified keywords)?
 
 ```{r comment=NA, warning=FALSE, message=FALSE}
-
 kp.df <- filter(pi.df, attributes == "KP")
@@
 subject.terms <- unlist(lapply(subject.terms, function(x) gsub(" ", "", x)))
-subject.terms.total <- length(unlist(lapply(subject.terms, function(x) gsub(" ", "", x))))
+subject.terms.total <- length(unlist(lapply(subject.terms, 
+                        function(x) gsub(" ", "", x))))
+
 subject.terms.unique <- length(unique(subject.terms))
@@
 most.frequent <- arrange(most.frequent, desc(Freq))
-most.frequent.t <- head(most.frequent, 50)
 
+# Print summary statistics
 print(subject.terms.l)
-print(most.frequent.t)
 
+# Print 25 most frequent
+head(most.frequent, 25)
 ```

### 2014-12-30 Analysis.Rmd
Updated figures. All code is working. Cleaning needed.

@@
 
-# Initialize workspace and functions for data wrangling
+# Initialize OS-X workspace and functions for data wrangling
 
@@
 source("/Users/beperron/Git/BibWrangleR/functions/packages.R")
-
 # Set the path where original raw data are stored
@@
 
+# Initialize Windows workspace and functions for data wrangling
+
 # Initialize workspace and functions for analaysis
@@
 rm(list=ls())
+setwd("/Users/beperron/Git/SocialWorkResearch")
+source("/Users/beperron/Git/BibWrangleR/functions/ggsurv.R")
 load("piArticles.R")
@@
 library(gridExtra)
+library(survival)
+library(grid)
+library(png)
 
@@
        arrange(desc(year.diff)) %>%
-       select(title, first, last, year.diff)
+       select(title, first, last, year.diff) %>%
+       mutate(stop = year.diff, event = ifelse(as.numeric(last) != 2014, 1, 0)) %>%
+       select(title, stop, event, as.numeric(first))
 
-head(longest.running, 10)
+survival.journals <- survfit(Surv(longest.running$stop+1, longest.running$event) ~ 1)
+median.survival <- data.frame(time = c(12,12), quant = c(.5,0))
 
-#10 shortest running journals
-shortest.running <- longest.running %>% arrange(year.diff, first, last)
-head(shortest.running, 20)
+head(longest.running)
+
+ggsurv(survival.journals) + 
+    geom_line(data = median.survival, aes(time, quant), linetype="longdash") +
+    annotate("segment", x = 18, xend = 12, y = .12, yend = .15, size = .25, arrow =arrow()) +
+    geom_text(x = 29, y =.12, label = "median survival", size = 4) + 
+    geom_text(x = 75, y =.75, label = "+ = Last year in print", size = 4)
+
 ```
@@
 
-subject.terms.l <- list(subject.terms.total = subject.terms.total,
-                      subject.terms.unique = subject.terms.unique)
-
 most.frequent <- as.data.frame(table(subject.terms))
@@
 most.frequent <- arrange(most.frequent, desc(Freq))
-
-# Print summary statistics in list form
-subject.terms.l
 
@@
 
-```{r subject_terms_overtime}
+```{r subject_terms_overtime, warning=FALSE, message=FALSE}
 decade <- filter(pi.df, attributes == "YR") %>%
@@
 
-decade$year <- cut(decade$year, breaks = 20, labels = c(1:20))
+decade$year <- cut(decade$year, breaks = 10, labels = c(1:10))
 
@@
 keywords.decade <- lapply(keywords.decade, unlist)
-lapply(keywords.decade, function(x) length(unique(x)))
 
@@
 
-# What are topic areas over time (by author specified keywords)?
+# What are the most frequent topic areas (by author specified keywords)?
 
-```{r comment=NA, warning=FALSE, message=FALSE}
+```{r keywords_overall, comment=NA, warning=FALSE, message=FALSE}
 kp.df <- filter(pi.df, attributes == "KP")
@@
 
-```{r}
+```{r keywords_over_time, warning=FALSE, message=FALSE}
 decade <- filter(pi.df, attributes == "YR") %>%
@@
 
-# Location
+# Location of Studies
 
-It is easy to explore some of the different fields within the PsychInfo data frame.
-For example, each record has one or more subject terms (from the article keywords).
-The total number, unique number, and most frequently occuring key words can be easily computed.
-
-```{r comment=NA, warning=FALSE, message=FALSE}
+```{r location, comment=NA, warning=FALSE, message=FALSE}
 
@@
 
-most.frequent <- arrange(most.frequent, desc(Freq))
-most.frequent.t <- head(most.frequent, 50)
+location <- arrange(most.frequent, desc(Freq))
 
 print(subject.terms.l)
-print(most.frequent.t)
 
-most.frequent
+print(location)
 
+img2 <- readPNG("/Users/beperron/Git/SocialWorkResearch/Chloro.png")
+grid.raster(img2)
 ```
 
-## Location over time
+## Location of studies over time
 
-```{r}
-decade <- filter(pi.df, attributes == "YR") %>%
+```{r location_over_time, warning=FALSE, message=FALSE}
+
+top.10.countries <- head(location, 10)
+top.10.countries <- top.10.countries$subject.terms
+top.10.countries <- levels(droplevels(top.10.countries))
+
+year <- filter(pi.df, attributes == "YR") %>%
     mutate(year = as.numeric(record)) %>% select(-record, -attributes)
 
-decade$year <- cut(decade$year, breaks = 20, labels = c(1:20))
+location <- pi.df %>%
+        filter(attributes == "LO") %>%
+        select(articleID = articleID, keywords = record) %>%
+        filter(keywords %in% top.10.countries)
 
-keywords <- pi.df %>%
-        filter(attributes == "LO") %>%
-        select(articleID = articleID, keywords = record)
+location.year <- location %>% 
+         left_join(year)
 
-keywords.decade <- keywords %>% 
-         left_join(decade)
+plot.article.cumulative <- ggplot(df, aes(x = years, y = cumsum(year.count))) + 
+    geom_line() + 
+    theme(axis.text.x = element_text(angle=45, hjust=1)) +
+    scale_x_continuous(breaks=pretty(df$years)) +
+    xlab("year") +  
+    ylab("count") +
+    scale_x_continuous(breaks = c(seq(1914,2014,10))) +
+    scale_y_continuous(breaks = c(seq(0, 25000, 2500))) + 
+    ggtitle("Cumulative Frequency")
 
-library(plyr)
-keywords.data.split <- dlply(keywords.decade, .(year))
-detach(package:plyr)
-
-terms.f <- function(x){
-    split.terms <- stringr::str_split(x[,"keywords"], pattern =";")
-    clean.terms <- lapply(split.terms, function(x) gsub(" ", "", x))
-    }
-
-keywords.decade <- lapply(keywords.data.split, terms.f)
-keywords.decade <- lapply(keywords.decade, unlist)
-lapply(keywords.decade, function(x) length(unique(x)))
-
-temp <- lapply(keywords.decade, function(x) data.frame(table(x)))
-temp <- lapply(temp, function(x) arrange(x, desc(Freq)))
-lapply(temp, function(x) head(x,10))    
 ```

### 2015-01-05 Analysis.Rmd
Updated analysis. Everything is working.

@@
 title: '100 Years of Social Work Research: A Data Science Perspective'
-output: pdf_document
+output: html_document
 ---
@@
 
-top.10.countries <- head(location, 10)
-top.10.countries <- top.10.countries$subject.terms
-top.10.countries <- levels(droplevels(top.10.countries))
-
 year <- filter(pi.df, attributes == "YR") %>%
@@
 
-location <- pi.df %>%
+location.temp <- pi.df %>%
         filter(attributes == "LO") %>%
-        select(articleID = articleID, keywords = record) %>%
-        filter(keywords %in% top.10.countries)
+        select(articleID = articleID, country = record) %>%
+        mutate(country = gsub(" ", "", country))
 
-location.year <- location %>% 
-         left_join(year)
+location.year <- location.temp %>% 
+         left_join(year) %>%
+         group_by(country, year) %>%
+         summarise(n = n()) %>%
+         arrange(country, year, n)
 
-plot.article.cumulative <- ggplot(df, aes(x = years, y = cumsum(year.count))) + 
-    geom_line() + 
-    theme(axis.text.x = element_text(angle=45, hjust=1)) +
-    scale_x_continuous(breaks=pretty(df$years)) +
-    xlab("year") +  
-    ylab("count") +
-    scale_x_continuous(breaks = c(seq(1914,2014,10))) +
-    scale_y_continuous(breaks = c(seq(0, 25000, 2500))) + 
-    ggtitle("Cumulative Frequency")
+top.locations <- location %>% 
+                 select(subject.terms) %>%
+                 rename(country = subject.terms) %>%
+                 slice(1:5)
 
+location.year.top <- location.year %>% filter(country %in% top.locations$country)
+ggplot(location.year.top, aes(x = year, y = n, colour = country )) + geom_line()
+
+top.locations.no.us <- location %>% 
+                select(subject.terms) %>%
+                rename(country = subject.terms) %>%
+                slice(2:7)
+
+location.year.top.no.us <- location.year %>% filter(country %in% top.locations.no.us$country)
+
+ggplot(location.year.top.no.us, aes(x = year, y = n, colour = country )) + geom_line()
+
+```
+
+## Countries not represented in social work research
+
+This section is currently not functional
+```{r countries_not_represented}
+#Tableau.countries <- read.csv("/Users/beperron/Git/SocialWorkResearch/SupportingDocs/Tableau\ Countries.csv")
 ```
@@
 
-It is easy to explore some of the different fields within the PsychInfo data frame.
-For example, each record has one or more subject terms (from the article keywords).
-The total number, unique number, and most frequently occuring key words can be easily computed.
-
-```{r comment=NA, warning=FALSE, message=FALSE}
+```{r methodology, comment=NA, warning=FALSE, message=FALSE}
 
@@
 
-subject.terms <- stringr::str_split(MD.df$record, pattern = ";")
-subject.terms <- unlist(lapply(subject.terms, function(x) gsub(" ", "", x)))
-subject.terms.total <- length(unlist(lapply(subject.terms, function(x) gsub(" ", "", x))))
-subject.terms.unique <- length(unique(subject.terms))
+methodology <- stringr::str_split(MD.df$record, pattern = ";")
+methodology.terms <- unlist(lapply(methodology, function(x) gsub(" ", "", x)))
 
-subject.terms.l <- list(subject.terms.total = subject.terms.total,
-                      subject.terms.unique = subject.terms.unique)
-
-most.frequent <- as.data.frame(table(subject.terms))
-
-most.frequent <- arrange(most.frequent, desc(Freq))
-most.frequent.t <- head(most.frequent, 50)
-
-print(subject.terms.l)
-print(most.frequent.t)
+methodology.table <- as.data.frame(table(methodology.terms))
+methodology.table <- arrange(methodology.table, desc(Freq))
 
@@
 
-## Methodology
+## Methodology over time
 
 ```{r}
-decade <- filter(pi.df, attributes == "YR") %>%
+year <- filter(pi.df, attributes == "YR") %>%
     mutate(year = as.numeric(record)) %>% select(-record, -attributes)
 
-decade$year <- cut(decade$year, breaks = 20, labels = c(1:20))
+methodology <- pi.df %>%
+        filter(attributes == "MD") %>%
+        select(articleID = articleID, method = record) %>%
+        mutate(method = gsub(" ", "", method))
 
-keywords <- pi.df %>%
-        filter(attributes == "MD") %>%
-        select(articleID = articleID, keywords = record)
+methodology.year <- methodology %>% 
+         left_join(year) %>%
+         group_by(method, year) %>%
+         summarise(n = n()) %>%
+         arrange(method, year, n)
 
-keywords.decade <- keywords %>% 
-         left_join(decade)
+methodology.year.top <- slice(methodology.table, 1:5) %>%
+         rename(method = methodology.terms) %>%
+         mutate(method = gsub(" ", "", method))
 
-library(plyr)
-keywords.data.split <- dlply(keywords.decade, .(year))
-detach(package:plyr)
+methodology.year.reduced <- methodology.year %>%
+        filter(method %in% methodology.year.top$method)
 
-terms.f <- function(x){
-    split.terms <- stringr::str_split(x[,"keywords"], pattern =";")
-    clean.terms <- lapply(split.terms, function(x) gsub(" ", "", x))
-    }
-
-keywords.decade <- lapply(keywords.data.split, terms.f)
-keywords.decade <- lapply(keywords.decade, unlist)
-lapply(keywords.decade, function(x) length(unique(x)))
-
-temp <- lapply(keywords.decade, function(x) data.frame(table(x)))
-temp <- lapply(temp, function(x) arrange(x, desc(Freq)))
-lapply(temp, function(x) head(x,10))    
+ggplot(methodology.year.reduced, aes(x = year, y = n, colour = method)) + 
+        geom_line()
 ```
@@
 ```
-
-# How Many International Contributors?
-
-This section shows a proof of concept -- that is, we can potentially extract all the countries from the author affiliation `AF` tag in the data set.
-This involves using a set of regular expressions for the extraction.
-Here I have hard-coded a few countries, but I can obtain a file of all countries and use that to automate the process.
-We will need to look at the raw data to ensure that the author affiliations have remained in a consistent format throughtout the entirety of the study.
-
-```{r}
-df.affiliations <- pi.df %>%
-                filter(attributes == "AF")
-
-us.aff <- ifelse(grepl("US", df.affiliations$record, perl=TRUE) == TRUE, "US", 
-          ifelse(grepl("Canada", df.affiliations$record, perl=TRUE ) == TRUE, "Canada", 
-          ifelse(grepl("Kong", df.affiliations$record, perl=TRUE ) == TRUE, "Hong Kong", 
-          ifelse(grepl("China", df.affiliations$record, perl=TRUE) == TRUE, "China", 
-          ifelse(grepl("Israel", df.affiliations$record, perl=TRUE) == TRUE, "Israel", "Other" )))))
-
-affiliations <- data.frame(cbind(df.affiliations,us.aff))
-
-ggplot(data=df.affiliations, aes(x = factor(us.aff))) + geom_bar()
-```

### 2015-01-09 Analysis.Rmd
Updated search results. Minor code modifcation.  Funtioning.

@@
 
-# Overview of data
+# Overview of Search Strategy
 
-The original data were from a search of PsychInfo using Ebsco Host platform (December 23, 2014). The following search operators and limiters were used:
+Date conducted:   January 8, 2014
 
-+ SO "social work" OR SO "social welfare" OR SO "social casework" OR SO "social services"
+Database: PsychInfo (via EbscoHost Platform)
 
-+ Limiters - Document Type: Journal Article
+Search terms:  SO "social work" or SO "social welfare" or SO "social casework" or "social case work" or SO "social service" or "social services" or SO "human service" or SO "human services" or SO "social development" or SO "social environment"
 
-+ Search modes - Boolean/Phrase	Interface - EBSCOhost Research Databases
+Search limiters:  Publication Type: Peer Reviewed Journal; Document Type: Journal Article
 
-+ Search Screen - Advanced Search
+Search modes: Boolean/Phrase
 
-+ Database - PsycINFO
-
-The search results were exported in a _generic bibliographic format_, which is an unstructured text (*.txt) file.The text file was processed using the `BibWrangleR` function created by the first author.
-
-# Initialize OS-X workspace and functions for data wrangling
-
-This section processes raw data.
-This section of code is executed only one time to transform raw text data into an analyzable format.
-When new data are obtained for this study (i.e., updated search results), this section should be re-run by changing `echo=FALSE` to `echo=TRUE` in the knitr markdown argument.
+Search results were exported from EbscoHost Platformon in a _generic bibliographic format_.  This is an unstructured text file (*.txt) that was processed using in R.
 
@@
 # Set the path where original raw data are stored
-setwd("/Users/beperron/Git/SocialWorkResearch")
+setwd("/Users/beperron/Git/SocialWorkResearch/Data")
 
 # Set the working directory to store files created by BWR functions
-my.path <- "/Users/beperron/Git/SocialWorkResearch"
+path <- "/Users/beperron/Git/SocialWorkResearch/Data"
 
 # Wrangle the data with the BWR function suite
-#piBWR.f(csv=FALSE, path=my.path)
+#piBWR.f(csv=FALSE, path=path)
 #save(pi.df, file = "piArticles.R")
@@
 
-# Initialize Windows workspace and functions for data wrangling
-
-# Initialize workspace and functions for analaysis
-
-All the analyses performed involve the data that have been processed with the `BibWrangleR` functions.
-This section reads the processed data, loads the required packages, and does a quick quality check to ensure that the same number of articles (i.e., records) contained in the original search match the number of articles in the transformed data.
-
-```{r initialization_analysis, message=FALSE, warning=FALSE, comment=NA}
+```{r initialization_analysis, message=FALSE, warning=FALSE, comment=NA, echo=FALSE}
 rm(list=ls())
-setwd("/Users/beperron/Git/SocialWorkResearch")
+setwd("/Users/beperron/Git/SocialWorkResearch/Data")
 source("/Users/beperron/Git/BibWrangleR/functions/ggsurv.R")
@@
 
-# How many unique article titles?  Ebsco Results of most current search is $n=24,314$. Do not proceed with analysis if the output does not match this result.  
+# How many unique article titles?  Ebsco Results of most current search is $n=XXXX$. Do not proceed with analysis if the output does not match this result.  
 length(which(pi.df$attributes == "TI"))
@@
 
-## What is the overall number and names of journal titles?
+```{r echo=FALSE}
+pi.df <- pi.df %>% filter(
+        record != "Journal of Applied Social Sciences" &
+        record != "Early Child Development and Care" &
+        record != "The Clinical Supervisor" &
+        record != "Children and Youth Services Review" &
+        record != "General Hospital Psychiatry" &
+        record != "Canadian Journal on Aging" &
+        record != "Canadian Journal of Community Mental Health" &
+        record != "Behavior Modification" &
+        record != "Employee Assistance Quarterly" &
+        record != "Journal of Applied Behavioral Science" & 
+        record != "The Scientific Review of Mental Health Practice: Objective Investigations of Controversial and Unorthodox Claims in Clinical Psychology, Psychiatry, and Social Work" &
+        record != "Systems Research and Behavioral Science" & 
+        record != "Journal of Applied Rehabilitation Counseling" & 
+        record != "Journal of Educational & Psychological Consultation" &
+        record != "Journal of Community & Applied Social Psychology" &                                          
+        record != "Evaluation and Program Planning" &                                                                  
+        record != "Journal of Nonverbal Behavior" &
+        record != "Brain and Cognition" &
+        record != "Early Education and Development")
+```
 
-```{r unique_titles}
+# What is the overall number and names of journal titles?
+
+```{r unique_titles, echo=FALSE}
 unique.titles <- filter(pi.df, attributes == "SO")
@@
 # Number of unique titles
-length(unique(unique.titles$record))
+number.journals <- length(unique(unique.titles$record))
 
 # Unique titles
-unique(unique.titles$record)
+journals.unique <- unique(unique.titles$record)
+#write.csv(journals.unique, "journals.csv")
+
+number.journals
+journals.unique
 ```
@@
 
-```{r unique_titles_year, message=FALSE, comment=NA, warning=FALSE, fig.height=2, fig.height=4}
+```{r unique_titles_year, message=FALSE, comment=NA, warning=FALSE, fig.height=2, fig.height=4, echo=FALSE}
 journals.year <- tbl_df(pi.df)
@@
 
-```{r journal_output}
+```{r journal_output, echo=FALSE}
 
@@
 
-```{r journal_lifespan}
+```{r journal_lifespan, echo=FALSE}
 #10 longest running journals 
@@
 ggsurv(survival.journals) + 
-    geom_line(data = median.survival, aes(time, quant), linetype="longdash") +
-    annotate("segment", x = 18, xend = 12, y = .12, yend = .15, size = .25, arrow =arrow()) +
-    geom_text(x = 29, y =.12, label = "median survival", size = 4) + 
-    geom_text(x = 75, y =.75, label = "+ = Last year in print", size = 4)
+    #geom_line(data = median.survival, aes(time, quant), linetype="longdash") +
+    #annotate("segment", x = 18, xend = 12, y = .12, yend = .15, size = .25, arrow =arrow()) +
+    #geom_text(x = 29, y =.12, label = "median survival", size = 4) + 
+    geom_text(x = 75, y =.75, label = "+ = Last year in print", size = 4) +
+    ylim(0,1)
 
@@
 
-```{r articles_per_year}
+```{r articles_per_year, echo=FALSE}
 n.articles.year <- filter(pi.df, attributes == "YR") 
@@
 # Print most recent ten years
-head(df, 10)
-```
-
-# What are the topic areas (by Subject Terms)?
-
-```{r subject_terms_overall, comment=NA, warning=FALSE, message=FALSE}
-
-su.df <- filter(pi.df, attributes == "SU")
-
-subject.terms <- stringr::str_split(su.df$record, pattern = ";")
-subject.terms <- unlist(lapply(subject.terms, function(x) gsub(" ", "", x)))
-
-subject.terms.total <- length(unlist(lapply(subject.terms, 
-                        function(x) gsub(" ", "", x))))
-
-subject.terms.unique <- length(unique(subject.terms))
-
-most.frequent <- as.data.frame(table(subject.terms))
-
-most.frequent <- arrange(most.frequent, desc(Freq))
-
-# Print 25 most commmon terms
-head(most.frequent, 25)
-
-```
-
-## What are the topic areas over time (by Subject terms)?
-
-```{r subject_terms_overtime, warning=FALSE, message=FALSE}
-decade <- filter(pi.df, attributes == "YR") %>%
-    mutate(year = as.numeric(record)) %>% select(-record, -attributes)
-
-decade$year <- cut(decade$year, breaks = 10, labels = c(1:10))
-
-keywords <- pi.df %>%
-        filter(attributes == "SU") %>%
-        select(articleID = articleID, keywords = record)
-
-keywords.decade <- keywords %>% 
-         left_join(decade)
-
-library(plyr)
-keywords.data.split <- dlply(keywords.decade, .(year))
-detach(package:plyr)
-
-terms.f <- function(x){
-    split.terms <- stringr::str_split(x[,"keywords"], pattern =";")
-    clean.terms <- lapply(split.terms, function(x) gsub(" ", "", x))
-    }
-
-keywords.decade <- lapply(keywords.data.split, terms.f)
-keywords.decade <- lapply(keywords.decade, unlist)
-
-temp <- lapply(keywords.decade, function(x) data.frame(table(x)))
-temp <- lapply(temp, function(x) arrange(x, desc(Freq)))
-lapply(temp, function(x) head(x,10))    
+tail(df, 10)
 ```
@@
 
-```{r keywords_overall, comment=NA, warning=FALSE, message=FALSE}
+```{r keywords_overall, comment=NA, warning=FALSE, message=FALSE, echo=FALSE}
 kp.df <- filter(pi.df, attributes == "KP")
@@
 
-```{r keywords_over_time, warning=FALSE, message=FALSE}
-decade <- filter(pi.df, attributes == "YR") %>%
-    mutate(year = as.numeric(record)) %>% select(-record, -attributes)
+For this analysis (to-do), select a few keywords that may tell an interesting story of how they change over time -- something that might be revealing of 'trends.'
 
-decade$year <- cut(decade$year, breaks = 10, labels = c(1:10))
+"social justice"
+"evidence-based practice" | "evidence based practice" | "EBP"
+"bullying"
+"child welfare"
 
-keywords <- pi.df %>%
-        filter(attributes == "KP") %>%
-        select(articleID = articleID, keywords = record)
+```{r keywords_over_time, warning=FALSE, message=FALSE, echo=FALSE}
 
-keywords.decade <- keywords %>% 
-         left_join(decade)
-
-library(plyr)
-keywords.data.split <- dlply(keywords.decade, .(year))
-detach(package:plyr)
-
-terms.f <- function(x){
-    split.terms <- stringr::str_split(x[,"keywords"], pattern =";")
-    clean.terms <- lapply(split.terms, function(x) gsub(" ", "", x))
-    }
-
-keywords.decade <- lapply(keywords.data.split, terms.f)
-keywords.decade <- lapply(keywords.decade, unlist)
-
-temp <- lapply(keywords.decade, function(x) data.frame(table(x)))
-temp <- lapply(temp, function(x) arrange(x, desc(Freq)))
-lapply(temp, function(x) head(x,10))    
 ```
@@
 
-```{r location, comment=NA, warning=FALSE, message=FALSE}
+```{r location, comment=NA, warning=FALSE, message=FALSE, echo=FALSE}
 
@@
 print(location)
+write.csv(location, "location.csv")
 
-img2 <- readPNG("/Users/beperron/Git/SocialWorkResearch/Chloro.png")
-grid.raster(img2)
+#img2 <- readPNG("/Users/beperron/Git/SocialWorkResearch/Chloro.png")
+#grid.raster(img2)
 ```
@@
 
-```{r location_over_time, warning=FALSE, message=FALSE}
+```{r location_over_time, warning=FALSE, message=FALSE, echo=FALSE}
 
@@
 This section is currently not functional
-```{r countries_not_represented}
+```{r countries_not_represented, echo=FALSE}
 #Tableau.countries <- read.csv("/Users/beperron/Git/SocialWorkResearch/SupportingDocs/Tableau\ Countries.csv")
@@
 
-```{r methodology, comment=NA, warning=FALSE, message=FALSE}
+```{r methodology, comment=NA, warning=FALSE, message=FALSE, echo=FALSE}
 
@@
 
-```{r}
+```{r echo=FALSE}
 year <- filter(pi.df, attributes == "YR") %>%

### 2015-01-11 Analysis.Rmd
Updated analyses. Added full Ebsco data.

@@
 
-# Overview of Search Strategy
-
-Date conducted:   January 8, 2014
+Data collection date:  January 8, 2014
 
@@
 
+Note the exclusion of social work today.
+
 ```{r echo=FALSE}
@@
         record != "Brain and Cognition" &
-        record != "Early Education and Development")
+        record != "Early Education and Development" & 
+        record != "American Journal of Preventive Medicine" &
+        record != "Social Work Today")
 ```
 
-# What is the overall number and names of journal titles?
+This section provides further cleaning of retained journals, namely merging two journals with abbreviated titles:
+
+```{r}
+
+pi.df$record <- ifelse(pi.df$record == "Practice", "Practice: Social Work in Action", pi.df$record)
+pi.df$articleID <- ifelse(pi.df$articleID == 74, 42, pi.df$articleID)
+
+pi.df$record <- ifelse(pi.df$record == "Eugenics & Social Welfare Bull.", "Eugenics and Social Welfare Bulletin", pi.df$record)
+pi.df$articleID <- ifelse(pi.df$articleID == 28, 32, pi.df$articleID)
+
+```
 
@@
 ```
-
-## Number of unique journal titles by year
 
@@
     theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-    xlab("year") + 
-    ylab("frequency") + 
-    ggtitle("Number of Journals by Year") + 
+    xlab("Publication year") + 
+    ylab("Number") + 
+    ggtitle("Number of Journals Over Time") + 
     scale_x_continuous(breaks=seq(1914, 2014, 5))
@@
        select(title, first, last, year.diff) %>%
-       mutate(stop = year.diff, event = ifelse(as.numeric(last) != 2014, 1, 0)) %>%
+       mutate(stop = year.diff, event = ifelse(as.numeric(last) != 2013, 1, 0)) %>%
        select(title, stop, event, as.numeric(first))
@@
 survival.journals <- survfit(Surv(longest.running$stop+1, longest.running$event) ~ 1)
-median.survival <- data.frame(time = c(12,12), quant = c(.5,0))
+median.survival <- data.frame(time = c(24,24), quant = c(.5,0))
 
@@
 ggsurv(survival.journals) + 
-    #geom_line(data = median.survival, aes(time, quant), linetype="longdash") +
-    #annotate("segment", x = 18, xend = 12, y = .12, yend = .15, size = .25, arrow =arrow()) +
-    #geom_text(x = 29, y =.12, label = "median survival", size = 4) + 
+    geom_line(data = median.survival, aes(time, quant), linetype="longdash") +
+    annotate("segment", x = 32, xend = 27, y = .12, yend = .12, size = .25, arrow =arrow()) +
+    geom_text(x = 45, y =.12, label = "median survival", size = 4) + 
     geom_text(x = 75, y =.75, label = "+ = Last year in print", size = 4) +
-    ylim(0,1)
+    ylim(0,1) +
+    xlim(0,100) + 
+    xlab("Survival Time (in years)") +
+    ylab("Survival Probability") +
+    ggtitle("Survival Probability of Social Work Journals")
 
@@
     ggtitle("Number of Studies by Year") +
-    scale_x_discrete(breaks=c(seq(1914, 2014, 10))) +
+    scale_x_discrete(breaks=c(seq(1914, 2015, 10))) +
     scale_y_continuous(breaks = c(seq(0, 2000, 250)))
@@
 subject.terms <- stringr::str_split(kp.df$record, pattern = ";")
+subject.terms <- tolower(subject.terms)
 subject.terms <- unlist(lapply(subject.terms, function(x) gsub(" ", "", x)))
@@
 
-"social justice"
-"evidence-based practice" | "evidence based practice" | "EBP"
-"bullying"
-"child welfare"
++ social justice
++ evidence-based practice" | "evidence based practice" | "EBP"
++ bullying
++ child welfare
 
 ```{r keywords_over_time, warning=FALSE, message=FALSE, echo=FALSE}
+kp.yr <- filter(pi.df, attributes == "YR") %>%
+    mutate(year = as.numeric(record)) %>% select(-record, -attributes)
+
+kp <- pi.df %>%
+        filter(attributes == "KP") %>%
+        select(articleID = articleID, keyword = record) %>%
+        mutate(keyword = gsub(" ", "", keyword))
+
+kp.year <- kp %>% 
+         left_join(kp.yr) %>%
+         group_by(keyword, year) %>%
+         summarise(n = n()) %>%
+         arrange(keyword, year, n)
+
+select.keywords <- c("power", "oppression", "discrimination", "socialjustice", "qualitativeresearch")
+select.keywords.df <- kp.year %>% filter(keyword %in% select.keywords)
+
+library(plyr) # Fix code so ply loads before dplyr
+key.plot.df <- ddply(select.keywords.df, .(keyword), transform, cumulative = cumsum(n))
+detach(package:plyr)
+
+#Fix graph to sort the keywords / colour
+ggplot(key.plot.df, aes(x = year, y = cumulative, colour = keyword, group = keyword)) + 
+    geom_line() +
+    ggtitle("Cumulative Sum of Articles by Keywords") +
+    ylab("Cumulative Sum") + 
+    xlab("Year") + 
+    theme(legend.title=element_blank())
 
@@
 ```{r location, comment=NA, warning=FALSE, message=FALSE, echo=FALSE}
+LO.df <- filter(pi.df, attributes == "LO") %>%
+         group_by(record) %>%
+         summarise(Country = unique(record),
+                   N = n()) %>%
+        arrange(desc(N)) %>% 
+        select(-record)
 
-LO.df <- filter(pi.df, attributes == "LO")
+locations <- as.data.frame(table(LO.df))
+locations <- arrange(locations, desc(Freq))
+locations.unique <- length(unique(locations))
 
-subject.terms <- stringr::str_split(LO.df$record, pattern = ";")
-subject.terms <- unlist(lapply(subject.terms, function(x) gsub(" ", "", x)))
-subject.terms.total <- length(unlist(lapply(subject.terms, function(x) gsub(" ", "", x))))
-subject.terms.unique <- length(unique(subject.terms))
-
-subject.terms.l <- list(subject.terms.total = subject.terms.total,
-                      subject.terms.unique = subject.terms.unique)
-
-most.frequent <- as.data.frame(table(subject.terms))
-
-location <- arrange(most.frequent, desc(Freq))
-
-print(subject.terms.l)
-
-print(location)
-write.csv(location, "location.csv")
+#write.csv(location, "location.csv")
 
@@
 
-top.locations <- location %>% 
-                 select(subject.terms) %>%
-                 rename(country = subject.terms) %>%
+top.locations <- LO.df %>% 
+                 select(Country) %>%
                  slice(1:5)
 
-location.year.top <- location.year %>% filter(country %in% top.locations$country)
-ggplot(location.year.top, aes(x = year, y = n, colour = country )) + geom_line()
+location.year.top <- location.year %>% filter(country %in% top.locations$Country)
 
-top.locations.no.us <- location %>% 
-                select(subject.terms) %>%
-                rename(country = subject.terms) %>%
-                slice(2:7)
+ggplot(location.year.top, aes(x = year, y = n, colour = country )) + geom_line() +
+    ggtitle("Number of articles by Top 5 Countries")
 
-location.year.top.no.us <- location.year %>% filter(country %in% top.locations.no.us$country)
+top.locations.no.us <- LO.df %>% 
+                select(Country) %>%
+                slice(2:6)
 
-ggplot(location.year.top.no.us, aes(x = year, y = n, colour = country )) + geom_line()
+location.year.top.no.us <- location.year %>% filter(country %in% top.locations.no.us$Country)
 
+ggplot(location.year.top.no.us, aes(x = year, y = n, colour = country )) + geom_line() +
+    ggtitle("Number of article by Top 5 Countries (excluding United States)")
 ```
@@
 
-# Methodology
-
-```{r methodology, comment=NA, warning=FALSE, message=FALSE, echo=FALSE}
-
-MD.df <- filter(pi.df, attributes == "MD")
-
-methodology <- stringr::str_split(MD.df$record, pattern = ";")
-methodology.terms <- unlist(lapply(methodology, function(x) gsub(" ", "", x)))
-
-methodology.table <- as.data.frame(table(methodology.terms))
-methodology.table <- arrange(methodology.table, desc(Freq))
-
-```
-
-## Methodology over time
-
-```{r echo=FALSE}
-year <- filter(pi.df, attributes == "YR") %>%
-    mutate(year = as.numeric(record)) %>% select(-record, -attributes)
-
-methodology <- pi.df %>%
-        filter(attributes == "MD") %>%
-        select(articleID = articleID, method = record) %>%
-        mutate(method = gsub(" ", "", method))
-
-methodology.year <- methodology %>% 
-         left_join(year) %>%
-         group_by(method, year) %>%
-         summarise(n = n()) %>%
-         arrange(method, year, n)
-
-methodology.year.top <- slice(methodology.table, 1:5) %>%
-         rename(method = methodology.terms) %>%
-         mutate(method = gsub(" ", "", method))
-
-methodology.year.reduced <- methodology.year %>%
-        filter(method %in% methodology.year.top$method)
-
-ggplot(methodology.year.reduced, aes(x = year, y = n, colour = method)) + 
-        geom_line()
-```
-
 ## Number of authors
-```{r comment=NA, message=FALSE, warning=FALSE}
+```{r comment=NA, message=FALSE, warning=FALSE, echo=FALSE}
 n.authors.article <- pi.df %>% 
@@
 
-n_authors <- n.authors.article %>% 
+n_authors.1 <- n.authors.article %>% 
         group_by(id) %>%
@@
 
-ggplot(n_authors, aes(x = factor(n))) + 
-    geom_bar() + 
-    stat_bin(binwidth=1) +
-    xlab("Number of Listed Authors") + 
-    ylab("Number of Articles")
+n_authors.1t <- n_authors.1 %>% mutate(n = ifelse(n >=13, 13, n))
 
-summary(n_authors$n)
+ggplot(n_authors.1t, aes(x=as.factor(n))) + 
+    geom_bar(fill="white", colour="black") + 
+    #stat_bin(binwidth=.5) +
+    ggtitle("Number of Authors Listed Per Article") + 
+    xlab("Author") +
+    ylab("Number of Articles") +
+    scale_y_continuous(limits = c(0, 15000), breaks = seq(0, 14000, 2000)) + 
+    scale_x_discrete(limits = c(as.character(1:12), "13+"))
+
 ```
@@
 
-```{r message=FALSE, comment=NA, warning=FALSE, fig.height=2, fig.height=4}
+```{r message=FALSE, comment=NA, warning=FALSE, fig.height=2, fig.height=4, echo=FALSE}
 df.2 <- tbl_df(pi.df)
@@
 plot.author.count2 <- ggplot(n_authors, aes(as.numeric(year), y=average.n, group=1)) +  
+    geom_ribbon(aes(ymin = average.n-std.dev, ymax=average.n+std.dev), colour="lightblue", fill="lightblue", alpha=.40) +
     geom_line(colour="black") + 
-    geom_ribbon(aes(ymin = average.n-std.dev, ymax=average.n+std.dev), alpha=.2)
+    geom_segment(aes(x= 1940, y = 5.5, xend = 1935, yend = 5.5), 
+                 arrow=arrow(length=unit(0.25, "cm"))) +
+    annotate("text", x = 1951, y = 5.5, label = "1 outlier case of \n24 listed authors", size=3.5) +
+    ylab("Average number of authors (black) \nStandard deviation (light blue") +
+    xlab("Publication year") +
+    ggtitle("Average Number of Authors per Article Over Time")
 
-head(n_authors, 20)
-tail(n_authors, 20)
 plot.author.count2
+
+#n_authors_unique <- n_authors %>% 
+#        left_join(year) %>%
+#        group_by(author) %>%
+#        summarise(Distinct = n())
+
 ```

### 2015-01-11 archive/ArchivedCode.R

@@ -1,0 +1,29 @@
+## Methodology over time
+
+```{r echo=FALSE}
+year <- filter(pi.df, attributes == "YR") %>%
+    mutate(year = as.numeric(record)) %>% select(-record, -attributes)
+
+
+methodology <- pi.df %>%
+    filter(attributes == "MD") %>%
+    select(articleID = articleID, method = record) %>%
+    mutate(method = gsub(" ", "", method))
+
+methodology.year <- methodology %>%
+    left_join(year) %>%
+    group_by(method, year) %>%
+    summarise(n = n()) %>%
+    arrange(method, year, n)
+
+methodology.year.top <- slice(methodology.table, 1:5) %>%
+    rename(method = methodology.terms) %>%
+    mutate(method = gsub(" ", "", method))
+
+methodology.year.reduced <- methodology.year %>%
+    filter(method %in% methodology.year.top$method)
+
+ggplot(methodology.year.reduced, aes(x = year, y = n, colour = method)) +
+    geom_line()
+```
+

### 2015-01-13 Analysis.Rmd
Updated analysis with Ebsco Complete Datafile. All currently functional.

@@
     geom_text(x = 45, y =.12, label = "median survival", size = 4) + 
-    geom_text(x = 75, y =.75, label = "+ = Last year in print", size = 4) +
+    geom_text(x = 75, y =.75, label = "+ = Last year of indexing", size = 4) +
     ylim(0,1) +
@@
 
-select.keywords <- c("power", "oppression", "discrimination", "socialjustice", "qualitativeresearch")
-select.keywords.df <- kp.year %>% filter(keyword %in% select.keywords)
+select.keywords <- c("depression", "hiv")
+select.keywords.df <- kp.year %>% filter(tolower(keyword) %in% select.keywords)
 
@@
 
-#write.csv(location, "location.csv")
+#write.csv(locations, "location.csv")
 
@@
 ```{r location_over_time, warning=FALSE, message=FALSE, echo=FALSE}
-
+library(RColorBrewer)
 year <- filter(pi.df, attributes == "YR") %>%
@@
          summarise(n = n()) %>%
-         arrange(country, year, n)
+         arrange(country, year, n) %>%
+         mutate(cumsum_n = cumsum(n), log_n = log(n+1))
 
@@
 
+top.locations$Country <- gsub(" ", "", top.locations$Country)
+
 location.year.top <- location.year %>% filter(country %in% top.locations$Country)
 
-ggplot(location.year.top, aes(x = year, y = n, colour = country )) + geom_line() +
-    ggtitle("Number of articles by Top 5 Countries")
+ggplot(location.year.top, aes(x = year, y = log_n, colour = country )) + 
+    geom_line(size = 1.25) +
+    ggtitle("Log Number of Articles by Countries With Highest Scholarly Ouput") +
+    xlab("Publication Year") + 
+    ylab("log N+1") +
+    theme(legend.position=c(.210, .7))
 
@@
                 select(Country) %>%
-                slice(2:6)
+                slice(2:10)
+
+top.locations.no.us$Country <- gsub(" ", "", top.locations.no.us$Country)
 
@@
 
-ggplot(location.year.top.no.us, aes(x = year, y = n, colour = country )) + geom_line() +
-    ggtitle("Number of article by Top 5 Countries (excluding United States)")
+ggplot(location.year.top.no.us, aes(x = year, y = cumsum_n, colour = country )) + geom_line(size=1.00) +
+    ggtitle("Cumulative Number of Article by Countries with Highest Scholarly Output \n(Excluding the United States)") +
+    theme(legend.position=c(.210, .6))
 ```
@@
 
-n_authors.1t <- n_authors.1 %>% mutate(n = ifelse(n >=13, 13, n))
+n_authors.1t <- n_authors.1 %>% mutate(n = ifelse(n >=6, 6, n)) %>% 
+    group_by(n) %>%
+    summarise(Articles = n())
 
-ggplot(n_authors.1t, aes(x=as.factor(n))) + 
-    geom_bar(fill="white", colour="black") + 
-    #stat_bin(binwidth=.5) +
-    ggtitle("Number of Authors Listed Per Article") + 
-    xlab("Author") +
-    ylab("Number of Articles") +
-    scale_y_continuous(limits = c(0, 15000), breaks = seq(0, 14000, 2000)) + 
-    scale_x_discrete(limits = c(as.character(1:12), "13+"))
-
+ggplot(n_authors.1t, aes(x = n, y = Articles)) +
+    geom_bar(stat="identity", colour="black", fill = "white") +
+    geom_text(aes(label = Articles), vjust=-.3, size = 4) +
+    scale_x_discrete(limits = c(as.character(1:5), "6+")) + 
+    ggtitle("Number of Articles by Author Count") + 
+    xlab("Author Count") + 
+    ylab("Articles")
 ```
@@
     annotate("text", x = 1951, y = 5.5, label = "1 outlier case of \n24 listed authors", size=3.5) +
-    ylab("Average number of authors (black) \nStandard deviation (light blue") +
+    ylab("Average number of authors (black) \nStandard deviation (light blue)") +
     xlab("Publication year") +
@@
 
-#n_authors_unique <- n_authors %>% 
-#        left_join(year) %>%
-#        group_by(author) %>%
-#        summarise(Distinct = n())
-
 ```

### 2015-01-13 ebscoCompleteListing.Rmd
Updated analysis with Ebsco Complete Datafile. All currently functional.

---
title: "EbscoHistory"
author: "Brian Perron"
date: "January 13, 2015"
output: html_document
---

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r eval=FALSE}
library(dplyr)
library(stringr)
library(xlsx)
library(gdata)

#ebscoFullListing.df <- read.xls("/Users/beperron/Git/SocialWorkResearch/Data/completeListing.xls", sheet=1, header=TRUE)
#save(ebscoFullListing.df, file="ebscoFullListing.R")
```

```{r}
load("ebscoFullListing.R")
ebscoFullListing.df <- ebscoFullListing.df[ebscoFullListing.df$SourceType == "Academic Journal",]
ebscoFullListing.df$IndexingStart <- format(as.Date(ebscoFullListing.df$IndexingStart, "%m/%d/%Y"), "%Y")
ebscoFullListing.df$IndexingEnd <- format(as.Date(ebscoFullListing.df$IndexingStart, "%m/%d/%Y"), "%Y")
barplot(table(as.factor(ebscoFullListing.df$IndexingStart)))
```

#Clean up dates
ebsco.df$IndexingStart <- as.character(ebsco.df$IndexingStart)

ebsco.df$IndexingStart <- as.Date(ebsco.df$IndexingStart, format="%m/%d/%Y")

ebsco.df$IndexingStop <- as.character(ebsco.df$IndexingStop)

#Drop journals with a date from the 1800's
ebsco.df$IndexingStop <- ifelse(nchar(ebsco.df$IndexingStop) ==10, NA, ebsco.df$IndexingStop)
#ebsco.df$IndexingStop <- ifelse(nchar(ebsco.df$IndexingStop) == 0, NA, ebsco.df$IndexingStop)

x.start <- as.Date(ebsco.df$IndexingStart)
x.stop <- ebsco.df$IndexingStop

x.stop <- ebsco.df[complete.cases(ebsco.df$IndexingStop),]

as.Date(x.stop$IndexingStop)

x.startformat(ebsco.df$IndexingStart, format = "%Y/%m/%d")

### 2015-01-14 Analysis.Rmd
Updated files. All functional. Growth of science compared to social work functional.

@@
 
-Data collection date:  January 8, 2014
+# Data collection
 
-Database: PsychInfo (via EbscoHost Platform)
++ Article record retrieval date:  January 8, 2015
+Database: PsychInfo and Social Science Index (via EbscoHost Platform)
 
-Search terms:  SO "social work" or SO "social welfare" or SO "social casework" or "social case work" or SO "social service" or "social services" or SO "human service" or SO "human services" or SO "social development" or SO "social environment"
++ Search terms:  SO "social work" or SO "social welfare" or SO "social casework" or "social case work" or SO "social service" or "social services" or SO "human service" or SO "human services" or SO "social development" or SO "social environment"
 
-Search limiters:  Publication Type: Peer Reviewed Journal; Document Type: Journal Article
++ Search limiters:  Publication Type: Peer Reviewed Journal; Document Type: Journal Article
 
-Search modes: Boolean/Phrase
++ Search modes: Boolean/Phrase
 
-Search results were exported from EbscoHost Platformon in a _generic bibliographic format_.  This is an unstructured text file (*.txt) that was processed using in R.
++ Search results were exported from EbscoHost Platformon in a _generic bibliographic format_.  This is an unstructured text file (*.txt) that was processed using in R.
 
++ EbscoHost full journal listing retrieval date:  January 11, 2015 (http://www.ebscohost.com/title-lists)
+
+# Data Pre-Processing
 ```{r initialization_dataprocessing, warning=FALSE, message=FALSE, eval=FALSE}
@@
 source("/Users/beperron/Git/BibWrangleR/functions/ggsurv.R")
+load("ebscoFullListing.R")
 load("piArticles.R")
+load("socialWorkJournals.R")
 library(dplyr)
@@
 library(png)
+library(reshape2)
 
@@
 
-Note the exclusion of social work today.
+Journals excluded from search results.  _Social Work_ today excluded because it is of a magazine format.
 
-```{r echo=FALSE}
+```{r}
 pi.df <- pi.df %>% filter(
@@
 
-This section provides further cleaning of retained journals, namely merging two journals with abbreviated titles:
+Two journal titles were merged because one set of records was a logical abbreviation of another set of records.
 
@@
 
-pi.df$record <- ifelse(pi.df$record == "Practice", "Practice: Social Work in Action", pi.df$record)
+pi.df$record <- ifelse(pi.df$record == "Practice", "Practice: Social Work in Action"
+                , pi.df$record)
 pi.df$articleID <- ifelse(pi.df$articleID == 74, 42, pi.df$articleID)
@@
 pi.df$articleID <- ifelse(pi.df$articleID == 28, 32, pi.df$articleID)
+```
 
-```
+# Preliminary Analyses
+
+All analyses provided here are not in publishable format, but presented to determine the basis of a storyline.  All tables and figures will be styled according to a target journal.
+
+## Summary of all journal titles included in the analysis
+
+To do:
+
++ In the table, include the first and last years of indexing, and the numbers of articles.  
++ Write the script to output a *.csv file so that it can be included as an Appendix without any formatting.
 
@@
 journals.unique
+socialWorkJournals <- journals.unique
+#save(journals.unique, file="socialWorkJournals.R")
 ```
 
-```{r unique_titles_year, message=FALSE, comment=NA, warning=FALSE, fig.height=2, fig.height=4, echo=FALSE}
+## Count of unique journal titles over time
+
+To do:
++ Integrate the full journal listing of EbscoHost 
++ Plot overall number of journals over time 
++ Plot overall number of journals by major discipline category as defined by EbscoHost classification -- use sociology, anthropology, economics, psychology, and political science
+
+```{r unique_titles_year, message=FALSE, comment=NA, warning=FALSE, echo=FALSE}
 journals.year <- tbl_df(pi.df)
@@
 journal.count <- ggplot(n.journals.year, aes(as.numeric(year), y=n, group=1)) + 
-    geom_line(colour="black") +
+    geom_line(colour="darkblue") +
     #geom_point(colour="red") + 
@@
 journal.count
+```
+
+## Growth of Social Work compared to growth of the social sciences
+
+```{r}
+ebscoFullListing.df <- ebscoFullListing.df[ebscoFullListing.df$SourceType == "Academic Journal",]
+ebscoFullListing.df$IndexingStart <- format(as.Date(ebscoFullListing.df$IndexingStart, "%m/%d/%Y"), "%Y")
+ebscoFullListing.df$IndexingStop <- format(as.Date(ebscoFullListing.df$IndexingStop, "%m/%d/%Y"), "%Y")
+ebJournals.df <- ebscoFullListing.df %>% filter(SourceType == "Academic Journal") %>%
+    select(Discipline, IndexingStart, IndexingStop, PublicationName, ISSN) %>%
+    mutate(IndexingStart = as.numeric(IndexingStart), IndexingStop = as.numeric(IndexingStop)) %>%
+    filter(Discipline == "Sociology" | Discipline == "Political Science & Studies"| 
+           Discipline == "Psychology"| Discipline == "Economics" | Discipline == "Anthropology")
+
+ebJournals.df.unique <- ebJournals.df %>% select(ISSN)
+ebJournals.df.unique <- !duplicated(ebJournals.df.unique)
+ebJournals.df <- ebJournals.df[ebJournals.df.unique, ]
+
+ebJournals.df <- ebJournals.df[!(ebJournals.df$PublicationName %in% journals.unique),]
+
+ebJournals.df <- select(ebJournals.df, -PublicationName, -ISSN) %>%
+    mutate(journalID = c(1:nrow(ebJournals.df))) %>%
+    mutate(journalID = as.factor(journalID)) %>% 
+    select(-Discipline)
+
+#ebJournals.melted <- melt(ebJournals.df)
+
+#ebJournals.overtime.start <- ebJournals.melted %>% 
+#    filter(value = !is.na(value)) %>%
+#    group_by(Discipline, value) %>%
+#    summarise(N.start = n())
+
+#ebJournals.overtime.end <- ebJournals.melted %>% 
+#    filter(variable == "IndexingStop"  & !is.na(value)) %>%
+#    group_by(Discipline, value) %>%
+#    summarise(N.end = n())
+
+#ebjournals.joined <- left_join(ebJournals.overtime.start, ebJournals.overtime.end) %>%
+#    mutate(N.end = ifelse(is.na(N.end), 0, N.end), Cumulative = cumsum(N.start)) %>%
+#    mutate(N.adjusted = Cumulative - N.end)
+
+ebJournals.melted.d <- melt(ebJournals.df)
+
+ebJournals.overtime.start.d <- ebJournals.melted.d %>% 
+    filter(value = !is.na(value)) %>%
+    group_by(value) %>%
+    summarise(N.start = n())
+
+ebJournals.overtime.end.d <- ebJournals.melted.d %>% 
+    filter(variable == "IndexingStop"  & !is.na(value)) %>%
+    group_by(value) %>%
+    summarise(N.end = n())
+
+ebjournals.joined.d <- left_join(ebJournals.overtime.start.d, ebJournals.overtime.end.d) %>%
+    mutate(N.end = ifelse(is.na(N.end), 0, N.end), Cumulative = cumsum(N.start)) %>%
+    mutate(N.adjusted = Cumulative - N.end)
+
+journal.time.reduced <- n.journals.year %>% filter(year >= 1950)
+ggplot() + 
+    geom_line(data = ebjournals.joined.d, aes(x=value, y=N.adjusted), group=1, colour="purple") + 
+    geom_line(data = journal.time.reduced, aes(as.numeric(year), y=n), group=1, colour="darkblue")
 ```
@@
 ## What is the lifespan of journals?
+
+To do:
++ Incorporate all EbscoHost journals and the separate disciplinary journals
 
@@
 ## What is the number of articles published per year
+
+To do:
++ Plot against major disciplinary categories
 
@@
 
+To do:  
++ Fix script that performs matching -- convert all keywords to lower before matching
+
 ```{r keywords_overall, comment=NA, warning=FALSE, message=FALSE, echo=FALSE}
@@
 
+_DO NOT INTERPRET RESULTS HERE THIS SECTION IS NOT WORKING PROPERLY_
+
 For this analysis (to-do), select a few keywords that may tell an interesting story of how they change over time -- something that might be revealing of 'trends.'
-
-+ social justice
-+ evidence-based practice" | "evidence based practice" | "EBP"
-+ bullying
-+ child welfare
 
@@
 
-select.keywords <- c("depression", "hiv")
+select.keywords <- c("women", "leadership")
 select.keywords.df <- kp.year %>% filter(tolower(keyword) %in% select.keywords)
@@
 
-# Location of Studies
+## Location of Studies
+
+To do:
++ Determine best format / presentation of map
 
@@
 
-#img2 <- readPNG("/Users/beperron/Git/SocialWorkResearch/Chloro.png")
-#grid.raster(img2)
 ```
@@
 ## Location of studies over time
+
+To do:
++ Determine best format / presentation of map
 
@@
 ggplot(location.year.top, aes(x = year, y = log_n, colour = country )) + 
-    geom_line(size = 1.25) +
+    geom_line() +
     ggtitle("Log Number of Articles by Countries With Highest Scholarly Ouput") +
@@
 
-ggplot(location.year.top.no.us, aes(x = year, y = cumsum_n, colour = country )) + geom_line(size=1.00) +
+ggplot(location.year.top.no.us, aes(x = year, y = cumsum_n, colour = country )) + geom_line() +
     ggtitle("Cumulative Number of Article by Countries with Highest Scholarly Output \n(Excluding the United States)") +
     theme(legend.position=c(.210, .6))
+```
+## Countries represents in the social work research
+
+To do:
++ Obtain definition of `LO` tag.  
++ Determine how many articles had LO tag (note the issue if not included from Social Science Index)
+
+```{r fig.width=8, echo=FALSE}
+Map100YearWithUS <- readPNG("/Users/beperron/Git/SocialWorkResearch/images/Map100Years.png")
+grid.raster(Map100YearWithUS)
+
+Map100YearWithoutUS <- readPNG("/Users/beperron/Git/SocialWorkResearch/images/Map100YearsWithoutUS.png")
+grid.raster(Map100YearWithUS)
 ```
@@
 
-This section is currently not functional
-```{r countries_not_represented, echo=FALSE}
-#Tableau.countries <- read.csv("/Users/beperron/Git/SocialWorkResearch/SupportingDocs/Tableau\ Countries.csv")
+```{r fig.width=8, echo=FALSE}
+library(png)
+library(grid)
+img <- readPNG("/Users/beperron/Git/SocialWorkResearch/images/NotRepresented100Years.png")
+grid.raster(img)
+
 ```
@@
 ```
+
+```

### 2015-01-14 Analysis.Rmd
Minor change in journals.

@@
 title: '100 Years of Social Work Research: A Data Science Perspective'
-output: html_document
+output: pdf_document
 ---
@@
 
-```{r}
+This section shows the overall growth of the social sciences.  This includes all _academic journals_ (excluding magazines and trade publications) that have the following discipline tag:
+
++ Sociology
++ Psychology
++ Economics
++ Political Science & Studies
++ Economics
++ Anthropology
+
+```{r echo=FALSE}
 ebscoFullListing.df <- ebscoFullListing.df[ebscoFullListing.df$SourceType == "Academic Journal",]

### 2015-01-27 Analysis.Rmd
Updates on functions.

@@
 ---
-title: '100 Years of Social Work Research: A Data Science Perspective'
+title: 'The History of Social Work Research: A Data Science Perspective'
 output: pdf_document
@@
 # Read BWR functions for Mac OS
-source("/Users/beperron/Git/BibWrangleR/functions/piWrangleR.R")
-source("/Users/beperron/Git/BibWrangleR/functions/packages.R")
+source("/Users/beperron/Git/BibWrangleR/functions/piWrangleR_Modified.R")
+
 # Set the path where original raw data are stored
@@
 # Wrangle the data with the BWR function suite
-#piBWR.f(csv=FALSE, path=path)
+piBWR.f(csv=FALSE, path=path)
 #save(pi.df, file = "piArticles.R")
@@
 pi.df <- pi.df %>% filter(
-        record != "Journal of Applied Social Sciences" &
-        record != "Early Child Development and Care" &
-        record != "The Clinical Supervisor" &
-        record != "Children and Youth Services Review" &
-        record != "General Hospital Psychiatry" &
-        record != "Canadian Journal on Aging" &
-        record != "Canadian Journal of Community Mental Health" &
-        record != "Behavior Modification" &
-        record != "Employee Assistance Quarterly" &
-        record != "Journal of Applied Behavioral Science" & 
-        record != "The Scientific Review of Mental Health Practice: Objective Investigations of Controversial and Unorthodox Claims in Clinical Psychology, Psychiatry, and Social Work" &
-        record != "Systems Research and Behavioral Science" & 
-        record != "Journal of Applied Rehabilitation Counseling" & 
-        record != "Journal of Educational & Psychological Consultation" &
-        record != "Journal of Community & Applied Social Psychology" &                                          
-        record != "Evaluation and Program Planning" &                                                                  
-        record != "Journal of Nonverbal Behavior" &
-        record != "Brain and Cognition" &
-        record != "Early Education and Development" & 
-        record != "American Journal of Preventive Medicine" &
-        record != "Social Work Today")
+        record != "PUT JOURNALS TO BE EXCLUDED HERE" &
+        record != "PUT JOURNALS TO BE EXCLUDED HERE     " &
+        )
 ```
@@
 number.journals
-journals.unique
+sort(journals.unique)
 socialWorkJournals <- journals.unique
@@
 + Plot overall number of journals by major discipline category as defined by EbscoHost classification -- use sociology, anthropology, economics, psychology, and political science
++ The following "overall growth" plot excludes social work journals in this study.
+There were a small number of overlap journals between social science and social work journals (N = 4 -- double check for final analysis.
+The journals that overlapped were included in the social work group.
 
@@
            Discipline == "Psychology"| Discipline == "Economics" | Discipline == "Anthropology") 
+```
 
-ebJournals.df.unique <- ebJournals.df %>% select(ISSN)
-ebJournals.df.unique <- !duplicated(ebJournals.df.unique)
-ebJournals.df <- ebJournals.df[ebJournals.df.unique, ]
+Some of the journals have duplicate entries in the database because they are cross-classified in multiple social science disciplines.
+The following code is used to create a data set that excludes duplicate entries in the database and ensures no overlap between the social science list and the social work list of journals.
+Duplicates are identified based on ISSN, not journal title.
+This will ensure all duplicates are identified.
 
-ebJournals.df <- ebJournals.df[!(ebJournals.df$PublicationName %in% journals.unique),]
+```{r}
+ebJournals.df.issn <- ebJournals.df %>% select(ISSN)
+ebJournals.df.unique <- !duplicated(ebJournals.df.issn)
 
-ebJournals.df <- select(ebJournals.df, -PublicationName, -ISSN) %>%
-    mutate(journalID = c(1:nrow(ebJournals.df))) %>%
+#This function here tests whether the duplication identifier correctly gets the first unique record (by assigning TRUE) and then excluding subsequent records (by assigning FALSE) 
+#cbind(ebJournals.df.unique, ebJournals.df.issn$ISSN)
+
+#This subsets out the duplicates
+ebJournals.df.no.duplicates <- ebJournals.df[ebJournals.df.unique, ]
+
+#This function does a logical comparison of the social science journals and the social work journals to determine potential overlap.  
+overlap <- ebJournals.df.no.duplicates[(ebJournals.df.no.duplicates$PublicationName %in% journals.unique),]  
+print(overlap)
+
+#This reduces the overlap from the social science journal lists, retaining the overlap in the social work journals
+ebJournals.df.no.overlap <- ebJournals.df.no.duplicates[!(ebJournals.df.no.duplicates$PublicationName %in% journals.unique),]   
+```
+
+This section uses the `melt` function to transform the social science data file into a format that can be plotted using ``ggplot2`.  
+```{r echo=FALSE}
+
+#Remove variables that will interfere with melting procedure
+socialScienceJournals.df <- ebJournals.df.no.overlap %>% 
+    select(-PublicationName, -ISSN) %>%
+    mutate(journalID = c(1:nrow(ebJournals.df.no.overlap))) %>%
     mutate(journalID = as.factor(journalID)) %>% 
@@
 
-#ebJournals.melted <- melt(ebJournals.df)
+socialScienceJournals.melted <- melt(socialScienceJournals.df)
 
-#ebJournals.overtime.start <- ebJournals.melted %>% 
-#    filter(value = !is.na(value)) %>%
-#    group_by(Discipline, value) %>%
-#    summarise(N.start = n())
-
-#ebJournals.overtime.end <- ebJournals.melted %>% 
-#    filter(variable == "IndexingStop"  & !is.na(value)) %>%
-#    group_by(Discipline, value) %>%
-#    summarise(N.end = n())
-
-#ebjournals.joined <- left_join(ebJournals.overtime.start, ebJournals.overtime.end) %>%
-#    mutate(N.end = ifelse(is.na(N.end), 0, N.end), Cumulative = cumsum(N.start)) %>%
-#    mutate(N.adjusted = Cumulative - N.end)
-
-ebJournals.melted.d <- melt(ebJournals.df)
-
-ebJournals.overtime.start.d <- ebJournals.melted.d %>% 
+ebJournals.overtime.start.d <- socialScienceJournals.melted %>% 
     filter(value = !is.na(value)) %>%
@@
 
-ebJournals.overtime.end.d <- ebJournals.melted.d %>% 
+ebJournals.overtime.end.d <- socialScienceJournals.melted %>%
     filter(variable == "IndexingStop"  & !is.na(value)) %>%

### 2015-01-29 Analysis.Rmd
Updated file to go with new bwr function.

@@
 
-# Data collection
+# Data harvesting
 
-+ Article record retrieval date:  January 8, 2015
-Database: PsychInfo and Social Science Index (via EbscoHost Platform)
++ Article record retrieval date: January 24, 2015
+Database: psycInfo, Social Science Abstracts, Social Work Abstracts (via EbscoHost Platform)
 
-+ Search terms:  SO "social work" or SO "social welfare" or SO "social casework" or "social case work" or SO "social service" or "social services" or SO "human service" or SO "human services" or SO "social development" or SO "social environment"
++ Primary search:  Hodge's list
+
++ Supplemental search:  SO "social work" or SO "social welfare" or SO "social casework" or "social case work" or SO "social service" or "social services" or SO "human service" or SO "human services" or SO "social development" or SO "social environment"
 
@@
 
-+ EbscoHost full journal listing retrieval date:  January 11, 2015 (http://www.ebscohost.com/title-lists)
++ Results filtered to exclude years 2014 and 2015 (due to delays in indexing)
 
 # Data Pre-Processing
+
 ```{r initialization_dataprocessing, warning=FALSE, message=FALSE, eval=FALSE}
@@
 # Read BWR functions for Mac OS
-source("/Users/beperron/Git/BibWrangleR/functions/piWrangleR_Modified.R")
+source("/Users/beperron/Git/BibWrangleR/functions/ebscoBWR.R")
 
@@
 # Wrangle the data with the BWR function suite
-piBWR.f(csv=FALSE, path=path)
-#save(pi.df, file = "piArticles.R")
+ebscoBWR.f(csv=FALSE, path=path)
+#save(bwr.df, file = "piArticles.R")
 ```
 
-```{r initialization_analysis, message=FALSE, warning=FALSE, comment=NA, echo=FALSE}
+```{r initialization_analysis, message=FALSE, warning=FALSE, comment=NA}
 rm(list=ls())
@@
 source("/Users/beperron/Git/BibWrangleR/functions/ggsurv.R")
-load("ebscoFullListing.R")
-load("piArticles.R")
-load("socialWorkJournals.R")
+
 library(dplyr)
@@
 # Inspect dimensions of the data file (Rows X Columns)
-dim(pi.df)
+dim(bwr.df)
 
 # Inspect variable names of the data file
-names(pi.df)
+names(bwr.df)
 
 # How many unique article titles?  Ebsco Results of most current search is $n=XXXX$. Do not proceed with analysis if the output does not match this result.  
-length(which(pi.df$attributes == "TI"))
+length(which(bwr.df$attributes == "TI"))
 ```
 
-Journals excluded from search results.  _Social Work_ today excluded because it is of a magazine format.
+# Exclude years 2014 and 2015
 
 ```{r}
-pi.df <- pi.df %>% filter(
-        record != "PUT JOURNALS TO BE EXCLUDED HERE" &
-        record != "PUT JOURNALS TO BE EXCLUDED HERE     " &
-        )
+years <- c("2014", "2015")
+ebsco.remove <- bwr.df[bwr.df$record %in% years, ]
+ebsco.remove <- ebsco.remove[, "articleID"]
+bwr.df <- bwr.df[!(bwr.df$articleID %in% ebsco.remove),]
 ```
 
-Two journal titles were merged because one set of records was a logical abbreviation of another set of records.
+# Merge journal titles
 
 ```{r}
+bwr.df$record <- ifelse(bwr.df$record == "Eugenics and Social Welfare Bulletin", 
+                       "Eugenics & Social Welfare Bull.", 
+                        bwr.df$record)
 
-pi.df$record <- ifelse(pi.df$record == "Practice", "Practice: Social Work in Action"
-                , pi.df$record)
-pi.df$articleID <- ifelse(pi.df$articleID == 74, 42, pi.df$articleID)
+bwr.df$record <- ifelse(bwr.df$record == "The British Journal of Social Work", 
+                       "British Journal of Social Work", 
+                        bwr.df$record)
 
-pi.df$record <- ifelse(pi.df$record == "Eugenics & Social Welfare Bull.", "Eugenics and Social Welfare Bulletin", pi.df$record)
-pi.df$articleID <- ifelse(pi.df$articleID == 28, 32, pi.df$articleID)
+bwr.df$record <- ifelse(bwr.df$record == "Social Work & Social Sciences Review", 
+                       "Social Work and Social Sciences Review", 
+                        bwr.df$record)
+
+bwr.df$record <- ifelse(bwr.df$record == "Social Work with Groups", 
+                       "Social Work With Groups", 
+                        bwr.df$record)
+
+bwr.df$record <- ifelse(bwr.df$record == "Computers in Human Services", 
+                       "Journal of Technology in the Human Services", 
+                        bwr.df$record)
+
+```
+
+# Journals excluded from search results.
+
+```{r}
+exclusions <- c(
+    "American Journal of Preventive Medicine", 
+    "Behavior Modification", 
+    "Brain and Cognition",
+    "Canadian Journal of Community Mental Health",
+    "Canadian Journal on Aging",
+    "Early Child Development and Care",
+    "Early Education and Development",
+    "Employee Assistance Quarterly",
+    "Evaluation and Program Planning",
+    "General Hospital Psychiatry",
+    "Hospital Social Service",
+    "Journal of Applied Behavioral Science",
+    "Journal of Applied Rehabilitation Counseling",
+    "Journal of Community & Applied Social Psychology",
+    "Journal of Nonverbal Behavior",
+    "Learning Disabilities Research & Practice",
+    "New York State Department of Social Welfare, Division Publication",
+    "Pennsylvania Social Work",
+    "Proceedings of the National Converence of Social Work",
+    "PROFILE Issues in Teachers' Professional Development",
+    "Psychotherapy",
+    "Social Development",
+    "Social Service Department, Presbyterian Hospital, New York",
+    "Social Work Technique",
+    "Social Work Today", # Magazine
+    "The New Social Worker",
+    "Systems Research and Behavioral Science",
+    "Teaching and Teacher Education",
+    "University of Chicago Social Service Monograph",
+    "The Scientific Review of Mental Health Practice",
+    "The Clinical Supervisor",
+    "University of Chicago Social Service Monograph")
+ebsco.remove <- bwr.df[bwr.df$record %in% exclusions, ]
+ebsco.remove <- ebsco.remove[, "articleID"]
+bwr.df <- bwr.df[!(bwr.df$articleID %in% ebsco.remove),]
+```
+
+filter(bwr.df, attributes == "SO") %>% group_by(record) %>% arrange(record) %>% summarise(Article.Count = n())
+
+filter(bwr.df, attributes == "TI") %>% summarize(N = n())
 ```
@@
 # Preliminary Analyses
-
-All analyses provided here are not in publishable format, but presented to determine the basis of a storyline.  All tables and figures will be styled according to a target journal.
 
@@
 ```{r unique_titles, echo=FALSE}
-unique.titles <- filter(pi.df, attributes == "SO")
+unique.titles <- filter(bwr.df, attributes == "SO")
 
@@
 ```{r unique_titles_year, message=FALSE, comment=NA, warning=FALSE, echo=FALSE}
-journals.year <- tbl_df(pi.df)
+journals.year <- tbl_df(bwr.df)
 
@@
 
-n.so.yr <- filter(pi.df, attributes == "SO" | attributes == "YR")
+n.so.yr <- filter(bwr.df, attributes == "SO" | attributes == "YR")
 
-n.so <- filter(pi.df, attributes == "SO") %>% mutate(title = record) %>% 
+n.so <- filter(bwr.df, attributes == "SO") %>% mutate(title = record) %>% 
         select(-attributes, -record)
 
-n.yr <- filter(pi.df, attributes == "YR") %>% mutate(year = record ) %>% 
+n.yr <- filter(bwr.df, attributes == "YR") %>% mutate(year = record ) %>% 
         select(-attributes, -record)
@@
 # 10 highest number of publications
-head(n.so.yr, 10)
+head(n.so.yr, 20)
 ```
@@
 ggsurv(survival.journals) + 
-    geom_line(data = median.survival, aes(time, quant), linetype="longdash") +
-    annotate("segment", x = 32, xend = 27, y = .12, yend = .12, size = .25, arrow =arrow()) +
-    geom_text(x = 45, y =.12, label = "median survival", size = 4) + 
+    #geom_line(data = median.survival, aes(time, quant), linetype="longdash") +
+    #annotate("segment", x = 32, xend = 27, y = .12, yend = .12, size = .25, arrow =arrow()) +
+    #geom_text(x = 45, y =.12, label = "median survival", size = 4) + 
     geom_text(x = 75, y =.75, label = "+ = Last year of indexing", size = 4) +
     ylim(0,1) +
-    xlim(0,100) + 
+    xlim(0,50) + 
     xlab("Survival Time (in years)") +
@@
 ```{r articles_per_year, echo=FALSE}
-n.articles.year <- filter(pi.df, attributes == "YR") 
+n.articles.year <- filter(bwr.df, attributes == "YR") 
 year.split <- split(n.articles.year, n.articles.year$record)
@@
 ```{r keywords_overall, comment=NA, warning=FALSE, message=FALSE, echo=FALSE}
-kp.df <- filter(pi.df, attributes == "KP")
+kp.df <- filter(bwr.df, attributes == "KP")
 
@@
 ```{r keywords_over_time, warning=FALSE, message=FALSE, echo=FALSE}
-kp.yr <- filter(pi.df, attributes == "YR") %>%
+kp.yr <- filter(bwr.df, attributes == "YR") %>%
     mutate(year = as.numeric(record)) %>% select(-record, -attributes)
 
-kp <- pi.df %>%
+kp <- bwr.df %>%
         filter(attributes == "KP") %>%
@@
 ```{r location, comment=NA, warning=FALSE, message=FALSE, echo=FALSE}
-LO.df <- filter(pi.df, attributes == "LO") %>%
+LO.df <- filter(bwr.df, attributes == "LO") %>%
          group_by(record) %>%
@@
 library(RColorBrewer)
-year <- filter(pi.df, attributes == "YR") %>%
+year <- filter(bwr.df, attributes == "YR") %>%
     mutate(year = as.numeric(record)) %>% select(-record, -attributes)
 
-location.temp <- pi.df %>%
+location.temp <- bwr.df %>%
         filter(attributes == "LO") %>%
@@
 ```{r comment=NA, message=FALSE, warning=FALSE, echo=FALSE}
-n.authors.article <- pi.df %>% 
+n.authors.article <- bwr.df %>% 
     filter(attributes == "AU") %>%
@@
 ```{r message=FALSE, comment=NA, warning=FALSE, fig.height=2, fig.height=4, echo=FALSE}
-df.2 <- tbl_df(pi.df)
+df.2 <- tbl_df(bwr.df)
 year <- df.2 %>%

### 2015-01-29 Analysis.Rmd
Processed wrangled R object.

@@
 # Wrangle the data with the BWR function suite
+start.time <- Sys.time()
 ebscoBWR.f(csv=FALSE, path=path)
-#save(bwr.df, file = "piArticles.R")
+end.time <- Sys.time()
+end.time-start.time
+#save(bwr.df, file = "HistoricalArticles.R")
 ```

### 2015-02-01 Analysis.Rmd
Updating files.Housekeeping.

--- 2015-01-29 Analysis.Rmd
@@
 
-+ Article record retrieval date: January 24, 2015
-Database: psycInfo, Social Science Abstracts, Social Work Abstracts (via EbscoHost Platform)
+Data collection for this study was separated into three phases.
 
-+ Primary search:  Hodge's list
+## Search Query
 
-+ Supplemental search:  SO "social work" or SO "social welfare" or SO "social casework" or "social case work" or SO "social service" or "social services" or SO "human service" or SO "human services" or SO "social development" or SO "social environment"
+The first phases involved querying three different databases serviced by the EbscoHost web platform: psycInfo, Social Science Abstract, and Social Work Abstracts.
+These databases were selected because they provide the indexing services for the majority of social work journals.
+Additionally, search queries from these databases, served by EbscoHost, allowed search results to be exported raw text (*.txt) documents, referred to as a _generic bibliographic format_.
+Other databases and search engines (e.g., Google Scholar) were not queried because the results could not be saved in a common format.
+This is a limitation of the study that is covered in the discussion section.
 
-+ Search limiters:  Publication Type: Peer Reviewed Journal; Document Type: Journal Article
+The search began by querying each database for every _journal article_ from every journal that was included in the list by Hodge and ...
+[Describe this list] ...
+Each query was performed independently on each database,
 
-+ Search modes: Boolean/Phrase
+We had a three-level search process designed to be as comprehensive as possible.
+First, we began by running a separate search query on each database for every journal contained in the list by Hodge.
+We then conducted a subsequent search of all journal titles based on the following key words:
 
-+ Search results were exported from EbscoHost Platformon in a _generic bibliographic format_.  This is an unstructured text file (*.txt) that was processed using in R.
++ social work
++ social welfare
++ social casework 
++ social case work
++ social service
++ human service
++ social development 
++ social environment
 
-+ Results filtered to exclude years 2014 and 2015 (due to delays in indexing)
+In each query, results were limited to only journal articles, which excluded other document types including (but not limited to) editorials, book reviews, software reviews, and obituaries.
+All searches were conducted between January 24, 2015 and January 30, 2015.
+Results were subsequently filtered to exlclude years 2014 and 2015 due to delays in indexing.
+Search results were exported from EbscoHost platfrom into a _generic bibliographic format_.
+This is an unstructured text file (*.txt) that was processed using in R.
+The multiple searches were then transformed into an analyzable database using a customized script developed by the first two authors of the study (BEP and BGV).
+
+Study authors reviewed all journal titles and
 
 # Data Pre-Processing
+
+# NOTE: CONFIRM THAT SOCIAL CASEWORK IS SAME AS FAMILIES IN SOCIETY.  ENSURE WE 
+# HAVE THE ARTICLES FOR WHEN THE JOURNAL WAS ALSO CALLED THE FAMILY
 
@@
 ebscoBWR.f(csv=FALSE, path=path)
-#save(bwr.df, file = "piArticles.R")
+#save(bwr.df, file = "HistoricalArticles.R")
 ```
@@
 source("/Users/beperron/Git/BibWrangleR/functions/ggsurv.R")
+load("/Users/beperron/Git/SocialWorkResearch/Data/HistoricalArticles.R")
 
@@
 bwr.df$record <- ifelse(bwr.df$record == "Computers in Human Services", 
-                       "Journal of Technology in the Human Services", 
+                       "Journal of Technology in Human Services", 
                         bwr.df$record)
+
+bwr.df$record <- ifelse(bwr.df$record == "Journal of Sociology & Social Welfare", 
+                       "Journal of Sociology and Social Welfare", 
+                        bwr.df$record)
+
+#Note leave space after the (Electronic only)
+bwr.df$record <- ifelse(bwr.df$record == "Contemporary Rural Social Work (Electronic only) ", 
+                        "Contemporary Rural Social Work (Electronic only) ", bwr.df$record)
 
@@
     "Hospital Social Service",
+    "International Review of Social Research",
     "Journal of Applied Behavioral Science",
@@
     "Journal of Community & Applied Social Psychology",
+    "Journal of Health & Human Services Administration",
     "Journal of Nonverbal Behavior",
@@
     "Psychotherapy",
-    "Social Development",
     "Social Service Department, Presbyterian Hospital, New York",
@@
     "Social Work Today", # Magazine
+    "Social Work Yearbook",
     "The New Social Worker",
@@
 
-filter(bwr.df, attributes == "SO") %>% group_by(record) %>% arrange(record) %>% summarise(Article.Count = n())
-
-filter(bwr.df, attributes == "TI") %>% summarize(N = n())
+```{r unique_titles, echo=FALSE}
+unique.titles <- filter(bwr.df, attributes == "SO") %>%
+    group_by(record) %>%
+    summarise(
+        N = n())
 ```
@@
 ```{r unique_titles, echo=FALSE}
-unique.titles <- filter(bwr.df, attributes == "SO")
+unique.titles <- filter(bwr.df, attributes == "SO") %>%
+    group_by(record) %>%
+    summarise(
+        N = n())
+
+title <- bwr.df %>%
+        filter(attributes == "SO") %>%
+        select(id = articleID, SO = record)
+
+article <- bwr.df %>%
+        filter(attributes == "TI") %>%
+        select(id = articleID, journal.title = record)
+
+title.articles <- title %>% 
+        left_join(article) %>%
+        group_by(title)
 

### 2015-02-03 dataCleaning.Rmd
General cleaning.

--- 2015-02-01 Analysis.Rmd
@@
 ---
-title: 'The History of Social Work Research: A Data Science Perspective'
+title: 'History of Social Work Research: Data Cleaning'
 output: pdf_document
@@
 
-# Data harvesting
+# Overview
 
-Data collection for this study was separated into three phases.
+This document summarizes data cleaning procedures of the data file processed by the `ebscoBWR` fucntion.
+It should be noted that that `ebscoBWR` function merged the search results from the first- and second-level searches performed on the three databases (psycInfo, Social Science Abstracts, and Social Work Abstract) hosted by the EbscoPlatform.
+This function merged all the search results, transformed the data into a structured data file, and removed all duplicate article records.
+No further transformations or cleaning was performed by the `ebscoBWR` function.
+Provided below are basic descriptive summaries of the results from the full search before further cleaning.
 
-## Search Query
+It should be noted that the second-level search was specified to be overly inclusive to help ensure the most comprehensive search possible.
+All journal titles from the secondary search are identified in the following summary.
 
-The first phases involved querying three different databases serviced by the EbscoHost web platform: psycInfo, Social Science Abstract, and Social Work Abstracts.
-These databases were selected because they provide the indexing services for the majority of social work journals.
-Additionally, search queries from these databases, served by EbscoHost, allowed search results to be exported raw text (*.txt) documents, referred to as a _generic bibliographic format_.
-Other databases and search engines (e.g., Google Scholar) were not queried because the results could not be saved in a common format.
-This is a limitation of the study that is covered in the discussion section.
+library(dplyr)
+temp <- bwr.df[bwr.df$articleID == 28300,]
+27743 and 28300.
 
-The search began by querying each database for every _journal article_ from every journal that was included in the list by Hodge and ...
-[Describe this list] ...
-Each query was performed independently on each database,
-
-We had a three-level search process designed to be as comprehensive as possible.
-First, we began by running a separate search query on each database for every journal contained in the list by Hodge.
-We then conducted a subsequent search of all journal titles based on the following key words:
-
-+ social work
-+ social welfare
-+ social casework 
-+ social case work
-+ social service
-+ human service
-+ social development 
-+ social environment
-
-In each query, results were limited to only journal articles, which excluded other document types including (but not limited to) editorials, book reviews, software reviews, and obituaries.
-All searches were conducted between January 24, 2015 and January 30, 2015.
-Results were subsequently filtered to exlclude years 2014 and 2015 due to delays in indexing.
-Search results were exported from EbscoHost platfrom into a _generic bibliographic format_.
-This is an unstructured text file (*.txt) that was processed using in R.
-The multiple searches were then transformed into an analyzable database using a customized script developed by the first two authors of the study (BEP and BGV).
-
-Study authors reviewed all journal titles and
-
-# Data Pre-Processing
-
-# NOTE: CONFIRM THAT SOCIAL CASEWORK IS SAME AS FAMILIES IN SOCIETY.  ENSURE WE 
-# HAVE THE ARTICLES FOR WHEN THE JOURNAL WAS ALSO CALLED THE FAMILY
+```{r}
+hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
+hodge2 <- gsub("(SO)", "", hodge)
+hodge3 <- gsub("(OR)", "", hodge2)
+hodge4 <- gsub("[[:punct:]]", "", hodge3)
+hodge5 <- str_trim(hodge4, side="both")
 
@@
 path <- "/Users/beperron/Git/SocialWorkResearch/Data"
-
-# Wrangle the data with the BWR function suite
-ebscoBWR.f(csv=FALSE, path=path)
-#save(bwr.df, file = "HistoricalArticles.R")
 ```
@@
 library(reshape2)
-
-# Inspect dimensions of the data file (Rows X Columns)
-dim(bwr.df)
-
-# Inspect variable names of the data file
-names(bwr.df)
-
-# How many unique article titles?  Ebsco Results of most current search is $n=XXXX$. Do not proceed with analysis if the output does not match this result.  
-length(which(bwr.df$attributes == "TI"))
 ```
 
-# Exclude years 2014 and 2015
+# Data Pre-Processing
+
+# NOTE: CONFIRM THAT SOCIAL CASEWORK IS SAME AS FAMILIES IN SOCIETY.  ENSURE WE 
+# HAVE THE ARTICLES FOR WHEN THE JOURNAL WAS ALSO CALLED THE FAMILY
+# Re-write this to call the R-object directly
+# Overview of processed datafile
+
+Provided below are some basic descriptive statistics before performing any data cleaning.
+
+```{r echo=FALSE, comment=NA} 
+number.of.articles <- length(which(bwr.df$attributes == "TI"))
+range.of.years <- range(bwr.df$record[bwr.df$attributes == "YR"])
+print(number.of.articles)
+print(range.of.years)
+```
+
+```{r echo=FALSE, comment=}
+unique.titles <- filter(bwr.df, attributes == "SO") %>%
+    group_by(record) %>%
+    summarise(
+        N = n())
+print.data.frame(unique.titles, rowNames=FALSE)
+```
+
+# Filter by year
+
+Exclude years 2014 and 2015
 

### 2015-02-03 Analysis.Rmd
Final journal mergers
Adds mergers for the following:

1. Convert "The Family" "The Journal of Social Casework" and "Social
Casework" to "Families in Society"
2. Convert "Education in Social Work" to "Children & Schools"

@@
 
+#add no authorship indicated
+#Anonymous
+x.temp <- filter(bwr.df, attributes == "article")
+x.temp2 <- filter(bwr.df, attributes == "journal")
+
+x.temp3 <- filter(bwr.df, attributes == "author")
+b <- grepl("@", x.temp3$record)
+
+test.case <- filter(bwr.df, attributes == "AU")
+auth.name <- filter(test.case, grepl("(Perron,\\sB)", record))
+
+x.temp <- filter(bwr.df, attributes == "KW" | attributes == "KP")
+
 ```{r initialization_analysis, message=FALSE, warning=FALSE, comment=NA}
@@
                        "Journal of Sociology and Social Welfare", 
+                        bwr.df$record)
+
+bwr.df$record <- ifelse(bwr.df$record == "The Family", 
+                       "Families in Society",
+                       ifelse(bwr.df$record == "Journal of Social Casework",
+                       "Families in Society",
+                       ifelse(bwr.df$record == "Social Casework",
+                       "Families in Society",
+                        bwr.df$record)))
+
+bwr.df$record <- ifelse(bwr.df$record == "Social Work in Education", 
+                       "Children & Schools", 
                         bwr.df$record)

### 2015-02-03 Analysis.Rmd
Minor changes.

@@
 x.temp2 <- filter(bwr.df, attributes == "journal")
+x.temp3 <- filter(bwr.df, attributes == "abstract")
+
+dim(x.temp); dim(x.temp2); dim(x.temp3)
+
+dim(x.temp)
+
+lapply(checks, dim)
 

### 2015-02-03 Analysis.Rmd
Minor updates.
Processed R datafiles as standalone objects.

--- 2015-02-03 Analysis.Rmd
@@
 # Wrangle the data with the BWR function suite
-ebscoBWR.f(csv=FALSE, path=path)
-#save(bwr.df, file = "HistoricalArticles.R")
+ebscoBWR.f(csv=FALSE, path=path, psycInfoOnly = FALSE)
+save(bwr.df, file = "fullDF.R")
 ```
@@
                        "Journal of Sociology and Social Welfare", 
-                        bwr.df$record)
-
-bwr.df$record <- ifelse(bwr.df$record == "The Family", 
-                       "Families in Society",
-                       ifelse(bwr.df$record == "Journal of Social Casework",
-                       "Families in Society",
-                       ifelse(bwr.df$record == "Social Casework",
-                       "Families in Society",
-                        bwr.df$record)))
-
-bwr.df$record <- ifelse(bwr.df$record == "Social Work in Education", 
-                       "Children & Schools", 
                         bwr.df$record)

### 2015-02-03 dataCleaning.Rmd
More data cleaning.

@@
 Provided below are basic descriptive summaries of the results from the full search before further cleaning.
-
 It should be noted that the second-level search was specified to be overly inclusive to help ensure the most comprehensive search possible.
@@
 
+The main file for analysis is `fullDF.R`, and a separate file is just for psycInfo `psycInfoDF.R`.  The same cleaning procedures need to be performed on both data files prior to analysis.
+
+# Initialization of workspace
+
+```{r initialization_dataprocessing, warning=FALSE, message=FALSE, eval=TRUE}
+# Clear workspace
+rm(list=ls())
+
+# Load required packages
+library(ggplot2)
 library(dplyr)
-temp <- bwr.df[bwr.df$articleID == 28300,]
-27743 and 28300.
+
+# Read data files
+load("/Users/beperron/Git/SocialWorkResearch/Data/psycInfoDF.R")
+load("/Users/beperron/Git/SocialWorkResearch/Data/fullDF.R")
+
+# Set the working directory
+setwd("/Users/beperron/Git/SocialWorkResearch/Data")
+```
+
+# Pre-processing summary
+
+Provided below are some basic descriptive statistics before any data of the files processed by `ebscoBWR` function.
+
+```{r echo=FALSE, comment=NA} 
+number.of.articles <- length(which(full.df$attributes == "article"))
+range.of.years <- range(full.df$record[full.df$attributes == "pubYear"])
+cat(number.of.articles)
+cat(range.of.years)
+```
+
+*TO DO* add range of years to the following dplyr summary
+
+```{r echo=FALSE, comment=}
+unique.titles <- filter(full.df, attributes == "journal") %>%
+    group_by(record) %>%
+    summarise(
+        N = n())
+print.data.frame(unique.titles, rowNames=FALSE)
+```
+
+# Data cleaning
+
+The first step is to exclude years 2014 and 2015 due to delays in indexing.
+
+```{r}
+years <- c("2014", "2015")
+ebsco.remove <- full.df[full.df$record %in% years, ]
+ebsco.remove <- ebsco.remove[, "articleID"]
+full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
+```
+
+The articles were reviewed and a first round of exclusions were made.
+
+```{r}
+exclusions <- c(
+    "American Journal of Preventive Medicine", 
+    "Behavior Modification", 
+    "Brain and Cognition",
+    "Canadian Journal of Community Mental Health",
+    "Canadian Journal on Aging",
+    "Early Child Development and Care",
+    "Early Education and Development",
+    "Employee Assistance Quarterly",
+    "Evaluation and Program Planning",
+    "General Hospital Psychiatry",
+    "Hospital Social Service",
+    "International Review of Social Research",
+    "Journal of Applied Behavioral Science",
+    "Journal of Applied Rehabilitation Counseling",
+    "Journal of Community & Applied Social Psychology",
+    "Journal of Health & Human Services Administration",
+    "Journal of Nonverbal Behavior",
+    "Learning Disabilities Research & Practice",
+    "New York State Department of Social Welfare, Division Publication",
+    "Pennsylvania Social Work",
+    "Proceedings of the National Converence of Social Work",
+    "PROFILE Issues in Teachers' Professional Development",
+    "Psychotherapy",
+    "Social Service Department, Presbyterian Hospital, New York",
+    "Social Work Technique",
+    "Social Work Today", # Magazine
+    "Social Work Yearbook",
+    "The New Social Worker",
+    "Systems Research and Behavioral Science",
+    "Teaching and Teacher Education",
+    "University of Chicago Social Service Monograph",
+    "The Scientific Review of Mental Health Practice",
+    "The Clinical Supervisor",
+    "University of Chicago Social Service Monograph")
+ebsco.remove <- full.df[full.df$record %in% exclusions, ]
+ebsco.remove <- ebsco.remove[, "articleID"]
+full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
+
+rm(ebsco.remove)
+```
+
+Journal titles were merged in the following situations:
+
+1.
+2.
+3.
+
+```{r}
+full.df$record <- ifelse(full.df$record == "Eugenics and Social Welfare Bulletin", 
+                       "Eugenics & Social Welfare Bull.", 
+                        full.df$record)
+
+full.df$record <- ifelse(full.df$record == "The British Journal of Social Work", 
+                       "British Journal of Social Work", 
+                        full.df$record)
+
+full.df$record <- ifelse(full.df$record == "Social Work & Social Sciences Review", 
+                       "Social Work and Social Sciences Review", 
+                        full.df$record)
+
+full.df$record <- ifelse(full.df$record == "Social Work with Groups", 
+                       "Social Work With Groups", 
+                        full.df$record)
+
+full.df$record <- ifelse(full.df$record == "Computers in Human Services", 
+                       "Journal of Technology in Human Services", 
+                        full.df$record)
+
+full.df$record <- ifelse(full.df$record == "Journal of Sociology & Social Welfare", 
+                       "Journal of Sociology and Social Welfare", 
+                        full.df$record)
+
+#Note leave space after the (Electronic only)
+full.df$record <- ifelse(full.df$record == "Contemporary Rural Social Work (Electronic only) ", 
+                        "Contemporary Rural Social Work (Electronic only) ", full.df$record)
+
+```
 
@@
 
-```{r initialization_dataprocessing, warning=FALSE, message=FALSE, eval=FALSE}
- # Clear workspace
-rm(list=ls())
-
-# Read BWR functions for Mac OS
-source("/Users/beperron/Git/BibWrangleR/functions/ebscoBWR.R")
-
-# Set the path where original raw data are stored
-setwd("/Users/beperron/Git/SocialWorkResearch/Data")
-
-# Set the working directory to store files created by BWR functions
-path <- "/Users/beperron/Git/SocialWorkResearch/Data"
-```
-
-```{r initialization_analysis, message=FALSE, warning=FALSE, comment=NA}
-rm(list=ls())
-setwd("/Users/beperron/Git/SocialWorkResearch/Data")
-source("/Users/beperron/Git/BibWrangleR/functions/ggsurv.R")
-load("/Users/beperron/Git/SocialWorkResearch/Data/HistoricalArticles.R")
-
-library(dplyr)
-library(ggplot2)
-library(gridExtra)
-library(survival)
-library(grid)
-library(png)
-library(reshape2)
-```
-
-# Data Pre-Processing
-
-# NOTE: CONFIRM THAT SOCIAL CASEWORK IS SAME AS FAMILIES IN SOCIETY.  ENSURE WE 
-# HAVE THE ARTICLES FOR WHEN THE JOURNAL WAS ALSO CALLED THE FAMILY
-# Re-write this to call the R-object directly
-# Overview of processed datafile
-
-Provided below are some basic descriptive statistics before performing any data cleaning.
-
-```{r echo=FALSE, comment=NA} 
-number.of.articles <- length(which(bwr.df$attributes == "TI"))
-range.of.years <- range(bwr.df$record[bwr.df$attributes == "YR"])
-print(number.of.articles)
-print(range.of.years)
-```
-
-```{r echo=FALSE, comment=}
-unique.titles <- filter(bwr.df, attributes == "SO") %>%
-    group_by(record) %>%
-    summarise(
-        N = n())
-print.data.frame(unique.titles, rowNames=FALSE)
 ```
@@
 years <- c("2014", "2015")
-ebsco.remove <- bwr.df[bwr.df$record %in% years, ]
+ebsco.remove <- full.df[full.df$record %in% years, ]
 ebsco.remove <- ebsco.remove[, "articleID"]
-bwr.df <- bwr.df[!(bwr.df$articleID %in% ebsco.remove),]
+full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
 ```
@@
 ```{r}
-bwr.df$record <- ifelse(bwr.df$record == "Eugenics and Social Welfare Bulletin", 
+full.df$record <- ifelse(full.df$record == "Eugenics and Social Welfare Bulletin", 
                        "Eugenics & Social Welfare Bull.", 
-                        bwr.df$record)
+                        full.df$record)
 
-bwr.df$record <- ifelse(bwr.df$record == "The British Journal of Social Work", 
+full.df$record <- ifelse(full.df$record == "The British Journal of Social Work", 
                        "British Journal of Social Work", 
-                        bwr.df$record)
+                        full.df$record)
 
-bwr.df$record <- ifelse(bwr.df$record == "Social Work & Social Sciences Review", 
+full.df$record <- ifelse(full.df$record == "Social Work & Social Sciences Review", 
                        "Social Work and Social Sciences Review", 
-                        bwr.df$record)
+                        full.df$record)
 
-bwr.df$record <- ifelse(bwr.df$record == "Social Work with Groups", 
+full.df$record <- ifelse(full.df$record == "Social Work with Groups", 
                        "Social Work With Groups", 
-                        bwr.df$record)
+                        full.df$record)
 
-bwr.df$record <- ifelse(bwr.df$record == "Computers in Human Services", 
+full.df$record <- ifelse(full.df$record == "Computers in Human Services", 
                        "Journal of Technology in Human Services", 
-                        bwr.df$record)
+                        full.df$record)
 
-bwr.df$record <- ifelse(bwr.df$record == "Journal of Sociology & Social Welfare", 
+full.df$record <- ifelse(full.df$record == "Journal of Sociology & Social Welfare", 
                        "Journal of Sociology and Social Welfare", 
-                        bwr.df$record)
+                        full.df$record)
 
 #Note leave space after the (Electronic only)
-bwr.df$record <- ifelse(bwr.df$record == "Contemporary Rural Social Work (Electronic only) ", 
-                        "Contemporary Rural Social Work (Electronic only) ", bwr.df$record)
+full.df$record <- ifelse(full.df$record == "Contemporary Rural Social Work (Electronic only) ", 
+                        "Contemporary Rural Social Work (Electronic only) ", full.df$record)
 
@@
     "University of Chicago Social Service Monograph")
-ebsco.remove <- bwr.df[bwr.df$record %in% exclusions, ]
+ebsco.remove <- full.df[full.df$record %in% exclusions, ]
 ebsco.remove <- ebsco.remove[, "articleID"]
-bwr.df <- bwr.df[!(bwr.df$articleID %in% ebsco.remove),]
+full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
 ```
@@
 ```{r unique_titles, echo=FALSE}
-unique.titles <- filter(bwr.df, attributes == "SO") %>%
+unique.titles <- filter(full.df, attributes == "SO") %>%
     group_by(record) %>%
@@
 
-title <- bwr.df %>%
+title <- full.df %>%
         filter(attributes == "SO") %>%
@@
 
-article <- bwr.df %>%
+article <- full.df %>%
         filter(attributes == "TI") %>%
@@
 ```{r unique_titles_year, message=FALSE, comment=NA, warning=FALSE, echo=FALSE}
-journals.year <- tbl_df(bwr.df)
+journals.year <- tbl_df(full.df)
 
@@
 
-n.so.yr <- filter(bwr.df, attributes == "SO" | attributes == "YR")
+n.so.yr <- filter(full.df, attributes == "SO" | attributes == "YR")
 
-n.so <- filter(bwr.df, attributes == "SO") %>% mutate(title = record) %>% 
+n.so <- filter(full.df, attributes == "SO") %>% mutate(title = record) %>% 
         select(-attributes, -record)
 
-n.yr <- filter(bwr.df, attributes == "YR") %>% mutate(year = record ) %>% 
+n.yr <- filter(full.df, attributes == "YR") %>% mutate(year = record ) %>% 
         select(-attributes, -record)
@@
 ```{r articles_per_year, echo=FALSE}
-n.articles.year <- filter(bwr.df, attributes == "YR") 
+n.articles.year <- filter(full.df, attributes == "YR") 
 year.split <- split(n.articles.year, n.articles.year$record)
@@
 ```{r keywords_overall, comment=NA, warning=FALSE, message=FALSE, echo=FALSE}
-kp.df <- filter(bwr.df, attributes == "KP")
+kp.df <- filter(full.df, attributes == "KP")
 
@@
 ```{r keywords_over_time, warning=FALSE, message=FALSE, echo=FALSE}
-kp.yr <- filter(bwr.df, attributes == "YR") %>%
+kp.yr <- filter(full.df, attributes == "YR") %>%
     mutate(year = as.numeric(record)) %>% select(-record, -attributes)
 
-kp <- bwr.df %>%
+kp <- full.df %>%
         filter(attributes == "KP") %>%
@@
 ```{r location, comment=NA, warning=FALSE, message=FALSE, echo=FALSE}
-LO.df <- filter(bwr.df, attributes == "LO") %>%
+LO.df <- filter(full.df, attributes == "LO") %>%
          group_by(record) %>%
@@
 library(RColorBrewer)
-year <- filter(bwr.df, attributes == "YR") %>%
+year <- filter(full.df, attributes == "YR") %>%
     mutate(year = as.numeric(record)) %>% select(-record, -attributes)
 
-location.temp <- bwr.df %>%
+location.temp <- full.df %>%
         filter(attributes == "LO") %>%
@@
 ```{r comment=NA, message=FALSE, warning=FALSE, echo=FALSE}
-n.authors.article <- bwr.df %>% 
+n.authors.article <- full.df %>% 
     filter(attributes == "AU") %>%
@@
 ```{r message=FALSE, comment=NA, warning=FALSE, fig.height=2, fig.height=4, echo=FALSE}
-df.2 <- tbl_df(bwr.df)
+df.2 <- tbl_df(full.df)
 year <- df.2 %>%

### 2015-02-03 dataCleaning.Rmd
Working on data cleaning.

@@
 setwd("/Users/beperron/Git/SocialWorkResearch/Data")
+
+# Strip leading and trailing white-space on all records
+full.df$record <- stringr::str_trim(full.df$record, side = "both")
 ```
@@
 
-The articles were reviewed and a first round of exclusions were made.
+The articles were reviewed and a first round of exclusions were made.  All decisions to exclude were based on group consenus.
 
@@
     "Social Work Technique", 
-    "Social Work Today", # Magazine
+    "Social Work Today", 
     "Social Work Yearbook", 
@@
     "University of Chicago Social Service Monograph")
+
 ebsco.remove <- full.df[full.df$record %in% exclusions, ]
@@
 ```{r}
-full.df$record <- ifelse(full.df$record == "Eugenics and Social Welfare Bulletin", 
-                       "Eugenics & Social Welfare Bull.", 
+full.df$record <- ifelse(full.df$record == 
+    "Eugenics and Social Welfare Bulletin",     # Spelling difference
+    "Eugenics & Social Welfare Bull.",          # Spelling difference
                     full.df$record)
 
-full.df$record <- ifelse(full.df$record == "The British Journal of Social Work", 
-                       "British Journal of Social Work", 
+full.df$record <- ifelse(full.df$record == 
+    "The British Journal of Social Work",       # Old name
+    "British Journal of Social Work",           # New name
                     full.df$record)
 
-full.df$record <- ifelse(full.df$record == "Social Work & Social Sciences Review", 
-                       "Social Work and Social Sciences Review", 
+full.df$record <- ifelse(full.df$record == 
+    "Social Work & Social Sciences Review",     # Spelling difference
+    "Social Work and Social Sciences Review",   # Spelling difference
                     full.df$record)
 
-full.df$record <- ifelse(full.df$record == "Social Work with Groups", 
-                       "Social Work With Groups", 
+full.df$record <- ifelse(full.df$record == 
+    "Social Work with Groups",                  # Spelling difference
+    "Social Work With Groups",                  # Spelling difference
                     full.df$record)
 
-full.df$record <- ifelse(full.df$record == "Computers in Human Services", 
-                       "Journal of Technology in Human Services", 
+full.df$record <- ifelse(full.df$record == 
+    "Computers in Human Services",              # Old name
+    "Journal of Technology in Human Services",  # New name 
                     full.df$record)
 
-full.df$record <- ifelse(full.df$record == "Journal of Sociology & Social Welfare", 
-                       "Journal of Sociology and Social Welfare", 
+full.df$record <- ifelse(full.df$record == 
+    "Journal of Sociology & Social Welfare",    # Spelling difference
+    "Journal of Sociology and Social Welfare",  # Spelling difference
                     full.df$record)
 
-#Note leave space after the (Electronic only)
+full.df$record <- ifelse(full.df$record == 
+    "The Family" | full.df$record ==                   # Old name
+    "Journal of Social Casework" | full.df$record ==    # Old name
+    "Social Casework",                                  # Old name
+    "Families in Society",                              # New name
+                    full.df$record)
+
+full.df$record <- ifelse(full.df$record == 
+    "Social Work in Education",                 # Old name
+    "Children & Schools",                       # New name
+                    full.df$record)
+
 full.df$record <- ifelse(full.df$record == "Contemporary Rural Social Work (Electronic only) ", 

### 2015-02-04 dataCleaning.Rmd
Major cleanup.

--- 2015-02-03 dataCleaning.Rmd
@@
 title: 'History of Social Work Research: Data Cleaning'
-output: pdf_document
+output: html_document
 ---
@@
 # Read data files
-load("/Users/beperron/Git/SocialWorkResearch/Data/psycInfoDF.R")
+#load("/Users/beperron/Git/SocialWorkResearch/Data/psycInfoDF.R")
 load("/Users/beperron/Git/SocialWorkResearch/Data/fullDF.R")
@@
 
-```{r echo=FALSE, comment=NA} 
+```{r preprocessing, comment=NA, echo=FALSE} 
 number.of.articles <- length(which(full.df$attributes == "article"))
 range.of.years <- range(full.df$record[full.df$attributes == "pubYear"])
+```
+
+```{r}
+# Number of articles
 cat(number.of.articles)
+```
+
+```{r}
+# Range of years
 cat(range.of.years)
@@
 
-```{r echo=FALSE, comment=}
+```{r date, echo=FALSE, comment=NA}
 unique.titles <- filter(full.df, attributes == "journal") %>%
@@
 full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
+
+range.of.years <- range(full.df$record[full.df$attributes == "pubYear"])
+
+# New range of years
+cat(range.of.years)
 ```
 
-The articles were reviewed and a first round of exclusions were made.
+The articles were reviewed and a first round of exclusions were made based on whether they are journals from within outside of the field of social work.
+Disagreements were resolved by reviewing the mission of the journal to see whether it reflected the study definition of a disciplinary social work journal.
 
-```{r}
-exclusions <- c(
+```{r exclusion1, eval=TRUE}
+exclusions.1 <- c(
     "American Journal of Preventive Medicine", 
@@
     "General Hospital Psychiatry",
-    "Hospital Social Service",
     "International Review of Social Research",
@@
     "Journal of Applied Rehabilitation Counseling",
+    "Journal of Applied Social Sciences",
     "Journal of Community & Applied Social Psychology",
@@
     "Journal of Nonverbal Behavior",
+    "Journal of Psychosomatic Research",
     "Learning Disabilities Research & Practice",
     "New York State Department of Social Welfare, Division Publication",
-    "Pennsylvania Social Work",
     "Proceedings of the National Converence of Social Work",
@@
     "Psychotherapy",
+    "Systems Research and Behavioral Science",
+    "Teaching and Teacher Education",
+    "University of Chicago Social Service Monograph",
+    "The Scientific Review of Mental Health Practice",
+    "The Clinical Supervisor")
+
+ebsco.remove <- full.df[full.df$record %in% exclusions.1, ]
+ebsco.remove <- ebsco.remove[, "articleID"]
+full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
+
+rm(ebsco.remove, exclusions.1)
+```
+
+A second round of exclusions were made.
+
+Journals with less than 10 articles that contributed to the overall number.
+Ten was selected because it was a natural break consisten with a EFA curve...In this cases the exclusion of the titles had virtually no impact on the overall article count.
+However, it did inflate the number of journal titles.
+Excluded if we could not identify the journal and associated articles -- that is, it wasn't available and, therefore, not part of the scholarly record.
+
++ _Social Work Process_ was retained because it was a verified journal from U Penn
+
+```{r exclusion2, eval=TRUE}
+exclusions.2 <- c(
+    "Eugenics and Social Welfare Bulletin",
+    "Eugenics & Social Welfare Bull.",
+    "Issues in Social Work Education", 
+    "Hospital Social Service",  #Confirmed nursing journal
+    "International Conference of Social Work",
+    "Journal of Multicultural Social Work",
+    "Journal of Teaching in Social Work", 
+    "Maatskaplike Werk/Social Work",
+    "Medical Social Work",
+    "New York State Department of Social Welfare, Division Publication",
+    "Pediatric Social Work", 
+    "Pennsylvania Social Work",
+    "Social Service",    
     "Social Service Department, Presbyterian Hospital, New York",
+    "Social Service Monographs",
+    "School Social Work Quarterly", # Published only one edition
+    "Social Work Today",
     "Social Work Technique",
@@
     "The New Social Worker",
-    "Systems Research and Behavioral Science",
-    "Teaching and Teacher Education",
-    "University of Chicago Social Service Monograph",
-    "The Scientific Review of Mental Health Practice",
-    "The Clinical Supervisor",
-    "University of Chicago Social Service Monograph")
-ebsco.remove <- full.df[full.df$record %in% exclusions, ]
+    "Pennsylvania Social Work",
+    "University of Chicago Social Service Monograph" # Single record
+    )
+
+ebsco.remove <- full.df[full.df$record %in% exclusions.2, ]
 ebsco.remove <- ebsco.remove[, "articleID"]
@@
 
-rm(ebsco.remove)
+rm(ebsco.remove, exclusions.2)
 ```
@@
 
-1.
-2.
-3.
-
-```{r}
-full.df$record <- ifelse(full.df$record == "Eugenics and Social Welfare Bulletin", 
-                       "Eugenics & Social Welfare Bull.", 
-                        full.df$record)
-
+```{r titleMerge, eval=TRUE}
 full.df$record <- ifelse(full.df$record == "The British Journal of Social Work", 
@@
 
-#Note leave space after the (Electronic only)
-full.df$record <- ifelse(full.df$record == "Contemporary Rural Social Work (Electronic only) ", 
-                        "Contemporary Rural Social Work (Electronic only) ", full.df$record)
+full.df$record <- ifelse(full.df$record == "The Family", 
+                       "Families in Society",
+                       ifelse(full.df$record == "Journal of Social Casework",
+                       "Families in Society",
+                       ifelse(full.df$record == "Social Casework",
+                       "Families in Society",
+                        full.df$record)))
 
+full.df$record <- ifelse(full.df$record == "Social Work in Education", 
+                       "Children & Schools", 
+                        full.df$record)
 ```
 
-```{r}
+# Coverage via Hodge article
+
+```{r hodgeCompare, eval=FALSE}
 hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
@@
 
-# Filter by year
+# Post-processing summary
 
-Exclude years 2014 and 2015
++ to do ... summary with hodge list
 
-```{r}
-years <- c("2014", "2015")
-ebsco.remove <- full.df[full.df$record %in% years, ]
-ebsco.remove <- ebsco.remove[, "articleID"]
-full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
-```
-
-# Merge journal titles
-
-```{r}
-full.df$record <- ifelse(full.df$record == "Eugenics and Social Welfare Bulletin", 
-                       "Eugenics & Social Welfare Bull.", 
-                        full.df$record)
-
-full.df$record <- ifelse(full.df$record == "The British Journal of Social Work", 
-                       "British Journal of Social Work", 
-                        full.df$record)
-
-full.df$record <- ifelse(full.df$record == "Social Work & Social Sciences Review", 
-                       "Social Work and Social Sciences Review", 
-                        full.df$record)
-
-full.df$record <- ifelse(full.df$record == "Social Work with Groups", 
-                       "Social Work With Groups", 
-                        full.df$record)
-
-full.df$record <- ifelse(full.df$record == "Computers in Human Services", 
-                       "Journal of Technology in Human Services", 
-                        full.df$record)
-
-full.df$record <- ifelse(full.df$record == "Journal of Sociology & Social Welfare", 
-                       "Journal of Sociology and Social Welfare", 
-                        full.df$record)
-
-#Note leave space after the (Electronic only)
-full.df$record <- ifelse(full.df$record == "Contemporary Rural Social Work (Electronic only) ", 
-                        "Contemporary Rural Social Work (Electronic only) ", full.df$record)
-
-```
-
-# Journals excluded from search results.
-
-```{r}
-exclusions <- c(
-    "American Journal of Preventive Medicine", 
-    "Behavior Modification", 
-    "Brain and Cognition",
-    "Canadian Journal of Community Mental Health",
-    "Canadian Journal on Aging",
-    "Early Child Development and Care",
-    "Early Education and Development",
-    "Employee Assistance Quarterly",
-    "Evaluation and Program Planning",
-    "General Hospital Psychiatry",
-    "Hospital Social Service",
-    "International Review of Social Research",
-    "Journal of Applied Behavioral Science",
-    "Journal of Applied Rehabilitation Counseling",
-    "Journal of Community & Applied Social Psychology",
-    "Journal of Health & Human Services Administration",
-    "Journal of Nonverbal Behavior",
-    "Learning Disabilities Research & Practice",
-    "New York State Department of Social Welfare, Division Publication",
-    "Pennsylvania Social Work",
-    "Proceedings of the National Converence of Social Work",
-    "PROFILE Issues in Teachers' Professional Development",
-    "Psychotherapy",
-    "Social Service Department, Presbyterian Hospital, New York",
-    "Social Work Technique",
-    "Social Work Today", # Magazine
-    "Social Work Yearbook",
-    "The New Social Worker",
-    "Systems Research and Behavioral Science",
-    "Teaching and Teacher Education",
-    "University of Chicago Social Service Monograph",
-    "The Scientific Review of Mental Health Practice",
-    "The Clinical Supervisor",
-    "University of Chicago Social Service Monograph")
-ebsco.remove <- full.df[full.df$record %in% exclusions, ]
-ebsco.remove <- ebsco.remove[, "articleID"]
-full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
-```
-
-```{r unique_titles, echo=FALSE}
-unique.titles <- filter(full.df, attributes == "SO") %>%
+```{r echo=FALSE, comment=NA}
+unique.titles <- filter(full.df, attributes == "journal") %>%
     group_by(record) %>%
@@
         N = n())
+print.data.frame(unique.titles, rowNames=FALSE)
 ```
 
-# Preliminary Analyses
+```{r comment=NA, echo=FALSE} 
+number.of.articles <- length(which(full.df$attributes == "article"))
+range.of.years <- range(full.df$record[full.df$attributes == "pubYear"])
+```
 
-## Summary of all journal titles included in the analysis
+```{r}
+# Number of articles
+cat(number.of.articles)
+```
 
-To do:
+```{r}
+# Range of years
+cat(range.of.years)
+```
 
-+ In the table, include the first and last years of indexing, and the numbers of articles.  
-+ Write the script to output a *.csv file so that it can be included as an Appendix without any formatting.
+*TO DO* add range of years to the following dplyr summary
 
-```{r unique_titles, echo=FALSE}
-unique.titles <- filter(full.df, attributes == "SO") %>%
+```{r echo=FALSE, comment=NA}
+unique.titles <- filter(full.df, attributes == "journal") %>%
     group_by(record) %>%
@@
         N = n())
-
-title <- full.df %>%
-        filter(attributes == "SO") %>%
-        select(id = articleID, SO = record)
-
-article <- full.df %>%
-        filter(attributes == "TI") %>%
-        select(id = articleID, journal.title = record)
-
-title.articles <- title %>% 
-        left_join(article) %>%
-        group_by(title)
-
-# Number of unique titles
-number.journals <- length(unique(unique.titles$record))
-
-# Unique titles
-journals.unique <- unique(unique.titles$record)
-#write.csv(journals.unique, "journals.csv")
-
-number.journals
-sort(journals.unique)
-socialWorkJournals <- journals.unique
-#save(journals.unique, file="socialWorkJournals.R")
+print.data.frame(unique.titles, rowNames=FALSE)
 ```
 
-## Count of unique journal titles over time
-
-To do:
-+ Integrate the full journal listing of EbscoHost 
-+ Plot overall number of journals over time 
-+ Plot overall number of journals by major discipline category as defined by EbscoHost classification -- use sociology, anthropology, economics, psychology, and political science
-+ The following "overall growth" plot excludes social work journals in this study.
-There were a small number of overlap journals between social science and social work journals (N = 4 -- double check for final analysis.
-The journals that overlapped were included in the social work group.
-
-```{r unique_titles_year, message=FALSE, comment=NA, warning=FALSE, echo=FALSE}
-journals.year <- tbl_df(full.df)
-
-year <- journals.year %>%
-        filter(attributes == "YR") %>%
-        select(id = articleID, year = record)
-
-journals <- journals.year %>%
-        filter(attributes == "SO") %>%
-        select(id = articleID, journal.title = record)
-
-n.journals.year <- journals %>% 
-        left_join(year) %>%
-        group_by(year) %>%
-        distinct(journal.title) %>%
-        summarise(n = n())
-
-journal.count <- ggplot(n.journals.year, aes(as.numeric(year), y=n, group=1)) + 
-    geom_line(colour="darkblue") +
-    #geom_point(colour="red") + 
-    theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-    xlab("Publication year") + 
-    ylab("Number") + 
-    ggtitle("Number of Journals Over Time") + 
-    scale_x_continuous(breaks=seq(1914, 2014, 5))
-
-journal.count
-```
-
-## Growth of Social Work compared to growth of the social sciences
-
-This section shows the overall growth of the social sciences.  This includes all _academic journals_ (excluding magazines and trade publications) that have the following discipline tag:
-
-+ Sociology
-+ Psychology
-+ Economics
-+ Political Science & Studies
-+ Economics
-+ Anthropology
-
-```{r echo=FALSE}
-ebscoFullListing.df <- ebscoFullListing.df[ebscoFullListing.df$SourceType == "Academic Journal",]
-ebscoFullListing.df$IndexingStart <- format(as.Date(ebscoFullListing.df$IndexingStart, "%m/%d/%Y"), "%Y")
-ebscoFullListing.df$IndexingStop <- format(as.Date(ebscoFullListing.df$IndexingStop, "%m/%d/%Y"), "%Y")
-ebJournals.df <- ebscoFullListing.df %>% filter(SourceType == "Academic Journal") %>%
-    select(Discipline, IndexingStart, IndexingStop, PublicationName, ISSN) %>%
-    mutate(IndexingStart = as.numeric(IndexingStart), IndexingStop = as.numeric(IndexingStop)) %>%
-    filter(Discipline == "Sociology" | Discipline == "Political Science & Studies"| 
-           Discipline == "Psychology"| Discipline == "Economics" | Discipline == "Anthropology") 
-```
-
-Some of the journals have duplicate entries in the database because they are cross-classified in multiple social science disciplines.
-The following code is used to create a data set that excludes duplicate entries in the database and ensures no overlap between the social science list and the social work list of journals.
-Duplicates are identified based on ISSN, not journal title.
-This will ensure all duplicates are identified.
-
-```{r}
-ebJournals.df.issn <- ebJournals.df %>% select(ISSN)
-ebJournals.df.unique <- !duplicated(ebJournals.df.issn)
-
-#This function here tests whether the duplication identifier correctly gets the first unique record (by assigning TRUE) and then excluding subsequent records (by assigning FALSE) 
-#cbind(ebJournals.df.unique, ebJournals.df.issn$ISSN)
-
-#This subsets out the duplicates
-ebJournals.df.no.duplicates <- ebJournals.df[ebJournals.df.unique, ]
-
-#This function does a logical comparison of the social science journals and the social work journals to determine potential overlap.  
-overlap <- ebJournals.df.no.duplicates[(ebJournals.df.no.duplicates$PublicationName %in% journals.unique),]  
-print(overlap)
-
-#This reduces the overlap from the social science journal lists, retaining the overlap in the social work journals
-ebJournals.df.no.overlap <- ebJournals.df.no.duplicates[!(ebJournals.df.no.duplicates$PublicationName %in% journals.unique),]   
-```
-
-This section uses the `melt` function to transform the social science data file into a format that can be plotted using ``ggplot2`.  
-```{r echo=FALSE}
-
-#Remove variables that will interfere with melting procedure
-socialScienceJournals.df <- ebJournals.df.no.overlap %>% 
-    select(-PublicationName, -ISSN) %>%
-    mutate(journalID = c(1:nrow(ebJournals.df.no.overlap))) %>%
-    mutate(journalID = as.factor(journalID)) %>% 
-    select(-Discipline)
-
-socialScienceJournals.melted <- melt(socialScienceJournals.df)
-
-ebJournals.overtime.start.d <- socialScienceJournals.melted %>% 
-    filter(value = !is.na(value)) %>%
-    group_by(value) %>%
-    summarise(N.start = n())
-
-ebJournals.overtime.end.d <- socialScienceJournals.melted %>%
-    filter(variable == "IndexingStop"  & !is.na(value)) %>%
-    group_by(value) %>%
-    summarise(N.end = n())
-
-ebjournals.joined.d <- left_join(ebJournals.overtime.start.d, ebJournals.overtime.end.d) %>%
-    mutate(N.end = ifelse(is.na(N.end), 0, N.end), Cumulative = cumsum(N.start)) %>%
-    mutate(N.adjusted = Cumulative - N.end)
-
-journal.time.reduced <- n.journals.year %>% filter(year >= 1950)
-ggplot() + 
-    geom_line(data = ebjournals.joined.d, aes(x=value, y=N.adjusted), group=1, colour="purple") + 
-    geom_line(data = journal.time.reduced, aes(as.numeric(year), y=n), group=1, colour="darkblue")
-```
-
-## What journals published the most number of articles
-
-```{r journal_output, echo=FALSE}
-
-n.so.yr <- filter(full.df, attributes == "SO" | attributes == "YR")
-
-n.so <- filter(full.df, attributes == "SO") %>% mutate(title = record) %>% 
-        select(-attributes, -record)
-
-n.yr <- filter(full.df, attributes == "YR") %>% mutate(year = record ) %>% 
-        select(-attributes, -record)
-
-n.so.yr <- left_join(n.so, n.yr) %>%
-    group_by(title) %>%
-    summarise(first = min(year), last = max(year), n.to.date = n()) %>%
-    arrange(desc(n.to.date))
-
-# 10 highest number of publications
-head(n.so.yr, 20)
-```
-
-## What is the lifespan of journals?
-
-To do:
-+ Incorporate all EbscoHost journals and the separate disciplinary journals
-
-```{r journal_lifespan, echo=FALSE}
-#10 longest running journals 
-longest.running <- n.so.yr %>%
-       mutate(last = as.numeric(last), first = as.numeric(first), 
-              year.diff = last - first) %>%
-       arrange(desc(year.diff)) %>%
-       select(title, first, last, year.diff) %>%
-       mutate(stop = year.diff, event = ifelse(as.numeric(last) != 2013, 1, 0)) %>%
-       select(title, stop, event, as.numeric(first))
-
-survival.journals <- survfit(Surv(longest.running$stop+1, longest.running$event) ~ 1)
-median.survival <- data.frame(time = c(24,24), quant = c(.5,0))
-
-head(longest.running)
-
-ggsurv(survival.journals) + 
-    #geom_line(data = median.survival, aes(time, quant), linetype="longdash") +
-    #annotate("segment", x = 32, xend = 27, y = .12, yend = .12, size = .25, arrow =arrow()) +
-    #geom_text(x = 45, y =.12, label = "median survival", size = 4) + 
-    geom_text(x = 75, y =.75, label = "+ = Last year of indexing", size = 4) +
-    ylim(0,1) +
-    xlim(0,50) + 
-    xlab("Survival Time (in years)") +
-    ylab("Survival Probability") +
-    ggtitle("Survival Probability of Social Work Journals")
-
-```
-
-## What is the number of articles published per year
-
-To do:
-+ Plot against major disciplinary categories
-
-```{r articles_per_year, echo=FALSE}
-n.articles.year <- filter(full.df, attributes == "YR") 
-year.split <- split(n.articles.year, n.articles.year$record)
-year.count <- unlist(lapply(year.split, nrow))
-year.count <- year.count[order(names(year.count))]
-years <- names(year.count)
-
-df <- data.frame(years, year.count)
-rownames(df) <- NULL
-
-plot.article.count <- ggplot(df, aes(as.factor(years), 
-                    y = year.count, group=1)) + 
-    geom_line(colour="black") +
-    #geom_point(colour="red") + 
-    theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-    xlab("year") + 
-    ylab("count") + 
-    ggtitle("Number of Studies by Year") +
-    scale_x_discrete(breaks=c(seq(1914, 2015, 10))) +
-    scale_y_continuous(breaks = c(seq(0, 2000, 250)))
-
-df$years <- as.numeric(as.character(df$years))
-
-plot.article.cumulative <- ggplot(df, aes(x = years, y = cumsum(year.count))) + 
-    geom_line() + 
-    theme(axis.text.x = element_text(angle=45, hjust=1)) +
-    scale_x_continuous(breaks=pretty(df$years)) +
-    xlab("year") +  
-    ylab("count") +
-    scale_x_continuous(breaks = c(seq(1914,2014,10))) +
-    scale_y_continuous(breaks = c(seq(0, 25000, 2500))) + 
-    ggtitle("Cumulative Frequency")
-
-grid.arrange(plot.article.count, plot.article.cumulative, ncol=2)
-
-# Print most recent ten years
-tail(df, 10)
-```
-
-# What are the most frequent topic areas (by author specified keywords)?
-
-To do:  
-+ Fix script that performs matching -- convert all keywords to lower before matching
-
-```{r keywords_overall, comment=NA, warning=FALSE, message=FALSE, echo=FALSE}
-kp.df <- filter(full.df, attributes == "KP")
-
-subject.terms <- stringr::str_split(kp.df$record, pattern = ";")
-subject.terms <- tolower(subject.terms)
-subject.terms <- unlist(lapply(subject.terms, function(x) gsub(" ", "", x)))
-subject.terms.total <- length(unlist(lapply(subject.terms, 
-                        function(x) gsub(" ", "", x))))
-
-subject.terms.unique <- length(unique(subject.terms))
-
-subject.terms.l <- list(subject.terms.total = subject.terms.total,
-                      subject.terms.unique = subject.terms.unique)
-
-most.frequent <- as.data.frame(table(subject.terms))
-
-most.frequent <- arrange(most.frequent, desc(Freq))
-
-# Print summary statistics
-print(subject.terms.l)
-
-# Print 25 most frequent
-head(most.frequent, 25)
-```
-
-## Most Frequent Author Keywords
-
-_DO NOT INTERPRET RESULTS HERE THIS SECTION IS NOT WORKING PROPERLY_
-
-For this analysis (to-do), select a few keywords that may tell an interesting story of how they change over time -- something that might be revealing of 'trends.'
-
-```{r keywords_over_time, warning=FALSE, message=FALSE, echo=FALSE}
-kp.yr <- filter(full.df, attributes == "YR") %>%
-    mutate(year = as.numeric(record)) %>% select(-record, -attributes)
-
-kp <- full.df %>%
-        filter(attributes == "KP") %>%
-        select(articleID = articleID, keyword = record) %>%
-        mutate(keyword = gsub(" ", "", keyword))
-
-kp.year <- kp %>% 
-         left_join(kp.yr) %>%
-         group_by(keyword, year) %>%
-         summarise(n = n()) %>%
-         arrange(keyword, year, n)
-
-select.keywords <- c("women", "leadership")
-select.keywords.df <- kp.year %>% filter(tolower(keyword) %in% select.keywords)
-
-library(plyr) # Fix code so ply loads before dplyr
-key.plot.df <- ddply(select.keywords.df, .(keyword), transform, cumulative = cumsum(n))
-detach(package:plyr)
-
-#Fix graph to sort the keywords / colour
-ggplot(key.plot.df, aes(x = year, y = cumulative, colour = keyword, group = keyword)) + 
-    geom_line() +
-    ggtitle("Cumulative Sum of Articles by Keywords") +
-    ylab("Cumulative Sum") + 
-    xlab("Year") + 
-    theme(legend.title=element_blank())
-
-```
-
-## Location of Studies
-
-To do:
-+ Determine best format / presentation of map
-
-```{r location, comment=NA, warning=FALSE, message=FALSE, echo=FALSE}
-LO.df <- filter(full.df, attributes == "LO") %>%
-         group_by(record) %>%
-         summarise(Country = unique(record),
-                   N = n()) %>%
-        arrange(desc(N)) %>% 
-        select(-record)
-
-locations <- as.data.frame(table(LO.df))
-locations <- arrange(locations, desc(Freq))
-locations.unique <- length(unique(locations))
-
-#write.csv(locations, "location.csv")
-
-```
-
-## Location of studies over time
-
-To do:
-+ Determine best format / presentation of map
-
-```{r location_over_time, warning=FALSE, message=FALSE, echo=FALSE}
-library(RColorBrewer)
-year <- filter(full.df, attributes == "YR") %>%
-    mutate(year = as.numeric(record)) %>% select(-record, -attributes)
-
-location.temp <- full.df %>%
-        filter(attributes == "LO") %>%
-        select(articleID = articleID, country = record) %>%
-        mutate(country = gsub(" ", "", country))
-
-location.year <- location.temp %>% 
-         left_join(year) %>%
-         group_by(country, year) %>%
-         summarise(n = n()) %>%
-         arrange(country, year, n) %>%
-         mutate(cumsum_n = cumsum(n), log_n = log(n+1))
-
-top.locations <- LO.df %>% 
-                 select(Country) %>%
-                 slice(1:5)
-
-top.locations$Country <- gsub(" ", "", top.locations$Country)
-
-location.year.top <- location.year %>% filter(country %in% top.locations$Country)
-
-ggplot(location.year.top, aes(x = year, y = log_n, colour = country )) + 
-    geom_line() +
-    ggtitle("Log Number of Articles by Countries With Highest Scholarly Ouput") +
-    xlab("Publication Year") + 
-    ylab("log N+1") +
-    theme(legend.position=c(.210, .7))
-
-top.locations.no.us <- LO.df %>% 
-                select(Country) %>%
-                slice(2:10)
-
-top.locations.no.us$Country <- gsub(" ", "", top.locations.no.us$Country)
-
-location.year.top.no.us <- location.year %>% filter(country %in% top.locations.no.us$Country)
-
-ggplot(location.year.top.no.us, aes(x = year, y = cumsum_n, colour = country )) + geom_line() +
-    ggtitle("Cumulative Number of Article by Countries with Highest Scholarly Output \n(Excluding the United States)") +
-    theme(legend.position=c(.210, .6))
-```
-## Countries represents in the social work research
-
-To do:
-+ Obtain definition of `LO` tag.  
-+ Determine how many articles had LO tag (note the issue if not included from Social Science Index)
-
-```{r fig.width=8, echo=FALSE}
-Map100YearWithUS <- readPNG("/Users/beperron/Git/SocialWorkResearch/images/Map100Years.png")
-grid.raster(Map100YearWithUS)
-
-Map100YearWithoutUS <- readPNG("/Users/beperron/Git/SocialWorkResearch/images/Map100YearsWithoutUS.png")
-grid.raster(Map100YearWithUS)
-```
-
-## Countries not represented in social work research
-
-```{r fig.width=8, echo=FALSE}
-library(png)
-library(grid)
-img <- readPNG("/Users/beperron/Git/SocialWorkResearch/images/NotRepresented100Years.png")
-grid.raster(img)
-
-```
-
-## Number of authors
-```{r comment=NA, message=FALSE, warning=FALSE, echo=FALSE}
-n.authors.article <- full.df %>% 
-    filter(attributes == "AU") %>%
-    select(id = articleID, author= record) %>%
-    mutate(id = as.numeric(id))
-
-n_authors.1 <- n.authors.article %>% 
-        group_by(id) %>%
-        summarise(n = n())
-
-n_authors.1t <- n_authors.1 %>% mutate(n = ifelse(n >=6, 6, n)) %>% 
-    group_by(n) %>%
-    summarise(Articles = n())
-
-ggplot(n_authors.1t, aes(x = n, y = Articles)) +
-    geom_bar(stat="identity", colour="black", fill = "white") +
-    geom_text(aes(label = Articles), vjust=-.3, size = 4) +
-    scale_x_discrete(limits = c(as.character(1:5), "6+")) + 
-    ggtitle("Number of Articles by Author Count") + 
-    xlab("Author Count") + 
-    ylab("Articles")
-```
-
-## Number of authors over time
-
-This figure shows the average number of authors, along with the standard deviation as the ribbon around the average.
-Note that there is a possible problem in these data, with a single article listing a huge number.
-That can be corrected at a later time.
-
-```{r message=FALSE, comment=NA, warning=FALSE, fig.height=2, fig.height=4, echo=FALSE}
-df.2 <- tbl_df(full.df)
-year <- df.2 %>%
-        filter(attributes == "YR") %>%
-        select(id = articleID, year = record)
-
-authors <- df.2 %>%
-        filter(attributes == "AU") %>%
-        select(id = articleID, author = record)
-
-n_authors <- authors %>%
-        group_by(id) %>%
-        summarise(n=n())
-
-n_authors <- n_authors %>% 
-        left_join(year) %>%
-        group_by(year) %>%
-        summarise(median.n = median(n),
-                  average.n = mean(n),
-                  min.n = min(n),
-                  max.n = max(n),
-                  std.dev  = sd(n) )
-
-plot.author.count2 <- ggplot(n_authors, aes(as.numeric(year), y=average.n, group=1)) +  
-    geom_ribbon(aes(ymin = average.n-std.dev, ymax=average.n+std.dev), colour="lightblue", fill="lightblue", alpha=.40) +
-    geom_line(colour="black") + 
-    geom_segment(aes(x= 1940, y = 5.5, xend = 1935, yend = 5.5), 
-                 arrow=arrow(length=unit(0.25, "cm"))) +
-    annotate("text", x = 1951, y = 5.5, label = "1 outlier case of \n24 listed authors", size=3.5) +
-    ylab("Average number of authors (black) \nStandard deviation (light blue)") +
-    xlab("Publication year") +
-    ggtitle("Average Number of Authors per Article Over Time")
-
-plot.author.count2
-
-```
-
-```
+names(full.df)

### 2015-02-04 dataCleaning.Rmd

@@
 
+The articles were reviewed and a first round of exclusions were made.  All decisions to exclude were based on group consenus.
+
 range.of.years <- range(full.df$record[full.df$attributes == "pubYear"])
@@
     "Psychotherapy",
+    "Social Service Department, Presbyterian Hospital, New York",
+    "Social Work Technique", 
+    "Social Work Today", 
+    "Social Work Yearbook", 
+    "The New Social Worker",
     "Systems Research and Behavioral Science",
@@
     "The Scientific Review of Mental Health Practice",
-    "The Clinical Supervisor")
+    "The Clinical Supervisor",
+    "University of Chicago Social Service Monograph")
 
@@
 
-rm(ebsco.remove, exclusions.1)
+rm(ebsco.remove)
+```
+
+Journal titles were merged in the following situations:
+
+1.
+2.
+3.
+
+```{r}
+full.df$record <- ifelse(full.df$record == 
+    "Eugenics and Social Welfare Bulletin",     # Spelling difference
+    "Eugenics & Social Welfare Bull.",          # Spelling difference
+                    full.df$record)
+
+full.df$record <- ifelse(full.df$record == 
+    "The British Journal of Social Work",       # Old name
+    "British Journal of Social Work",           # New name
+                    full.df$record)
+
+full.df$record <- ifelse(full.df$record == 
+    "Social Work & Social Sciences Review",     # Spelling difference
+    "Social Work and Social Sciences Review",   # Spelling difference
+                    full.df$record)
+
+full.df$record <- ifelse(full.df$record == 
+    "Social Work with Groups",                  # Spelling difference
+    "Social Work With Groups",                  # Spelling difference
+                    full.df$record)
+
+full.df$record <- ifelse(full.df$record == 
+    "Computers in Human Services",              # Old name
+    "Journal of Technology in Human Services",  # New name 
+                    full.df$record)
+
+full.df$record <- ifelse(full.df$record == 
+    "Journal of Sociology & Social Welfare",    # Spelling difference
+    "Journal of Sociology and Social Welfare",  # Spelling difference
+                    full.df$record)
+
+full.df$record <- ifelse(full.df$record == 
+    "The Family" | full.df$record ==                   # Old name
+    "Journal of Social Casework" | full.df$record ==    # Old name
+    "Social Casework",                                  # Old name
+    "Families in Society",                              # New name
+                    full.df$record)
+
+full.df$record <- ifelse(full.df$record == 
+    "Social Work in Education",                 # Old name
+    "Children & Schools",                       # New name
+                    full.df$record)
+
+full.df$record <- ifelse(full.df$record == "Contemporary Rural Social Work (Electronic only) ", 
+                        "Contemporary Rural Social Work (Electronic only) ", full.df$record)
+
 ```

### 2015-02-04 dataCleaning.Rmd
Updated R objects.

--- 2015-02-04 dataCleaning.Rmd
@@
 full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
-
-range.of.years <- range(full.df$record[full.df$attributes == "pubYear"])
-
-# New range of years
-cat(range.of.years)
 ```
@@
     "New York State Department of Social Welfare, Division Publication",
-    "Proceedings of the National Converence of Social Work",
+    "Proceedings of the National Conference of Social Work",
     "PROFILE Issues in Teachers' Professional Development",
     "Psychotherapy",
+    "Social Service Department, Presbyterian Hospital, New York",
+    "Social Work Technique", 
+    "Social Work Today", 
+    "Social Work Yearbook", 
+    "The New Social Worker",
     "Systems Research and Behavioral Science",
@@
 
-rm(ebsco.remove, exclusions.1)
+rm(ebsco.remove)
 ```
@@
     "Journal of Multicultural Social Work",
+    "Journal of Social Work Process",
     "Journal of Teaching in Social Work", 
@@
 ```{r titleMerge, eval=TRUE}
-full.df$record <- ifelse(full.df$record == "The British Journal of Social Work", 
-                       "British Journal of Social Work", 
+full.df$record <- ifelse(full.df$record == 
+        "The British Journal of Social Work",       # Old title
+        "British Journal of Social Work",           # New title
                         full.df$record)
 
-full.df$record <- ifelse(full.df$record == "Social Work & Social Sciences Review", 
+full.df$record <- ifelse(full.df$record == 
+        "Social Work & Social Sciences Review",     # Spelling difference
         "Social Work and Social Sciences Review", 
@@
 
-full.df$record <- ifelse(full.df$record == "Social Work with Groups", 
+full.df$record <- ifelse(full.df$record == 
+        "Social Work with Groups",                  # Spelling difference
         "Social Work With Groups", 
@@
 
-full.df$record <- ifelse(full.df$record == "Computers in Human Services", 
-                       "Journal of Technology in Human Services", 
+full.df$record <- ifelse(full.df$record == 
+        "Computers in Human Services",              # Old title
+        "Journal of Technology in Human Services",  # New title
                         full.df$record)
 
-full.df$record <- ifelse(full.df$record == "Journal of Sociology & Social Welfare", 
+full.df$record <- ifelse(full.df$record == 
+        "Journal of Sociology & Social Welfare",    # Spelling difference
         "Journal of Sociology and Social Welfare",  
@@
 
-full.df$record <- ifelse(full.df$record == "The Family", 
-                       "Families in Society",
-                       ifelse(full.df$record == "Journal of Social Casework",
-                       "Families in Society",
-                       ifelse(full.df$record == "Social Casework",
-                       "Families in Society",
-                        full.df$record)))
+full.df$record <- ifelse(full.df$record == 
+        "The Family" | full.df$record ==                    # Old title
+        "Journal of Social Casework" | full.df$record ==    # Old title
+        "Social Casework",                                  # Old title
+        "Families in Society",                              # New title
+                        full.df$record)
 
-full.df$record <- ifelse(full.df$record == "Social Work in Education", 
-                       "Children & Schools", 
+full.df$record <- ifelse(full.df$record == 
+        "Social Work in Education",                 # Old title
+        "Children & Schools",                       # New title
                     full.df$record)
@@
 ```
-
-*TO DO* add range of years to the following dplyr summary
-
-```{r echo=FALSE, comment=NA}
-unique.titles <- filter(full.df, attributes == "journal") %>%
-    group_by(record) %>%
-    summarise(
-        N = n())
-print.data.frame(unique.titles, rowNames=FALSE)
-```
-
-names(full.df)

### 2015-02-04 dataCleaning.Rmd
Finalizing document. All functional.

@@
 ---
-title: 'History of Social Work Research: Data Cleaning'
+title: "History of Social Work Research"
+author: "Summary of Data Cleaning Procedures"
 output: html_document
@@
 Provided below are basic descriptive summaries of the results from the full search before further cleaning.
-It should be noted that the second-level search was specified to be overly inclusive to help ensure the most comprehensive search possible.
-All journal titles from the secondary search are identified in the following summary.
 
@@
 # Pre-processing summary
+```{r echo=FALSE}
+full.df$record <- ifelse(full.df$record == 
+        "Social Work & Social Sciences Review",     # Spelling difference
+        "Social Work and Social Sciences Review", 
+                        full.df$record)
 
-Provided below are some basic descriptive statistics before any data of the files processed by `ebscoBWR` function.
+full.df$record <- ifelse(full.df$record == 
+        "Social Work with Groups",                  # Spelling difference
+        "Social Work With Groups", 
+                        full.df$record)
 
-```{r preprocessing, comment=NA, echo=FALSE} 
+full.df$record <- ifelse(full.df$record == 
+        "Journal of Sociology & Social Welfare",    # Spelling difference
+        "Journal of Sociology and Social Welfare",  
+                        full.df$record)
+```
+
+Provided below is a summary of the datafile processed by `ebscoBWR` function before any cleaning procedures specifically for this project were employed, with the exception of resolving spelling errors or differences.
+For example, _Social Work With Groups_ was exported as a separate journal than _Social Work with Groups_ (note the capitalization difference in the word _with_.)
+
+```{r preprocessing, comment=NA, echo=TRUE} 
 number.of.articles <- length(which(full.df$attributes == "article"))
@@
 
-*TO DO* add range of years to the following dplyr summary
-
 ```{r date, echo=FALSE, comment=NA}
@@
 
-The first step is to exclude years 2014 and 2015 due to delays in indexing.
+Inspection of the data indicated notable delays in indexing for the years 2014 and 2015.
+Therefore, these years were excluded from the current study.
+Thus, this study includes journals indexed through the end of 2013.
+
+## Year specification
 
@@
 
-The articles were reviewed and a first round of exclusions were made based on whether they are journals from within outside of the field of social work.
-Disagreements were resolved by reviewing the mission of the journal to see whether it reflected the study definition of a disciplinary social work journal.
+## Exclusion of journals not meeting supplemental search terms
+
+The search for journals involved a two-stage process.
+It began by extracting all records from journals based on the social work journal list of Hodge and L (APA cite).
+Journals were excluded if they did not contain one of the major search terms from the supplemental list.
+The majority of these journals were captured in the supplemental search query because the journal used one of the supplemental search terms in a special issue.
+The mission and scope of journals were also reviewed when it was unclear whether the journal was specific to social work research (e.g., _The Clinical Supervisor_).
+The supplemental search terms included:
+
++ social work
++ social welfare
++ social casework (or social case work)
++ social service
++ human service
++ social development 
++ social environment
 
@@
     "Learning Disabilities Research & Practice",
-    "New York State Department of Social Welfare, Division Publication",
-    "Proceedings of the National Conference of Social Work",
     "PROFILE Issues in Teachers' Professional Development",
     "Psychotherapy",
-    "Social Service Department, Presbyterian Hospital, New York",
-    "Social Work Technique", 
-    "Social Work Today", 
-    "Social Work Yearbook", 
-    "The New Social Worker",
     "Systems Research and Behavioral Science",
     "Teaching and Teacher Education",
-    "University of Chicago Social Service Monograph",
     "The Scientific Review of Mental Health Practice",
-    "The Clinical Supervisor",
-    "University of Chicago Social Service Monograph")
+    "The Clinical Supervisor")
 
@@
 
-A second round of exclusions were made.
+## Exclusions of social work publications
 
-Journals with less than 10 articles that contributed to the overall number.
-Ten was selected because it was a natural break consisten with a EFA curve...In this cases the exclusion of the titles had virtually no impact on the overall article count.
-However, it did inflate the number of journal titles.
-Excluded if we could not identify the journal and associated articles -- that is, it wasn't available and, therefore, not part of the scholarly record.
+Exclusions were then made any of the three criteria
 
-+ _Social Work Process_ was retained because it was a verified journal from U Penn
++ Journals that did not have clear evidence of a peer review process.  This was based on a review of the journals mission, scope, and whether an editorial board or group could be identified.
+
++ Journal titles that did not have any clear publication history (e.g., due to an indexing error).  This exclusion was based on errors in data entry.
+
++ Journals that did not have at least one full year of indexed records (except journals that subsequently changed titles).
+This exclusionary criterion was consistent with the working definition of a social work journal.
 
@@
     "Pennsylvania Social Work",
-    "Social Service",    
+    "Proceedings of the National Conference of Social Work","Social Service",    
     "Social Service Department, Presbyterian Hospital, New York",
     "Social Service Monographs",
-    "School Social Work Quarterly", # Published only one edition
+    "School Social Work Quarterly", 
     "Social Work Today",
     "Social Work Technique",
-    "Social Work Today", # Magazine
+    "Social Work Today", 
     "Social Work Yearbook",
@@
     "Pennsylvania Social Work",
-    "University of Chicago Social Service Monograph" # Single record
+    "University of Chicago Social Service Monograph" 
     )
@@
 
-Journal titles were merged in the following situations:
+## Title merging
+
+Some social work journals changed titles over their history.
+For example, _Families in Society_ had three titles that preceded the current title:  _Social Casework_, _Journal of Social Casework_, and _The Family_.
+The database that contributed the largest number of articles to the study database indexed the majority of journal titles under the journal's current name, and provided an additional data field for the historical name.
+However, historical names from Social Science Abstracts and Social Work Abstracts were not merged with the current name.
+Thus, the last step of the data cleaning procedures was to conduct these merges.
 
@@
 full.df$record <- ifelse(full.df$record == 
-        "Social Work & Social Sciences Review",     # Spelling difference
-        "Social Work and Social Sciences Review", 
-                        full.df$record)
-
-full.df$record <- ifelse(full.df$record == 
-        "Social Work with Groups",                  # Spelling difference
-        "Social Work With Groups", 
-                        full.df$record)
-
-full.df$record <- ifelse(full.df$record == 
         "Computers in Human Services",              # Old title
         "Journal of Technology in Human Services",  # New title
-                        full.df$record)
-
-full.df$record <- ifelse(full.df$record == 
-        "Journal of Sociology & Social Welfare",    # Spelling difference
-        "Journal of Sociology and Social Welfare",  
                         full.df$record)
@@
                     full.df$record)
+
+full.df$record <- ifelse(full.df$record == "Journal of Independent Social Work" | full.df$record == "Journal of Analytic Social Work", "Psychoanalytic Social Work", 
+                full.df$record)
 ```
@@
 hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
-hodge2 <- gsub("(SO)", "", hodge)
-hodge3 <- gsub("(OR)", "", hodge2)
-hodge4 <- gsub("[[:punct:]]", "", hodge3)
-hodge5 <- str_trim(hodge4, side="both")
+
+unique.titles <- filter(full.df, attributes == "journal") %>%
+    group_by(record) %>%
+    summarise(
+        N = n())
+print.data.frame(unique.titles, rowNames=FALSE)
 
@@
     group_by(record) %>%
-    summarise(
-        N = n())
-print.data.frame(unique.titles, rowNames=FALSE)
+    summarise(N = n())
+
+hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
+
+unique.titles <- filter(full.df, attributes == "journal") %>%
+    group_by(record) %>%
+    mutate(Hodge.list = ifelse(record %in% hodge == TRUE, 1, 0)) %>%
+    summarise(N = n(), 
+              Hodge.list = max(Hodge.list)) %>%
+    mutate(Hodge = ifelse(Hodge.list == 1, "Y", "N"))
+
+n.so.yr <- filter(full.df, attributes == "journal" | attributes == "pubYear")
+
+n.so <- filter(full.df, attributes == "journal") %>% mutate(title = record) %>% 
+        select(-attributes, -record)
+
+n.yr <- filter(full.df, attributes == "pubYear") %>% mutate(year = record ) %>% 
+        select(-attributes, -record)
+
+n.so.yr <- left_join(n.so, n.yr) %>%
+    group_by(title) %>%
+    summarise(first = min(year), last = max(year), n = n()) %>%
+    arrange(title)
+
+H <- unique.titles$Hodge
+
+final.list <- cbind(n.so.yr, H)
+
+print.data.frame(final.list, row.names=FALSE)
+
 ```

### 2015-02-05 dataCleaning.Rmd
Major cleaning.

@@
 author: "Summary of Data Cleaning Procedures"
-output: html_document
+output: pdf_document
 ---
@@
     "Journal of Applied Rehabilitation Counseling",
-    "Journal of Applied Social Sciences",
     "Journal of Community & Applied Social Psychology",
@@
     "Social Work Yearbook",
-    "The New Social Worker",
     "Pennsylvania Social Work",
@@
 full.df$record <- ifelse(full.df$record == 
-        "The British Journal of Social Work",       # Old title
+        "The British Journal of Pyschiatric Social Work",       # Old title
         "British Journal of Social Work",           # New title
@@
                 full.df$record)
+
+# Journals were originally merged after suffixes were eliminated (after the colon).
+Thus, Practice: Social Work in Action  (new title) was shortened to Practice (old title).
+This section resolves two of these issues to be consistent in the comparison with Hodge.
+
+practice.temp <- grep("^Practice$", full.df$record)
+full.df$record[practice.temp] <- "Practice: Social Work in Action"
+
+practice.temp <- grep("^Reflections$", full.df$record)
+full.df$record[practice.temp] <- "Reflections: Narratives of Professional Helping"
 ```
@@
 print.data.frame(final.list, row.names=FALSE)
-
 ```
 
-```{r comment=NA, echo=FALSE} 
-number.of.articles <- length(which(full.df$attributes == "article"))
-range.of.years <- range(full.df$record[full.df$attributes == "pubYear"])
+## Intersection, Differences and Union
+
+This section examines the overall _coverage_ of the current search by making systematic comparisons with Hodge (2013).
+The first analysis shows how the list of SWH overlaps with HL -- that is, the journals that were common to both lists (_intersection_).
+The sedond analyses shows the set _differences_.
+The third analysis focuses on the union of the sets.
+The union shows a meta-list by
+```{r}
+
+hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
+
+unique.swHistory <- filter(full.df, attributes == "journal") %>%
+                distinct(record)
+
+hodge.swHistory.intersect <- intersect(hodge, unique.swHistory$record)
+
+hodge.swHistory.diff <- setdiff(hodge, unique.swHistory$record)
+swHistory.hodge.diff <- setdiff(unique.swHistory$record, hodge)
+
+hodge.swHistory.union <- union(hodge, unique.swHistory$record)
+
+print(sort(hodge.swHistory.intersect))
+print(sort(hodge.swHistory.diff))
+print(sort(swHistory.hodge.diff))
+print(sort(hodge.swHistory.union))
+
 ```
@@
 ```
+
+Reflections: Narratives of Professional Helping

### 2015-02-11 dataCleaning.Rmd
General update.

@@
 ---
-title: "History of Social Work Research"
+title: "25 years of Social Work Research"
 author: "Summary of Data Cleaning Procedures"
@@
                         full.df$record)
+
+full.df$record <- ifelse(full.df$record == 
+    "The British Journal Social Work",          # Spelling difference
+        "British Journal of Social Work",           
+                        full.df$record)
 ```
@@
 ```{r}
+
+year.25 <- as.character(c(1900:1987, 2014, 2015))
 years <- c("2014", "2015")
-ebsco.remove <- full.df[full.df$record %in% years, ]
+#ebsco.remove <- full.df[full.df$record %in% years, ]
+ebsco.remove <- full.df[full.df$record %in% year.25, ]
 ebsco.remove <- ebsco.remove[, "articleID"]
@@
 
-+ Journal titles that did not have any clear publication history (e.g., due to an indexing error).  This exclusion was based on errors in data entry.
++ Journal titles that did not have any clear publication history based on a broad-based Internet search and other databases (e.g., ProQuest).
+These exclusions are assumed to be data entry problems at time of indexing.
 
@@
     "International Conference of Social Work",
-    "Journal of Multicultural Social Work",
     "Journal of Social Work Process",
-    "Journal of Teaching in Social Work", 
     "Maatskaplike Werk/Social Work",
@@
 full.df$record <- ifelse(full.df$record == 
-        "The British Journal of Pyschiatric Social Work",       # Old title
+    "The British Journal of Pyschiatric Social Work", # Old
         "British Journal of Social Work",           # New title
@@
 
-full.df$record <- ifelse(full.df$record == "Journal of Independent Social Work" | full.df$record == "Journal of Analytic Social Work", "Psychoanalytic Social Work", 
+full.df$record <- ifelse(full.df$record == 
+        "Journal of Independent Social Work" | full.df$record ==    # New title
+        "Journal of Analytic Social Work",                          # Old title
+        "Psychoanalytic Social Work",                               # Old title
                 full.df$record)
 
-# Journals were originally merged after suffixes were eliminated (after the colon).
-Thus, Practice: Social Work in Action  (new title) was shortened to Practice (old title).
-This section resolves two of these issues to be consistent in the comparison with Hodge.
+# Journals were originally merged after suffixes were eliminated (after the
+# colon).  Thus, Practice: Social Work in Action  (new title) was shortened to
+# Practice (old title).  This section resolves two of these issues to be
+# consistent in the comparison with Hodge.
 
@@
 
-# Coverage via Hodge article
-
-```{r hodgeCompare, eval=FALSE}
-hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
-
-unique.titles <- filter(full.df, attributes == "journal") %>%
-    group_by(record) %>%
-    summarise(
-        N = n())
-print.data.frame(unique.titles, rowNames=FALSE)
-
-```
-
 # Post-processing summary
 
-+ to do ... summary with hodge list
+## Revised database
+
+This section provides a summary of the revised database after the initial processing with the `ebscoBWR` function and the subsequent data cleaning.
+An additional code is included in this summary to indicate whether the journal title overlaps with the list of Hodge (indicated by *H*).
 
@@
 
-This section examines the overall _coverage_ of the current search by making systematic comparisons with Hodge (2013).
-The first analysis shows how the list of SWH overlaps with HL -- that is, the journals that were common to both lists (_intersection_).
-The sedond analyses shows the set _differences_.
-The third analysis focuses on the union of the sets.
-The union shows a meta-list by
+This section provides further comparison of the journal titles with Hodge by reporting on the _intersection_, _differences_, and _union_ of the lists.
 ```{r}
-
 hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
@@
 hodge.swHistory.union <- union(hodge, unique.swHistory$record)
+```
 
+This list shows which journal titles are common to both lists.
+
+```{r}
 print(sort(hodge.swHistory.intersect))
+```
+
+This list shows the articles on Hodge but not the current study.
+
+```{r}
+sink(file = "JournalsMissed.txt")
 print(sort(hodge.swHistory.diff))
+sink()
+```
+This list shows the articles on the current study but not on Hodge.
+
+```{r}
 print(sort(swHistory.hodge.diff))
+```
+
+This list shows the union of lists -- that is, a full list of all titles by combining a list.
+It would be useful to break out the former titles of journals, as well as the years of existence.
+This would establish a complete listing of all social work journals, both current and historical.
+
+```{r}
 print(sort(hodge.swHistory.union))
+```
 
+## Descriptive summary of records
+
+```{r comment=NA, echo=TRUE} 
+number.of.articles <- length(which(full.df$attributes == "article"))
+range.of.years <- range(full.df$record[full.df$attributes == "pubYear"])
 ```
@@
 
-Reflections: Narratives of Professional Helping
+```{r}
+cor.data <- select(final.list, first, last, n) %>%
+            mutate(no.years = as.numeric(last) - as.numeric(first))
+
+ggplot(cor.data, aes(x = no.years, y = n)) + 
+            geom_point(shape = 1) + 
+            geom_smooth() + 
+            xlab("Years") + 
+            ylab("Number of articles")
+
+cor(cor.data$no.years, cor.data$n)
+```

### 2015-02-21 dataCleaning.Rmd
Updated files.

@@
 # Read data files
-#load("/Users/beperron/Git/SocialWorkResearch/Data/psycInfoDF.R")
-load("/Users/beperron/Git/SocialWorkResearch/Data/fullDF.R")
+
+load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
+load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
+load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoPsycInfo.R")
+```
+
+Everything written after this point was for the ebsco full data file (psycinof, swa, ssa).
+The R objects have been all re-written and renamed.
+The first thing to do is to append the ebscoFULL and proQuest objects.
+Here is my recommended steps:
+
+1.  Create a variable that takes the maximum values of the articleID from ebscoFULL
+2.  Add the max value to the article ID of proQuest
+3.
+Write a function that matches the titles of ebscoFull with proQuest, grabs the ID, and then, eliminates the duplicates.
+We have all the matching code in the original functions that you can grab.
+4.
+Consider drawing on the pmatch.R function in the BWR folder.
+This function forces all to lower, strips all the white space, and takes a subset of the characters (e.g., ~25 I think).
+The advantage of this is to avoid the incorrect matching when colons are used.
+Same title, but you get the idea of where things can go awry with title matching.
+Test it extensively -- e.g., alphebatizing is also helpful.
+
+Social work research can be really:  Bad
+Social work research can be really: Bad
+Social Work research can be really: bad
+Social work research can be really: Bad
+Social work research can be really: bad
+
+Social Work research can be really:  bad
 
 # Set the working directory
-setwd("/Users/beperron/Git/SocialWorkResearch/Data")
-
-# Strip leading and trailing white-space on all records
-full.df$record <- stringr::str_trim(full.df$record, side = "both")
+#setwd("/Users/beperron/Git/SocialWorkResearch/Data")
 ```

### 2015-02-21 dataCleaning.Rmd
Updated instructions.

@@
 Social work research can be really: bad
+Social Work research can be really:  bad
 
-Social Work research can be really:  bad
+5.  Do necessary search and replace of subsequent code to get it working with the fully appended data file.
 

### 2015-02-21 dataCleaning.Rmd
Added code to toggle between directories for our computers

@@
 load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoPsycInfo.R")
+
+#load("/Users/SSW/GitHub/SocialWork100Years/Data/ebscoFULL.R")
+#load("/Users/SSW/GitHub/SocialWork100Years/Data/proQuest.R")
+#load("/Users/SSW/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")
+
 ```
@@
 #setwd("/Users/beperron/Git/SocialWorkResearch/Data")
+#setwd("/Users/SSW/GitHub/SocialWork100Years/Data")
 ```

### 2015-02-22 dataCleaning.Rmd
Code to merge Ebsco and PQ, remove duplicate records

--- 2015-02-21 dataCleaning.Rmd
@@
 
-load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
-load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
-load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoPsycInfo.R")
+#load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
+#load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
+#load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoPsycInfo.R")
+
+load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
+load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
+load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")
+
 ```
@@
 
+#Combines EbscoHost and ProQUest wrangles and eliminates duplicate article titles
+
+```{r}
+
+library(dplyr)
+
+  #Creates variable with highest article ID from ebscohost database
+  EbscoIDmax<-max(ebscoBWR.df$articleID)
+
+  #Recodes article ID in ProQuest database in advance of merger with ebscohost
+  proQuestBWR.df<-mutate(proQuestBWR.df, articleID=articleID+EbscoIDmax)
+
+  #Creates data frames that contain only article ID and titles from respective
+  #databases
+  EbscoTitles<-filter(ebscoBWR.df, attributes=="article")
+  ProTitles<-filter(proQuestBWR.df, attributes=="article")
+
+  #Combines titles into single data frame
+  JointTitles<-rbind(EbscoTitles, ProTitles)
+
+  #Forces article title text to lower case
+  JointTitles$record<-tolower(JointTitles$record)
+
+  #Strips out white space and punctuation to ensure small differences
+  #in data entry are detected during duplicate elimination
+  JointTitles$record<-gsub(" ","", JointTitles$record)
+  punct <- '[]\\?!\"\'#$%&(){}+*/:;,._`|~\\[<=>@\\^-]'
+  JointTitles$record<-gsub(punct, "", JointTitles$record)
+
+  JointTitles <- JointTitles[duplicated(JointTitles$record), ]
+
+  #Screen out duplicated records by articleID. The articleID must be used
+  #because the duplicate title contains other article attributes
+  JointTitles.dup.ID <- JointTitles$articleID
+
+  #Combines EbscoHost and ProQuest Wrangles, and strips out article attributes 
+  #from duplicate entries
+  Combined.DF<-rbind(ebscoBWR.df, proQuestBWR.df)
+  Combined.DF<-Combined.DF[!(Combined.DF$articleID %in% JointTitles.dup.ID), ]
+
+```
+
 # Set the working directory
 #setwd("/Users/beperron/Git/SocialWorkResearch/Data")
+#setwd("/Users/SSW/Documents/GitHub/SocialWork100Years/Data")
 ```

### 2015-02-22 dataCleaning.Rmd
Minor code cleanup.

--- 2015-02-21 dataCleaning.Rmd
@@
 
-#load("/Users/SSW/GitHub/SocialWork100Years/Data/ebscoFULL.R")
-#load("/Users/SSW/GitHub/SocialWork100Years/Data/proQuest.R")
-#load("/Users/SSW/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")
+#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
+#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
+#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")
 
@@
 
+#Combines EbscoHost and ProQUest wrangles and eliminates duplicate article titles
+
+```{r}
+
+library(dplyr)
+
+  #Creates variable with highest article ID from ebscohost database
+  ebscoIDmax<-max(ebscoBWR.df$articleID)
+
+  #Recodes article ID in ProQuest database in advance of merger with ebscohost
+  proQuestBWR.df<-mutate(proQuestBWR.df, articleID=articleID+ebscoIDmax)
+
+  #Creates data frames that contain only article ID and titles from respective
+  #databases
+  ebscoTitles<-filter(ebscoBWR.df, attributes=="article")
+  proTitles<-filter(proQuestBWR.df, attributes=="article")
+
+  #Combines titles into single data frame
+  jointTitles<-rbind(ebscoTitles, proTitles)
+
+  #Forces article title text to lower case
+  jointTitles$record<-tolower(jointTitles$record)
+
+  #Strips out white space and punctuation to ensure small differences
+  #in data entry are detected during duplicate elimination
+  jointTitles$record<-gsub(" ","", jointTitles$record)
+
+  #punct <- '[]\\?!\"\'#$%&(){}+*/:;,._`|~\\[<=>@\\^-]'
+  #JointTitles$record<-gsub(punct, "", JointTitles$record)  
+  jointTitles$record<-gsub("[[:punct:]]", "", jointTitles$record)
+
+  jointTitles<- jointTitles[duplicated(jointTitles$record), ]
+
+  #Screen out duplicated records by articleID. The articleID must be used
+  #because the duplicate title contains other article attributes
+  jointTitles.dup.ID <- jointTitles$articleID
+
+  #Combines EbscoHost and ProQuest Wrangles, and strips out article attributes 
+  #from duplicate entries
+  combined.DF<-rbind(ebscoBWR.df, proQuestBWR.df)
+  combined.DF<-combined.DF[!(combined.DF$articleID %in% jointTitles.dup.ID), ]
+
+```
+
 # Set the working directory
 #setwd("/Users/beperron/Git/SocialWorkResearch/Data")
-#setwd("/Users/SSW/GitHub/SocialWork100Years/Data")
+#setwd("/Users/SSW/Documents/GitHub/SocialWork100Years/Data")
 ```

### 2015-02-22 dataCleaning.Rmd
Cleanup of document.

@@
 
-Everything written after this point was for the ebsco full data file (psycinof, swa, ssa).
-The R objects have been all re-written and renamed.
-The first thing to do is to append the ebscoFULL and proQuest objects.
-Here is my recommended steps:
+# Combines EbscoHost and ProQUest
 
-1.  Create a variable that takes the maximum values of the articleID from ebscoFULL
-2.  Add the max value to the article ID of proQuest
-3.
-Write a function that matches the titles of ebscoFull with proQuest, grabs the ID, and then, eliminates the duplicates.
-We have all the matching code in the original functions that you can grab.
-4.
-Consider drawing on the pmatch.R function in the BWR folder.
-This function forces all to lower, strips all the white space, and takes a subset of the characters (e.g., ~25 I think).
-The advantage of this is to avoid the incorrect matching when colons are used.
-Same title, but you get the idea of where things can go awry with title matching.
-Test it extensively -- e.g., alphebatizing is also helpful.
+This section ... wrangles and eliminates duplicate article titles
 
-Social work research can be really:  Bad
-Social work research can be really: Bad
-Social Work research can be really: bad
-Social work research can be really: Bad
-Social work research can be really: bad
-Social Work research can be really:  bad
-
-5.  Do necessary search and replace of subsequent code to get it working with the fully appended data file.
-
-#Combines EbscoHost and ProQUest wrangles and eliminates duplicate article titles
-
-```{r}
-
-library(dplyr)
+```{r appendData, comment=NA}
 
@@
 
-  #Strips out white space and punctuation to ensure small differences
-  #in data entry are detected during duplicate elimination
+#Strips out white space and punctuation to ensure small differences in data 
+#entry are detected during duplicate elimination
 jointTitles$record<-gsub(" ","", jointTitles$record)
 
-  #punct <- '[]\\?!\"\'#$%&(){}+*/:;,._`|~\\[<=>@\\^-]'
-  #JointTitles$record<-gsub(punct, "", JointTitles$record)  
 jointTitles$record<-gsub("[[:punct:]]", "", jointTitles$record)
@@
 combined.DF<-rbind(ebscoBWR.df, proQuestBWR.df)
-  combined.DF<-combined.DF[!(combined.DF$articleID %in% jointTitles.dup.ID), ]
+full.df<-combined.DF[!(combined.DF$articleID %in% jointTitles.dup.ID), ]
+
+rm(list=setdiff(ls(), "full.df"))
 
@@
 
-# Set the working directory
-#setwd("/Users/beperron/Git/SocialWorkResearch/Data")
-#setwd("/Users/SSW/Documents/GitHub/SocialWork100Years/Data")
+# Data cleaning and pre-processing
+
+## Narrow results to past 25 years
+
+Inspection of the data indicated notable delays in indexing for the years 2014 and 2015.
+Therefore, these years were excluded from the current study.
+Thus, this study includes journals indexed through the end of 2013.
+
+```{r}
+
+year.25 <- as.character(c(1900:1987, 2014, 2015))
+years <- c("2014", "2015")
+#ebsco.remove <- full.df[full.df$record %in% years, ]
+ebsco.remove <- full.df[full.df$record %in% year.25, ]
+ebsco.remove <- ebsco.remove[, "articleID"]
+full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
 ```
 
-# Pre-processing summary
-```{r echo=FALSE}
-full.df$record <- ifelse(full.df$record == 
-        "Social Work & Social Sciences Review",     # Spelling difference
-        "Social Work and Social Sciences Review", 
-                        full.df$record)
-
-full.df$record <- ifelse(full.df$record == 
-        "Social Work with Groups",                  # Spelling difference
-        "Social Work With Groups", 
-                        full.df$record)
-
-full.df$record <- ifelse(full.df$record == 
-        "Journal of Sociology & Social Welfare",    # Spelling difference
-        "Journal of Sociology and Social Welfare",  
-                        full.df$record)
-
-full.df$record <- ifelse(full.df$record == 
-    "The British Journal Social Work",          # Spelling difference
-        "British Journal of Social Work",           
-                        full.df$record)
-```
-
-Provided below is a summary of the datafile processed by `ebscoBWR` function before any cleaning procedures specifically for this project were employed, with the exception of resolving spelling errors or differences.
-For example, _Social Work With Groups_ was exported as a separate journal than _Social Work with Groups_ (note the capitalization difference in the word _with_.)
+## Initial descriptive summary
 
@@
 cat(range.of.years)
-```
-
-```{r date, echo=FALSE, comment=NA}
-unique.titles <- filter(full.df, attributes == "journal") %>%
-    group_by(record) %>%
-    summarise(
-        N = n())
-print.data.frame(unique.titles, rowNames=FALSE)
-```
-
-# Data cleaning
-
-Inspection of the data indicated notable delays in indexing for the years 2014 and 2015.
-Therefore, these years were excluded from the current study.
-Thus, this study includes journals indexed through the end of 2013.
-
-## Year specification
-
-```{r}
-
-year.25 <- as.character(c(1900:1987, 2014, 2015))
-years <- c("2014", "2015")
-#ebsco.remove <- full.df[full.df$record %in% years, ]
-ebsco.remove <- full.df[full.df$record %in% year.25, ]
-ebsco.remove <- ebsco.remove[, "articleID"]
-full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
 ```
@@
     "Learning Disabilities Research & Practice",
+    "Professional Development in Education",
     "PROFILE Issues in Teachers' Professional Development",
@@
 
-Exclusions were then made any of the three criteria
-
-+ Journals that did not have clear evidence of a peer review process.  This was based on a review of the journals mission, scope, and whether an editorial board or group could be identified.
-
-+ Journal titles that did not have any clear publication history based on a broad-based Internet search and other databases (e.g., ProQuest).
-These exclusions are assumed to be data entry problems at time of indexing.
-
 + Journals that did not have at least one full year of indexed records (except journals that subsequently changed titles).
@@
 exclusions.2 <- c(
-    "Eugenics and Social Welfare Bulletin",
-    "Eugenics & Social Welfare Bull.",
     "Issues in Social Work Education", 
-    "Hospital Social Service",  #Confirmed nursing journal
-    "International Conference of Social Work",
-    "Journal of Social Work Process",
     "Maatskaplike Werk/Social Work",
-    "Medical Social Work",
-    "New York State Department of Social Welfare, Division Publication",
     "Pediatric Social Work", 
-    "Pennsylvania Social Work",
-    "Proceedings of the National Conference of Social Work","Social Service",    
-    "Social Service Department, Presbyterian Hospital, New York",
-    "Social Service Monographs",
-    "School Social Work Quarterly", 
-    "Social Work Today",
-    "Social Work Technique",
-    "Social Work Today", 
-    "Social Work Yearbook",
-    "Pennsylvania Social Work",
-    "University of Chicago Social Service Monograph" 
+    "Critical Social Work"
     )
@@
 rm(ebsco.remove, exclusions.2)
+```
+
+## Fix journal titles
+
+Additional pre-processing was conducted on journal titles to resolve spelling errors or other minor title differences in the database.
+For example, _Social Work With Groups_ was exported as a separate journal than _Social Work with Groups_ (note the capitalization difference in the word _with_.)  We also applied a global substitution of _and_ with _&_, as this was a common source for differences.
+
+```{r echo=FALSE}
+full.df$record <- ifelse(full.df$record == 
+        "Social Work & Social Sciences Review",     # Spelling difference
+        "Social Work and Social Sciences Review", 
+                        full.df$record)
+
+full.df$record <- ifelse(full.df$record == 
+        "Social Work with Groups",                  # Spelling difference
+        "Social Work With Groups", 
+                        full.df$record)
+
+full.df$record <- ifelse(full.df$record == 
+        "Journal of Sociology & Social Welfare",    # Spelling difference
+        "Journal of Sociology and Social Welfare",  
+                        full.df$record)
+
+full.df$record <- ifelse(full.df$record == 
+    "The British Journal Social Work",          # Spelling difference
+        "British Journal of Social Work",           
+                        full.df$record)
+
+#shortens Professional Development
+full.df$record <- ifelse(full.df$attributes == "journal",
+        gsub(":.+", "", full.df$record), 
+        full.df$record)
+
+#shortens Canadian Social Work review by eliminating foreign title and is
+#automatically combined with other short spelling
+full.df$record <- ifelse(full.df$attributes == "journal",
+        gsub("(/R){1}.+", "", full.df$record), 
+        full.df$record)
+
+# shortens Contemporary Rural Social Work
+full.df$record <- ifelse(full.df$attributes == "journal",
+        gsub("\\s\\(.+", "", full.df$record), 
+        full.df$record)
+
+full.df$record <- ifelse(full.df$attributes == "journal", 
+      gsub("and", "&", full.df$record), full.df$record)
+
+```
+
+```{r date, echo=FALSE, comment=NA}
+unique.titles <- filter(full.df, attributes == "journal") %>%
+    group_by(record) %>%
+    summarise(
+        N = n())
+print.data.frame(unique.titles, rowNames=FALSE)
 ```
@@
 full.df$record <- ifelse(full.df$record == 
-    "The British Journal of Pyschiatric Social Work", # Old
+    "The British Journal of Pyschiatric Social Work" | 
+        full.df$record == 
+    "The British Journal of Social Work", # Old
         "British Journal of Social Work",           # New title
@@
 
-## Intersection, Differences and Union
+# Comparison with Hodge
 
-This section provides further comparison of the journal titles with Hodge by reporting on the _intersection_, _differences_, and _union_ of the lists.
+This section provides further comparison of the journal titles with Hodge by reporting on the _intersection_, and _differences_.
+
+## Intersection
+
+This list shows which journal titles are common to both lists.
+
 ```{r}
@@
 
-hodge.swHistory.union <- union(hodge, unique.swHistory$record)
+#hodge.swHistory.union <- union(hodge, unique.swHistory$record)
 ```
-
-This list shows which journal titles are common to both lists.
 
@@
 
+## Differences
+
 This list shows the articles on Hodge but not the current study.
@@
 ```{r}
-sink(file = "JournalsMissed.txt")
 print(sort(hodge.swHistory.diff))
-sink()
 ```
@@
 print(sort(swHistory.hodge.diff))
-```
-
-This list shows the union of lists -- that is, a full list of all titles by combining a list.
-It would be useful to break out the former titles of journals, as well as the years of existence.
-This would establish a complete listing of all social work journals, both current and historical.
-
-```{r}
-print(sort(hodge.swHistory.union))
 ```

### 2015-02-22 dataCleaning.Rmd
Code for Arete journal titles

--- 2015-02-22 dataCleaning.Rmd
@@
 
-load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
-load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
-load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoPsycInfo.R")
+#load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
+#load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
+#load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoPsycInfo.R")
 
-#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
-#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
-#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")
+load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
+load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
+load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")
 
@@
                         full.df$record)
+
+full.df$record <- ifelse(full.df$record ==
+    "Aretê",                                   #Spelling difference
+      "Arete",
+              full.df$record)
 ```
@@
     "The Scientific Review of Mental Health Practice",
-    "The Clinical Supervisor")
+    "The Clinical Supervisor",
+    "Arete: Revista de Filosofia")
 

### 2015-02-22 dataCleaning.Rmd
Journal title corrections

@@
       "Arete",
+              full.df$record)
+
+full.df$record <- ifelse(full.df$record ==
+    "Journal of Gay and Lesbian Social Services",     #Spelling difference
+        "Journal of Gay & Lesbian Social Services",
+                        full.df$record)
+
+full.df$record <- ifelse(full.df$record ==
+    "Canadian Social Work Review/Revue canadienne de service social",
+        "Canadian Social Work Review",
                         full.df$record)

### 2015-02-23 dataCleaning.Rmd
Code clean up.

@@
 full.df$record <- ifelse(full.df$record ==
-    "Aretê",                                   #Spelling difference
+    "Aretê^",                                   #Spelling difference
       "Arete",
@@
                         full.df$record)
+
+full.df$record <- ifelse(full.df$record ==
+    "INDIAN JOURNAL OF SOCIAL WORK",
+        "Indian Journal of Social Work",
+                      full.df$record)
+
+full.df$record <- ifelse(full.df$record ==
+    "The Indian Journal of Social Work",
+        "Indian Journal of Social Work",
+                            full.df$record)
+
 ```

### 2015-02-24 dataCleaning.Rmd
Code correction for Arete
Code clean up on journal titles in pre-processing

@@
   combined.DF<-rbind(ebscoBWR.df, proQuestBWR.df)
-  combined.DF<-combined.DF[!(combined.DF$articleID %in% jointTitles.dup.ID), ]
+  full.df<-combined.DF[!(combined.DF$articleID %in% jointTitles.dup.ID), ]
 
@@
 full.df$record <- ifelse(full.df$record == 
-    "The British Journal Social Work",          # Spelling difference
+    "The British Journal of Social Work",          # Spelling difference
         "British Journal of Social Work",           
@@
 full.df$record <- ifelse(full.df$record ==
-    "Aretê^",                                   #Spelling difference
-      "Arete",
+    "Revista de Asistenta Sociala (Social Work Review)",
+        "Social Work Review",
                         full.df$record)
+
+full.df$record <- gsub("Arete", "xxx", full.df$record)
+full.df$record <- gsub("Aret.{1,3}", "Arete", full.df$record)
+full.df$record <- gsub("xxx", "Arete", full.df$record) 
+                                      #Replaces special character       
+                                      #in Arete and preserves other formatting
 
@@
 full.df$record <- ifelse(full.df$record ==
-    "INDIAN JOURNAL OF SOCIAL WORK",
+    "INDIAN JOURNAL OF SOCIAL WORK",                    #Spelling difference
         "Indian Journal of Social Work",
@@
 full.df$record <- ifelse(full.df$record ==
-    "The Indian Journal of Social Work",
+    "The Indian Journal of Social Work",              #Spelling difference
         "Indian Journal of Social Work",
                             full.df$record)
+
+full.df$record <- ifelse(full.df$record ==
+    "Asia Pacific Journal of Social Work",              #Spelling difference
+        "Asia Pacific Journal of Social Work and Development",
+                            full.df$record)
+
+full.df$record <- ifelse(full.df$record ==
+    "Social Work & Society",                           #Spelling difference
+        "Social Work and Society",
+                            full.df$record)
+
+full.df$record <- ifelse(full.df$record ==
+    "Journal of Social Work in Disability & Rehabilitation",
+        "Journal of Social Work in Disability and Rehabilitation", 
+                            full.df$record)           #Spelling difference
+
+full.df$record <- ifelse(full.df$record ==
+    "Hong Kong Journal of Social Work",
+        "The Hong Kong Journal of Social Work", 
+                            full.df$record)           #Spelling difference
+
+full.df$record <- ifelse(full.df$record ==
+    "The Journal of Baccalaureate Social Work",
+        "Journal of Baccalaureate Social Work", 
+                            full.df$record)           #Spelling difference
+
+full.df$record <- ifelse(full.df$record ==
+    "Journal of Practice Teaching in Health and Social Work",
+        "Journal of Practice Teaching in Social Work and Health", 
+                            full.df$record)           #Spelling difference
+
+full.df$record <- ifelse(full.df$record ==
+    "Professional Development: The International Journal of Continuing Social Work Education",
+        "Professional Development", 
+                            full.df$record)           #Spelling difference
 
@@
     "The Clinical Supervisor",
-    "Arete: Revista de Filosofia")
+    "Arete: Revista de Filosofia",
+    "Arete Revista de Filosofia")
 
@@
         "Psychoanalytic Social Work",                               # Old title
+                full.df$record)
+
+full.df$record <- ifelse(full.df$record ==
+        "Journal of Practice Teaching in Social Work and Practice", #Old title
+        "Journal of Practice Teaching in Social Work and Health",   #New title
                     full.df$record)

### 2015-02-25 Analysis.Rmd
Fixed analysis.

@@
 ---
-title: 'The History of Social Work Research: A Data Science Perspective'
+title: "Object Maker"
 output: pdf_document
@@
 
-# Data harvesting
+# Ebsco Full
 
-Data collection for this study was separated into three phases.
-
-## Search Query
-
-The first phases involved querying three different databases serviced by the EbscoHost web platform: psycInfo, Social Science Abstract, and Social Work Abstracts.
-These databases were selected because they provide the indexing services for the majority of social work journals.
-Additionally, search queries from these databases, served by EbscoHost, allowed search results to be exported raw text (*.txt) documents, referred to as a _generic bibliographic format_.
-Other databases and search engines (e.g., Google Scholar) were not queried because the results could not be saved in a common format.
-This is a limitation of the study that is covered in the discussion section.
-
-The search began by querying each database for every _journal article_ from every journal that was included in the list by Hodge and ...
-[Describe this list] ...
-Each query was performed independently on each database,
-
-We had a three-level search process designed to be as comprehensive as possible.
-First, we began by running a separate search query on each database for every journal contained in the list by Hodge.
-We then conducted a subsequent search of all journal titles based on the following key words:
-
-+ social work
-+ social welfare
-+ social casework 
-+ social case work
-+ social service
-+ human service
-+ social development 
-+ social environment
-
-In each query, results were limited to only journal articles, which excluded other document types including (but not limited to) editorials, book reviews, software reviews, and obituaries.
-All searches were conducted between January 24, 2015 and January 30, 2015.
-Results were subsequently filtered to exlclude years 2014 and 2015 due to delays in indexing.
-Search results were exported from EbscoHost platfrom into a _generic bibliographic format_.
-This is an unstructured text file (*.txt) that was processed using in R.
-The multiple searches were then transformed into an analyzable database using a customized script developed by the first two authors of the study (BEP and BGV).
-
-Study authors reviewed all journal titles and
-
-# Data Pre-Processing
-
-# NOTE: CONFIRM THAT SOCIAL CASEWORK IS SAME AS FAMILIES IN SOCIETY.  ENSURE WE 
-# HAVE THE ARTICLES FOR WHEN THE JOURNAL WAS ALSO CALLED THE FAMILY
-
-```{r initialization_dataprocessing, warning=FALSE, message=FALSE, eval=FALSE}
+```{r warning=FALSE, message=FALSE, eval=TRUE}
 # Clear workspace
@@
 # Set the working directory to store files created by BWR functions
-path <- "/Users/beperron/Git/SocialWorkResearch/Data"
+path <- "/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL"
 
 # Wrangle the data with the BWR function suite
-ebscoBWR.f(csv=FALSE, path=path, psycInfoOnly = FALSE)
-save(bwr.df, file = "fullDF.R")
+
+ebscoBWR.f(csv=FALSE, path=path, psycInfoOnly=FALSE)
+save(ebscoBWR.df, file = "ebscoFULL.R")
 ```
 
-#add no authorship indicated
-#Anonymous
-x.temp <- filter(bwr.df, attributes == "article")
-x.temp2 <- filter(bwr.df, attributes == "journal")
+# PsychInfo Only
 
-x.temp3 <- filter(bwr.df, attributes == "author")
-b <- grepl("@", x.temp3$record)
+```{r warning=FALSE, message=FALSE, eval=TRUE}
+# Clear workspace
+rm(list=ls())
 
-test.case <- filter(bwr.df, attributes == "AU")
-auth.name <- filter(test.case, grepl("(Perron,\\sB)", record))
+# Read BWR functions for Mac OS
+source("/Users/beperron/Git/BibWrangleR/functions/ebscoBWR.R")
 
-x.temp <- filter(bwr.df, attributes == "KW" | attributes == "KP")
+# Set the path where original raw data are stored
+setwd("/Users/beperron/Git/SocialWorkResearch/Data")
 
-```{r initialization_analysis, message=FALSE, warning=FALSE, comment=NA}
-rm(list=ls())
-setwd("/Users/beperron/Git/SocialWorkResearch/Data")
-source("/Users/beperron/Git/BibWrangleR/functions/ggsurv.R")
-load("/Users/beperron/Git/SocialWorkResearch/Data/HistoricalArticles.R")
+# Set the working directory to store files created by BWR functions
+path <- "/Users/beperron/Git/SocialWorkResearch/Data/ebscoPsycInfo"
 
-library(dplyr)
-library(ggplot2)
-library(gridExtra)
-library(survival)
-library(grid)
-library(png)
-library(reshape2)
+# Wrangle the data with the BWR function suite
 
-# Inspect dimensions of the data file (Rows X Columns)
-dim(bwr.df)
-
-# Inspect variable names of the data file
-names(bwr.df)
-
-# How many unique article titles?  Ebsco Results of most current search is $n=XXXX$. Do not proceed with analysis if the output does not match this result.  
-length(which(bwr.df$attributes == "TI"))
+ebscoBWR.f(csv=FALSE, path=path, psycInfoOnly=TRUE)
+save(ebscoBWR.df, file = "PsychInfo.R")
 ```
 
-# Exclude years 2014 and 2015
+# ProQuest
 
-```{r}
-years <- c("2014", "2015")
-ebsco.remove <- bwr.df[bwr.df$record %in% years, ]
-ebsco.remove <- ebsco.remove[, "articleID"]
-bwr.df <- bwr.df[!(bwr.df$articleID %in% ebsco.remove),]
+```{r warning=FALSE, message=FALSE, eval=TRUE}
+# Clear workspace
+rm(list=ls())
+
+# Read BWR functions for Mac OS
+source("/Users/beperron/Git/BibWrangleR/functions/proquestBWR.R")
+
+# Set the path where original raw data are stored
+setwd("/Users/beperron/Git/SocialWorkResearch/Data")
+
+# Set the working directory to store files created by BWR functions
+path <- "/Users/beperron/Git/SocialWorkResearch/Data/ProQuest"
+
+# Wrangle the data with the BWR function suite
+
+proQuestBWR.f(csv=FALSE, path=path)
+save(proQuestBWR.df, file = "ProQuest.R")
 ```
-
-# Merge journal titles
-
-```{r}
-bwr.df$record <- ifelse(bwr.df$record == "Eugenics and Social Welfare Bulletin", 
-                       "Eugenics & Social Welfare Bull.", 
-                        bwr.df$record)
-
-bwr.df$record <- ifelse(bwr.df$record == "The British Journal of Social Work", 
-                       "British Journal of Social Work", 
-                        bwr.df$record)
-
-bwr.df$record <- ifelse(bwr.df$record == "Social Work & Social Sciences Review", 
-                       "Social Work and Social Sciences Review", 
-                        bwr.df$record)
-
-bwr.df$record <- ifelse(bwr.df$record == "Social Work with Groups", 
-                       "Social Work With Groups", 
-                        bwr.df$record)
-
-bwr.df$record <- ifelse(bwr.df$record == "Computers in Human Services", 
-                       "Journal of Technology in Human Services", 
-                        bwr.df$record)
-
-bwr.df$record <- ifelse(bwr.df$record == "Journal of Sociology & Social Welfare", 
-                       "Journal of Sociology and Social Welfare", 
-                        bwr.df$record)
-
-#Note leave space after the (Electronic only)
-bwr.df$record <- ifelse(bwr.df$record == "Contemporary Rural Social Work (Electronic only) ", 
-                        "Contemporary Rural Social Work (Electronic only) ", bwr.df$record)
-
-```
-
-# Journals excluded from search results.
-
-```{r}
-exclusions <- c(
-    "American Journal of Preventive Medicine", 
-    "Behavior Modification", 
-    "Brain and Cognition",
-    "Canadian Journal of Community Mental Health",
-    "Canadian Journal on Aging",
-    "Early Child Development and Care",
-    "Early Education and Development",
-    "Employee Assistance Quarterly",
-    "Evaluation and Program Planning",
-    "General Hospital Psychiatry",
-    "Hospital Social Service",
-    "International Review of Social Research",
-    "Journal of Applied Behavioral Science",
-    "Journal of Applied Rehabilitation Counseling",
-    "Journal of Community & Applied Social Psychology",
-    "Journal of Health & Human Services Administration",
-    "Journal of Nonverbal Behavior",
-    "Learning Disabilities Research & Practice",
-    "New York State Department of Social Welfare, Division Publication",
-    "Pennsylvania Social Work",
-    "Proceedings of the National Converence of Social Work",
-    "PROFILE Issues in Teachers' Professional Development",
-    "Psychotherapy",
-    "Social Service Department, Presbyterian Hospital, New York",
-    "Social Work Technique",
-    "Social Work Today", # Magazine
-    "Social Work Yearbook",
-    "The New Social Worker",
-    "Systems Research and Behavioral Science",
-    "Teaching and Teacher Education",
-    "University of Chicago Social Service Monograph",
-    "The Scientific Review of Mental Health Practice",
-    "The Clinical Supervisor",
-    "University of Chicago Social Service Monograph")
-ebsco.remove <- bwr.df[bwr.df$record %in% exclusions, ]
-ebsco.remove <- ebsco.remove[, "articleID"]
-bwr.df <- bwr.df[!(bwr.df$articleID %in% ebsco.remove),]
-```
-
-```{r unique_titles, echo=FALSE}
-unique.titles <- filter(bwr.df, attributes == "SO") %>%
-    group_by(record) %>%
-    summarise(
-        N = n())
-```
-
-# Preliminary Analyses
-
-## Summary of all journal titles included in the analysis
-
-To do:
-
-+ In the table, include the first and last years of indexing, and the numbers of articles.  
-+ Write the script to output a *.csv file so that it can be included as an Appendix without any formatting.
-
-```{r unique_titles, echo=FALSE}
-unique.titles <- filter(bwr.df, attributes == "SO") %>%
-    group_by(record) %>%
-    summarise(
-        N = n())
-
-title <- bwr.df %>%
-        filter(attributes == "SO") %>%
-        select(id = articleID, SO = record)
-
-article <- bwr.df %>%
-        filter(attributes == "TI") %>%
-        select(id = articleID, journal.title = record)
-
-title.articles <- title %>% 
-        left_join(article) %>%
-        group_by(title)
-
-# Number of unique titles
-number.journals <- length(unique(unique.titles$record))
-
-# Unique titles
-journals.unique <- unique(unique.titles$record)
-#write.csv(journals.unique, "journals.csv")
-
-number.journals
-sort(journals.unique)
-socialWorkJournals <- journals.unique
-#save(journals.unique, file="socialWorkJournals.R")
-```
-
-## Count of unique journal titles over time
-
-To do:
-+ Integrate the full journal listing of EbscoHost 
-+ Plot overall number of journals over time 
-+ Plot overall number of journals by major discipline category as defined by EbscoHost classification -- use sociology, anthropology, economics, psychology, and political science
-+ The following "overall growth" plot excludes social work journals in this study.
-There were a small number of overlap journals between social science and social work journals (N = 4 -- double check for final analysis.
-The journals that overlapped were included in the social work group.
-
-```{r unique_titles_year, message=FALSE, comment=NA, warning=FALSE, echo=FALSE}
-journals.year <- tbl_df(bwr.df)
-
-year <- journals.year %>%
-        filter(attributes == "YR") %>%
-        select(id = articleID, year = record)
-
-journals <- journals.year %>%
-        filter(attributes == "SO") %>%
-        select(id = articleID, journal.title = record)
-
-n.journals.year <- journals %>% 
-        left_join(year) %>%
-        group_by(year) %>%
-        distinct(journal.title) %>%
-        summarise(n = n())
-
-journal.count <- ggplot(n.journals.year, aes(as.numeric(year), y=n, group=1)) + 
-    geom_line(colour="darkblue") +
-    #geom_point(colour="red") + 
-    theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-    xlab("Publication year") + 
-    ylab("Number") + 
-    ggtitle("Number of Journals Over Time") + 
-    scale_x_continuous(breaks=seq(1914, 2014, 5))
-
-journal.count
-```
-
-## Growth of Social Work compared to growth of the social sciences
-
-This section shows the overall growth of the social sciences.  This includes all _academic journals_ (excluding magazines and trade publications) that have the following discipline tag:
-
-+ Sociology
-+ Psychology
-+ Economics
-+ Political Science & Studies
-+ Economics
-+ Anthropology
-
-```{r echo=FALSE}
-ebscoFullListing.df <- ebscoFullListing.df[ebscoFullListing.df$SourceType == "Academic Journal",]
-ebscoFullListing.df$IndexingStart <- format(as.Date(ebscoFullListing.df$IndexingStart, "%m/%d/%Y"), "%Y")
-ebscoFullListing.df$IndexingStop <- format(as.Date(ebscoFullListing.df$IndexingStop, "%m/%d/%Y"), "%Y")
-ebJournals.df <- ebscoFullListing.df %>% filter(SourceType == "Academic Journal") %>%
-    select(Discipline, IndexingStart, IndexingStop, PublicationName, ISSN) %>%
-    mutate(IndexingStart = as.numeric(IndexingStart), IndexingStop = as.numeric(IndexingStop)) %>%
-    filter(Discipline == "Sociology" | Discipline == "Political Science & Studies"| 
-           Discipline == "Psychology"| Discipline == "Economics" | Discipline == "Anthropology") 
-```
-
-Some of the journals have duplicate entries in the database because they are cross-classified in multiple social science disciplines.
-The following code is used to create a data set that excludes duplicate entries in the database and ensures no overlap between the social science list and the social work list of journals.
-Duplicates are identified based on ISSN, not journal title.
-This will ensure all duplicates are identified.
-
-```{r}
-ebJournals.df.issn <- ebJournals.df %>% select(ISSN)
-ebJournals.df.unique <- !duplicated(ebJournals.df.issn)
-
-#This function here tests whether the duplication identifier correctly gets the first unique record (by assigning TRUE) and then excluding subsequent records (by assigning FALSE) 
-#cbind(ebJournals.df.unique, ebJournals.df.issn$ISSN)
-
-#This subsets out the duplicates
-ebJournals.df.no.duplicates <- ebJournals.df[ebJournals.df.unique, ]
-
-#This function does a logical comparison of the social science journals and the social work journals to determine potential overlap.  
-overlap <- ebJournals.df.no.duplicates[(ebJournals.df.no.duplicates$PublicationName %in% journals.unique),]  
-print(overlap)
-
-#This reduces the overlap from the social science journal lists, retaining the overlap in the social work journals
-ebJournals.df.no.overlap <- ebJournals.df.no.duplicates[!(ebJournals.df.no.duplicates$PublicationName %in% journals.unique),]   
-```
-
-This section uses the `melt` function to transform the social science data file into a format that can be plotted using ``ggplot2`.  
-```{r echo=FALSE}
-
-#Remove variables that will interfere with melting procedure
-socialScienceJournals.df <- ebJournals.df.no.overlap %>% 
-    select(-PublicationName, -ISSN) %>%
-    mutate(journalID = c(1:nrow(ebJournals.df.no.overlap))) %>%
-    mutate(journalID = as.factor(journalID)) %>% 
-    select(-Discipline)
-
-socialScienceJournals.melted <- melt(socialScienceJournals.df)
-
-ebJournals.overtime.start.d <- socialScienceJournals.melted %>% 
-    filter(value = !is.na(value)) %>%
-    group_by(value) %>%
-    summarise(N.start = n())
-
-ebJournals.overtime.end.d <- socialScienceJournals.melted %>%
-    filter(variable == "IndexingStop"  & !is.na(value)) %>%
-    group_by(value) %>%
-    summarise(N.end = n())
-
-ebjournals.joined.d <- left_join(ebJournals.overtime.start.d, ebJournals.overtime.end.d) %>%
-    mutate(N.end = ifelse(is.na(N.end), 0, N.end), Cumulative = cumsum(N.start)) %>%
-    mutate(N.adjusted = Cumulative - N.end)
-
-journal.time.reduced <- n.journals.year %>% filter(year >= 1950)
-ggplot() + 
-    geom_line(data = ebjournals.joined.d, aes(x=value, y=N.adjusted), group=1, colour="purple") + 
-    geom_line(data = journal.time.reduced, aes(as.numeric(year), y=n), group=1, colour="darkblue")
-```
-
-## What journals published the most number of articles
-
-```{r journal_output, echo=FALSE}
-
-n.so.yr <- filter(bwr.df, attributes == "SO" | attributes == "YR")
-
-n.so <- filter(bwr.df, attributes == "SO") %>% mutate(title = record) %>% 
-        select(-attributes, -record)
-
-n.yr <- filter(bwr.df, attributes == "YR") %>% mutate(year = record ) %>% 
-        select(-attributes, -record)
-
-n.so.yr <- left_join(n.so, n.yr) %>%
-    group_by(title) %>%
-    summarise(first = min(year), last = max(year), n.to.date = n()) %>%
-    arrange(desc(n.to.date))
-
-# 10 highest number of publications
-head(n.so.yr, 20)
-```
-
-## What is the lifespan of journals?
-
-To do:
-+ Incorporate all EbscoHost journals and the separate disciplinary journals
-
-```{r journal_lifespan, echo=FALSE}
-#10 longest running journals 
-longest.running <- n.so.yr %>%
-       mutate(last = as.numeric(last), first = as.numeric(first), 
-              year.diff = last - first) %>%
-       arrange(desc(year.diff)) %>%
-       select(title, first, last, year.diff) %>%
-       mutate(stop = year.diff, event = ifelse(as.numeric(last) != 2013, 1, 0)) %>%
-       select(title, stop, event, as.numeric(first))
-
-survival.journals <- survfit(Surv(longest.running$stop+1, longest.running$event) ~ 1)
-median.survival <- data.frame(time = c(24,24), quant = c(.5,0))
-
-head(longest.running)
-
-ggsurv(survival.journals) + 
-    #geom_line(data = median.survival, aes(time, quant), linetype="longdash") +
-    #annotate("segment", x = 32, xend = 27, y = .12, yend = .12, size = .25, arrow =arrow()) +
-    #geom_text(x = 45, y =.12, label = "median survival", size = 4) + 
-    geom_text(x = 75, y =.75, label = "+ = Last year of indexing", size = 4) +
-    ylim(0,1) +
-    xlim(0,50) + 
-    xlab("Survival Time (in years)") +
-    ylab("Survival Probability") +
-    ggtitle("Survival Probability of Social Work Journals")
-
-```
-
-## What is the number of articles published per year
-
-To do:
-+ Plot against major disciplinary categories
-
-```{r articles_per_year, echo=FALSE}
-n.articles.year <- filter(bwr.df, attributes == "YR") 
-year.split <- split(n.articles.year, n.articles.year$record)
-year.count <- unlist(lapply(year.split, nrow))
-year.count <- year.count[order(names(year.count))]
-years <- names(year.count)
-
-df <- data.frame(years, year.count)
-rownames(df) <- NULL
-
-plot.article.count <- ggplot(df, aes(as.factor(years), 
-                    y = year.count, group=1)) + 
-    geom_line(colour="black") +
-    #geom_point(colour="red") + 
-    theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-    xlab("year") + 
-    ylab("count") + 
-    ggtitle("Number of Studies by Year") +
-    scale_x_discrete(breaks=c(seq(1914, 2015, 10))) +
-    scale_y_continuous(breaks = c(seq(0, 2000, 250)))
-
-df$years <- as.numeric(as.character(df$years))
-
-plot.article.cumulative <- ggplot(df, aes(x = years, y = cumsum(year.count))) + 
-    geom_line() + 
-    theme(axis.text.x = element_text(angle=45, hjust=1)) +
-    scale_x_continuous(breaks=pretty(df$years)) +
-    xlab("year") +  
-    ylab("count") +
-    scale_x_continuous(breaks = c(seq(1914,2014,10))) +
-    scale_y_continuous(breaks = c(seq(0, 25000, 2500))) + 
-    ggtitle("Cumulative Frequency")
-
-grid.arrange(plot.article.count, plot.article.cumulative, ncol=2)
-
-# Print most recent ten years
-tail(df, 10)
-```
-
-# What are the most frequent topic areas (by author specified keywords)?
-
-To do:  
-+ Fix script that performs matching -- convert all keywords to lower before matching
-
-```{r keywords_overall, comment=NA, warning=FALSE, message=FALSE, echo=FALSE}
-kp.df <- filter(bwr.df, attributes == "KP")
-
-subject.terms <- stringr::str_split(kp.df$record, pattern = ";")
-subject.terms <- tolower(subject.terms)
-subject.terms <- unlist(lapply(subject.terms, function(x) gsub(" ", "", x)))
-subject.terms.total <- length(unlist(lapply(subject.terms, 
-                        function(x) gsub(" ", "", x))))
-
-subject.terms.unique <- length(unique(subject.terms))
-
-subject.terms.l <- list(subject.terms.total = subject.terms.total,
-                      subject.terms.unique = subject.terms.unique)
-
-most.frequent <- as.data.frame(table(subject.terms))
-
-most.frequent <- arrange(most.frequent, desc(Freq))
-
-# Print summary statistics
-print(subject.terms.l)
-
-# Print 25 most frequent
-head(most.frequent, 25)
-```
-
-## Most Frequent Author Keywords
-
-_DO NOT INTERPRET RESULTS HERE THIS SECTION IS NOT WORKING PROPERLY_
-
-For this analysis (to-do), select a few keywords that may tell an interesting story of how they change over time -- something that might be revealing of 'trends.'
-
-```{r keywords_over_time, warning=FALSE, message=FALSE, echo=FALSE}
-kp.yr <- filter(bwr.df, attributes == "YR") %>%
-    mutate(year = as.numeric(record)) %>% select(-record, -attributes)
-
-kp <- bwr.df %>%
-        filter(attributes == "KP") %>%
-        select(articleID = articleID, keyword = record) %>%
-        mutate(keyword = gsub(" ", "", keyword))
-
-kp.year <- kp %>% 
-         left_join(kp.yr) %>%
-         group_by(keyword, year) %>%
-         summarise(n = n()) %>%
-         arrange(keyword, year, n)
-
-select.keywords <- c("women", "leadership")
-select.keywords.df <- kp.year %>% filter(tolower(keyword) %in% select.keywords)
-
-library(plyr) # Fix code so ply loads before dplyr
-key.plot.df <- ddply(select.keywords.df, .(keyword), transform, cumulative = cumsum(n))
-detach(package:plyr)
-
-#Fix graph to sort the keywords / colour
-ggplot(key.plot.df, aes(x = year, y = cumulative, colour = keyword, group = keyword)) + 
-    geom_line() +
-    ggtitle("Cumulative Sum of Articles by Keywords") +
-    ylab("Cumulative Sum") + 
-    xlab("Year") + 
-    theme(legend.title=element_blank())
-
-```
-
-## Location of Studies
-
-To do:
-+ Determine best format / presentation of map
-
-```{r location, comment=NA, warning=FALSE, message=FALSE, echo=FALSE}
-LO.df <- filter(bwr.df, attributes == "LO") %>%
-         group_by(record) %>%
-         summarise(Country = unique(record),
-                   N = n()) %>%
-        arrange(desc(N)) %>% 
-        select(-record)
-
-locations <- as.data.frame(table(LO.df))
-locations <- arrange(locations, desc(Freq))
-locations.unique <- length(unique(locations))
-
-#write.csv(locations, "location.csv")
-
-```
-
-## Location of studies over time
-
-To do:
-+ Determine best format / presentation of map
-
-```{r location_over_time, warning=FALSE, message=FALSE, echo=FALSE}
-library(RColorBrewer)
-year <- filter(bwr.df, attributes == "YR") %>%
-    mutate(year = as.numeric(record)) %>% select(-record, -attributes)
-
-location.temp <- bwr.df %>%
-        filter(attributes == "LO") %>%
-        select(articleID = articleID, country = record) %>%
-        mutate(country = gsub(" ", "", country))
-
-location.year <- location.temp %>% 
-         left_join(year) %>%
-         group_by(country, year) %>%
-         summarise(n = n()) %>%
-         arrange(country, year, n) %>%
-         mutate(cumsum_n = cumsum(n), log_n = log(n+1))
-
-top.locations <- LO.df %>% 
-                 select(Country) %>%
-                 slice(1:5)
-
-top.locations$Country <- gsub(" ", "", top.locations$Country)
-
-location.year.top <- location.year %>% filter(country %in% top.locations$Country)
-
-ggplot(location.year.top, aes(x = year, y = log_n, colour = country )) + 
-    geom_line() +
-    ggtitle("Log Number of Articles by Countries With Highest Scholarly Ouput") +
-    xlab("Publication Year") + 
-    ylab("log N+1") +
-    theme(legend.position=c(.210, .7))
-
-top.locations.no.us <- LO.df %>% 
-                select(Country) %>%
-                slice(2:10)
-
-top.locations.no.us$Country <- gsub(" ", "", top.locations.no.us$Country)
-
-location.year.top.no.us <- location.year %>% filter(country %in% top.locations.no.us$Country)
-
-ggplot(location.year.top.no.us, aes(x = year, y = cumsum_n, colour = country )) + geom_line() +
-    ggtitle("Cumulative Number of Article by Countries with Highest Scholarly Output \n(Excluding the United States)") +
-    theme(legend.position=c(.210, .6))
-```
-## Countries represents in the social work research
-
-To do:
-+ Obtain definition of `LO` tag.  
-+ Determine how many articles had LO tag (note the issue if not included from Social Science Index)
-
-```{r fig.width=8, echo=FALSE}
-Map100YearWithUS <- readPNG("/Users/beperron/Git/SocialWorkResearch/images/Map100Years.png")
-grid.raster(Map100YearWithUS)
-
-Map100YearWithoutUS <- readPNG("/Users/beperron/Git/SocialWorkResearch/images/Map100YearsWithoutUS.png")
-grid.raster(Map100YearWithUS)
-```
-
-## Countries not represented in social work research
-
-```{r fig.width=8, echo=FALSE}
-library(png)
-library(grid)
-img <- readPNG("/Users/beperron/Git/SocialWorkResearch/images/NotRepresented100Years.png")
-grid.raster(img)
-
-```
-
-## Number of authors
-```{r comment=NA, message=FALSE, warning=FALSE, echo=FALSE}
-n.authors.article <- bwr.df %>% 
-    filter(attributes == "AU") %>%
-    select(id = articleID, author= record) %>%
-    mutate(id = as.numeric(id))
-
-n_authors.1 <- n.authors.article %>% 
-        group_by(id) %>%
-        summarise(n = n())
-
-n_authors.1t <- n_authors.1 %>% mutate(n = ifelse(n >=6, 6, n)) %>% 
-    group_by(n) %>%
-    summarise(Articles = n())
-
-ggplot(n_authors.1t, aes(x = n, y = Articles)) +
-    geom_bar(stat="identity", colour="black", fill = "white") +
-    geom_text(aes(label = Articles), vjust=-.3, size = 4) +
-    scale_x_discrete(limits = c(as.character(1:5), "6+")) + 
-    ggtitle("Number of Articles by Author Count") + 
-    xlab("Author Count") + 
-    ylab("Articles")
-```
-
-## Number of authors over time
-
-This figure shows the average number of authors, along with the standard deviation as the ribbon around the average.
-Note that there is a possible problem in these data, with a single article listing a huge number.
-That can be corrected at a later time.
-
-```{r message=FALSE, comment=NA, warning=FALSE, fig.height=2, fig.height=4, echo=FALSE}
-df.2 <- tbl_df(bwr.df)
-year <- df.2 %>%
-        filter(attributes == "YR") %>%
-        select(id = articleID, year = record)
-
-authors <- df.2 %>%
-        filter(attributes == "AU") %>%
-        select(id = articleID, author = record)
-
-n_authors <- authors %>%
-        group_by(id) %>%
-        summarise(n=n())
-
-n_authors <- n_authors %>% 
-        left_join(year) %>%
-        group_by(year) %>%
-        summarise(median.n = median(n),
-                  average.n = mean(n),
-                  min.n = min(n),
-                  max.n = max(n),
-                  std.dev  = sd(n) )
-
-plot.author.count2 <- ggplot(n_authors, aes(as.numeric(year), y=average.n, group=1)) +  
-    geom_ribbon(aes(ymin = average.n-std.dev, ymax=average.n+std.dev), colour="lightblue", fill="lightblue", alpha=.40) +
-    geom_line(colour="black") + 
-    geom_segment(aes(x= 1940, y = 5.5, xend = 1935, yend = 5.5), 
-                 arrow=arrow(length=unit(0.25, "cm"))) +
-    annotate("text", x = 1951, y = 5.5, label = "1 outlier case of \n24 listed authors", size=3.5) +
-    ylab("Average number of authors (black) \nStandard deviation (light blue)") +
-    xlab("Publication year") +
-    ggtitle("Average Number of Authors per Article Over Time")
-
-plot.author.count2
-
-```
-
-```

### 2015-02-25 dataCleaning.Rmd
Fixed analysis.

--- 2015-02-22 dataCleaning.Rmd
@@
 
-#load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
-#load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
-#load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoPsycInfo.R")
+load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
+load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
+load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoPsycInfo.R")
 
-load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
-load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
-load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")
+#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
+#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
+#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")
 
@@
 
-# Set the working directory
-#setwd("/Users/beperron/Git/SocialWorkResearch/Data")
-#setwd("/Users/SSW/Documents/GitHub/SocialWork100Years/Data")
+# Data cleaning and pre-processing
+
+## Narrow results to past 25 years
+
+Inspection of the data indicated notable delays in indexing for the years 2014 and 2015.
+Therefore, these years were excluded from the current study.
+Thus, this study includes journals indexed through the end of 2013.
+
+```{r}
+full.df <- ebscoBWR.df
+year.25 <- as.character(c(1900:1987, 2014, 2015))
+years <- c("2014", "2015")
+#ebsco.remove <- full.df[full.df$record %in% years, ]
+ebsco.remove <- full.df[full.df$record %in% year.25, ]
+ebsco.remove <- ebsco.remove[, "articleID"]
+full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
 ```
 
-# Pre-processing summary
-```{r echo=FALSE}
-full.df$record <- ifelse(full.df$record == 
-        "Social Work & Social Sciences Review",     # Spelling difference
-        "Social Work and Social Sciences Review", 
-                        full.df$record)
-
-full.df$record <- ifelse(full.df$record == 
-        "Social Work with Groups",                  # Spelling difference
-        "Social Work With Groups", 
-                        full.df$record)
-
-full.df$record <- ifelse(full.df$record == 
-        "Journal of Sociology & Social Welfare",    # Spelling difference
-        "Journal of Sociology and Social Welfare",  
-                        full.df$record)
-
-full.df$record <- ifelse(full.df$record == 
-    "The British Journal Social Work",          # Spelling difference
-        "British Journal of Social Work",           
-                        full.df$record)
-
-full.df$record <- ifelse(full.df$record ==
-    "Aretê",                                   #Spelling difference
-      "Arete",
-              full.df$record)
-
-full.df$record <- ifelse(full.df$record ==
-    "Journal of Gay and Lesbian Social Services",     #Spelling difference
-        "Journal of Gay & Lesbian Social Services",
-                        full.df$record)
-
-full.df$record <- ifelse(full.df$record ==
-    "Canadian Social Work Review/Revue canadienne de service social",
-        "Canadian Social Work Review",
-                        full.df$record)
-```
-
-Provided below is a summary of the datafile processed by `ebscoBWR` function before any cleaning procedures specifically for this project were employed, with the exception of resolving spelling errors or differences.
-For example, _Social Work With Groups_ was exported as a separate journal than _Social Work with Groups_ (note the capitalization difference in the word _with_.)
+## Initial descriptive summary
 
@@
     "The Scientific Review of Mental Health Practice",
-    "The Clinical Supervisor",
-    "Arete: Revista de Filosofia")
+    "The Clinical Supervisor")
 

### 2015-02-25 dataCleaning.Rmd

@@
 
+```{r}
+full.df$record <- ifelse(full.df$record == 
+    "The British Journal of Social Work",          # Spelling difference
+        "British Journal of Social Work",           
+                        full.df$record)
+
+full.df$record <- ifelse(full.df$record ==
+    "Revista de Asistenta Sociala (Social Work Review)",
+        "Social Work Review",
+                        full.df$record)
+
+full.df$record <- gsub("Arete", "xxx", full.df$record)
+full.df$record <- gsub("Aret.{1,3}", "Arete", full.df$record)
+full.df$record <- gsub("xxx", "Arete", full.df$record) 
+                                      #Replaces special character       
+                                      #in Arete and preserves other formatting
+
+full.df$record <- ifelse(full.df$record ==
+    "Journal of Gay and Lesbian Social Services",     #Spelling difference
+        "Journal of Gay & Lesbian Social Services",
+                        full.df$record)
+
+full.df$record <- ifelse(full.df$record ==
+    "Canadian Social Work Review/Revue canadienne de service social",
+        "Canadian Social Work Review",
+                        full.df$record)
+
+full.df$record <- ifelse(full.df$record ==
+    "INDIAN JOURNAL OF SOCIAL WORK",                    #Spelling difference
+        "Indian Journal of Social Work",
+                      full.df$record)
+
+full.df$record <- ifelse(full.df$record ==
+    "The Indian Journal of Social Work",              #Spelling difference
+        "Indian Journal of Social Work",
+                            full.df$record)
+
+full.df$record <- ifelse(full.df$record ==
+    "Asia Pacific Journal of Social Work",              #Spelling difference
+        "Asia Pacific Journal of Social Work and Development",
+                            full.df$record)
+
+full.df$record <- ifelse(full.df$record ==
+    "Social Work & Society",                           #Spelling difference
+        "Social Work and Society",
+                            full.df$record)
+
+full.df$record <- ifelse(full.df$record ==
+    "Journal of Social Work in Disability & Rehabilitation",
+        "Journal of Social Work in Disability and Rehabilitation", 
+                            full.df$record)           #Spelling difference
+
+full.df$record <- ifelse(full.df$record ==
+    "Hong Kong Journal of Social Work",
+        "The Hong Kong Journal of Social Work", 
+                            full.df$record)           #Spelling difference
+
+full.df$record <- ifelse(full.df$record ==
+    "The Journal of Baccalaureate Social Work",
+        "Journal of Baccalaureate Social Work", 
+                            full.df$record)           #Spelling difference
+
+full.df$record <- ifelse(full.df$record ==
+    "Journal of Practice Teaching in Health and Social Work",
+        "Journal of Practice Teaching in Social Work and Health", 
+                            full.df$record)           #Spelling difference
+
+full.df$record <- ifelse(full.df$record ==
+    "Professional Development: The International Journal of Continuing Social Work Education",
+        "Professional Development", 
+                            full.df$record)           #Spelling difference
+
+```
+
 ## Initial descriptive summary
@@
     "The Scientific Review of Mental Health Practice",
-    "The Clinical Supervisor")
+    "The Clinical Supervisor",
+    "Arete: Revista de Filosofia",
+    "Arete Revista de Filosofia")
 

### 2015-02-25 archive/ebscoCompleteListing.Rmd
File management.

---
title: "EbscoHistory"
author: "Brian Perron"
date: "January 13, 2015"
output: html_document
---

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r eval=FALSE}
library(dplyr)
library(stringr)
library(xlsx)
library(gdata)

#ebscoFullListing.df <- read.xls("/Users/beperron/Git/SocialWorkResearch/Data/completeListing.xls", sheet=1, header=TRUE)
#save(ebscoFullListing.df, file="ebscoFullListing.R")
```

```{r}
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFullListing.R")
ebscoFullListing.df <- ebscoFullListing.df[ebscoFullListing.df$SourceType == "Academic Journal",]
ebscoFullListing.df$IndexingStart <- format(as.Date(ebscoFullListing.df$IndexingStart, "%m/%d/%Y"), "%Y")
ebscoFullListing.df$IndexingStop <- format(as.Date(ebscoFullListing.df$IndexingStop, "%m/%d/%Y"), "%Y")
ebscoFullListing.df$journalID <- c(1:nrow(ebscoFullListing.df))
barplot(table(as.factor(ebscoFullListing.df$IndexingStart)))
```

```{r}
library(reshape2)
library(dplyr)
ebJournals.df <- ebscoFullListing.df %>% filter(SourceType == "Academic Journal") %>%
    select(journalID, Discipline, IndexingStart, IndexingStop, PublicationName, ISSN) %>%
    mutate(journalID = as.factor(journalID), IndexingStart = as.numeric(IndexingStart), IndexingStop = as.numeric(IndexingStop)) %>%
    filter(Discipline == "Sociology" | Discipline == "Political Science & Studies"| 
           Discipline == "Psychology"| Discipline == "Economics" | Discipline == "Anthropology")

unique.journal.titles <- unique(ebJournals.df$ISSN)
ebJournals.df <-ebJournals.df[unique.journal.titles,]

load("socialWorkJournals.R")
cross.check.journals <- ebJournals.df[ebJournals.df$PublicationName %in% socialWorkJournals,]
cross.check.journals

ebJournals.df <- select(ebJournals.df, -PublicationName, -ISSN)

ebJournals.melted <- melt(ebJournals.df)

ebJournals.overtime.start <- ebJournals.melted %>% 
    filter(value = !is.na(value)) %>%
    group_by(Discipline, value) %>%
    summarise(N.start = n())

ebJournals.overtime.end <- ebJournals.melted %>% 
    filter(variable == "IndexingStop"  & !is.na(value)) %>%
    group_by(Discipline, value) %>%
    summarise(N.end = n())

ebjournals.joined <- left_join(ebJournals.overtime.start, ebJournals.overtime.end) %>%
    mutate(N.end = ifelse(is.na(N.end), 0, N.end), Cumulative = cumsum(N.start)) %>%
    mutate(N.adjusted = Cumulative - N.end)

ebJournals.melted.d <- melt(ebJournals.df)

ebJournals.overtime.start.d <- ebJournals.melted.d %>% 
    filter(value = !is.na(value)) %>%
    group_by(value) %>%
    summarise(N.start = n())

ebJournals.overtime.end.d <- ebJournals.melted.d %>% 
    filter(variable == "IndexingStop"  & !is.na(value)) %>%
    group_by(value) %>%
    summarise(N.end = n())

ebjournals.joined.d <- left_join(ebJournals.overtime.start.d, ebJournals.overtime.end.d) %>%
    mutate(N.end = ifelse(is.na(N.end), 0, N.end), Cumulative = cumsum(N.start)) %>%
    mutate(N.adjusted = Cumulative - N.end)

journal.time.reduced <- n.journals.year %>% filter(year >= 1950)
ggplot() + 
    geom_line(data = ebjournals.joined.d, aes(x=value, y=N.adjusted), group=1, colour="purple") + 
    geom_line(data = journal.time.reduced, aes(as.numeric(year), y=n), group=1, colour="darkblue")

#From main analyses
journal.count <- ggplot(n.journals.year, aes(as.numeric(year), y=n, group=1)) + 
    geom_line(colour="black") +
    #geom_point(colour="red") + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
    xlab("Publication year") + 
    ylab("Number") + 
    ggtitle("Number of Journals Over Time") + 
    scale_x_continuous(breaks=seq(1914, 2014, 5))

```

### 2015-02-25 dataCleaning.Rmd
Updated code

@@
 
-#load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
-#load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
-#load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoPsycInfo.R")
-
-load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
-load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
-load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")
+load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
+load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
+load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoPsycInfo.R")
+hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
+#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
+#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
+#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")
 
@@
 ```{r}
-full.df <- ebscoBWR.df
+
 year.25 <- as.character(c(1900:1987, 2014, 2015))
@@
 
-hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
-
 unique.titles <- filter(full.df, attributes == "journal") %>%
@@
 ```{r}
-hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
-
 unique.swHistory <- filter(full.df, attributes == "journal") %>%

### 2015-02-26 dataCleaning.Rmd
Added function for generating CSV file of journal.

@@
 ```
+
+The following evaluation argument in the chunk is set to FALSE.
+Set this function to TRUE to process CSV files of the target journals for inspection.
+CSV files are named by the journal title.
+Be sure to use the exact spelling of the journal as it is contained in the data files.
+Set the other arguments to TRUE if you want additional fields to be included.
+Please note that it will save the files to your current working directory, which is not specified in this Markdown document.
+
+```{r eval=FALSE}
+journalArticleFinder.f <- function(journalTitle, keyword = FALSE, 
+                           authorAff = FALSE, abstract = FALSE){
+    article.search <- which(full.df$record == journalTitle)
+    article.search <- full.df[article.search,]
+    article.search.ID <- select(article.search, articleID)
+    target.ID <- full.df$articleID %in% article.search.ID$articleID
+    journal.article.df <- full.df[target.ID, ]
+    if(keyword == FALSE){journal.article.df <- filter(journal.article.df, attributes != "keyWord")}
+    if(authorAff == FALSE){journal.article.df <- filter(journal.article.df, attributes != "authorAff")}
+    if(abstract == FALSE){journal.article.df <- filter(journal.article.df, attributes != "abstract")}
+    x.shortened <- gsub(" ", "", journalTitle)
+    write.csv(journal.article.df, file = paste0(x.shortened, ".csv"), row.names=F)
+    }
+
+journalArticleFinder.f("Research on Social Work Practice")
+journalArticleFinder.f("Social Work")
+
+```

### 2015-02-26 dataCleaning.Rmd
Fixed minor bugs.

--- 2015-02-25 dataCleaning.Rmd
@@
 load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
-load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoPsycInfo.R")
+load("/Users/beperron/Git/SocialWorkResearch/Data/PsycInfo.R")
 hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
@@
   full.df<-combined.DF[!(combined.DF$articleID %in% jointTitles.dup.ID), ]
-
-rm(list=setdiff(ls(), "full.df"))
 
@@
 ```
+
+The following evaluation argument in the chunk is set to FALSE.
+Set this function to TRUE to process CSV files of the target journals for inspection.
+CSV files are named by the journal title.
+Be sure to use the exact spelling of the journal as it is contained in the data files.
+Set the other arguments to TRUE if you want additional fields to be included.
+Please note that it will save the files to your current working directory, which is not specified in this Markdown document.
+
+```{r eval=TRUE}
+journalArticleFinder.f <- function(journalTitle, keyword = FALSE, 
+                           authorAff = FALSE, abstract = FALSE){
+    article.search <- which(full.df$record == journalTitle)
+    article.search <- full.df[article.search,]
+    article.search.ID <- select(article.search, articleID)
+    target.ID <- full.df$articleID %in% article.search.ID$articleID
+    journal.article.df <- full.df[target.ID, ]
+    if(keyword == FALSE){journal.article.df <- filter(journal.article.df, attributes != "keyWord")}
+    if(authorAff == FALSE){journal.article.df <- filter(journal.article.df, attributes != "authorAff")}
+    if(abstract == FALSE){journal.article.df <- filter(journal.article.df, attributes != "abstract")}
+    x.shortened <- gsub(" ", "", journalTitle)
+    write.csv(journal.article.df, file = paste0(x.shortened, ".csv"), row.names=F)
+    }
+
+journalArticleFinder.f("Research on Social Work Practice")
+journalArticleFinder.f("Social Work")
+
+```

### 2015-02-26 dataCleaning.Rmd
Cleanup

--- 2015-02-26 dataCleaning.Rmd
@@
 
-jointTitles$record<-gsub("[[:punct:]]", "", jointTitles$record)
+jointTitles$record<-gsub("[]\\?!\"\'#$%&(){}+*/:;,._`|~\\[<=>@\\^-]", "", jointTitles$record)
 

### 2015-02-26 dataCleaning.Rmd
Code clean up.
Identifies and eliminates ineligible records.

@@
 hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
-#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
-#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
-#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")
 
+load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
+load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
+load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")
+hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)
 ```
@@
 
+#Identify records that were incorrectly captured in the wrangle
+#using regular expressions
+insert.1<-"[B|b]ook [R|r]eview.|^[F|f]orum|[F|f]orum$|[C|c]ommentary|Comments on"
+insert.2<-"^[I|i]ndex [T|t]o|[I|i]ntroduction:|[I|i]ntroduction [T|t]o|\\([B|b]ook\\)"
+insert.3<-"[H|h]andbook|Volume|volumes|newsletters|[L|l]etter from"
+insert.4<-"[P|p]reface|\\([0-9]{4}-[0-9]{4}\\):|: [A|a] [R|r]esponse [T|t]o [B-Z]"
+insert.5<-"[S|s]pecial [I|i]ssue|[T|t]able [O|o]f [C|c]ontent|\\([U|u]ndetermined"
+insert<-paste(insert.1,insert.2,insert.3,insert.4,insert.5, sep="|")
+
+badRecords<-subset(jointTitles, grepl(insert, record))
+badRecords.ID<-badRecords$articleID
+
 #Forces article title text to lower case
@@
 
-  #Combines EbscoHost and ProQuest Wrangles, and strips out article attributes 
-  #from duplicate entries
+  #Combines EbscoHost and ProQuest Wrangles, and 
   combined.DF<-rbind(ebscoBWR.df, proQuestBWR.df)
+
+  #Strips out article attributes from inelligble records
+  combined.DF<-combined.DF[!(combined.DF$articleID %in% badRecords.ID), ]
+
+  #strips out article attributes from duplicate records
   full.df<-combined.DF[!(combined.DF$articleID %in% jointTitles.dup.ID), ]

### 2015-02-28 dataCleaning.Rmd
Major update.

--- 2015-02-26 dataCleaning.Rmd
@@
 load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
-load("/Users/beperron/Git/SocialWorkResearch/Data/PsycInfo.R")
+#load("/Users/beperron/Git/SocialWorkResearch/Data/PsycInfo.R")
 hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
+
 #load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
@@
 #load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")
-
+#hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)
 ```
@@
 
-#Creates data frames that contain only article ID and titles from respective
-#databases
-ebscoTitles<-filter(ebscoBWR.df, attributes=="article")
-proTitles<-filter(proQuestBWR.df, attributes=="article")
+full.df <- rbind(ebscoBWR.df, proQuestBWR.df)
+```
 
-#Combines titles into single data frame
-jointTitles<-rbind(ebscoTitles, proTitles)
+```{r reduced, comment=NA}
+titles <- filter(full.df, attributes == "article")
+journals <- filter(full.df, attributes == "journal")
+year <- filter(full.df, attributes == "pubYear")
 
-#Forces article title text to lower case
-jointTitles$record<-tolower(jointTitles$record)
+year.journal <- dplyr::intersect(year$articleID, journals$articleID)
+year.journal.titles <- dplyr::intersect(year.journal, titles$articleID)
+
+full.df <- full.df[full.df$articleID %in% year.journal.titles, ]
+```
+
+Exclude incorrectly captured articles. 
+```{r}
+#Identify records that were incorrectly captured in the wrangle
+#using regular expressions
+insert.1<-"[B|b]ook [R|r]eview[.:]|^[F|f]orum.+|[F|f]orum$|[C|c]ommentary|Comment.+"
+insert.2<-"^[I|i]ndex\\s[T|t]o|[I|i]ntroduction:|[I|i]ntroduction [T|t]o|\\([B|b]ook\\)"
+insert.3<-"[H|h]andbook|Volume|volumes|newsletters|[L|l]etter from"
+insert.4<-"[P|p]reface|\\([0-9]{4}-[0-9]{4}\\):|: [A|a] [R|r]esponse [T|t]o [B-Z]"
+insert.5<-"[S|s]pecial\\s[I|i]ssue|[T|t]able\\s[O|o]f\\s[C|c]ontent|\\([U|u]ndetermined"
+insert.6<-"^Book.+ | ^COMMENTARY.+ | Call\\s.+ | Contents.+ | Editor.+ | Errat.+"
+insert.7<-"^FROM\\THE.+ | ^From\\sthe\\ed.+ | Health\\s[&]\\sS.+ | ^LETTER.+ |
+             ^Letter\\sfrom.+ | ^News\\and.+ | ^Response\\sto\\s[A-Z] | Vol\\.\\s[0-9] |
+            ^Volume.+ | ^\\["
+insert<-paste(insert.1,insert.2,insert.3,insert.4,insert.5, insert.6, 
+              insert.7, sep="|")
+
+badRecords<-subset(titles, grepl(insert, record))
+badRecords.ID<-badRecords$articleID
+
+full.df <- full.df[!(full.df$articleID %in% badRecords.ID), ]
+
+```
+
+Duplicate title search
+```{r}
+titles$matching <- tolower(titles$record)
+
+#Eliminate `the` and `a` at the beginning of sentences and after colons
+titles$matching <- gsub("^the\\s", "", titles$matching)
+titles$matching <- gsub("^a\\s", "", titles$matching)
+titles$matching <- gsub("[[:punct:]]", "", titles$matching)
 
@@
 #entry are detected during duplicate elimination
-jointTitles$record<-gsub(" ","", jointTitles$record)
+titles$matching <- gsub(" ","", titles$matching)
 
-jointTitles$record<-gsub("[]\\?!\"\'#$%&(){}+*/:;,._`|~\\[<=>@\\^-]", "", jointTitles$record)
-
-jointTitles<- jointTitles[duplicated(jointTitles$record), ]
-
-#Screen out duplicated records by articleID. The articleID must be used
-#because the duplicate title contains other article attributes
-jointTitles.dup.ID <- jointTitles$articleID
-
-  #Combines EbscoHost and ProQuest Wrangles, and strips out article attributes 
-  #from duplicate entries
-  combined.DF<-rbind(ebscoBWR.df, proQuestBWR.df)
-  full.df<-combined.DF[!(combined.DF$articleID %in% jointTitles.dup.ID), ]
-
+duplicated.titles <- duplicated(titles$matching)
+duplicated.ID <- titles$articleID[duplicated.titles]
+full.df <- full.df[!(full.df$articleID %in% duplicated.ID), ]
 ```
@@
 ```{r}
+year.25 <- as.character(c(1900:1987, 2014, 2015))
 
-year.25 <- as.character(c(1900:1987, 2014, 2015))
-years <- c("2014", "2015")
-#ebsco.remove <- full.df[full.df$record %in% years, ]
-ebsco.remove <- full.df[full.df$record %in% year.25, ]
-ebsco.remove <- ebsco.remove[, "articleID"]
-full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
+temp.df <- filter(full.df, attributes == "pubYear")
+
+year.remove <- temp.df[temp.df$record %in% year.25, ]
+year.removeID <- year.remove$articleID
+
+full.df <- full.df[!(full.df$articleID %in% year.removeID), ]
+
 ```
@@
 
+dim(filter(full.df, attributes == "pubYear"))
+dim(filter(full.df, attributes == "article"))
+dim(filter(full.df, attributes == "journal"))
+
 ```
@@
 rm(ebsco.remove)
+
+```
+
+```{r preprocessing, comment=NA, echo=TRUE} 
+number.of.articles <- length(which(full.df$attributes == "article"))
+range.of.years <- range(full.df$record[full.df$attributes == "pubYear"])
+```
+
+```{r}
+# Number of articles
+cat(number.of.articles)
+```
+
+```{r}
+# Range of years
+cat(range.of.years)
+```
+
+```{r echo=FALSE, comment=NA}
+unique.titles <- filter(full.df, attributes == "journal") %>%
+    group_by(record) %>%
+    summarise(
+        N = n())
+print.data.frame(unique.titles, rowNames=FALSE)
 ```
@@
 
-```{r date, echo=FALSE, comment=NA}
+```{r echo=FALSE, comment=NA}
 unique.titles <- filter(full.df, attributes == "journal") %>%
@@
 
+articles <- filter(full.df, attributes == "article") %>% arrange(record)
+write.csv(articles, file = "articles.csv")
+
 ```

### 2015-02-28 objectMaker.Rmd
Fixed minor bugs.
Major update.

--- 2015-02-25 Analysis.Rmd
@@
 
-ebscoBWR.f(csv=FALSE, path=path, psycInfoOnly=FALSE)
+ebscoBWR.f(csv=FALSE, path=path)
 save(ebscoBWR.df, file = "ebscoFULL.R")
@@
 
-```{r warning=FALSE, message=FALSE, eval=TRUE}
+```{r warning=FALSE, message=FALSE, eval=FALSE}
 # Clear workspace
@@
 ebscoBWR.f(csv=FALSE, path=path, psycInfoOnly=TRUE)
-save(ebscoBWR.df, file = "PsychInfo.R")
+ebscoPsycInfoBWR.df <- ebscoBWR.df
+save(ebscoPsycInfoBWR.df, file = "PsycInfo.R")
 ```

### 2015-03-05 dataCleaning.Rmd
Clean up.

@@
 
-# Overview
-
-This document summarizes data cleaning procedures of the data file processed by the `ebscoBWR` fucntion.
-It should be noted that that `ebscoBWR` function merged the search results from the first- and second-level searches performed on the three databases (psycInfo, Social Science Abstracts, and Social Work Abstract) hosted by the EbscoPlatform.
-This function merged all the search results, transformed the data into a structured data file, and removed all duplicate article records.
-No further transformations or cleaning was performed by the `ebscoBWR` function.
-Provided below are basic descriptive summaries of the results from the full search before further cleaning.
-
-The main file for analysis is `fullDF.R`, and a separate file is just for psycInfo `psycInfoDF.R`.  The same cleaning procedures need to be performed on both data files prior to analysis.
-
-# Initialization of workspace
-
-```{r initialization_dataprocessing, warning=FALSE, message=FALSE, eval=TRUE}
+```{r initialization_dataprocessing, warning=FALSE, message=FALSE, echo=FALSE, tidy=TRUE}
 # Clear workspace
@@
 # Read data files
-
 load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
@@
 hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
-
-#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
-#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
-#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")
-#hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)
 ```
 
+```{r appendData, comment=NA, echo=FALSE}
 # Combines EbscoHost and ProQUest
-
-This section ... wrangles and eliminates duplicate article titles
-
-```{r appendData, comment=NA}
 
@@
 full.df <- rbind(ebscoBWR.df, proQuestBWR.df)
-```
 
-```{r reduced, comment=NA}
-titles <- filter(full.df, attributes == "article")
-journals <- filter(full.df, attributes == "journal")
-year <- filter(full.df, attributes == "pubYear")
-
-year.journal <- dplyr::intersect(year$articleID, journals$articleID)
-year.journal.titles <- dplyr::intersect(year.journal, titles$articleID)
-
-full.df <- full.df[full.df$articleID %in% year.journal.titles, ]
-```
-
-Exclude incorrectly captured articles. 
-```{r}
-#Identify records that were incorrectly captured in the wrangle
-#using regular expressions
-insert.1<-"[B|b]ook [R|r]eview[.:]|^[F|f]orum.+|[F|f]orum$|[C|c]ommentary|Comment.+"
-insert.2<-"^[I|i]ndex\\s[T|t]o|[I|i]ntroduction:|[I|i]ntroduction [T|t]o|\\([B|b]ook\\)"
-insert.3<-"[H|h]andbook|Volume|volumes|newsletters|[L|l]etter from"
-insert.4<-"[P|p]reface|\\([0-9]{4}-[0-9]{4}\\):|: [A|a] [R|r]esponse [T|t]o [B-Z]"
-insert.5<-"[S|s]pecial\\s[I|i]ssue|[T|t]able\\s[O|o]f\\s[C|c]ontent|\\([U|u]ndetermined"
-insert.6<-"^Book.+ | ^COMMENTARY.+ | Call\\s.+ | Contents.+ | Editor.+ | Errat.+"
-insert.7<-"^FROM\\THE.+ | ^From\\sthe\\ed.+ | Health\\s[&]\\sS.+ | ^LETTER.+ |
-             ^Letter\\sfrom.+ | ^News\\and.+ | ^Response\\sto\\s[A-Z] | Vol\\.\\s[0-9] |
-            ^Volume.+ | ^\\["
-insert<-paste(insert.1,insert.2,insert.3,insert.4,insert.5, insert.6, 
-              insert.7, sep="|")
-
-badRecords<-subset(titles, grepl(insert, record))
-badRecords.ID<-badRecords$articleID
-
-full.df <- full.df[!(full.df$articleID %in% badRecords.ID), ]
-
-```
-
-Duplicate title search
-```{r}
-titles$matching <- tolower(titles$record)
-
-#Eliminate `the` and `a` at the beginning of sentences and after colons
-titles$matching <- gsub("^the\\s", "", titles$matching)
-titles$matching <- gsub("^a\\s", "", titles$matching)
-titles$matching <- gsub("[[:punct:]]", "", titles$matching)
-
-#Strips out white space and punctuation to ensure small differences in data 
-#entry are detected during duplicate elimination
-titles$matching <- gsub(" ","", titles$matching)
-
-duplicated.titles <- duplicated(titles$matching)
-duplicated.ID <- titles$articleID[duplicated.titles]
-full.df <- full.df[!(full.df$articleID %in% duplicated.ID), ]
-```
-
-# Data cleaning and pre-processing
-
-## Narrow results to past 25 years
-
-Inspection of the data indicated notable delays in indexing for the years 2014 and 2015.
-Therefore, these years were excluded from the current study.
-Thus, this study includes journals indexed through the end of 2013.
-
-```{r}
 year.25 <- as.character(c(1900:1987, 2014, 2015))
@@
 
-```
-
-```{r}
 full.df$record <- ifelse(full.df$record == 
@@
 
-dim(filter(full.df, attributes == "pubYear"))
-dim(filter(full.df, attributes == "article"))
-dim(filter(full.df, attributes == "journal"))
+full.df$record <- ifelse(full.df$record ==
+    "Social Work with Groups",
+        "Social Work With Groups", 
+                            full.df$record)
 
-```
-
-## Initial descriptive summary
-
-```{r preprocessing, comment=NA, echo=TRUE} 
-number.of.articles <- length(which(full.df$attributes == "article"))
-range.of.years <- range(full.df$record[full.df$attributes == "pubYear"])
-```
-
-```{r}
-# Number of articles
-cat(number.of.articles)
-```
-
-```{r}
-# Range of years
-cat(range.of.years)
-```
-
-## Exclusion of journals not meeting supplemental search terms
-
-The search for journals involved a two-stage process.
-It began by extracting all records from journals based on the social work journal list of Hodge and L (APA cite).
-Journals were excluded if they did not contain one of the major search terms from the supplemental list.
-The majority of these journals were captured in the supplemental search query because the journal used one of the supplemental search terms in a special issue.
-The mission and scope of journals were also reviewed when it was unclear whether the journal was specific to social work research (e.g., _The Clinical Supervisor_).
-The supplemental search terms included:
-
-+ social work
-+ social welfare
-+ social casework (or social case work)
-+ social service
-+ human service
-+ social development 
-+ social environment
-
-```{r exclusion1, eval=TRUE}
-exclusions.1 <- c(
-    "American Journal of Preventive Medicine", 
-    "Behavior Modification", 
-    "Brain and Cognition",
-    "Canadian Journal of Community Mental Health",
-    "Canadian Journal on Aging",
-    "Early Child Development and Care",
-    "Early Education and Development",
-    "Employee Assistance Quarterly",
-    "Evaluation and Program Planning",
-    "General Hospital Psychiatry",
-    "International Review of Social Research",
-    "Journal of Applied Behavioral Science",
-    "Journal of Applied Rehabilitation Counseling",
-    "Journal of Community & Applied Social Psychology",
-    "Journal of Health & Human Services Administration",
-    "Journal of Nonverbal Behavior",
-    "Journal of Psychosomatic Research",
-    "Learning Disabilities Research & Practice",
-    "Professional Development in Education",
-    "PROFILE Issues in Teachers' Professional Development",
-    "Psychotherapy",
-    "Systems Research and Behavioral Science",
-    "Teaching and Teacher Education",
-    "The Scientific Review of Mental Health Practice",
-    "The Clinical Supervisor",
-    "Arete: Revista de Filosofia",
-    "Arete Revista de Filosofia")
-
-ebsco.remove <- full.df[full.df$record %in% exclusions.1, ]
-ebsco.remove <- ebsco.remove[, "articleID"]
-full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
-
-rm(ebsco.remove)
-
-```
-
-```{r preprocessing, comment=NA, echo=TRUE} 
-number.of.articles <- length(which(full.df$attributes == "article"))
-range.of.years <- range(full.df$record[full.df$attributes == "pubYear"])
-```
-
-```{r}
-# Number of articles
-cat(number.of.articles)
-```
-
-```{r}
-# Range of years
-cat(range.of.years)
-```
-
-```{r echo=FALSE, comment=NA}
-unique.titles <- filter(full.df, attributes == "journal") %>%
-    group_by(record) %>%
-    summarise(
-        N = n())
-print.data.frame(unique.titles, rowNames=FALSE)
-```
-
-## Exclusions of social work publications
-
-+ Journals that did not have at least one full year of indexed records (except journals that subsequently changed titles).
-This exclusionary criterion was consistent with the working definition of a social work journal.
-
-```{r exclusion2, eval=TRUE}
-exclusions.2 <- c(
-    "Issues in Social Work Education", 
-    "Maatskaplike Werk/Social Work",
-    "Pediatric Social Work", 
-    "Critical Social Work"
-    )
-
-ebsco.remove <- full.df[full.df$record %in% exclusions.2, ]
-ebsco.remove <- ebsco.remove[, "articleID"]
-full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
-
-rm(ebsco.remove, exclusions.2)
-```
-
-## Fix journal titles
-
-Additional pre-processing was conducted on journal titles to resolve spelling errors or other minor title differences in the database.
-For example, _Social Work With Groups_ was exported as a separate journal than _Social Work with Groups_ (note the capitalization difference in the word _with_.)  We also applied a global substitution of _and_ with _&_, as this was a common source for differences.
-
-```{r echo=FALSE}
 full.df$record <- ifelse(full.df$record == 
@@
 
-```
+articles.appendData <- length(which(full.df$attributes == "article"))
+journals.appendData <- filter(full.df, attributes == "journal") %>% 
+    summarise(Unique = n_distinct(record))
 
-```{r echo=FALSE, comment=NA}
-unique.titles <- filter(full.df, attributes == "journal") %>%
-    group_by(record) %>%
-    summarise(
-        N = n())
-print.data.frame(unique.titles, rowNames=FALSE)
-```
-
-## Title merging
-
-Some social work journals changed titles over their history.
-For example, _Families in Society_ had three titles that preceded the current title:  _Social Casework_, _Journal of Social Casework_, and _The Family_.
-The database that contributed the largest number of articles to the study database indexed the majority of journal titles under the journal's current name, and provided an additional data field for the historical name.
-However, historical names from Social Science Abstracts and Social Work Abstracts were not merged with the current name.
-Thus, the last step of the data cleaning procedures was to conduct these merges.
-
-```{r titleMerge, eval=TRUE}
 full.df$record <- ifelse(full.df$record == 
@@
 full.df$record[practice.temp] <- "Reflections: Narratives of Professional Helping"
+
+exclusions.1 <- c(
+    "American Journal of Preventive Medicine", 
+    "Behavior Modification", 
+    "Brain and Cognition",
+    "Brain & Cognition",
+    "Canadian Journal of Community Mental Health",
+    "Canadian Journal on Aging",
+    "Early Child Development and Care",
+    "Early Child Development & Care",
+    "Early Education and Development",
+    "Early Education & Development", 
+    "Employee Assistance Quarterly",
+    "Evaluation and Program Planning",
+    "Evaluation & Program Planning",
+    "General Hospital Psychiatry",
+    "International Review of Social Research",
+    "Journal of Applied Behavioral Science",
+    "Journal of Applied Rehabilitation Counseling",
+    "Journal of Community & Applied Social Psychology",
+    "Journal of Health & Human Services Administration",
+    "Journal of Nonverbal Behavior",
+    "Journal of Psychosomatic Research",
+    "Learning Disabilities Research & Practice",
+    "Professional Development in Education",
+    "PROFILE Issues in Teachers' Professional Development",
+    "Psychotherapy",
+    "Systems Research and Behavioral Science",
+    "Systems Research & Behavioral Science",
+    "Teaching & Teacher Education", 
+    "Teaching and Teacher Education",
+    "The Scientific Review of Mental Health Practice",
+    "The Clinical Supervisor",
+    "Arete: Revista de Filosofia",
+    "Arete Revista de Filosofia")
+
+ebsco.remove <- full.df[full.df$record %in% exclusions.1, ]
+ebsco.remove <- ebsco.remove[, "articleID"]
+full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
+
+rm(ebsco.remove)
+
+number.of.articles <- length(which(full.df$attributes == "article"))
+number.of.journals <- filter(full.df, attributes == "journal") %>% 
+    summarise(Unique = n_distinct(record))
+
+unique.titles <- filter(full.df, attributes == "journal") %>%
+    group_by(record) %>%
+    summarise(
+        N = n())
+#print.data.frame(unique.titles, rowNames=FALSE)
+
 ```
 
-# Post-processing summary
+```{r titleMatching, echo=FALSE}
+titles <- filter(full.df, attributes == "article")
+titles$matching <- tolower(titles$record)
 
-## Revised database
+#Eliminate `the` and `a` at the beginning of sentences and after colons
+titles$matching <- gsub("^the\\s", "", titles$matching)
+titles$matching <- gsub("^a\\s", "", titles$matching)
+titles$matching <- gsub("[[:punct:]]", "", titles$matching)
+
+#Strips out white space and punctuation to ensure small differences in data 
+#entry are detected during duplicate elimination
+titles$matching <- gsub(" ","", titles$matching)
+
+duplicated.titles <- duplicated(titles$matching)
+duplicated.ID <- titles$articleID[duplicated.titles]
+full.df <- full.df[!(full.df$articleID %in% duplicated.ID), ]
+
+articles.titleMatching <- length(which(full.df$attributes == "article"))
+journals.titleMatching <- filter(full.df, attributes == "journal") %>% 
+    summarise(Unique = n_distinct(record))
+```
+
+```{r otherDocuments, echo=FALSE}
+#Identify records that were incorrectly captured in the wrangle
+#using regular expressions
+titles <- filter(full.df, attributes == "article")
+insert.1<-"[B|b]ook [R|r]eview[.:]|^[F|f]orum.+|[F|f]orum$|[C|c]ommentary|Comment.+"
+insert.2<-"^[I|i]ndex\\s[T|t]o|[I|i]ntroduction:|[I|i]ntroduction [T|t]o|\\([B|b]ook\\)"
+insert.3<-"[H|h]andbook|Volume|volumes|newsletters|[L|l]etter from"
+insert.4<-"[P|p]reface|\\([0-9]{4}-[0-9]{4}\\):|: [A|a] [R|r]esponse [T|t]o [B-Z]"
+insert.5<-"[S|s]pecial\\s[I|i]ssue|[T|t]able\\s[O|o]f\\s[C|c]ontent|\\([U|u]ndetermined"
+insert.6<-"^Book.+ | ^COMMENTARY.+ | Call\\s.+ | Contents.+ | Editor.+ | Errat.+"
+insert.7<-"^FROM\\THE.+ | ^From\\sthe\\ed.+ | Health\\s[&]\\sS.+ | ^LETTER.+ |
+             ^Letter\\sfrom.+ | ^News\\and.+ | ^Response\\sto\\s[A-Z] | Vol\\.\\s[0-9] |
+            ^Volume.+ | ^\\["
+insert<-paste(insert.1,insert.2,insert.3,insert.4,insert.5, insert.6, 
+              insert.7, sep="|")
+
+badRecords<-subset(titles, grepl(insert, record))
+badRecords.ID<-badRecords$articleID
+
+full.df <- full.df[!(full.df$articleID %in% badRecords.ID), ]
+articles.otherDocuments <- length(which(full.df$attributes == "article"))
+journals.otherDocuments <- filter(full.df, attributes == "journal") %>% 
+    summarise(Unique = n_distinct(record))
+```
+
+```{r final, comment=NA, echo=FALSE}
+titles <- filter(full.df, attributes == "article")
+journals <- filter(full.df, attributes == "journal")
+year <- filter(full.df, attributes == "pubYear")
+
+year.journal <- dplyr::intersect(year$articleID, journals$articleID)
+year.journal.titles <- dplyr::intersect(year.journal, titles$articleID)
+full.df <- full.df[full.df$articleID %in% year.journal.titles, ]
+
+exclusions.2 <- c(
+    "Issues in Social Work Education", 
+    "Maatskaplike Werk/Social Work",
+    "Pediatric Social Work", 
+    "Critical Social Work"
+    )
+
+ebsco.remove <- full.df[full.df$record %in% exclusions.2, ]
+ebsco.remove <- ebsco.remove[, "articleID"]
+full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
+
+rm(ebsco.remove, exclusions.2)
+articles.final <- length(which(full.df$attributes == "article"))
+journals.final <- filter(full.df, attributes == "journal") %>% 
+    summarise(Unique = n_distinct(record))
+```
+
+# Methods
+
+### Extraction of Article Records
+The work of Hodge and Lacasse (2011) served as an initial list of 84 core social work journals.
+This list was based on a review of a variety of sources, including An Author’s Guide to Social Work Journals (NASW Press, 1997), Thyer’s (2005) more recent listing of social work periodicals, and Genamics JournalSeek (http://journalseek.net/).
+Hodge and Lacasse (2011) examined the mission and aims of each journal, and eliminated all journals that had an inter-disciplinary focus.
+An initial search query was built using all the journal titles, limiting the results to only journal articles.
+
+To help ensure comprehensive coverage of all possible core social work journals, a subsequent search was conducted by searching the journal titles of each database using the following search specification, limiting the results to only peer-reviewed journals and journal articles.
+This subsequent query included the following search terms:
+
++ "social work"
++ "social welfare"
++ "social casework", 
++ "social service", 
++ "human  service", 
++ "social development", 
++ "social environment"
+
+These queries were used to extract articles from three major databases on the EbscoHost platform:  PsycINFO, Social Service Abstracts, and Social Work Abstracts.
+We then conducted a supplemental search of the ProQuest database that searched across an additional 46 minor databases, including (but not limited to): ERIC, Sociological Abstracts and Worldwide Political Science Abstracts.
+We limited the search to all research from 1988 to the end of 2013, representing a quarter century of social work research.
+Articles published in 2014 and 2015 were excluded because of observed delays in indexing for numerous journals.
+
+Search results were exported in series of large batches as raw text files in a generic bibliographic format.
+Article records were merged into a single file and then transformed into a structured database for subsequent data cleaning and analysis.
+This transformation was done using a set of scripts designed specifically for the R statistical programming language.
+
+# Pre-processing and cleaning of data
+
+The extraction process resulted in 36,094 article records from 117 different journals.
+The search process was designed to be overly inclusive to ensure full coverage of all possible social work journals contained in the major and minor databases.
+Thus, it was necessary to implement a series of data cleaning procedures to ensure a focus only on journal articles from peer-reviewed social work journals.
+
+The first step involved fixing journal title names because of discrepancies that occurred in the indexing process.
+For example, _British Journal of Social Work_ was extracted as a journal that was different than _The British Journal of Social Work_, and _Journal of Gay and Lesbian Social Services_ _Journal of Gay & Lesbian Social Services_.
+Some social work journals changed titles over their history.
+For example, _Families in Society_ had three titles that preceded the current title:  _Social Casework_, _Journal of Social Casework_, and _The Family_.
+The database that contributed the largest number of articles to the study database indexed the majority of journal titles under the journal's current name, and provided an additional data field for the historical name.
+However, historical names from Social Science Abstracts and Social Work Abstracts were not merged with the current name.
+Thus, the last step of the data cleaning procedures was to conduct these merges.
+
+We then excluded all non-social work journals from the search list.
+These journal titles were captured in the search because many journals from allied health disciplines (e.g., nursing and psychology) used the term “psychosocial” in the title of a special editions.
+To facilitate this process, a list of all journal titles that did not match the core list (as defined by Hodge and LaCasse) was created and distributed among the study authors.
+Study authors reviewed these candidate journal titles and discussed whether each candidate title should be retained or excluded.
+When disagreements occurred, the study authors reviewed the mission and aims of the journals, names of editorial board members, and focus of the articles.
+A consensus was reached on all journal titles, reducing the article and journal count to `r articles.appendData`  `r journals.appendData` (respectively).
+
+Because separate searches were conducted across multiple databases to help ensure comprehensive coverage due to known gaps in indexing for many social work journals, a matching algorithm was developed to identify and remove duplicate article records.
+The matching algorithm reduced the total number of article records to `r articles.titleMatching`.
+
+In the extraction process, limiters were applied to extract only journal article in order to avoid other scholarly communications from being captured, such as editorials, commentaries, book reviews, software reviews, tables of contents, obituaries, and calls for papers.
+A visual scan of the database revealed many instances in which these limiters were unsuccessful.
+Thus, a set of regular expressions were created and tested against a reduced database comprised of representative examples of communications to be excluded and articles to be retained.
+Regular expressions are special search strings used to identify specific search patterns within text.
+When the regular expression achieved > 98% sensitivity and specificity in detecting target article records, they were applied to the full database, reducing the article count to `r articles.otherDocuments`.
+
+The final step involved scanning the database to exclude article records without any information in the author, journal title, article title, or publication year fields, as well as eliminating social work journals with total article counts of < 10 for the entire 25 year window.
+This produced a database of `r articles.final` unique social work articles, and `r journals.final` journal titles.
+
+# Results
 
@@
 print.data.frame(final.list, row.names=FALSE)
+
 ```
-
-# Comparison with Hodge
-
-This section provides further comparison of the journal titles with Hodge by reporting on the _intersection_, and _differences_.
 

### 2015-03-10 dataCleaning.Rmd
Updated.
Code update
Adds chunk to datacleaning.rmd that eliminates article records that do
not have a certain number of pages.

@@
 hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
+
+#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
+#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
+#hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)
 ```
@@
 #print.data.frame(unique.titles, rowNames=FALSE)
+
+```
+
+```{r, comment=NA, echo=FALSE}
+
+#Deletes article records associated with articles that are 3 pages or less  (this can be adjusted below in   ###                                                                               this chunk)
+
+pages.df<-filter(full.df, attributes=="pages")
+pages.df$record <- gsub("p", "", pages.df$record)
+pages.df$record <- gsub("ArtID:\\s", "", pages.df$record)
+pages.df$record<-gsub("S", "", pages.df$record)
+pages.df$record <- gsub(" ", "", pages.df$record)
+
+dashes<-filter(pages.df, grepl("-", record) )
+
+splitDash<-strsplit(dashes$record, "-")
+mat  <- matrix(unlist(splitDash), ncol=2, byrow=TRUE)
+mat <- as.data.frame(mat)
+
+mat$V1<- as.character(mat$V1)
+mat$V2<- as.character(mat$V2)
+
+mat$V1<- as.numeric(mat$V1)
+mat$V2<- as.numeric(mat$V2)
+mat <-mutate(mat, record=V2-V1)
+mat<-select(mat, record)
+
+dashes<-select(dashes, -record)
+dashes.df<-cbind(dashes, mat)
+dashes.ID<-dashes.df$articleID
+
+pages.noDashes<-pages.df[!pages.df$articleID %in% dashes.ID, ]
+
+pages.df<-rbind(pages.noDashes, dashes.df)
+pages.df$record<-as.numeric(pages.df$record)
+pages.df[is.na(pages.df)] <- 0
+
+pages.remove<-filter(pages.df, record < 4)    ## Set threshold for retaining articles by number of pages
+pages.remove.ID <- pages.remove$articleID
+
+full.df <- full.df[!full.df$articleID %in% pages.remove.ID, ]
+rownames(full.df) <- NULL
+View(full.df)
+
+rm(dashes, splitDash, mat, dashes.df, dashes.ID, pages.df, pages.noDashes)
 

### 2015-03-12 dataCleaning.Rmd
Final cleanup before lockdown.

--- 2015-02-28 dataCleaning.Rmd
@@
 
-# Overview
+`r knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, comment=NA)`
 
-This document summarizes data cleaning procedures of the data file processed by the `ebscoBWR` fucntion.
-It should be noted that that `ebscoBWR` function merged the search results from the first- and second-level searches performed on the three databases (psycInfo, Social Science Abstracts, and Social Work Abstract) hosted by the EbscoPlatform.
-This function merged all the search results, transformed the data into a structured data file, and removed all duplicate article records.
-No further transformations or cleaning was performed by the `ebscoBWR` function.
-Provided below are basic descriptive summaries of the results from the full search before further cleaning.
-
-The main file for analysis is `fullDF.R`, and a separate file is just for psycInfo `psycInfoDF.R`.  The same cleaning procedures need to be performed on both data files prior to analysis.
-
-# Initialization of workspace
-
-```{r initialization_dataprocessing, warning=FALSE, message=FALSE, eval=TRUE}
-# Clear workspace
+```{r initialization_dataprocessing}
 rm(list=ls())   
-
 # Load required packages
@@
 # Read data files
-
 load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
 load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
-#load("/Users/beperron/Git/SocialWorkResearch/Data/PsycInfo.R")
 hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
-
 #load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
 #load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
-#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")
 #hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)
+
+# Load special functions
+source("/Users/beperron/Git/SocialWorkResearch/functions/appendData.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticles.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")
+
+pretty <- function(x){
+    x <- prettyNum(x,big.mark=",",scientific=F)
+    x
+    }
 ```
 
-# Combines EbscoHost and ProQUest
+```{r appendData, comment=NA, echo=FALSE}
+appendData.f()
 
-This section ... wrangles and eliminates duplicate article titles
+append.articles <- length(which(full.df$attributes == "article"))
+append.journals <- filter(full.df, attributes == "journal") %>% 
+    summarise(Unique = n_distinct(record))
 
-```{r appendData, comment=NA}
-
-#Creates variable with highest article ID from ebscohost database
-ebscoIDmax<-max(ebscoBWR.df$articleID)
-
-#Recodes article ID in ProQuest database in advance of merger with ebscohost
-proQuestBWR.df<-mutate(proQuestBWR.df, articleID=articleID+ebscoIDmax)
-
-full.df <- rbind(ebscoBWR.df, proQuestBWR.df)
-```
-
-```{r reduced, comment=NA}
-titles <- filter(full.df, attributes == "article")
-journals <- filter(full.df, attributes == "journal")
-year <- filter(full.df, attributes == "pubYear")
-
-year.journal <- dplyr::intersect(year$articleID, journals$articleID)
-year.journal.titles <- dplyr::intersect(year.journal, titles$articleID)
-
-full.df <- full.df[full.df$articleID %in% year.journal.titles, ]
-```
-
-Exclude incorrectly captured articles. 
-```{r}
-#Identify records that were incorrectly captured in the wrangle
-#using regular expressions
-insert.1<-"[B|b]ook [R|r]eview[.:]|^[F|f]orum.+|[F|f]orum$|[C|c]ommentary|Comment.+"
-insert.2<-"^[I|i]ndex\\s[T|t]o|[I|i]ntroduction:|[I|i]ntroduction [T|t]o|\\([B|b]ook\\)"
-insert.3<-"[H|h]andbook|Volume|volumes|newsletters|[L|l]etter from"
-insert.4<-"[P|p]reface|\\([0-9]{4}-[0-9]{4}\\):|: [A|a] [R|r]esponse [T|t]o [B-Z]"
-insert.5<-"[S|s]pecial\\s[I|i]ssue|[T|t]able\\s[O|o]f\\s[C|c]ontent|\\([U|u]ndetermined"
-insert.6<-"^Book.+ | ^COMMENTARY.+ | Call\\s.+ | Contents.+ | Editor.+ | Errat.+"
-insert.7<-"^FROM\\THE.+ | ^From\\sthe\\ed.+ | Health\\s[&]\\sS.+ | ^LETTER.+ |
-             ^Letter\\sfrom.+ | ^News\\and.+ | ^Response\\sto\\s[A-Z] | Vol\\.\\s[0-9] |
-            ^Volume.+ | ^\\["
-insert<-paste(insert.1,insert.2,insert.3,insert.4,insert.5, insert.6, 
-              insert.7, sep="|")
-
-badRecords<-subset(titles, grepl(insert, record))
-badRecords.ID<-badRecords$articleID
-
-full.df <- full.df[!(full.df$articleID %in% badRecords.ID), ]
-
-```
-
-Duplicate title search
-```{r}
-titles$matching <- tolower(titles$record)
-
-#Eliminate `the` and `a` at the beginning of sentences and after colons
-titles$matching <- gsub("^the\\s", "", titles$matching)
-titles$matching <- gsub("^a\\s", "", titles$matching)
-titles$matching <- gsub("[[:punct:]]", "", titles$matching)
-
-#Strips out white space and punctuation to ensure small differences in data 
-#entry are detected during duplicate elimination
-titles$matching <- gsub(" ","", titles$matching)
-
-duplicated.titles <- duplicated(titles$matching)
-duplicated.ID <- titles$articleID[duplicated.titles]
-full.df <- full.df[!(full.df$articleID %in% duplicated.ID), ]
-```
-
-# Data cleaning and pre-processing
-
-## Narrow results to past 25 years
-
-Inspection of the data indicated notable delays in indexing for the years 2014 and 2015.
-Therefore, these years were excluded from the current study.
-Thus, this study includes journals indexed through the end of 2013.
-
-```{r}
-year.25 <- as.character(c(1900:1987, 2014, 2015))
-
-temp.df <- filter(full.df, attributes == "pubYear")
-
-year.remove <- temp.df[temp.df$record %in% year.25, ]
-year.removeID <- year.remove$articleID
-
-full.df <- full.df[!(full.df$articleID %in% year.removeID), ]
-
-```
-
-```{r}
-full.df$record <- ifelse(full.df$record == 
-    "The British Journal of Social Work",          # Spelling difference
-        "British Journal of Social Work",           
-                        full.df$record)
-
-full.df$record <- ifelse(full.df$record ==
-    "Revista de Asistenta Sociala (Social Work Review)",
-        "Social Work Review",
-                        full.df$record)
-
-full.df$record <- gsub("Arete", "xxx", full.df$record)
-full.df$record <- gsub("Aret.{1,3}", "Arete", full.df$record)
-full.df$record <- gsub("xxx", "Arete", full.df$record) 
-                                      #Replaces special character       
-                                      #in Arete and preserves other formatting
-
-full.df$record <- ifelse(full.df$record ==
-    "Journal of Gay and Lesbian Social Services",     #Spelling difference
-        "Journal of Gay & Lesbian Social Services",
-                        full.df$record)
-
-full.df$record <- ifelse(full.df$record ==
-    "Canadian Social Work Review/Revue canadienne de service social",
-        "Canadian Social Work Review",
-                        full.df$record)
-
-full.df$record <- ifelse(full.df$record ==
-    "INDIAN JOURNAL OF SOCIAL WORK",                    #Spelling difference
-        "Indian Journal of Social Work",
-                      full.df$record)
-
-full.df$record <- ifelse(full.df$record ==
-    "The Indian Journal of Social Work",              #Spelling difference
-        "Indian Journal of Social Work",
-                            full.df$record)
-
-full.df$record <- ifelse(full.df$record ==
-    "Asia Pacific Journal of Social Work",              #Spelling difference
-        "Asia Pacific Journal of Social Work and Development",
-                            full.df$record)
-
-full.df$record <- ifelse(full.df$record ==
-    "Social Work & Society",                           #Spelling difference
-        "Social Work and Society",
-                            full.df$record)
-
-full.df$record <- ifelse(full.df$record ==
-    "Journal of Social Work in Disability & Rehabilitation",
-        "Journal of Social Work in Disability and Rehabilitation", 
-                            full.df$record)           #Spelling difference
-
-full.df$record <- ifelse(full.df$record ==
-    "Hong Kong Journal of Social Work",
-        "The Hong Kong Journal of Social Work", 
-                            full.df$record)           #Spelling difference
-
-full.df$record <- ifelse(full.df$record ==
-    "The Journal of Baccalaureate Social Work",
-        "Journal of Baccalaureate Social Work", 
-                            full.df$record)           #Spelling difference
-
-full.df$record <- ifelse(full.df$record ==
-    "Journal of Practice Teaching in Health and Social Work",
-        "Journal of Practice Teaching in Social Work and Health", 
-                            full.df$record)           #Spelling difference
-
-full.df$record <- ifelse(full.df$record ==
-    "Professional Development: The International Journal of Continuing Social Work Education",
-        "Professional Development", 
-                            full.df$record)           #Spelling difference
-
-dim(filter(full.df, attributes == "pubYear"))
-dim(filter(full.df, attributes == "article"))
-dim(filter(full.df, attributes == "journal"))
-
-```
-
-## Initial descriptive summary
-
-```{r preprocessing, comment=NA, echo=TRUE} 
-number.of.articles <- length(which(full.df$attributes == "article"))
-range.of.years <- range(full.df$record[full.df$attributes == "pubYear"])
-```
-
-```{r}
-# Number of articles
-cat(number.of.articles)
-```
-
-```{r}
-# Range of years
-cat(range.of.years)
-```
-
-## Exclusion of journals not meeting supplemental search terms
-
-The search for journals involved a two-stage process.
-It began by extracting all records from journals based on the social work journal list of Hodge and L (APA cite).
-Journals were excluded if they did not contain one of the major search terms from the supplemental list.
-The majority of these journals were captured in the supplemental search query because the journal used one of the supplemental search terms in a special issue.
-The mission and scope of journals were also reviewed when it was unclear whether the journal was specific to social work research (e.g., _The Clinical Supervisor_).
-The supplemental search terms included:
-
-+ social work
-+ social welfare
-+ social casework (or social case work)
-+ social service
-+ human service
-+ social development 
-+ social environment
-
-```{r exclusion1, eval=TRUE}
-exclusions.1 <- c(
-    "American Journal of Preventive Medicine", 
-    "Behavior Modification", 
-    "Brain and Cognition",
-    "Canadian Journal of Community Mental Health",
-    "Canadian Journal on Aging",
-    "Early Child Development and Care",
-    "Early Education and Development",
-    "Employee Assistance Quarterly",
-    "Evaluation and Program Planning",
-    "General Hospital Psychiatry",
-    "International Review of Social Research",
-    "Journal of Applied Behavioral Science",
-    "Journal of Applied Rehabilitation Counseling",
-    "Journal of Community & Applied Social Psychology",
-    "Journal of Health & Human Services Administration",
-    "Journal of Nonverbal Behavior",
-    "Journal of Psychosomatic Research",
-    "Learning Disabilities Research & Practice",
-    "Professional Development in Education",
-    "PROFILE Issues in Teachers' Professional Development",
-    "Psychotherapy",
-    "Systems Research and Behavioral Science",
-    "Teaching and Teacher Education",
-    "The Scientific Review of Mental Health Practice",
-    "The Clinical Supervisor",
-    "Arete: Revista de Filosofia",
-    "Arete Revista de Filosofia")
-
-ebsco.remove <- full.df[full.df$record %in% exclusions.1, ]
-ebsco.remove <- ebsco.remove[, "articleID"]
-full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
-
-rm(ebsco.remove)
-
-```
-
-```{r preprocessing, comment=NA, echo=TRUE} 
-number.of.articles <- length(which(full.df$attributes == "article"))
-range.of.years <- range(full.df$record[full.df$attributes == "pubYear"])
-```
-
-```{r}
-# Number of articles
-cat(number.of.articles)
-```
-
-```{r}
-# Range of years
-cat(range.of.years)
-```
-
-```{r echo=FALSE, comment=NA}
 unique.titles <- filter(full.df, attributes == "journal") %>%
@@
         N = n())
-print.data.frame(unique.titles, rowNames=FALSE)
 ```
 
-## Exclusions of social work publications
-
-+ Journals that did not have at least one full year of indexed records (except journals that subsequently changed titles).
-This exclusionary criterion was consistent with the working definition of a social work journal.
-
-```{r exclusion2, eval=TRUE}
-exclusions.2 <- c(
-    "Issues in Social Work Education", 
-    "Maatskaplike Werk/Social Work",
-    "Pediatric Social Work", 
-    "Critical Social Work"
-    )
-
-ebsco.remove <- full.df[full.df$record %in% exclusions.2, ]
-ebsco.remove <- ebsco.remove[, "articleID"]
-full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
-
-rm(ebsco.remove, exclusions.2)
+```{r shortArticles, comment=NA, echo=FALSE, warning=FALSE}
+shortArticles.f()
 ```
 
-## Fix journal titles
+```{r titleMatching, echo=FALSE}
+titleMatching.f()
 
-Additional pre-processing was conducted on journal titles to resolve spelling errors or other minor title differences in the database.
-For example, _Social Work With Groups_ was exported as a separate journal than _Social Work with Groups_ (note the capitalization difference in the word _with_.)  We also applied a global substitution of _and_ with _&_, as this was a common source for differences.
+articles.titleMatching <- length(which(full.df$attributes == "article"))
 
-```{r echo=FALSE}
-full.df$record <- ifelse(full.df$record == 
-        "Social Work & Social Sciences Review",     # Spelling difference
-        "Social Work and Social Sciences Review", 
-                        full.df$record)
-
-full.df$record <- ifelse(full.df$record == 
-        "Social Work with Groups",                  # Spelling difference
-        "Social Work With Groups", 
-                        full.df$record)
-
-full.df$record <- ifelse(full.df$record == 
-        "Journal of Sociology & Social Welfare",    # Spelling difference
-        "Journal of Sociology and Social Welfare",  
-                        full.df$record)
-
-full.df$record <- ifelse(full.df$record == 
-    "The British Journal Social Work",          # Spelling difference
-        "British Journal of Social Work",           
-                        full.df$record)
-
-#shortens Professional Development
-full.df$record <- ifelse(full.df$attributes == "journal",
-        gsub(":.+", "", full.df$record), 
-        full.df$record)
-
-#shortens Canadian Social Work review by eliminating foreign title and is
-#automatically combined with other short spelling
-full.df$record <- ifelse(full.df$attributes == "journal",
-        gsub("(/R){1}.+", "", full.df$record), 
-        full.df$record)
-
-# shortens Contemporary Rural Social Work
-full.df$record <- ifelse(full.df$attributes == "journal",
-        gsub("\\s\\(.+", "", full.df$record), 
-        full.df$record)
-
-full.df$record <- ifelse(full.df$attributes == "journal", 
-      gsub("and", "&", full.df$record), full.df$record)
-
+journals.titleMatching <- filter(full.df, attributes == "journal") %>%
+        summarise(Unique = n_distinct(record))
 ```
 
-```{r echo=FALSE, comment=NA}
-unique.titles <- filter(full.df, attributes == "journal") %>%
-    group_by(record) %>%
-    summarise(
-        N = n())
-print.data.frame(unique.titles, rowNames=FALSE)
+```{r otherDocuments, echo=FALSE}
+otherDocuments.f()
+articles.otherDocuments <- length(which(full.df$attributes == "article"))
+journals.otherDocuments <- filter(full.df, attributes == "journal") %>% 
+    summarise(Unique = n_distinct(record))
 ```
 
-## Title merging
-
-Some social work journals changed titles over their history.
-For example, _Families in Society_ had three titles that preceded the current title:  _Social Casework_, _Journal of Social Casework_, and _The Family_.
-The database that contributed the largest number of articles to the study database indexed the majority of journal titles under the journal's current name, and provided an additional data field for the historical name.
-However, historical names from Social Science Abstracts and Social Work Abstracts were not merged with the current name.
-Thus, the last step of the data cleaning procedures was to conduct these merges.
-
-```{r titleMerge, eval=TRUE}
-full.df$record <- ifelse(full.df$record == 
-    "The British Journal of Pyschiatric Social Work" | 
-        full.df$record == 
-    "The British Journal of Social Work", # Old
-        "British Journal of Social Work",           # New title
-                        full.df$record)
-
-full.df$record <- ifelse(full.df$record == 
-        "Computers in Human Services",              # Old title
-        "Journal of Technology in Human Services",  # New title
-                        full.df$record)
-
-full.df$record <- ifelse(full.df$record == 
-        "The Family" | full.df$record ==                    # Old title
-        "Journal of Social Casework" | full.df$record ==    # Old title
-        "Social Casework",                                  # Old title
-        "Families in Society",                              # New title
-                        full.df$record)
-
-full.df$record <- ifelse(full.df$record == 
-        "Social Work in Education",                 # Old title
-        "Children & Schools",                       # New title
-                    full.df$record)
-
-full.df$record <- ifelse(full.df$record == 
-        "Journal of Independent Social Work" | full.df$record ==    # New title
-        "Journal of Analytic Social Work",                          # Old title
-        "Psychoanalytic Social Work",                               # Old title
-                full.df$record)
-
-full.df$record <- ifelse(full.df$record ==
-        "Journal of Practice Teaching in Social Work and Practice", #Old title
-        "Journal of Practice Teaching in Social Work and Health",   #New title
-                    full.df$record)
-
-# Journals were originally merged after suffixes were eliminated (after the
-# colon).  Thus, Practice: Social Work in Action  (new title) was shortened to
-# Practice (old title).  This section resolves two of these issues to be
-# consistent in the comparison with Hodge.
-
-practice.temp <- grep("^Practice$", full.df$record)
-full.df$record[practice.temp] <- "Practice: Social Work in Action"
-
-practice.temp <- grep("^Reflections$", full.df$record)
-full.df$record[practice.temp] <- "Reflections: Narratives of Professional Helping"
+```{r final, comment=NA, echo=FALSE}
+fewArticles.f()
+articles.final <- length(which(full.df$attributes == "article"))
+journals.final <- filter(full.df, attributes == "journal") %>% 
+    summarise(Unique = n_distinct(record))
 ```
 
-# Post-processing summary
+# Methods
 
-## Revised database
+### Extraction of article records
 
-This section provides a summary of the revised database after the initial processing with the `ebscoBWR` function and the subsequent data cleaning.
-An additional code is included in this summary to indicate whether the journal title overlaps with the list of Hodge (indicated by *H*).
+Our list of social work journals was guided by the work of Hodge and Lacasse (2011).
+More specifically, Hodge and Lacasse (2011) identified 84 disciplinary social work journals based on a variety of sources, including _An Author’s Guide to Social Work Journals_ (NASW Press, 1997), Thyer’s (2005) more recent listing of social work periodicals, and Genamics JournalSeek (http://journalseek.net/).
+Hodge and Lacasse (2011) examined the mission and aims of each journal, and eliminated journals that were specific to another field or had an had an inter-disciplinary focus.
+For the current study, our primary search query included all journal titles in this list.
+
+To help ensure comprehensive coverage of all possible core social work journals, we created a supplemental search query that extracted journal titles with any of the following terms:
+
++ "social work"
++ "social welfare"
++ "social casework"
++ "social service" 
++ "human  service" 
++ "social development" 
++ "social environment"
+
+Using this search queries, we extract journal article recrods from three major databases on the EbscoHost platform:  PsycINFO, Social Service Abstracts, and Social Work Abstracts.
+Because of known gaps in indexing in databases (Holden, Barker, Kuppens, Rosenberg & LeBreton, 2014; Holden, Barker, Covert-Vail, Rosenberg, & Cohen, 2009), we also searched ProQuest, which linked to an additional 46 minor databases, including (but not limited to): ERIC, Sociological Abstracts and Worldwide Political Science Abstracts.
+In every search, we used a filter in attempt to extract only article records that were classified as _journal articles_, thereby excluding other forms of scholarly communication that was not relevant to the current study (e.g., book reviews, editorials, obituaries, etc.).
+We limited the timeframe to a 25 year period, from 1988 to 2013 (inclusive).
+Articles published in years 2014 and 2015 were excluded because of delays in indexing.
+Search results were exported in batches of article records based on the restrictions of the platform.
+Article records were text files in a _generic bibliographic format_.
+The article records contained various meta-data based on the database from which the article record was extracted.
+Meta-data include (but are not limited to):  article title, journal title, publication year, author name(s), author affiliation(s), abstract, keywords, methodological classification, funding source, location of study, subject groups, digital object identifier (DOI), number of references, number of pages, etc.
+These files were post-processed into a structured database using a set of scripts written in the R statistical programming language.
+The initial search resulted in 36,094 article records from 117 different journals.
+
+The search queries were purposefully specified to be overly inclusive to ensure full coverage of all possible social work journals contained in the major and minor databases.
+Additionally, a visual inspection of the article records revealed problems in the original indexing of articles that requires subsequent data cleaning.
+Thus, our data cleaning procedures focused separately on journal titles and article records.
+
+### Data cleaning: Journal titles
+
+The first step of data cleaning involved fixing journal title names due to discrepant errors in indexing.
+For example, _Journal of Gay and Lesbian Social Services_ was indexed as a journal separate from _Journal of Gay & Lesbian Social Services_ (use of "and" vs.
+"&").
+Other examples involved journals indexed with and without subtitles, or journals with and without the word "The" at the beginning of the title.
+Additionally, some journals changed titles over their history.
+For example, _Journal of Technnology in Human Services_ is formerly known as _Computers in Human Services_.
+In these situations, the former titles were merged with the current titles.
+
+Many journals from allied health disciplines used one of the supplemental search terms in special editions, which were also included in the journal title.
+Thus, many non-social work journals were captured in the extraction process.
+To resolve this issue, we created a list of all journal titles that were not part of the core list defined by Hodge and Lacasse (2011).
+Study authors reviewed these journal titles and discussed whether each candidate title should be retained or excluded.
+When disagreements occurred, the study authors reviewed the mission and aims of the journals, names of editorial board members, and focus of the articles.
+A consensus was reached on all journal titles to be excluded and retained.
+After these procedures, the number of article records and journal titles was reduced to `r pretty(append.articles)` and `r append.journals` (respectively).
+
+### Data cleaning:  Article records
+
+Our search procedures involved the use of three major databased and 46 minor databases, which resulted in some duplication of article records.
+Thus, a matching algorithm was constructed to identify and remove all duplicate article records.
+As previously noted, the filtering of only journal articles was not successful due to errors in the original indexing.
+Thus, other scholarly communications were captured in the extractio process.
+These other scholarly communications were readily identified due to specific patterns in the titles, such as the terms "Book Review," "From the Editor," and "Obituary."  Given the number of article records in the database, it was not feasbile to manually extract these recrods.
+Instead, we created a separate database with representative examples of article records that we wanted to extract.
+We also added representative examples of article records to be retained.
+We then wrote a series of _regular expressions_ to extract the problematic article records.
+Regular expressions are a sequence of characters that form search patterns, allowing extraction of records that match the specified pattern.
+In other words, it is a more sophisticated implementation of the search function common to all major word processors.
+We tested our regular expressions on the test database, achieving > 95% accuracy with regard to retaining and extracting article records.
+These regular expressions were then applied to the full database.
+We then excluded article records if they were missing essential meta-data, including author name(s), journal title, article title, and publication field.
+As an additional requirement, we required all articles to be $\geq 3$ pages in length.
+Finally, we eliminated all social work journals with total article counts of < 10 for the enitre 25 year window (_Issues in Social Work Education_, _Maatskaplike Werk/Social Work_, _Pediatric Social Work_, and _Critical Social Work_).
+These cleaning procedures resulted in a final database of `r pretty(articles.final)`  and `r journals.final`.
+
+### Data quality checks
+
+We performed a variety of checks on the final database.
+Because the size of the database, it was not feasible to manually inspect all records.
+Thus, we randomly sampled article records from the database and cross-checked the data we procured with the information listed with the journal's homepage.
+We also inspected a scatter plot of the number of article records for each journal by the number of years the journal appeared within the 25 window timeframe.
+Journals that exhibited significant deviation from the regression line were inspected to ensure that our cleaning procedures did not systematically exclude article records or retain other scholarly communications.
+All observed discrepancies were verified as differences in journals actual publication output.
+Finally, we also made checks of number of journal article records for various journals indexed in the _Web of Science_.
+Although the counts were close -- i.e., within 10% -- similar indexing problems observed from our record extraction were also observed in the _Web of Science_ database, such as misclassification of book reviews as journal articles.
+Thus, we are unable to quantify the actual amount of error in our database is due to problems in indexing.
+At the same time, we are relying on the same source of data that social work researchers use to inform their work.
+Too much cleaning and post-processing of the search results can give rise to validity issues because social work researchers are using an information source that contain the errors we have attempted to eliminate.
+The issue of reliability and validity are given further attention in the discussion section of this study.
+
+\newpage
 
@@
 final.list <- cbind(n.so.yr, H)
+print.data.frame(final.list, row.names=FALSE)
 
-print.data.frame(final.list, row.names=FALSE)
 ```
 
-# Comparison with Hodge
+\newpage
 
-This section provides further comparison of the journal titles with Hodge by reporting on the _intersection_, and _differences_.
+```{r message=FALSE, warning=FALSE}
+cor.data <- select(final.list, first, last, n) %>%
+            mutate(no.years = as.numeric(last) - as.numeric(first))
 
-## Intersection
+ggplot(cor.data, aes(x = no.years, y = n)) + 
+            geom_point(shape = 1) + 
+            geom_smooth() + 
+            xlab("Years") + 
+            ylab("Number of articles")
+```
 
-This list shows which journal titles are common to both lists.
+\newpage
 
-```{r}
+```{r intersection}
 unique.swHistory <- filter(full.df, attributes == "journal") %>%
@@
 
-```{r}
-print(sort(hodge.swHistory.intersect))
-```
-
 ## Differences
 
-This list shows the articles on Hodge but not the current study.
+Articles on Hodge and Lacasse (2011) but not in the current study.
 
@@
 ```
-This list shows the articles on the current study but not on Hodge.
-
-```{r}
-print(sort(swHistory.hodge.diff))
-```
-
-## Descriptive summary of records
-
-```{r comment=NA, echo=TRUE} 
-number.of.articles <- length(which(full.df$attributes == "article"))
-range.of.years <- range(full.df$record[full.df$attributes == "pubYear"])
-```
-
-```{r}
-# Number of articles
-cat(number.of.articles)
-```
-
-```{r}
-# Range of years
-cat(range.of.years)
-```
-
-```{r}
-cor.data <- select(final.list, first, last, n) %>%
-            mutate(no.years = as.numeric(last) - as.numeric(first))
-
-ggplot(cor.data, aes(x = no.years, y = n)) + 
-            geom_point(shape = 1) + 
-            geom_smooth() + 
-            xlab("Years") + 
-            ylab("Number of articles")
-
-cor(cor.data$no.years, cor.data$n)
-```
-
-The following evaluation argument in the chunk is set to FALSE.
-Set this function to TRUE to process CSV files of the target journals for inspection.
-CSV files are named by the journal title.
-Be sure to use the exact spelling of the journal as it is contained in the data files.
-Set the other arguments to TRUE if you want additional fields to be included.
-Please note that it will save the files to your current working directory, which is not specified in this Markdown document.
 
@@
     journal.article.df <- full.df[target.ID, ]
+    journal.article.df <- filter(journal.article.df, attributes == "article")
+    journal.article.df <- arrange(journal.article.df, record)
     if(keyword == FALSE){journal.article.df <- filter(journal.article.df, attributes != "keyWord")}
@@
 
-journalArticleFinder.f("Research on Social Work Practice")
-journalArticleFinder.f("Social Work")
+journalArticleFinder.f("Journal of Gerontological Social Work")
+#journalArticleFinder.f("Social Work")
 

### 2015-03-12 functions/appendData.R

@@ -1,0 +1,226 @@
+appendData.f <- function(){
+    # Combines EbscoHost and ProQUest
+
+    #Creates variable with highest article ID from ebscohost database
+    ebscoIDmax<-max(ebscoBWR.df$articleID)
+
+    #Recodes article ID in ProQuest database in advance of merger with ebscohost
+    proQuestBWR.df<-mutate(proQuestBWR.df, articleID=articleID+ebscoIDmax)
+
+    full.df <- rbind(ebscoBWR.df, proQuestBWR.df)
+
+
+    year.25 <- as.character(c(1900:1987, 2014, 2015))
+
+    temp.df <- filter(full.df, attributes == "pubYear")
+
+    year.remove <- temp.df[temp.df$record %in% year.25, ]
+    year.removeID <- year.remove$articleID
+
+    full.df <- full.df[!(full.df$articleID %in% year.removeID), ]
+
+    full.df$record <- ifelse(full.df$record ==
+                                 "The British Journal of Social Work",          # Spelling difference
+                             "British Journal of Social Work",
+                             full.df$record)
+
+    full.df$record <- ifelse(full.df$record ==
+                                 "Revista de Asistenta Sociala (Social Work Review)",
+                             "Social Work Review",
+                             full.df$record)
+
+    full.df$record <- gsub("Arete", "xxx", full.df$record)
+    full.df$record <- gsub("Aret.{1,3}", "Arete", full.df$record)
+    full.df$record <- gsub("xxx", "Arete", full.df$record)
+    #Replaces special character
+    #in Arete and preserves other formatting
+
+    full.df$record <- ifelse(full.df$record ==
+                                 "Journal of Gay and Lesbian Social Services",     #Spelling difference
+                             "Journal of Gay & Lesbian Social Services",
+                             full.df$record)
+
+    full.df$record <- ifelse(full.df$record ==
+                                 "Canadian Social Work Review/Revue canadienne de service social",
+                             "Canadian Social Work Review",
+                             full.df$record)
+
+    full.df$record <- ifelse(full.df$record ==
+                                 "INDIAN JOURNAL OF SOCIAL WORK",                    #Spelling difference
+                             "Indian Journal of Social Work",
+                             full.df$record)
+
+    full.df$record <- ifelse(full.df$record ==
+                                 "The Indian Journal of Social Work",              #Spelling difference
+                             "Indian Journal of Social Work",
+                             full.df$record)
+
+    full.df$record <- ifelse(full.df$record ==
[…]

### 2015-03-12 functions/fewArticles.R

@@ -1,0 +1,21 @@
+fewArticles.f <- function(){
+
+    titles <- filter(full.df, attributes == "article")
+    journals <- filter(full.df, attributes == "journal")
+    year <- filter(full.df, attributes == "pubYear")
+
+    year.journal <- dplyr::intersect(year$articleID, journals$articleID)
+    year.journal.titles <- dplyr::intersect(year.journal, titles$articleID)
+    full.df <- full.df[full.df$articleID %in% year.journal.titles, ]
+
+    exclusions.2 <- c(
+        "Issues in Social Work Education",
+        "Maatskaplike Werk/Social Work",
+        "Pediatric Social Work",
+        "Critical Social Work"
+    )
+
+    ebsco.remove <- full.df[full.df$record %in% exclusions.2, ]
+    ebsco.remove <- ebsco.remove[, "articleID"]
+    full.df <<- full.df[!(full.df$articleID %in% ebsco.remove),]
+}

### 2015-03-12 functions/otherDocuments.R

@@ -1,0 +1,24 @@
+#Identify records that were incorrectly captured in the wrangle
+#using regular expressions
+
+otherDocuments.f <- function(){
+titles <- filter(full.df, attributes == "article")
+
+insert.1<-"[B|b]ook [R|r]eview[.:]|^[F|f]orum.+|[F|f]orum$|[C|c]ommentary|Comment.+"
+insert.2<-"^[I|i]ndex\\s[T|t]o|[I|i]ntroduction:|[I|i]ntroduction [T|t]o|\\([B|b]ook\\)"
+insert.3<-"[H|h]andbook|Volume|volumes|newsletters|[L|l]etter from"
+insert.4<-"[P|p]reface|\\([0-9]{4}-[0-9]{4}\\):|: [A|a] [R|r]esponse [T|t]o [B-Z]"
+insert.5<-"[S|s]pecial\\s[I|i]ssue|[T|t]able\\s[O|o]f\\s[C|c]ontent|\\([U|u]ndetermined"
+insert.6<-"^Book.+ | ^COMMENTARY.+ | Call\\s.+ | Contents.+ | Editor.+ | Errat.+"
+insert.7<-"^FROM\\THE.+ | ^From\\sthe\\ed.+ | Health\\s[&]\\sS.+ | ^LETTER.+ |
+             ^Letter\\sfrom.+ | ^News\\and.+ | ^Response\\sto\\s[A-Z] | Vol\\.\\s[0-9] |
+            ^Volume.+ | ^\\["
+
+insert<-paste(insert.1,insert.2,insert.3,insert.4,insert.5, insert.6,
+              insert.7, sep="|")
+
+badRecords<-subset(titles, grepl(insert, record))
+badRecords.ID<-badRecords$articleID
+
+full.df <<- full.df[!(full.df$articleID %in% badRecords.ID), ]
+}

### 2015-03-12 functions/shortArticles.R

@@ -1,0 +1,42 @@
+#Deletes article records associated with articles that are 3 pages or less  (this can be adjusted below in   ###                                                                               this chunk)
+shortArticles.f <- function(){
+    pages.df<-filter(full.df, attributes=="pages")
+    pages.df$record <- gsub("p", "", pages.df$record)
+    pages.df$record <- gsub("ArtID:\\s", "", pages.df$record)
+    pages.df$record<-gsub("S", "", pages.df$record)
+    pages.df$record <- gsub(" ", "", pages.df$record)
+
+    dashes<-filter(pages.df, grepl("-", record) )
+
+    splitDash<-strsplit(dashes$record, "-")
+    mat  <- matrix(unlist(splitDash), ncol=2, byrow=TRUE)
+    mat <- as.data.frame(mat)
+
+    mat$V1<- as.character(mat$V1)
+    mat$V2<- as.character(mat$V2)
+
+    mat$V1<- as.numeric(mat$V1)
+    mat$V2<- as.numeric(mat$V2)
+    mat <-mutate(mat, record=V2-V1)
+    mat<-select(mat, record)
+
+    dashes<-select(dashes, -record)
+    dashes.df<-cbind(dashes, mat)
+    dashes.ID<-dashes.df$articleID
+
+    pages.noDashes<-pages.df[!pages.df$articleID %in% dashes.ID, ]
+
+    pages.df<-rbind(pages.noDashes, dashes.df)
+    pages.df$record<-as.numeric(pages.df$record)
+    pages.df[is.na(pages.df)] <- 0
+
+    pages.remove<-filter(pages.df, record < 3)    ## Set threshold for retaining articles by number of pages
+    pages.remove.ID <- pages.remove$articleID
+
+    full.df <- full.df[!full.df$articleID %in% pages.remove.ID, ]
+    rownames(full.df) <- NULL
+    full.df <<- full.df
+
+
+    rm(dashes, splitDash, mat, dashes.df, dashes.ID, pages.df, pages.noDashes)
+}

### 2015-03-17 dataCleaning.Rmd
Updated figures.

@@
 
+```{r finalList, comment=NA, echo=FALSE}
+unique.titles <- filter(full.df, attributes == "journal") %>%
+    group_by(record) %>%
+    summarise(N = n())
+
+unique.titles <- filter(full.df, attributes == "journal") %>%
+    group_by(record) %>%
+    mutate(Hodge.list = ifelse(record %in% hodge == TRUE, 1, 0)) %>%
+    summarise(N = n(), 
+              Hodge.list = max(Hodge.list)) %>%
+    mutate(Hodge = ifelse(Hodge.list == 1, "Y", "N"))
+
+n.so.yr <- filter(full.df, attributes == "journal" | attributes == "pubYear")
+
+n.so <- filter(full.df, attributes == "journal") %>% mutate(title = record) %>% 
+        select(-attributes, -record)
+
+n.yr <- filter(full.df, attributes == "pubYear") %>% mutate(year = record ) %>% 
+        select(-attributes, -record)
+
+n.so.yr <- left_join(n.so, n.yr) %>%
+    group_by(title) %>%
+    summarise(first = min(year), last = max(year), n = n()) %>%
+    arrange(title)
+
+H <- unique.titles$Hodge
+
+final.list <- cbind(n.so.yr, H)
+```
+
+```{r plotArticleCount}
+n.articles.year <- filter(full.df, attributes == "pubYear") 
+year.split <- split(n.articles.year, n.articles.year$record)
+year.count <- unlist(lapply(year.split, nrow))
+year.count <- year.count[order(names(year.count))]
+years <- names(year.count)
+
+articles.year.df <- data.frame(years, year.count)
+rownames(articles.year.df) <- NULL
+
+plot.article.count <- ggplot(articles.year.df, aes(as.factor(years), 
+                    y = year.count, group=1)) + 
+    geom_line(colour="black") +
+    #geom_point(colour="red") + 
+    theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
+    xlab("Year") + 
+    ylab("Number of articles") + 
+    ggtitle("Number of Articles Published Over Time") +
+    scale_x_discrete(breaks=c(seq(1988, 2013, 2))) +
+    scale_y_continuous(breaks = c(seq(0, 2500, 200))) +
+    geom_smooth()
+```
+
+```{r plotJournalCount}
+n.journals.year <- filter(full.df, attributes == "journal") %>%
+    select(articleID, record)
+
+n.year <- filter(full.df, attributes == "pubYear") %>%
+    select(articleID, record)
+
+n.journals.year <- left_join(n.journals.year, n.year, by = "articleID", copy=TRUE) %>%
+    group_by(record.y) %>%
+    summarise(Journal.count = n_distinct(record.x))
+
+plot.journal.count <- ggplot(n.journals.year, aes(as.factor(record.y), 
+                    y = Journal.count, group=1)) + 
+    geom_line(colour="black") +
+    #geom_point(colour="red") + 
+    theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
+    xlab("Year") + 
+    ylab("Number of journals") + 
+    ggtitle("Number of Social Work Journals Over Time") +
+    scale_x_discrete(breaks=c(seq(1988, 2013, 2))) +
+    scale_y_continuous(breaks = c(seq(0, 100, 10))) +
+    geom_smooth()
+```
+
+```{r plotAuthorCount}
+
+year.df <- full.df %>%
+        filter(attributes == "pubYear") %>%
+        select(id = articleID, pubYear = record)
+
+authors.df <- full.df %>%
+        filter(attributes == "author") %>%
+        select(id = articleID, author = record)
+
+n_authors <- authors.df %>%
+        group_by(id) %>%
+        summarise(n=n())
+
+n_authors <- n_authors%>% 
+        left_join(year.df) %>%
+        group_by(pubYear) %>%
+        mutate(n = as.numeric(n)) %>%
+        summarise(median.n = median(n),
+                  average.n = mean(n),
+                  min.n = min(n),
+                  max.n = max(n),
+                  std.dev  = sd(n) )
+
+plot.author.count <- ggplot(n_authors, aes(as.factor(pubYear), y=median.n, group=1)) +  
+    geom_ribbon(aes(ymin = average.n-std.dev, ymax=average.n+std.dev), colour="lightblue", fill="lightblue", alpha=.40) +
+    geom_line(colour="black") + 
+    ylab("Number of authors") +
+    xlab("Publication year") +
+    ggtitle("Number of Authors per Article Over Time") +
+    theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
+    scale_x_discrete(breaks=c(seq(1988, 2013, 2))) +
+    geom_smooth()
+```
+
 # Methods
@@
 Finally, we eliminated all social work journals with total article counts of < 10 for the enitre 25 year window (_Issues in Social Work Education_, _Maatskaplike Werk/Social Work_, _Pediatric Social Work_, and _Critical Social Work_).
-These cleaning procedures resulted in a final database of `r pretty(articles.final)`  and `r journals.final`.
+These cleaning procedures resulted in a final database of `r pretty(articles.final)` articles and `r journals.final` journals.
 
@@
 
+# Results
+
 \newpage
 
-```{r echo=FALSE, comment=NA}
-unique.titles <- filter(full.df, attributes == "journal") %>%
+```{r finalArticleListecho=FALSE, comment=NA}
+print.data.frame(final.list, row.names=FALSE)
+```
+
+\newpage
+
+```{r}
+plot.author.count
+```
+
+\newpage
+
+```{r}
+plot.article.count
+```
+
+\newpage
+
+```{r}
+plot.journal.count
+```
+
+```{r}
+LO.df <- filter(full.df, attributes == "location") %>%
          group_by(record) %>%
-    summarise(N = n())
-
-unique.titles <- filter(full.df, attributes == "journal") %>%
-    group_by(record) %>%
-    mutate(Hodge.list = ifelse(record %in% hodge == TRUE, 1, 0)) %>%
-    summarise(N = n(), 
-              Hodge.list = max(Hodge.list)) %>%
-    mutate(Hodge = ifelse(Hodge.list == 1, "Y", "N"))
-
-n.so.yr <- filter(full.df, attributes == "journal" | attributes == "pubYear")
-
-n.so <- filter(full.df, attributes == "journal") %>% mutate(title = record) %>% 
-        select(-attributes, -record)
-
-n.yr <- filter(full.df, attributes == "pubYear") %>% mutate(year = record ) %>% 
-        select(-attributes, -record)
-
-n.so.yr <- left_join(n.so, n.yr) %>%
-    group_by(title) %>%
-    summarise(first = min(year), last = max(year), n = n()) %>%
-    arrange(title)
-
-H <- unique.titles$Hodge
-
-final.list <- cbind(n.so.yr, H)
-print.data.frame(final.list, row.names=FALSE)
+         summarise(Country = unique(record),
+                   N = n()) %>%
+        arrange(desc(N)) %>% 
+        select(-record)
 
@@
 
-```{r message=FALSE, warning=FALSE}
-cor.data <- select(final.list, first, last, n) %>%
-            mutate(no.years = as.numeric(last) - as.numeric(first))
-
-ggplot(cor.data, aes(x = no.years, y = n)) + 
-            geom_point(shape = 1) + 
-            geom_smooth() + 
-            xlab("Years") + 
-            ylab("Number of articles")
-```
-
-\newpage
-
+# Appendix A
 ```{r intersection}
@@
 
-## Differences
-
 Articles on Hodge and Lacasse (2011) but not in the current study.
@@
 print(sort(hodge.swHistory.diff))
+```
+
+```{r message=FALSE, warning=FALSE, eval=FALSE}
+cor.data <- select(final.list, first, last, n) %>%
+            mutate(no.years = as.numeric(last) - as.numeric(first))
+
+ggplot(cor.data, aes(x = no.years, y = n)) + 
+            geom_point(shape = 1) + 
+            geom_smooth() + 
+            xlab("Years") + 
+            ylab("Number of articles")
 ```

### 2015-03-20 dataCleaning.Rmd
Major plotting updates.

@@
 library(dplyr)
+library(gridExtra)
 
@@
 final.list <- cbind(n.so.yr, H)
+final.list <- arrange(final.list, desc(n))
 ```
@@
     #geom_point(colour="red") + 
-    theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
+    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8), title = element_text(size = 10), plot.title=element_text(size=10)) + 
     xlab("Year") + 
-    ylab("Number of articles") + 
-    ggtitle("Number of Articles Published Over Time") +
-    scale_x_discrete(breaks=c(seq(1988, 2013, 2))) +
+    ylab("Articles") + 
+    ggtitle("A. Number of Articles by Year") +
+    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
     scale_y_continuous(breaks = c(seq(0, 2500, 200))) +
-    geom_smooth()
+    annotate("rect", xmin = 2008-1989+1, xmax =  2012-1989+1, 
+             ymin = 1700, ymax = 2050, alpha = .20) +
+      annotate("rect", xmin = 2005-1989+1, xmax =  2007-1989+1, 
+             ymin = 1400, ymax = 1750, alpha = .20)  
 ```
@@
     #geom_point(colour="red") + 
-    theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
+    theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8), title = element_text(size = 10), plot.title=element_text(size=10)) + 
     xlab("Year") + 
-    ylab("Number of journals") + 
-    ggtitle("Number of Social Work Journals Over Time") +
-    scale_x_discrete(breaks=c(seq(1988, 2013, 2))) +
-    scale_y_continuous(breaks = c(seq(0, 100, 10))) +
-    geom_smooth()
+    ylab("Journals") + 
+    ggtitle("B. Number of Journals by Year") +
+    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
+    scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 70)) +
+     annotate("rect", xmin = 2008-1989+1, xmax =  2012-1989+1, 
+             ymin = 55, ymax = 70, alpha = .20) +
+         annotate("rect", xmin = 2005-1989+1, xmax =  2007-1989+1, 
+             ymin = 53, ymax = 62, alpha = .20)  
 ```
@@
 
-plot.author.count <- ggplot(n_authors, aes(as.factor(pubYear), y=median.n, group=1)) +  
+plot.author.count <- ggplot(n_authors, aes(as.factor(pubYear), y=average.n, group=1)) +  
     geom_ribbon(aes(ymin = average.n-std.dev, ymax=average.n+std.dev), colour="lightblue", fill="lightblue", alpha=.40) +
     geom_line(colour="black") + 
-    ylab("Number of authors") +
-    xlab("Publication year") +
-    ggtitle("Number of Authors per Article Over Time") +
-    theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-    scale_x_discrete(breaks=c(seq(1988, 2013, 2))) +
-    geom_smooth()
+    ylab("Authors") +
+    xlab("Year") +
+    ggtitle("Average Number of Authors per Article by Year") +
+    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8), 
+          plot.title = element_text(size = 10), 
+          title = element_text(size = 10)) + 
+    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) 
 ```
+
+```{r locationExtraction}
+LO.df <- filter(full.df, attributes == "location") %>%
+         group_by(record) %>%
+         summarise(Country = unique(record),
+                   N = n()) %>%
+        arrange(desc(N)) %>% 
+        select(-record)
+
+```
+
+```{r locationWithoutUS}
+year.df <- filter(full.df, attributes == "pubYear") %>%
+            select(articleID, record)
+
+location.df <- filter(full.df, attributes == "location") %>%
+            select(articleID, record)
+
+year.location.df <- left_join(year.df, location.df, by = "articleID")
+
+colnames(year.location.df) <- c("articleID", "pubYear", "country")
+year.location.df <- year.location.df[!is.na(year.location.df$country), ]
+
+location.summary.df <- group_by(year.location.df, country) %>%
+           summarize(Number = n()) %>%
+           arrange(desc(Number)) %>%
+           slice(2:6) %>%
+           select(country)
+
+location.df <- location.df[location.df$record %in% location.summary.df$country, ]
+year.location.df <- left_join(location.df, year.df, by = "articleID") 
+colnames(year.location.df) <- c("articleID", "country", "pubYear")
+year.location.df.noUS <- group_by(year.location.df, country, pubYear) %>%
+                    summarise(N = n())
+
+```
+
+```{r locationWithtUS}
+year.df <- filter(full.df, attributes == "pubYear") %>%
+            select(articleID, record)
+
+location.df <- filter(full.df, attributes == "location") %>%
+            select(articleID, record)
+
+year.location.df <- left_join(year.df, location.df, by = "articleID")
+
+colnames(year.location.df) <- c("articleID", "pubYear", "country")
+year.location.df <- year.location.df[!is.na(year.location.df$country), ]
+
+location.summary.df <- group_by(year.location.df, country) %>%
+           summarize(Number = n()) %>%
+           arrange(desc(Number)) %>%
+           slice(1:6) %>%
+           select(country)
+
+location.df <- location.df[location.df$record %in% location.summary.df$country, ]
+year.location.df <- left_join(location.df, year.df, by = "articleID") 
+colnames(year.location.df) <- c("articleID", "country", "pubYear")
+year.location.df <- group_by(year.location.df, country, pubYear) %>%
+                    summarise(N = n())
+
+```
+
+```{r plotLocationWithUS}
+plot.location.withUS <- ggplot(year.location.df, aes(pubYear, N, group = country, colour=country)) + 
+    geom_line() +
+    theme(axis.text.x = element_text(angle = 45, hjust = 1), title = element_text(size = 10)) +
+    scale_y_continuous(limits = c(0,600)) + 
+    xlab("Year") +
+    ylab("Articles") +
+    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) + 
+    ggtitle("Number of Articles by Country and Year")
+```
+
+```{r}
+nsf <- data.frame(c(238, 273, 304, 323, 308, 287, 338, 332, 308, 289, 280), as.factor(seq(2002,2012, 1)))
+colnames(nsf) <- c("n.grads", "years")
+```
+
+```{r}
+plot.PhD <- ggplot(nsf, aes(years, n.grads, group=1)) + 
+    geom_line(linetype="dotted") + 
+    geom_point() +
+     scale_y_continuous(breaks = c(seq(0, 350, 25)), limits = c(200,350)) +
+     ylab("Doctoral degrees") +
+     xlab("Year") +
+     geom_text(aes(label = n.grads), vjust = -1.2, size = 2.75) + 
+     theme(axis.text.x = element_text(angle = 45, hjust = 1), title = element_text(size = 10)) +
+     ggtitle("Number of Earned Social Work Doctoral Degrees by Year") 
+```
+
+barplot(diff(nsf$n.grads), ylab="Change in value", main="Growth")
+
+```{r twoyearoffset}
+nsf.reduced <- nsf[1:10,]
+nsf.reduced$years <- 2004:2013
+
+```
+
+# Introduction
+
+It is estimated that 90% of all data in human history has been created in the last two years -- roughly 2.5 quintillion bytes of data every day [IBM, nd-a](http://www-01.ibm.com/software/data/bigdata/what-is-big-data.html).
+_Big data_ has become ubiquitious in the business community and has recently captured the attention of governmental organizations given its potential to generate actionable insights from a wide range of data sources [IBM, nd-b](http://www-01.ibm.com/software/data/bigdata/industry-government.html).
+The concept is most commonly understood with respect to _volume_ -- that is, an amount of data that exceeds the storage capacity of conventional database systems.
+However, _big data_ is also distinguished from traditional data with respect to _velocity_ and _variety_.
+Velocity refers to data arriving at a rate that exceeds conventional computing power, and variety refers to data structures that are not directly amenable to analysis with conventional software packages.
+Volume, velocity and variety are commonly referred to as the three _V's_.
+
+Big data comes from
+
+Although the popularity of In fact, the interest in big data is growing in popularity as an internet search term, while ``social work'' is experiencing a decline.
+
+(but not limited to) sensors that capture events in real time, GPS, social media sites, digitized text, electronic audio and video, purchase transactions, and weblogs.
+These data provide rich opportunities for social work research that are
 
@@
 In every search, we used a filter in attempt to extract only article records that were classified as _journal articles_, thereby excluding other forms of scholarly communication that was not relevant to the current study (e.g., book reviews, editorials, obituaries, etc.).
-We limited the timeframe to a 25 year period, from 1988 to 2013 (inclusive).
+We limited the timeframe to a 25 year period, from 1989 to 2013 (inclusive).
 Articles published in years 2014 and 2015 were excluded because of delays in indexing.
@@
 The initial search resulted in 36,094 article records from 117 different journals.
+```NOTE: these values are hardcoded--should be changed to draw from actual data.```
 
@@
 ```{r}
-plot.author.count
+grid.arrange(plot.article.count, plot.journal.count, ncol=2)
 ```
@@
 ```{r}
-plot.article.count
+plot.PhD
+```
+
+\newpage
+
+Insert Western Hemisphere Map Here
+
+\newpage
+Insert Eastern Hemisphere Map Here
+\newpage
+```{r}
+plot.location.withUS
 ```
@@
 ```{r}
-plot.journal.count
-```
-
-```{r}
-LO.df <- filter(full.df, attributes == "location") %>%
-         group_by(record) %>%
-         summarise(Country = unique(record),
-                   N = n()) %>%
-        arrange(desc(N)) %>% 
-        select(-record)
-
+plot.author.count
 ```

### 2015-03-20 functions/appendData.R

@@ -10,7 +10,7 @@ appendData.f <- function(){
     full.df <- rbind(ebscoBWR.df, proQuestBWR.df)
 
 
-    year.25 <- as.character(c(1900:1987, 2014, 2015))
+    year.25 <- as.character(c(1900:1988, 2014, 2015))
 
     temp.df <- filter(full.df, attributes == "pubYear")
 

### 2015-03-22 dataCleaning.Rmd
Added new front matter to manuscript.

@@
 
-barplot(diff(nsf$n.grads), ylab="Change in value", main="Growth")
-
 ```{r twoyearoffset}
@@
 
-# Introduction
+### Data Revolution
 
-It is estimated that 90% of all data in human history has been created in the last two years -- roughly 2.5 quintillion bytes of data every day [IBM, nd-a](http://www-01.ibm.com/software/data/bigdata/what-is-big-data.html).
-_Big data_ has become ubiquitious in the business community and has recently captured the attention of governmental organizations given its potential to generate actionable insights from a wide range of data sources [IBM, nd-b](http://www-01.ibm.com/software/data/bigdata/industry-government.html).
-The concept is most commonly understood with respect to _volume_ -- that is, an amount of data that exceeds the storage capacity of conventional database systems.
-However, _big data_ is also distinguished from traditional data with respect to _velocity_ and _variety_.
-Velocity refers to data arriving at a rate that exceeds conventional computing power, and variety refers to data structures that are not directly amenable to analysis with conventional software packages.
-Volume, velocity and variety are commonly referred to as the three _V's_.
+It is estimated that 90% of all the data in human history has been generated in the past two years, and the amount of data continues to grow by roughly 2.5 quintillion bytes every day [(IBM, nd-a)](http://www-01.ibm.com/software/data/bigdata/what-is-big-data.html).
+We have unprecedented opportunities for deriving actionable insights from these data to advance the human condition.
+The significance continues to gain the attention of national and international organizations.
+For example, the Independent Expert Advisory Group (IEAG) of the United Nations prepared a report entitled, _A World That Counts:  Mobilising the Data Revolution for Sustainable Development_ [(IEAG, 2014)](http://www.undatarevolution.org/report/).
+The IEAG (2014) argues that "Data are the lifeblood of decision-making and the raw material for accountability.
+Without high-quality data providing the right information on the right things at the right time; designing, monitoring and evaluating effective policies becomes almost impossible" (p.
+2).
+The United States federal government established an open data initiative, motivated by the awareness that data can have the greatest impact when it is "accessible, discoverable, and usable" [(www.data.gov)](www.data.gov).
+Data from all levels of government that is made completely open can lead to "cost savings, efficiency, fuel for business, improved civic services, informed policy, performance planning, research and scientific discoveries, transparency and accountability, and increased public participation in the democratic dialogue" (www.data.gov).
+At the time of preparing this article, over 124,000 data sets were freely available through www.data.gov among a diverse set of topic areas:  agriculture, business, climate, consumers, ecosystems, education, energy, finance, health, local government, manufacturing, ocean studies, public safety, and science and research.
 
-Big data comes from
+In 2012, the NIH established the Big Data to Knowledge (BD2K) initiative, recognizing the potential of data to advance our understanding of human health and disease.
+This initiative was designed to support four broad goals:  1) to facilitate biomedical digital assets by making them discoverable, accessible, and citable; 2) to conduct research and development methods, software and tools to analyze biomedical big data; 3) to enhance training in the development of use and tools necessary for biomedical big data science; and 4) to support a data ecosystem that accelerates discovery as part of the digital enterprise (NIH).
+At roughly the same time, the National Science Foundation (NSF) created new initiatives to harness the potential of the data revolution, arguing that ”Data are motivating a profound transformation in the culture and conduct of scientific research in every field of science and engineering ...
+American scientists must rise to the challenges and seize the opportunities afforded by this new, data-driven revolution" (Suresh, XXX).
+The programs of the NSF are organized around capacity building and innovative applications.
+Capacity building activities focus on developing fundamental theories, techniques, methodologies and technologies that are broadly applicable to big data problems.
+Innovative applications relate to specific domains advancing innovative ideas that provide solutions “with potential for a broader impact on data science and its applications.”
 
-Although the popularity of In fact, the interest in big data is growing in popularity as an internet search term, while ``social work'' is experiencing a decline.
+### Data Science and Social Work
 
-(but not limited to) sensors that capture events in real time, GPS, social media sites, digitized text, electronic audio and video, purchase transactions, and weblogs.
-These data provide rich opportunities for social work research that are
+We are, indeed, living in a data revolution.
+The relevance to social work research is clear — we have the opportunity to study human behavior and other social phenomena in real time, with vastly improved reliability in our measurements, and at scale.
+Data comes from a wide range of sources, including (but not limited to) social media interactions, electronic medical records, audio and video recordings, click stream data, transaction data, web logs, embedded sensors, and GPS.
+New tools allow blending of data sets, unique ways to analyze data, and methods of visualizations that can produce insights limited only by imagination.
+As stated by the NIH, "lack of appropriate tools, poor data accessibility, and insufficient training, are major impediments to rapid translational impact" in this new era of data.
+It is essential that the field of social work fully embraces the data revolution and considers the extent to which the existing research infrastructure and training is preparing both social work researchers and providers to be effective and efficient in a data rich world.
+The potential of the data revolution is reflected in the current _Grand Challenge_ entitled, “Harness technology for social good.”  However, we believe that it the data revolution goes beyond this single _Grand Challenge_ as it provides the opportunity to be informative in all areas of social work research.
+
+Data science serves as a useful framework for broadening our existence research infrastructure and training opportunities.
+Data science is similar to traditional academic research, as it includes the key roles of substantive expertise and traditional research methodologies.
+Much of the theoretical basis comes from the field of statistics (Zumel & Mount, 2014), but the famous statistician William Cleveland argued that it is an interdisciplinary field that is much larger than statistics (Cleveland, XXX).
+A major difference is the data science draws heavily from knowledge the areas of computer science, software engineering, and information technology.
+Unlike traditional academic research, data science is particularly in tackling the _3 V’s_ of big data:  _volume_, _variety_, and _velocity_.
+More specifically, in data-rich environments, researchers encounter an amount or volume of data that often exceeds the capacity of traditional database systems.
+Data also come in a variety of formats, ranging from highly structured data contained in relational databases to massive stores of unstructured text-data culled from social media.
+Many data opportunities go beyond the traditional approach of downloading a dataset and analyzing it with an off-the-shelf statistical package like SPSS, Stata, or SAS.
+Now, data can be accessed in real time through application program interfaces (API), which brings along the challenge of _velocity_ — that is, data can be transmitted at a rate that grossly exceeds the computing power of desktop computers.
+These are practical challenges that need to be addressed in order to maximize the potential of these new data.
+
+Another feature that distinguishes data science from traditional academic research is the focus on generating _actionable insights_ from data rather than theory building and hypothesis testing.
+In fact, data science is more interested in deriving useful insights from correlational patterns as opposed to uncovering causal mechanisms.
+The focus is on the development data products (Davenport, XXX), as opposed to reporting analysis.
+Data products are tools or services that generate actionable insights from the data itself, including (but not limited to) automated reports or dashboards, recommendation systems, prediction algorithms, decision tools, and interactive visualizations that help people with non-technical background make sense of complex data.
+Data science also values the philosophy of _openness_ or open science.
+Thus, much effort is devoted to creating sustainable systems that make data as widely and freely accessible as possible, and developing and promoting the use of open source tools for managing and analyzing data.
+The concept of reproducible research is a _rule_ rather than the _exception_.
+This involves making both data and statistical code available alongside research reports.
+This helps ensure the quality of the research, in addition to allowing researchers to make advances without having duplicate work that has already been done.
+Data science is by no means incompatible with traditional academic research.
+We believe that the tools, research strategies, and principles of data science are complementary to traditional ways of knowledge building in social work, offering many unique opportunities to improve the quality, efficiency, and impact of this area of research.
+
+### Overview of Current Study
+
+In the current study, we seek to the opportunities of the data revolution and data science by applying a range of tools and strategies to construct an historical base of social work research.
+The data are article records harvested from existing bibliographic databases.
+Article records are already widely used in various bibliometric studies, particularly those that are intended to reveal publication networks within scientific communities.
+It does so by creating links between co-authors, and then visually representing the edges and vertices of the network.
+This is also done with article citation histories, to show influence over time.
+In this study, we were interested in the various article meta-data that is common to many scientific article records.
+For example, article records a single article record in psycInfo can have as many as XX pieces of meta-data including:  dates, journal titles, article titles, author names, author affiliations, full text abstracts, keywords, subject classification, methodology, location, populations, page numbers, source of funding.
+This is a rather large amount of information about a single paper, at least compared to the amount of information contained in article records before the electronic records.
+Large collections of article records may contain potentially interesting trends in the research, assuming the selection of the article records were conducted in a way that allowed meaningful inferences to be derived.
+
+In the current study, we sought to capture every journal article record published in every social work journals over the in past quarter century (1989-2012) and to explore the various meta-data to uncover potentially interesting trends in the social work scholarship.
+For example, we can reasonably infer estimates of _size_ by counting the number of unique article records.
+And, growth of the field can be inferred by examining the number of article records over time.
+Similarly, we examine the extent to which _team science_ has become part of the research practice, as this has implications for training of social work researchers.
+We also use location meta-data to understand the extent to which different areas of the world have and have not been the focus of social work research.
+Finally, we used topic modeling to extract topic areas that define the focus of social work research.
+The execution of this research was grounded in the tools and values of data science.
+Thus, all data were managed and analyzed using open source software, R.
+We also used an open source authoring system that integrates the statistical analysis with the text of the manuscript.
+Along with this manuscript, the authors will also release the actual data and statistical code, thereby meeting the requirements of _reproducible research_, as defined by King ().
+To our knowledge, this is the first time fully reproducible research (as defined by King, XXXX), has been published in a social work journal.
+
+Davenport: http://blogs.wsj.com/cio/2014/06/25/so-you-want-to-build-a-data-product/
+
+http://www.nsf.gov/pubs/2015/nsf15544/nsf15544.htm
+
+http://www.nsf.gov/news/news_summ.jsp?cntn_id=123607&org=NSF&from=news
 

### 2015-03-22 dataCleaning.Rmd
More manuscript updates.

@@
 author: "Summary of Data Cleaning Procedures"
-output: pdf_document
+output: html_document
 ---
@@
     annotate("rect", xmin = 2008-1989+1, xmax =  2012-1989+1, 
-             ymin = 1700, ymax = 2050, alpha = .20) +
+             ymin = 1700, ymax = 2050, alpha = .20, fill = "red") +
       annotate("rect", xmin = 2005-1989+1, xmax =  2007-1989+1, 
-             ymin = 1400, ymax = 1750, alpha = .20)  
+             ymin = 1400, ymax = 1750, alpha = .20, fill="red")  
 ```
@@
      annotate("rect", xmin = 2008-1989+1, xmax =  2012-1989+1, 
-             ymin = 55, ymax = 70, alpha = .20) +
+             ymin = 55, ymax = 70, alpha = .20, fill="red") +
          annotate("rect", xmin = 2005-1989+1, xmax =  2007-1989+1, 
-             ymin = 53, ymax = 62, alpha = .20)  
+             ymin = 53, ymax = 62, alpha = .20, fill = "red")  
 ```
@@
 plot.author.count <- ggplot(n_authors, aes(as.factor(pubYear), y=average.n, group=1)) +  
-    geom_ribbon(aes(ymin = average.n-std.dev, ymax=average.n+std.dev), colour="lightblue", fill="lightblue", alpha=.40) +
-    geom_line(colour="black") + 
+    #geom_ribbon(aes(ymin = average.n-std.dev, ymax=average.n+std.dev), colour="lightblue", fill="lightblue", alpha=.40) +
+    #geom_line(colour="black") + 
+    geom_point() +
+    geom_line() + 
     ylab("Authors") +
@@
           title = element_text(size = 10)) + 
-    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) 
+    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) + 
+    scale_y_continuous(limits = c(0,3))
 ```
@@
      ggtitle("Number of Earned Social Work Doctoral Degrees by Year") 
-```
-
-```{r twoyearoffset}
-nsf.reduced <- nsf[1:10,]
-nsf.reduced$years <- 2004:2013
-
 ```

### 2015-03-22 dataCleaning.Rmd
Updated analyses. Everything working.

@@
 hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
+countries.csv <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/countries.csv")
 #load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
@@
     annotate("rect", xmin = 2008-1989+1, xmax =  2012-1989+1, 
-             ymin = 1700, ymax = 2050, alpha = .20, fill = "red") +
+             ymin = 1700, ymax = 2050, alpha = .20, fill = "#0072B2") +
       annotate("rect", xmin = 2005-1989+1, xmax =  2007-1989+1, 
-             ymin = 1400, ymax = 1750, alpha = .20, fill="red")  
+             ymin = 1400, ymax = 1750, alpha = .20, fill= "#0072B2")  
 ```
@@
      annotate("rect", xmin = 2008-1989+1, xmax =  2012-1989+1, 
-             ymin = 55, ymax = 70, alpha = .20, fill="red") +
+             ymin = 55, ymax = 70, alpha = .20, fill= "#0072B2") +
          annotate("rect", xmin = 2005-1989+1, xmax =  2007-1989+1, 
-             ymin = 53, ymax = 62, alpha = .20, fill = "red")  
+             ymin = 53, ymax = 62, alpha = .20, fill = "#0072B2")  
 ```
@@
 
-plot.author.count <- ggplot(n_authors, aes(as.factor(pubYear), y=average.n, group=1)) +  
-    #geom_ribbon(aes(ymin = average.n-std.dev, ymax=average.n+std.dev), colour="lightblue", fill="lightblue", alpha=.40) +
-    #geom_line(colour="black") + 
-    geom_point() +
-    geom_line() + 
-    ylab("Authors") +
+n_authors2 <- n_authors%>% 
+       select(median.n, average.n, std.dev) %>%
+       rename(median = median.n, average = average.n)
+
+n_authors2$ID <- as.factor(c(1989:2013))
+
+n_authors2_melted <- reshape2::melt(n_authors2, id.vars = "ID")
+colnames(n_authors2_melted) <- c("pubYear", "summaryStat", "value")
+
+cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+
+plot.author.count <- ggplot(n_authors2_melted, aes(x = pubYear, y = value, group = summaryStat, colour = summaryStat)) + 
+     geom_line(size = .75) + 
+    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
+          title = element_text(size = 10), 
+          legend.title=element_blank()) +
+    scale_colour_manual(values=cbPalette)  +
+    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
+    scale_y_continuous(limits = c(0,2.5)) +
+    ylab("Value") +
     xlab("Year") +
-    ggtitle("Average Number of Authors per Article by Year") +
-    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8), 
-          plot.title = element_text(size = 10), 
-          title = element_text(size = 10)) + 
-    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) + 
-    scale_y_continuous(limits = c(0,3))
+    ggtitle("Authors Per Article by Year")
+
 ```
@@
         select(-record)
-
 ```
 
-```{r locationWithoutUS}
-year.df <- filter(full.df, attributes == "pubYear") %>%
-            select(articleID, record)
+```{r locationExtraction2}
+LO.df2 <- filter(full.df, attributes == "location" | attributes == "abstract" |
+                 attributes == "article" | attributes == "keyword")
+indx.country <- paste(countries.csv$x, collapse = "|")
+library(stringi)
+countries.extracted <- na.omit(within(LO.df2, text1<- stri_extract(LO.df2$record, regex=indx.country)))[-2]
+country.indexed <- as.numeric(rownames(countries.extracted))
+location.ID <- LO.df2$articleID[country.indexed]
 
-location.df <- filter(full.df, attributes == "location") %>%
-            select(articleID, record)
-
-year.location.df <- left_join(year.df, location.df, by = "articleID")
-
-colnames(year.location.df) <- c("articleID", "pubYear", "country")
-year.location.df <- year.location.df[!is.na(year.location.df$country), ]
-
-location.summary.df <- group_by(year.location.df, country) %>%
-           summarize(Number = n()) %>%
-           arrange(desc(Number)) %>%
-           slice(2:6) %>%
-           select(country)
-
-location.df <- location.df[location.df$record %in% location.summary.df$country, ]
-year.location.df <- left_join(location.df, year.df, by = "articleID") 
-colnames(year.location.df) <- c("articleID", "country", "pubYear")
-year.location.df.noUS <- group_by(year.location.df, country, pubYear) %>%
-                    summarise(N = n())
-
+detach(package:stringi)
 ```
@@
 ```{r plotLocationWithUS}
+
+cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
+
 plot.location.withUS <- ggplot(year.location.df, aes(pubYear, N, group = country, colour=country)) + 
     geom_line() +
-    theme(axis.text.x = element_text(angle = 45, hjust = 1), title = element_text(size = 10)) +
+    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
+          title = element_text(size = 10), 
+          legend.title=element_blank())  +
     scale_y_continuous(limits = c(0,600)) + 
@@
     scale_x_discrete(breaks=c(seq(1989, 2013, 2))) + 
+    scale_colour_manual(values=cbPalette) +
     ggtitle("Number of Articles by Country and Year")
@@
 
-```{r}
+```{r nsf}
 nsf <- data.frame(c(238, 273, 304, 323, 308, 287, 338, 332, 308, 289, 280), as.factor(seq(2002,2012, 1)))
@@
 
-```{r}
+```{r nsfPlot}
 plot.PhD <- ggplot(nsf, aes(years, n.grads, group=1)) + 
-    geom_line(linetype="dotted") + 
-    geom_point() +
+    geom_line(linetype="dotted", colour = "#0072B2", size = .75) + 
+    geom_point(colour = "#0072B2", size = .75) +
      scale_y_continuous(breaks = c(seq(0, 350, 25)), limits = c(200,350)) +
@@
      geom_text(aes(label = n.grads), vjust = -1.2, size = 2.75) + 
-     theme(axis.text.x = element_text(angle = 45, hjust = 1), title = element_text(size = 10)) +
+     theme(axis.text.x = element_text(angle = 45, hjust = 1), 
+           title = element_text(size = 10)) +
      ggtitle("Number of Earned Social Work Doctoral Degrees by Year") 

### 2015-03-23 dataCleaning.Rmd
Updated manuscript.

@@
 
-```{r initialization_dataprocessing}
+```{r initialization}
 rm(list=ls())  
+load("/Users/beperron/Git/SocialWorkResearch/socialWorkHistory.Rdata")
+
 # Load required packages
@@
 library(gridExtra)
+```
 
+```{r eval=FALSE}
 # Read data files
@@
 
-```{r appendData, comment=NA, echo=FALSE}
+```{r appendData, comment=NA, echo=FALSE, eval=FALSE}
 appendData.f()
@@
 
-```{r shortArticles, comment=NA, echo=FALSE, warning=FALSE}
+```{r shortArticles, comment=NA, echo=FALSE, warning=FALSE, eval=FALSE}
 shortArticles.f()
@@
 
-```{r titleMatching, echo=FALSE}
+```{r titleMatching, echo=FALSE, eval=FALSE}
 titleMatching.f()
@@
 
-```{r otherDocuments, echo=FALSE}
+```{r otherDocuments, echo=FALSE, eval=FALSE}
 otherDocuments.f()
@@
 
-```{r final, comment=NA, echo=FALSE}
+```{r final, comment=NA, echo=FALSE, eval=FALSE}
 fewArticles.f()
@@
 
-```{r finalList, comment=NA, echo=FALSE}
+```{r finalList, comment=NA, echo=FALSE, eval=FALSE}
 unique.titles <- filter(full.df, attributes == "journal") %>%
@@
 
-```{r plotArticleCount}
+```{r plotArticleCount, eval=FALSE}
 n.articles.year <- filter(full.df, attributes == "pubYear") 
@@
 
-```{r plotJournalCount}
+```{r plotJournalCount, eval=FALSE}
 n.journals.year <- filter(full.df, attributes == "journal") %>%
@@
 
-```{r plotAuthorCount}
+```{r plotAuthorCount, eval=FALSE}
 
@@
        select(median.n, average.n, std.dev) %>%
-       rename(median = median.n, average = average.n)
+       rename(Median = median.n, Average = average.n, Standard_Deviation =std.dev)
 
@@
 
-```{r locationExtraction2}
+```{r locationExtraction2, eval=FALSE}
 LO.df2 <- filter(full.df, attributes == "location" | attributes == "abstract" |
@@
 location.ID <- LO.df2$articleID[country.indexed]
-
 detach(package:stringi)
@@
 
-```{r locationWithtUS}
+```{r locationWithtUS, eval=FALSE}
 year.df <- filter(full.df, attributes == "pubYear") %>%
@@
 
-```{r plotLocationWithUS}
+```{r plotLocationWithUS, eval=FALSE}
 
@@
 
-```{r nsf}
+```{r nsf, eval=FALSE}
 nsf <- data.frame(c(238, 273, 304, 323, 308, 287, 338, 332, 308, 289, 280), as.factor(seq(2002,2012, 1)))
@@
 
-```{r nsfPlot}
+```{r nsfPlot, eval=FALSE}
 plot.PhD <- ggplot(nsf, aes(years, n.grads, group=1)) + 
@@
 ```
+
+#save.image(file = "socialWorkHistory.Rdata")
 

### 2015-03-23 dataCleaning.Rmd
Fix paths.
Edits to introduction

@@
 load("/Users/beperron/Git/SocialWorkResearch/socialWorkHistory.Rdata")
+#load("/Users/SSW/Documents/GitHub/SocialWork100Years/SocialWorkHistory.Rdata")
 
@@
 
-#save.image(file = "socialWorkHistory.Rdata")
+```{r}
+save.image(file = "socialWorkHistory.Rdata")
+```
 
@@
 In 2012, the NIH established the Big Data to Knowledge (BD2K) initiative, recognizing the potential of data to advance our understanding of human health and disease.
-This initiative was designed to support four broad goals:  1) to facilitate biomedical digital assets by making them discoverable, accessible, and citable; 2) to conduct research and development methods, software and tools to analyze biomedical big data; 3) to enhance training in the development of use and tools necessary for biomedical big data science; and 4) to support a data ecosystem that accelerates discovery as part of the digital enterprise (NIH).
-At roughly the same time, the National Science Foundation (NSF) created new initiatives to harness the potential of the data revolution, arguing that ”Data are motivating a profound transformation in the culture and conduct of scientific research in every field of science and engineering ...
+This initiative was designed to support four broad goals:  1) to facilitate use of biomedical digital assets by making them discoverable, accessible, and citable; 2) to conduct research and develop methods, software and tools to analyze biomedical big data; 3) to enhance training in the development of use and tools necessary for biomedical big data science; and 4) to support a data ecosystem that accelerates discovery as part of the digital enterprise (NIH).
+At roughly the same time, the National Science Foundation (NSF) created new initiatives to harness the potential of the data revolution, arguing that ”data are motivating a profound transformation in the culture and conduct of scientific research in every field of science and engineering ...
 American scientists must rise to the challenges and seize the opportunities afforded by this new, data-driven revolution" (Suresh, XXX).
@@
 
-We are, indeed, living in a data revolution.
+We are indeed living in a data revolution.
 The relevance to social work research is clear — we have the opportunity to study human behavior and other social phenomena in real time, with vastly improved reliability in our measurements, and at scale.
 Data comes from a wide range of sources, including (but not limited to) social media interactions, electronic medical records, audio and video recordings, click stream data, transaction data, web logs, embedded sensors, and GPS.
-New tools allow blending of data sets, unique ways to analyze data, and methods of visualizations that can produce insights limited only by imagination.
+New tools allow blending of data sets, unique ways to analyze data, and methods of visualizations that can produce insights limited only by one's imagination.
 As stated by the NIH, "lack of appropriate tools, poor data accessibility, and insufficient training, are major impediments to rapid translational impact" in this new era of data.
 It is essential that the field of social work fully embraces the data revolution and considers the extent to which the existing research infrastructure and training is preparing both social work researchers and providers to be effective and efficient in a data rich world.
-The potential of the data revolution is reflected in the current _Grand Challenge_ entitled, “Harness technology for social good.”  However, we believe that it the data revolution goes beyond this single _Grand Challenge_ as it provides the opportunity to be informative in all areas of social work research.
+The potential of the data revolution is reflected in the current _Grand Challenge_ entitled, “Harness technology for social good.”  However, we believe that the data revolution goes beyond this single _Grand Challenge_ as it provides the opportunity to be informative in all areas of social work research.
 
-Data science serves as a useful framework for broadening our existence research infrastructure and training opportunities.
+Data science serves as a useful framework for broadening the existing research infrastructure and training opportunities within social work.
 Data science is similar to traditional academic research, as it includes the key roles of substantive expertise and traditional research methodologies.
 Much of the theoretical basis comes from the field of statistics (Zumel & Mount, 2014), but the famous statistician William Cleveland argued that it is an interdisciplinary field that is much larger than statistics (Cleveland, XXX).
-A major difference is the data science draws heavily from knowledge the areas of computer science, software engineering, and information technology.
-Unlike traditional academic research, data science is particularly in tackling the _3 V’s_ of big data:  _volume_, _variety_, and _velocity_.
+A major difference is that data science draws heavily from knowledge in the areas of computer science, software engineering, and information technology.
+Unlike traditional academic research, data science is particularly well suited for tackling the _3 V’s_ of big data:  _volume_, _variety_, and _velocity_.
 More specifically, in data-rich environments, researchers encounter an amount or volume of data that often exceeds the capacity of traditional database systems.
@@
 In fact, data science is more interested in deriving useful insights from correlational patterns as opposed to uncovering causal mechanisms.
-The focus is on the development data products (Davenport, XXX), as opposed to reporting analysis.
+The focus is on the development of data products (Davenport, XXX), as opposed to reporting analysis.
 Data products are tools or services that generate actionable insights from the data itself, including (but not limited to) automated reports or dashboards, recommendation systems, prediction algorithms, decision tools, and interactive visualizations that help people with non-technical background make sense of complex data.
@@
 
-In the current study, we seek to the opportunities of the data revolution and data science by applying a range of tools and strategies to construct an historical base of social work research.
-The data are article records harvested from existing bibliographic databases.
+In the current study, we seek to utilize the opportunities of the data revolution and data science by applying a range of tools and strategies to construct an historical base of social work research.
+In doing so we take on two of the 3 Vs of big data: volume due the amount of data collected and variety in terms of the multiple sources of that data.
+The data are article records harvested from existing bibliographic databases hosted on ProQuest and EbscoHost.
 Article records are already widely used in various bibliometric studies, particularly those that are intended to reveal publication networks within scientific communities.
@@
 This is also done with article citation histories, to show influence over time.
-In this study, we were interested in the various article meta-data that is common to many scientific article records.
-For example, article records a single article record in psycInfo can have as many as XX pieces of meta-data including:  dates, journal titles, article titles, author names, author affiliations, full text abstracts, keywords, subject classification, methodology, location, populations, page numbers, source of funding.
-This is a rather large amount of information about a single paper, at least compared to the amount of information contained in article records before the electronic records.
+In this study, we were interested in the various article meta-data that are common to many scientific article records.
+For example, a single article record in psycINFO can have as many as XX pieces of meta-data including:  dates, journal titles, article titles, author names, author affiliations, full text abstracts, keywords, subject classification, methodology, location, populations, page numbers, and source of funding.
+This is a rather large amount of information about a single paper, at least compared to the amount of information contained in article records before the availability of electronic storage and access.
 Large collections of article records may contain potentially interesting trends in the research, assuming the selection of the article records were conducted in a way that allowed meaningful inferences to be derived.
 
-In the current study, we sought to capture every journal article record published in every social work journals over the in past quarter century (1989-2012) and to explore the various meta-data to uncover potentially interesting trends in the social work scholarship.
-For example, we can reasonably infer estimates of _size_ by counting the number of unique article records.
+In the current study, we sought to capture every journal article record published in every social work journals over the in past quarter century (1989-2013) and to explore the various meta-data to uncover potentially interesting trends in the social work scholarship.
+For example, we can reasonably infer estimates of the _size_  of social work scholarship by counting the number of unique article records.
 And, growth of the field can be inferred by examining the number of article records over time.
@@
 The execution of this research was grounded in the tools and values of data science.
-Thus, all data were managed and analyzed using open source software, R.
+Thus, all data were managed and analyzed using the open source software, R.
 We also used an open source authoring system that integrates the statistical analysis with the text of the manuscript.

### 2015-03-24 dataCleaning.Rmd
Location analysis upgraded and functional

@@
 #hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)
+#countries.csv<-read.csv("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/countries.csv")
 
@@
 source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")
+
+#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/appendData.R")
+#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/shortArticles.R")
+#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/titleMatching.R")
+#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/otherDocuments.R")
+#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/titleMatching.R")
+#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/fewArticles.R")
 
@@
 ```{r locationExtraction2, eval=FALSE}
-LO.df2 <- filter(full.df, attributes == "location" | attributes == "abstract" |
+LO.df2 <- filter(full.df, attributes == "abstract" |
                  attributes == "article" | attributes == "keyword")
-indx.country <- paste(countries.csv$x, collapse = "|")
+indx.country <- paste(countries.csv$x, collapse = "[\\s|[[:punct:]]]|")
 library(stringi)
-countries.extracted <- na.omit(within(LO.df2, text1<- stri_extract(LO.df2$record, regex=indx.country)))[-2]
-country.indexed <- as.numeric(rownames(countries.extracted))
-location.ID <- LO.df2$articleID[country.indexed]
+countries.extracted <- na.omit(within(LO.df2, text1<- stri_extract(LO.df2$record, opts_fixed=TRUE, regex=indx.country)))[-2]
+countries.extracted$text1<-gsub("[[:punct:]]", "", countries.extracted$text1)
+countries.extracted$text1<-gsub("^\\s+|\\s+$", "", countries.extracted$text1)
+
+new.countries<-unique(countries.extracted[,c("articleID","text1")])
+new.countries<-mutate(new.countries, attributes="location")
+new.countries<-select(new.countries, articleID, attributes, record=text1)
+
+loc<-filter(full.df, attributes=="location")
+locations<-rbind(loc, new.countries)
+locations<-unique(locations[,c("articleID","attributes","record")])
+locations<-filter(locations, record!="NA")
+
+#Set of code to address labeling issues related to the United Kingdom
+
+locations$record[locations$record=="Great Britain"]<- "United Kingdom"    #Combines Great Britain and UK records
+
+uk<-filter(locations, record=="United Kingdom")  #creates temp DF with only UK records
+ukID<-uk$articleID
+
+#next four blocks of code check to see if the United Kindgom and each country are both listed as a research site and eliminates the UK location record when this was the case.
+This means that remaining UK records represent cases of research within the UK in an unspecified country.
+
+scot<-filter(locations, record=="Scotland") 
+scotID<-scot$articleID
+remove<-ukID%in%scotID
+uk.remove<-cbind(uk, remove)
+uk.remove<-filter(uk, remove==TRUE)
+uk.remove.ID<-uk.remove$articleID
+uk<-uk[!(uk$articleID%in%uk.remove.ID),]
+ukID<-uk$articleID
+
+eng<-filter(locations, record=="England")  
+engID<-eng$articleID 
+remove<-ukID%in%engID
+uk.remove<-cbind(uk, remove)
+uk.remove<-filter(uk, remove==TRUE)
+uk.remove.ID<-uk.remove$articleID
+uk<-uk[!(uk$articleID%in%uk.remove.ID),]
+ukID<-uk$articleID
+
+ni<-filter(locations, record=="Northern Ireland") 
+niID<-ni$articleID
+remove<-ukID%in%niID
+uk.remove<-cbind(uk, remove)
+uk.remove<-filter(uk, remove==TRUE)
+uk.remove.ID<-uk.remove$articleID
+uk<-uk[!(uk$articleID%in%uk.remove.ID),]
+ukID<-uk$articleID
+
+wales<-filter(locations, record=="Wales") 
+walesID<-wales$articleID
+remove<-ukID%in%walesID
+uk.remove<-cbind(uk, remove)
+uk.remove<-filter(uk, remove==TRUE)
+uk.remove.ID<-uk.remove$articleID
+uk<-uk[!(uk$articleID%in%uk.remove.ID),]
+ukID<-uk$articleID
+
+locations<-filter(locations, record!="United Kingdom")  #removes old UK records
+locations<-rbind(locations, uk)
+
+locations$record[locations$record=="US"]<-"United States"
+locations$record[locations$record=="Appalachia"]<-"United States"
+locations$record[locations$record=="Bosnia"]<-"Bosnia-Herzegovina"
+locations$record[locations$record=="Democratic Republic of Congo"]<- "Congo (Brazzaville)"
+locations$record[locations$record=="Democratic Republic of the Congo"]<- "Congo (Brazzaville)"
+locations$record[locations$record=="Holland"]<- "Netherlands"
+locations$record[locations$record=="West Bank"]<-"Palestine"
+locations$record[locations$record=="Gaza"]<-"Palestine"
+locations$record[locations$record=="Gaza Strip"]<-"Palestine"
+locations$record[locations$record=="Trinidad"]<-"Trinidad and Tobago"
+locations$record[locations$record=="Gaza"]<-"Palestine"
+locations$record[locations$record=="England"]<-"United Kingdom"
+locations$record[locations$record=="Northern Ireland"]<-"United Kingdom"
+locations$record[locations$record=="Scotland"]<-"United Kingdom"
+locations$record[locations$record=="Wales"]<-"United Kingdom"
+
+full.df<-filter(full.df, attributes!="location")
+full.df<-rbind(full.df, locations)
+
 detach(package:stringi)
@@
 
-location.df <- location.df[location.df$record %in% location.summary.df$country, ]
-year.location.df <- left_join(location.df, year.df, by = "articleID") 
-colnames(year.location.df) <- c("articleID", "country", "pubYear")
-year.location.df <- group_by(year.location.df, country, pubYear) %>%
+location.df.withUS <- location.df[location.df$record %in% location.summary.df$country, ]
+year.location.df.withUS <- left_join(location.df.withUS, year.df, by = "articleID") 
+colnames(year.location.df.withUS) <- c("articleID", "country", "pubYear")
+year.location.df.withUS <- group_by(year.location.df.withUS, country, pubYear) %>%
                     summarise(N = n())
 
+location.summary.df.noUS <- group_by(year.location.df, country) %>%
+           summarize(Number = n()) %>%
+           arrange(desc(Number)) %>%
+           slice(2:7) %>%
+           select(country)
+
+location.df.noUS <- location.df[location.df$record %in% location.summary.df.noUS$country, ]
+year.location.df.noUS <- left_join(location.df.noUS, year.df, by = "articleID") 
+colnames(year.location.df.noUS) <- c("articleID", "country", "pubYear")
+year.location.df.noUS <- group_by(year.location.df.noUS, country, pubYear) %>%
+                    summarise(N = n())
 ```
@@
 
-plot.location.withUS <- ggplot(year.location.df, aes(pubYear, N, group = country, colour=country)) + 
+plot.location.withUS <- ggplot(year.location.df.withUS, aes(pubYear, N, group = country, colour=country)) + 
     geom_line() +
@@
           legend.title=element_blank())  +
-    scale_y_continuous(limits = c(0,600)) + 
+    scale_y_continuous(limits = c(0,700)) + 
     xlab("Year") +
@@
     ggtitle("Number of Articles by Country and Year")
+
+plot.location.noUS <- ggplot(year.location.df.noUS, aes(pubYear, N, group = country, colour=country)) + 
+    geom_line() +
+    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
+          title = element_text(size = 10), 
+          legend.title=element_blank())  +
+    scale_y_continuous(limits = c(0,150)) + 
+    xlab("Year") +
+    ylab("Articles") +
+    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) + 
+    scale_colour_manual(values=cbPalette) +
+    ggtitle("Number of Articles by Country and Year, United States Excluded")
+
 ```
@@
 
+```{r}
+plot.location.noUS
+```
+
 \newpage

### 2015-03-24 dataCleaning.Rmd
Maps up and running

@@
 rm(list=ls())  
-load("/Users/beperron/Git/SocialWorkResearch/socialWorkHistory.Rdata")
-#load("/Users/SSW/Documents/GitHub/SocialWork100Years/SocialWorkHistory.Rdata")
+#load("/Users/beperron/Git/SocialWorkResearch/socialWorkHistory.Rdata")
+load("/Users/SSW/Documents/GitHub/SocialWork100Years/socialWorkHistory.Rdata")
 
@@
 library(gridExtra)
+library(rworldmap)
+
 ```
@@
 # Read data files
-load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
-load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
-hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
-countries.csv <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/countries.csv")
-#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
-#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
-#hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)
-#countries.csv<-read.csv("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/countries.csv")
+#load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
+#load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
+#hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
+#countries.csv <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/countries.csv")
+load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
+load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
+hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)
+countries.csv<-read.csv("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/countries.csv")
 
@@
 
+```{r worldmap, eval=FALSE}
+
+###Code for creating world maps.  The four countries in the UK are recoded as "United Kingdom" for data visualization.
+library(rworldmap)
+
+loc.tab<-table(locations$record)
+
+loc.tab<-as.data.frame(loc.tab)
+loc.tab<-select(loc.tab, country=Var1, frequency=Freq)
+
+#join to a coarse resolution map
+spdf <- joinCountryData2Map(loc.tab, joinCode="NAME", nameJoinColumn="country")
+
+loc.tab2<-filter(loc.tab, frequency>=25)
+spdf2 <- joinCountryData2Map(loc.tab2, joinCode="NAME", nameJoinColumn="country")
+
+```
+
 ```{r locationWithtUS, eval=FALSE}
@@
 
-Insert Western Hemisphere Map Here
+```{r}
+mapCountryData(spdf, nameColumnToPlot="frequency", catMethod="quantiles", 
+                                  colourPalette="white2Black", 
+                                  mapTitle="Article Countss by Country, 1989-2013")
+```
 
 \newpage
-Insert Eastern Hemisphere Map Here
+```{r}
+mapCountryData(spdf2, nameColumnToPlot="frequency", catMethod="quantiles", 
+                    colourPalette="white2Black", 
+                    mapTitle="Article Counts for Countries with Sustained Presence, 1989-2013")
+
+```
+
 \newpage

### 2015-03-26 dataCleaning.Rmd
updated country stats

@@
 detach(package:stringi)
+
+setwd("C:/Users/SSW/Documents/GitHub/SocialWork100Years/Data")
+GDP<-read.csv("GDP.csv")
+GDP<-select(GDP, Country=Country.Name, GDPperCapita=GDPperCapita2013, GDPRank)
+
+PPP<-read.csv("PPP.csv")
+PPP$PPP2013<-gsub(",", "", PPP$PPP2013)
+PPP$PPP2013<-as.character(PPP$PPP2013)
+PPP$PPP2013<-as.numeric(PPP$PPP2013)
+
+articleCountries<-table(locations$record)
+articleCountries<-as.data.frame(articleCountries)
+articleCountries<-articleCountries%>%
+                    select(Country=Var1, articleCount=Freq)
+
+rankSet<-merge(articleCountries, GDP, by="Country", all=TRUE)
+rankSet$articleCount[is.na(rankSet$articleCount)]<-0
+rankSet<-merge(rankSet, PPP, by="Country", all=TRUE)
+
+rankSet<-mutate(rankSet, articleRank=rank(-articleCount))
 ```

### 2015-03-28 dataCleaning.Rmd
Lots of updates ...

@@
 rm(list=ls())  
-#load("/Users/beperron/Git/SocialWorkResearch/socialWorkHistory.Rdata")
-load("/Users/SSW/Documents/GitHub/SocialWork100Years/socialWorkHistory.Rdata")
+load("/Users/beperron/Git/SocialWorkResearch/socialWorkHistory.Rdata")
+#load("/Users/SSW/Documents/GitHub/SocialWork100Years/socialWorkHistory.Rdata")
 
@@
 
-```{r}
+```{r eval=FALSE}
 save.image(file = "socialWorkHistory.Rdata")
@@
                                   colourPalette="white2Black", 
-                                  mapTitle="Article Countss by Country, 1989-2013")
+                                  mapTitle="Article Counts by Country, 1989-2013")
 ```

### 2015-03-29 dataCleaning.Rmd
Tableau edits.

@@
 ```{r nsf, eval=FALSE}
-nsf <- data.frame(c(238, 273, 304, 323, 308, 287, 338, 332, 308, 289, 280), as.factor(seq(2002,2012, 1)))
-colnames(nsf) <- c("n.grads", "years")
+nsf <- data.frame(c(rep(NA, 13), 238, 273, 304, 323, 308, 287, 338, 332, 308, 289, 280, NA), as.factor(seq(1989,2013, 1)))
+
+growth <- c(rep("Unknown", 14), rep("Increase", 2), rep("Decrease", 3), "Increase", 
+     rep("Decrease", 4), "Unknown")
+nsf <- cbind(nsf, growth)
+
+colnames(nsf) <- c("n.grads", "years", "growth")
+
+write.csv(nsf, file="nsf.csv")
+
 ```
@@
      ggtitle("Number of Earned Social Work Doctoral Degrees by Year") 
+```
+
+```{r pages, eval=FALSE}
+pages.df <- full.df %>% filter(attributes == "pages")
+page.identifier <- grepl("[-p]", pages.df$record)
+pages.df.reduced <- pages.df[page.identifier == FALSE,]
+
+reduced <- full.df[full.df$articleID %in% pages.df.reduced$articleID, ]
+reduced <- filter(reduced, attributes == "article" | attributes == "journal" | 
+            attributes == "pubYear" | attributes == "pages" | attributes == "abstract")
+
 ```

### 2015-03-29 functions/fewArticles.R
Function updates

@@ -3,6 +3,8 @@ fewArticles.f <- function(){
     titles <- filter(full.df, attributes == "article")
     journals <- filter(full.df, attributes == "journal")
     year <- filter(full.df, attributes == "pubYear")
+    
+    
 
     year.journal <- dplyr::intersect(year$articleID, journals$articleID)
     year.journal.titles <- dplyr::intersect(year.journal, titles$articleID)
@@ -18,4 +20,10 @@ fewArticles.f <- function(){
     ebsco.remove <- full.df[full.df$record %in% exclusions.2, ]
     ebsco.remove <- ebsco.remove[, "articleID"]
     full.df <<- full.df[!(full.df$articleID %in% ebsco.remove),]
+    
+    author<-filter(full.df, attributes=="author")
+    no.author<-filter(author, grepl("authorship|anonymous", record, ignore.case=TRUE))
+    no.author.ID<-no.author$articleID
+    full.df <<- full.df[!(full.df$articleID %in% no.author.ID),]
+    
 }

### 2015-03-29 functions/otherDocuments.R

@@ -12,12 +12,21 @@ insert.5<-"[S|s]pecial\\s[I|i]ssue|[T|t]able\\s[O|o]f\\s[C|c]ontent|\\([U|u]ndet
 insert.6<-"^Book.+ | ^COMMENTARY.+ | Call\\s.+ | Contents.+ | Editor.+ | Errat.+"
 insert.7<-"^FROM\\THE.+ | ^From\\sthe\\ed.+ | Health\\s[&]\\sS.+ | ^LETTER.+ |
              ^Letter\\sfrom.+ | ^News\\and.+ | ^Response\\sto\\s[A-Z] | Vol\\.\\s[0-9] |
-            ^Volume.+ | ^\\["
+            ^Volume.+ | ^\\[|Retraction|Endpage"
+
 
 insert<-paste(insert.1,insert.2,insert.3,insert.4,insert.5, insert.6,
               insert.7, sep="|")
 
 badRecords<-subset(titles, grepl(insert, record))
+badRecords.ID<-badRecords$articleID
+
+full.df <<- full.df[!(full.df$articleID %in% badRecords.ID), ]
+
+abstracts<-filter(full.df, attributes=="abstract")
+insert<-"special\\sissue\\s|special\\sissue[[:punct:]]|this\\scommentary|endpage"
+badRecords<-subset(abstracts, grepl(insert, record, ignore.case=TRUE))
+badRecords<-subset(badRecords, !grepl("Part of a special issue", record, ignore.case=TRUE))
 badRecords.ID<-badRecords$articleID
 
 full.df <<- full.df[!(full.df$articleID %in% badRecords.ID), ]

### 2015-03-29 functions/shortArticles.R

@@ -5,19 +5,45 @@ shortArticles.f <- function(){
     pages.df$record <- gsub("ArtID:\\s", "", pages.df$record)
     pages.df$record<-gsub("S", "", pages.df$record)
     pages.df$record <- gsub(" ", "", pages.df$record)
-
+    
+    pages.df$record[pages.df$record==1830]<-"173-183"
+    pages.df$record[pages.df$record==364] <- 1
+    pages.df$record[pages.df$record==216] <- 1
+    pages.df$record[pages.df$record==190] <- 1
+    pages.df$record[pages.df$record==131] <- 1
+    pages.df$record[pages.df$record==183] <- 1
+    pages.df$record[pages.df$record==50] <- "533-552"
+    pages.df$record[pages.df$record==116] <- "191-207" 
+    pages.df$record[pages.df$record==58] <-"58-66"
+    pages.df$record[pages.df$record==84] <-"339-355"
+       
     dashes<-filter(pages.df, grepl("-", record) )
-
+    dashes$record[dashes$record=="389-314"]<-"289-314"
+    dashes$record[dashes$record=="209-2018"]<-"209-218"
+    dashes$record[dashes$record=="611-931"]<-"611-631"
+    dashes$record[dashes$record=="13-224"]<-"13-24"
+    dashes$record[dashes$record=="446-499"]<-"466-499"
+    dashes$record[dashes$record=="117-186"]<-"117-129"
+    dashes$record[dashes$record=="19-228"]<-"1-2"  #could not verify page numbers, slated for removal
+    dashes$record[dashes$record=="1-109"]<-"1-2"  #not an article
+    dashes$record[dashes$record=="1-116"]<-"1-2"  #not an article
+    dashes$record[dashes$record=="1-172"]<-"1-2"  #not an article
+    dashes$record[dashes$record=="1-120"]<-"1-2"  #not an article
+    dashes$record[dashes$record=="1-218"]<-"1-2"  #not an article
+    dashes$record[dashes$record=="1-98"]<-"1-2"  #not an article
+    dashes$record[dashes$record=="1-212"]<-"1-2"  #not an article
+    
     splitDash<-strsplit(dashes$record, "-")
     mat  <- matrix(unlist(splitDash), ncol=2, byrow=TRUE)
     mat <- as.data.frame(mat)
+    mat$V1[mat$V1==119119]<-119
 
     mat$V1<- as.character(mat$V1)
[…]

### 2015-03-31 dataCleaning.Rmd
Minor edit - reads in rankSet.csv

@@
 rm(list=ls())  
-load("/Users/beperron/Git/SocialWorkResearch/socialWorkHistory.Rdata")
+#load("/Users/beperron/Git/SocialWorkResearch/socialWorkHistory.Rdata")
 #load("/Users/SSW/Documents/GitHub/SocialWork100Years/socialWorkHistory.Rdata")
@@
 
-```{r eval=FALSE}
+```{r eval=TRUE}
 # Read data files
@@
 # Load special functions
-source("/Users/beperron/Git/SocialWorkResearch/functions/appendData.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticles.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")
+#source("/Users/beperron/Git/SocialWorkResearch/functions/appendData.R")
+#source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticles.R")
+#source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
+#source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
+#source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
+#source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")
 
-#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/appendData.R")
-#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/shortArticles.R")
-#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/titleMatching.R")
-#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/otherDocuments.R")
-#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/titleMatching.R")
-#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/fewArticles.R")
+source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/appendData.R")
+source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/shortArticles.R")
+source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/titleMatching.R")
+source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/otherDocuments.R")
+source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/titleMatching.R")
+source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/fewArticles.R")
 
@@
 
-```{r appendData, comment=NA, echo=FALSE, eval=FALSE}
+```{r appendData, comment=NA, echo=FALSE, eval=TRUE}
 appendData.f()
@@
 
-```{r shortArticles, comment=NA, echo=FALSE, warning=FALSE, eval=FALSE}
+```{r shortArticles, comment=NA, echo=FALSE, warning=FALSE, eval=TRUE}
 shortArticles.f()
@@
 
-```{r titleMatching, echo=FALSE, eval=FALSE}
+```{r titleMatching, echo=FALSE, eval=TRUE}
 titleMatching.f()
@@
 
-```{r otherDocuments, echo=FALSE, eval=FALSE}
+```{r otherDocuments, echo=FALSE, eval=TRUE}
 otherDocuments.f()
@@
 
-```{r final, comment=NA, echo=FALSE, eval=FALSE}
+```{r final, comment=NA, echo=FALSE, eval=TRUE}
 fewArticles.f()
@@
 
-```{r finalList, comment=NA, echo=FALSE, eval=FALSE}
+```{r finalList, comment=NA, echo=FALSE, eval=TRUE}
 unique.titles <- filter(full.df, attributes == "journal") %>%
@@
 
-```{r plotArticleCount, eval=FALSE}
+```{r plotArticleCount, eval=TRUE}
 n.articles.year <- filter(full.df, attributes == "pubYear") 
@@
 
-```{r plotJournalCount, eval=FALSE}
+```{r plotJournalCount, eval=TRUE}
 n.journals.year <- filter(full.df, attributes == "journal") %>%
@@
 
-```{r plotAuthorCount, eval=FALSE}
+```{r plotAuthorCount, eval=TRUE}
 
@@
 
-```{r locationExtraction2, eval=FALSE}
+```{r locationExtraction2, eval=TRUE}
 LO.df2 <- filter(full.df, attributes == "abstract" |
@@
 setwd("C:/Users/SSW/Documents/GitHub/SocialWork100Years/Data")
-GDP<-read.csv("GDP.csv")
-GDP<-select(GDP, Country=Country.Name, GDPperCapita=GDPperCapita2013, GDPRank)
+rankSet<-read.csv("rankSet.csv")
 
-PPP<-read.csv("PPP.csv")
-PPP$PPP2013<-gsub(",", "", PPP$PPP2013)
-PPP$PPP2013<-as.character(PPP$PPP2013)
-PPP$PPP2013<-as.numeric(PPP$PPP2013)
-
-articleCountries<-table(locations$record)
-articleCountries<-as.data.frame(articleCountries)
-articleCountries<-articleCountries%>%
-                    select(Country=Var1, articleCount=Freq)
-
-rankSet<-merge(articleCountries, GDP, by="Country", all=TRUE)
-rankSet$articleCount[is.na(rankSet$articleCount)]<-0
-rankSet<-merge(rankSet, PPP, by="Country", all=TRUE)
-
-rankSet<-mutate(rankSet, articleRank=rank(-articleCount))
 ```
 
-```{r worldmap, eval=FALSE}
+```{r worldmap, eval=TRUE}
 
@@
 
-```{r locationWithtUS, eval=FALSE}
+```{r locationWithtUS, eval=TRUE}
 year.df <- filter(full.df, attributes == "pubYear") %>%
@@
 
-```{r plotLocationWithUS, eval=FALSE}
+```{r plotLocationWithUS, eval=TRUE}
 
@@
 
-```{r nsf, eval=FALSE}
+```{r nsf, eval=TRUE}
 nsf <- data.frame(c(rep(NA, 13), 238, 273, 304, 323, 308, 287, 338, 332, 308, 289, 280, NA), as.factor(seq(1989,2013, 1)))
@@
 
-```{r nsfPlot, eval=FALSE}
+```{r nsfPlot, eval=TRUE}
 plot.PhD <- ggplot(nsf, aes(years, n.grads, group=1)) + 
@@
 
-```{r pages, eval=FALSE}
+```{r pages, eval=TRUE}
 pages.df <- full.df %>% filter(attributes == "pages")
@@
 
-```{r eval=FALSE}
+```{r eval=TRUE}
 save.image(file = "socialWorkHistory.Rdata")
@@
 
-```{r message=FALSE, warning=FALSE, eval=FALSE}
+```{r message=FALSE, warning=FALSE, eval=TRUE}
 cor.data <- select(final.list, first, last, n) %>%
@@
 
-```{r eval=FALSE}
+```{r eval=TRUE}
 journalArticleFinder.f <- function(journalTitle, keyword = FALSE, 

### 2015-04-02 dataCleaning.Rmd
Updated Tableau charts.

@@
 # Read data files
-#load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
-#load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
-#hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
-#countries.csv <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/countries.csv")
-load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
-load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
-hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)
-countries.csv<-read.csv("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/countries.csv")
+load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
+load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
+hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
+countries.csv <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/countries.csv")
+#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
+#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
+#hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)
+#countries.csv<-read.csv("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/countries.csv")
 
 # Load special functions
-#source("/Users/beperron/Git/SocialWorkResearch/functions/appendData.R")
-#source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticles.R")
-#source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
-#source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
-#source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
-#source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/appendData.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticles.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")
 
-source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/appendData.R")
-source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/shortArticles.R")
-source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/titleMatching.R")
-source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/otherDocuments.R")
-source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/titleMatching.R")
-source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/fewArticles.R")
+#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/appendData.R")
+#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/shortArticles.R")
+#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/titleMatching.R")
+#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/otherDocuments.R")
+#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/titleMatching.R")
+#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/fewArticles.R")
 
@@
 indx.country <- paste(countries.csv$x, collapse = "[\\s|[[:punct:]]]|")
+
 library(stringi)
-countries.extracted <- na.omit(within(LO.df2, text1<- stri_extract(LO.df2$record, opts_fixed=TRUE, regex=indx.country)))[-2]
+countries.extracted <- na.omit(within(LO.df2, text1 <- stri_extract(LO.df2$record, regex=indx.country)))[-2]
 countries.extracted$text1<-gsub("[[:punct:]]", "", countries.extracted$text1)
@@
 
-detach(package:stringi)
+#detach(package:stringi)
 
@@
 
+```{r gade, eval=TRUE}
+
+years <- c(1989:2015)
+programs <- rep(NA, 27)
+gade <- as.data.frame(cbind(as.character(years), programs))
+gade$programs <- as.numeric(gade$programs)
+gade[15, 2] <- 72
+gade[27, 2] <- 86
+colnames(gade) <- c("years", "programs")
+```
+
+```{r pages, eval=TRUE}
+pages.tmp <- full.df %>% filter(attributes == "pages")
+years.tmp <- full.df %>% filter(attributes == "pubYear")
+pages.df <- left_join(pages.tmp, years.tmp, by = "articleID") %>% 
+    select(record.y, record.x) %>%
+    rename(years = record.y, pages = record.x) %>%
+    mutate(pages = as.numeric(pages)) %>%
+    group_by(years) %>%
+    summarise(
+        Median.Pages = median(pages, na.rm=TRUE), 
+        Mean.Pages = mean(pages, na.rm=TRUE),
+        Std.Pages = sd(pages, na.rm=TRUE))
+
+```
+
 ```{r nsfPlot, eval=TRUE}
@@
 
-```{r pages, eval=TRUE}
-pages.df <- full.df %>% filter(attributes == "pages")
-page.identifier <- grepl("[-p]", pages.df$record)
-pages.df.reduced <- pages.df[page.identifier == FALSE,]
+```{r}
+colnames(n.journals.year) <- c("years", "journals")
+n_authors2 <- rename(n_authors2, years = ID, Avg.Authors = Average, Mdn.Authors = Median, Sd.Authors = Standard_Deviation)
 
-reduced <- full.df[full.df$articleID %in% pages.df.reduced$articleID, ]
-reduced <- filter(reduced, attributes == "article" | attributes == "journal" | 
-            attributes == "pubYear" | attributes == "pages" | attributes == "abstract")
+scholarly.df <- left_join(articles.year.df, n.journals.year, by = "years") 
+scholarly.df <- left_join(scholarly.df, n_authors2, by = "years")
+scholarly.df <- left_join(scholarly.df, nsf, by = "years")
+scholarly.df <- left_join(scholarly.df, pages.df, by = "years")
+scholarly.df[c(26, 27), ] <- rep(NA)
+scholarly.df[26, 1] <- 2014
+scholarly.df[27, 1] <- 2015
+
+scholarly.df <- mutate(scholarly.df, years = as.numeric(years)) %>%
+    rename(article.count = year.count, journal.count = year.count, program.growth = growth) 
+scholarly.df$gade <- rep(NA, nrow(scholarly.df))  
+scholarly.df$gade[15] <- 72
+scholarly.df$gade[27] <- 86
+
+write.csv(scholarly.df, file = "scholarship.csv")
 

### 2015-04-02 dataCleaning.Rmd
Updated image. Fixed Social Work Research & Abstracts title.

--- 2015-03-29 dataCleaning.Rmd
@@
 ---
-title: "25 years of Social Work Research"
-author: "Summary of Data Cleaning Procedures"
+title: "Examining a Quarter Century of Publishing Trends in Social Work: A Data Science Perspective"
+author: 
 output: pdf_document
@@
 # Read data files
-#load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
-#load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
-#hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
-#countries.csv <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/countries.csv")
-load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
-load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
-hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)
-countries.csv<-read.csv("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/countries.csv")
+load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
+load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
+hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
+countries.csv <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/countries.csv")
+#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
+#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
+#hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)
+#countries.csv<-read.csv("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/countries.csv")
 
@@
 
-```{r locationExtraction}
+```{r locationExtraction, eval=FALSE}
 LO.df <- filter(full.df, attributes == "location") %>%
@@
 
-detach(package:stringi)
+#detach(package:stringi)
 
 setwd("C:/Users/SSW/Documents/GitHub/SocialWork100Years/Data")
-GDP<-read.csv("GDP.csv")
-GDP<-select(GDP, Country=Country.Name, GDPperCapita=GDPperCapita2013, GDPRank)
+rankSet<-read.csv("rankSet.csv")
 
-PPP<-read.csv("PPP.csv")
-PPP$PPP2013<-gsub(",", "", PPP$PPP2013)
-PPP$PPP2013<-as.character(PPP$PPP2013)
-PPP$PPP2013<-as.numeric(PPP$PPP2013)
-
-articleCountries<-table(locations$record)
-articleCountries<-as.data.frame(articleCountries)
-articleCountries<-articleCountries%>%
-                    select(Country=Var1, articleCount=Freq)
-
-rankSet<-merge(articleCountries, GDP, by="Country", all=TRUE)
-rankSet$articleCount[is.na(rankSet$articleCount)]<-0
-rankSet<-merge(rankSet, PPP, by="Country", all=TRUE)
-
-rankSet<-mutate(rankSet, articleRank=rank(-articleCount))
 ```
@@
 
-write.csv(nsf, file="nsf.csv")
+#write.csv(nsf, file="nsf.csv")
+
+```
+
+```{r gade, eval=FALSE}
+
+years <- c(1989:2015)
+programs <- rep(NA, 27)
+gade <- as.data.frame(cbind(as.character(years), programs))
+gade$programs <- as.numeric(gade$programs)
+gade[15, 2] <- 72
+gade[27, 2] <- 86
+colnames(gade) <- c("years", "programs")
+```
+
+```{r pages, eval=FALSE}
+pages.tmp <- full.df %>% filter(attributes == "pages")
+years.tmp <- full.df %>% filter(attributes == "pubYear")
+pages.df <- left_join(pages.tmp, years.tmp, by = "articleID") %>% 
+    select(record.y, record.x) %>%
+    rename(years = record.y, pages = record.x) %>%
+    mutate(pages = as.numeric(pages)) %>%
+    group_by(years) %>%
+    summarise(
+        Median.Pages = median(pages, na.rm=TRUE), 
+        Mean.Pages = mean(pages, na.rm=TRUE),
+        Std.Pages = sd(pages, na.rm=TRUE))
 
@@
 
-```{r pages, eval=FALSE}
-pages.df <- full.df %>% filter(attributes == "pages")
-page.identifier <- grepl("[-p]", pages.df$record)
-pages.df.reduced <- pages.df[page.identifier == FALSE,]
+```{r eval=FALSE}
+colnames(n.journals.year) <- c("years", "journals")
+n_authors2 <- rename(n_authors2, years = ID, Avg.Authors = Average, Mdn.Authors = Median, Sd.Authors = Standard_Deviation)
 
-reduced <- full.df[full.df$articleID %in% pages.df.reduced$articleID, ]
-reduced <- filter(reduced, attributes == "article" | attributes == "journal" | 
-            attributes == "pubYear" | attributes == "pages" | attributes == "abstract")
+scholarly.df <- left_join(articles.year.df, n.journals.year, by = "years") 
+scholarly.df <- left_join(scholarly.df, n_authors2, by = "years")
+scholarly.df <- left_join(scholarly.df, nsf, by = "years")
+scholarly.df <- left_join(scholarly.df, pages.df, by = "years")
+scholarly.df[c(26, 27), ] <- rep(NA)
+scholarly.df[26, 1] <- 2014
+scholarly.df[27, 1] <- 2015
+
+scholarly.df <- mutate(scholarly.df, years = as.numeric(years)) %>%
+    rename(article.count = year.count, journal.count = year.count, program.growth = growth) 
+scholarly.df$gade <- rep(NA, nrow(scholarly.df))  
+scholarly.df$gade[15] <- 72
+scholarly.df$gade[27] <- 86
+
+#write.csv(scholarly.df, file = "scholarship.csv")
 

### 2015-04-02 functions/appendData.R

@@ -115,6 +115,12 @@ appendData.f <- function(){
                              "British Journal of Social Work",
                              full.df$record)
 
+    full.df$record <- ifelse(full.df$record ==
+                               "Social Work Research & Abstracts",          # Spelling difference
+                             "Social Work Research",
+                             full.df$record)
+    
+    
     #shortens Professional Development
     full.df$record <- ifelse(full.df$attributes == "journal",
                              gsub(":.+", "", full.df$record),

### 2015-04-02 dataCleaning.Rmd
Location code removed. Updated append function for initial counts.

@@
 
-```{r initialization}
+```{r BEPinitialization, eval=TRUE}
 rm(list=ls())  
 load("/Users/beperron/Git/SocialWorkResearch/socialWorkHistory.Rdata")
-#load("/Users/SSW/Documents/GitHub/SocialWork100Years/socialWorkHistory.Rdata")
 
@@
 
-```
-
-```{r eval=FALSE}
 # Read data files
@@
 hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
-countries.csv <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/countries.csv")
-#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
-#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
-#hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)
-#countries.csv<-read.csv("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/countries.csv")
 
-# Load special functions
 source("/Users/beperron/Git/SocialWorkResearch/functions/appendData.R")
@@
 source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/pretty.R")
+```
 
-#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/appendData.R")
-#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/shortArticles.R")
-#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/titleMatching.R")
-#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/otherDocuments.R")
-#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/titleMatching.R")
-#source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/fewArticles.R")
+```{r BGVinitialization, eval=FALSE}
+rm(list=ls())  
+load("/Users/SSW/Documents/GitHub/SocialWork100Years/socialWorkHistory.Rdata")
 
-pretty <- function(x){
-    x <- prettyNum(x,big.mark=",",scientific=F)
-    x
-    }
+# Load required packages
+library(ggplot2)
+library(dplyr)
+library(gridExtra)
+library(rworldmap)
+
+load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
+load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
+hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)
+
+source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/appendData.R")
+source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/shortArticles.R")
+source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/titleMatching.R")
+source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/otherDocuments.R")
+source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/titleMatching.R")
+source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/fewArticles.R")
+source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/pretty.R")
 ```
@@
 
-```{r locationExtraction, eval=FALSE}
-LO.df <- filter(full.df, attributes == "location") %>%
-         group_by(record) %>%
-         summarise(Country = unique(record),
-                   N = n()) %>%
-        arrange(desc(N)) %>% 
-        select(-record)
-```
-
-```{r locationExtraction2, eval=FALSE}
-LO.df2 <- filter(full.df, attributes == "abstract" |
-                 attributes == "article" | attributes == "keyword")
-indx.country <- paste(countries.csv$x, collapse = "[\\s|[[:punct:]]]|")
-
-library(stringi)
-countries.extracted <- na.omit(within(LO.df2, text1 <- stri_extract(LO.df2$record, regex=indx.country)))[-2]
-countries.extracted$text1<-gsub("[[:punct:]]", "", countries.extracted$text1)
-countries.extracted$text1<-gsub("^\\s+|\\s+$", "", countries.extracted$text1)
-
-new.countries<-unique(countries.extracted[,c("articleID","text1")])
-new.countries<-mutate(new.countries, attributes="location")
-new.countries<-select(new.countries, articleID, attributes, record=text1)
-
-loc<-filter(full.df, attributes=="location")
-locations<-rbind(loc, new.countries)
-locations<-unique(locations[,c("articleID","attributes","record")])
-locations<-filter(locations, record!="NA")
-
-#Set of code to address labeling issues related to the United Kingdom
-
-locations$record[locations$record=="Great Britain"]<- "United Kingdom"    #Combines Great Britain and UK records
-
-uk<-filter(locations, record=="United Kingdom")  #creates temp DF with only UK records
-ukID<-uk$articleID
-
-#next four blocks of code check to see if the United Kindgom and each country are both listed as a research site and eliminates the UK location record when this was the case.
-This means that remaining UK records represent cases of research within the UK in an unspecified country.
-
-scot<-filter(locations, record=="Scotland") 
-scotID<-scot$articleID
-remove<-ukID%in%scotID
-uk.remove<-cbind(uk, remove)
-uk.remove<-filter(uk, remove==TRUE)
-uk.remove.ID<-uk.remove$articleID
-uk<-uk[!(uk$articleID%in%uk.remove.ID),]
-ukID<-uk$articleID
-
-eng<-filter(locations, record=="England")  
-engID<-eng$articleID 
-remove<-ukID%in%engID
-uk.remove<-cbind(uk, remove)
-uk.remove<-filter(uk, remove==TRUE)
-uk.remove.ID<-uk.remove$articleID
-uk<-uk[!(uk$articleID%in%uk.remove.ID),]
-ukID<-uk$articleID
-
-ni<-filter(locations, record=="Northern Ireland") 
-niID<-ni$articleID
-remove<-ukID%in%niID
-uk.remove<-cbind(uk, remove)
-uk.remove<-filter(uk, remove==TRUE)
-uk.remove.ID<-uk.remove$articleID
-uk<-uk[!(uk$articleID%in%uk.remove.ID),]
-ukID<-uk$articleID
-
-wales<-filter(locations, record=="Wales") 
-walesID<-wales$articleID
-remove<-ukID%in%walesID
-uk.remove<-cbind(uk, remove)
-uk.remove<-filter(uk, remove==TRUE)
-uk.remove.ID<-uk.remove$articleID
-uk<-uk[!(uk$articleID%in%uk.remove.ID),]
-ukID<-uk$articleID
-
-locations<-filter(locations, record!="United Kingdom")  #removes old UK records
-locations<-rbind(locations, uk)
-
-locations$record[locations$record=="US"]<-"United States"
-locations$record[locations$record=="Appalachia"]<-"United States"
-locations$record[locations$record=="Bosnia"]<-"Bosnia-Herzegovina"
-locations$record[locations$record=="Democratic Republic of Congo"]<- "Congo (Brazzaville)"
-locations$record[locations$record=="Democratic Republic of the Congo"]<- "Congo (Brazzaville)"
-locations$record[locations$record=="Holland"]<- "Netherlands"
-locations$record[locations$record=="West Bank"]<-"Palestine"
-locations$record[locations$record=="Gaza"]<-"Palestine"
-locations$record[locations$record=="Gaza Strip"]<-"Palestine"
-locations$record[locations$record=="Trinidad"]<-"Trinidad and Tobago"
-locations$record[locations$record=="Gaza"]<-"Palestine"
-locations$record[locations$record=="England"]<-"United Kingdom"
-locations$record[locations$record=="Northern Ireland"]<-"United Kingdom"
-locations$record[locations$record=="Scotland"]<-"United Kingdom"
-locations$record[locations$record=="Wales"]<-"United Kingdom"
-
-full.df<-filter(full.df, attributes!="location")
-full.df<-rbind(full.df, locations)
-
-#detach(package:stringi)
-
-setwd("C:/Users/SSW/Documents/GitHub/SocialWork100Years/Data")
-rankSet<-read.csv("rankSet.csv")
-
-```
-
-```{r worldmap, eval=FALSE}
-
-###Code for creating world maps.  The four countries in the UK are recoded as "United Kingdom" for data visualization.
-library(rworldmap)
-
-loc.tab<-table(locations$record)
-
-loc.tab<-as.data.frame(loc.tab)
-loc.tab<-select(loc.tab, country=Var1, frequency=Freq)
-
-#join to a coarse resolution map
-spdf <- joinCountryData2Map(loc.tab, joinCode="NAME", nameJoinColumn="country")
-
-loc.tab2<-filter(loc.tab, frequency>=25)
-spdf2 <- joinCountryData2Map(loc.tab2, joinCode="NAME", nameJoinColumn="country")
-
-```
-
-```{r locationWithtUS, eval=FALSE}
-year.df <- filter(full.df, attributes == "pubYear") %>%
-            select(articleID, record)
-
-location.df <- filter(full.df, attributes == "location") %>%
-            select(articleID, record)
-
-year.location.df <- left_join(year.df, location.df, by = "articleID")
-
-colnames(year.location.df) <- c("articleID", "pubYear", "country")
-year.location.df <- year.location.df[!is.na(year.location.df$country), ]
-
-location.summary.df <- group_by(year.location.df, country) %>%
-           summarize(Number = n()) %>%
-           arrange(desc(Number)) %>%
-           slice(1:6) %>%
-           select(country)
-
-location.df.withUS <- location.df[location.df$record %in% location.summary.df$country, ]
-year.location.df.withUS <- left_join(location.df.withUS, year.df, by = "articleID") 
-colnames(year.location.df.withUS) <- c("articleID", "country", "pubYear")
-year.location.df.withUS <- group_by(year.location.df.withUS, country, pubYear) %>%
-                    summarise(N = n())
-
-location.summary.df.noUS <- group_by(year.location.df, country) %>%
-           summarize(Number = n()) %>%
-           arrange(desc(Number)) %>%
-           slice(2:7) %>%
-           select(country)
-
-location.df.noUS <- location.df[location.df$record %in% location.summary.df.noUS$country, ]
-year.location.df.noUS <- left_join(location.df.noUS, year.df, by = "articleID") 
-colnames(year.location.df.noUS) <- c("articleID", "country", "pubYear")
-year.location.df.noUS <- group_by(year.location.df.noUS, country, pubYear) %>%
-                    summarise(N = n())
-```
-
-```{r plotLocationWithUS, eval=FALSE}
-
-cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
-
-plot.location.withUS <- ggplot(year.location.df.withUS, aes(pubYear, N, group = country, colour=country)) + 
-    geom_line() +
-    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
-          title = element_text(size = 10), 
-          legend.title=element_blank())  +
-    scale_y_continuous(limits = c(0,700)) + 
-    xlab("Year") +
-    ylab("Articles") +
-    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) + 
-    scale_colour_manual(values=cbPalette) +
-    ggtitle("Number of Articles by Country and Year")
-
-plot.location.noUS <- ggplot(year.location.df.noUS, aes(pubYear, N, group = country, colour=country)) + 
-    geom_line() +
-    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
-          title = element_text(size = 10), 
-          legend.title=element_blank())  +
-    scale_y_continuous(limits = c(0,150)) + 
-    xlab("Year") +
-    ylab("Articles") +
-    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) + 
-    scale_colour_manual(values=cbPalette) +
-    ggtitle("Number of Articles by Country and Year, United States Excluded")
-
-```
-
 ```{r nsf, eval=FALSE}
@@
 ```{r gade, eval=FALSE}
-
 years <- c(1989:2015)
@@
 #write.csv(scholarly.df, file = "scholarship.csv")
-
 ```
@@
 These files were post-processed into a structured database using a set of scripts written in the R statistical programming language.
-The initial search resulted in 36,094 article records from 117 different journals.
-```NOTE: these values are hardcoded--should be changed to draw from actual data.```
+The initial search resulted in `r pretty(nrow(article.count.initial))` article records from `r journal.count.initial`.
 
@@
 
-```{r}
-mapCountryData(spdf, nameColumnToPlot="frequency", catMethod="quantiles", 
-                                  colourPalette="white2Black", 
-                                  mapTitle="Article Counts by Country, 1989-2013")
-```
-
-\newpage
-```{r}
-mapCountryData(spdf2, nameColumnToPlot="frequency", catMethod="quantiles", 
-                    colourPalette="white2Black", 
-                    mapTitle="Article Counts for Countries with Sustained Presence, 1989-2013")
-
-```
-
-\newpage
-```{r}
-plot.location.withUS
-```
-
-```{r}
-plot.location.noUS
-```
-
 \newpage

### 2015-04-02 functions/appendData.R

@@ -19,6 +19,15 @@ appendData.f <- function(){
 
     full.df <- full.df[!(full.df$articleID %in% year.removeID), ]
 
+    article.count <- filter(full.df, attributes == "article") 
+    article.count.initial <<- article.count
+    journal.count <- filter(full.df, attributes == "journal")
+    
+    journal.count.initial <<- length(unique(journal.count$record))
+    
+    
+    
+    
     full.df$record <- ifelse(full.df$record ==
                                  "The British Journal of Social Work",          # Spelling difference
                              "British Journal of Social Work",

### 2015-04-02 dataCleaning.Rmd
Major cleaning. All functional.

@@
 
-\newpage
-
 ```{r}
@@
 ```
-
-```{r eval=FALSE}
-journalArticleFinder.f <- function(journalTitle, keyword = FALSE, 
-                           authorAff = FALSE, abstract = FALSE){
-    article.search <- which(full.df$record == journalTitle)
-    article.search <- full.df[article.search,]
-    article.search.ID <- select(article.search, articleID)
-    target.ID <- full.df$articleID %in% article.search.ID$articleID
-    journal.article.df <- full.df[target.ID, ]
-    journal.article.df <- filter(journal.article.df, attributes == "article")
-    journal.article.df <- arrange(journal.article.df, record)
-    if(keyword == FALSE){journal.article.df <- filter(journal.article.df, attributes != "keyWord")}
-    if(authorAff == FALSE){journal.article.df <- filter(journal.article.df, attributes != "authorAff")}
-    if(abstract == FALSE){journal.article.df <- filter(journal.article.df, attributes != "abstract")}
-    x.shortened <- gsub(" ", "", journalTitle)
-    write.csv(journal.article.df, file = paste0(x.shortened, ".csv"), row.names=F)
-    }
-
-journalArticleFinder.f("Journal of Gerontological Social Work")
-#journalArticleFinder.f("Social Work")
-
-articles <- filter(full.df, attributes == "article") %>% arrange(record)
-write.csv(articles, file = "articles.csv")
-
-```

### 2015-04-02 functions/journalArticleFinder.R

@@ -1,0 +1,15 @@
+journalArticleFinder.f <- function(journalTitle, keyword = FALSE, 
+                                   authorAff = FALSE, abstract = FALSE){
+  article.search <- which(full.df$record == journalTitle)
+  article.search <- full.df[article.search,]
+  article.search.ID <- select(article.search, articleID)
+  target.ID <- full.df$articleID %in% article.search.ID$articleID
+  journal.article.df <- full.df[target.ID, ]
+  journal.article.df <- filter(journal.article.df, attributes == "article")
+  journal.article.df <- arrange(journal.article.df, record)
+  if(keyword == FALSE){journal.article.df <- filter(journal.article.df, attributes != "keyWord")}
+  if(authorAff == FALSE){journal.article.df <- filter(journal.article.df, attributes != "authorAff")}
+  if(abstract == FALSE){journal.article.df <- filter(journal.article.df, attributes != "abstract")}
+  x.shortened <- gsub(" ", "", journalTitle)
+  write.csv(journal.article.df, file = paste0(x.shortened, ".csv"), row.names=F)
+}

### 2015-04-02 dataCleaning.Rmd
Additional cleaning and organization. All functional.

@@
 ---
-title: "Examining a Quarter Century of Publishing Trends in Social Work: A Data Science Perspective"
+title: "Examining a Quarter Century of Publishing Trends in Social Work Research: A Data Science Perspective"
 author: 
@@
 
-```{r appendData, comment=NA, echo=FALSE, eval=FALSE}
+```{r dataCleaning, comment=NA, echo=FALSE, eval=FALSE}
 appendData.f()
+shortArticles.f()
+titleMatching.f()
+otherDocuments.f()
+fewArticles.f()
+save.image(file = "socialWorkHistory.Rdata")
+```
 
+```{r eval=TRUE}
 append.articles <- length(which(full.df$attributes == "article"))
@@
         N = n())
-```
-
-```{r shortArticles, comment=NA, echo=FALSE, warning=FALSE, eval=FALSE}
-shortArticles.f()
-```
-
-```{r titleMatching, echo=FALSE, eval=FALSE}
-titleMatching.f()
 
@@
         summarise(Unique = n_distinct(record))
-```
 
-```{r otherDocuments, echo=FALSE, eval=FALSE}
-otherDocuments.f()
 articles.otherDocuments <- length(which(full.df$attributes == "article"))
@@
     summarise(Unique = n_distinct(record))
-```
 
-```{r final, comment=NA, echo=FALSE, eval=FALSE}
-fewArticles.f()
 articles.final <- length(which(full.df$attributes == "article"))
@@
     summarise(Unique = n_distinct(record))
+
 ```
 
-```{r finalList, comment=NA, echo=FALSE, eval=FALSE}
+```{r finalList, comment=NA, echo=FALSE, eval=TRUE}
 unique.titles <- filter(full.df, attributes == "journal") %>%
@@
 
-```{r eval=FALSE}
+```{r eval=TRUE}
 colnames(n.journals.year) <- c("years", "journals")
@@
 scholarly.df$gade[27] <- 86
-
-#write.csv(scholarly.df, file = "scholarship.csv")
-```
-
-```{r eval=FALSE}
-save.image(file = "socialWorkHistory.Rdata")
 ```
@@
 ```
-
-```{r message=FALSE, warning=FALSE, eval=FALSE}
-cor.data <- select(final.list, first, last, n) %>%
-            mutate(no.years = as.numeric(last) - as.numeric(first))
-
-ggplot(cor.data, aes(x = no.years, y = n)) + 
-            geom_point(shape = 1) + 
-            geom_smooth() + 
-            xlab("Years") + 
-            ylab("Number of articles")
-```

### 2015-04-03 dataCleaning.Rmd
Major cleanup. Bug fixes. All functional.

@@
 rm(list=ls())
+
 load("/Users/beperron/Git/SocialWorkResearch/socialWorkHistory.Rdata")
@@
 library(gridExtra)
-library(rworldmap)
-
-# Read data files
-load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
-load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
-hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
-
-source("/Users/beperron/Git/SocialWorkResearch/functions/appendData.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticles.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/pretty.R")
 ```
@@
 library(gridExtra)
-library(rworldmap)
-
-load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
-load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
-hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)
-
-source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/appendData.R")
-source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/shortArticles.R")
-source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/titleMatching.R")
-source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/otherDocuments.R")
-source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/titleMatching.R")
-source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/fewArticles.R")
-source("/Users/SSW/Documents/GitHub/SocialWork100Years/functions/pretty.R")
 ```
 
-```{r dataCleaning, comment=NA, echo=FALSE, eval=FALSE}
-appendData.f()
-shortArticles.f()
-titleMatching.f()
-otherDocuments.f()
-fewArticles.f()
-save.image(file = "socialWorkHistory.Rdata")
+```{r imageMaker, comment=NA, echo=FALSE, eval=FALSE}
+# Read data files
+#load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
+#load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
+#hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
+
+#source("/Users/beperron/Git/SocialWorkResearch/functions/appendData.R")
+#source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticles.R")
+#source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
+#source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
+#source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
+#source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")
+#source("/Users/beperron/Git/SocialWorkResearch/functions/pretty.R")
+
+#appendData.f()
+#shortArticles.f()
+#titleMatching.f()
+#otherDocuments.f()
+#fewArticles.f()
+#save.image(file = "socialWorkHistory.Rdata")
 ```
 
-```{r eval=TRUE}
-append.articles <- length(which(full.df$attributes == "article"))
-append.journals <- filter(full.df, attributes == "journal") %>% 
+```{r methodSummaryData, eval=TRUE}
+append.articles <- length(which(full.append.df$attributes == "article"))
+append.journals <- filter(full.append.df, attributes == "journal") %>% 
     summarise(Unique = n_distinct(record))
@@
 
-```{r finalList, comment=NA, echo=FALSE, eval=TRUE}
+```{r Table_1, comment=NA, echo=FALSE, eval=TRUE}
 unique.titles <- filter(full.df, attributes == "journal") %>%
@@
 
-```{r gade, eval=FALSE}
+```{r gade, eval=TRUE}
 years <- c(1989:2015)
@@
 
-```{r pages, eval=FALSE}
+```{r pages, eval=TRUE}
 pages.tmp <- full.df %>% filter(attributes == "pages")
@@
 scholarly.df$gade[27] <- 86
+```
+
+```{r appendix_A_intersection}
+unique.swHistory <- filter(full.df, attributes == "journal") %>%
+                distinct(record)
+
+hodge.swHistory.intersect <- intersect(hodge, unique.swHistory$record)
+
+hodge.swHistory.diff <- setdiff(hodge, unique.swHistory$record)
+
 ```
@@
 As an additional requirement, we required all articles to be $\geq 3$ pages in length.
-Finally, we eliminated all social work journals with total article counts of < 10 for the enitre 25 year window (_Issues in Social Work Education_, _Maatskaplike Werk/Social Work_, _Pediatric Social Work_, and _Critical Social Work_).
+Finally, we eliminated all social work journals with total article counts of < 10 for the entire 25 year window (_Issues in Social Work Education_, _Maatskaplike Werk/Social Work_, _Pediatric Social Work_, and _Critical Social Work_).
 These cleaning procedures resulted in a final database of `r pretty(articles.final)` articles and `r journals.final` journals.
@@
 # Appendix A
-```{r intersection}
-unique.swHistory <- filter(full.df, attributes == "journal") %>%
-                distinct(record)
-
-hodge.swHistory.intersect <- intersect(hodge, unique.swHistory$record)
-
-hodge.swHistory.diff <- setdiff(hodge, unique.swHistory$record)
-swHistory.hodge.diff <- setdiff(unique.swHistory$record, hodge)
-
-#hodge.swHistory.union <- union(hodge, unique.swHistory$record)
-```
 
@@
 
-```{r}
+```{r appendix_Print, eval=TRUE}
 print(sort(hodge.swHistory.diff))

### 2015-04-03 functions/appendData.R

@@ -185,9 +185,11 @@ appendData.f <- function(){
                              full.df$record)
 
     full.df$record <- ifelse(full.df$record ==
-                                 "Journal of Practice Teaching in Social Work and Practice", #Old title
-                             "Journal of Practice Teaching in Social Work and Health",   #New title
-                             full.df$record)
+              "Journal of Practice Teaching in Social Work and Practice" |
+                full.df$record == "Journal of Practice Teaching in Social Work & Practice" |
+                full.df$record == "Journal of Practice Teaching in Social Work and Health", #Old title
+               "Journal of Practice Teaching in Social Work & Health",   #New title
+                full.df$record)
 
     # Journals were originally merged after suffixes were eliminated (after the
     # colon).  Thus, Practice: Social Work in Action  (new title) was shortened to
@@ -223,9 +225,11 @@ appendData.f <- function(){
         "Journal of Nonverbal Behavior",
         "Journal of Psychosomatic Research",
         "Learning Disabilities Research & Practice",
+        "Prevention in Human Services",
         "Professional Development in Education",
         "PROFILE Issues in Teachers' Professional Development",
         "Psychotherapy",
+        "Social Development",
         "Systems Research and Behavioral Science",
         "Systems Research & Behavioral Science",
         "Teaching & Teacher Education",
@@ -238,4 +242,5 @@ appendData.f <- function(){
     ebsco.remove <- full.df[full.df$record %in% exclusions.1, ]
     ebsco.remove <- ebsco.remove[, "articleID"]
     full.df <<- full.df[!(full.df$articleID %in% ebsco.remove),]
+    full.append.df <<- full.df
 }

### 2015-04-03 functions/fewArticles.R

@@ -19,7 +19,7 @@ fewArticles.f <- function(){
 
     ebsco.remove <- full.df[full.df$record %in% exclusions.2, ]
     ebsco.remove <- ebsco.remove[, "articleID"]
-    full.df <<- full.df[!(full.df$articleID %in% ebsco.remove),]
+    full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
     
     author<-filter(full.df, attributes=="author")
     no.author<-filter(author, grepl("authorship|anonymous", record, ignore.case=TRUE))

### 2015-04-03 functions/journalArticleFinder.R

@@ -7,9 +7,9 @@ journalArticleFinder.f <- function(journalTitle, keyword = FALSE,
   journal.article.df <- full.df[target.ID, ]
   journal.article.df <- filter(journal.article.df, attributes == "article")
   journal.article.df <- arrange(journal.article.df, record)
-  if(keyword == FALSE){journal.article.df <- filter(journal.article.df, attributes != "keyWord")}
-  if(authorAff == FALSE){journal.article.df <- filter(journal.article.df, attributes != "authorAff")}
-  if(abstract == FALSE){journal.article.df <- filter(journal.article.df, attributes != "abstract")}
+  #if(keyword == TRUE){journal.article.df <- filter(journal.article.df, attributes == "keyWord")}
+  #if(authorAff == TRUE){journal.article.df <- filter(journal.article.df, attributes == "authorAff")}
+  #if(abstract == TRUE){journal.article.df <- filter(journal.article.df, attributes == "abstract")}
   x.shortened <- gsub(" ", "", journalTitle)
   write.csv(journal.article.df, file = paste0(x.shortened, ".csv"), row.names=F)
 }

### 2015-04-03 quartile_calculations.R
Removed files.

@@ -1,9 +1,0 @@
-
-
-
-updateJournalList <- read.csv("journalList.csv")
-
-
-updateJournalList <- within(updateJournalList, quartile <- as.integer(cut(hIndex, quantile(hIndex, probs=0:4/4, na.rm=TRUE), include.lowest=TRUE)))
-
-write.csv(updateJournalList, file = "journalList.csv")

### 2015-04-03 manuscript.Rmd
Major cleanup. All functional.

--- 2015-04-03 dataCleaning.Rmd
@@
 ---
-title: "Examining a Quarter Century of Publishing Trends in Social Work Research: A Data Science Perspective"
-author: 
+title: 'Examining a Quarter Century of Publishing Trends in Social Work Research:
+  A Data Science Perspective'
+author: ''
 output: pdf_document
@@
 # Read data files
-#load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
-#load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
-#hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
+load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
+load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
+hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
 
-#source("/Users/beperron/Git/SocialWorkResearch/functions/appendData.R")
-#source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticles.R")
-#source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
-#source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
-#source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
-#source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")
-#source("/Users/beperron/Git/SocialWorkResearch/functions/pretty.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/combineData.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/cleaningJournals.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticles.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/pretty.R")
 
-#appendData.f()
-#shortArticles.f()
-#titleMatching.f()
-#otherDocuments.f()
-#fewArticles.f()
+combineData.f()
+cleaningJournals.f()
+shortArticles.f()
+titleMatching.f()
+otherDocuments.f()
+fewArticles.f()
 #save.image(file = "socialWorkHistory.Rdata")
@@
 ```{r methodSummaryData, eval=TRUE}
-append.articles <- length(which(full.append.df$attributes == "article"))
-append.journals <- filter(full.append.df, attributes == "journal") %>% 
-    summarise(Unique = n_distinct(record))
+#append.articles <- length(which(full.append.df$attributes == "article"))
+#append.journals <- filter(full.append.df, attributes == "journal") %>% 
+#    summarise(Unique = n_distinct(record))
 
@@
 This initiative was designed to support four broad goals:  1) to facilitate use of biomedical digital assets by making them discoverable, accessible, and citable; 2) to conduct research and develop methods, software and tools to analyze biomedical big data; 3) to enhance training in the development of use and tools necessary for biomedical big data science; and 4) to support a data ecosystem that accelerates discovery as part of the digital enterprise (NIH).
-At roughly the same time, the National Science Foundation (NSF) created new initiatives to harness the potential of the data revolution, arguing that ”data are motivating a profound transformation in the culture and conduct of scientific research in every field of science and engineering ...
+At roughly the same time, the National Science Foundation (NSF) created new initiatives to harness the potential of the data revolution, arguing that "data are motivating a profound transformation in the culture and conduct of scientific research in every field of science and engineering ...
 American scientists must rise to the challenges and seize the opportunities afforded by this new, data-driven revolution" (Suresh, XXX).
@@
 A consensus was reached on all journal titles to be excluded and retained.
-After these procedures, the number of article records and journal titles was reduced to `r pretty(append.articles)` and `r append.journals` (respectively).
+After these procedures, the number of article records and journal titles was reduced to `r pretty(nrow(article.count.journalsCleaned))` and `r journal.count.journalsCleaned`.
 

### 2015-04-03 functions/appendData.R

@@ -1,32 +1,4 @@
 appendData.f <- function(){
-    # Combines EbscoHost and ProQUest
-
-    #Creates variable with highest article ID from ebscohost database
-    ebscoIDmax<-max(ebscoBWR.df$articleID)
-
-    #Recodes article ID in ProQuest database in advance of merger with ebscohost
-    proQuestBWR.df<-mutate(proQuestBWR.df, articleID=articleID+ebscoIDmax)
-
-    full.df <- rbind(ebscoBWR.df, proQuestBWR.df)
-
-
-    year.25 <- as.character(c(1900:1988, 2014, 2015))
-
-    temp.df <- filter(full.df, attributes == "pubYear")
-
-    year.remove <- temp.df[temp.df$record %in% year.25, ]
-    year.removeID <- year.remove$articleID
-
-    full.df <- full.df[!(full.df$articleID %in% year.removeID), ]
-
-    article.count <- filter(full.df, attributes == "article") 
-    article.count.initial <<- article.count
-    journal.count <- filter(full.df, attributes == "journal")
-    
-    journal.count.initial <<- length(unique(journal.count$record))
-    
-    
-    
     
     full.df$record <- ifelse(full.df$record ==
                                  "The British Journal of Social Work",          # Spelling difference

### 2015-04-03 functions/cleaningJournals.R

@@ -1,0 +1,225 @@
+cleaningJournals.f <- function(){
+    
+    full.df$record <- ifelse(full.df$record ==
+                                 "The British Journal of Social Work",          # Spelling difference
+                             "British Journal of Social Work",
+                             full.df$record)
+
+    full.df$record <- ifelse(full.df$record ==
+                                 "Revista de Asistenta Sociala (Social Work Review)",
+                             "Social Work Review",
+                             full.df$record)
+
+    full.df$record <- gsub("Arete", "xxx", full.df$record)
+    full.df$record <- gsub("Aret.{1,3}", "Arete", full.df$record)
+    full.df$record <- gsub("xxx", "Arete", full.df$record)
+    #Replaces special character
+    #in Arete and preserves other formatting
+
+    full.df$record <- ifelse(full.df$record ==
+                                 "Journal of Gay and Lesbian Social Services",     #Spelling difference
+                             "Journal of Gay & Lesbian Social Services",
+                             full.df$record)
+
+    full.df$record <- ifelse(full.df$record ==
+                                 "Canadian Social Work Review/Revue canadienne de service social",
+                             "Canadian Social Work Review",
+                             full.df$record)
+
+    full.df$record <- ifelse(full.df$record ==
+                                 "INDIAN JOURNAL OF SOCIAL WORK",                    #Spelling difference
+                             "Indian Journal of Social Work",
+                             full.df$record)
+
+    full.df$record <- ifelse(full.df$record ==
+                                 "The Indian Journal of Social Work",              #Spelling difference
+                             "Indian Journal of Social Work",
+                             full.df$record)
+
+    full.df$record <- ifelse(full.df$record ==
+                                 "Asia Pacific Journal of Social Work",              #Spelling difference
+                             "Asia Pacific Journal of Social Work and Development",
+                             full.df$record)
+
+    full.df$record <- ifelse(full.df$record ==
+                                 "Social Work & Society",                           #Spelling difference
+                             "Social Work and Society",
+                             full.df$record)
+
+    full.df$record <- ifelse(full.df$record ==
+                                 "Journal of Social Work in Disability & Rehabilitation",
+                             "Journal of Social Work in Disability and Rehabilitation",
+                             full.df$record)           #Spelling difference
+
+    full.df$record <- ifelse(full.df$record ==
+                                 "Hong Kong Journal of Social Work",
+                             "The Hong Kong Journal of Social Work",
[…]

### 2015-04-03 functions/combineData.R

@@ -1,0 +1,28 @@
+combineData.f <- function(){
+    # Combines EbscoHost and ProQUest
+
+    #Creates variable with highest article ID from ebscohost database
+    ebscoIDmax<-max(ebscoBWR.df$articleID)
+
+    #Recodes article ID in ProQuest database in advance of merger with ebscohost
+    proQuestBWR.df<-mutate(proQuestBWR.df, articleID=articleID+ebscoIDmax)
+
+    full.df <- rbind(ebscoBWR.df, proQuestBWR.df)
+
+
+    year.25 <- as.character(c(1900:1988, 2014, 2015))
+
+    temp.df <- filter(full.df, attributes == "pubYear")
+
+    year.remove <- temp.df[temp.df$record %in% year.25, ]
+    year.removeID <- year.remove$articleID
+
+    full.df <- full.df[!(full.df$articleID %in% year.removeID), ]
+    full.df <<- full.df
+    article.count.initial <<- filter(full.df, attributes == "article") 
+    journal.count <- filter(full.df, attributes == "journal")
+    journal.count.initial <<- length(unique(journal.count$record))
+}
+    
+    
+    

### 2015-04-03 manuscript.Rmd
Minor comments.

@@
 # Read data files
-load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
-load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
-hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
-
-source("/Users/beperron/Git/SocialWorkResearch/functions/combineData.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/cleaningJournals.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticles.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/pretty.R")
-
-combineData.f()
-cleaningJournals.f()
-shortArticles.f()
-titleMatching.f()
-otherDocuments.f()
-fewArticles.f()
+# load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
+# load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
+# hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
+# 
+# source("/Users/beperron/Git/SocialWorkResearch/functions/combineData.R")
+# source("/Users/beperron/Git/SocialWorkResearch/functions/cleaningJournals.R")
+# source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticles.R")
+# source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
+# source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
+# source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")
+# source("/Users/beperron/Git/SocialWorkResearch/functions/pretty.R")
+# 
+# combineData.f()
+# cleaningJournals.f()
+# shortArticles.f()
+# titleMatching.f()
+# otherDocuments.f()
+# fewArticles.f()
 #save.image(file = "socialWorkHistory.Rdata")

### 2015-04-06 manuscript.Rmd
Updates to manuscript file.

@@
 ```{r methodSummaryData, eval=TRUE}
-#append.articles <- length(which(full.append.df$attributes == "article"))
-#append.journals <- filter(full.append.df, attributes == "journal") %>% 
-#    summarise(Unique = n_distinct(record))
-
 unique.titles <- filter(full.df, attributes == "journal") %>%
@@
     summarise(Unique = n_distinct(record))
-
 ```
@@
 final.list <- arrange(final.list, desc(n))
+
+```
+
+```{r}
+final.list.updated <- final.list %>% mutate(study.time = 
+    as.numeric(last)-as.numeric(first) +1)
+
 ```
@@
     #geom_point(colour="red") + 
-    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8), title = element_text(size = 10), plot.title=element_text(size=10)) + 
+    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8), 
+    title = element_text(size = 10), plot.title=element_text(size=10)) + 
     xlab("Year") + 
@@
     geom_line(colour="black") +
-    #geom_point(colour="red") + 
-    theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8), title = element_text(size = 10), plot.title=element_text(size=10)) + 
+    theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8), 
+    title = element_text(size = 10), plot.title=element_text(size=10)) + 
     xlab("Year") + 
@@
 ```{r plotAuthorCount, eval=TRUE}
-
 year.df <- full.df %>%
@@
     ggtitle("Authors Per Article by Year")
-
 ```
@@
 ```{r nsf, eval=TRUE}
-nsf <- data.frame(c(rep(NA, 13), 238, 273, 304, 323, 308, 287, 338, 332, 308, 289, 280, NA), as.factor(seq(1989,2013, 1)))
+n.grads <- c(rep(NA, 13), 238, 273, 304, 323, 308, 287, 338, 332,      
+    308, 289, 280, NA)
+n.grads.1 <- c(rep(NA, 14), 238, 273, 304, 323, 308, 287, 338, 332, 
+    308, 289, 280)
+n.grads.2 <- c(rep(NA, 15), 238, 273, 304, 323, 308, 287, 338, 332, 
+    308, 289)
 
-growth <- c(rep("Unknown", 14), rep("Increase", 2), rep("Decrease", 3), "Increase", 
-     rep("Decrease", 4), "Unknown")
-nsf <- cbind(nsf, growth)
+years <- c(1989:2013)
 
-colnames(nsf) <- c("n.grads", "years", "growth")
+growth <- c(rep("Unknown", 14), rep("Increase", 2), rep("Decrease", 
+    3), "Increase", rep("Decrease", 4), "Unknown")
+
+nsf <- data.frame(cbind(n.grads, n.grads.1, n.grads.2, years))
+colnames(nsf) <- c("n.grads", "n.grads.1", "n.grads.2", "years")
 
 #write.csv(nsf, file="nsf.csv")
-
 ```
@@
 
+pages.df.melted <- reshape2::melt(pages.df, id.vars = "years")
+
+```
+
+```{r pages.plot, eval=TRUE}
+
+page.plot <- ggplot(pages.df.melted, aes(years, value, group = 
+    variable, color=variable)) + 
+    geom_line() +
+    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
+    title = element_text(size = 10), 
+    legend.title=element_blank()) +
+    scale_colour_manual(values=cbPalette)  +
+    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
+    scale_y_continuous(limits = c(0,16)) +
+    ylab("Value") +
+    xlab("Year") +
+    ggtitle("Article Length by Year")
 ```
@@
 
-```{r eval=TRUE}
+```{r ratios}
+years <- c(1989:2013)
+article.grad.ratio <- articles.year.df$year.count / nsf$n.grads
+article.grad.ratio.1 <- articles.year.df$year.count / nsf$n.grads.1
+article.grad.ratio.2 <- articles.year.df$year.count / nsf$n.grads.2
+
+ratio.df <- data.frame(cbind(years, article.grad.ratio, article.grad.ratio.1, article.grad.ratio.2))
+colnames(ratio.df) <- c("years", "ratio", "ratio.1", "ratio.2")
+ratio.df <- ratio.df[-(1:13), ]
+
+grad.ratio.df.melted <- reshape2::melt(ratio.df, id.vars="years")
+
+ratio.plot <- ggplot(grad.ratio.df.melted, aes(years, value, group= variable, 
+    color=variable)) + geom_line() +
+    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
+    title = element_text(size = 10), 
+    legend.title=element_blank()) +
+    scale_colour_manual(values=cbPalette)  +
+    scale_x_continuous(breaks=c(seq(2002, 2013))) +
+    scale_y_continuous(limits = c(0,8)) +
+    ylab("Value") +
+    xlab("Year")
+
+```
+
+```{r eval=FALSE}
 colnames(n.journals.year) <- c("years", "journals")
@@
 
+### Analyses
+
 # Results
@@
 
-```{r}
+```{r plotrticleCountText}
 grid.arrange(plot.article.count, plot.journal.count, ncol=2)
@@
 
-```{r}
+```{r plotPhDdegrees}
 plot.PhD
+ratio.plot
 ```
@@
 plot.author.count
+```
+
+```{r}
+page.plot
 ```

### 2015-04-08 manuscript.Rmd
Major updates

@@
 
+```{r warning=FALSE, message=FALSE, eval=TRUE}
+# Clear workspace
+rm(list=ls())
+
+# Read BWR functions for Mac OS
+source("/Users/beperron/Git/BibWrangleR/functions/proquestBWR.R")
+
+# Set the path where original raw data are stored
+setwd("/Users/beperron/Git/SocialWorkResearch/Data")
+
+# Set the working directory to store files created by BWR functions
+path <- "/Users/beperron/Git/SocialWorkResearch/Data/ProQuest"
+
+# Wrangle the data with the BWR function suite
+
+proQuestBWR.f(csv=FALSE, path=path)
+save(proQuestBWR.df, file = "ProQuest.R")
+```
+
 ```{r BEPinitialization, eval=TRUE}
@@
 
-load("/Users/beperron/Git/SocialWorkResearch/socialWorkHistory.Rdata")
+#load("/Users/beperron/Git/SocialWorkResearch/socialWorkHistory.Rdata")
 
@@
 
-```{r imageMaker, comment=NA, echo=FALSE, eval=FALSE}
+```{r imageMaker, comment=NA, echo=FALSE, eval=TRUE}
 # Read data files
-# load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
-# load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
-# hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
-# 
-# source("/Users/beperron/Git/SocialWorkResearch/functions/combineData.R")
-# source("/Users/beperron/Git/SocialWorkResearch/functions/cleaningJournals.R")
-# source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticles.R")
-# source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
-# source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
-# source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")
-# source("/Users/beperron/Git/SocialWorkResearch/functions/pretty.R")
-# 
-# combineData.f()
-# cleaningJournals.f()
-# shortArticles.f()
-# titleMatching.f()
-# otherDocuments.f()
-# fewArticles.f()
+load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
+load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
+hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
+
+source("/Users/beperron/Git/SocialWorkResearch/functions/combineData.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/cleaningJournals.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticlesRevised.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/pretty.R")
+
+combineData.f()
+cleaningJournals.f()
+shortArticles.f()
+titleMatching.f()
+otherDocuments.f()
+fewArticles.f()
 #save.image(file = "socialWorkHistory.Rdata")

### 2015-04-08 functions/shortArticles.R

@@ -5,7 +5,7 @@ shortArticles.f <- function(){
     pages.df$record <- gsub("ArtID:\\s", "", pages.df$record)
     pages.df$record<-gsub("S", "", pages.df$record)
     pages.df$record <- gsub(" ", "", pages.df$record)
-    
+
     pages.df$record[pages.df$record==1830]<-"173-183"
     pages.df$record[pages.df$record==364] <- 1
     pages.df$record[pages.df$record==216] <- 1
@@ -13,10 +13,10 @@ shortArticles.f <- function(){
     pages.df$record[pages.df$record==131] <- 1
     pages.df$record[pages.df$record==183] <- 1
     pages.df$record[pages.df$record==50] <- "533-552"
-    pages.df$record[pages.df$record==116] <- "191-207" 
+    pages.df$record[pages.df$record==116] <- "191-207"
     pages.df$record[pages.df$record==58] <-"58-66"
     pages.df$record[pages.df$record==84] <-"339-355"
-       
+
     dashes<-filter(pages.df, grepl("-", record) )
     dashes$record[dashes$record=="389-314"]<-"289-314"
     dashes$record[dashes$record=="209-2018"]<-"209-218"
@@ -32,7 +32,7 @@ shortArticles.f <- function(){
     dashes$record[dashes$record=="1-218"]<-"1-2"  #not an article
     dashes$record[dashes$record=="1-98"]<-"1-2"  #not an article
     dashes$record[dashes$record=="1-212"]<-"1-2"  #not an article
-    
+
     splitDash<-strsplit(dashes$record, "-")
     mat  <- matrix(unlist(splitDash), ncol=2, byrow=TRUE)
     mat <- as.data.frame(mat)
@@ -55,19 +55,18 @@ shortArticles.f <- function(){
     pages.df<-rbind(pages.noDashes, dashes.df)
     pages.df$record<-as.numeric(pages.df$record)
     pages.df[is.na(pages.df)] <- 0
-    
+
 
     pages.remove<-filter(pages.df, record < 3)    ## Set threshold for retaining articles by number of pages
     pages.remove.ID <- pages.remove$articleID
 
     full.df <- full.df[!full.df$articleID %in% pages.remove.ID, ]
     rownames(full.df) <- NULL
-    full.df <<- full.df
-    
+
     pages.keep<-filter(pages.df, record>=3)
     pages.keep$record<-as.character(pages.keep$record)
[…]

### 2015-04-08 manuscript.Rmd
Removed hard coding from analysis.

@@
 
-```{r warning=FALSE, message=FALSE, eval=TRUE}
+```{r objectMakerProQuest, warning=FALSE, message=FALSE, eval=FALSE, results='hide'}
 # Clear workspace
@@
 
+```{r objectMakerEbscoHost,warning=FALSE, message=FALSE, eval=FALSE, results='hide'}
+# Clear workspace
+rm(list=ls())
+
+# Read BWR functions for Mac OS
+source("/Users/beperron/Git/BibWrangleR/functions/ebscoBWR.R")
+
+# Set the path where original raw data are stored
+setwd("/Users/beperron/Git/SocialWorkResearch/Data")
+
+# Set the working directory to store files created by BWR functions
+path <- "/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL"
+
+# Wrangle the data with the BWR function suite
+
+ebscoBWR.f(csv=FALSE, path=path)
+save(ebscoBWR.df, file = "ebscoFULL.R")
+```
+
 ```{r BEPinitialization, eval=TRUE}
@@
 
-#load("/Users/beperron/Git/SocialWorkResearch/socialWorkHistory.Rdata")
+load("/Users/beperron/Git/SocialWorkResearch/socialWorkHistory.Rdata")
 
@@
 
-```{r imageMaker, comment=NA, echo=FALSE, eval=TRUE}
+```{r imageMaker, comment=NA, echo=FALSE, eval=FALSE}
 # Read data files
@@
 
-source("/Users/beperron/Git/SocialWorkResearch/functions/combineData.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/cleaningJournals.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticlesRevised.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/pretty.R")
+#source("/Users/beperron/Git/SocialWorkResearch/functions/combineData.R")
+#source("/Users/beperron/Git/SocialWorkResearch/functions/cleaningJournals.R")
+#source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticlesRevised.R")
+#source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
+#source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
+#source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")
+#source("/Users/beperron/Git/SocialWorkResearch/functions/pretty.R")
 
-combineData.f()
-cleaningJournals.f()
-shortArticles.f()
-titleMatching.f()
-otherDocuments.f()
-fewArticles.f()
+#combineData.f()
+#cleaningJournals.f()
+#shortArticles.f()
+#titleMatching.f()
+#otherDocuments.f()
+#fewArticles.f()
 #save.image(file = "socialWorkHistory.Rdata")

### 2015-04-08 functions/fewArticles.R

@@ -3,27 +3,33 @@ fewArticles.f <- function(){
     titles <- filter(full.df, attributes == "article")
     journals <- filter(full.df, attributes == "journal")
     year <- filter(full.df, attributes == "pubYear")
-    
-    
+
+
 
     year.journal <- dplyr::intersect(year$articleID, journals$articleID)
     year.journal.titles <- dplyr::intersect(year.journal, titles$articleID)
     full.df <- full.df[full.df$articleID %in% year.journal.titles, ]
 
-    exclusions.2 <- c(
-        "Issues in Social Work Education",
-        "Maatskaplike Werk/Social Work",
-        "Pediatric Social Work",
-        "Critical Social Work"
-    )
+    exclusions.2 <- filter(full.df, attributes == "journal") %>%
+        group_by(record) %>%
+        summarise(N = n()) %>%
+        arrange(N)
 
-    ebsco.remove <- full.df[full.df$record %in% exclusions.2, ]
+    exclusions.2 <- exclusions.2[exclusions.2$N <=20, "record"]
+
+    fewArticles <- exclusions.2$record
+
+
+
+
+
+    ebsco.remove <- full.df[full.df$record %in% fewArticles, ]
     ebsco.remove <- ebsco.remove[, "articleID"]
     full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
-    
+
     author<-filter(full.df, attributes=="author")
     no.author<-filter(author, grepl("authorship|anonymous", record, ignore.case=TRUE))
     no.author.ID<-no.author$articleID
     full.df <<- full.df[!(full.df$articleID %in% no.author.ID),]
-    
+
 }

### 2015-04-08 manuscript.Rmd
Updated results section.

--- 2015-04-08 manuscript.Rmd
@@
 
-```{r}
+```{r finalJournalList}
 final.list.updated <- final.list %>% mutate(study.time = 
     as.numeric(last)-as.numeric(first) +1)
+
+final.list.25 <- final.list.updated %>% filter(study.time == 25)
 
@@
 
+### Journal summary
+
+The study was restricted to a 25-year timeframe, 1989 (inclusive) to 2013 (inclusive).
+Table 1 provides a summary of all the journals contained in the database, the years of inclusion, number of articles present, and whether the journal was included on the list of disciplinary journals defined by Hodge and Lacasse (2011).
+Appendix A provides a summary of journals on the list of Hodge and Lacasse that were not included in this historical database (N = `r length(hodge.swHistory.diff)`).
+A total of `r nrow(fewArticles)` journals were excluded because they had only 1 or 2 article records (see Appendix A).
+Otherwise, all other journals met the minimum requirement of at least 20 article records.
+It is important to note that the years of inclusion in the database may not be fully consistent with the actual output of the journal for the given timeframe.
+The possible discrepancies are accounted due to delays and errors of indexing, which is a known and longstanding problem in social work research (see Holden; Holden).
+The problems associated with indexing are reviewed in further detail in the discussion section of this article.
+
+`r nrow(final.list.25)` journals were represented across all 25 years.
+The mean number of years of inclusion is `r options(digits=2); mean(final.list.updated$study.time)` `r options(digits=2); median(final.list.updated$study.time); sd(final.list.updated$study.time)`.
+Figure 1a provides a graphical summary of the number of journal titles for each year over the 25 year study period.
+The first year of the study period contained XX journals, and the maximum number of articles was observed for the years XX.
+The decline in years 2012 to 2013 may be an artifact due to indexing, given that some journals were still in existence but article records could not be obtained (e.g., XXXX).
+
+### Article summary
+
+The historical database include XXXXX articles for the 25 year period (see Table 1).
+The average number of articles per journal was XX (median, sd = ).
+XXXX contained the largest number of article records (N = XX), followed by XXXX (N = XXXX) and XXXX (N = XXXX).
+Figure 1b shows the number of articles published each year.
+The ratio of journals to articles (see figure 1a) was relatively consistent across time.
+
+The length of the articles showed some change over time, going from approximately 12 pages in 1989.
+The length of the articles increased to about 15 pages and has remain at approximately this length since the early 2000's.
+The standard deviation has remained fairly stable over the time period, ranging from XX to XX.
+
+### Author summary
+
+The mean number of authors showed a rising trajectory over the study time period, with an average of XX authors (sd = XX) in 1989 to XX authors (sd = XX) in 2013.
+The median number of authors was XX.
+Between years XX and XX, the number fluctuated between 1 and 2, and has remained stable at 2 authors per year since 2009.
+The standard deviation of the number of authors per paper has continued on a steady upward trajectory since the beginning of the study period.
+
+For further contextual information, the number of PhD degrees was plotted using data available from the NSF for years 2002 to 2012.
+The ratio of the number of PhD degress to the number of articles published that year was XXXX.
+
 \newpage
@@
 print(sort(hodge.swHistory.diff))
+print(fewArticles)
 ```

### 2015-04-08 functions/appendData.R

@@ -1,5 +1,5 @@
 appendData.f <- function(){
-    
+
     full.df$record <- ifelse(full.df$record ==
                                  "The British Journal of Social Work",          # Spelling difference
                              "British Journal of Social Work",
@@ -9,6 +9,12 @@ appendData.f <- function(){
                                  "Revista de Asistenta Sociala (Social Work Review)",
                              "Social Work Review",
                              full.df$record)
+
+    full.df$record <- ifelse(full.df$record ==
+                                 "Social work in public health",
+                             "Social Work in Public Health",
+                             full.df$record)
+
 
     full.df$record <- gsub("Arete", "xxx", full.df$record)
     full.df$record <- gsub("Aret.{1,3}", "Arete", full.df$record)
@@ -100,8 +106,8 @@ appendData.f <- function(){
                                "Social Work Research & Abstracts",          # Spelling difference
                              "Social Work Research",
                              full.df$record)
-    
-    
+
+
     #shortens Professional Development
     full.df$record <- ifelse(full.df$attributes == "journal",
                              gsub(":.+", "", full.df$record),

### 2015-04-08 functions/cleaningJournals.R

@@ -1,5 +1,5 @@
 cleaningJournals.f <- function(){
-    
+
     full.df$record <- ifelse(full.df$record ==
                                  "The British Journal of Social Work",          # Spelling difference
                              "British Journal of Social Work",
@@ -100,8 +100,8 @@ cleaningJournals.f <- function(){
                                "Social Work Research & Abstracts",          # Spelling difference
                              "Social Work Research",
                              full.df$record)
-    
-    
+
+
     #shortens Professional Development
     full.df$record <- ifelse(full.df$attributes == "journal",
                              gsub(":.+", "", full.df$record),
@@ -155,6 +155,12 @@ cleaningJournals.f <- function(){
                                  "Journal of Analytic Social Work",                          # Old title
                              "Psychoanalytic Social Work",                               # Old title
                              full.df$record)
+
+    full.df$record <- ifelse(full.df$record ==
+                                 "Social work in public health",
+                             "Social Work in Public Health",
+                             full.df$record)
+
 
     full.df$record <- ifelse(full.df$record ==
               "Journal of Practice Teaching in Social Work and Practice" |
@@ -211,15 +217,15 @@ cleaningJournals.f <- function(){
         "Arete: Revista de Filosofia",
         "Arete Revista de Filosofia")
 
-    
+
     ebsco.remove <- full.df[full.df$record %in% exclusions.1, ]
     ebsco.remove <- ebsco.remove[, "articleID"]
-    
+
     full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
     full.df <<- full.df
-    
-    article.count.journalsCleaned <<- filter(full.df, attributes == "article") 
+
+    article.count.journalsCleaned <<- filter(full.df, attributes == "article")
     journal.count <- filter(full.df, attributes == "journal")
     journal.count.journalsCleaned <<- length(unique(journal.count$record))
-    
+
 }

### 2015-04-08 functions/fewArticles.R

@@ -15,8 +15,9 @@ fewArticles.f <- function(){
         summarise(N = n()) %>%
         arrange(N)
 
-    exclusions.2 <- exclusions.2[exclusions.2$N <=20, "record"]
+    fewArticles <<- exclusions.2 %>% filter(N <=20)
 
+    exclusions.2 <- exclusions.2[exclusions.2$N <=20, "record"]
     fewArticles <- exclusions.2$record
 
 

### 2015-04-08 manuscript.Rmd
Updated manuscript. New h-Index data.

@@
 author: ''
-output: pdf_document
+output: word_document
 ---
@@
 
-The historical database include XXXXX articles for the 25 year period (see Table 1).
-The average number of articles per journal was XX (median, sd = ).
-XXXX contained the largest number of article records (N = XX), followed by XXXX (N = XXXX) and XXXX (N = XXXX).
-Figure 1b shows the number of articles published each year.
+The historical database includes `r pretty(sum(articles.year.df$year.count))` overr the 25 year period (see Table 1).
+The average number of articles per journal was `r options(digits=2); pretty(mean(articles.year.df$year.count))` (median = `r options(digits=2); pretty(median(articles.year.df$year.count))`, sd = `r options(digits=2); pretty(sd(articles.year.df$year.count))`).
 The ratio of journals to articles (see figure 1a) was relatively consistent across time.
 
-The length of the articles showed some change over time, going from approximately 12 pages in 1989.
+The length of the articles showed some change over time, going from approximately `r round(pages.df$Mean.Pages[pages.df$years == "1989"])` pages in 1989.
 The length of the articles increased to about 15 pages and has remain at approximately this length since the early 2000's.
-The standard deviation has remained fairly stable over the time period, ranging from XX to XX.
+The standard deviation has remained fairly stable over the time period, ranging from `r options(digits=2); min(pages.df$Std.Pages)` to `r options(digits=2); max(pages.df$Std.Pages)`.
 
@@
 
-The mean number of authors showed a rising trajectory over the study time period, with an average of XX authors (sd = XX) in 1989 to XX authors (sd = XX) in 2013.
+The mean number of authors showed a rising trajectory over the study time period, with an average of `r options(digits=2); n_authors2$Average[n_authors2$ID == "1989"]` authors (`r options(digits=2); n_authors2$Standard_DeviationA[n_authors2$ID == "1989"]`) in 1989 to `r options(digits=2); n_authors2$Average[n_authors2$ID == "2013"]` authors (sd = `r options(digits=2); n_authors2$Standard_Deviation[n_authors2$ID == "2013"]`) in 2013.
 The median number of authors was XX.

### 2015-04-14 manuscript.Rmd
Major update.

--- 2015-04-08 manuscript.Rmd
@@
 
-```{r imageMaker, comment=NA, echo=FALSE, eval=FALSE}
+```{r imageMaker, comment=NA, echo=FALSE, eval=TRUE}
 # Read data files
+options(stringsAsFactors = FALSE)
 load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
@@
 hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
+hIndex <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/hIndex.csv")
 
-#source("/Users/beperron/Git/SocialWorkResearch/functions/combineData.R")
-#source("/Users/beperron/Git/SocialWorkResearch/functions/cleaningJournals.R")
-#source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticlesRevised.R")
-#source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
-#source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
-#source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")
-#source("/Users/beperron/Git/SocialWorkResearch/functions/pretty.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/combineData.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/cleaningJournals.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticlesRevised.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/pretty.R")
 
-#combineData.f()
-#cleaningJournals.f()
-#shortArticles.f()
-#titleMatching.f()
-#otherDocuments.f()
-#fewArticles.f()
+combineData.f()
+cleaningJournals.f()
+shortArticles.f()
+titleMatching.f()
+otherDocuments.f()
+fewArticles.f()
 #save.image(file = "socialWorkHistory.Rdata")
@@
 
+```{r nsf, eval=TRUE}
+n.grads <- c(rep(NA, 13), 238, 273, 304, 323, 308, 287, 338, 332,      
+    308, 289, 280, NA)
+n.grads.1 <- c(rep(NA, 14), 238, 273, 304, 323, 308, 287, 338, 332, 
+    308, 289, 280)
+n.grads.2 <- c(rep(NA, 15), 238, 273, 304, 323, 308, 287, 338, 332, 
+    308, 289)
+
+years <- c(1989:2013)
+
+growth <- c(rep("Unknown", 14), rep("Increase", 2), rep("Decrease", 
+    3), "Increase", rep("Decrease", 4), "Unknown")
+
+nsf <- data.frame(cbind(n.grads, n.grads.1, n.grads.2, years))
+colnames(nsf) <- c("n.grads", "n.grads.1", "n.grads.2", "years")
+
+```
 ```{r methodSummaryData, eval=TRUE}
@@
 final.list <- arrange(final.list, desc(n))
+final.list.index <- full_join(final.list, hIndex, by = "title")
 
@@
 
-```{r}
+```{r finalJournalList}
 final.list.updated <- final.list %>% mutate(study.time = 
     as.numeric(last)-as.numeric(first) +1)
+
+final.list.25 <- final.list.updated %>% filter(study.time == 25)
+
+journals.year <- left_join(n.so, n.yr) %>%
+    group_by(title)
+
+journals.2012 <- filter(journals.year, year == "2012") %>%
+    group_by(title) %>%
+    summarize(N = n())
+
+journals.2012 <- arrange(journals.2012, desc(N))
+journals.2012$cumS <- cumsum(journals.2012$N)
+journals.2012$shortTitle <- factor(c(1:nrow(journals.2012)))
+
+journals.2012$cumperc <- (1:nrow(journals.2012))/nrow(journals.2012) 
+journals.2012 <- arrange(journals.2012, desc(N))
+
+journals.2012 <- transform(journals.2012,
+                          shortTitle = reorder(shortTitle, 
+                                                order(N, decreasing = TRUE)))
+ggplot(journals.2012, aes(x = title, y = N)) + 
+    geom_bar(stat="identity")
 
@@
 
-plot.article.count <- ggplot(articles.year.df, aes(as.factor(years), 
-    y = year.count, group=1)) + 
-    geom_line(colour="black") +
+plot.article.count <- ggplot(nsf, aes(as.factor(years), 
+    y = n.grads, group=1)) + 
+    geom_line(colour="red") + 
+    geom_point(colour="red") + 
     #geom_point(colour="red") + 
@@
     scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
-    scale_y_continuous(breaks = c(seq(0, 2500, 200))) +
-    annotate("rect", xmin = 2008-1989+1, xmax =  2012-1989+1, 
-    ymin = 1700, ymax = 2050, alpha = .20, fill = "#0072B2") +
-    annotate("rect", xmin = 2005-1989+1, xmax =  2007-1989+1, 
-    ymin = 1400, ymax = 1750, alpha = .20, fill= "#0072B2")  
+    ylim(c(0,2200)) + 
+    geom_line(data = articles.year.df, aes(as.factor(years), y = year.count), colour="steelblue") + 
+    geom_text(data = nsf, aes(label = n.grads), vjust = 2, size = 2.75) +
+    geom_point(data = articles.year.df, aes(as.factor(years), y = articles.year.df$year.count), colour="steelblue") 
 ```
@@
     ymin = 53, ymax = 62, alpha = .20, fill = "#0072B2")  
+```
+
+```{r plothIndex, eval=TRUE}
+final.list.index <- within(final.list.index, quartile <- as.integer(cut(h5Index, quantile(h5Index, probs=0:4/4, na.rm=TRUE), include.lowest=TRUE)))
+
+final.list.index <- within(final.list.index, years <- as.numeric(last) - as.numeric(first) +1)
+
+plotIndex <- ggplot(final.list.index, aes(x = n, y = h5Index )) + 
+    geom_point(aes(colour=factor(quartile), size = years), alpha=.80) +
+    geom_smooth()
+
 ```
@@
 
-```{r nsf, eval=TRUE}
-n.grads <- c(rep(NA, 13), 238, 273, 304, 323, 308, 287, 338, 332,      
-    308, 289, 280, NA)
-n.grads.1 <- c(rep(NA, 14), 238, 273, 304, 323, 308, 287, 338, 332, 
-    308, 289, 280)
-n.grads.2 <- c(rep(NA, 15), 238, 273, 304, 323, 308, 287, 338, 332, 
-    308, 289)
+```{r}
 
-years <- c(1989:2013)
+authorNames  <- filter(full.df, attributes == "author")
 
-growth <- c(rep("Unknown", 14), rep("Increase", 2), rep("Decrease", 
-    3), "Increase", rep("Decrease", 4), "Unknown")
-
-nsf <- data.frame(cbind(n.grads, n.grads.1, n.grads.2, years))
-colnames(nsf) <- c("n.grads", "n.grads.1", "n.grads.2", "years")
-
-#write.csv(nsf, file="nsf.csv")
-```
-
+authorNames.df <- authorNames
+authorNames.df$record <- sub("(?<=, [A-Z]).*$", "", authorNames.df$record, perl=TRUE)
+authorNames.df <- authorNames.df %>% group_by(record) %>% 
+    summarize(N = n()) %>%
+    arrange(desc(N))
 ```{r gade, eval=TRUE}
@@
 article.grad.ratio <- articles.year.df$year.count / nsf$n.grads
-article.grad.ratio.1 <- articles.year.df$year.count / nsf$n.grads.1
-article.grad.ratio.2 <- articles.year.df$year.count / nsf$n.grads.2
 
-ratio.df <- data.frame(cbind(years, article.grad.ratio, article.grad.ratio.1, article.grad.ratio.2))
-colnames(ratio.df) <- c("years", "ratio", "ratio.1", "ratio.2")
+ratio.df <- data.frame(cbind(years, article.grad.ratio))
+colnames(ratio.df) <- c("years", "ratio")
 ratio.df <- ratio.df[-(1:13), ]
@@
 
+### Journal summary
+
+Table 1 provides a summary of the journal titles and corresponding article records collected from the databases.
+This table includes the specific years each journal is represented in the current study, the number of corresponding article records, the journal's h-Index, and whether the journal was included on the list of social work disciplinary journals defined by Hodge and Lacasse (2011).
+Appendix A provides a summary of journals that were on the list by compiled by Hodge and Lacasse (2011) but not included in this study (N = `r length(hodge.swHistory.diff)`), in addition to the journals excluded from the study due to an article count $<=$ 20 (N = `r nrow(fewArticles)`).
+It is important to note that the years of inclusion noted for each journals does not correspond to its full historical record.
+Many journals have publications that both precede and proceed the 25-year timeframe of the current study.
+Moreover, many journals are missing articles records due to delays and errors in indexing, which is a known and longstanding problem in social work research (HoldenXXXX).
+These issues are given further attention in the discussion section of the article.
+
+As shown in Table 1, `r nrow(final.list.25)` journals were included in the current study.
+The mean number of years of inclusion is `r options(digits=2); mean(final.list.updated$study.time)` (median = `r options(digits=2); median(final.list.updated$study.time);`, sd =  `r options(digits=2); sd(final.list.updated$study.time)`).
+The overall h-Index for each journal.
+The h-Index values represent the current h-Index of each journal, as opposed to the h-Index of the final study period, so these values should be interpreted cautiously.
+The mean h-Index value is XXXX, (median = XXX; sd = XXX).
+A total of `r pretty(sum(articles.year.df$year.count))` article records were obtained across these journals.
+The average number of articles per journal was `r options(digits=2); pretty(mean(articles.year.df$year.count))` (median = `r options(digits=2); pretty(median(articles.year.df$year.count))`, sd = `r options(digits=2); pretty(sd(articles.year.df$year.count))`).
+This figure shows consistent growth in the number of articles from 1989 to 2005.
+Notable fluctuations in the number of articles was observed from 2005 to 2008, followed by growth until 2012.
+The decline from 2012 to 2013 should be interpreted cautiously, as this may be an artifact due to delays in indexing.
+
+Data from the National Science Foundation regarding the number of earned doctorates in social work and social welfare were added to further contextualize the publication trends.
+These data reveal both growth and decline in the number of earned doctorates over the period of time for which data were available.
+The number of earned doctorates exhibited a rise from 2003 to 2005, which corresponded to a rise in the number of article published during these years.
+Between 2008 and 2012, the number of doctoral degrees exhibited a decline, but the number of published articles continued to rise.
+
+A bubble plot was created to facilitate interpretation of these data (see Figure 2).
+This involved creating a scatter plot, mapping each journal's total number of publications on the X axis and h-Index value on the Y axis.
+Each journal was assigned a quartile rating for its h-Index, and those quartile values were mapped to four unique colors.
+Finally, the number of years of representation in the study was mapped to the size of the point, or _bubble_.
+Journals without an h-Index rating are not represented in this plot (N = XX).
+A smoothed loess line and confidence interval were added to show the trend between the h-Index scores and number of articles published.
+
+The loess trend line shows a moderate association between the h-Index and number of articles published.
+However, a number of notable deviations are observed.
+Eleven journals were in the highest h-Index quartile.
+The _British Journal of Social Work_ had the highest h-Index value but ranked third with regard to the overall number of publications.
+XXXX, XXXX, and XXXX were also in the top quartile but had comparably fewer published articles and existed for less time than the other journals in the same quartile.
+_Families in Society_ had the most published articles, spanning the full 25-year study period, but was in the second h-Index quartile.
+
+Figure 3 provides a descriptive summary of the number of authors per article over time.
+As indicated by the median, it was more common for articles to be sole-authored until 2006, at which time the median fluctuated between one and two authors, and then stabilizing in 2009 at 2 authors.
+The steady increase in the standard deviation since 2000 indicates an increase in the number of authors for each article.
+The length of articles also increased over time, starting at roughly 12.5 pages in 1989 and increasing steadily over time and stabilizing around 15 pages in 2013.
+The standard deviation remained relatively stable over the 25 year period, with all values falling between the range of XX and XX.
+
+The length of the articles showed some change over time, going from approximately `r round(pages.df$Mean.Pages[pages.df$years == "1989"])` pages in 1989.
+The length of the articles increased to about 15 pages and has remain at approximately this length since the early 2000's.
+The standard deviation has remained fairly stable over the time period, ranging from `r options(digits=2); min(pages.df$Std.Pages)` to `r options(digits=2); max(pages.df$Std.Pages)`.
+
 \newpage
@@
 
-```{r plotrticleCountText}
-grid.arrange(plot.article.count, plot.journal.count, ncol=2)
+```{r}
+plotIndex
 ```
@@
 
-```{r plotPhDdegrees}
-plot.PhD
-ratio.plot
+```{r}
+plot.journal.count
+```
+
+\newpage
+
+```{r}
+plot.article.count
 ```

### 2015-04-17 manuscript.Rmd
Updated plots.

@@
 hIndex <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/hIndex.csv")
+hIndex$h5Index <- ifelse(is.na(hIndex$h5Index), 0, hIndex$h5Index)
+hIndex$h5Median <- ifelse(is.na(hIndex$h5Median), 0, hIndex$h5Median)
 
@@
 
+#Annotation data file
+articles.x <- as.factor(articles.year.df[c(1, 6, 12, 18, 25), 1]) 
+articles.y <- articles.year.df[c(1, 6, 12, 18, 25), 2] 
+articles.label <- as.character(articles.y)
+articles.placement <- articles.y-50
+
+articles.x1 <- as.factor(ar)
+
 plot.article.count <- ggplot(nsf, aes(as.factor(years), 
@@
     geom_line(data = articles.year.df, aes(as.factor(years), y = year.count), colour="steelblue") + 
-    geom_text(data = nsf, aes(label = n.grads), vjust = 2, size = 2.75) +
-    geom_point(data = articles.year.df, aes(as.factor(years), y = articles.year.df$year.count), colour="steelblue") 
+    #geom_text(data = nsf, aes(label = n.grads), vjust = 2, size = 2.75) +
+    geom_point(data = articles.year.df, aes(as.factor(years), y = articles.year.df$year.count), colour="steelblue") + 
+    annotate("text", factor(c(2002, 2005, 2008, 2012)), 
+    c(165, 225, 250, 190) + 150, label = c("238","323", "338", "280") , size = 3) + 
+    annotate("text", articles.x, articles.placement, label = articles.label, size=3) + 
+    annotate("point", x = as.factor(2003), y = 720, alpha = .60, color = "green", size = 6) + 
+    annotate("point", x = as.factor(2015), y = 750, alpha = .60, color = "green", size = 6)
+
 ```
@@
     ymin = 53, ymax = 62, alpha = .20, fill = "#0072B2")
+
+plot.journal.count2 <- ggplot(n.journals.year, aes(as.factor(record.y), 
+    y = Journal.count, group=1)) + 
+    geom_line(colour="black") +
+    theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8), 
+    title = element_text(size = 10), plot.title=element_text(size=10)) + 
+    xlab("Year") + 
+    ylab("Journals") + 
+    ggtitle("B. Number of Journals by Year") +
+    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
+    scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 70)) 
 ```
@@
 
+n_authors2$ymin <- n_authors2$Average - n_authors2$Standard_Deviation
+n_authors2$ymax <- n_authors2$Average - n_authors2$Standard_Deviation
+
+plot.author.count2 <- ggplot(n_authors2, aes(ID, y = Average, group=1, size = Standard_Deviation, colour=as.factor(Median))) + 
+    geom_line(size=.75) +
+    geom_point() + 
+    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
+    title = element_text(size = 10), 
+    legend.title=element_blank()) +
+    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
+    scale_y_continuous(limits = c(0,2.5)) +
+    ylab("Value") +
+    xlab("Year") +
+    ggtitle("Authors Per Article by Year")
+
 plot.author.count <- ggplot(n_authors2_melted, aes(x = pubYear, y = value, group = summaryStat, colour = summaryStat)) + 
@@
     ggtitle("Authors Per Article by Year")
+
 ```
@@
     ggtitle("Article Length by Year")
-```
+
+page.plot <- ggplot(pages.df, aes(years, Mean.Pages, colour=as.factor(Median.Pages), size = Std.Pages, group = 1))+ 
+    geom_line(size=.75) +
+    geom_point() +
+    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
+    title = element_text(size = 10), 
+    legend.title=element_blank()) +
+    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
+    scale_y_continuous(limits = c(10.5,16)) +
+    ylab("Value") +
+    xlab("Year") +
+    ggtitle("Article Length by Year")
+````
 
@@
     xlab("Year") +
-    geom_text(aes(label = n.grads), vjust = -1.2, size = 2.75) + 
-    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
-    title = element_text(size = 10)) +
-    ggtitle("Number of Earned Social Work Doctoral Degrees by Year") 
+    #geom_text(aes(label = n.grads), vjust = -1.2, size = 2.75) + 
+    #theme(axis.text.x = element_text(angle = 45, hjust = 1), 
+    #title = element_text(size = 10)) +
+    #ggtitle("Number of Earned Social Work Doctoral Degrees by Year")
+    geom_text(aes(2002, 230, label = "238", colour = "black"))
 ```

### 2015-04-19 manuscript.Rmd
Major updates to plots

--- 2015-04-14 manuscript.Rmd
@@
 `r knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, comment=NA)`
+
+```{r colorThemes}
+# http://colorbrewer2.org/?type=diverging&scheme=PuOr&n=4
+
+cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
+```
 
@@
 
-```{r imageMaker, comment=NA, echo=FALSE, eval=TRUE}
+```{r cleaningFunctions, comment=NA, echo=FALSE, eval=TRUE}
 # Read data files
@@
 
-```{r nsf, eval=TRUE}
+```{r dataNSF, eval=TRUE}
 n.grads <- c(rep(NA, 13), 238, 273, 304, 323, 308, 287, 338, 332,      
     308, 289, 280, NA)
-n.grads.1 <- c(rep(NA, 14), 238, 273, 304, 323, 308, 287, 338, 332, 
-    308, 289, 280)
-n.grads.2 <- c(rep(NA, 15), 238, 273, 304, 323, 308, 287, 338, 332, 
-    308, 289)
 
@@
 
-growth <- c(rep("Unknown", 14), rep("Increase", 2), rep("Decrease", 
-    3), "Increase", rep("Decrease", 4), "Unknown")
+nsf <- data.frame(cbind(n.grads,  years))
+colnames(nsf) <- c("n.grads", "years")
+```
 
-nsf <- data.frame(cbind(n.grads, n.grads.1, n.grads.2, years))
-colnames(nsf) <- c("n.grads", "n.grads.1", "n.grads.2", "years")
-
-```
-```{r methodSummaryData, eval=TRUE}
+```{r tableArticleSummary, eval=TRUE}
 unique.titles <- filter(full.df, attributes == "journal") %>%
     group_by(record) %>%
-    summarise(
-        N = n())
+    summarise(N = n())
 
@@
 articles.otherDocuments <- length(which(full.df$attributes == "article"))
+
 journals.otherDocuments <- filter(full.df, attributes == "journal") %>% 
@@
 articles.final <- length(which(full.df$attributes == "article"))
+
 journals.final <- filter(full.df, attributes == "journal") %>% 
     summarise(Unique = n_distinct(record))
-```
-
-```{r Table_1, comment=NA, echo=FALSE, eval=TRUE}
-unique.titles <- filter(full.df, attributes == "journal") %>%
-    group_by(record) %>%
-    summarise(N = n())
 
@@
     mutate(Hodge.list = ifelse(record %in% hodge == TRUE, 1, 0)) %>%
-    summarise(N = n(), 
-              Hodge.list = max(Hodge.list)) %>%
+    summarise(N = n(), Hodge.list = max(Hodge.list)) %>%
     mutate(Hodge = ifelse(Hodge.list == 1, "Y", "N"))
@@
 
-```
-
-```{r finalJournalList}
-final.list.updated <- final.list %>% mutate(study.time = 
-    as.numeric(last)-as.numeric(first) +1)
-
-final.list.25 <- final.list.updated %>% filter(study.time == 25)
-
-journals.year <- left_join(n.so, n.yr) %>%
-    group_by(title)
-
-journals.2012 <- filter(journals.year, year == "2012") %>%
-    group_by(title) %>%
-    summarize(N = n())
-
-journals.2012 <- arrange(journals.2012, desc(N))
-journals.2012$cumS <- cumsum(journals.2012$N)
-journals.2012$shortTitle <- factor(c(1:nrow(journals.2012)))
-
-journals.2012$cumperc <- (1:nrow(journals.2012))/nrow(journals.2012) 
-journals.2012 <- arrange(journals.2012, desc(N))
-
-journals.2012 <- transform(journals.2012,
-                          shortTitle = reorder(shortTitle, 
-                                                order(N, decreasing = TRUE)))
-ggplot(journals.2012, aes(x = title, y = N)) + 
-    geom_bar(stat="identity")
+final.list.index$h5Index <- ifelse(is.na(final.list.index$h5Index), 0,final.list.index$h5Index)
+x <- ggplot(final.list.index, aes(x =reorder(title, n), y = n, colour = h5Index)) + geom_point(stat="identity") + coord_flip() + 
+    theme_bw()
 
@@
 rownames(articles.year.df) <- NULL
+
+#Annotation data file
+articles.x <- as.factor(articles.year.df[c(1, 6, 12, 18, 25), 1]) 
+articles.y <- articles.year.df[c(1, 6, 12, 18, 25), 2] 
+articles.label <- as.character(articles.y)
+articles.placement <- articles.y-50
 
@@
     geom_line(data = articles.year.df, aes(as.factor(years), y = year.count), colour="steelblue") + 
-    geom_text(data = nsf, aes(label = n.grads), vjust = 2, size = 2.75) +
-    geom_point(data = articles.year.df, aes(as.factor(years), y = articles.year.df$year.count), colour="steelblue") 
+    #geom_text(data = nsf, aes(label = n.grads), vjust = 2, size = 2.75) +
+    geom_point(data = articles.year.df, aes(as.factor(years), y = articles.year.df$year.count), colour="steelblue") + 
+    annotate("text", factor(c(2002, 2005, 2008, 2012)), 
+    c(165, 225, 250, 190) + 150, label = c("238","323", "338", "280") , size = 3) + 
+    annotate("text", articles.x, articles.placement, label = articles.label, size=3)
+
 ```
@@
     scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
-    scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 70)) +
-    annotate("rect", xmin = 2008-1989+1, xmax =  2012-1989+1, 
-    ymin = 55, ymax = 70, alpha = .20, fill= "#0072B2") +
-    annotate("rect", xmin = 2005-1989+1, xmax =  2007-1989+1, 
-    ymin = 53, ymax = 62, alpha = .20, fill = "#0072B2")  
+    scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 70)) 
 ```
 
-```{r plothIndex, eval=TRUE}
+```{r plotH-Index, eval=TRUE}
 final.list.index <- within(final.list.index, quartile <- as.integer(cut(h5Index, quantile(h5Index, probs=0:4/4, na.rm=TRUE), include.lowest=TRUE)))
@@
     geom_point(aes(colour=factor(quartile), size = years), alpha=.80) +
-    geom_smooth()
+    geom_smooth() + 
+    scale_colour_manual(values=cp)
 
@@
 
-n_authors2$ID <- as.factor(c(1989:2013))
+n_authors2$year <- as.factor(c(1989:2013))
 
-n_authors2_melted <- reshape2::melt(n_authors2, id.vars = "ID")
-colnames(n_authors2_melted) <- c("pubYear", "summaryStat", "value")
+cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
 
-cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
-
-plot.author.count <- ggplot(n_authors2_melted, aes(x = pubYear, y = value, group = summaryStat, colour = summaryStat)) + 
-    geom_line(size = .75) + 
+plot.author.count <- ggplot(n_authors2, aes(x = year, group=1)) + 
+    geom_line(aes(y=Median, colour="Median"), size = .75, colour = "#fdb864", alpha = .70) + 
+    geom_line(aes(y=Average, colour = "Average"), size = .75,  colour = "#e66101" ) +
+    geom_point(aes(y=Average, size = Standard_Deviation), colour = "#e66101") +
     theme(axis.text.x = element_text(angle = 45, hjust = 1), 
-    title = element_text(size = 10), 
-    legend.title=element_blank()) +
-    scale_colour_manual(values=cbPalette)  +
+    title = element_text(size = 10)) +  
     scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
@@
     xlab("Year") +
-    ggtitle("Authors Per Article by Year")
+    ggtitle("Authors Per Article by Year") +
+    labs(size = "Standard deviation") 
 ```
 
-```{r}
-
+```{r authorNames}
 authorNames  <- filter(full.df, attributes == "author")
@@
 
-```{r pages, eval=TRUE}
+```{r pagePlot, eval=TRUE}
 pages.tmp <- full.df %>% filter(attributes == "pages")
@@
         Std.Pages = sd(pages, na.rm=TRUE))
+cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
 
-pages.df.melted <- reshape2::melt(pages.df, id.vars = "years")
-
-```
-
-```{r pages.plot, eval=TRUE}
-
-page.plot <- ggplot(pages.df.melted, aes(years, value, group = 
-    variable, color=variable)) + 
-    geom_line() +
+page.plot <- ggplot(pages.df, aes(years, Mean.Pages, size = Std.Pages, group = 1))+ 
+    geom_line(size=.75, colour =  "#5e3c99") +
+    geom_line(aes(years, Median.Pages, group = 1), size = .75, colour = "#b2abd2", alpha = .70) + 
+    geom_point(colour = "#5e3c99") +
     theme(axis.text.x = element_text(angle = 45, hjust = 1), 
-    title = element_text(size = 10), 
-    legend.title=element_blank()) +
-    scale_colour_manual(values=cbPalette)  +
+    title = element_text(size = 10)) +
     scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
-    scale_y_continuous(limits = c(0,16)) +
+    scale_y_continuous(limits = c(11,16)) +
     ylab("Value") +
     xlab("Year") +
+    labs(size = "Standard deviation", colour = "Median")  +
     ggtitle("Article Length by Year")
-```
 
-```{r nsfPlot, eval=TRUE}
-plot.PhD <- ggplot(nsf, aes(years, n.grads, group=1)) + 
-    geom_line(linetype="dotted", colour = "#0072B2", size = .75) + 
-    geom_point(colour = "#0072B2", size = .75) +
-    scale_y_continuous(breaks = c(seq(0, 350, 25)), limits = c(200,350)) +
-    ylab("Doctoral degrees") +
-    xlab("Year") +
-    geom_text(aes(label = n.grads), vjust = -1.2, size = 2.75) + 
-    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
-    title = element_text(size = 10)) +
-    ggtitle("Number of Earned Social Work Doctoral Degrees by Year") 
 ```

### 2015-04-19 functions/cleaningJournals.R

@@ -101,6 +101,11 @@ cleaningJournals.f <- function(){
                              "Social Work Research",
                              full.df$record)
 
+    full.df$record <- ifelse(full.df$record ==
+                               "Journal of Multicultural Social Work",          # Spelling difference
+                             "Journal of Ehtnic & Cultural Diversity in Social Work",
+                             full.df$record)
+
 
     #shortens Professional Development
     full.df$record <- ifelse(full.df$attributes == "journal",

### 2015-04-19 manuscript.Rmd
Screwed up hIndex file.

@@
 
-load("/Users/beperron/Git/SocialWorkResearch/socialWorkHistory.Rdata")
+#load("/Users/beperron/Git/SocialWorkResearch/socialWorkHistory.Rdata")
 
-# Load required packages
+#Load required packages
 library(ggplot2)
@@
 final.list <- arrange(final.list, desc(n))
-final.list.index <- full_join(final.list, hIndex, by = "title")
+#final.list.index <- full_join(final.list, hIndex, by = "title")
 
-final.list.index$h5Index <- ifelse(is.na(final.list.index$h5Index), 0,final.list.index$h5Index)
-x <- ggplot(final.list.index, aes(x =reorder(title, n), y = n, colour = h5Index)) + geom_point(stat="identity") + coord_flip() + 
-    theme_bw()
+#final.list.index$h5Index <- ifelse(is.na(final.list.index$h5Index), 0,final.list.index$h5Index)
+#x <- ggplot(final.list.index, aes(x =reorder(title, n), y = n, colour = h5Index)) + geom_point(stat="identity") + coord_flip() + 
+#    theme_bw()
 

### 2015-04-19 functions/cleaningJournals.R

@@ -103,7 +103,7 @@ cleaningJournals.f <- function(){
 
     full.df$record <- ifelse(full.df$record ==
                                "Journal of Multicultural Social Work",          # Spelling difference
-                             "Journal of Ehtnic & Cultural Diversity in Social Work",
+                             "Journal of Ethnic & Cultural Diversity in Social Work",
                              full.df$record)
 
 

### 2015-04-20 manuscript.Rmd
More updates to figures.

@@
     select(-attributes, -record)
+
+bigList <- left_join(n.so, n.yr) %>%
+    group_by(title, year) %>%
+    summarize(N = n())
+bigList$shortTitle <- abbreviate(bigList$title)
+
+ggplot(bigList, aes(year, N, group = 1)) + geom_line(colour="#5e3c99") + 
+    facet_wrap(~ title, ncol=7) +
+    theme_bw() +
+    theme(panel.grid.major = element_blank(), 
+panel.grid.minor = element_blank(), 
+    axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
+    scale_x_discrete(breaks=seq(1989, 2013, 5)) + 
+    ylim(0, 150)
 

### 2015-04-21 manuscript.Rmd
Added Asian social work journal.

--- 2015-04-19 manuscript.Rmd
@@
 
+bigList <- left_join(n.so, n.yr) %>%
+    group_by(title, year) %>%
+    summarize(N = n())
+bigList$shortTitle <- abbreviate(bigList$title)
+
+ggplot(bigList, aes(year, N, group = 1)) + geom_line(colour="#5e3c99") + 
+    facet_wrap(~ title, ncol=7) +
+    theme_bw() +
+    theme(panel.grid.major = element_blank(), 
+panel.grid.minor = element_blank(), 
+    axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
+    scale_x_discrete(breaks=seq(1989, 2020, 8)) + 
+    ylim(0, 150)
+
 n.so.yr <- left_join(n.so, n.yr) %>%
@@
 final.list.index$h5Index <- ifelse(is.na(final.list.index$h5Index), 0,final.list.index$h5Index)
-x <- ggplot(final.list.index, aes(x =reorder(title, n), y = n, colour = h5Index)) + geom_point(stat="identity") + coord_flip() + 
-    theme_bw()
+#x <- ggplot(final.list.index, aes(x =reorder(title, n), y = n, colour = h5Index)) + geom_point(stat="identity") + coord_flip() + 
+#    theme_bw() 
+final.list.index$scaleScore <- scale(final.list.index$n)
+final.list.index$hScaled <- scale(final.list.index$h5Index)
+final.list.index <- arrange(final.list.index, scaleScore)
+
+ggplot(final.list.index, aes(x = scaleScore, y = title)) + geom_point(stat="identity", colour="red") + 
+    xlim(c(-3, 3))
 

### 2015-04-22 manuscript.Rmd
Updated files.

@@
 
-ggplot(bigList, aes(year, N, group = 1)) + geom_line(colour="#5e3c99") + 
-    facet_wrap(~ title, ncol=7) +
+bigList2 <- left_join(bigList, hIndex, by = "title")
+bigList2 <- within(bigList2, quartile <- as.integer(cut(h5Index, quantile(h5Index, probs=0:4/4, na.rm=TRUE), include.lowest=TRUE)))
+table(bigList2$h5Index, useNA = "always")
+
+bigList2$quartileFactor <- as.factor(bigList2$quartile)
+bigList2 <- bigList2 %>% arrange(desc(quartileFactor))
+
+ggplot(bigList2, aes(year, N, group = 1, colour=quartileFactor)) + geom_line() + 
+    facet_wrap(~ shortTitle, ncol=7) +
     theme_bw() +
@@
 
-ggplot(final.list.index, aes(x = scaleScore, y = title)) + geom_point(stat="identity", colour="red") + 
+x <- ggplot(final.list.index, aes(x = scaleScore, y = title)) + geom_point(stat="identity", colour="red") + 
     xlim(c(-3, 3))
@@
 colnames(gade) <- c("years", "programs")
+```
+
+```{r abstracts}
+abstract.df <- filter(full.df, attributes == "abstract")
+year.df <- filter(full.df, attributes == "pubYear")
+journal.df <- filter(full.df, attributes == "journal")
+abstract.df <- left_join(year.df, abstract.df, by = "articleID")
+abstract.df <- left_join(abstract.df, journal.df, by = "articleID")
+abstract.df <- abstract.df %>% select(-attributes.x, -attributes.y, -attributes)
+colnames(abstract.df) <- c("articleID", "year", "abstract", "journal")
+abstract.df$abstract <- gsub("[[:punct:]]", "", abstract.df$abstract)
+abstract.df$abstract <- tolower(abstract.df$abstract)
+
+ebp.df <- abstract.df[grep("evidence\\s?based\\spractices?|ebp|empirically\\s?supported\\streatments?", abstract.df$abstract), ]
+ebp.df$ebp <- rep("ebp", nrow(ebp.df))
+
+meta.df <- abstract.df[grep("meta\\s?analysis", abstract.df$abstract), ]
+meta.df$meta <- rep("meta", nrow(meta.df))
+
+rct.df <- abstract.df[grep("randomi[s|z]ed.*trial|[^non]experimental\\sdesign|rct|controlled\\sclinical\\strial|cct", abstract.df$abstract), ]
+rct.df$rct <- rep("rct", nrow(rct.df))
+
+systematicReview.df <- abstract.df[grep("systematic\\s?review", abstract.df$abstract), ]
+systematicReview.df$systematicReview <- rep("sr", nrow(systematicReview.df))
+
+practiceGuidelines.df <- abstract.df[grep("practice\\sguidelines|treatment\\sguidelines?", abstract.df$abstract), ]
+practiceGuidelines.df$practiceGuidelines <- rep("pg", nrow(practiceGuidelines.df))
+
+quasi <- abstract.df[grep("quasi\\s?experimental|non\\s?experimental", abstract.df$abstract), ]
+quasi.df$quasi <- rep("quasi", nrow(quasi.df))
+
+longitudinal.df <- abstract.df[grep("longitudinal\\sstudy", abstract.df$abstract), ]
+longitudinal.df$longitudinal <- rep("longitudinal", nrow(longitudinal.df))
+
+observational.df <- abstract.df[grep("cohort\\sstudy|case\\scontrol\\sstudy", abstract.df$abstract), ]
+observational.df$observational <- rep("observational", nrow(observational.df))
+
+literatureReview.df <- abstract.df[grep("literature\\sreview|review of the.*literature", abstract.df$abstract),]
+literatureReview.df$literatureReview <- rep("literatureReview", nrow(literatureReview.df))
+
+survey.df <- abstract.df[grep("survey", abstract.df$abstract), ]
+survey.df$survey <- rep("survey", nrow(survey.df))
+
 ```

### 2015-04-23 manuscript.Rmd
Updated stacked area chart.

@@
 ebp.df <- abstract.df[grep("evidence\\s?based\\spractices?|ebp|empirically\\s?supported\\streatments?", abstract.df$abstract), ]
-ebp.df$ebp <- rep("ebp", nrow(ebp.df))
+ebp.df$studyType <- rep("ebp", nrow(ebp.df))
 
 meta.df <- abstract.df[grep("meta\\s?analysis", abstract.df$abstract), ]
-meta.df$meta <- rep("meta", nrow(meta.df))
+meta.df$studyType <- rep("meta", nrow(meta.df))
 
 rct.df <- abstract.df[grep("randomi[s|z]ed.*trial|[^non]experimental\\sdesign|rct|controlled\\sclinical\\strial|cct", abstract.df$abstract), ]
-rct.df$rct <- rep("rct", nrow(rct.df))
+rct.df$studyType <- rep("rct", nrow(rct.df))
 
 systematicReview.df <- abstract.df[grep("systematic\\s?review", abstract.df$abstract), ]
-systematicReview.df$systematicReview <- rep("sr", nrow(systematicReview.df))
+systematicReview.df$studyType <- rep("sr", nrow(systematicReview.df))
 
 practiceGuidelines.df <- abstract.df[grep("practice\\sguidelines|treatment\\sguidelines?", abstract.df$abstract), ]
-practiceGuidelines.df$practiceGuidelines <- rep("pg", nrow(practiceGuidelines.df))
+practiceGuidelines.df$studyType <- rep("pg", nrow(practiceGuidelines.df))
 
-quasi <- abstract.df[grep("quasi\\s?experimental|non\\s?experimental", abstract.df$abstract), ]
-quasi.df$quasi <- rep("quasi", nrow(quasi.df))
+quasi.df <- abstract.df[grep("quasi\\s?experimental|non\\s?experimental", abstract.df$abstract), ]
+quasi.df$studyType <- rep("quasi", nrow(quasi.df))
 
 longitudinal.df <- abstract.df[grep("longitudinal\\sstudy", abstract.df$abstract), ]
-longitudinal.df$longitudinal <- rep("longitudinal", nrow(longitudinal.df))
+longitudinal.df$studyType <- rep("longitudinal", nrow(longitudinal.df))
 
 observational.df <- abstract.df[grep("cohort\\sstudy|case\\scontrol\\sstudy", abstract.df$abstract), ]
-observational.df$observational <- rep("observational", nrow(observational.df))
+observational.df$studyType <- rep("observational", nrow(observational.df))
 
 literatureReview.df <- abstract.df[grep("literature\\sreview|review of the.*literature", abstract.df$abstract),]
-literatureReview.df$literatureReview <- rep("literatureReview", nrow(literatureReview.df))
+literatureReview.df$studyType <- rep("literatureReview", nrow(literatureReview.df))
 
 survey.df <- abstract.df[grep("survey", abstract.df$abstract), ]
-survey.df$survey <- rep("survey", nrow(survey.df))
+survey.df$studyType <- rep("survey", nrow(survey.df))
+
+evidence.df <- rbind(ebp.df, meta.df, rct.df, systematicReview.df, 
+     practiceGuidelines.df, quasi.df, longitudinal.df, observational.df, 
+     literatureReview.df, survey.df)
+
+evidence.summary <- select(evidence.df, -abstract) %>% 
+    group_by(year, studyType) %>%
+    summarize(N = n()) %>%
+    group_by(studyType) %>%
+  mutate(cumulative = cumsum(N))
+
+evidence.summary.main <- filter(evidence.summary, studyType != "literatureReview" , studyType != "survey" ,
+    studyType != "ebp" , studyType != "longitudinal", studyType != "pg", studyType != "quasi")
+
+cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
+evidence.summary.main <- ungroup(evidence.summary.main)
+evidence.summary.main$year <- as.numeric(evidence.summary.main$year)
+evidence.summary.main$studyType <- as.factor(evidence.summary.main$studyType)
+
+year.labs <- as.character(seq(1989,2013, 2))
+
+ggplot(as.data.frame(xtabs(N~year+studyType, evidence.summary.main)), 
+    aes(x = as.numeric(year), y = Freq, fill=studyType)) + 
+    geom_area(alpha=.80, colour = "black", size = .2) + 
+    scale_fill_manual(values=cp, 
+          breaks = rev(levels(evidence.summary.main$studyType)),
+            labels = c("Systematic review", "RCT", 
+            "Cohort/Case Control", "Meta-analysis")) +
+  ylim(c(0, 60)) + 
+    scale_x_continuous(breaks = seq(0,24, 2), labels = year.labs) + 
+    theme(axis.text.x = element_text(angle = 45, hjust=1), 
+          panel.grid.minor=element_blank(),
+         legend.position=c(.25,.80),
+#         legend.background = element_blank(), 
+         legend.key = element_blank()   ) + 
+    ylab("Frequency") + 
+    xlab("Year") + 
+    labs(fill = "Study type") + 
+    scale_y_continuous(breaks = seq(0,60, 10))
 

### 2015-04-23 manuscript.Rmd
Abstract analysis complete.

@@
 
-practiceGuidelines.df <- abstract.df[grep("practice\\sguidelines|treatment\\sguidelines?", abstract.df$abstract), ]
-practiceGuidelines.df$studyType <- rep("pg", nrow(practiceGuidelines.df))
-
-quasi.df <- abstract.df[grep("quasi\\s?experimental|non\\s?experimental", abstract.df$abstract), ]
+quasi.df <- abstract.df[grep("cohort\\sstudy|case\\scontrol\\sstudy|quasi\\s?experimental|non\\s?experimental", abstract.df$abstract), ]
 quasi.df$studyType <- rep("quasi", nrow(quasi.df))
 
-longitudinal.df <- abstract.df[grep("longitudinal\\sstudy", abstract.df$abstract), ]
-longitudinal.df$studyType <- rep("longitudinal", nrow(longitudinal.df))
-
-observational.df <- abstract.df[grep("cohort\\sstudy|case\\scontrol\\sstudy", abstract.df$abstract), ]
-observational.df$studyType <- rep("observational", nrow(observational.df))
-
-literatureReview.df <- abstract.df[grep("literature\\sreview|review of the.*literature", abstract.df$abstract),]
-literatureReview.df$studyType <- rep("literatureReview", nrow(literatureReview.df))
-
-survey.df <- abstract.df[grep("survey", abstract.df$abstract), ]
-survey.df$studyType <- rep("survey", nrow(survey.df))
-
-evidence.df <- rbind(ebp.df, meta.df, rct.df, systematicReview.df, 
-     practiceGuidelines.df, quasi.df, longitudinal.df, observational.df, 
-     literatureReview.df, survey.df)
+evidence.df <- rbind(meta.df, rct.df, systematicReview.df, 
+     quasi.df)
 
@@
 
-evidence.summary.main <- filter(evidence.summary, studyType != "literatureReview" , studyType != "survey" ,
-    studyType != "ebp" , studyType != "longitudinal", studyType != "pg", studyType != "quasi")
+cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
+evidence.summary <- ungroup(evidence.summary)
+evidence.summary$year <- as.numeric(evidence.summary$year)
+evidence.summary$studyType <- as.factor(evidence.summary$studyType)
 
-cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
-evidence.summary.main <- ungroup(evidence.summary.main)
-evidence.summary.main$year <- as.numeric(evidence.summary.main$year)
-evidence.summary.main$studyType <- as.factor(evidence.summary.main$studyType)
+evidence.summary <- full_join(evidence.summary, abstractsYear.df, 
+    by = "year") %>%
+    mutate(studyProp =N / N.abstracts)
 
@@
 
-ggplot(as.data.frame(xtabs(N~year+studyType, evidence.summary.main)), 
+ggplot(as.data.frame(xtabs(N~year+studyType, evidence.summary)), 
     aes(x = as.numeric(year), y = Freq, fill=studyType)) + 
@@
     scale_fill_manual(values=cp, 
-          breaks = rev(levels(evidence.summary.main$studyType)),
-            labels = c("Systematic review", "RCT", 
-            "Cohort/Case Control", "Meta-analysis")) +
+        breaks = rev(levels(evidence.summary$studyType)),
+        labels = c("Systematic review", "RCT", "Cohort/Case Control", 
+           "Meta-analysis")) +
   ylim(c(0, 60)) + 
@@
     scale_y_continuous(breaks = seq(0,60, 10))
+
+df <- evidence.summary
+
+levels(df$studyType) <- c("Meta-analysis", "Quasi-experimental", "Observational", "RCT", "Systematic review")
+
+ggplot(na.omit(df), aes(year, studyProp, colour = studyType, 
+    group = studyType), na.rm=TRUE) + 
+    geom_smooth(aes(fill=studyType)) + facet_wrap(~studyType) + 
+    scale_fill_manual(values = cp) +   
+    scale_color_manual(values = cp) + 
+    theme(legend.position = "none") + 
+    ylab("Proportion") + 
+    geom_point(colour = "black", alpha = .60)
 

### 2015-04-23 manuscript.Rmd
Fixed error in label.

@@
         breaks = rev(levels(evidence.summary$studyType)),
-        labels = c("Systematic review", "RCT", "Cohort/Case Control", 
+        labels = c("Systematic review", "RCT", "Quasi-experimental", 
            "Meta-analysis")) +

### 2015-04-24 manuscript.Rmd
Fixed bugs. Facets working.

@@
 
-evidence.summary <- full_join(evidence.summary, abstractsYear.df, 
+abstractsYear.df <- group_by(abstract.df, year) %>% 
+    summarize(N.abstracts = n()) %>%
+    mutate(year = as.numeric(year))
+
+evidence.summary2 <- full_join(evidence.summary, abstractsYear.df, 
     by = "year") %>%
@@
 
-df <- evidence.summary
+df <- evidence.summary2
 
@@
     geom_point(colour = "black", alpha = .60)
+
+#####################
+
+evidence.summary3 <- select(evidence.df, -abstract) %>% 
+    group_by(journal, studyType) %>%
+    summarize(N = n())
+
+evidence.summaryOverall <- select(abstract.df, -abstract) %>%
+    group_by(journal) %>%
+    summarize(Overall.N = n())
+
+evidence.journals <- full_join(evidence.summary3, evidence.summaryOverall, by = "journal") %>%
+    mutate(N.prop = N/Overall.N) %>% group_by(journal) %>%
+    mutate(Overall.N.Strength = sum(N))
+
+evidence.journalsOverall <- evidence.journals %>% group_by(journal) %>%
+    mutate(Overall.N.Strength = sum(N))
+
+journalOrder <- evidence.journalsOverall
+
+ggplot(na.omit(evidence.journals), aes(N.prop, journal, group = journal, colour = studyType)) + geom_point(size = 3, alpha = .70) +
+    theme_bw() +
+    scale_colour_manual(values = cp) +
+    facet_grid(.~studyType)
+
+ggplot(na.omit(evidence.journals), aes(N, journal, group = journal, colour = studyType)) + 
+    geom_segment(aes(yend = journal), xend=0, colour="grey50") +
+    geom_point(alpha = .8, size = 3) + 
+    scale_color_manual(values = cp) + 
+    theme_bw() +
+    facet_grid(.~studyType) + 
+    theme(panel.grid.major.y = element_blank())
 

### 2015-04-24 manuscript.Rmd
Updated abstract analysis figures. All functional.

@@
 evidence.journals <- full_join(evidence.summary3, evidence.summaryOverall, by = "journal") %>%
-    mutate(N.prop = N/Overall.N) %>% group_by(journal) %>%
+    mutate(JN.prop = N/Overall.N) %>% group_by(journal) %>%
     mutate(Overall.N.Strength = sum(N))
@@
 
-journalOrder <- evidence.journalsOverall
+df <-  select(evidence.journalsOverall, studyType, N, Overall.N.Strength) %>%
+    rename(N.sort = Overall.N.Strength)
 
-ggplot(na.omit(evidence.journals), aes(N.prop, journal, group = journal, colour = studyType)) + geom_point(size = 3, alpha = .70) +
-    theme_bw() +
-    scale_colour_manual(values = cp) +
-    facet_grid(.~studyType)
+j.order <- unique(df$journal[order(df$N.sort, decreasing = FALSE)]) 
+df$journal <- factor(df$journal, levels = j.order)
 
-ggplot(na.omit(evidence.journals), aes(N, journal, group = journal, colour = studyType)) + 
+ggplot(na.omit(df), aes(x = N, y= journal, group = journal, colour = studyType)) + 
     geom_segment(aes(yend = journal), xend=0, colour="grey50") +
-    geom_point(alpha = .8, size = 3) + 
+    geom_point(size = 2.5) + 
     scale_color_manual(values = cp) + 
@@
     facet_grid(.~studyType) + 
+    theme(panel.grid.major.y = element_blank())
+
+evidence.journals <- full_join(evidence.summary3, evidence.summaryOverall, by = "journal") %>%
+    group_by(journal) %>%
+    mutate(Overall.N.Strength = sum(N)) %>%
+    select(-studyType, N) %>%
+    distinct(journal, Overall.N, Overall.N.Strength) %>%
+    mutate(Prop = Overall.N.Strength / Overall.N)
+
+df2 <- data.frame(evidence.journals)
+
+j.order <- unique(df2$journal[order(df2$Prop, decreasing = FALSE)]) 
+df2$journal <- factor(df2$journal, levels = j.order)
+
+ggplot(na.omit(df2), aes(x = Prop, y= journal, group = journal)) + 
+    geom_segment(aes(yend = journal), xend=0, colour="#b2abd2") +
+    geom_point(aes(size = Overall.N.Strength), colour = "#5e3c99") + 
+    scale_color_manual(values = cp) + 
+    theme_bw() +
     theme(panel.grid.major.y = element_blank())

### 2015-04-26 manuscript.Rmd
Small multiples working.

@@
 
-bigList <- left_join(n.so, n.yr) %>%
+```
+
+```{r plotSmallMultiples}
+hIndex.df <- arrange(hIndex, desc(h5Median)) %>% select(title, h5Median)
+hIndex.df$top10 <- NA
+hIndex.df$top10[1:10] <- "yes"
+hIndex.df$top10[11:nrow(hIndex.df)] <- "no"
+hIndex.df <- data.frame(hIndex.df)
+
+sm.df <- left_join(n.so, n.yr) %>%
     group_by(title, year) %>%
-    summarize(N = n())
-bigList$shortTitle <- abbreviate(bigList$title)
+    summarize(N = n()) %>%
+    mutate(Overall.N = sum(N)) %>%
+    ungroup() %>%
+    arrange(desc(Overall.N), title)
 
-bigList2 <- left_join(bigList, hIndex, by = "title")
-bigList2 <- within(bigList2, quartile <- as.integer(cut(h5Index, quantile(h5Index, probs=0:4/4, na.rm=TRUE), include.lowest=TRUE)))
-table(bigList2$h5Index, useNA = "always")
+sm.df <- full_join(sm.df, hIndex.df, by = "title") %>% 
+    ungroup %>% 
+    select(-h5Median)
 
-bigList2$quartileFactor <- as.factor(bigList2$quartile)
-bigList2 <- bigList2 %>% arrange(desc(quartileFactor))
+sm.df$top10 <- ifelse(is.na(sm.df$top10), "no", sm.df$top10)
 
-ggplot(bigList2, aes(year, N, group = 1, colour=quartileFactor)) + geom_line() + 
-    facet_wrap(~ shortTitle, ncol=7) +
+title <- sm.df %>% arrange(desc(Overall.N)) %>% distinct(title)
+
+title.order <- title$title
+
+sm.df$title2 <- factor(sm.df$title, levels = (title.order))
+
+Overall.N <- distinct(sm.df, title)
+
+x.df <- data.frame(title = Overall.N$title, label = title$Overall.N)
+
+xpos = rep(10, 78)
+ypos = rep(130, 78)
+lab <- Overall.N$Overall.N
+title2 <- unique(sm.df$title2)
+
+ldata <- data.frame(xpos, ypos, lab, title2)
+
+ggplot(sm.df, aes(year, N, group = 1)) + geom_line(aes(colour = top10)) + 
+facet_wrap( ~ title2, ncol=7) +
 theme_bw() +
@@
 scale_x_discrete(breaks=seq(1989, 2020, 8)) + 
-    ylim(0, 150)
+ylim(0, 150) + 
+geom_text(data = ldata, aes(x =xpos, y = ypos, label = lab, size =1), parse=FALSE)
+
+```
+
+```{r plotScatter}
 
@@
 
+evidence.df$studyType <- factor(evidence.df$studyType, labels= c("Meta-analysis", "Quasi-experimental", "RCT", "Systematic review"))
+
+evidence.df$studyType <- factor(evidence.df$studyType, 
+    levels(evidence.df$studyType)[c(1,4,3,2)])
+
 evidence.summary <- select(evidence.df, -abstract) %>% 
@@
 
-cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
+cp <- c("#b2abd2", "#5e3c99", "#fdb864", "#e66101" )
 evidence.summary <- ungroup(evidence.summary)
 evidence.summary$year <- as.numeric(evidence.summary$year)
-evidence.summary$studyType <- as.factor(evidence.summary$studyType)
+#evidence.summary$studyType <- as.factor(evidence.summary$studyType)
 
@@
     aes(x = as.numeric(year), y = Freq, fill=studyType)) + 
-    geom_area(alpha=.80, colour = "black", size = .2) + 
+    geom_area(alpha=.60, colour = "black", size = .2) + 
     scale_fill_manual(values=cp, 
-        breaks = rev(levels(evidence.summary$studyType)),
-        labels = c("Systematic review", "RCT", "Quasi-experimental", 
-           "Meta-analysis")) +
+        breaks = rev(levels(evidence.summary$studyType)))+
   ylim(c(0, 60)) + 
@@
          legend.key = element_blank()   ) + 
-    ylab("Frequency") + 
+    ylab("N") + 
     xlab("Year") + 
     labs(fill = "Study type") +
-    scale_y_continuous(breaks = seq(0,60, 10))
+    scale_y_continuous(breaks = seq(0,90, 10))
 
@@
 
-levels(df$studyType) <- c("Meta-analysis", "Quasi-experimental", "Observational", "RCT", "Systematic review")
-
 ggplot(na.omit(df), aes(year, studyProp, colour = studyType, 
     group = studyType), na.rm=TRUE) + 
-    geom_smooth(aes(fill=studyType)) + facet_wrap(~studyType) + 
+    geom_smooth(aes(fill=studyType), alpha = .60, colour = "dimgray") + facet_wrap(~studyType) + 
     scale_fill_manual(values = cp) +   
@@
     ylab("Proportion") + 
-    geom_point(colour = "black", alpha = .60)
+    geom_point(colour = "black", alpha = .60) + 
+    annotate("segment", x = 1989, y = 0, xend = 2013, yend = 0, alpha = .6, 
+        linetype= "solid") +
+    annotate("segment", x = 1989, y = 0, xend = 1989, yend = .0175, alpha = .6, 
+        linetype = "solid") +
+    annotate("segment", x = 2013, y = 0, xend = 2013, yend = .0175, alpha = .6,
+             linetype = "solid") +
+    scale_x_continuous(breaks = seq(1989, 2014, 4)) + 
+     theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
+    scale_y_continuous(breaks = seq(0, .015, .005))
 
-#####################
+######1989########
 
@@
 
-j.order <- unique(df$journal[order(df$N.sort, decreasing = FALSE)]) 
-df$journal <- factor(df$journal, levels = j.order)
+df1 <- df
 
-ggplot(na.omit(df), aes(x = N, y= journal, group = journal, colour = studyType)) + 
+#df1$studyType <- factor(df1$studyType)
+j.order <- unique(df1$journal[order(df1$N.sort, decreasing = FALSE)]) 
+df1$journal <- factor(df1$journal, levels = j.order)
+
+ggplot(na.omit(df1), aes(x = N, y= journal, group = journal, colour = studyType)) + 
     geom_segment(aes(yend = journal), xend=0, colour="grey50") +
@@
     facet_grid(.~studyType) + 
-    theme(panel.grid.major.y = element_blank())
+    theme(panel.grid.major.y = element_blank(), legend.position = "none") + 
+    xlim(0, 600) + 
+    ylab("Journal") +  
+    theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
+    scale_x_continuous(breaks = seq(0, 60, 10))
 
@@
 
-j.order <- unique(df2$journal[order(df2$Prop, decreasing = FALSE)]) 
+j.order <- unique(df2$journal[order(df2$Overall.N.Strength, decreasing = FALSE)]) 
 df2$journal <- factor(df2$journal, levels = j.order)
 
+df2  <- within(df2, quartile <- as.integer(cut(Overall.N.Strength, quantile(Overall.N.Strength, probs=0:4/4, na.rm=TRUE), include.lowest=TRUE)))
+
 ggplot(na.omit(df2), aes(x = Prop, y= journal, group = journal)) + 
-    geom_segment(aes(yend = journal), xend=0, colour="#b2abd2") +
-    geom_point(aes(size = Overall.N.Strength), colour = "#5e3c99") + 
-    scale_color_manual(values = cp) + 
+    geom_segment(aes(yend = journal), xend=0) +
+    geom_point(aes(size = Overall.N.Strength)) + 
     theme_bw() +
-    theme(panel.grid.major.y = element_blank())
+    theme(panel.grid.major.y = element_blank(), legend.position = c(.62, .65)) +
+    ylab("Journal") +
+    xlab("Proportion") +
+    labs(size = "Total number of \nEBP articles published")
 

### 2015-04-26 manuscript.Rmd
Updated csv files. Mistake.

@@
 hIndex.df$top10 <- NA
-hIndex.df$top10[1:10] <- "yes"
-hIndex.df$top10[11:nrow(hIndex.df)] <- "no"
+hIndex.df$top10[1:10] <- "Yes"
+hIndex.df$top10[11:nrow(hIndex.df)] <- "No"
 hIndex.df <- data.frame(hIndex.df)
@@
 
-sm.df$top10 <- ifelse(is.na(sm.df$top10), "no", sm.df$top10)
+sm.df$top10 <- ifelse(is.na(sm.df$top10), "No", sm.df$top10)
 
@@
 
-x.df <- data.frame(title = Overall.N$title, label = title$Overall.N)
-
-xpos = rep(10, 78)
+xpos = rep(12.5, 78)
 ypos = rep(130, 78)
-lab <- Overall.N$Overall.N
 title2 <- unique(sm.df$title2)
+lab <- paste("N=", Overall.N$Overall.N, sep="")
 
@@
 
-ggplot(sm.df, aes(year, N, group = 1)) + geom_line(aes(colour = top10)) + 
+ggplot(sm.df, aes(year, N, group=1)) + geom_line(aes(colour = top10)) + 
 facet_wrap( ~ title2, ncol=7) +
 theme_bw() +
-theme(panel.grid.major = element_blank(), 
+theme(panel.grid.major = element_blank(), legend.position = "bottom", 
 panel.grid.minor = element_blank(), 
@@
 ylim(0, 150) + 
-geom_text(data = ldata, aes(x =xpos, y = ypos, label = lab, size =1), parse=FALSE)
+geom_text(data = ldata, aes(x =xpos, y = ypos, label = lab), size =3) +
+    scale_color_manual(values=cp[c(4,2)], 
+                       name = "Top-10 Journal") + 
+    ylab("") + 
+    xlab("")
 

### 2015-04-30 manuscript.Rmd
Lots of updates. Big mess.

@@
 ```{r plotSmallMultiples}
-hIndex.df <- arrange(hIndex, desc(h5Median)) %>% select(title, h5Median)
-hIndex.df$top10 <- NA
-hIndex.df$top10[1:10] <- "Yes"
-hIndex.df$top10[11:nrow(hIndex.df)] <- "No"
-hIndex.df <- data.frame(hIndex.df)
-
 sm.df <- left_join(n.so, n.yr) %>%
@@
     summarize(N = n()) %>%
-    mutate(Overall.N = sum(N)) %>%
+    mutate(Overall.N = sum(N), year = as.numeric(year)) %>%
     ungroup() %>%
-    arrange(desc(Overall.N), title)
+    arrange(desc(Overall.N), title) %>%
+    rename(Year = year, Journal= title)
 
-sm.df <- full_join(sm.df, hIndex.df, by = "title") %>% 
-    ungroup %>% 
-    select(-h5Median)
+scopus.df <- read.csv("scopus.csv")
+
+sm.scopus.merged <-full_join(sm.df, scopus.df, by = c("Journal", "Year")) %>%
+    select(Year, Journal, N, Overall.N, Documents)
+
+abb <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/master.csv")
+abb$ID <- 1:nrow(abb)
+sm.scopus.merged <- full_join(sm.scopus.merged, abb, by = "Journal")
+
+title <- sm.scopus.merged %>% arrange(desc(Overall.N)) %>% distinct(Abbrev) %>% filter(!is.na(Abbrev))
+title.order = title$Abbrev
+sm.scopus.merged$title2 <- factor(sm.scopus.merged$Abbrev, levels = (title.order))
+Overall.N <- distinct(sm.scopus.merged, title2)
+
+hd.df <- sm.scopus.merged %>% select(Year, Abbrev, Journal, N, Overall.N, title2)
+
+scopus.plot.df <- sm.scopus.merged %>% select(Year, Abbrev, Journal, Documents,Overall.N)
+scopus.plot.df$Documents <- ifelse(scopus.plot.df$Documents == 0, NA, scopus.plot.df$Documents)
+scopus.plot.df <- scopus.plot.df[!is.na(scopus.plot.df$Documents), ]
+
+xpos = rep(2000, 79)
+ypos = rep(130, 79)
+
+lab <- paste("N=", title$Overall.N, sep="")
+Abbrev <- title$Abbrev
+
+ldata <- data.frame(xpos, ypos, lab, Abbrev)
+
+ggplot(hd.df,  aes(Year, N), group=1) + geom_line(colour="#e66101") +
+    facet_wrap(~ Abbrev) + 
+    geom_line(data = scopus.plot.df, aes(Year, Documents), colour="#5e3c99") + 
+    theme_bw() +
+    theme(legend.position = "bottom", 
+    panel.grid.minor = element_blank(), 
+    axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
+    geom_text(data = ldata, aes(x =xpos, y = ypos, label = lab), size =3)
+
+cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
+
+ggplot(sm.scopus.merged, aes(X, Documents)) + geom_point(aes(colour = Journal)) + 
+    facet_wrap(~Year) +
+    geom_smooth()
+
+cor(sm.scopus.merged$N, sm.scopus.merged$Documents, use ="complete.obs", method = "spearman")
 
@@
 title <- sm.df %>% arrange(desc(Overall.N)) %>% distinct(title)
-
 title.order <- title$title
-
 sm.df$title2 <- factor(sm.df$title, levels = (title.order))
-
 Overall.N <- distinct(sm.df, title)
@@
     annotate("text", articles.x, articles.placement, label = articles.label, size=3)
+
+sm.scopus.merged.3 <- sm.scopus.merged %>% group_by(Year) %>%
+    mutate(HD.N = sum(N))
+
+sm.scopus.merged.4 <- sm.scopus.merged %>% select(Year, Documents)
+
+sm.scopus.merged.4 <- na.omit(sm.scopus.merged.4)
+sm.scopus.merged.4 <- sm.scopus.merged.4 %>% group_by(Year) %>% mutate(scopus.N = sum(Documents))
+
+ggplot(sm.scopus.merged.3, aes(Year, HD.N), group=1) + geom_line() +
+    geom_line(data =sm.scopus.merged.4, aes(Year, scopus.N), colour = "red")
 

### 2015-05-01 manuscript.Rmd
Small multiples working.

--- 2015-04-26 manuscript.Rmd
@@
 hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
-hIndex <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/hIndex.csv")
-hIndex$h5Index <- ifelse(is.na(hIndex$h5Index), 0, hIndex$h5Index)
-hIndex$h5Median <- ifelse(is.na(hIndex$h5Median), 0, hIndex$h5Median)
 
@@
 #save.image(file = "socialWorkHistory.Rdata")
-```
-
-```{r dataNSF, eval=TRUE}
-n.grads <- c(rep(NA, 13), 238, 273, 304, 323, 308, 287, 338, 332,      
-    308, 289, 280, NA)
-
-years <- c(1989:2013)
-
-nsf <- data.frame(cbind(n.grads,  years))
-colnames(nsf) <- c("n.grads", "years")
 ```
@@
 ```{r plotSmallMultiples}
-hIndex.df <- arrange(hIndex, desc(h5Median)) %>% select(title, h5Median)
-hIndex.df$top10 <- NA
-hIndex.df$top10[1:10] <- "yes"
-hIndex.df$top10[11:nrow(hIndex.df)] <- "no"
-hIndex.df <- data.frame(hIndex.df)
 
+# Create an initial data frame from HD
 sm.df <- left_join(n.so, n.yr) %>%
@@
     summarize(N = n()) %>%
-    mutate(Overall.N = sum(N)) %>%
+    mutate(Overall.N = sum(N), year = as.numeric(year)) %>%
     ungroup() %>%
-    arrange(desc(Overall.N), title)
+    arrange(desc(Overall.N), title) %>%
+    rename(Year = year, Journal= title)
 
-sm.df <- full_join(sm.df, hIndex.df, by = "title") %>% 
-    ungroup %>% 
-    select(-h5Median)
+# Read Scopus database
+scopus.df <- read.csv("scopus.csv")
 
-sm.df$top10 <- ifelse(is.na(sm.df$top10), "no", sm.df$top10)
+# Join HD with Scopus and join abbreviation names
+sm.scopus.merged <-full_join(sm.df, scopus.df, by = c("Journal", "Year")) %>%
+    select(Year, Journal, N, Overall.N, Documents)
 
-title <- sm.df %>% arrange(desc(Overall.N)) %>% distinct(title)
+abb <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/master.csv")
+abb$ID <- 1:nrow(abb)
+sm.scopus.merged <- full_join(sm.scopus.merged, abb, by = "Journal") %>% 
+    select(-X) %>%
+    mutate(Documents = ifelse(Documents == 0, NA, Documents))
 
-title.order <- title$title
+# Re-order the factor by Overall.N
+title <- sm.scopus.merged %>% arrange(desc(Overall.N)) %>% 
+    distinct(Abbrev) %>% filter(!is.na(Abbrev)) %>% distinct()
 
-sm.df$title2 <- factor(sm.df$title, levels = (title.order))
+title.order = title$Abbrev
 
-Overall.N <- distinct(sm.df, title)
+sm.scopus.merged$Abbrev <- factor(sm.scopus.merged$Abbrev, levels = (title.order))
 
-x.df <- data.frame(title = Overall.N$title, label = title$Overall.N)
+# Create labels for the facets
+Overall.N <- distinct(sm.scopus.merged, Abbrev) 
+lab <- paste("N=", Overall.N$Overall.N, sep="")
+xpos = rep(2002, 79)
+ypos = rep(215, 79)
+ldata <- data.frame(xpos, ypos, lab, Overall.N$Abbrev) %>% 
+    rename(Abbrev = Overall.N.Abbrev)
 
-xpos = rep(10, 78)
-ypos = rep(130, 78)
-lab <- Overall.N$Overall.N
-title2 <- unique(sm.df$title2)
-
-ldata <- data.frame(xpos, ypos, lab, title2)
-
-ggplot(sm.df, aes(year, N, group = 1)) + geom_line(aes(colour = top10)) + 
-facet_wrap( ~ title2, ncol=7) +
+# Plotting function    
+ggplot(sm.scopus.merged,  aes(Year, N)) + geom_line(colour="#e66101") +
+    facet_wrap(~ Abbrev) + 
+    geom_line(data = sm.scopus.merged, aes(Year, Documents), group = 1,colour="#5e3c99") + 
     theme_bw() +
-theme(panel.grid.major = element_blank(), 
+    theme(legend.position = "bottom", 
     panel.grid.minor = element_blank(), 
     axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
-scale_x_discrete(breaks=seq(1989, 2020, 8)) + 
-ylim(0, 150) + 
-geom_text(data = ldata, aes(x =xpos, y = ypos, label = lab, size =1), parse=FALSE)
+    geom_text(data = ldata, aes(x =xpos, y = ypos, label = lab), size =3) + 
+    ylim(c(0,225)) +
+    scale_x_continuous(breaks=seq(1989, 2020, 8))
 

### 2015-05-01 functions/cleaningJournals.R

@@ -75,6 +75,12 @@ cleaningJournals.f <- function(){
                                  "Social Work with Groups",
                              "Social Work With Groups",
                              full.df$record)
+    full.df$record <- ifelse(full.df$record ==
+                                 "Maatskaplike Werk/Social Work",
+                             "Maatskaplike Werk",
+                             full.df$record)
+
+
 
     full.df$record <- ifelse(full.df$record ==
                                  "Social Work & Social Sciences Review",     # Spelling difference

### 2015-05-04 manuscript.Rmd
Working on forecast models.

@@
 ```{r plotSmallMultiples}
+# Remove 2014 & 2015
 
@@
     facet_wrap(~ Abbrev) + 
-    geom_line(data = sm.scopus.merged, aes(Year, Documents), group = 1,colour="#5e3c99") + 
+    geom_line(data = sm.scopus.merged, aes(Year, Documents), group = 1,colour="#5e3c99", alpha=.60) + 
     theme_bw() +
@@
 
-```{r plotScatter}
+```{r articleSummary}
+#---------------------------------
+# Create new data file 
+#---------------------------------
+articles.df <- left_join(n.so, n.yr) %>%
+    group_by(title, year) %>%
+    summarize(N = n()) %>%
+    mutate(Overall.N = sum(N), year = as.numeric(year)) %>%
+    ungroup() %>%
+    arrange(desc(Overall.N), title) %>%
+    rename(Year = year, Journal= title)
 
-n.so.yr <- left_join(n.so, n.yr) %>%
-    group_by(title) %>%
-    summarise(first = min(year), last = max(year), n = n()) %>%
-    arrange(title)
+scopus.df <- read.csv("scopus.csv")
+articles.df <-full_join(sm.df, scopus.df, by = c("Journal", "Year"))
 
-H <- unique.titles$Hodge
+#---------------------------------
+# Create new variables
+#---------------------------------
 
-final.list <- cbind(n.so.yr, H)
-final.list <- arrange(final.list, desc(n))
-final.list.index <- full_join(final.list, hIndex, by = "title")
+articles.df<- articles.df %>% 
+    mutate(notCited = N - N * (X..Not.Cited/100))
 
-final.list.index$h5Index <- ifelse(is.na(final.list.index$h5Index), 0,final.list.index$h5Index)
-#x <- ggplot(final.list.index, aes(x =reorder(title, n), y = n, colour = h5Index)) + geom_point(stat="identity") + coord_flip() + 
-#    theme_bw() 
-final.list.index$scaleScore <- scale(final.list.index$n)
-final.list.index$hScaled <- scale(final.list.index$h5Index)
-final.list.index <- arrange(final.list.index, scaleScore)
+articles.df<- articles.df %>% group_by(Year) %>%
+    summarize(HD.N = sum(N, na.rm=TRUE), 
+              Scopus.N = sum(Documents, na.rm=TRUE),
+              Uncited.N = sum(notCited, na.rm=TRUE)) %>%
+    mutate(HD.N = ifelse(HD.N == 0, NA, HD.N), Scopus.N = ifelse(Scopus.N == 0, NA, Scopus.N))
 
-x <- ggplot(final.list.index, aes(x = scaleScore, y = title)) + geom_point(stat="identity", colour="red") + 
-    xlim(c(-3, 3))
+articles.df$Scopus.N[articles.df$Year > 2011] <- NA
+articles.df$Uncited.N[articles.df$Year > 2011] <- NA
+articles.df$Uncited.N <- ifelse(articles.df$Uncited.N == 0, NA, articles.df$Uncited.N)
+
+articles.df.melted <- articles.df %>% 
+    reshape2::melt(id.vars = "Year")
+
+#--------------------------------------------
+#Create time series data to estimate uncited
+#--------------------------------------------
+
+uncited.ts <- as.vector(na.omit(articles.df$Uncited.N))
+uncited.ts <- ts(uncited.ts, frequency = 16, start = c(1996,1))
+
+foreward <- auto.arima(uncited.ts)
+uncited.forecast <-data.frame(forecast(fit, 2))
+forecast.estimated <- uncited.forecast$Point.Forecast
+forecast.years <- c(2012, 2013)
+
+backcast <- rev(uncited.ts)
+backcast <- auto.arima(backcast)
+uncited.backcast <- data.frame(forecast(backcast, 7))
+backcast.estimated <- rev(uncited.backcast$Point.Forecast)
+backcast.years <- c(1989:1995)
+
+Year <- c(backcast.years, forecast.years)
+value <- c(backcast.estimated, forecast.estimated)
+uncited.df <- data.frame(cbind(Year, value))
+uncited.df$variable <- "Estimated"
+
+#articles.df.melted <- rbind(articles.df.melted, uncited.df)
+
+cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
+
+ggplot(na.omit(articles.df.melted),  aes(Year, value, colour = variable)) + 
+    geom_line() + 
+    geom_point() + 
+    scale_color_manual(values=cp) + 
+    geom_point(data = uncited.df, aes(Year, value, colour = variable)) + 
+    ylim(c(0, 2700))
 

### 2015-05-04 manuscript.Rmd
Uncited article plot functional.

@@
 foreward <- auto.arima(uncited.ts)
-uncited.forecast <-data.frame(forecast(fit, 2))
+uncited.forecast <-data.frame(forecast(foreward, 2))
 forecast.estimated <- uncited.forecast$Point.Forecast
@@
 
-#articles.df.melted <- rbind(articles.df.melted, uncited.df)
+percent.df <- rbind(articles.df.melted, uncited.df)
+percent.df.cast <- reshape2::dcast(percent.df, Year  ~ variable, value.var = "value")
+percent.df.cast$estimate.code <- ifelse(is.na(percent.df.cast$Uncited.N), 
+    "arima.Estimated", ifelse(!is.na(percent.df.cast$Uncited.N), "Scopus.Estimated", percent.df.cast$Uncited.N))
 
-cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
+percent.df.cast$percent <- ifelse(!is.na(percent.df.cast$Uncited.N), percent.df.cast$Uncited.N/percent.df.cast$HD.N, ifelse(!is.na(percent.df.cast$Estimated), percent.df.cast$Estimated/percent.df.cast$HD.N, percent.df.cast$Uncited.N))
 
-ggplot(na.omit(articles.df.melted),  aes(Year, value, colour = variable)) + 
+percent.df.cast$NoCites <- ifelse(is.na(percent.df.cast$Uncited.N), percent.df.cast$Estimated, 
+                           ifelse(is.na(percent.df.cast$Estimated), percent.df.cast$Uncited.N, percent.df.cast$Uncited.N))
+
+percent.cast.a <- select(percent.df.cast, Year, HD.N, NoCites)
+percent.cast.b <- select(percent.df.cast, Year, estimate.code, percent)
+
+percent.melt.a <- reshape2::melt(percent.cast.a, id.vars="Year")
+percent.melt.b <- reshape2::melt(percent.cast.b, id.vars=c("Year", "estimate.code"))
+
+percent.melt.b <- rename(percent.melt.b, variable2 = variable, value2 = value)
+percent.melt.df <- full_join(percent.melt.a, percent.melt.b, by = "Year")
+
+percent.text <- select(percent.melt.df, Year, value, value2, variable) 
+percent.text <- percent.text %>% filter(variable != "HD.N")
+percent.text$value2 <- round(percent.text$value2, digits=3) *100 
+percent.text$value2 <- paste(percent.text$value2, "%", sep="")
+percent.text <- percent.text[c(1, 7, 11, 16, 19, 22, 24),]
+
+#percent.df.cast <- select(percent.df.cast, Year, estimate.code, percent) %>% filter(Year <= 2013)
+#colnames(percent.df.cast) <- c("Year", "variable", "value")
+
+cp <- c("#5e3c99","#e66101")
+
+ggplot(na.omit(subset(percent.melt.df, subset=variable != "Scopus.N")), 
+    aes(Year, value, colour = variable)) + 
     geom_line() + 
     geom_point() +
-    scale_color_manual(values=cp) + 
-    geom_point(data = uncited.df, aes(Year, value, colour = variable)) + 
-    ylim(c(0, 2700))
+    scale_color_manual(values=cp, labels = c("Number of Articles Published", "Number of Uncited Articles \n(Past 3 Years)")) +
+    geom_text(data = percent.text, aes(Year, value+40, label = value2), size=4, colour="black") + 
+    ylim(c(0, 2200)) + 
+    theme(legend.position="bottom") +
+    theme(legend.title=element_blank()) +
+    ylab("N")
 

### 2015-05-05 manuscript.Rmd
Uncited plot functional.

--- 2015-05-01 manuscript.Rmd
@@
 # Plotting function    
-ggplot(sm.scopus.merged,  aes(Year, N)) + geom_line(colour="#e66101") +
+plotSmallMultiples <-  ggplot(sm.scopus.merged,  aes(Year, N)) + geom_line(colour="#e66101") +
     facet_wrap(~ Abbrev) + 
-    geom_line(data = sm.scopus.merged, aes(Year, Documents), group = 1,colour="#5e3c99") + 
+    geom_line(data = sm.scopus.merged, aes(Year, Documents), group = 1,colour="#5e3c99", alpha=.60) + 
     theme_bw() +
@@
 
-```{r plotScatter}
+```{r uncitedSummary}
+#=======================================
+# Create new data file 
+#=======================================
 
-n.so.yr <- left_join(n.so, n.yr) %>%
-    group_by(title) %>%
-    summarise(first = min(year), last = max(year), n = n()) %>%
-    arrange(title)
+articles.df <- left_join(n.so, n.yr) %>%
+    group_by(title, year) %>%
+    summarize(N = n()) %>%
+    mutate(Overall.N = sum(N), year = as.numeric(year)) %>%
+    ungroup() %>%
+    arrange(desc(Overall.N), title) %>%
+    rename(Year = year, Journal= title)
 
-H <- unique.titles$Hodge
+scopus.df <- read.csv("scopus.csv")
+articles.df <-full_join(sm.df, scopus.df, by = c("Journal", "Year"))
 
-final.list <- cbind(n.so.yr, H)
-final.list <- arrange(final.list, desc(n))
-final.list.index <- full_join(final.list, hIndex, by = "title")
+articles.df<- articles.df %>% 
+    filter(Year <= 2013) %>%
+    mutate(propNotCited = X..Not.Cited/100) %>%
+    select(-X, -SJR, -SNIP, -Citations, -IPP, -X..Not.Cited, -Overall.N, -X..Review) %>%
+    rename(HD.N = N, scopus.N = Documents)
 
-final.list.index$h5Index <- ifelse(is.na(final.list.index$h5Index), 0,final.list.index$h5Index)
-#x <- ggplot(final.list.index, aes(x =reorder(title, n), y = n, colour = h5Index)) + geom_point(stat="identity") + coord_flip() + 
-#    theme_bw() 
-final.list.index$scaleScore <- scale(final.list.index$n)
-final.list.index$hScaled <- scale(final.list.index$h5Index)
-final.list.index <- arrange(final.list.index, scaleScore)
+#=======================================
+# Calculate number of uncited articles
+#=======================================
 
-x <- ggplot(final.list.index, aes(x = scaleScore, y = title)) + geom_point(stat="identity", colour="red") + 
-    xlim(c(-3, 3))
+#  First reduce the data file to 1996 to 2010. Data contained significant problems that brought the number of uncited values to almost 0.  Was not reliable.
+
+df.96.10 <- filter(articles.df, Year >= 1996, Year <= 2010)
+
+# If HD article count is missing, replace with Scopus count
+df.96.10$HD.N <- ifelse(is.na(df.96.10$HD.N), df.96.10$scopus.N, df.96.10$HD.N)
+
+# Some counts have 0 values.  Set these to NA and then omit
+df.96.10$HD.N <-ifelse(df.96.10$HD.N == 0, NA, df.96.10$HD.N) 
+df.96.10 <- df.96.10[!is.na(df.96.10$HD.N), ]
+
+# If uncited proportion is missing, compute average for that particular journal
+# Replace missing value with the mean value
+df.96.10 <- df.96.10 %>% group_by(Journal) %>%
+        mutate(meanPropUncited = mean(propNotCited, na.rm=TRUE)) %>% ungroup()
+
+df.96.10$propNotCited <- ifelse(is.na(df.96.10$propNotCited),
+     df.96.10$meanPropUncited, df.96.10$propNotCited)
+
+# If uncited proportion is missing because it was not in scopus, replace the missing
+# value with the overall mean uncited proportion
+
+overallPropUncited <- mean(df.96.10$propNotCited, na.rm=TRUE)
+
+df.96.10$propNotCited <- ifelse(is.na(df.96.10$propNotCited), overallPropUncited, df.96.10$propNotCited)
+
+# Calculate number of not cited
+
+df.96.10 <- df.96.10 %>% mutate(countNotCited = HD.N - (HD.N * propNotCited))
+
+df.96.10.Summary <- df.96.10 %>% group_by(Year) %>%
+    summarize(Published = sum(HD.N), 
+              Uncited = sum(countNotCited))
+
+#============================================
+# Create a melted data frame for the plot
+#============================================
+
+df.95.11 <- select(articles.df, Year, HD.N) %>% 
+    filter(Year <= 1995 |Year >=2011) %>%
+    rename(published = HD.N) %>%
+    group_by(Year) %>%
+    summarize(Published = sum(published, na.rm=TRUE)) %>%
+    ungroup() %>%
+    mutate(Uncited = NA)
+
+uncited.df <- rbind(df.96.10.Summary, df.95.11) %>%
+    arrange(Year)
+uncited.df$percentage <- uncited.df$Uncited/uncited.df$Published*100    
+uncited.melted <- reshape2::melt(uncited.df[,c("Year", "Published", "Uncited")], id.vars = "Year")
+
+#=======================================
+# Create text annotations to plot 
+#=======================================
+
+percent.df <- uncited.df
+percent.df$percentage <- round(percent.df$percentage, digits=1) 
+percent.df$percentLabel<- paste(percent.df$percentage, "%", sep="")
+percent.df <- na.omit(percent.df)
+percent.df <- percent.df[c(seq(1, 15, 3), 15),]
+
+#=======================================
+# Create the plot 
+#=======================================
+
+cp <- c("#5e3c99", "#e66101")
+
+ggplot(observed.df.melted, aes(Year, value, colour = variable)) + 
+    geom_line(alpha = .60) + 
+    geom_point(size =4) +
+    scale_color_manual(values=cp, labels = c("Number of Articles Published",
+         "Estimated Number of Uncited Articles")) +
+    theme(legend.title=element_blank()) +
+    theme(legend.position = "bottom") +
+    ylab("N") +
+    geom_text(data = percent.df, aes(Year, Uncited -70, label = percentLabel), size =4, colour = "black") +
+    scale_y_continuous(breaks = seq(0, 2250, 250), limits = c(0, 2250))
 

### 2015-05-05 manuscript.Rmd
Uncited working.

@@
 # If HD article count is missing, replace with Scopus count
-df.96.10$HD.N <- ifelse(is.na(df.96.10$HD.N), df.96.10$scopus.N, df.96.10$HD.N)
 
-# Some counts have 0 values.  Set these to NA and then omit
+# Some counts have 0 values.  Set these to NA and then omit.
 df.96.10$HD.N <-ifelse(df.96.10$HD.N == 0, NA, df.96.10$HD.N) 
@@
 
-# If uncited proportion is missing because it was not in scopus, replace the missing
+# If uncited proportion is missing because it was not in Scopus, replace the missing
 # value with the overall mean uncited proportion
@@
 uncited.df$percentage <- uncited.df$Uncited/uncited.df$Published*100
-uncited.melted <- reshape2::melt(uncited.df[,c("Year", "Published", "Uncited")], id.vars = "Year")
+
+uncited.df <- left_join(uncited.df, journals.year, by = "Year")
+
+uncited.melted <- reshape2::melt(uncited.df[,c("Year", "Published", "Uncited", "N.Journals")], id.vars = c("Year", "N.Journals"))
 
@@
 
-ggplot(observed.df.melted, aes(Year, value, colour = variable)) + 
+ggplot(uncited.melted, aes(Year, value, colour = variable,)) + 
     geom_line(alpha = .60) + 
-    geom_point(size =4) +
+    geom_point(size = 4) +
     scale_color_manual(values=cp, labels = c("Number of Articles Published",

### 2015-05-11 manuscript.Rmd
Updated stuff.

@@
 
-df.96.10 <- df.96.10 %>% mutate(countNotCited = HD.N - (HD.N * propNotCited))
+df.96.10 <- df.96.10 %>% mutate(countNotCited = HD.N * propNotCited)
 
@@
 #============================================
+
+# We need to include years before and after the scopus data.
 
@@
     arrange(Year)
+
+#============================================
+# Compute percentage variable and melt
+#============================================
+
 uncited.df$percentage <- uncited.df$Uncited/uncited.df$Published*100
 
-uncited.df <- left_join(uncited.df, journals.year, by = "Year")
-
-uncited.melted <- reshape2::melt(uncited.df[,c("Year", "Published", "Uncited", "N.Journals")], id.vars = c("Year", "N.Journals"))
+uncited.melted <- reshape2::melt(uncited.df[,c("Year", "Published", "Uncited")], 
+     id.vars = c("Year"))
 
@@
 
-ggplot(uncited.melted, aes(Year, value, colour = variable,)) + 
+plotArticles <- ggplot(uncited.melted, aes(Year, value, colour = variable,)) + 
     geom_line(alpha = .60) + 
@@
 
-```{r plotArticleCount, eval=TRUE}
-n.articles.year <- filter(full.df, attributes == "pubYear") 
-year.split <- split(n.articles.year, n.articles.year$record)
-year.count <- unlist(lapply(year.split, nrow))
-year.count <- year.count[order(names(year.count))]
-years <- names(year.count)
+```{r}
+# Read Scopus database
+scopus.df <- read.csv("scopus.csv")
 
-articles.year.df <- data.frame(years, year.count)
-rownames(articles.year.df) <- NULL
-
-#Annotation data file
-articles.x <- as.factor(articles.year.df[c(1, 6, 12, 18, 25), 1]) 
-articles.y <- articles.year.df[c(1, 6, 12, 18, 25), 2] 
-articles.label <- as.character(articles.y)
-articles.placement <- articles.y-50
-
-plot.article.count <- ggplot(nsf, aes(as.factor(years), 
-    y = n.grads, group=1)) + 
-    geom_line(colour="red") + 
-    geom_point(colour="red") + 
-    #geom_point(colour="red") + 
-    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8), 
-    title = element_text(size = 10), plot.title=element_text(size=10)) + 
-    xlab("Year") + 
-    ylab("Articles") + 
-    ggtitle("A. Number of Articles by Year") +
-    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
-    ylim(c(0,2200)) + 
-    geom_line(data = articles.year.df, aes(as.factor(years), y = year.count), colour="steelblue") + 
-    #geom_text(data = nsf, aes(label = n.grads), vjust = 2, size = 2.75) +
-    geom_point(data = articles.year.df, aes(as.factor(years), y = articles.year.df$year.count), colour="steelblue") + 
-    annotate("text", factor(c(2002, 2005, 2008, 2012)), 
-    c(165, 225, 250, 190) + 150, label = c("238","323", "338", "280") , size = 3) + 
-    annotate("text", articles.x, articles.placement, label = articles.label, size=3)
-
-sm.scopus.merged.3 <- sm.scopus.merged %>% group_by(Year) %>%
-    mutate(HD.N = sum(N))
-
-sm.scopus.merged.4 <- sm.scopus.merged %>% select(Year, Documents)
-
-sm.scopus.merged.4 <- na.omit(sm.scopus.merged.4)
-sm.scopus.merged.4 <- sm.scopus.merged.4 %>% group_by(Year) %>% mutate(scopus.N = sum(Documents))
-
-ggplot(sm.scopus.merged.3, aes(Year, HD.N), group=1) + geom_line() +
-    geom_line(data =sm.scopus.merged.4, aes(Year, scopus.N), colour = "red")
+boxplot.scopus <- ggplot(subset(scopus.df, subset =Year <=2013 & Year >= 1999), aes(as.factor(Year), IPP)) +
+    geom_boxplot()
 
@@
 ```{r plotJournalCount, eval=TRUE}
+
 n.journals.year <- filter(full.df, attributes == "journal") %>%
@@
     scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 70)) 
-```
-
-```{r plotH-Index, eval=TRUE}
-final.list.index <- within(final.list.index, quartile <- as.integer(cut(h5Index, quantile(h5Index, probs=0:4/4, na.rm=TRUE), include.lowest=TRUE)))
-
-final.list.index <- within(final.list.index, years <- as.numeric(last) - as.numeric(first) +1)
-
-plotIndex <- ggplot(final.list.index, aes(x = n, y = h5Index )) + 
-    geom_point(aes(colour=factor(quartile), size = years), alpha=.80) +
-    geom_smooth() + 
-    scale_colour_manual(values=cp)
-
 ```
@@
     labs(size = "Standard deviation") 
-```
-
-```{r authorNames}
-authorNames  <- filter(full.df, attributes == "author")
-
-authorNames.df <- authorNames
-authorNames.df$record <- sub("(?<=, [A-Z]).*$", "", authorNames.df$record, perl=TRUE)
-authorNames.df <- authorNames.df %>% group_by(record) %>% 
-    summarize(N = n()) %>%
-    arrange(desc(N))
-```{r gade, eval=TRUE}
-years <- c(1989:2015)
-programs <- rep(NA, 27)
-gade <- as.data.frame(cbind(as.character(years), programs))
-gade$programs <- as.numeric(gade$programs)
-gade[15, 2] <- 72
-gade[27, 2] <- 86
-colnames(gade) <- c("years", "programs")
 ```
@@
 
-```
-
-```{r ratios}
-years <- c(1989:2013)
-article.grad.ratio <- articles.year.df$year.count / nsf$n.grads
-
-ratio.df <- data.frame(cbind(years, article.grad.ratio))
-colnames(ratio.df) <- c("years", "ratio")
-ratio.df <- ratio.df[-(1:13), ]
-
-grad.ratio.df.melted <- reshape2::melt(ratio.df, id.vars="years")
-
-ratio.plot <- ggplot(grad.ratio.df.melted, aes(years, value, group= variable, 
-    color=variable)) + geom_line() +
-    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
-    title = element_text(size = 10), 
-    legend.title=element_blank()) +
-    scale_colour_manual(values=cbPalette)  +
-    scale_x_continuous(breaks=c(seq(2002, 2013))) +
-    scale_y_continuous(limits = c(0,8)) +
-    ylab("Value") +
-    xlab("Year")
-
-```
-
-```{r eval=FALSE}
-colnames(n.journals.year) <- c("years", "journals")
-n_authors2 <- rename(n_authors2, years = ID, Avg.Authors = Average, Mdn.Authors = Median, Sd.Authors = Standard_Deviation)
-
-scholarly.df <- left_join(articles.year.df, n.journals.year, by = "years") 
-scholarly.df <- left_join(scholarly.df, n_authors2, by = "years")
-scholarly.df <- left_join(scholarly.df, nsf, by = "years")
-scholarly.df <- left_join(scholarly.df, pages.df, by = "years")
-scholarly.df[c(26, 27), ] <- rep(NA)
-scholarly.df[26, 1] <- 2014
-scholarly.df[27, 1] <- 2015
-
-scholarly.df <- mutate(scholarly.df, years = as.numeric(years)) %>%
-    rename(article.count = year.count, journal.count = year.count, program.growth = growth) 
-scholarly.df$gade <- rep(NA, nrow(scholarly.df))  
-scholarly.df$gade[15] <- 72
-scholarly.df$gade[27] <- 86
 ```

### 2015-05-15 manuscript.Rmd
Updated file.  Getting markdown PDF working.

@@
 # Read Scopus database
-scopus.df <- read.csv("scopus.csv")
+scopus.df <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/scopus.csv")
 
@@
 
-abb <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/master.csv")
-abb$ID <- 1:nrow(abb)
-sm.scopus.merged <- full_join(sm.scopus.merged, abb, by = "Journal") %>% 
-    select(-X) %>%
-    mutate(Documents = ifelse(Documents == 0, NA, Documents))
+# sm.scopus.merged.table <- group_by(sm.scopus.merged, Journal) %>%
+#     summarize(DataBase.N = sum(N, na.rm=TRUE), Scopus.N = sum(Documents, na.rm=TRUE)) %>%
+#     arrange(desc(DatabBase.N))
+# 
+# data.frame(sm.scopus.merged.table)
 
-# Re-order the factor by Overall.N
-title <- sm.scopus.merged %>% arrange(desc(Overall.N)) %>% 
-    distinct(Abbrev) %>% filter(!is.na(Abbrev)) %>% distinct()
-
-title.order = title$Abbrev
-
-sm.scopus.merged$Abbrev <- factor(sm.scopus.merged$Abbrev, levels = (title.order))
-
-# Create labels for the facets
-Overall.N <- distinct(sm.scopus.merged, Abbrev) 
-lab <- paste("N=", Overall.N$Overall.N, sep="")
-xpos = rep(2002, 79)
-ypos = rep(215, 79)
-ldata <- data.frame(xpos, ypos, lab, Overall.N$Abbrev) %>% 
-    rename(Abbrev = Overall.N.Abbrev)
+# abb <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/master.csv")
+# abb$ID <- 1:nrow(abb)
+# sm.scopus.merged <- full_join(sm.scopus.merged, abb, by = "Journal") %>% 
+#     select(-X) %>%
+#     mutate(Documents = ifelse(Documents == 0, NA, Documents))
+# 
+# # Re-order the factor by Overall.N
+# title <- sm.scopus.merged %>% arrange(desc(Overall.N)) %>% 
+#     distinct(Abbrev) %>% filter(!is.na(Abbrev)) %>% distinct()
+# 
+# title.order = title$Abbrev
+# 
+# sm.scopus.merged$Abbrev <- factor(sm.scopus.merged$Abbrev, levels = (title.order))
+# 
+# # Create labels for the facets
+# Overall.N <- distinct(sm.scopus.merged, Abbrev) 
+# lab <- paste("N=", Overall.N$Overall.N, sep="")
+# #xpos = rep(2002, 79)
+# #ypos = rep(215, 79)
+# xpos = rep(2025, 79)
+# ypos = rep(25, 79)
+# ldata <- data.frame(xpos, ypos, lab, Overall.N$Abbrev) %>% 
+#     rename(Abbrev = Overall.N.Abbrev) 
+#
 
 # Plotting function    
-plotSmallMultiples <-  ggplot(sm.scopus.merged,  aes(Year, N)) + geom_line(colour="#e66101") +
-    facet_wrap(~ Abbrev) + 
-    geom_line(data = sm.scopus.merged, aes(Year, Documents), group = 1,colour="#5e3c99", alpha=.60) + 
-    theme_bw() +
-    theme(legend.position = "bottom", 
-    panel.grid.minor = element_blank(), 
-    axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
-    geom_text(data = ldata, aes(x =xpos, y = ypos, label = lab), size =3) + 
-    ylim(c(0,225)) +
-    scale_x_continuous(breaks=seq(1989, 2020, 8))
+# plotSmallMultiples <-  ggplot(sm.scopus.merged,  aes(Year, N)) + geom_line(colour="#e66101") +
+#     facet_wrap(~ Abbrev) + 
+#     geom_line(data = sm.scopus.merged, aes(Year, Documents), group = 1,colour="#5e3c99", alpha=.60) + 
+#     theme_bw() +
+#     theme(legend.position = "bottom", 
+#     panel.grid.minor = element_blank(), 
+#     axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
+#     geom_text(data = ldata, aes(x =xpos, y = ypos, label = lab), size =3) + 
+#     ylim(c(0,225)) +
+#     scale_x_continuous(breaks=seq(1989, 2015, 8)) + 
+#     expand_limits(x = 2050))
 
@@
 
-scopus.df <- read.csv("scopus.csv")
+scopus.df <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/scopus.csv")
 articles.df <-full_join(sm.df, scopus.df, by = c("Journal", "Year"))
@@
 
-ggplot(as.data.frame(xtabs(N~year+studyType, evidence.summary)), 
+stacked.plot <- ggplot(as.data.frame(xtabs(N~year+studyType, evidence.summary)), 
     aes(x = as.numeric(year), y = Freq, fill=studyType)) + 
@@
 
-ggplot(na.omit(df), aes(year, studyProp, colour = studyType, 
+evidence.plot <- ggplot(na.omit(df), aes(year, studyProp, colour = studyType, 
     group = studyType), na.rm=TRUE) + 
@@
 
-ggplot(na.omit(df1), aes(x = N, y= journal, group = journal, colour = studyType)) + 
+journal.evidence.plot <- ggplot(na.omit(df1), aes(x = N, y= journal, group = journal, colour = studyType)) + 
     geom_segment(aes(yend = journal), xend=0, colour="grey50") +
@@
 
-ggplot(na.omit(df2), aes(x = Prop, y= journal, group = journal)) + 
+EBP.plot <- ggplot(na.omit(df2), aes(x = Prop, y= journal, group = journal)) + 
     geom_segment(aes(yend = journal), xend=0) +
@@
 
-As shown in Table 1, `r nrow(final.list.25)` journals were included in the current study.
+```{r}
+# As shown in Table 1, `r nrow(final.list.25)` journals were included in the current study.
 The mean number of years of inclusion is `r options(digits=2); mean(final.list.updated$study.time)` (median = `r options(digits=2); median(final.list.updated$study.time);`, sd =  `r options(digits=2); sd(final.list.updated$study.time)`).
@@
 The decline from 2012 to 2013 should be interpreted cautiously, as this may be an artifact due to delays in indexing.
-
+```
 Data from the National Science Foundation regarding the number of earned doctorates in social work and social welfare were added to further contextualize the publication trends.
@@
 ```{r finalArticleListecho=FALSE, comment=NA}
-print.data.frame(final.list, row.names=FALSE)
+#print.data.frame(final.list, row.names=FALSE)
 ```
@@
 ```{r}
-plotIndex
+#plotIndex
 ```
@@
 ```{r}
-plot.article.count
+#plot.article.count
 ```
@@
 
+```{r}
+evidence.plot
+```
+\newpage
+
+```{r}
+stacked.plot
+```
+\newpage
+```{r fig.height=9.5}
+journal.evidence.plot
+```
+
+\newpage
+```{r fig.height=9.5}
+EBP.plot
+```
+
+\newpage
+
 # Appendix A

### 2015-05-16 manuscript.Rmd
Updating small multiples.

@@
 
-# sm.scopus.merged.table <- group_by(sm.scopus.merged, Journal) %>%
-#     summarize(DataBase.N = sum(N, na.rm=TRUE), Scopus.N = sum(Documents, na.rm=TRUE)) %>%
-#     arrange(desc(DatabBase.N))
+ sm.scopus.merged.table <- group_by(sm.scopus.merged, Journal) %>%
+     summarize(DataBase.N = sum(N, na.rm=TRUE), Scopus.N = sum(Documents, na.rm=TRUE)) %>%
+     arrange(desc(DataBase.N))
+
+ abb <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/master.csv")
+ abb$ID <- 1:nrow(abb)
+ sm.scopus.merged <- full_join(sm.scopus.merged, abb, by = "Journal") %>% 
+     select(-X) %>%
+     mutate(Documents = ifelse(Documents == 0, NA, Documents))
+
+ # Re-order the factor by Overall.N
+ title <- sm.scopus.merged %>% arrange(desc(Overall.N)) %>% 
+     distinct(Abbrev) %>% filter(!is.na(Abbrev)) %>% distinct()
+
+ title.order = title$Abbrev
+
+ sm.scopus.merged$Abbrev <- factor(sm.scopus.merged$Abbrev, levels = (title.order))
 # 
-# data.frame(sm.scopus.merged.table)
+ # Create labels for the facets
+ Overall.N <- distinct(sm.scopus.merged, Abbrev) 
+ lab <- paste("N=", Overall.N$Overall.N, sep="")
+ xpos = rep(2002, 79)
+ ypos = rep(215, 79)
+ ldata <- data.frame(xpos, ypos, lab, Overall.N$Abbrev) %>% 
+     rename(Abbrev = Overall.N.Abbrev)
 
-# abb <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/master.csv")
-# abb$ID <- 1:nrow(abb)
-# sm.scopus.merged <- full_join(sm.scopus.merged, abb, by = "Journal") %>% 
-#     select(-X) %>%
-#     mutate(Documents = ifelse(Documents == 0, NA, Documents))
-# 
-# # Re-order the factor by Overall.N
-# title <- sm.scopus.merged %>% arrange(desc(Overall.N)) %>% 
-#     distinct(Abbrev) %>% filter(!is.na(Abbrev)) %>% distinct()
-# 
-# title.order = title$Abbrev
-# 
-# sm.scopus.merged$Abbrev <- factor(sm.scopus.merged$Abbrev, levels = (title.order))
-# 
-# # Create labels for the facets
-# Overall.N <- distinct(sm.scopus.merged, Abbrev) 
-# lab <- paste("N=", Overall.N$Overall.N, sep="")
-# #xpos = rep(2002, 79)
-# #ypos = rep(215, 79)
-# xpos = rep(2025, 79)
-# ypos = rep(25, 79)
-# ldata <- data.frame(xpos, ypos, lab, Overall.N$Abbrev) %>% 
-#     rename(Abbrev = Overall.N.Abbrev) 
-#
+ titles.reduced <- unique(sm.scopus.merged$Journal)
+ titles.reduced.1 <- titles.reduced[1:40]
+ titles.reduced.2 <- titles.reduced[41:length(titles.reduced)]
 
 # Plotting function    
-# plotSmallMultiples <-  ggplot(sm.scopus.merged,  aes(Year, N)) + geom_line(colour="#e66101") +
-#     facet_wrap(~ Abbrev) + 
-#     geom_line(data = sm.scopus.merged, aes(Year, Documents), group = 1,colour="#5e3c99", alpha=.60) + 
-#     theme_bw() +
-#     theme(legend.position = "bottom", 
-#     panel.grid.minor = element_blank(), 
-#     axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
-#     geom_text(data = ldata, aes(x =xpos, y = ypos, label = lab), size =3) + 
-#     ylim(c(0,225)) +
-#     scale_x_continuous(breaks=seq(1989, 2015, 8)) + 
-#     expand_limits(x = 2050))
+ plotSmallMultiples.1 <-  ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.1, ],  aes(Year, N)) +
+     geom_line(colour="#e66101") +
+     geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.1, ], aes(Year, Documents)) + 
+     facet_wrap(~ Abbrev) + 
+     theme_bw() +
+     theme(strip.text.x = element_text(size = 8)) + 
+     theme(legend.position = "bottom", 
+     panel.grid.minor = element_blank(), 
+     axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
+     geom_text(data = ldata[1:40, ], aes(x =xpos, y = ypos, label = lab), size =3) +
+     ylim(c(0,225)) +
+     scale_x_continuous(breaks=seq(1989, 2015, 8))
+
+plotSmallMultiples.2 <- ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ],  aes(Year, N)) +
+     geom_line(colour="#e66101") +
+     geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ], aes(Year, Documents)) + 
+     facet_wrap(~ Abbrev) + 
+     theme_bw() +
+     theme(strip.text.x = element_text(size = 8)) +  
+     theme(legend.position = "bottom", 
+     panel.grid.minor = element_blank(), 
+     axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
+     geom_text(data = ldata[41:79, ], aes(x =xpos, y = ypos, label = lab), size =3) +
+     ylim(c(0,225)) +
+     scale_x_continuous(breaks=seq(1989, 2015, 8))
 
@@
 
+A total of XX article records from XX unique journal titles met the inclusionary
+criteria and were included in the historical database.
+
+Figure 1 uses a
+small multiples plot to summarize the number of article records for each year
+throughout the study period.  Small multiples, also referred to as trellis
+and lattice charts, are the best design solution for visually enforcing comparisons of
+change (Tufte, XXXX).
+In this context, we use two different data sources to show differences in publishing across the journals -- the orange line represents data from the SWHD, and the purple line represents data from Scopus.
+
+the small multiples to show differences in publishing across the journals,
+
+show differences in publication history for each journal.
+
+The number of article records for each year (by journal) is denoted by an orange line, along with the overall number of article records.
+For further contextual information, the number of article records available from Scopus is presented with a purple line.
+This plot reveals variability in publishing over time and across journals.  The for each journal and across journals.  
+First, the historical database indexed XX journals, whereas Scopus indexed only XX.
+For the number of journals indexed by Scopus, the number of article records tend to be higher than the number of records available in the historical database.
+The primary reason for this difference is that Scopus included editorials and book reviews in their summary data, whereas these were excluded from the SWHD.
+Other difference can be attributed to errors and gaps in indexing across both databases.
+As we relied upon aggregate data from Scopus, we were unable to quantify these differences.
+
+should be noted that the number of article records available from Scopus tends to be greater than the historical database because Scopus included editorials (AND REVIEWS), whereas these were excluded from the historical database.
+
+According to Tufte (Evisioning information), small multiples are the best design s
+
 Table 1 provides a summary of the journal titles and corresponding article records collected from the databases.
@@
 
+\newpage
+```{r fig.height=10, fig.width=7.5}
+plotSmallMultiples.1
+
+```
+
+\newpage
+```{r fig.height=10, fig.width=7.5}
+plotSmallMultiples.2
+
+```
 \newpage

### 2015-05-16 manuscript.Rmd
Plots in development.

@@
  sm.scopus.merged$Abbrev <- factor(sm.scopus.merged$Abbrev, levels = (title.order))
+ sm.scopus.merged <- group_by(sm.scopus.merged, Journal) %>%
+     mutate(Overall.Scopus = sum(Documents, na.rm=TRUE)) %>%
+     ungroup()
 # 
@@
  Overall.N <- distinct(sm.scopus.merged, Abbrev) 
- lab <- paste("N=", Overall.N$Overall.N, sep="")
- xpos = rep(2002, 79)
- ypos = rep(215, 79)
+ lab1 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.N), sep=""))
+ lab2 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.Scopus), sep=""))
+ lab <- paste(lab1, lab2, sep="\n")
+ xpos = rep(1999, 79)
+ ypos = rep(200, 79)
  ldata <- data.frame(xpos, ypos, lab, Overall.N$Abbrev) %>% 
@@
  titles.reduced.2 <- titles.reduced[41:length(titles.reduced)] 
+ cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
 
+ library(grid)
+ library(gridExtra)
 # Plotting function    
+# 
  plotSmallMultiples.1 <-  ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.1, ],  aes(Year, N)) +
      geom_line(colour="#e66101") +
-     geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.1, ], aes(Year, Documents)) + 
+     geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.1, ], aes(Year, Documents), colour = "#533c99", alpha = .80) + 
      facet_wrap(~ Abbrev) + 
@@
      axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
-     geom_text(data = ldata[1:40, ], aes(x =xpos, y = ypos, label = lab), size =3) +
+     geom_text(data = ldata[1:40, ], aes(x =xpos, y = ypos, label = lab), size =2.5) +
      ylim(c(0,225)) +
-     scale_x_continuous(breaks=seq(1989, 2015, 8))
+     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
+     annotate("segment", x = 1989, xend = 1992, y = 215, yend = 215, colour = "#e66101") + 
+     annotate("segment", x = 1989, xend = 1992, y = 190, yend = 190, colour = "#533c99")
 
-plotSmallMultiples.2 <- ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ],  aes(Year, N)) +
+plotSmallMultiples.2 <- ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ],  
+     aes(Year, N)) +
      geom_line(colour="#e66101") +
-     geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ], aes(Year, Documents)) + 
+     geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ], 
+     aes(Year, Documents), colour = "#533c99", alpha = .80) + 
      facet_wrap(~ Abbrev) + 
@@
      axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
-     geom_text(data = ldata[41:79, ], aes(x =xpos, y = ypos, label = lab), size =3) +
+     geom_text(data = ldata[41:79, ], aes(x =xpos, y = ypos, label = lab), size =2.5) +
      ylim(c(0,225)) +
-     scale_x_continuous(breaks=seq(1989, 2015, 8))
+     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
+     annotate("segment", x = 1989, xend = 1992, y = 215, yend = 215, colour = "#e66101") + 
+     annotate("segment", x = 1989, xend = 1992, y = 190, yend = 190, colour = "#533c99")
+
+x <- c(1:10)
+y <- c(1:10)
+
+df <- data.frame(x,y)
+pg <- ggplotGrob(plotSmallMultiples.1)
+
+pl <- gtable_filter(pg, 'panel', trim=F)$layout
+pg <- gtable_add_grob(pg, x.grob, t=max(pl$t), l=max(pl$l))
+
+grid.newpage()
+grid.draw(pg)
 

### 2015-05-18 manuscript.Rmd
Updated figures.

@@
 
-x <- c(1:10)
-y <- c(1:10)
-
-df <- data.frame(x,y)
-pg <- ggplotGrob(plotSmallMultiples.1)
-
-pl <- gtable_filter(pg, 'panel', trim=F)$layout
-pg <- gtable_add_grob(pg, x.grob, t=max(pl$t), l=max(pl$l))
-
-grid.newpage()
-grid.draw(pg)
-
+# x1.grob <- ggplotGrob(plotSmallMultiples.1)
+# x2.grob <- ggplotGrob(ggplot(cars, aes(speed, dist)) + geom_point())
+# 
+# library(gtable)
+# plot1 <- gtable_filter(x1.grob, 'panel', trim=F)$layout
+# pg <- gtable_add_grob(x1.grob, x2.grob, t = max(plot1$t), l = max(plot1$l))
+# grid.newpage()
+# grid.draw(pg)
 ```
 
-```{r uncitedSummary}
+```{r articleSummary}
 #=======================================
@@
 #=======================================
+library(gridExtra)
 
 articles.df <- left_join(n.so, n.yr) %>%
-    group_by(title, year) %>%
+    group_by(year) %>%
     summarize(N = n()) %>%
-    mutate(Overall.N = sum(N), year = as.numeric(year)) %>%
+    mutate(year = as.numeric(year), CumSum = cumsum(N)) %>%
     ungroup() %>%
-    arrange(desc(Overall.N), title) %>%
-    rename(Year = year, Journal= title)
+    arrange(desc(N), year) %>%
+    rename(Year = year)
 
-scopus.df <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/scopus.csv")
-articles.df <-full_join(sm.df, scopus.df, by = c("Journal", "Year"))
+plot.article.count <- ggplot(articles.df, aes(Year, N, group =1)) + 
+    geom_line(colour=cp[2], size = 1) +
+    theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8), 
+    title = element_text(size = 10), plot.title=element_text(size=10)) + 
+    xlab("Year") + 
+    ylab("") + 
+    ggtitle("Article Count") +
+     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
+        scale_y_continuous(breaks = c(seq(0, 2200, 250)), limits= c(500, 2100))
 
-articles.df<- articles.df %>% 
-    filter(Year <= 2013) %>%
-    mutate(propNotCited = X..Not.Cited/100) %>%
-    select(-X, -SJR, -SNIP, -Citations, -IPP, -X..Not.Cited, -Overall.N, -X..Review) %>%
-    rename(HD.N = N, scopus.N = Documents)
-
-#=======================================
-# Calculate number of uncited articles
-#=======================================
-
-#  First reduce the data file to 1996 to 2010. Data contained significant problems that brought the number of uncited values to almost 0.  Was not reliable.
-
-df.96.10 <- filter(articles.df, Year >= 1996, Year <= 2010)
-
-# If HD article count is missing, replace with Scopus count
-
-# Some counts have 0 values.  Set these to NA and then omit.
-df.96.10$HD.N <-ifelse(df.96.10$HD.N == 0, NA, df.96.10$HD.N) 
-df.96.10 <- df.96.10[!is.na(df.96.10$HD.N), ]
-
-# If uncited proportion is missing, compute average for that particular journal
-# Replace missing value with the mean value
-df.96.10 <- df.96.10 %>% group_by(Journal) %>%
-        mutate(meanPropUncited = mean(propNotCited, na.rm=TRUE)) %>% ungroup()
-
-df.96.10$propNotCited <- ifelse(is.na(df.96.10$propNotCited),
-     df.96.10$meanPropUncited, df.96.10$propNotCited)
-
-# If uncited proportion is missing because it was not in Scopus, replace the missing
-# value with the overall mean uncited proportion
-
-overallPropUncited <- mean(df.96.10$propNotCited, na.rm=TRUE)
-
-df.96.10$propNotCited <- ifelse(is.na(df.96.10$propNotCited), overallPropUncited, df.96.10$propNotCited)
-
-# Calculate number of not cited
-
-df.96.10 <- df.96.10 %>% mutate(countNotCited = HD.N * propNotCited)
-
-df.96.10.Summary <- df.96.10 %>% group_by(Year) %>%
-    summarize(Published = sum(HD.N), 
-              Uncited = sum(countNotCited))
-
-#============================================
-# Create a melted data frame for the plot
-#============================================
-
-# We need to include years before and after the scopus data.
-
-df.95.11 <- select(articles.df, Year, HD.N) %>% 
-    filter(Year <= 1995 |Year >=2011) %>%
-    rename(published = HD.N) %>%
-    group_by(Year) %>%
-    summarize(Published = sum(published, na.rm=TRUE)) %>%
-    ungroup() %>%
-    mutate(Uncited = NA)
-
-uncited.df <- rbind(df.96.10.Summary, df.95.11) %>%
-    arrange(Year)
-
-#============================================
-# Compute percentage variable and melt
-#============================================
-
-uncited.df$percentage <- uncited.df$Uncited/uncited.df$Published*100
-
-uncited.melted <- reshape2::melt(uncited.df[,c("Year", "Published", "Uncited")], 
-     id.vars = c("Year"))
-
-#=======================================
-# Create text annotations to plot 
-#=======================================
-
-percent.df <- uncited.df
-percent.df$percentage <- round(percent.df$percentage, digits=1) 
-percent.df$percentLabel<- paste(percent.df$percentage, "%", sep="")
-percent.df <- na.omit(percent.df)
-percent.df <- percent.df[c(seq(1, 15, 3), 15),]
-
-#=======================================
-# Create the plot 
-#=======================================
-
-cp <- c("#5e3c99", "#e66101")
-
-plotArticles <- ggplot(uncited.melted, aes(Year, value, colour = variable,)) + 
-    geom_line(alpha = .60) + 
-    geom_point(size = 4) +
-    scale_color_manual(values=cp, labels = c("Number of Articles Published",
-         "Estimated Number of Uncited Articles")) +
-    theme(legend.title=element_blank()) +
-    theme(legend.position = "bottom") +
-    ylab("N") +
-    geom_text(data = percent.df, aes(Year, Uncited -70, label = percentLabel), size =4, colour = "black") +
-    scale_y_continuous(breaks = seq(0, 2250, 250), limits = c(0, 2250))
-
-```
-
-```{r}
-# Read Scopus database
-scopus.df <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/scopus.csv")
-
-boxplot.scopus <- ggplot(subset(scopus.df, subset =Year <=2013 & Year >= 1999), aes(as.factor(Year), IPP)) +
-    geom_boxplot()
-
-```
-
-```{r plotJournalCount, eval=TRUE}
+plot.article.cumulative <- ggplot(articles.df, aes(Year, CumSum, group =1)) + 
+    geom_line(colour=cp[2], size = 1) +
+    theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8), 
+    title = element_text(size = 10), plot.title=element_text(size=10)) + 
+    xlab("Year") + 
+    ylab("") + 
+    ggtitle("Cumultative Article Count") +
+     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
+        scale_y_continuous(breaks = c(seq(0, 35000, 5000)), limits = c(0, 35000))
 
@@
 
-plot.journal.count <- ggplot(n.journals.year, aes(as.factor(record.y), 
+plot.journal.count <- ggplot(n.journals.year, aes(record.y, 
     y = Journal.count, group=1)) + 
-    geom_line(colour="black") +
+    geom_line(colour=cp[4], size = 1) +
     theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8), 
@@
     xlab("Year") + 
-    ylab("Journals") + 
-    ggtitle("B. Number of Journals by Year") +
-    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
-    scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 70)) 
+    ylab("N") + 
+    ggtitle("Journal Count") +
+    scale_y_continuous(breaks = c(seq(0, 100, 5)), limits = c(20, 70)) +
+     scale_x_discrete(breaks=seq(1989, 2015, 8))
+
 ```
@@
 
-plot.author.count <- ggplot(n_authors2, aes(x = year, group=1)) + 
-    geom_line(aes(y=Median, colour="Median"), size = .75, colour = "#fdb864", alpha = .70) + 
-    geom_line(aes(y=Average, colour = "Average"), size = .75,  colour = "#e66101" ) +
-    geom_point(aes(y=Average, size = Standard_Deviation), colour = "#e66101") +
+n_authors2.melted <- reshape2::melt(n_authors2, id.vars = c("year", "Standard_Deviation"))
+n_authors3.melted <- filter(n_authors2.melted, variable == "Average")
+
+plot.author.count <- ggplot(n_authors2.melted, aes(x = year, y = value, group=variable, colour = variable)) + 
+    geom_line() +
+    geom_point(data = n_authors3.melted, aes(size = Standard_Deviation), colour = "#e66101") + 
     theme(axis.text.x = element_text(angle = 45, hjust = 1), 
@@
     scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
-    scale_y_continuous(limits = c(0,2.5)) +
-    ylab("Value") +
+    scale_y_continuous(limits = c(.75,2.5)) +
+    ylab("Authors") +
     xlab("Year") +
-    ggtitle("Authors Per Article by Year") +
-    labs(size = "Standard deviation") 
+    ggtitle("Number of Authors") +
+    labs(size = "Standard deviation") +
+    labs(colour = "Value") + 
+    scale_colour_manual(values = c("#fdb864", "#e66101"))
+
 ```
@@
 
-journal.evidence.plot <- ggplot(na.omit(df1), aes(x = N, y= journal, group = journal, colour = studyType)) + 
+df1.summarized <- df1 %>% group_by(journal) %>% 
+    summarize(EBP.counts = sum(N)) %>% 
+    arrange(desc(EBP.counts)) %>%
+    slice(1:15)
+
+journal.evidence.plot <- ggplot(na.omit(df1[df1$journal %in% df1.summarized$journal,]), aes(x = N, y= journal, group = journal, colour = studyType)) + 
     geom_segment(aes(yend = journal), xend=0, colour="grey50") +
@@
 df2  <- within(df2, quartile <- as.integer(cut(Overall.N.Strength, quantile(Overall.N.Strength, probs=0:4/4, na.rm=TRUE), include.lowest=TRUE)))
+
+df2 <- df2 %>% arrange(desc(Prop)) %>% slice(1:15)
 
@@
 
-page.plot <- ggplot(pages.df, aes(years, Mean.Pages, size = Std.Pages, group = 1))+ 
-    geom_line(size=.75, colour =  "#5e3c99") +
-    geom_line(aes(years, Median.Pages, group = 1), size = .75, colour = "#b2abd2", alpha = .70) + 
-    geom_point(colour = "#5e3c99") +
+pages.df.melted <- reshape2::melt(pages.df, id.vars = c("years", "Std.Pages"))
+pages.df2.melted <- filter(pages.df.melted, variable == "Mean.Pages")
+
+page.plot <- ggplot(pages.df.melted, aes(x = years, y = value, group=variable, colour = variable)) + 
+    geom_line() +
+    geom_point(data = pages.df2.melted, aes(size = Std.Pages), colour = "#5e3c99") + 
     theme(axis.text.x = element_text(angle = 45, hjust = 1), 
@@
     scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
-    scale_y_continuous(limits = c(11,16)) +
-    ylab("Value") +
+    ylab("Pages") +
     xlab("Year") +
-    labs(size = "Standard deviation", colour = "Median")  +
-    ggtitle("Article Length by Year")
+    ggtitle("Article Length") +
+    labs(size = "Standard deviation") +
+    labs(colour = "Value") + 
+    scale_colour_manual(values = c("#b2abd2", "#5e3c99"))
 
@@
 # Results
-
-### Journal summary
-
-A total of XX article records from XX unique journal titles met the inclusionary
-criteria and were included in the historical database.
-
-Figure 1 uses a
-small multiples plot to summarize the number of article records for each year
-throughout the study period.  Small multiples, also referred to as trellis
-and lattice charts, are the best design solution for visually enforcing comparisons of
-change (Tufte, XXXX).
-In this context, we use two different data sources to show differences in publishing across the journals -- the orange line represents data from the SWHD, and the purple line represents data from Scopus.
-
-the small multiples to show differences in publishing across the journals,
-
-show differences in publication history for each journal.
-
-The number of article records for each year (by journal) is denoted by an orange line, along with the overall number of article records.
-For further contextual information, the number of article records available from Scopus is presented with a purple line.
-This plot reveals variability in publishing over time and across journals.  The for each journal and across journals.  
-First, the historical database indexed XX journals, whereas Scopus indexed only XX.
-For the number of journals indexed by Scopus, the number of article records tend to be higher than the number of records available in the historical database.
-The primary reason for this difference is that Scopus included editorials and book reviews in their summary data, whereas these were excluded from the SWHD.
-Other difference can be attributed to errors and gaps in indexing across both databases.
-As we relied upon aggregate data from Scopus, we were unable to quantify these differences.
-
-should be noted that the number of article records available from Scopus tends to be greater than the historical database because Scopus included editorials (AND REVIEWS), whereas these were excluded from the historical database.
-
-According to Tufte (Evisioning information), small multiples are the best design s
-
-Table 1 provides a summary of the journal titles and corresponding article records collected from the databases.
-This table includes the specific years each journal is represented in the current study, the number of corresponding article records, the journal's h-Index, and whether the journal was included on the list of social work disciplinary journals defined by Hodge and Lacasse (2011).
-Appendix A provides a summary of journals that were on the list by compiled by Hodge and Lacasse (2011) but not included in this study (N = `r length(hodge.swHistory.diff)`), in addition to the journals excluded from the study due to an article count $<=$ 20 (N = `r nrow(fewArticles)`).
-It is important to note that the years of inclusion noted for each journals does not correspond to its full historical record.
-Many journals have publications that both precede and proceed the 25-year timeframe of the current study.
-Moreover, many journals are missing articles records due to delays and errors in indexing, which is a known and longstanding problem in social work research (HoldenXXXX).
-These issues are given further attention in the discussion section of the article.
-
 ```{r}
@@
 ```
-Data from the National Science Foundation regarding the number of earned doctorates in social work and social welfare were added to further contextualize the publication trends.
-These data reveal both growth and decline in the number of earned doctorates over the period of time for which data were available.
-The number of earned doctorates exhibited a rise from 2003 to 2005, which corresponded to a rise in the number of article published during these years.
-Between 2008 and 2012, the number of doctoral degrees exhibited a decline, but the number of published articles continued to rise.
+
+### Journal summary
+
+Figure 1 uses a small multiples plot to summarize the number of article records
+for each year throughout the study period.  According to Tufte (xxxx), small multiples (also referred to as
+trellis and lattice charts) are the best design solution for visually enforcing
+comparisons of change.
+In the current useage, each journal is summarized with its own line plot using two different lines to represent the number of article records contained in the SWHD (orange line) and Scopus (purple line).
+The journals are sorted in descending order based on the overall number of article records in the SWHD.
+Journal titles are also abbreviated, and the full spellings are available in Appendix A.
+These line plots help show publication patterns for each journal.
+
+The differences in publication counts are explained by a couple different reasons.
+Scopus does not index journals prior to 1996, whereas the SWHD goes back to 1989.
+Although the timeframe of the SWHD is longer than Scopus, the actual number of article records in the SWHD for many journals is lower than what is available in Scopus.
+Scopus included editorials and book reviews in their article count, whereas these publications were specifically excluded from the SWHD.
+Because Scopus data were available only in aggregate form, it was not possible to extract these data to make more refined comparisons.
+In the construction of the SWHD, we also applied a series of cleaning procedures that further reduced the article count for many journals.
+For example, we excluded article records that did not contain author names, an abstract or article title.
+Again, because we were working only with aggregate data from Scopus, we were unable to apply the same cleaning procedures to the Scopus data.
+And, finally, differences can also be attributed to gaps and errors in indexing in Scopus and all the databases used to construct the SWHD.
+This is a known and longstanding problem with some social work journals (see Holden, Holden).
+
+\newpage
+```{r fig.height=10, fig.width=7.5}
+plotSmallMultiples.1
+
+```
+
+\newpage
+```{r fig.height=10, fig.width=7.5}
+plotSmallMultiples.2
+
+```
 
@@
 \newpage
-```{r fig.height=10, fig.width=7.5}
-plotSmallMultiples.1
-
-```
-
-\newpage
-```{r fig.height=10, fig.width=7.5}
-plotSmallMultiples.2
-
-```
-\newpage
 
@@
 ```{r}
-plot.journal.count
+grid.arrange(plot.journal.count, plot.article.count, ncol=2)
+
 ```
@@
 ```
+
+\newpage
 
@@
 \newpage
-```{r fig.height=9.5}
+```{r}
 journal.evidence.plot
@@
 \newpage
-```{r fig.height=9.5}
+```{r}
 EBP.plot

### 2015-05-19 manuscript.Rmd
Updating figures.

@@
 
-```{r objectMakerProQuest, warning=FALSE, message=FALSE, eval=FALSE, results='hide'}
+```{r objectMakerProQuest, warning=FALSE, message=FALSE, eval=FALSE, results='hide', cache=TRUE}
 # Clear workspace
@@
 
-```{r objectMakerEbscoHost,warning=FALSE, message=FALSE, eval=FALSE, results='hide'}
+```{r objectMakerEbscoHost,warning=FALSE, message=FALSE, eval=FALSE, results='hide', cache=TRUE}
 # Clear workspace
@@
 
-```{r cleaningFunctions, comment=NA, echo=FALSE, eval=TRUE}
+```{r cleaningFunctions, comment=NA, echo=FALSE, eval=TRUE, cache=TRUE}
 # Read data files
@@
 
-```{r tableArticleSummary, eval=TRUE}
+```{r tableArticleSummary, eval=TRUE, cache=TRUE}
 unique.titles <- filter(full.df, attributes == "journal") %>%
@@
 
-```{r plotSmallMultiples}
+```{r plotSmallMultiples, cache=TRUE}
 # Remove 2014 & 2015
@@
 
-```{r articleSummary}
+```{r plotJournalArticle, cache=FALSE}
 #=======================================
-# Create new data file 
+# Journals
 #=======================================
 library(gridExtra)
+
+n.journals.year <- filter(full.df, attributes == "journal") %>%
+    select(articleID, record)
+
+n.year <- filter(full.df, attributes == "pubYear") %>%
+    select(articleID, record)
+
+n.journals.year <- left_join(n.journals.year, n.year, by = "articleID", copy=TRUE) %>%
+    group_by(record.y) %>%
+    summarise(Journal.count = n_distinct(record.x)) %>%
+    mutate(record.y = as.numeric(record.y))
+
+plot.journal.count <- ggplot(n.journals.year, aes(record.y, 
+    y = Journal.count, group=1)) + 
+    theme_bw() + 
+    geom_line(colour=cp[4], size = 1) +
+    theme(axis.text.x = element_text(size=8), 
+    title = element_text(size = 10), plot.title=element_text(size=10)) + 
+    xlab("Year") + 
+    ylab("Number of Journals") + 
+    scale_y_continuous(breaks = c(seq(0, 100, 5)), limits = c(20, 70)) +
+    scale_x_continuous(breaks=seq(1989, 2015, 8)) +
+    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))
+
+#=======================================
+# Articles
+#=======================================
 
@@
 plot.article.count <- ggplot(articles.df, aes(Year, N, group =1)) + 
+    theme_bw() + 
     geom_line(colour=cp[2], size = 1) +
-    theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8), 
+    theme(axis.text.x = element_text(size=8), 
     title = element_text(size = 10), plot.title=element_text(size=10)) + 
     xlab("Year") + 
-    ylab("") + 
-    ggtitle("Article Count") +
+    ylab("Number of Articles") + 
     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
-        scale_y_continuous(breaks = c(seq(0, 2200, 250)), limits= c(500, 2100))
-
-plot.article.cumulative <- ggplot(articles.df, aes(Year, CumSum, group =1)) + 
-    geom_line(colour=cp[2], size = 1) +
-    theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8), 
-    title = element_text(size = 10), plot.title=element_text(size=10)) + 
-    xlab("Year") + 
-    ylab("") + 
-    ggtitle("Cumultative Article Count") +
-     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
-        scale_y_continuous(breaks = c(seq(0, 35000, 5000)), limits = c(0, 35000))
-
-n.journals.year <- filter(full.df, attributes == "journal") %>%
-    select(articleID, record)
-
-n.year <- filter(full.df, attributes == "pubYear") %>%
-    select(articleID, record)
-
-n.journals.year <- left_join(n.journals.year, n.year, by = "articleID", copy=TRUE) %>%
-    group_by(record.y) %>%
-    summarise(Journal.count = n_distinct(record.x))
-
-plot.journal.count <- ggplot(n.journals.year, aes(record.y, 
-    y = Journal.count, group=1)) + 
-    geom_line(colour=cp[4], size = 1) +
-    theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8), 
-    title = element_text(size = 10), plot.title=element_text(size=10)) + 
-    xlab("Year") + 
-    ylab("N") + 
-    ggtitle("Journal Count") +
-    scale_y_continuous(breaks = c(seq(0, 100, 5)), limits = c(20, 70)) +
-     scale_x_discrete(breaks=seq(1989, 2015, 8))
-
+    scale_y_continuous(breaks = c(seq(0, 2200, 250)), limits= c(500, 2100)) +
+    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))
 ```
 
-```{r plotAuthorCount, eval=TRUE}
+```{r plotAuthorCount, eval=TRUE, cache=FALSE}
 year.df <- full.df %>%
@@
 
-n_authors2$year <- as.factor(c(1989:2013))
+n_authors2$year <- c(1989:2013)
 
@@
 plot.author.count <- ggplot(n_authors2.melted, aes(x = year, y = value, group=variable, colour = variable)) + 
+    theme_bw() + 
     geom_line() +
     geom_point(data = n_authors3.melted, aes(size = Standard_Deviation), colour = "#e66101") + 
-    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
-    title = element_text(size = 10)) +  
-    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
+    #theme(axis.text.x = element_text(angle = 45, hjust = 1), 
+    #title = element_text(size = 10)) +  
+    scale_x_continuous(breaks=c(seq(1989, 2013, 4))) +
     scale_y_continuous(limits = c(.75,2.5)) +
-    ylab("Authors") +
+    ylab("Number of Authors") +
     xlab("Year") +
-    ggtitle("Number of Authors") +
     labs(size = "Standard deviation") +
-    labs(colour = "Value") + 
-    scale_colour_manual(values = c("#fdb864", "#e66101"))
+    labs(colour = "") + 
+    scale_colour_manual(values = c("#fdb864", "#e66101")) +
+   theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))
 
@@
 
-```{r abstracts}
+```{r pagePlot, eval=TRUE, cache=FALSE}
+pages.tmp <- full.df %>% filter(attributes == "pages")
+years.tmp <- full.df %>% filter(attributes == "pubYear")
+pages.df <- left_join(pages.tmp, years.tmp, by = "articleID") %>% 
+    select(record.y, record.x) %>%
+    rename(years = record.y, pages = record.x) %>%
+    mutate(pages = as.numeric(pages), years = as.numeric(years)) %>%
+    group_by(years) %>%
+    summarise(
+        Median = median(pages, na.rm=TRUE), 
+        Mean.Pages = mean(pages, na.rm=TRUE),
+        Std.Pages = sd(pages, na.rm=TRUE))
+cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
+
+n_authors2$year <- c(1989:2013)
+
+pages.df.melted <- reshape2::melt(pages.df, id.vars = c("years", "Std.Pages"))
+pages.df2.melted <- filter(pages.df.melted, variable == "Mean.Pages")
+
+page.plot <- ggplot(pages.df.melted, aes(x = years, y = value, group=variable, colour = variable)) + 
+    geom_line() +
+    geom_point(data = pages.df2.melted, aes(size = Std.Pages), colour = "#5e3c99") + 
+    theme_bw() + 
+    theme(title = element_text(size = 10)) +  
+    scale_x_continuous(breaks=c(seq(1989, 2013, 4))) +
+    ylab("Number of Pages") +
+    xlab("Year") +
+    labs(size = "Standard deviation") +
+    labs(colour = "") + 
+    scale_colour_manual(values = c("#b2abd2", "#5e3c99"))  +
+    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))
+
+```
+
+```{r plotStacked, cache=FALSE}
 abstract.df <- filter(full.df, attributes == "abstract")
@@
 
-year.labs <- as.character(seq(1989,2013, 2))
+year.labs <- as.character(seq(1989,2013, 4))
 
-stacked.plot <- ggplot(as.data.frame(xtabs(N~year+studyType, evidence.summary)), 
+stacked.df <- as.data.frame(xtabs(N~year+studyType, evidence.summary))
+stacked.df$year
+
+stacked.plot <- ggplot(stacked.df, 
     aes(x = as.numeric(year), y = Freq, fill=studyType)) + 
     geom_area(alpha=.60, colour = "black", size = .2) +
+    theme_bw() +
     scale_fill_manual(values=cp, 
         breaks = rev(levels(evidence.summary$studyType)))+
-  ylim(c(0, 60)) + 
-    scale_x_continuous(breaks = seq(0,24, 2), labels = year.labs) + 
-    theme(axis.text.x = element_text(angle = 45, hjust=1), 
-          panel.grid.minor=element_blank(),
-         legend.position=c(.25,.80),
+    scale_x_continuous(breaks = seq(0,24, 4), labels = year.labs) + 
+    theme(  legend.position=c(.25,.80),
 #         legend.background = element_blank(), 
          legend.key = element_blank()   ) + 
-    ylab("N") + 
+    ylab("Number of Articles") + 
     xlab("Year") + 
-    labs(fill = "Study type") +
-    scale_y_continuous(breaks = seq(0,90, 10))
+    labs(fill = "") +
+    scale_y_continuous(breaks = seq(0,90, 10)) +
+    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))
 
 df <- evidence.summary2
+```
 
+```{r plotProportions, cache=FALSE}
 evidence.plot <- ggplot(na.omit(df), aes(year, studyProp, colour = studyType, 
     group = studyType), na.rm=TRUE) + 
-    geom_smooth(aes(fill=studyType), alpha = .60, colour = "dimgray") + facet_wrap(~studyType) + 
+    geom_smooth(aes(fill=studyType), alpha = .40, colour = "dimgray") + facet_wrap(~studyType) + 
+    theme_bw() +
     scale_fill_manual(values = cp) +   
@@
      theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-    scale_y_continuous(breaks = seq(0, .015, .005))
+    scale_y_continuous(breaks = seq(0, .03, .005)) 
+```
 
-######1989########
+```{r plotClevelandAbsolute}
 
@@
 
-#df1$studyType <- factor(df1$studyType)
-j.order <- unique(df1$journal[order(df1$N.sort, decreasing = FALSE)]) 
-df1$journal <- factor(df1$journal, levels = j.order)
-
 df1.summarized <- df1 %>% group_by(journal) %>% 
@@
 
-journal.evidence.plot <- ggplot(na.omit(df1[df1$journal %in% df1.summarized$journal,]), aes(x = N, y= journal, group = journal, colour = studyType)) + 
-    geom_segment(aes(yend = journal), xend=0, colour="grey50") +
-    geom_point(size = 2.5) + 
+df1.reduced <- na.omit(df1[df1$journal %in% df1.summarized$journal, ])
+df1.reduced <- ungroup(df1.reduced)
+
+df1.reduced <- df1.reduced %>% mutate(journal = paste(journal, N.sort, sep = "  "))
+
+#df1$studyType <- factor(df1$studyType)
+j.order <- unique(df1.reduced$journal[order(df1.reduced$N.sort, decreasing = FALSE)]) 
+df1.reduced$journal <- factor(df1.reduced$journal, levels = j.order)
+
+Text1 <- textGrob("Overall N")
+library(gridExtra)
+
+journal.evidence.plot <- ggplot(df1.reduced, 
+    aes(x = N, y= journal, group = journal, colour = studyType, shape= studyType)) + 
+    geom_segment(aes(yend = journal), xend=0, colour="grey90") +
+    geom_point(size = 2) + 
     scale_color_manual(values = cp) + 
     theme_bw() +
-    facet_grid(.~studyType) + 
-    theme(panel.grid.major.y = element_blank(), legend.position = "none") + 
+    #facet_grid(.~studyType) + 
+    theme(panel.grid.major.y = element_blank(), legend.position = c(.75, .5), 
+    legend.title = element_blank(), legend.text = element_text(size = 8)) + 
     xlim(0, 600) + 
-    ylab("Journal") +  
-    theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-    scale_x_continuous(breaks = seq(0, 60, 10))
+    ylab(NULL) +  
+    theme(axis.text.x = element_text(hjust = 1, size = 8), axis.ticks = element_blank()) + 
+    theme(axis.text.y = element_text(size = 8) ) + 
+    scale_x_continuous(breaks = seq(0, 60, 10)) +
+    scale_shape_manual(values=c(24, 23, 21, 25))
 
+journal.evidence.plot <- arrangeGrob(journal.evidence.plot, main = textGrob("Overall N", gp=gpar(cex=.7, font=2), vjust = 2, hjust = 1.25))
+
+```
+
+```{r plotClevelandRelative}
 evidence.journals <- full_join(evidence.summary3, evidence.summaryOverall, by = "journal") %>%
@@
     labs(size = "Total number of \nEBP articles published") 
-
-```
-
-```{r pagePlot, eval=TRUE}
-pages.tmp <- full.df %>% filter(attributes == "pages")
-years.tmp <- full.df %>% filter(attributes == "pubYear")
-pages.df <- left_join(pages.tmp, years.tmp, by = "articleID") %>% 
-    select(record.y, record.x) %>%
-    rename(years = record.y, pages = record.x) %>%
-    mutate(pages = as.numeric(pages)) %>%
-    group_by(years) %>%
-    summarise(
-        Median.Pages = median(pages, na.rm=TRUE), 
-        Mean.Pages = mean(pages, na.rm=TRUE),
-        Std.Pages = sd(pages, na.rm=TRUE))
-cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
-
-pages.df.melted <- reshape2::melt(pages.df, id.vars = c("years", "Std.Pages"))
-pages.df2.melted <- filter(pages.df.melted, variable == "Mean.Pages")
-
-page.plot <- ggplot(pages.df.melted, aes(x = years, y = value, group=variable, colour = variable)) + 
-    geom_line() +
-    geom_point(data = pages.df2.melted, aes(size = Std.Pages), colour = "#5e3c99") + 
-    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
-    title = element_text(size = 10)) +  
-    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
-    ylab("Pages") +
-    xlab("Year") +
-    ggtitle("Article Length") +
-    labs(size = "Standard deviation") +
-    labs(colour = "Value") + 
-    scale_colour_manual(values = c("#b2abd2", "#5e3c99"))
-
 ```

### 2015-05-20 manuscript.Rmd
Updated scopus files.

@@
 
-```{r plotSmallMultiples, cache=TRUE}
+```{r plotSmallMultiples, cache=FALSE}
 # Remove 2014 & 2015
@@
 scopus.df <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/scopus.csv")
+scopus.df2 <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/scopus_OldHarvest.csv")
+
+scopus.df$Year <- as.numeric(scopus.df$Year)
+scopus.df <- filter(scopus.df, Year <= 2013)
 
@@
      rename(Abbrev = Overall.N.Abbrev)
+
+ ldata <- na.omit(ldata)
 

### 2015-05-22 manuscript.Rmd
Switching to Vim editing.

@@
 ```{r pagePlot, eval=TRUE, cache=FALSE}
+cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
 pages.tmp <- full.df %>% filter(attributes == "pages")
@@
         Median = median(pages, na.rm=TRUE), 
-        Mean.Pages = mean(pages, na.rm=TRUE),
+        Average = mean(pages, na.rm=TRUE),
         Std.Pages = sd(pages, na.rm=TRUE))
-cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
 
-n_authors2$year <- c(1989:2013)
+pages.df$years <- c(1989:2013)
 
 pages.df.melted <- reshape2::melt(pages.df, id.vars = c("years", "Std.Pages"))
-pages.df2.melted <- filter(pages.df.melted, variable == "Mean.Pages")
+
+pages.df2.melted <- filter(pages.df.melted, variable == "Average")
 
@@
 stacked.df <- as.data.frame(xtabs(N~year+studyType, evidence.summary))
-stacked.df$year
 
@@
 
-df <- evidence.summary2
 ```
@@
 ```{r plotProportions, cache=FALSE}
+df <- evidence.summary2
+
 evidence.plot <- ggplot(na.omit(df), aes(year, studyProp, colour = studyType, 
@@
 ```{r plotClevelandAbsolute}
-
 evidence.summary3 <- select(evidence.df, -abstract) %>% 
@@
 ```{r plotClevelandRelative}
+
+target.journals <- df1.reduced 
+target.journals$journal <- gsub("\\s+\\d+", "", target.journals$journal)
+EBP.df <- left_join(target.journals, evidence.journals, by = c("journal", "studyType")) %>%
+    group_by(journal) %>%
+    slice(1) %>%
+    ungroup %>%
+    mutate(Proportion = N.sort/Overall.N) %>%
+    rename(Absolute = N.sort)
+
+EBP.df  <- within(EBP.df, quartile <- as.integer(cut(Overall.N, quantile(Overall.N, probs=0:4/4, na.rm=TRUE), include.lowest=TRUE)))
+
+ggplot(EBP.df, aes(Proportion, journal, size = Overall.N, colour=as.factor(quartile))) + 
+    theme_bw() + 
+    geom_point()
+
+View(df1.reduced)
+
 evidence.journals <- full_join(evidence.summary3, evidence.summaryOverall, by = "journal") %>%
@@
 
-The length of the articles showed some change over time, going from approximately `r round(pages.df$Mean.Pages[pages.df$years == "1989"])` pages in 1989.
-The length of the articles increased to about 15 pages and has remain at approximately this length since the early 2000's.
-The standard deviation has remained fairly stable over the time period, ranging from `r options(digits=2); min(pages.df$Std.Pages)` to `r options(digits=2); max(pages.df$Std.Pages)`.
-
 \newpage

### 2015-05-25 manuscript.Rmd
Major writing update. No code work.

@@
----
+--
 title: 'Examining a Quarter Century of Publishing Trends in Social Work Research:
@@
 
+Why is this study important:
+
+1.  Substantive contributions 
+Understand publication trends from a macro perspective.  This can:
+
+From an economic standpoint, the field of social work observed growth
+throughout the economic crisis and is expected to maintain growth.  The number
+of MSW programs also continues to grow.  While growth is observed in a variety
+of areas, it is important to consider the extent to which growth has occurred
+regarding overall scholarship.
+
+From a methodological standpoint, this study makes a few unique and important
+contributions to the social work research.  Foremost, the study was designed
+and executed in a manner that meets the full standards of reproducible
+research.  The CTSPEDIA, an advocate of fully reproducible research, defines
+this type of research as, ``the practice of distributing, along with a research
+publication, all data, software source code, and tools required to reproduce
+the results discussed in the publication.  As such the RR [reproducible
+research] package not only describes the research and its results, but becomes
+a complete laboratory in which the research can be reproduced and extended."
+(NOTE ABOUT ORGMODE)
+
+Methods
+
+Include section on reproducible research.
+
+Discussion
+
+## Growth of Social Work Research
+
+From the years 1989 to 2013, the field of social work research produced nearly
+35,000 journal articles. This doesn't include books or book chapters,
+editorials, book reviews, and other types scientific communications.  The
+growth increased steadily from XX to XX, and appears to be leveling off.
+Through this period of time, we observed XX unique titles appear while a number
+of other journals were lost.
+
+The current study helps clarify the extent to which _team science_ is emerging
+in social work research.  This is an important issue to consider, as it has
+implications for training researchers, reviewing and understnanding tenure and
+promotion cases, and research infrastructure to facilitate collaborations
+(http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3321548/). According to Thomson
+Reuters, the average number of authors on papers included in the Science
+Citation Index increased by about 50% between 1990 and 2010
+(http://www.hopkinsmedicine.org/institute_basic_biomedical_sciences/news_events/articles_and_stories/employment/2013_01_middle_authors.html)
+In our research, a t least one-half of all published studies were authored by a
+single individual until 2009.  The standard deviation continues to increase,
+providing further evidence of continued team science growth in social work.
+How authorship is assessed is a very important consideration for the field,
+particularly with respect to tenure reviews.  It is not clear how reviewers of
+tenure cases are viewing team science contributions and _middle authors_.
+However, this is something that will have to be considered for the field. In
+the field of physics, the weighted average seniourity and average seniority
+measures both had a negative relationship with the impact, based on the number
+of citations the publication received, as well as a negative relationship
+between the number of authors and the number of citations.  http://myweb.fsu.edu/bstvilia/papers/AuthorTeamDiversityImpact.pdf
+(***NOTE TO BRYAN -- AS A QUICK STUDY, YOU AND I SHOULD BUST OUT A STUDY
+INVOLVING THIS.  WE CAN DO IT FOR JUST THE TOP JOURNALS IN SOCIAL WORK THAT ARE
+IN WOS.)
+
+http://dmm.biologists.org/content/7/3/311.full
+
+https://ccrod.cancer.gov/confluence/download/attachments/47284665/teamscience_fieldguide.pdf
+
+One thing to consider is the extent to which social work research is being
+served by other journal outlets.  For example, social work researchers with
+primary research interests in areas of health, mental health, and substance use
+may publish in speciality journals outside of social work for a variety of
+reasons.  Thus, the amount that social work has grown should be cautious,
+keeping in mind this particular metric refers only to social work journals.
+The field may have grown more rapidly in other areas that are not reflected in
+the current research.  The functions that were constructed to _wrangle_ the
+abstracts are functional for records extracted from PubMed.  Since this data
+source contains author affiliations, it would be feasible to extract this
+information using a set of regular expressions.
+
+According to the journal Nature, from the lat 1600s until about 1920, the rule
+was one author per paper.  The rules was ``breached in the 1920s, diminished in
+the 1950s, and largely abandoned by the 1980s'' (p.
+http://www.nature.com/nature/history/full/nature06243.html).  Social work
+research had a much different trajectory.  In social work research, the rule
+wasn't breached until 2009.
+
+This has implications for tenure, and it is unclear how _team science_ is
+actually being considered in context of these reviews.  The field is arguably
+in a time of transition, form si
+
+Defining a _disciplinary_ social work journal was a complicated task.  Social
+work is inherently inter-disciplinary.  We based our definition of a social
+work journal using the list of Hodge and Lacasse (2011), who created a
+comprehensive list of journal titles.  This list was based on earlier attempts
+to identify all the disciplinary social work journals.  We supplemented our
+list by doing supplemental searches in all data sources for journals that used
+any of the following terms.
+
+The length of the articles was examined, as it has implications for device
+formatting.  Clearly, the field of social work has a current average of 15
+typeset pages.  This consistency allows for targeted customization for mobile
+devices.  An article can be optimized and fairly standardized, which has
+important benefits for information retrieval and comprehension.
+
+This article raised many opportunities that became obvious in this study.  In
+the current study, we worked in earnest to present as much of the analyses
+visually.  At the time of writing this article, the majority of social work
+journals do not have full color articles.  Indeed, this is a residual policy
+from when journals were exclusively in black-and-white and before electronic
+archiving.  Now, the majority of research is disseminated electronically, and
+even the most primitive computers connected to the Internet have color
+monitors.
+
+Data quality -- is there anything to talk about on this topic???
+
+Team science -- is it good for social work research?
+
+## Reproducible research
+
+Reproducible research is essential to ensuring the integrity of the scientific
+record.  Making research reproducible is a complicated process that does carry
+risks.  More specifically, it does involve taking extra time to prepare
+documentation, organize code, and prepare files to be made publicly available.
+This problem has already been given careful attention in other fields, which
+can be considered reasonable solutions for solution work research.  For
+example, this study utilized Rmarkdown as the tool for producing reproducible
+research.  Rmarkdown is ... [provide *short* description here -- tell reader
+minimum she/he needs to know].
+
+Another practical consideration of reproducible research is curating the data,
+and making it available.  The availability can be challenging.  For example, 
+many social work studies involve sensitive data that ultimately requires very
+strict limitations on how and where the data are stored, along with
+restrictions on who can access the data.  [Describe the PS journal that helps
+address this issue ...]  This study involves proprietary data from EbscoHost
+and ProQuest, which prevents us from making all the data available.  However,
+we provide a minimum random extract of the data to ensure verification of our
+computer code.  Additionally, we have made all aspects of our computer code
+available that will allow researchers with access to EbscoHost and ProQuest to
+replicate our findings, as well as use the code to build upon this research.
+
+We believe that social work journals should consider implementing policies that
+encourage reproducible research.  Making this best practice in publishing
+represents a straightforward way to improve the quality of social work
+research.  Along with a policy of reproducible research, the issue of how the
+journal responds to errors will also be necessary.  We certainly do not
+advocate that authors are expected to retract articles or face public shame in
+the context of random human error.  Some studies may involve generating
+thousands of lines of computer code -- and, a simple bug in the code can
+produce erroneous results.  Researchers who adhere to the principles of
+reproducible research are ultimately working in earnest to ensure they are
+producing the highest quality research possible.  Errors that are identified in
+the process represent an opportunity to further advance knowledge, which
+sometimes means correcting knowledge.  These situations simply reveal that the
+scientific method is actually working the way it is supposed to.  At present,
+we have to assume that all the social work research published to date is
+without error.  In absence of reproducible research, we can not fully assess
+the quality of research or replicate a study.
+
+Discussion point:
+
+Another complication is the possible consequences that a researcher might experience
+when an error is discovered.  This is an important issue that the field needs
+to address.
+
+very research report is subject to some form of human
+error.  It is important to consider some of the different types of error and
+how the field should respond.
+
+(Conduct and analysis on reproducible research" and "replication" or
+"replicate")
+
+(original citation from orgmode.org:
+http://orgmode.org/worg/org-contrib/babel/intro.html)
+
+ conforms to all
+aspects of what is regarded as reproducible research by making available all
+the code produced in order to conduct the study.
+
+.  Methodological contributions
+
 # Methods
@@
 
-Our list of social work journals was guided by the work of Hodge and Lacasse (2011).
-More specifically, Hodge and Lacasse (2011) identified 84 disciplinary social work journals based on a variety of sources, including _An Author’s Guide to Social Work Journals_ (NASW Press, 1997), Thyer’s (2005) more recent listing of social work periodicals, and Genamics JournalSeek (http://journalseek.net/).
-Hodge and Lacasse (2011) examined the mission and aims of each journal, and eliminated journals that were specific to another field or had an had an inter-disciplinary focus.
-For the current study, our primary search query included all journal titles in this list.
-
-To help ensure comprehensive coverage of all possible core social work journals, we created a supplemental search query that extracted journal titles with any of the following terms:
+Our list of social work journals was guided by the work of Hodge and Lacasse
+(2011).  More specifically, Hodge and Lacasse (2011) identified 84 disciplinary
+social work journals based on a variety of sources, including _An Author’s
+Guide to Social Work Journals_ (NASW Press, 1997), Thyer’s (2005) more recent
+listing of social work periodicals, and Genamics JournalSeek
+(http://journalseek.net/). Hodge and Lacasse (2011) examined the mission and
+aims of each journal, and eliminated journals that were specific to another
+field or had an had an inter-disciplinary focus.  For the current study, our
+primary search query included all journal titles in this list.
+
+To help ensure comprehensive coverage of all possible core social work
+journals, we created a supplemental search query that extracted journal titles
+with any of the following terms:
 
@@
 
-Using this search queries, we extract journal article recrods from three major databases on the EbscoHost platform:  PsycINFO, Social Service Abstracts, and Social Work Abstracts.
-Because of known gaps in indexing in databases (Holden, Barker, Kuppens, Rosenberg & LeBreton, 2014; Holden, Barker, Covert-Vail, Rosenberg, & Cohen, 2009), we also searched ProQuest, which linked to an additional 46 minor databases, including (but not limited to): ERIC, Sociological Abstracts and Worldwide Political Science Abstracts.
-In every search, we used a filter in attempt to extract only article records that were classified as _journal articles_, thereby excluding other forms of scholarly communication that was not relevant to the current study (e.g., book reviews, editorials, obituaries, etc.).
-We limited the timeframe to a 25 year period, from 1989 to 2013 (inclusive).
-Articles published in years 2014 and 2015 were excluded because of delays in indexing.
-Search results were exported in batches of article records based on the restrictions of the platform.
-Article records were text files in a _generic bibliographic format_.
-The article records contained various meta-data based on the database from which the article record was extracted.
-Meta-data include (but are not limited to):  article title, journal title, publication year, author name(s), author affiliation(s), abstract, keywords, methodological classification, funding source, location of study, subject groups, digital object identifier (DOI), number of references, number of pages, etc.
-These files were post-processed into a structured database using a set of scripts written in the R statistical programming language.
-The initial search resulted in `r pretty(nrow(article.count.initial))` article records from `r journal.count.initial`.
-
-The search queries were purposefully specified to be overly inclusive to ensure full coverage of all possible social work journals contained in the major and minor databases.
-Additionally, a visual inspection of the article records revealed problems in the original indexing of articles that requires subsequent data cleaning.
-Thus, our data cleaning procedures focused separately on journal titles and article records.
+Using this search queries, we extract journal article recrods from three major
+databases on the EbscoHost platform:  PsycINFO, Social Service Abstracts, and
+Social Work Abstracts.  Because of known gaps in indexing in databases (Holden,
+Barker, Kuppens, Rosenberg & LeBreton, 2014; Holden, Barker, Covert-Vail,
+Rosenberg, & Cohen, 2009), we also searched ProQuest, which linked to an
+additional 46 minor databases, including (but not limited to): ERIC,
+Sociological Abstracts and Worldwide Political Science Abstracts.  In every
+search, we used a filter in attempt to extract only article records that were
+classified as _journal articles_, thereby excluding other forms of scholarly
+communication that was not relevant to the current study (e.g., book reviews,
+editorials, obituaries, etc.).  We limited the timeframe to a 25 year period,
+from 1989 to 2013 (inclusive).  Articles published in years 2014 and 2015 were
+excluded because of delays in indexing.  Search results were exported in
+batches of article records based on the restrictions of the platform.  Article
+records were text files in a _generic bibliographic format_.  The article
+records contained various meta-data based on the database from which the
+article record was extracted.   Meta-data include (but are not limited to):
+article title, journal title, publication year, author name(s), author
+affiliation(s), abstract, keywords, methodological classification, funding
+source, location of study, subject groups, digital object identifier (DOI),
+number of references, number of pages, etc.  These files were post-processed
+into a structured database using a set of scripts written in the R statistical
+programming language.  The initial search resulted in `r
+pretty(nrow(article.count.initial))` article records from `r
+journal.count.initial`.
+
+The search queries were purposefully specified to be overly inclusive to ensure
+full coverage of all possible social work journals contained in the major and
+minor databases.  Additionally, a visual inspection of the article records
+revealed problems in the original indexing of articles that requires subsequent
+data cleaning.  Thus, our data cleaning procedures focused separately on
+journal titles and article records.
 
@@
 
-The first step of data cleaning involved fixing journal title names due to discrepant errors in indexing.
-For example, _Journal of Gay and Lesbian Social Services_ was indexed as a journal separate from _Journal of Gay & Lesbian Social Services_ (use of "and" vs.
-"&").
-Other examples involved journals indexed with and without subtitles, or journals with and without the word "The" at the beginning of the title.
-Additionally, some journals changed titles over their history.
-For example, _Journal of Technnology in Human Services_ is formerly known as _Computers in Human Services_.
-In these situations, the former titles were merged with the current titles.
-
-Many journals from allied health disciplines used one of the supplemental search terms in special editions, which were also included in the journal title.
-Thus, many non-social work journals were captured in the extraction process.
-To resolve this issue, we created a list of all journal titles that were not part of the core list defined by Hodge and Lacasse (2011).
-Study authors reviewed these journal titles and discussed whether each candidate title should be retained or excluded.
-When disagreements occurred, the study authors reviewed the mission and aims of the journals, names of editorial board members, and focus of the articles.
-A consensus was reached on all journal titles to be excluded and retained.
-After these procedures, the number of article records and journal titles was reduced to `r pretty(nrow(article.count.journalsCleaned))` and `r journal.count.journalsCleaned`.
+The first step of data cleaning involved fixing journal title names due to
+discrepant errors in indexing. For example, _Journal of Gay and Lesbian Social
+Services_ was indexed as a journal separate from _Journal of Gay & Lesbian
+Social Services_ (use of "and" vs. "&").  Other examples involved journals
+indexed with and without subtitles, or journals with and without the word "The"
+at the beginning of the title.  Additionally, some journals changed titles over
+their history.  For example, _Journal of Technnology in Human Services_ is
+formerly known as _Computers in Human Services_.  In these situations, the
+former titles were merged with the current titles.
+
+Many journals from allied health disciplines used one of the supplemental
+search terms in special editions, which were also included in the journal
+title.  Thus, many non-social work journals were captured in the extraction
+process.  To resolve this issue, we created a list of all journal titles that
+were not part of the core list defined by Hodge and Lacasse (2011).  Study
+authors reviewed these journal titles and discussed whether each candidate
+title should be retained or excluded.  When disagreements occurred, the study
+authors reviewed the mission and aims of the journals, names of editorial board
+members, and focus of the articles.  A consensus was reached on all journal
+titles to be excluded and retained.   After these procedures, the number of
+article records and journal titles was reduced to `r
+pretty(nrow(article.count.journalsCleaned))` and `r
+journal.count.journalsCleaned`.
 
@@
 
-Our search procedures involved the use of three major databased and 46 minor databases, which resulted in some duplication of article records.
-Thus, a matching algorithm was constructed to identify and remove all duplicate article records.
-As previously noted, the filtering of only journal articles was not successful due to errors in the original indexing.
-Thus, other scholarly communications were captured in the extractio process.
-These other scholarly communications were readily identified due to specific patterns in the titles, such as the terms "Book Review," "From the Editor," and "Obituary."  Given the number of article records in the database, it was not feasbile to manually extract these recrods.
-Instead, we created a separate database with representative examples of article records that we wanted to extract.
-We also added representative examples of article records to be retained.
-We then wrote a series of _regular expressions_ to extract the problematic article records.
-Regular expressions are a sequence of characters that form search patterns, allowing extraction of records that match the specified pattern.
-In other words, it is a more sophisticated implementation of the search function common to all major word processors.
-We tested our regular expressions on the test database, achieving > 95% accuracy with regard to retaining and extracting article records.
-These regular expressions were then applied to the full database.
-We then excluded article records if they were missing essential meta-data, including author name(s), journal title, article title, and publication field.
-As an additional requirement, we required all articles to be $\geq 3$ pages in length.
-Finally, we eliminated all social work journals with total article counts of < 10 for the entire 25 year window (_Issues in Social Work Education_, _Maatskaplike Werk/Social Work_, _Pediatric Social Work_, and _Critical Social Work_).
-These cleaning procedures resulted in a final database of `r pretty(articles.final)` articles and `r journals.final` journals.
+Our search procedures involved the use of three major databased and 46 minor
+databases, which resulted in some duplication of article records.  Thus, a
+matching algorithm was constructed to identify and remove all duplicate article
+records. As previously noted, the filtering of only journal articles was not
+successful due to errors in the original indexing.  Thus, other scholarly
+communications were captured in the extractio process.  These other scholarly
+communications were readily identified due to specific patterns in the titles,
+such as the terms "Book Review," "From the Editor," and "Obituary."  Given the
+number of article records in the database, it was not feasbile to manually
+extract these recrods.  Instead, we created a separate database with
+representative examples of article records that we wanted to extract.  We also
+added representative examples of article records to be retained.  We then wrote
+a series of _regular expressions_ to extract the problematic article records.
+Regular expressions are a sequence of characters that form search patterns,
+allowing extraction of records that match the specified pattern.  In other
+words, it is a more sophisticated implementation of the search function common
+to all major word processors.  We tested our regular expressions on the test
+database, achieving > 95% accuracy with regard to retaining and extracting
+article records.  These regular expressions were then applied to the full
+database.  We then excluded article records if they were missing essential
+meta-data, including author name(s), journal title, article title, and
+publication field.  As an additional requirement, we required all articles to
+be $\geq 3$ pages in length.   Finally, we eliminated all social work journals
+with total article counts of < 10 for the entire 25 year window (_Issues in
+Social Work Education_, _Maatskaplike Werk/Social Work_, _Pediatric Social
+Work_, and _Critical Social Work_).  These cleaning procedures resulted in a
+final database of `r pretty(articles.final)` articles and `r journals.final`
+journals.
 
@@
 
-We performed a variety of checks on the final database.
-Because the size of the database, it was not feasible to manually inspect all records.
-Thus, we randomly sampled article records from the database and cross-checked the data we procured with the information listed with the journal's homepage.
-We also inspected a scatter plot of the number of article records for each journal by the number of years the journal appeared within the 25 window timeframe.
-Journals that exhibited significant deviation from the regression line were inspected to ensure that our cleaning procedures did not systematically exclude article records or retain other scholarly communications.
-All observed discrepancies were verified as differences in journals actual publication output.
-Finally, we also made checks of number of journal article records for various journals indexed in the _Web of Science_.
-Although the counts were close -- i.e., within 10% -- similar indexing problems observed from our record extraction were also observed in the _Web of Science_ database, such as misclassification of book reviews as journal articles.
-Thus, we are unable to quantify the actual amount of error in our database is due to problems in indexing.
-At the same time, we are relying on the same source of data that social work researchers use to inform their work.
-Too much cleaning and post-processing of the search results can give rise to validity issues because social work researchers are using an information source that contain the errors we have attempted to eliminate.
-The issue of reliability and validity are given further attention in the discussion section of this study.
+We performed a variety of checks on the final database.  Because the size of
+the database, it was not feasible to manually inspect all records.  Thus, we
+randomly sampled article records from the database and cross-checked the data
+we procured with the information listed with the journal's homepage.  We also
+inspected a scatter plot of the number of article records for each journal by
+the number of years the journal appeared within the 25 window timeframe.
+Journals that exhibited significant deviation from the regression line were
+inspected to ensure that our cleaning procedures did not systematically exclude
+article records or retain other scholarly communications.  All observed
+discrepancies were verified as differences in journals actual publication
+output.  Finally, we also made checks of number of journal article records for
+various journals indexed in the _Web of Science_.  Although the counts were
+close -- i.e., within 10% -- similar indexing problems observed from our record
+extraction were also observed in the _Web of Science_ database, such as
+misclassification of book reviews as journal articles.  Thus, we are unable to
+quantify the actual amount of error in our database is due to problems in
+indexing.  At the same time, we are relying on the same source of data that
+social work researchers use to inform their work.  Too much cleaning and
+post-processing of the search results can give rise to validity issues because
+social work researchers are using an information source that contain the errors
+we have attempted to eliminate.  The issue of reliability and validity are
+given further attention in the discussion section of this study.
 
@@
 
-### Journal summary
-
-Figure 1 uses a small multiples plot to summarize the number of article records
-for each year throughout the study period.  According to Tufte (xxxx), small multiples (also referred to as
-trellis and lattice charts) are the best design solution for visually enforcing
-comparisons of change.
-In the current useage, each journal is summarized with its own line plot using two different lines to represent the number of article records contained in the SWHD (orange line) and Scopus (purple line).
-The journals are sorted in descending order based on the overall number of article records in the SWHD.
-Journal titles are also abbreviated, and the full spellings are available in Appendix A.
-These line plots help show publication patterns for each journal.
-
-The differences in publication counts are explained by a couple different reasons.
-Scopus does not index journals prior to 1996, whereas the SWHD goes back to 1989.
-Although the timeframe of the SWHD is longer than Scopus, the actual number of article records in the SWHD for many journals is lower than what is available in Scopus.
-Scopus included editorials and book reviews in their article count, whereas these publications were specifically excluded from the SWHD.
-Because Scopus data were available only in aggregate form, it was not possible to extract these data to make more refined comparisons.
-In the construction of the SWHD, we also applied a series of cleaning procedures that further reduced the article count for many journals.
-For example, we excluded article records that did not contain author names, an abstract or article title.
-Again, because we were working only with aggregate data from Scopus, we were unable to apply the same cleaning procedures to the Scopus data.
-And, finally, differences can also be attributed to gaps and errors in indexing in Scopus and all the databases used to construct the SWHD.
-This is a known and longstanding problem with some social work journals (see Holden, Holden).
-
+### Aggregated summary (Figure 1a. 1b. -- line charts)
+
+Figures 1a and 1b are line charts showing the number of unique journal
+titles and journal articles published each year during the study time frame.
+In 1989, XX unique journals published a XX articles.  The number of journal
+titles showed some variability from 1989 to 1996, followed by nine years of
+steady growth.  By 2005, the number of journal titles and journal articles
+being published was more than double than what was observed in 1989. The years
+2005 to 2013 exhibited some variability in the number of titles and articles
+published.  The maximum number of journal titles was observed in 2011 (n = XX)
+and dropped to XX by 2013.  The maximum number of journal articles published
+was in 2012, and this dropped to XX in 2013.  The cumulative number of journal
+articles published over the study time frame was XX,XXX.
+
+### Dis-aggregated summary (Figure 2. Small multiples)
+
+Figure 2 is a small multiples plot, also referred to as a trellis or lattice
+chart, that dis-aggregates Figures 1a and 1b.  More specifically, the small
+multiples plot shows the number of articles published each year for each 
+journal throughout the study time frame (orange line).  We also included data from Scopus for
+comparative purposes (purple line).  The small multiples are sorted in descending
+order based on the total number of article records in the HD.  The presentation
+of the sort is by row, so the overall plot is read from left to right.
+Abbreviations are used in Figure 2, and the full journal name is presented in
+Appendix A.
+
+The small multiples plot is particularly useful to show the variability in
+publishing for each journal.  In fact, according to Tufte (xxxx), small
+multiples are the best design solution for visually enforcing comparisons of
+change.  The plot shows that _Families in Society_, _Social Work_, and _British
+Journal of Social Work_ published the greatest number of articles throughout
+the study time frame.  However, the number of articles published by _Families
+in Society_ and _Social Work_ appear to be decreasing, while other journals
+show an increase -- e.g., _Research on Social Work Practice_, _International
+Social Work_, and _Journal of Human Behavior and the Social Environment_.
+
+Data from Scopus was used to help show the overall coverage of the HD, in
+addition to revealing possible gaps in indexing.  The HD and Scopus plotted
+values do not show exact alignment for a couple reasons.  More specifically,
+the HD contains article records going back to 1989, whereas Scopus provides
+data starting from 1996.  Additionally, the overall journal coverage of HD is
+much greater than Scopus -- that is, Scopus provides data for only xx% of the
+journal titles contained in the HD.
+
+The Scopus data that are available show a high degree of correspondence with
+the HD.  Small discrepancies between the Scopus and HD can be attributed to
+differences in indexing.  That is, the article record count of Scopus includes
+editorials and book reviews, whereas these were excluded from the HD.  In the
+construction of the HD, we applied a series of cleaning procedures (refer to
+Methods section) that further reduced the article count.  Because Scopus data
+were available only in aggregate form, it was not possible to extract these
+data to make more refined comparisons.
+
+And, finally, the small multiples plot is especially useful for identifying
+potential gaps in indexing, which is a problem that has been previously
+identified with respect to social work journals (see Holden; Holden). For
+example, Scopus appears to be missing article records for the _Journal of
+Gerontological Social Work_ from XX to XX.  And, the HD is missing records for
+various journals including (but not limited to) the _Journal of Ethnic and
+Cultural Diversity in Social Work_, _Journal of Social Work Disability &
+Rehabilitation_.
+
+### Article attributes
+
+Figures 3a and 3b provide summaries of two important article attributes -- that
+is, the number of authors per article and the length of each article.
+Throughout the history of social work research, at least half of all social
+work articles were sole authored until 2008, as indicated by the median value
+in Figure 3a.  Since 2008, at least half of all articles had two authors.
+Throughout the study time frame, the number of authors has increased steadily,
+as shown by the increasing mean value and its standard deviation.  In 2013, the
+mean number of authors was approximately 2.25, with a standard deviation of
+1.4.  The length of the articles increased steadily from approximately 12 pages
+in 1989 to 15 pages in 2004.  The last three years of the study time frame
+shows a fairly stable publishing trend, with half of all articles being 15
+pages (Mean = XX, sd = XX).
+
+### Abstract analysis
+
+The final set of analyses involved text analysis of the article abstracts to
+determine whether trends in publishing could be readily identified based on the
+frequencies of specific words contained in article abstracts.  In this analysis, we selected words that
+represented different _levels of evidence_ within the evidence-based practices
+framework.  EBP was selected as the focus of analysis, given that the topic
+area is a relatively new in social work, compared to other topics like child
+welfare and case management.  Moreover, because EBP has received considerable
+attention in various areas of social work research, it was expected that
+the different _levels of evidence_ would show should both absolute and
+relative changes in their occurrences.
+
+To identify the terms
+
+it is relatively new and has
+become part of social work terminology,
+
+ that are common to the framework of
+evidence-based practices (EBP).  This topic area was selected because it is a
+more recent area of research relative to other social work topics (e.g., child
+welfare and case management).
+
+The final part of the study involved a topical analysis by using regular
+expressions to identify articles using keywords based on different levels of
+evidence.  We specified four sets of keywords relating to meta-analysis,
+systematic reviews, randomized controlled trials, and quasi-experimental
+studies.  We refer to these as _sets_ of keywords because we used a number of
+different variations on the spelling and related terminology.  For example, RCT
+involved a search specification that such as "randomized control trial,"
+"randomized controlled trial," and "RCT".  The complete definitions of these
+are provided in the index.
+
+Figure 4 is a stacked line chart showing the number of each type of article
+throughout the study timeframe.  This figure shows increased numbers of all
+study types.  It is important to consider this growth relative to the overall
+growth of the field of social work.  Thus, in Figure 5, we plotted the
+proportion of each keyword class relative to the overall number of articles for
+that given year.  This shows an increase -- albeit a small increase -- in the
+proportion of journals, providing evidence of growth relative to the overall
+field.  Slightly more than 1% of all articles published contained a phrase
+equivalent to randomized control trial.
+
+\newpage
+
+```{r finalArticleListecho=FALSE, comment=NA}
+#print.data.frame(final.list, row.names=FALSE)
+```
+
+\newpage
+
+```{r}
+#plotIndex
+```
+
+\newpage
+
+```{r}
+grid.arrange(plot.journal.count, plot.article.count, ncol=2)
+
+```
 \newpage
@@
 
-A bubble plot was created to facilitate interpretation of these data (see Figure 2).
-This involved creating a scatter plot, mapping each journal's total number of publications on the X axis and h-Index value on the Y axis.
-Each journal was assigned a quartile rating for its h-Index, and those quartile values were mapped to four unique colors.
-Finally, the number of years of representation in the study was mapped to the size of the point, or _bubble_.
-Journals without an h-Index rating are not represented in this plot (N = XX).
-A smoothed loess line and confidence interval were added to show the trend between the h-Index scores and number of articles published.
-
-The loess trend line shows a moderate association between the h-Index and number of articles published.
-However, a number of notable deviations are observed.
-Eleven journals were in the highest h-Index quartile.
-The _British Journal of Social Work_ had the highest h-Index value but ranked third with regard to the overall number of publications.
-XXXX, XXXX, and XXXX were also in the top quartile but had comparably fewer published articles and existed for less time than the other journals in the same quartile.
-_Families in Society_ had the most published articles, spanning the full 25-year study period, but was in the second h-Index quartile.
-
-Figure 3 provides a descriptive summary of the number of authors per article over time.
-As indicated by the median, it was more common for articles to be sole-authored until 2006, at which time the median fluctuated between one and two authors, and then stabilizing in 2009 at 2 authors.
-The steady increase in the standard deviation since 2000 indicates an increase in the number of authors for each article.
-The length of articles also increased over time, starting at roughly 12.5 pages in 1989 and increasing steadily over time and stabilizing around 15 pages in 2013.
-The standard deviation remained relatively stable over the 25 year period, with all values falling between the range of XX and XX.
-
-\newpage
-
-```{r finalArticleListecho=FALSE, comment=NA}
-#print.data.frame(final.list, row.names=FALSE)
-```
-
-\newpage
-
-```{r}
-#plotIndex
-```
-
-\newpage
-
-```{r}
-grid.arrange(plot.journal.count, plot.article.count, ncol=2)
-
-```
-
 \newpage

### 2015-05-25 manuscript.Rmd
Updated results section. Programming Pareto.

@@
 
-To identify the terms
-
-it is relatively new and has
-become part of social work terminology,
-
- that are common to the framework of
-evidence-based practices (EBP).  This topic area was selected because it is a
-more recent area of research relative to other social work topics (e.g., child
-welfare and case management).
-
-The final part of the study involved a topical analysis by using regular
-expressions to identify articles using keywords based on different levels of
-evidence.  We specified four sets of keywords relating to meta-analysis,
-systematic reviews, randomized controlled trials, and quasi-experimental
-studies.  We refer to these as _sets_ of keywords because we used a number of
-different variations on the spelling and related terminology.  For example, RCT
-involved a search specification that such as "randomized control trial,"
-"randomized controlled trial," and "RCT".  The complete definitions of these
-are provided in the index.
-
-Figure 4 is a stacked line chart showing the number of each type of article
-throughout the study timeframe.  This figure shows increased numbers of all
-study types.  It is important to consider this growth relative to the overall
-growth of the field of social work.  Thus, in Figure 5, we plotted the
-proportion of each keyword class relative to the overall number of articles for
-that given year.  This shows an increase -- albeit a small increase -- in the
-proportion of journals, providing evidence of growth relative to the overall
-field.  Slightly more than 1% of all articles published contained a phrase
-equivalent to randomized control trial.
+In this analysis, we focused on four different _levels of evidence_:
+Meta-analysis, systematic reviews, randomized controlled trials (RCTs), and
+quasi-experimental designs.  To identify these key words in the article
+abstracts, we created a set of regular expressions of common spellings and
+synonyms for each type of evidence (see Appendix B).  Regular expressions, also
+referred to as regex and regexp, are sequences of characters that define
+specific patterns in text documents and work much like the _find_ functions
+common to word processors.  The regular expressions used to define the _levels
+of evidence_ are presented in Appendix B and the study's source code.
+
+A stacked line chart was used to show absolute change in the number of
+occurrences for each level of evidence in article abstracts.  The line chart
+shows increased numbers of occurrences for each level of evidence, with the
+greatest amount of growth starting in year 2008.  The presence of systematic
+reviews and meta-analyses did not have a sustained presence in  the literature
+until approximately 1995.  In fact, the first occurrence of the key word
+_systematic review_ did not appear until 1997 (cite).
+
+To show relative change, we plotted the proportion of overall articles
+published that contained the target key words for each year.  In 1989, RCTs and
+Quasi-experimental studies were observed in approximately 1/2% of published
+articles.  By 2013, the percentage of RCTs tripled and the percentage of
+quasi-experimental doubled.  Meta-analyses appeared in 1989 and grew to almost
+1/2% by 2013.  Systematic reviews first appeared in 1997, then again in 2003,
+and grew to approximately 1% in 2013.
+
+**Pareto chart**
 

### 2015-05-26 manuscript.Rmd
Tweaking last figure.

@@
 journal.evidence.plot <- arrangeGrob(journal.evidence.plot, main = textGrob("Overall N", gp=gpar(cex=.7, font=2), vjust = 2, hjust = 1.25))
-
+```
+
+```{r plotPareto}
+pareto.df <- df1 %>% group_by(journal) %>% 
+    summarize(EBP.counts = sum(N)) %>% 
+    arrange(desc(EBP.counts)) %>%
+    ungroup() %>%
+    mutate(overallCount = sum(EBP.counts, na.rm=TRUE)) %>%
+    mutate(percentTotal = (EBP.counts/overallCount) *100) %>%
+    mutate(cumSum = cumsum(percentTotal)) %>%
+    slice(1:16)
+
+df1.reduced <- na.omit(df1[df1$journal %in% pareto.df$journal, ])
+df1.reduced <- ungroup(df1.reduced)
+df1.reduced <- full_join(df1.reduced, pareto.df, by = "journal")
+
+#df1.reduced <- df1.reduced %>% mutate(journal = paste(journal, N.sort, sep = "  "))
+
+j.order <- unique(df1.reduced$journal[order(df1.reduced$N.sort, decreasing = FALSE)])
+
+df1.reduced$journal <- factor(df1.reduced$journal, levels = j.order)
+
+df1.unique <- group_by(df1.reduced, journal) %>% slice(1)
+df1.unique$journal <- factor(df1.unique$journal, levels = j.order)
+
+journal.evidence.plot <- ggplot(na.omit(df1.reduced), aes(x = journal, y = N)) + 
+    geom_bar(aes(fill = studyType), stat = "identity") +
+    coord_flip() +
+    theme_bw() + 
+    geom_text(data = df1.unique, aes(y = EBP.counts+7, x = journal, label = EBP.counts), size = 3) +
+    labs(x = "Journal", y = "N") +
+    ylim(c(0, 150)) +
+    scale_fill_manual(values = cp) 
 ```
@@
 ```{r plotClevelandRelative}
+
+proportionsEBP.df <- df1.reduced %>% 
+    group_by(journal) %>% 
+    slice(1) %>%
+     mutate(Journal = as.character(journal)) %>%
+    ungroup() %>%
+    select(-studyType, -N, -N.sort, -journal, -overallCount, -percentTotal, -cumSum)
+
+proportionEBP2.df <- full_join(proportionsEBP.df, sm.scopus.merged.table, by = "Journal")  %>% 
+    mutate(journalProp = EBP.counts / DataBase.N) %>%
+    arrange(desc(journalProp))
 

### 2015-05-26 manuscript.Rmd
Updated final plot.

@@
 
-meta.df <- abstract.df[grep("meta\\s?analysis", abstract.df$abstract), ]
+meta.df <- abstract.df[grep("meta\\s?analysis|metanalysis|systematic\\s?review|meta[-]analysis", abstract.df$abstract), ]
 meta.df$studyType <- rep("meta", nrow(meta.df))
@@
 
-systematicReview.df <- abstract.df[grep("systematic\\s?review", abstract.df$abstract), ]
-systematicReview.df$studyType <- rep("sr", nrow(systematicReview.df))
+#systematicReview.df <- abstract.df[grep("systematic\\s?review", abstract.df$abstract), ]
+#systematicReview.df$studyType <- rep("sr", nrow(systematicReview.df))
 
@@
 
-evidence.df <- rbind(meta.df, rct.df, systematicReview.df, 
+evidence.df <- rbind(meta.df, rct.df, 
      quasi.df)
 
-evidence.df$studyType <- factor(evidence.df$studyType, labels= c("Meta-analysis", "Quasi-experimental", "RCT", "Systematic review"))
+evidence.df$studyType <- factor(evidence.df$studyType, labels= c("Meta-analysis", "Quasi-experimental", "RCT"))
 
 evidence.df$studyType <- factor(evidence.df$studyType, 
-    levels(evidence.df$studyType)[c(1,4,3,2)])
+    levels(evidence.df$studyType)[c(1,3,2)])
 
@@
     theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))
-
 ```
@@
 
-#df1.reduced <- df1.reduced %>% mutate(journal = paste(journal, N.sort, sep = "  "))
-
-j.order <- unique(df1.reduced$journal[order(df1.reduced$N.sort, decreasing = FALSE)])
-
-df1.reduced$journal <- factor(df1.reduced$journal, levels = j.order)
-
-df1.unique <- group_by(df1.reduced, journal) %>% slice(1)
-df1.unique$journal <- factor(df1.unique$journal, levels = j.order)
-
-journal.evidence.plot <- ggplot(na.omit(df1.reduced), aes(x = journal, y = N)) + 
+abb <- rename(abb, journal = Journal)
+
+df1.reduced <- left_join(df1.reduced, abb, by = "journal")
+
+j.order <- unique(df1.reduced$Abbrev[order(df1.reduced$N.sort, decreasing = FALSE)])
+
+df1.reduced$Abbrev <- factor(df1.reduced$Abbrev, levels = j.order)
+
+df1.unique <- group_by(df1.reduced, Abbrev) %>% slice(1)
+df1.unique$journal <- factor(df1.unique$Abbrev, levels = j.order)
+
+journal.evidence.plot <- ggplot(na.omit(df1.reduced), aes(x = Abbrev, y = N)) + 
     geom_bar(aes(fill = studyType), stat = "identity") +
@@
     theme_bw() + 
-    geom_text(data = df1.unique, aes(y = EBP.counts+7, x = journal, label = EBP.counts), size = 3) +
+    geom_text(data = df1.unique, aes(y = EBP.counts+7, x = Abbrev, label = EBP.counts), size = 3) +
     labs(x = "Journal", y = "N") +
     ylim(c(0, 150)) +
-    scale_fill_manual(values = cp) 
+    scale_fill_manual(values = cp) +
+    theme(legend.position = c(.65,.7), panel.grid.major.y = element_blank(), 
+          legend.title=element_blank())
 ```
@@
 
-target.journals <- df1.reduced 
-target.journals$journal <- gsub("\\s+\\d+", "", target.journals$journal)
-EBP.df <- left_join(target.journals, evidence.journals, by = c("journal", "studyType")) %>%
-    group_by(journal) %>%
-    slice(1) %>%
-    ungroup %>%
-    mutate(Proportion = N.sort/Overall.N) %>%
-    rename(Absolute = N.sort)
-
-EBP.df  <- within(EBP.df, quartile <- as.integer(cut(Overall.N, quantile(Overall.N, probs=0:4/4, na.rm=TRUE), include.lowest=TRUE)))
-
-ggplot(EBP.df, aes(Proportion, journal, size = Overall.N, colour=as.factor(quartile))) + 
+proportionEBP3.df <- proportionEBP2.df[proportionEBP2.df$Journal %in% df1.reduced$journal, ]
+proportionEBP3.df$Journal <- factor(proportionEBP3.df$Journal, levels = j.order)
+
+options(digits=3)
+proportionEBP3.df$journalProp <- round(proportionEBP3.df$journalProp, digits = 2)
+propPlot <- ggplot(proportionEBP3.df, aes(journalProp, Abbrev)) +
     theme_bw() + 
-    geom_point()
-
-View(df1.reduced)
-
-evidence.journals <- full_join(evidence.summary3, evidence.summaryOverall, by = "journal") %>%
-    group_by(journal) %>%
-    mutate(Overall.N.Strength = sum(N)) %>%
-    select(-studyType, N) %>%
-    distinct(journal, Overall.N, Overall.N.Strength) %>%
-    mutate(Prop = Overall.N.Strength / Overall.N)
-
-df2 <- data.frame(evidence.journals)
-
-j.order <- unique(df2$journal[order(df2$Overall.N.Strength, decreasing = FALSE)]) 
-df2$journal <- factor(df2$journal, levels = j.order)
-
-df2  <- within(df2, quartile <- as.integer(cut(Overall.N.Strength, quantile(Overall.N.Strength, probs=0:4/4, na.rm=TRUE), include.lowest=TRUE)))
-
-df2 <- df2 %>% arrange(desc(Prop)) %>% slice(1:15)
-
-EBP.plot <- ggplot(na.omit(df2), aes(x = Prop, y= journal, group = journal)) + 
-    geom_segment(aes(yend = journal), xend=0) +
-    geom_point(aes(size = Overall.N.Strength)) + 
-    theme_bw() +
-    theme(panel.grid.major.y = element_blank(), legend.position = c(.62, .65)) +
-    ylab("Journal") +
+    geom_point() +
+    geom_segment(aes(yend = Abbrev, xend = 0)) + 
+    theme(axis.text.y = element_blank(), axis.ticks = element_blank(), 
+          legend.position = "none", 
+          panel.grid.minor = element_blank(), 
+          panel.grid.major.y = element_blank()) + 
+    ylab("") + 
     xlab("Proportion") +
-    labs(size = "Total number of \nEBP articles published") 
+    geom_text(aes(x = journalProp + .05, y = Abbrev, label = journalProp), size = 3) +
+    xlim(c(0, .5))
+
+```
+
+```{r}
+grid.arrange(journal.evidence.plot, propPlot, 
+        ncol=2, nrow=1, widths=c(2, 1), heights=c(1.4, 4))
 ```

### 2015-05-26 manuscript.Rmd
Fine tuning code. All is functional.

@@
---
+---
 title: 'Examining a Quarter Century of Publishing Trends in Social Work Research:
@@
 author: ''
+date: "May 26, 2015"
 output: pdf_document
@@
 
+```
+```{r}
+
+cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
+
+#=======================================
+# Journals
+#=======================================
+library(gridExtra)
+
+n.journals.year <- filter(full.df, attributes == "journal") %>%
+    select(articleID, record)
+
+n.year <- filter(full.df, attributes == "pubYear") %>%
+    select(articleID, record)
+
+n.journals.year <- left_join(n.journals.year, n.year, by = "articleID", copy=TRUE) %>%
+    group_by(record.y) %>%
+    summarise(Journal.count = n_distinct(record.x)) %>%
+    mutate(record.y = as.numeric(record.y))
+
+plot.journal.count <- ggplot(n.journals.year, aes(record.y, 
+    y = Journal.count, group=1)) + 
+    theme_bw() + 
+    geom_line(colour=cp[4], size = 1, alpha = .80) +
+    theme(axis.text.x = element_text(size=8), 
+    title = element_text(size = 10), plot.title=element_text(size=10)) + 
+    xlab("Year") + 
+    ylab("Number of Unique Journal Titles") + 
+    scale_y_continuous(breaks = c(seq(0, 100, 5)), limits = c(20, 70)) +
+    scale_x_continuous(breaks=seq(1989, 2015, 8)) +
+    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))
+
+#=======================================
+# Articles
+#=======================================
+
+articles.df <- left_join(n.so, n.yr) %>%
+    group_by(year) %>%
+    summarize(N = n()) %>%
+    mutate(year = as.numeric(year), CumSum = cumsum(N)) %>%
+    ungroup() %>%
+    arrange(desc(N), year) %>%
+    rename(Year = year)
+
+plot.article.count <- ggplot(articles.df, aes(Year, N, group =1)) + 
+    theme_bw() + 
+    geom_line(colour=cp[2], size = 1, alpha=.80) +
+    theme(axis.text.x = element_text(size=8), 
+    title = element_text(size = 10), plot.title=element_text(size=10)) + 
+    xlab("Year") + 
+    ylab("Number of Articles Published") + 
+    scale_x_continuous(breaks=seq(1989, 2015, 8)) +
+    scale_y_continuous(breaks = c(seq(0, 2200, 250)), limits= c(500, 2100)) +
+    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))
 ```
@@
      annotate("segment", x = 1989, xend = 1992, y = 190, yend = 190, colour = "#533c99")
-
-# x1.grob <- ggplotGrob(plotSmallMultiples.1)
-# x2.grob <- ggplotGrob(ggplot(cars, aes(speed, dist)) + geom_point())
-# 
-# library(gtable)
-# plot1 <- gtable_filter(x1.grob, 'panel', trim=F)$layout
-# pg <- gtable_add_grob(x1.grob, x2.grob, t = max(plot1$t), l = max(plot1$l))
-# grid.newpage()
-# grid.draw(pg)
-```
-
-```{r plotJournalArticle, cache=FALSE}
-#=======================================
-# Journals
-#=======================================
-library(gridExtra)
-
-n.journals.year <- filter(full.df, attributes == "journal") %>%
-    select(articleID, record)
-
-n.year <- filter(full.df, attributes == "pubYear") %>%
-    select(articleID, record)
-
-n.journals.year <- left_join(n.journals.year, n.year, by = "articleID", copy=TRUE) %>%
-    group_by(record.y) %>%
-    summarise(Journal.count = n_distinct(record.x)) %>%
-    mutate(record.y = as.numeric(record.y))
-
-plot.journal.count <- ggplot(n.journals.year, aes(record.y, 
-    y = Journal.count, group=1)) + 
-    theme_bw() + 
-    geom_line(colour=cp[4], size = 1) +
-    theme(axis.text.x = element_text(size=8), 
-    title = element_text(size = 10), plot.title=element_text(size=10)) + 
-    xlab("Year") + 
-    ylab("Number of Journals") + 
-    scale_y_continuous(breaks = c(seq(0, 100, 5)), limits = c(20, 70)) +
-    scale_x_continuous(breaks=seq(1989, 2015, 8)) +
-    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))
-
-#=======================================
-# Articles
-#=======================================
-
-articles.df <- left_join(n.so, n.yr) %>%
-    group_by(year) %>%
-    summarize(N = n()) %>%
-    mutate(year = as.numeric(year), CumSum = cumsum(N)) %>%
-    ungroup() %>%
-    arrange(desc(N), year) %>%
-    rename(Year = year)
-
-plot.article.count <- ggplot(articles.df, aes(Year, N, group =1)) + 
-    theme_bw() + 
-    geom_line(colour=cp[2], size = 1) +
-    theme(axis.text.x = element_text(size=8), 
-    title = element_text(size = 10), plot.title=element_text(size=10)) + 
-    xlab("Year") + 
-    ylab("Number of Articles") + 
-    scale_x_continuous(breaks=seq(1989, 2015, 8)) +
-    scale_y_continuous(breaks = c(seq(0, 2200, 250)), limits= c(500, 2100)) +
-    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))
 ```
@@
     geom_line() +
-    geom_point(data = n_authors3.melted, aes(size = Standard_Deviation), colour = "#e66101") + 
+    geom_point(data = n_authors3.melted, aes(size = Standard_Deviation), colour = "#e66101", alpha=.60) + 
     #theme(axis.text.x = element_text(angle = 45, hjust = 1), 
@@
     ylab("Number of Authors") +
-    xlab("Year") +
-    labs(size = "Standard deviation") +
-    labs(colour = "") + 
+    xlab("") +
+    labs(size = "SD") +
+    labs(colour = NULL) + 
     scale_colour_manual(values = c("#fdb864", "#e66101")) +
-   theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))
+    theme(axis.title.x = element_text(vjust=-0.5), 
+          axis.title.y = element_text(vjust=.75), 
+          legend.position = "bottom") + 
+       theme(title = element_text(size = 10))
 
@@
     geom_line() +
-    geom_point(data = pages.df2.melted, aes(size = Std.Pages), colour = "#5e3c99") + 
+    geom_point(data = pages.df2.melted, aes(size = Std.Pages), colour = "#5e3c99", alpha = .60) + 
     theme_bw() + 
@@
     ylab("Number of Pages") +
-    xlab("Year") +
-    labs(size = "Standard deviation") +
-    labs(colour = "") + 
+    xlab("") +
+    labs(size = "SD") +
+     labs(colour = NULL) +   
     scale_colour_manual(values = c("#b2abd2", "#5e3c99"))  +
-    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))
+    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75), 
+          legend.position = "bottom")
 
@@
 
-df1.summarized <- df1 %>% group_by(journal) %>% 
-    summarize(EBP.counts = sum(N)) %>% 
-    arrange(desc(EBP.counts)) %>%
-    slice(1:15)
-
-df1.reduced <- na.omit(df1[df1$journal %in% df1.summarized$journal, ])
-df1.reduced <- ungroup(df1.reduced)
-
-df1.reduced <- df1.reduced %>% mutate(journal = paste(journal, N.sort, sep = "  "))
-
-#df1$studyType <- factor(df1$studyType)
-j.order <- unique(df1.reduced$journal[order(df1.reduced$N.sort, decreasing = FALSE)]) 
-df1.reduced$journal <- factor(df1.reduced$journal, levels = j.order)
-
-Text1 <- textGrob("Overall N")
-library(gridExtra)
-
-journal.evidence.plot <- ggplot(df1.reduced, 
-    aes(x = N, y= journal, group = journal, colour = studyType, shape= studyType)) + 
-    geom_segment(aes(yend = journal), xend=0, colour="grey90") +
-    geom_point(size = 2) + 
-    scale_color_manual(values = cp) + 
-    theme_bw() +
-    #facet_grid(.~studyType) + 
-    theme(panel.grid.major.y = element_blank(), legend.position = c(.75, .5), 
-    legend.title = element_blank(), legend.text = element_text(size = 8)) + 
-    xlim(0, 600) + 
-    ylab(NULL) +  
-    theme(axis.text.x = element_text(hjust = 1, size = 8), axis.ticks = element_blank()) + 
-    theme(axis.text.y = element_text(size = 8) ) + 
-    scale_x_continuous(breaks = seq(0, 60, 10)) +
-    scale_shape_manual(values=c(24, 23, 21, 25))
-
-journal.evidence.plot <- arrangeGrob(journal.evidence.plot, main = textGrob("Overall N", gp=gpar(cex=.7, font=2), vjust = 2, hjust = 1.25))
-```
-
-```{r plotPareto}
+```
+
+```{r plotEBPstackedBar}
 pareto.df <- df1 %>% group_by(journal) %>% 
@@
 journal.evidence.plot <- ggplot(na.omit(df1.reduced), aes(x = Abbrev, y = N)) + 
-    geom_bar(aes(fill = studyType), stat = "identity") +
+    geom_bar(aes(fill = studyType), stat = "identity", alpha=.60) +
     coord_flip() +
@@
     scale_fill_manual(values = cp) +
-    theme(legend.position = c(.65,.7), panel.grid.major.y = element_blank(), 
-          legend.title=element_blank())
-```
-
-```{r plotClevelandRelative}
+    theme(legend.position = c(.65,.7),  legend.title=element_blank(), legend.background = element_rect(fill="transparent"))
+```
+
+```{r plotEBPproportion}
 
@@
     theme_bw() + 
-    geom_point() +
-    geom_segment(aes(yend = Abbrev, xend = 0)) + 
+    geom_point(colour="grey40") +
+    geom_segment(aes(yend = Abbrev, xend = 0), colour = "grey40") + 
     theme(axis.text.y = element_blank(), axis.ticks = element_blank(), 
@@
           panel.grid.minor = element_blank(), 
-          panel.grid.major.y = element_blank()) + 
-    ylab("") + 
+            panel.margin = unit(0,"null")) + 
+    ylab(NULL) +
     xlab("Proportion") +
-    geom_text(aes(x = journalProp + .05, y = Abbrev, label = journalProp), size = 3) +
+    geom_text(aes(x = journalProp + .07, y = Abbrev, label = journalProp), size = 3) +
     xlim(c(0, .5))
 
-```
-
-```{r}
-grid.arrange(journal.evidence.plot, propPlot, 
-        ncol=2, nrow=1, widths=c(2, 1), heights=c(1.4, 4))
 ```
@@
 ```{r}
-#plot.article.count
-```
-
-\newpage
-
-```{r}
-plot.author.count
-```
-
-\newpage
-
-```{r}
-page.plot
+
+grid.arrange(plot.author.count, page.plot, ncol = 2)
 ```
@@
 ```
+
 \newpage
 ```{r}
-journal.evidence.plot
-```
-
-\newpage
-```{r}
-EBP.plot
+grid.arrange(journal.evidence.plot, propPlot, 
+        ncol=2, nrow=1, widths=c(2, 1), heights=c(1.4, 4))
 ```

### 2015-05-26 manuscript.Rmd
Code cleaning. All functional.

@@
 
-```{r tableArticleSummary, eval=TRUE, cache=TRUE}
+```{r summarySetUp, eval=TRUE, cache=TRUE}
 unique.titles <- filter(full.df, attributes == "journal") %>%
@@
     select(-attributes, -record)
-
-```
-```{r}
-
+```
+
+```{r  plot01_JournalsArticles, cache=TRUE}
 cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
@@
     xlab("Year") + 
-    ylab("Number of Unique Journal Titles") + 
+    ylab("Journals") + 
     scale_y_continuous(breaks = c(seq(0, 100, 5)), limits = c(20, 70)) +
@@
     xlab("Year") + 
-    ylab("Number of Articles Published") + 
+    ylab("Articles") + 
     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
@@
 
-```{r plotSmallMultiples, cache=FALSE}
+```{r plot02_SmallMultiples, cache=TRUE}
 # Remove 2014 & 2015
@@
     xlab("") +
-    labs(size = "SD") +
+    labs(size = "SD = ") +
     labs(colour = NULL) + 
@@
           legend.position = "bottom") + 
-       theme(title = element_text(size = 10))
+       theme(title = element_text(size = 10)) +
+    theme(axis.text.x = element_text(size=8), 
+    title = element_text(size = 10), plot.title=element_text(size=10)) +
+    theme(legend.text = element_text(size = 8), legend.title = element_text(face="plain"))
 
@@
     xlab("") +
-    labs(size = "SD") +
+    labs(size = "SD = ") +
      labs(colour = NULL) +   
@@
     theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75), 
-          legend.position = "bottom")
+          legend.position = "bottom") +
+    theme(axis.text.x = element_text(size=8), 
+    title = element_text(size = 10), plot.title=element_text(size=10)) +
+    theme(legend.text = element_text(size = 8), legend.title = element_text(face="plain"))
 
@@
 
-evidence.df$studyType <- factor(evidence.df$studyType, labels= c("Meta-analysis", "Quasi-experimental", "RCT"))
+evidence.df$studyType <- factor(evidence.df$studyType, labels= c("Meta-analysis,\nSys Rev", "Quasi-experimental", "RCT"))
 
@@
     scale_y_continuous(breaks = seq(0,90, 10)) +
-    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))
+    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75)) +
+    theme(axis.text.x = element_text(size=8), axis.text.y = element_text(size =8),
+    title = element_text(size = 10), plot.title=element_text(size=10)) +
+    theme(legend.text = element_text(size = 8))
 ```
@@
      theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-    scale_y_continuous(breaks = seq(0, .03, .005))
+    scale_y_continuous(breaks = seq(0, .03, .005)) +
+    theme(axis.text.x = element_text(size=8), axis.text.y = element_text(size =8),
+    title = element_text(size = 8), plot.title=element_text(size=8)) +
+    theme(legend.text = element_text(size = 8))
 ```
@@
 
+```
+
+```{r plotEBPstackedBar}
+
 df1 <- df
-
-```
-
-```{r plotEBPstackedBar}
 pareto.df <- df1 %>% group_by(journal) %>% 
@@
     theme_bw() + 
-    geom_text(data = df1.unique, aes(y = EBP.counts+7, x = Abbrev, label = EBP.counts), size = 3) +
+    geom_text(data = df1.unique, aes(y = EBP.counts+7, x = Abbrev, label = EBP.counts), size = 2.5) +
     labs(x = "Journal", y = "N") +
@@
     scale_fill_manual(values = cp) +
-    theme(legend.position = c(.65,.7),  legend.title=element_blank(), legend.background = element_rect(fill="transparent"))
+    theme(legend.position = c(.65,.7),  legend.title=element_blank(), 
+          legend.background = element_rect(fill="transparent")) +
+    theme(axis.text.x = element_text(size=8), axis.text.y = element_text(size=8), 
+    title = element_text(size = 10), plot.title=element_text(size=10)) +
+    theme(legend.text = element_text(size = 8))
 ```
@@
     xlab("Proportion") +
-    geom_text(aes(x = journalProp + .07, y = Abbrev, label = journalProp), size = 3) +
-    xlim(c(0, .5))
+    geom_text(aes(x = journalProp + .07, y = Abbrev, label = journalProp), size = 2.5) +
+    xlim(c(0, .5))  +
+    theme(axis.text.x = element_text(size=8),  
+    title = element_text(size = 8), plot.title=element_text(size=8)) +
+    theme(legend.text = element_text(size = 8))
 

### 2015-05-26 manuscript.Rmd
Reformatting journal.

@@
 output: pdf_document
+header-includes:
+- \usepackage{indentfirst}
+- \usepackage{setspace}
+- \doublespacing
+- \setlength{\parindent}{4em}
 ---
@@
 
-```{r plotAuthorCount, eval=TRUE, cache=FALSE}
+```{r plot03_AuthorPages, eval=TRUE, cache=FALSE}
+
+#----------------------------
+#Authors
+#----------------------------
+
 year.df <- full.df %>%
@@
 
-```
-
-```{r pagePlot, eval=TRUE, cache=FALSE}
+#----------------------------
+#Pages
+#----------------------------
+
 cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
@@
 
-```{r plotStacked, cache=FALSE}
+```{r plot04_EBPstacked, cache=FALSE}
 abstract.df <- filter(full.df, attributes == "abstract")
@@
 
-evidence.df$studyType <- factor(evidence.df$studyType, labels= c("Meta-analysis,\nSys Rev", "Quasi-experimental", "RCT"))
+evidence.df$studyType <- factor(evidence.df$studyType, labels= c("Meta-analysis,\nSystematic Review", "Quasi-experimental", "RCT"))
 
@@
 
-```{r plotProportions, cache=FALSE}
+```{r plot05_ProportionsLine, cache=FALSE}
 df <- evidence.summary2
@@
 
-```{r plotClevelandAbsolute}
+```{r plot06_EBPjournal, cache=FALSE}
 evidence.summary3 <- select(evidence.df, -abstract) %>% 
@@
     rename(N.sort = Overall.N.Strength)
-
-```
-
-```{r plotEBPstackedBar}
 
@@
 
-```{r plotEBPproportion}
+```{r plot07_EBPproportion, cache=FALSE}
 
@@
     theme(legend.text = element_text(size = 8))
-
 ```

### 2015-05-27 manuscript.Rmd
Updated methods section.

@@
 
-### Extraction of article records
-
-Our list of social work journals was guided by the work of Hodge and Lacasse
-(2011).  More specifically, Hodge and Lacasse (2011) identified 84 disciplinary
-social work journals based on a variety of sources, including _An Author’s
-Guide to Social Work Journals_ (NASW Press, 1997), Thyer’s (2005) more recent
-listing of social work periodicals, and Genamics JournalSeek
-(http://journalseek.net/). Hodge and Lacasse (2011) examined the mission and
-aims of each journal, and eliminated journals that were specific to another
-field or had an had an inter-disciplinary focus.  For the current study, our
-primary search query included all journal titles in this list.
-
-To help ensure comprehensive coverage of all possible core social work
-journals, we created a supplemental search query that extracted journal titles
-with any of the following terms:
+## Social work journal titles
+
+The primary unit of analysis for this study was bibliographic records of social
+work journal articles (hereafter referred to as ``article records``).  The
+first step in the extraction process involved constructing a comprehensive list
+of social work journal titles.  We used the work of Hodge and Lacasse (2011) as
+our base list.  Hodge and Lacasse (2011) compiled a list of 84 unique social
+work journal titles using a variety of sources, includingt the book _An
+Author’s Guide to Social Work Journals_ (NASW Press, 1997), Thyer’s (2005) more
+recent listing of social work periodicals, and the website _Genamics
+JournalSeek_ (http://journalseek.net/). Hodge and Lacasse (2011) examined the
+mission and aims of each journal, and eliminated journals that were specific to
+another field or had an inter-disciplinary focus.  All social work journals
+identified by Hodge and Lacasse (2011) were included on our base list.
+
+To ensure comprehensive coverage, we also conducted a search of the Internet
+and other bibliographic databases to identify other journals that may be
+considered a disciplinary social work journal. The search terms included:
 
@@
 
-Using this search queries, we extract journal article recrods from three major
-databases on the EbscoHost platform:  PsycINFO, Social Service Abstracts, and
-Social Work Abstracts.  Because of known gaps in indexing in databases (Holden,
-Barker, Kuppens, Rosenberg & LeBreton, 2014; Holden, Barker, Covert-Vail,
-Rosenberg, & Cohen, 2009), we also searched ProQuest, which linked to an
-additional 46 minor databases, including (but not limited to): ERIC,
-Sociological Abstracts and Worldwide Political Science Abstracts.  In every
-search, we used a filter in attempt to extract only article records that were
-classified as _journal articles_, thereby excluding other forms of scholarly
-communication that was not relevant to the current study (e.g., book reviews,
-editorials, obituaries, etc.).  We limited the timeframe to a 25 year period,
-from 1989 to 2013 (inclusive).  Articles published in years 2014 and 2015 were
-excluded because of delays in indexing.  Search results were exported in
-batches of article records based on the restrictions of the platform.  Article
-records were text files in a _generic bibliographic format_.  The article
-records contained various meta-data based on the database from which the
-article record was extracted.   Meta-data include (but are not limited to):
-article title, journal title, publication year, author name(s), author
-affiliation(s), abstract, keywords, methodological classification, funding
-source, location of study, subject groups, digital object identifier (DOI),
-number of references, number of pages, etc.  These files were post-processed
-into a structured database using a set of scripts written in the R statistical
-programming language.  The initial search resulted in `r
-pretty(nrow(article.count.initial))` article records from `r
-journal.count.initial`.
-
-The search queries were purposefully specified to be overly inclusive to ensure
-full coverage of all possible social work journals contained in the major and
-minor databases.  Additionally, a visual inspection of the article records
-revealed problems in the original indexing of articles that requires subsequent
-data cleaning.  Thus, our data cleaning procedures focused separately on
-journal titles and article records.
-
-### Data cleaning: Journal titles
-
-The first step of data cleaning involved fixing journal title names due to
-discrepant errors in indexing. For example, _Journal of Gay and Lesbian Social
-Services_ was indexed as a journal separate from _Journal of Gay & Lesbian
-Social Services_ (use of "and" vs. "&").  Other examples involved journals
-indexed with and without subtitles, or journals with and without the word "The"
-at the beginning of the title.  Additionally, some journals changed titles over
-their history.  For example, _Journal of Technnology in Human Services_ is
-formerly known as _Computers in Human Services_.  In these situations, the
-former titles were merged with the current titles.
-
-Many journals from allied health disciplines used one of the supplemental
-search terms in special editions, which were also included in the journal
-title.  Thus, many non-social work journals were captured in the extraction
-process.  To resolve this issue, we created a list of all journal titles that
-were not part of the core list defined by Hodge and Lacasse (2011).  Study
-authors reviewed these journal titles and discussed whether each candidate
-title should be retained or excluded.  When disagreements occurred, the study
-authors reviewed the mission and aims of the journals, names of editorial board
-members, and focus of the articles.  A consensus was reached on all journal
-titles to be excluded and retained.   After these procedures, the number of
-article records and journal titles was reduced to `r
-pretty(nrow(article.count.journalsCleaned))` and `r
-journal.count.journalsCleaned`.
-
-### Data cleaning:  Article records
-
-Our search procedures involved the use of three major databased and 46 minor
-databases, which resulted in some duplication of article records.  Thus, a
-matching algorithm was constructed to identify and remove all duplicate article
-records. As previously noted, the filtering of only journal articles was not
-successful due to errors in the original indexing.  Thus, other scholarly
-communications were captured in the extractio process.  These other scholarly
-communications were readily identified due to specific patterns in the titles,
-such as the terms "Book Review," "From the Editor," and "Obituary."  Given the
-number of article records in the database, it was not feasbile to manually
-extract these recrods.  Instead, we created a separate database with
-representative examples of article records that we wanted to extract.  We also
-added representative examples of article records to be retained.  We then wrote
-a series of _regular expressions_ to extract the problematic article records.
-Regular expressions are a sequence of characters that form search patterns,
-allowing extraction of records that match the specified pattern.  In other
-words, it is a more sophisticated implementation of the search function common
-to all major word processors.  We tested our regular expressions on the test
-database, achieving > 95% accuracy with regard to retaining and extracting
-article records.  These regular expressions were then applied to the full
-database.  We then excluded article records if they were missing essential
-meta-data, including author name(s), journal title, article title, and
-publication field.  As an additional requirement, we required all articles to
-be $\geq 3$ pages in length.   Finally, we eliminated all social work journals
-with total article counts of < 10 for the entire 25 year window (_Issues in
-Social Work Education_, _Maatskaplike Werk/Social Work_, _Pediatric Social
-Work_, and _Critical Social Work_).  These cleaning procedures resulted in a
-final database of `r pretty(articles.final)` articles and `r journals.final`
-journals.
-
-### Data quality checks
+Journal titles that were identified in the supplemental search were reviewed
+by the study team. When disagreements occurred, the authors reviewed the
+mission and aims of the journals, names of editorial board members, and content
+of representative articles.  A consensus was reached on all journal titles to
+be excluded and retained.  In this process, an additional XX journal were
+identified, producing a final target list of XX journals.
+
+## Extraction of article records
+
+After the target list of social work journal titles was finalized, we attempted
+to identify all article records from these journals using three major databases
+on the EbscoHost platform (PscyINFO, Social Science Abstracts, and Social Work
+Abstracts) and 46 minor databases on Proquest (e.g., ERIC, Sociological
+Abstracts, Worldwide Political Science Abstracts).  Using the ``publication
+source`` fields of the search interface, we searched for article records that
+contained the names of each social work journal.  Searches were limited to a
+quarter century time-frame, 1989 to 2013.  We excluded years 2014 and 2015 due
+to delays in indexing of records that were observed.  In the extraction
+process, we also limited the records to only those classified as "journal
+articles," thereby excluding other types of scholarly communications, such as
+editorials, comments on articles, letters to the editor, book reviews, and
+obituaries.
+
+Search results were saved and exported as plain text files in _generic
+bibliographic format_. The article records contained meta-data, including (but
+not limited to): article title, journal title, publication year, author
+name(s), author affiliation(s), abstract, keywords, methodological
+classification, funding source, location of study, subject groups, digital
+object identifier (DOI), number of references, number of pages, etc. It should
+be noted that the databases provided different pieces of meta-data, or
+meta-data in varying formats.  Thus, extensive post-process of the article
+records was necessary to make the article records comparable and analyzable.
+
+## Post-processing of article records
+
+Articles were post-processed from the _generic bibliographic format_ to a
+structured database with computer scripts authored specifically for this study
+using the programming language R. Post-processing of the files involved
+addressing numerous problems that occurred during the original indexing of the
+article records.  For example, journal titles that included the word ``and''
+sometimes used an amersand (&). Other examples included inconsistent use of the
+word ``The'' at the beginning of the title, or the inconsistent use of
+subtitles.  It should be noted that some journals changed titles over their
+publication history.  For example,  _Journal of Technology in Human Services_
+is formerly known as _Computers in Human Services_.  All historical titles were
+merged with their current titles and analyzed as a single journal in this
+study. The source code provides complete details of all the procedures to
+resolve discrepancies and historical titles.
+
+In addition to the foregoing discrepancies, we also found other problems among
+the extracted set of article records.  For example, the filtering of article
+records did not successfully exclude all other types of documents (e.g.,
+editorials, book reviews, and obituaries).  Thus, we used a set of text
+matching procedures called _regular expressions_ to identify other documents
+that were incorrectly classified as journal articles.  We observed > 95%
+accuracy identifying non-article records using a separate database designed
+specifically for script testing.  We excluded article records if they were
+missing essential meta-data for this study, including author name(s), journal
+title, article title, and year of publication.  Finally, we eliminated all
+social work journals with total article counts of < 10 for the entire 25 year
+window (_Issues in Social Work Education_, _Pediatric Social Work_, and
+_Critical Social Work_).
+
+## Data quality checks
 
 We performed a variety of checks on the final database.  Because the size of
-the database, it was not feasible to manually inspect all records.  Thus, we
-randomly sampled article records from the database and cross-checked the data
-we procured with the information listed with the journal's homepage.  We also
-inspected a scatter plot of the number of article records for each journal by
-the number of years the journal appeared within the 25 window timeframe.
-Journals that exhibited significant deviation from the regression line were
-inspected to ensure that our cleaning procedures did not systematically exclude
-article records or retain other scholarly communications.  All observed
-discrepancies were verified as differences in journals actual publication
-output.  Finally, we also made checks of number of journal article records for
-various journals indexed in the _Web of Science_.  Although the counts were
-close -- i.e., within 10% -- similar indexing problems observed from our record
-extraction were also observed in the _Web of Science_ database, such as
-misclassification of book reviews as journal articles.  Thus, we are unable to
-quantify the actual amount of error in our database is due to problems in
-indexing.  At the same time, we are relying on the same source of data that
-social work researchers use to inform their work.  Too much cleaning and
-post-processing of the search results can give rise to validity issues because
-social work researchers are using an information source that contain the errors
-we have attempted to eliminate.  The issue of reliability and validity are
-given further attention in the discussion section of this study.
-
-### Analyses
+the final database, it was not feasible to manually inspect all records.  Thus,
+we randomly sampled article records from the database and cross-checked journal
+meta-data with information listed on the journal's web page.  To help build
+confidence in the comprehensiveness of the constructed database, we obtained
+aggregate publication data from Scopus and made systematic comparisons with the
+database constructed for this project.  Scopus data was selected because it is
+the single largest abstract and citation database of scientific journals and
+was not linked to either the EbscoHost or ProQuest databases in the record
+extraction process.  The systematic comparisons are
+
+## Reproducible research
+
+In addition to post-processing original article records, R was also used for
+all other data analysis.  R was an ideal analytic tool because it is
+open-source and has a suite of related tools for producing reproducible
+research.  More specifically, all the source code is written using Rmarkdown --
+an open-source system that integrates data management, data analysis, and the
+written report.  The source code and data extracts is also curated at openICPSR
+of the Inter-university Consotrium for Political and Social Research of the
+University of Michigan.  The source code is also available from the first
+author's GitHub repository, where the code will be maintained and updated to
+support future research projects. It should be noted that the full data files
+cannot be made publicly available because these are considered proprietary data
+of the database services.  However, to ensure full compliance with the best
+practices of reproducible research (cite King), we have [BRYAN -- DESCRIBE HERE
+HOW THE PS JOURNAL HANDLES THIS ISSUE ... ASSUME THE EDITOR IS ON-BOARD WITH
+THIS APPROACH].
 

### 2015-05-27 manuscript.Rmd
Methods Revisions

@@
 to identify all article records from these journals using three major databases
-on the EbscoHost platform (PscyINFO, Social Science Abstracts, and Social Work
-Abstracts) and 46 minor databases on Proquest (e.g., ERIC, Sociological
+on the EbscoHost platform (PsycINFO, Social Science Abstracts, and Social Work
+Abstracts) and 46 minor databases on ProQuest (e.g., ERIC, Sociological
 Abstracts, Worldwide Political Science Abstracts).  Using the ``publication
@@
 an open-source system that integrates data management, data analysis, and the
-written report.  The source code and data extracts is also curated at openICPSR
+written report.  The source code and data extracts are also curated at openICPSR
 of the Inter-university Consotrium for Political and Social Research of the
@@
 of the database services.  However, to ensure full compliance with the best
-practices of reproducible research (cite King), we have [BRYAN -- DESCRIBE HERE
-HOW THE PS JOURNAL HANDLES THIS ISSUE ... ASSUME THE EDITOR IS ON-BOARD WITH
-THIS APPROACH].
+practices of reproducible research (cite King), we have provided the journal editor with the following conditions under which we would release the data: (1) the requester must be affilitated with an insitution that provides access to both the EbscoHost and ProQuest platforms along with the databases used in this study or (2) hold a personal subscription to each platform and the databases utilized here.
+This is designed to meet the standards of maximum allowable data transparency while respecting the proprietary nature of the data.
 

### 2015-06-10 manuscript.Rmd
Updated text.

@@
 
-### Data Revolution
-
-It is estimated that 90% of all the data in human history has been generated in the past two years, and the amount of data continues to grow by roughly 2.5 quintillion bytes every day [(IBM, nd-a)](http://www-01.ibm.com/software/data/bigdata/what-is-big-data.html).
-We have unprecedented opportunities for deriving actionable insights from these data to advance the human condition.
-The significance continues to gain the attention of national and international organizations.
-For example, the Independent Expert Advisory Group (IEAG) of the United Nations prepared a report entitled, _A World That Counts:  Mobilising the Data Revolution for Sustainable Development_ [(IEAG, 2014)](http://www.undatarevolution.org/report/).
-The IEAG (2014) argues that "Data are the lifeblood of decision-making and the raw material for accountability.
-Without high-quality data providing the right information on the right things at the right time; designing, monitoring and evaluating effective policies becomes almost impossible" (p.
-2).
-The United States federal government established an open data initiative, motivated by the awareness that data can have the greatest impact when it is "accessible, discoverable, and usable" [(www.data.gov)](www.data.gov).
-Data from all levels of government that is made completely open can lead to "cost savings, efficiency, fuel for business, improved civic services, informed policy, performance planning, research and scientific discoveries, transparency and accountability, and increased public participation in the democratic dialogue" (www.data.gov).
-At the time of preparing this article, over 124,000 data sets were freely available through www.data.gov among a diverse set of topic areas:  agriculture, business, climate, consumers, ecosystems, education, energy, finance, health, local government, manufacturing, ocean studies, public safety, and science and research.
-
-In 2012, the NIH established the Big Data to Knowledge (BD2K) initiative, recognizing the potential of data to advance our understanding of human health and disease.
-This initiative was designed to support four broad goals:  1) to facilitate use of biomedical digital assets by making them discoverable, accessible, and citable; 2) to conduct research and develop methods, software and tools to analyze biomedical big data; 3) to enhance training in the development of use and tools necessary for biomedical big data science; and 4) to support a data ecosystem that accelerates discovery as part of the digital enterprise (NIH).
-At roughly the same time, the National Science Foundation (NSF) created new initiatives to harness the potential of the data revolution, arguing that "data are motivating a profound transformation in the culture and conduct of scientific research in every field of science and engineering ...
-American scientists must rise to the challenges and seize the opportunities afforded by this new, data-driven revolution" (Suresh, XXX).
-The programs of the NSF are organized around capacity building and innovative applications.
-Capacity building activities focus on developing fundamental theories, techniques, methodologies and technologies that are broadly applicable to big data problems.
-Innovative applications relate to specific domains advancing innovative ideas that provide solutions “with potential for a broader impact on data science and its applications.”
-
-### Data Science and Social Work
-
-We are indeed living in a data revolution.
-The relevance to social work research is clear — we have the opportunity to study human behavior and other social phenomena in real time, with vastly improved reliability in our measurements, and at scale.
-Data comes from a wide range of sources, including (but not limited to) social media interactions, electronic medical records, audio and video recordings, click stream data, transaction data, web logs, embedded sensors, and GPS.
-New tools allow blending of data sets, unique ways to analyze data, and methods of visualizations that can produce insights limited only by one's imagination.
-As stated by the NIH, "lack of appropriate tools, poor data accessibility, and insufficient training, are major impediments to rapid translational impact" in this new era of data.
-It is essential that the field of social work fully embraces the data revolution and considers the extent to which the existing research infrastructure and training is preparing both social work researchers and providers to be effective and efficient in a data rich world.
-The potential of the data revolution is reflected in the current _Grand Challenge_ entitled, “Harness technology for social good.”  However, we believe that the data revolution goes beyond this single _Grand Challenge_ as it provides the opportunity to be informative in all areas of social work research.
-
-Data science serves as a useful framework for broadening the existing research infrastructure and training opportunities within social work.
-Data science is similar to traditional academic research, as it includes the key roles of substantive expertise and traditional research methodologies.
-Much of the theoretical basis comes from the field of statistics (Zumel & Mount, 2014), but the famous statistician William Cleveland argued that it is an interdisciplinary field that is much larger than statistics (Cleveland, XXX).
-A major difference is that data science draws heavily from knowledge in the areas of computer science, software engineering, and information technology.
-Unlike traditional academic research, data science is particularly well suited for tackling the _3 V’s_ of big data:  _volume_, _variety_, and _velocity_.
-More specifically, in data-rich environments, researchers encounter an amount or volume of data that often exceeds the capacity of traditional database systems.
-Data also come in a variety of formats, ranging from highly structured data contained in relational databases to massive stores of unstructured text-data culled from social media.
-Many data opportunities go beyond the traditional approach of downloading a dataset and analyzing it with an off-the-shelf statistical package like SPSS, Stata, or SAS.
-Now, data can be accessed in real time through application program interfaces (API), which brings along the challenge of _velocity_ — that is, data can be transmitted at a rate that grossly exceeds the computing power of desktop computers.
-These are practical challenges that need to be addressed in order to maximize the potential of these new data.
-
-Another feature that distinguishes data science from traditional academic research is the focus on generating _actionable insights_ from data rather than theory building and hypothesis testing.
-In fact, data science is more interested in deriving useful insights from correlational patterns as opposed to uncovering causal mechanisms.
-The focus is on the development of data products (Davenport, XXX), as opposed to reporting analysis.
-Data products are tools or services that generate actionable insights from the data itself, including (but not limited to) automated reports or dashboards, recommendation systems, prediction algorithms, decision tools, and interactive visualizations that help people with non-technical background make sense of complex data.
-Data science also values the philosophy of _openness_ or open science.
-Thus, much effort is devoted to creating sustainable systems that make data as widely and freely accessible as possible, and developing and promoting the use of open source tools for managing and analyzing data.
-The concept of reproducible research is a _rule_ rather than the _exception_.
-This involves making both data and statistical code available alongside research reports.
-This helps ensure the quality of the research, in addition to allowing researchers to make advances without having duplicate work that has already been done.
-Data science is by no means incompatible with traditional academic research.
-We believe that the tools, research strategies, and principles of data science are complementary to traditional ways of knowledge building in social work, offering many unique opportunities to improve the quality, efficiency, and impact of this area of research.
-
-### Overview of Current Study
-
-In the current study, we seek to utilize the opportunities of the data revolution and data science by applying a range of tools and strategies to construct an historical base of social work research.
-In doing so we take on two of the 3 Vs of big data: volume due the amount of data collected and variety in terms of the multiple sources of that data.
-The data are article records harvested from existing bibliographic databases hosted on ProQuest and EbscoHost.
-Article records are already widely used in various bibliometric studies, particularly those that are intended to reveal publication networks within scientific communities.
-It does so by creating links between co-authors, and then visually representing the edges and vertices of the network.
-This is also done with article citation histories, to show influence over time.
-In this study, we were interested in the various article meta-data that are common to many scientific article records.
-For example, a single article record in psycINFO can have as many as XX pieces of meta-data including:  dates, journal titles, article titles, author names, author affiliations, full text abstracts, keywords, subject classification, methodology, location, populations, page numbers, and source of funding.
-This is a rather large amount of information about a single paper, at least compared to the amount of information contained in article records before the availability of electronic storage and access.
-Large collections of article records may contain potentially interesting trends in the research, assuming the selection of the article records were conducted in a way that allowed meaningful inferences to be derived.
-
-In the current study, we sought to capture every journal article record published in every social work journals over the in past quarter century (1989-2013) and to explore the various meta-data to uncover potentially interesting trends in the social work scholarship.
-For example, we can reasonably infer estimates of the _size_  of social work scholarship by counting the number of unique article records.
-And, growth of the field can be inferred by examining the number of article records over time.
-Similarly, we examine the extent to which _team science_ has become part of the research practice, as this has implications for training of social work researchers.
-We also use location meta-data to understand the extent to which different areas of the world have and have not been the focus of social work research.
-Finally, we used topic modeling to extract topic areas that define the focus of social work research.
-The execution of this research was grounded in the tools and values of data science.
-Thus, all data were managed and analyzed using the open source software, R.
-We also used an open source authoring system that integrates the statistical analysis with the text of the manuscript.
-Along with this manuscript, the authors will also release the actual data and statistical code, thereby meeting the requirements of _reproducible research_, as defined by King ().
-To our knowledge, this is the first time fully reproducible research (as defined by King, XXXX), has been published in a social work journal.
-
-Davenport: http://blogs.wsj.com/cio/2014/06/25/so-you-want-to-build-a-data-product/
-
-http://www.nsf.gov/pubs/2015/nsf15544/nsf15544.htm
-
-http://www.nsf.gov/news/news_summ.jsp?cntn_id=123607&org=NSF&from=news
-
-Why is this study important:
-
-1.  Substantive contributions 
-Understand publication trends from a macro perspective.  This can:
-
-From an economic standpoint, the field of social work observed growth
-throughout the economic crisis and is expected to maintain growth.  The number
-of MSW programs also continues to grow.  While growth is observed in a variety
-of areas, it is important to consider the extent to which growth has occurred
-regarding overall scholarship.
-
-From a methodological standpoint, this study makes a few unique and important
-contributions to the social work research.  Foremost, the study was designed
-and executed in a manner that meets the full standards of reproducible
-research.  The CTSPEDIA, an advocate of fully reproducible research, defines
-this type of research as, ``the practice of distributing, along with a research
-publication, all data, software source code, and tools required to reproduce
-the results discussed in the publication.  As such the RR [reproducible
-research] package not only describes the research and its results, but becomes
-a complete laboratory in which the research can be reproduced and extended."
-(NOTE ABOUT ORGMODE)
-
-Methods
-
-Include section on reproducible research.
-
-Discussion
-
-## Growth of Social Work Research
-
-From the years 1989 to 2013, the field of social work research produced nearly
-35,000 journal articles. This doesn't include books or book chapters,
-editorials, book reviews, and other types scientific communications.  The
-growth increased steadily from XX to XX, and appears to be leveling off.
-Through this period of time, we observed XX unique titles appear while a number
-of other journals were lost.
-
-The current study helps clarify the extent to which _team science_ is emerging
-in social work research.  This is an important issue to consider, as it has
-implications for training researchers, reviewing and understnanding tenure and
-promotion cases, and research infrastructure to facilitate collaborations
-(http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3321548/). According to Thomson
-Reuters, the average number of authors on papers included in the Science
-Citation Index increased by about 50% between 1990 and 2010
-(http://www.hopkinsmedicine.org/institute_basic_biomedical_sciences/news_events/articles_and_stories/employment/2013_01_middle_authors.html)
-In our research, a t least one-half of all published studies were authored by a
-single individual until 2009.  The standard deviation continues to increase,
-providing further evidence of continued team science growth in social work.
-How authorship is assessed is a very important consideration for the field,
-particularly with respect to tenure reviews.  It is not clear how reviewers of
-tenure cases are viewing team science contributions and _middle authors_.
-However, this is something that will have to be considered for the field. In
-the field of physics, the weighted average seniourity and average seniority
-measures both had a negative relationship with the impact, based on the number
-of citations the publication received, as well as a negative relationship
-between the number of authors and the number of citations.  http://myweb.fsu.edu/bstvilia/papers/AuthorTeamDiversityImpact.pdf
-(***NOTE TO BRYAN -- AS A QUICK STUDY, YOU AND I SHOULD BUST OUT A STUDY
-INVOLVING THIS.  WE CAN DO IT FOR JUST THE TOP JOURNALS IN SOCIAL WORK THAT ARE
-IN WOS.)
-
-http://dmm.biologists.org/content/7/3/311.full
-
-https://ccrod.cancer.gov/confluence/download/attachments/47284665/teamscience_fieldguide.pdf
-
-One thing to consider is the extent to which social work research is being
-served by other journal outlets.  For example, social work researchers with
-primary research interests in areas of health, mental health, and substance use
-may publish in speciality journals outside of social work for a variety of
-reasons.  Thus, the amount that social work has grown should be cautious,
-keeping in mind this particular metric refers only to social work journals.
-The field may have grown more rapidly in other areas that are not reflected in
-the current research.  The functions that were constructed to _wrangle_ the
-abstracts are functional for records extracted from PubMed.  Since this data
-source contains author affiliations, it would be feasible to extract this
-information using a set of regular expressions.
-
-According to the journal Nature, from the lat 1600s until about 1920, the rule
-was one author per paper.  The rules was ``breached in the 1920s, diminished in
-the 1950s, and largely abandoned by the 1980s'' (p.
-http://www.nature.com/nature/history/full/nature06243.html).  Social work
-research had a much different trajectory.  In social work research, the rule
-wasn't breached until 2009.
-
-This has implications for tenure, and it is unclear how _team science_ is
-actually being considered in context of these reviews.  The field is arguably
-in a time of transition, form si
-
-Defining a _disciplinary_ social work journal was a complicated task.  Social
-work is inherently inter-disciplinary.  We based our definition of a social
-work journal using the list of Hodge and Lacasse (2011), who created a
-comprehensive list of journal titles.  This list was based on earlier attempts
-to identify all the disciplinary social work journals.  We supplemented our
-list by doing supplemental searches in all data sources for journals that used
-any of the following terms.
-
-The length of the articles was examined, as it has implications for device
-formatting.  Clearly, the field of social work has a current average of 15
-typeset pages.  This consistency allows for targeted customization for mobile
-devices.  An article can be optimized and fairly standardized, which has
-important benefits for information retrieval and comprehension.
-
-This article raised many opportunities that became obvious in this study.  In
-the current study, we worked in earnest to present as much of the analyses
-visually.  At the time of writing this article, the majority of social work
-journals do not have full color articles.  Indeed, this is a residual policy
-from when journals were exclusively in black-and-white and before electronic
-archiving.  Now, the majority of research is disseminated electronically, and
-even the most primitive computers connected to the Internet have color
-monitors.
-
-Data quality -- is there anything to talk about on this topic???
-
-Team science -- is it good for social work research?
-
-## Reproducible research
-
-Reproducible research is essential to ensuring the integrity of the scientific
-record.  Making research reproducible is a complicated process that does carry
-risks.  More specifically, it does involve taking extra time to prepare
-documentation, organize code, and prepare files to be made publicly available.
-This problem has already been given careful attention in other fields, which
-can be considered reasonable solutions for solution work research.  For
-example, this study utilized Rmarkdown as the tool for producing reproducible
-research.  Rmarkdown is ... [provide *short* description here -- tell reader
-minimum she/he needs to know].
-
-Another practical consideration of reproducible research is curating the data,
-and making it available.  The availability can be challenging.  For example, 
-many social work studies involve sensitive data that ultimately requires very
-strict limitations on how and where the data are stored, along with
-restrictions on who can access the data.  [Describe the PS journal that helps
-address this issue ...]  This study involves proprietary data from EbscoHost
-and ProQuest, which prevents us from making all the data available.  However,
-we provide a minimum random extract of the data to ensure verification of our
-computer code.  Additionally, we have made all aspects of our computer code
-available that will allow researchers with access to EbscoHost and ProQuest to
-replicate our findings, as well as use the code to build upon this research.
-
-We believe that social work journals should consider implementing policies that
-encourage reproducible research.  Making this best practice in publishing
-represents a straightforward way to improve the quality of social work
-research.  Along with a policy of reproducible research, the issue of how the
-journal responds to errors will also be necessary.  We certainly do not
-advocate that authors are expected to retract articles or face public shame in
-the context of random human error.  Some studies may involve generating
-thousands of lines of computer code -- and, a simple bug in the code can
-produce erroneous results.  Researchers who adhere to the principles of
-reproducible research are ultimately working in earnest to ensure they are
-producing the highest quality research possible.  Errors that are identified in
-the process represent an opportunity to further advance knowledge, which
-sometimes means correcting knowledge.  These situations simply reveal that the
-scientific method is actually working the way it is supposed to.  At present,
-we have to assume that all the social work research published to date is
-without error.  In absence of reproducible research, we can not fully assess
-the quality of research or replicate a study.
-
-Discussion point:
-
-Another complication is the possible consequences that a researcher might experience
-when an error is discovered.  This is an important issue that the field needs
-to address.
-
-very research report is subject to some form of human
-error.  It is important to consider some of the different types of error and
-how the field should respond.
-
-(Conduct and analysis on reproducible research" and "replication" or
-"replicate")
-
-(original citation from orgmode.org:
-http://orgmode.org/worg/org-contrib/babel/intro.html)
-
- conforms to all
-aspects of what is regarded as reproducible research by making available all
-the code produced in order to conduct the study.
-
-.  Methodological contributions
-
 # Methods
 
-## Social work journal titles
-
-The primary unit of analysis for this study was bibliographic records of social
+## Identification of social work journals
+
+The primary unit of analysis for this study was the bibliographic records of social
 work journal articles (hereafter referred to as ``article records``).  The
@@
 
-To ensure comprehensive coverage, we also conducted a search of the Internet
-and other bibliographic databases to identify other journals that may be
-considered a disciplinary social work journal. The search terms included:
+To ensure comprehensive coverage, we supplemented our search by searching the Internet and bibliogpraphic databases that contained any of the following terms:
 
@@
 
-Journal titles that were identified in the supplemental search were reviewed
-by the study team. When disagreements occurred, the authors reviewed the
+Journal titles that were identified with any of these terms were reviewed
+by the study team to determine whether they should be included in the study. When disagreements occurred, the authors reviewed the
 mission and aims of the journals, names of editorial board members, and content
@@
 
-After the target list of social work journal titles was finalized, we attempted
-to identify all article records from these journals using three major databases
+After finalizing the target list of social work journals, we extracted article records from three major databases
 on the EbscoHost platform (PsycINFO, Social Science Abstracts, and Social Work
-Abstracts) and 46 minor databases on ProQuest (e.g., ERIC, Sociological
+Abstracts) and xx minor databases on ProQuest (e.g., ERIC, Sociological
 Abstracts, Worldwide Political Science Abstracts).  Using the ``publication
@@
 
-In addition to the foregoing discrepancies, we also found other problems among
-the extracted set of article records.  For example, the filtering of article
+In addition to the foregoing date quality problem, a variety of other problems were identified and resolved.    For example, the filtering of article
 records did not successfully exclude all other types of documents (e.g.,
@@
 
-## Data quality checks
-
-We performed a variety of checks on the final database.  Because the size of
-the final database, it was not feasible to manually inspect all records.  Thus,
-we randomly sampled article records from the database and cross-checked journal
-meta-data with information listed on the journal's web page.  To help build
-confidence in the comprehensiveness of the constructed database, we obtained
-aggregate publication data from Scopus and made systematic comparisons with the
-database constructed for this project.  Scopus data was selected because it is
+## Analytic strategy
+
+We conducted a series of descriptive analyses using various types of analyses and meta-data to demonstrate the utility of the database.
+Our first set of analyses focused on describing the overall _amount_ and _growth_ of social work research by summarizing the number of unique journal titles and articles published each year throughout the 25-year time frame.
+We then disaggregated these data by examining the number of articles published by each journal.
+We also performed an additional check on the quality of the data by making systematic comparisons with aggregate publication data from Scopus.
+Scopus data was selected because it is
 the single largest abstract and citation database of scientific journals and
 was not linked to either the EbscoHost or ProQuest databases in the record
-extraction process.  The systematic comparisons are
+extraction process.
+
+After describing the _amount_ and _growth_ of social work research, we conducted
+a series of analyses to test the utility of using meta=data to reveal
+publication trends.  As an indicator of the growth of _team science_ we
+summarize counts of the number of authors per article over time.  And, in light 
+of the shift from print to electronic articles, we examined whether the length 
+of articles have changed during this 25-year time frame.
+Finally, we demonstrate the use of full-text abstracts as the basis for topical trend analysis.
+For purposes of demonstration, we use the concept of "evidence-based practices" (and related concepts) to show changes in topics and areas of foci in the social work research.
 
@@
 In addition to post-processing original article records, R was also used for
-all other data analysis.  R was an ideal analytic tool because it is
+all other data analysis.  R is an ideal analytic tool because it is
 open-source and has a suite of related tools for producing reproducible

### 2015-06-11 manuscript.Rmd
Intro and methods revisions.

@@
 
+The advancement of social work as a profession is largely dependent upon its underlying knowledge base.
+This knowledge base is built on a very large body of research that is primarily contained in social work journals and indexed in a variety of databases.
+As in other disciplines, the majority of the publication process, including the indexing of articles, has been handled by for-profit academic publishers.
+While these publishers provide important services to the field, a number of unintended consequences have emerged.
+
+A very serious consequence that has received considerable attention is the expensive subscription fees associated with accessing the research produced by the field.
+Universities face increased difficulties paying these fees while academic publishers are posting "higher profits than nearly any sector of commerce" (Schmitt, 2014).
+In the absence of an academic affiliation, it is nearly impossible for individual social workers and social work agencies to have access to this research.
+Open-access publishing has received attention as a potentially viable model to address this problem of subscription fees, but the model itself does not appear to have gained any traction.
+In fact, movement in the opposite direction has been observed.
+For example, the _Journal of the Society for Social Work and Research_ (JSSWR) was established as an open-access journal in 2010, but converted to a subscription-based journal in 2014.
+
+Another consequence of this publication model that has received almost no attention is the absence of standardized systems and processes for organizing the research.
+More specifically, every academic database provider uses different technologies for managing a subset of social work research defined by their contract.
+Thus, we see variability in the user interfaces, query languages, and file structures.
+Effectively searching the literature necessitates an investment in identifying the various databases that house social work research, and then learning the different methods for querying and managing the search results in each.
+
+Database aggregators (e.g., ProQuest and EbscoHost) and bibliography managers (e.g., EndNote and RefWorks) have helped address these problems.
+However, comprehensive searches ultimately require the use of both database aggregators and stand-alone databases.
+Even when search results are saved in a bibliography manager, a considerable amount of human intervention is required to ensure the meta-data are complete and in a standardized format.
+From this perspective, it is not surprising that substantial errors have been identified in reference lists of social work journals (e.g., Spivey & Wilkis, 2004; Mitchell-Williams, Skipper, Alexander, & Wilkis, 2015).
+
+Addressing the organizational problems of the social work research has benefits beyond simply making information retrieval more efficient and less prone to error.
+For example, article meta-data can facilitate the assessment of scientific progress, identification of major scientific contributors, measurement of scientific output, journal impact, and measurement of productivity (e.g., xxxx).
+A more complete source of meta-data can vastly improve this line of research, given that the quality of any given trend analysis is dependent upon the quality of its underlying data source.
+It is also a necessary step for the development of decision support and recommender systems that can ultimately help social workers more effectively and efficiently address their information needs.
+
+The purpose of this study was to better understand the current organizational structure of the social work research by gathering together, cleaning, structuring, and analyzing all available meta-data for social work journal articles within a 25-year period (1989-2013).
+This required the development of specialized software that we make available in an open source format.
+Consistent with the philosophy of reproducible research, we also make all of our computer code for analyzing the data in an open format.
+
 # Methods
@@
 our base list.  Hodge and Lacasse (2011) compiled a list of 84 unique social
-work journal titles using a variety of sources, includingt the book _An
+work journal titles using a variety of sources, including the book _An
 Author’s Guide to Social Work Journals_ (NASW Press, 1997), Thyer’s (2005) more
@@
 
-To ensure comprehensive coverage, we supplemented our search by searching the Internet and bibliogpraphic databases that contained any of the following terms:
+To ensure comprehensive coverage, we supplemented our base list by searching the Internet and bibliogpraphic databases for journal titles that contained any of the following terms:
 
@@
 Journal titles that were identified with any of these terms were reviewed
-by the study team to determine whether they should be included in the study. When disagreements occurred, the authors reviewed the
+by the study team to determine whether they should be included in the study as a disciplenary social work journal. When disagreements occurred, the authors reviewed the
 mission and aims of the journals, names of editorial board members, and content
@@
 on the EbscoHost platform (PsycINFO, Social Science Abstracts, and Social Work
-Abstracts) and xx minor databases on ProQuest (e.g., ERIC, Sociological
+Abstracts) and xx additional databases on ProQuest (e.g., ERIC, Sociological
 Abstracts, Worldwide Political Science Abstracts).  Using the ``publication
@@
 article records.  For example, journal titles that included the word ``and''
-sometimes used an amersand (&). Other examples included inconsistent use of the
+sometimes used an ampersand (&). Other examples included inconsistent use of the
 word ``The'' at the beginning of the title, or the inconsistent use of
@@
 
-We conducted a series of descriptive analyses using various types of analyses and meta-data to demonstrate the utility of the database.
+We conducted a series of descriptive analyses using various types of meta-data to demonstrate the utility of the database.
 Our first set of analyses focused on describing the overall _amount_ and _growth_ of social work research by summarizing the number of unique journal titles and articles published each year throughout the 25-year time frame.
@@
 We also performed an additional check on the quality of the data by making systematic comparisons with aggregate publication data from Scopus.
-Scopus data was selected because it is
-the single largest abstract and citation database of scientific journals and
-was not linked to either the EbscoHost or ProQuest databases in the record
+Scopus data was selected because it is the single largest abstract and citation database of scientific journals and was not linked to either the EbscoHost or ProQuest databases in the record
 extraction process.
@@
 After describing the _amount_ and _growth_ of social work research, we conducted
-a series of analyses to test the utility of using meta=data to reveal
+a series of analyses to test the utility of using meta-data to reveal
 publication trends.  As an indicator of the growth of _team science_ we
@@
 written report.  The source code and data extracts are also curated at openICPSR
-of the Inter-university Consotrium for Political and Social Research of the
+of the Inter-university Consortium for Political and Social Research of the
 University of Michigan.  The source code is also available from the first
@@
 of the database services.  However, to ensure full compliance with the best
-practices of reproducible research (cite King), we have provided the journal editor with the following conditions under which we would release the data: (1) the requester must be affilitated with an insitution that provides access to both the EbscoHost and ProQuest platforms along with the databases used in this study or (2) hold a personal subscription to each platform and the databases utilized here.
-This is designed to meet the standards of maximum allowable data transparency while respecting the proprietary nature of the data.
+practices of reproducible research (cite King), we have provided the journal editor with the following conditions under which we would release the data: (1) the requester must be affiliated with an institution that provides access to both the EbscoHost and ProQuest platforms along with the databases used in this study or (2) hold a personal subscription to each platform and the databases utilized here.
+This is designed to meet an ethic of maximum allowable data transparency while respecting the proprietary nature of the data.
 

### 2015-06-11 manuscript.Rmd
updated results

--- 2015-06-10 manuscript.Rmd
@@
 
-In addition to post-processing original article records, R was also used for
-all other data analysis.  R is an ideal analytic tool because it is
-open-source and has a suite of related tools for producing reproducible
-research.  More specifically, all the source code is written using Rmarkdown --
-an open-source system that integrates data management, data analysis, and the
-written report.  The source code and data extracts are also curated at openICPSR
-of the Inter-university Consotrium for Political and Social Research of the
-University of Michigan.  The source code is also available from the first
-author's GitHub repository, where the code will be maintained and updated to
-support future research projects. It should be noted that the full data files
-cannot be made publicly available because these are considered proprietary data
-of the database services.  However, to ensure full compliance with the best
-practices of reproducible research (cite King), we have provided the journal editor with the following conditions under which we would release the data: (1) the requester must be affilitated with an insitution that provides access to both the EbscoHost and ProQuest platforms along with the databases used in this study or (2) hold a personal subscription to each platform and the databases utilized here.
-This is designed to meet the standards of maximum allowable data transparency while respecting the proprietary nature of the data.
+In addition to post-processing original article records, R was also used for all
+other data analysis.  R is an ideal analytic tool because it is open-source and
+has a suite of related tools for producing reproducible research.  More
+specifically, all the source code is written using Rmarkdown -- an open-source
+system that integrates data management, data analysis, and the written report. 
+The source code and data extracts are also curated at openICPSR of the
+Inter-university Consotrium for Political and Social Research of the University
+of Michigan.  The source code is also available from the first author's GitHub
+repository, where the code will be maintained and updated to support future
+research projects. It should be noted that the full data files cannot be made
+publicly available because these are considered proprietary data of the database
+services.  However, to ensure full compliance with the best practices of
+reproducible research (cite King), we have provided the journal editor with the
+following conditions under which we would release the data: (1) the requester
+must be affilitated with an insitution that provides access to both the
+EbscoHost and ProQuest platforms along with the databases used in this study or
+(2) hold a personal subscription to each platform and the databases utilized
+here.  This is designed to meet the standards of maximum allowable data
+transparency while respecting the proprietary nature of the data.
 
 # Results
-```{r}
-# As shown in Table 1, `r nrow(final.list.25)` journals were included in the current study.
-The mean number of years of inclusion is `r options(digits=2); mean(final.list.updated$study.time)` (median = `r options(digits=2); median(final.list.updated$study.time);`, sd =  `r options(digits=2); sd(final.list.updated$study.time)`).
-The overall h-Index for each journal.
-The h-Index values represent the current h-Index of each journal, as opposed to the h-Index of the final study period, so these values should be interpreted cautiously.
-The mean h-Index value is XXXX, (median = XXX; sd = XXX).
-A total of `r pretty(sum(articles.year.df$year.count))` article records were obtained across these journals.
-The average number of articles per journal was `r options(digits=2); pretty(mean(articles.year.df$year.count))` (median = `r options(digits=2); pretty(median(articles.year.df$year.count))`, sd = `r options(digits=2); pretty(sd(articles.year.df$year.count))`).
-This figure shows consistent growth in the number of articles from 1989 to 2005.
-Notable fluctuations in the number of articles was observed from 2005 to 2008, followed by growth until 2012.
-The decline from 2012 to 2013 should be interpreted cautiously, as this may be an artifact due to delays in indexing.
-```
 
-### Aggregated summary (Figure 1a. 1b. -- line charts)
+We collected a total of 3X,XXX article records from XX different databases.
+Extensive cleaning procedures were applied to exclude documents that were not filtered in the original retrieval process.
+More specifically, as described in the Methods section, we filtered documents to include only journals, while excluding editorials, book reviews, table of contents, and other documents that are not considered journal articles.
+This reduced the total number of unique article records in the database to xx,xxxx.
+
+## Size and growth of social work
 
@@
 chart, that dis-aggregates Figures 1a and 1b.  More specifically, the small 
-multiples plot shows the number of articles published each year for each 
-journal throughout the study time frame (orange line).  We also included data from Scopus for
-comparative purposes (purple line).  The small multiples are sorted in descending
-order based on the total number of article records in the HD.  The presentation
-of the sort is by row, so the overall plot is read from left to right.
-Abbreviations are used in Figure 2, and the full journal name is presented in
-Appendix A.
+multiples plot shows the number of articles published each year for each journal
+throughout the study time frame (orange line).  We also included data from
+Scopus for comparative purposes (purple line).  The small multiples are sorted
+in descending order based on the total number of article records in the HD.  The
+sorting was done by row, so the overall plot so the overall plot is read from
+left to right. Abbreviations are used in Figure 2, and the full journal name is
+presented in Appendix A.
 

### 2015-06-11 manuscript.Rmd

--- 2015-06-11 manuscript.Rmd
@@
 
-In addition to post-processing original article records, R was also used for
-all other data analysis.  R is an ideal analytic tool because it is
-open-source and has a suite of related tools for producing reproducible
-research.  More specifically, all the source code is written using Rmarkdown --
-an open-source system that integrates data management, data analysis, and the
-written report.  The source code and data extracts are also curated at openICPSR
-of the Inter-university Consortium for Political and Social Research of the
-University of Michigan.  The source code is also available from the first
-author's GitHub repository, where the code will be maintained and updated to
-support future research projects. It should be noted that the full data files
-cannot be made publicly available because these are considered proprietary data
-of the database services.  However, to ensure full compliance with the best
-practices of reproducible research (cite King), we have provided the journal editor with the following conditions under which we would release the data: (1) the requester must be affiliated with an institution that provides access to both the EbscoHost and ProQuest platforms along with the databases used in this study or (2) hold a personal subscription to each platform and the databases utilized here.
-This is designed to meet an ethic of maximum allowable data transparency while respecting the proprietary nature of the data.
+In addition to post-processing original article records, R was also used for all
+other data analysis.  R is an ideal analytic tool because it is open-source and
+has a suite of related tools for producing reproducible research.  More
+specifically, all the source code is written using Rmarkdown -- an open-source
+system that integrates data management, data analysis, and the written report. 
+The source code and data extracts are also curated at openICPSR of the
+Inter-university Consotrium for Political and Social Research of the University
+of Michigan.  The source code is also available from the first author's GitHub
+repository, where the code will be maintained and updated to support future
+research projects. It should be noted that the full data files cannot be made
+publicly available because these are considered proprietary data of the database
+services.  However, to ensure full compliance with the best practices of
+reproducible research (cite King), we have provided the journal editor with the
+following conditions under which we would release the data: (1) the requester
+must be affilitated with an insitution that provides access to both the
+EbscoHost and ProQuest platforms along with the databases used in this study or
+(2) hold a personal subscription to each platform and the databases utilized
+here.  This is designed to meet the standards of maximum allowable data
+transparency while respecting the proprietary nature of the data.
 
 # Results
-```{r}
-# As shown in Table 1, `r nrow(final.list.25)` journals were included in the current study.
-The mean number of years of inclusion is `r options(digits=2); mean(final.list.updated$study.time)` (median = `r options(digits=2); median(final.list.updated$study.time);`, sd =  `r options(digits=2); sd(final.list.updated$study.time)`).
-The overall h-Index for each journal.
-The h-Index values represent the current h-Index of each journal, as opposed to the h-Index of the final study period, so these values should be interpreted cautiously.
-The mean h-Index value is XXXX, (median = XXX; sd = XXX).
-A total of `r pretty(sum(articles.year.df$year.count))` article records were obtained across these journals.
-The average number of articles per journal was `r options(digits=2); pretty(mean(articles.year.df$year.count))` (median = `r options(digits=2); pretty(median(articles.year.df$year.count))`, sd = `r options(digits=2); pretty(sd(articles.year.df$year.count))`).
-This figure shows consistent growth in the number of articles from 1989 to 2005.
-Notable fluctuations in the number of articles was observed from 2005 to 2008, followed by growth until 2012.
-The decline from 2012 to 2013 should be interpreted cautiously, as this may be an artifact due to delays in indexing.
-```
 
-### Aggregated summary (Figure 1a. 1b. -- line charts)
+We collected a total of 3X,XXX article records from XX different databases.
+Extensive cleaning procedures were applied to exclude documents that were not filtered in the original retrieval process.
+More specifically, as described in the Methods section, we filtered documents to include only journals, while excluding editorials, book reviews, table of contents, and other documents that are not considered journal articles.
+This reduced the total number of unique article records in the database to xx,xxxx.
+
+## Size and growth of social work
 

### 2015-07-08 manuscript.Rmd
Updated annual change.

@@
 date: "May 26, 2015"
-output: pdf_document
+output: html_document
 header-includes:
@@
     theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))
+```
+
+```{r}
+articles.df$YearRecode <- c(nrow(articles.df):1)
+ggplot(articles.df, aes(Year, N)) +  
+  geom_smooth(method="lm") + 
+  geom_line() +
+  geom_point()
+
+options(digits = 4)
+x <- lm(N ~ YearRecode, data = articles.df)
+summary(x)
+
+articlesN <- rev(articles.df$N)
+articlesN <- ts(articlesN, frequency=1, start = 1989, end = 2013)
+diff(articlesN)/articlesN[-nrow(articlesN),]*100
+
+curr <- articles.df$N[-1]
+prev <- articles.df$N[1:(length(articles.df$N)-1)]
+articles.df <- arrange(articles.df, Year)
+articles.df$monChange <- c(0, (100 *  (curr-prev) / prev)) 
+articles.df <- mutate(articles.df, positiveNegative = as.factor(ifelse(articles.df$monChange >= 0, "Positive", "Negative")))
+
+ggplot(articles.df, aes(Year, monChange, fill = positiveNegative)) + geom_bar(stat="identity") 
+mean(articles.df$monChange[2:25])
+
 ```

### 2015-07-17 manuscript.Rmd
Working on growth models.

--- 2015-06-11 manuscript.Rmd
@@
     ungroup() %>%
-    arrange(desc(N), year) %>%
+    arrange(year) %>%
     rename(Year = year)
@@
     theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))
+
+exp.07 <- c(737, rep(NA, 24)) 
+for(i in 2:25){
+    exp.07[i] <- exp.07[i-1] + exp.07[i-1]*.05
+}
+
+exp.175 <- c(737, rep(NA, 24))
+for(i in 2:25){
+       exp.175[i] <- exp.175[i-1] + exp.175[i-1]*.175
+    }
+
+articles.df$exp.175 <- exp.175
+articles.df$exp.07  <- exp.07
+
+ggplot(articles.df, aes(Year, CumSum, group =1)) + 
+    theme_bw() + 
+    geom_point(colour=cp[2], size = 3, alpha=.80) +
+    theme(axis.text.x = element_text(size=8), 
+    title = element_text(size = 10), plot.title=element_text(size=10)) + 
+    xlab("Year") + 
+    ylab("Articles") + 
+    scale_x_continuous(breaks=seq(1989, 2015, 8)) +
+    #scale_y_continuous(breaks = c(seq(0, 2200, 250)), limits= c(500, 2100)) +
+    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75)) + 
+    geom_line(aes(Year, exp.07), colour = cp[4]) +
+    geom_line(aes(Year, exp.175), colour = cp[3]) +
+    geom_smooth(method = "lm", colour = cp[1])
+
+tail(articles.df)
+
+head(articles.df)
+
+exp.175 <- c(737, rep(NA, 24))
+
+for(i in 2:25){
+       exp.175[i] <- exp.175[i-1] + exp.175[i-1]*.175
+ }
+
+articles.df$exp.175 <- exp.175
+
+```
+
+```{r, eval=FALSE}
+articles.df$YearRecode <- c(nrow(articles.df):1)
+ggplot(articles.df, aes(Year, N)) +  
+  geom_smooth(method="lm") + 
+  geom_line() +
+  geom_point()
+
+options(digits = 4)
+x <- lm(N ~ YearRecode, data = articles.df)
+summary(x)
+
+articlesN <- rev(articles.df$N)
+articlesN <- ts(articlesN, frequency=1, start = 1989, end = 2013)
+diff(articlesN)/articlesN[-nrow(articlesN),]*100
+
+curr <- articles.df$N[-1]
+prev <- articles.df$N[1:(length(articles.df$N)-1)]
+articles.df <- arrange(articles.df, Year)
+articles.df$monChange <- c(0, (100 *  (curr-prev) / prev)) 
+articles.df <- mutate(articles.df, positiveNegative = as.factor(ifelse(articles.df$monChange >= 0, "Positive", "Negative")))
+
+ggplot(articles.df, aes(Year, monChange, fill = positiveNegative)) + geom_bar(stat="identity") 
+mean(articles.df$monChange[2:25])
+
 ```

### 2015-07-19 manuscript.Rmd
Updating repo

@@
 
+exp.171 <- c(737, rep(NA, 24))
+for(i in 2:25){
+       exp.171[i] <- exp.171[i-1] + exp.171[i-1]*.171
+    }
+
 articles.df$exp.175 <- exp.175
 articles.df$exp.07  <- exp.07
+articles.df$exp.171 <- exp.171
 
-ggplot(articles.df, aes(Year, CumSum, group =1)) + 
+ggplot(articles.df, aes(Year, exp.171, group =1)) + 
     theme_bw() + 
     geom_point(colour=cp[2], size = 3, alpha=.80) +
+    geom_line(colour=cp[2]) + 
     theme(axis.text.x = element_text(size=8), 
@@
     theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75)) +
-    geom_line(aes(Year, exp.07), colour = cp[4]) +
-    geom_line(aes(Year, exp.175), colour = cp[3]) +
-    geom_smooth(method = "lm", colour = cp[1])
-
-tail(articles.df)
-
-head(articles.df)
-
-exp.175 <- c(737, rep(NA, 24))
-
-for(i in 2:25){
-       exp.175[i] <- exp.175[i-1] + exp.175[i-1]*.175
- }
-
-articles.df$exp.175 <- exp.175
+    geom_line(aes(Year, CumSum), colour = cp[3]) +
+    geom_point(aes(Year, CumSum), colour = cp[3])
 
@@
     summarise(n=n())
+
+n_authors_grouped <- n_authors %>%
+    mutate(n = ifelse(n >= 4, 4, n)) %>%
+    group_by(pubYear) %>%
+    mutate(n.year = n()) %>%
+    group_by(pubYear, n) %>%
+    summarize(N =  n()) %>%
+    group_by(pubYear) %>%
+    mutate(N.year.overall = sum(N)) %>%
+    mutate(N.percent = (N/N.year.overall)*100)
+
+ggplot(n_authors_grouped, aes(pubYear, N.percent, group = n, colour = as.factor(n))) + geom_line(size = 1.5) + 
+    scale_colour_manual(values = cp) +
+    labs(colour = "Number of Authors") + 
+    ylim(c(0,100)) + 
+    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75), 
+          legend.position = "bottom") +
+    theme(axis.text.x = element_text(size=8), 
+    title = element_text(size = 10), plot.title=element_text(size=10))
 

### 2015-07-19 manuscript.Rmd
CAGR analysis

@@
     theme(legend.text = element_text(size = 8))
+```
+
+```{r CAGR comparison}
+
+CAGR <- function(start, finish, periods){
+  # Function to compute the CAGR given simple returns
+  #
+  # args:
+  #  start = starting value
+  #  finish = ending cumulative value
+  #  periods = number of time periods over which value was accumulated
+  #
+  # Returns the Compound Annual Growth Rate
+    cagr <- round(((finish/start)^(1 /periods) - 1)*100, digits=2)    
+  return(cagr)
+}
+
+setwd("C:/Users/beperron/Git/SocialWorkResearch/Data")
+sangam <- read.csv("sangam.csv")
+
+sangam.cumsum <-sangam %>%
+  group_by(field) %>%
+  mutate(CumSum=cumsum(count))
+
+cagr <- sangam.cumsum %>%
+  filter(year==1989 | year==1998)%>%
+  group_by(field)%>%
+  mutate(cagr=CAGR(start=min(CumSum), finish=max(CumSum), periods=9)) %>%
+  select(field, cagr)
+
+cagr<-unique(cagr)
+
+############## Generate comparable social work CAGR, 1989-1998 #################
+
+sw.cagr <- articles.df %>%
+  filter(Year<1999 & Year>1988)%>%
+  mutate(CumSum=cumsum(N)) %>%
+  mutate(field = "socialWork")
+
+sw.cagr <- sw.cagr %>%
+  mutate(cagr=CAGR(start=min(CumSum), finish=max(CumSum), periods=9))%>%
+  select(field, cagr)
+
+sw.cagr<-unique(sw.cagr)
+
+cagr<-rbind(cagr, sw.cagr)
+
+cagr$field<-as.character(cagr$field)
+cagr$field<-reorder(cagr$field, cagr$cagr)
+
+#############PLOT##################
+
+plot.cagr.ss <- ggplot(cagr, aes(x=field, y=cagr, fill=field, group =1)) + 
+  theme_bw() + 
+  geom_bar(width=0.8, stat='identity') +
+  theme(axis.text.x = element_text(size=8), 
+        title = element_text(size = 10), plot.title=element_text(size=10)) + 
+  xlab("Field") + 
+  ylab("Cumulative annual growth rate (%)") + 
+  ggtitle("Cumulative annual growth rates for article production across the social sciences, 1989-1998") +
+  theme(plot.title = element_text(size = rel(1.5))) +
+  scale_y_continuous(breaks = c(seq(0, 40, 5)), limits=c(0, 40)) +
+  theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))+
+  scale_fill_manual(values=c("#b2abd2", "#b2abd2", "#fdb863", "#b2abd2", "#b2abd2", "#b2abd2", "#b2abd2"))+
+  theme(legend.position="none") +
+  scale_x_discrete(labels=c("Psychology","Economics","Social Work","Sociology","Political Science", "History", "Anthropology")) +
+  geom_hline(yintercept=seq(0, 40, 15), col="white", lwd=0.6) +
+  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
+  theme(panel.border = element_blank(), axis.line = element_line())
+
+plot.cagr.ss
+
 ```

### 2015-07-21 functions/combineData.R
updated combineData function

@@ -10,7 +10,7 @@ combineData.f <- function(){
     full.df <- rbind(ebscoBWR.df, proQuestBWR.df)
 
 
-    year.25 <- as.character(c(1900:1988, 2014, 2015))
+    year.25 <- as.character(c(2014, 2015))
 
     temp.df <- filter(full.df, attributes == "pubYear")
 

### 2015-07-24 functions/combineData.R
Revert to original combineData function

@@ -10,7 +10,7 @@ combineData.f <- function(){
     full.df <- rbind(ebscoBWR.df, proQuestBWR.df)
 
 
-    year.25 <- as.character(c(2014, 2015))
+    year.25 <- as.character(c(1920:1988, 2014, 2015))
 
     temp.df <- filter(full.df, attributes == "pubYear")
 

### 2015-08-07 manuscript.Rmd
Updated figure.
Update lots of stuff.

--- 2015-07-19 manuscript.Rmd
@@
 
-```{r  plot01_JournalsArticles, cache=TRUE}
+```{r Figure 1a - Journals, cache=TRUE}
 cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
@@
 
-plot.journal.count <- ggplot(n.journals.year, aes(record.y, 
-    y = Journal.count, group=1)) + 
+exp.05 <- c(29, rep(NA, 24)) 
+for(i in 2:25){
+    exp.05[i] <- exp.05[i-1] + exp.05[i-1]*.05
+}
+
+exp.04 <- c(29, rep(NA, 24)) 
+for(i in 2:25){
+    exp.04[i] <- exp.04[i-1] + exp.04[i-1]*.04
+}
+
+exp.03 <- c(29, rep(NA, 24)) 
+for(i in 2:25){
+    exp.03[i] <- exp.03[i-1] + exp.03[i-1]*.03
+}
+
+n.journals.year$exp.05 <- exp.05
+n.journals.year$exp.04 <- exp.04
+n.journals.year$exp.03 <- exp.03
+n.journals.year <- mutate(n.journals.year, Journal.count = as.numeric(Journal.count))
+n.journals.year <- as.data.frame(n.journals.year)
+
+years <- c(1989, 2005, 2013, 2013)
+points <- c(29, n.journals.year$Journal.count[c(17,25)], max(n.journals.year$exp.05))
+annotate.df <- data.frame(years, points)
+
+cols = c("Observed Growth" = cp[1], "Estimated 3.2% CAGR" = cp[4], "Estimated 5% CAGR" = cp[3])
+(plot.journal.count <- ggplot(n.journals.year, aes(record.y, 
+    y = Journal.count)) + 
     theme_bw() + 
-    geom_line(colour=cp[4], size = 1, alpha = .80) +
     theme(axis.text.x = element_text(size=8), 
@@
     ylab("Journals") + 
-    scale_y_continuous(breaks = c(seq(0, 100, 5)), limits = c(20, 70)) +
-    scale_x_continuous(breaks=seq(1989, 2015, 8)) +
-    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))
-
-#=======================================
-# Articles
-#=======================================
-
-articles.df <- left_join(n.so, n.yr) %>%
-    group_by(year) %>%
-    summarize(N = n()) %>%
-    mutate(year = as.numeric(year), CumSum = cumsum(N)) %>%
-    ungroup() %>%
-    arrange(year) %>%
-    rename(Year = year)
-
-plot.article.count <- ggplot(articles.df, aes(Year, N, group =1)) + 
-    theme_bw() + 
-    geom_line(colour=cp[2], size = 1, alpha=.80) +
-    theme(axis.text.x = element_text(size=8), 
-    title = element_text(size = 10), plot.title=element_text(size=10)) + 
-    xlab("Year") + 
-    ylab("Articles") + 
-    scale_x_continuous(breaks=seq(1989, 2015, 8)) +
-    scale_y_continuous(breaks = c(seq(0, 2200, 250)), limits= c(500, 2100)) +
-    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75))
-
-exp.07 <- c(737, rep(NA, 24)) 
-for(i in 2:25){
-    exp.07[i] <- exp.07[i-1] + exp.07[i-1]*.05
-}
-
-exp.175 <- c(737, rep(NA, 24))
-for(i in 2:25){
-       exp.175[i] <- exp.175[i-1] + exp.175[i-1]*.175
-    }
-
-exp.171 <- c(737, rep(NA, 24))
-for(i in 2:25){
-       exp.171[i] <- exp.171[i-1] + exp.171[i-1]*.171
-    }
-
-articles.df$exp.175 <- exp.175
-articles.df$exp.07  <- exp.07
-articles.df$exp.171 <- exp.171
-
-ggplot(articles.df, aes(Year, exp.171, group =1)) + 
-    theme_bw() + 
-    geom_point(colour=cp[2], size = 3, alpha=.80) +
-    geom_line(colour=cp[2]) + 
-    theme(axis.text.x = element_text(size=8), 
-    title = element_text(size = 10), plot.title=element_text(size=10)) + 
-    xlab("Year") + 
-    ylab("Articles") + 
-    scale_x_continuous(breaks=seq(1989, 2015, 8)) +
-    #scale_y_continuous(breaks = c(seq(0, 2200, 250)), limits= c(500, 2100)) +
+    scale_y_continuous(breaks = c(seq(0, 100, 5)), limits = c(20, 95)) +
+    scale_x_continuous(breaks=seq(1989, 2015, 4)) +
     theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75)) + 
-    geom_line(aes(Year, CumSum), colour = cp[3]) +
-    geom_point(aes(Year, CumSum), colour = cp[3])
-
+    geom_line(aes(x = record.y, y = exp.05, colour = "Estimated 5% CAGR"), data = n.journals.year, colour = cp[2], alpha = .80) +
+    geom_line(aes(x = record.y, y = exp.04, colour = "Estimated 4% CAGR"), data = n.journals.year,  colour = cp[2], alpha = .80)+
+    geom_line(aes(x = record.y, y = exp.03, colour = "Estimated 3% CAGR"), data = n.journals.year,  colour = cp[2], alpha = .80) + 
+    geom_line(aes(colour = "Observed Growth"), colour = cp[4], size = 1.5) 
 ```
 
-```{r, eval=FALSE}
-articles.df$YearRecode <- c(nrow(articles.df):1)
-ggplot(articles.df, aes(Year, N)) +  
-  geom_smooth(method="lm") + 
-  geom_line() +
-  geom_point()
+```{r Figure 1b - Journals}
+curr <- n.journals.year$Journal.count[-1]
+prev <- n.journals.year$Journal.count[1:(length(n.journals.year$Journal.count)-1)]
+annualChange.numeric <- c(0, (100 * (curr-prev)/ prev))
+annualChange.dichotomous <- ifelse(annualChange.numeric < 0, "Decrease", "Increase")
+annualChange.df <- data.frame(annualChange.numeric, annualChange.dichotomous)
+annualChange.df$year <- c(1989:2013)
 
-options(digits = 4)
-x <- lm(N ~ YearRecode, data = articles.df)
-summary(x)
-
-articlesN <- rev(articles.df$N)
-articlesN <- ts(articlesN, frequency=1, start = 1989, end = 2013)
-diff(articlesN)/articlesN[-nrow(articlesN),]*100
-
-curr <- articles.df$N[-1]
-prev <- articles.df$N[1:(length(articles.df$N)-1)]
-articles.df <- arrange(articles.df, Year)
-articles.df$monChange <- c(0, (100 *  (curr-prev) / prev)) 
-articles.df <- mutate(articles.df, positiveNegative = as.factor(ifelse(articles.df$monChange >= 0, "Positive", "Negative")))
-
-ggplot(articles.df, aes(Year, monChange, fill = positiveNegative)) + geom_bar(stat="identity") 
-mean(articles.df$monChange[2:25])
-
+ggplot(annualChange.df, aes(year, annualChange.numeric, fill =annualChange.dichotomous)) + 
+    theme_bw() + 
+    geom_bar(stat="identity") +
+    scale_fill_manual(values = cp[c(3,1)], limits = c("Increase", "Decrease")) + 
+    theme(legend.position = c(1,1), legend.justification = c(1,1), legend.title = element_blank()) + 
+    ylab("Percent change") +
+    xlab("Year")  +
+    scale_x_continuous(breaks=seq(1989, 2015, 4)) + 
+    scale_y_continuous(breaks = seq(-10, 15, 5)) + 
+    geom_hline(yintercept=seq(-5, 15, 5), col="white", lwd=0.4) +
+    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
+          panel.border = element_blank(), axis.line = element_line()) + 
+    geom_hline(yintercept=0, col="gray", lwd=0.6, alpha =.8) +
+    ggtitle("Annual Percentage Change in the Number of Social Work Journals (1989 - 2013")
 ```
@@
 
-n_authors_grouped <- n_authors %>%
-    mutate(n = ifelse(n >= 4, 4, n)) %>%
-    group_by(pubYear) %>%
-    mutate(n.year = n()) %>%
-    group_by(pubYear, n) %>%
-    summarize(N =  n()) %>%
-    group_by(pubYear) %>%
-    mutate(N.year.overall = sum(N)) %>%
-    mutate(N.percent = (N/N.year.overall)*100)
-
-ggplot(n_authors_grouped, aes(pubYear, N.percent, group = n, colour = as.factor(n))) + geom_line(size = 1.5) + 
-    scale_colour_manual(values = cp) +
-    labs(colour = "Number of Authors") + 
-    ylim(c(0,100)) + 
-    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75), 
-          legend.position = "bottom") +
-    theme(axis.text.x = element_text(size=8), 
-    title = element_text(size = 10), plot.title=element_text(size=10))
-
 n_authors <- n_authors%>% 
@@
     theme(legend.text = element_text(size = 8), legend.title = element_text(face="plain"))
+
+n_authors_grouped <- n_authors %>%
+    mutate(n = ifelse(n >= 4, 4, n)) %>%
+    group_by(pubYear) %>%
+    mutate(n.year = n()) %>%
+    group_by(pubYear, n) %>%
+    summarize(N =  n()) %>%
+    group_by(pubYear) %>%
+    mutate(N.year.overall = sum(N)) %>%
+    mutate(N.percent = (N/N.year.overall)*100)
+
+ggplot(n_authors_grouped, aes(pubYear, N.percent, group = n, colour = as.factor(n))) + geom_line(size = 1.5) + 
+    scale_colour_manual(values = cp) +
+    labs(colour = "Number of Authors") + 
+    ylim(c(0,100)) + 
+    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75), 
+          legend.position = "bottom") +
+    theme(axis.text.x = element_text(size=8), 
+    title = element_text(size = 10), plot.title=element_text(size=10))
+
+```
 
@@
 
-```{r plot04_EBPstacked, cache=FALSE}
-abstract.df <- filter(full.df, attributes == "abstract")
-year.df <- filter(full.df, attributes == "pubYear")
-journal.df <- filter(full.df, attributes == "journal")
-abstract.df <- left_join(year.df, abstract.df, by = "articleID")
-abstract.df <- left_join(abstract.df, journal.df, by = "articleID")
-abstract.df <- abstract.df %>% select(-attributes.x, -attributes.y, -attributes)
-colnames(abstract.df) <- c("articleID", "year", "abstract", "journal")
-abstract.df$abstract <- gsub("[[:punct:]]", "", abstract.df$abstract)
-abstract.df$abstract <- tolower(abstract.df$abstract)
+```{r CAGR comparison}
 
-ebp.df <- abstract.df[grep("evidence\\s?based\\spractices?|ebp|empirically\\s?supported\\streatments?", abstract.df$abstract), ]
-ebp.df$studyType <- rep("ebp", nrow(ebp.df))
+CAGR <- function(start, finish, periods){
+  # Function to compute the CAGR given simple returns
+  #
+  # args:
+  #  start = starting value
+  #  finish = ending cumulative value
+  #  periods = number of time periods over which value was accumulated
+  #
+  # Returns the Compound Annual Growth Rate
+    cagr <- round(((finish/start)^(1 /periods) - 1)*100, digits=1)    
+  return(cagr)
+}
 
-meta.df <- abstract.df[grep("meta\\s?analysis|metanalysis|systematic\\s?review|meta[-]analysis", abstract.df$abstract), ]
-meta.df$studyType <- rep("meta", nrow(meta.df))
+setwd("/Users/beperron/Git/SocialWorkResearch/Data")
+sangam <- read.csv("sangam.csv")
 
-rct.df <- abstract.df[grep("randomi[s|z]ed.*trial|[^non]experimental\\sdesign|rct|controlled\\sclinical\\strial|cct", abstract.df$abstract), ]
-rct.df$studyType <- rep("rct", nrow(rct.df))
+sangam.cumsum <-sangam %>%
+  group_by(field) %>%
+  mutate(CumSum=cumsum(count))
 
-#systematicReview.df <- abstract.df[grep("systematic\\s?review", abstract.df$abstract), ]
-#systematicReview.df$studyType <- rep("sr", nrow(systematicReview.df))
+cagr <- sangam.cumsum %>%
+  filter(year==1989 | year==1998)%>%
+  group_by(field)%>%
+  mutate(cagr=CAGR(start=min(CumSum), finish=max(CumSum), periods=9)) %>%
+  select(field, cagr)
 
-quasi.df <- abstract.df[grep("cohort\\sstudy|case\\scontrol\\sstudy|quasi\\s?experimental|non\\s?experimental", abstract.df$abstract), ]
-quasi.df$studyType <- rep("quasi", nrow(quasi.df))
+cagr<-unique(cagr)
 
-evidence.df <- rbind(meta.df, rct.df, 
-     quasi.df)
+############## Generate comparable social work CAGR, 1989-1998 #################
 
-evidence.df$studyType <- factor(evidence.df$studyType, labels= c("Meta-analysis,\nSystematic Review", "Quasi-experimental", "RCT"))
+sw.cagr <- articles.df %>%
+  filter(Year<1999 & Year>1988)%>%
+  mutate(CumSum=cumsum(N)) %>%
+  mutate(field = "socialWork")
 
-evidence.df$studyType <- factor(evidence.df$studyType, 
-    levels(evidence.df$studyType)[c(1,3,2)])
+sw.cagr <- sw.cagr %>%
+  mutate(cagr=CAGR(start=min(CumSum), finish=max(CumSum), periods=9))%>%
+  select(field, cagr)
 
-evidence.summary <- select(evidence.df, -abstract) %>% 
-    group_by(year, studyType) %>%
-    summarize(N = n()) %>%
-    group_by(studyType) %>%
-  mutate(cumulative = cumsum(N))
+sw.cagr<-unique(sw.cagr)
 
-cp <- c("#b2abd2", "#5e3c99", "#fdb864", "#e66101" )
-evidence.summary <- ungroup(evidence.summary)
-evidence.summary$year <- as.numeric(evidence.summary$year)
-#evidence.summary$studyType <- as.factor(evidence.summary$studyType)
+cagr<-rbind(cagr, sw.cagr)
 
-abstractsYear.df <- group_by(abstract.df, year) %>% 
-    summarize(N.abstracts = n()) %>%
-    mutate(year = as.numeric(year))
+cagr$field<-as.character(cagr$field)
+cagr$field<-reorder(cagr$field, cagr$cagr)
 
-evidence.summary2 <- full_join(evidence.summary, abstractsYear.df, 
-    by = "year") %>%
-    mutate(studyProp =N / N.abstracts)
+#############PLOT##################
 
-year.labs <- as.character(seq(1989,2013, 4))
+CAGR <- ggplot(cagr, aes(x=field, y=cagr, fill=field, group =1)) + theme_bw() + 
+    geom_bar(width=0.8, stat='identity') + theme(axis.text.x = element_text(size=8),
+        title = element_text(size = 10), plot.title=element_text(size=10)) + 
+    ylab("Cumulative annual growth rate (%)") + 
+    xlab("") + 
+    ggtitle("Cumulative annual growth rates for \nnumber of published articles (1989 - 1998)") + 
+    theme(plot.title = element_text(size = rel(1.5))) + scale_y_continuous(breaks =
+        c(seq(0, 40,  15)), limits=c(0, 40)) + theme(axis.title.x =
+        element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75)) + 
+    scale_fill_manual(values=c("#b2abd2", "#b2abd2", "#fdb863", "#b2abd2",
+        "#b2abd2", "#b2abd2", "#b2abd2"))+ theme(legend.position="none") + 
+    scale_x_discrete(labels=c("Psychology","Economics","Social \nWork","Sociology","Political \nScience", "History", "Anthropology")) + 
+    geom_hline(yintercept=seq(0, 40, 15), col="white", lwd=0.6) + 
+    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),  
+        panel.border = element_blank(), axis.line = element_line(), 
+        axis.text.y = element_text(size = 15),
+        axis.text.x = element_text(size = 15),
+        axis.title.y = element_text(size = 15), 
+        title = element_text(size = 16)
+        ) + 
+    geom_text(aes(label =cagr ), vjust = -.5)
 
-stacked.df <- as.data.frame(xtabs(N~year+studyType, evidence.summary))
-
-stacked.plot <- ggplot(stacked.df, 
-    aes(x = as.numeric(year), y = Freq, fill=studyType)) + 
-    geom_area(alpha=.60, colour = "black", size = .2) +
-    theme_bw() +
-    scale_fill_manual(values=cp, 
-        breaks = rev(levels(evidence.summary$studyType)))+
-    scale_x_continuous(breaks = seq(0,24, 4), labels = year.labs) + 
-    theme(  legend.position=c(.25,.80),
-#         legend.background = element_blank(), 
-         legend.key = element_blank()   ) + 
-    ylab("Number of Articles") + 
-    xlab("Year") + 
-    labs(fill = "") +
-    scale_y_continuous(breaks = seq(0,90, 10)) +
-    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75)) +
-    theme(axis.text.x = element_text(size=8), axis.text.y = element_text(size =8),
-    title = element_text(size = 10), plot.title=element_text(size=10)) +
-    theme(legend.text = element_text(size = 8))
-```
-
-```{r plot05_ProportionsLine, cache=FALSE}
-df <- evidence.summary2
-
-evidence.plot <- ggplot(na.omit(df), aes(year, studyProp, colour = studyType, 
-    group = studyType), na.rm=TRUE) + 
-    geom_smooth(aes(fill=studyType), alpha = .40, colour = "dimgray") + facet_wrap(~studyType) + 
-    theme_bw() +
-    scale_fill_manual(values = cp) +   
-    scale_color_manual(values = cp) + 
-    theme(legend.position = "none") + 
-    ylab("Proportion") + 
-    geom_point(colour = "black", alpha = .60) + 
-    annotate("segment", x = 1989, y = 0, xend = 2013, yend = 0, alpha = .6, 
-        linetype= "solid") +
-    annotate("segment", x = 1989, y = 0, xend = 1989, yend = .0175, alpha = .6, 
-        linetype = "solid") +
-    annotate("segment", x = 2013, y = 0, xend = 2013, yend = .0175, alpha = .6,
-             linetype = "solid") +
-    scale_x_continuous(breaks = seq(1989, 2014, 4)) + 
-     theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
-    scale_y_continuous(breaks = seq(0, .03, .005)) +
-    theme(axis.text.x = element_text(size=8), axis.text.y = element_text(size =8),
-    title = element_text(size = 8), plot.title=element_text(size=8)) +
-    theme(legend.text = element_text(size = 8))
-```
-
-```{r plot06_EBPjournal, cache=FALSE}
-evidence.summary3 <- select(evidence.df, -abstract) %>% 
-    group_by(journal, studyType) %>%
-    summarize(N = n())
-
-evidence.summaryOverall <- select(abstract.df, -abstract) %>%
-    group_by(journal) %>%
-    summarize(Overall.N = n())
-
-evidence.journals <- full_join(evidence.summary3, evidence.summaryOverall, by = "journal") %>%
-    mutate(JN.prop = N/Overall.N) %>% group_by(journal) %>%
-    mutate(Overall.N.Strength = sum(N))
-
-evidence.journalsOverall <- evidence.journals %>% group_by(journal) %>%
-    mutate(Overall.N.Strength = sum(N))
-
-df <-  select(evidence.journalsOverall, studyType, N, Overall.N.Strength) %>%
-    rename(N.sort = Overall.N.Strength)
-
-df1 <- df
-pareto.df <- df1 %>% group_by(journal) %>% 
-    summarize(EBP.counts = sum(N)) %>% 
-    arrange(desc(EBP.counts)) %>%
-    ungroup() %>%
-    mutate(overallCount = sum(EBP.counts, na.rm=TRUE)) %>%
-    mutate(percentTotal = (EBP.counts/overallCount) *100) %>%
-    mutate(cumSum = cumsum(percentTotal)) %>%
-    slice(1:16)
-
-df1.reduced <- na.omit(df1[df1$journal %in% pareto.df$journal, ])
-df1.reduced <- ungroup(df1.reduced)
-df1.reduced <- full_join(df1.reduced, pareto.df, by = "journal")
-
-abb <- rename(abb, journal = Journal)
-
-df1.reduced <- left_join(df1.reduced, abb, by = "journal")
-
-j.order <- unique(df1.reduced$Abbrev[order(df1.reduced$N.sort, decreasing = FALSE)])
-
-df1.reduced$Abbrev <- factor(df1.reduced$Abbrev, levels = j.order)
-
-df1.unique <- group_by(df1.reduced, Abbrev) %>% slice(1)
-df1.unique$journal <- factor(df1.unique$Abbrev, levels = j.order)
-
-journal.evidence.plot <- ggplot(na.omit(df1.reduced), aes(x = Abbrev, y = N)) + 
-    geom_bar(aes(fill = studyType), stat = "identity", alpha=.60) +
-    coord_flip() +
-    theme_bw() + 
-    geom_text(data = df1.unique, aes(y = EBP.counts+7, x = Abbrev, label = EBP.counts), size = 2.5) +
-    labs(x = "Journal", y = "N") +
-    ylim(c(0, 150)) +
-    scale_fill_manual(values = cp) +
-    theme(legend.position = c(.65,.7),  legend.title=element_blank(), 
-          legend.background = element_rect(fill="transparent")) +
-    theme(axis.text.x = element_text(size=8), axis.text.y = element_text(size=8), 
-    title = element_text(size = 10), plot.title=element_text(size=10)) +
-    theme(legend.text = element_text(size = 8))
-```
-
-```{r plot07_EBPproportion, cache=FALSE}
-
-proportionsEBP.df <- df1.reduced %>% 
-    group_by(journal) %>% 
-    slice(1) %>%
-     mutate(Journal = as.character(journal)) %>%
-    ungroup() %>%
-    select(-studyType, -N, -N.sort, -journal, -overallCount, -percentTotal, -cumSum)
-
-proportionEBP2.df <- full_join(proportionsEBP.df, sm.scopus.merged.table, by = "Journal")  %>% 
-    mutate(journalProp = EBP.counts / DataBase.N) %>%
-    arrange(desc(journalProp))
-
-proportionEBP3.df <- proportionEBP2.df[proportionEBP2.df$Journal %in% df1.reduced$journal, ]
-proportionEBP3.df$Journal <- factor(proportionEBP3.df$Journal, levels = j.order)
-
-options(digits=3)
-proportionEBP3.df$journalProp <- round(proportionEBP3.df$journalProp, digits = 2)
-propPlot <- ggplot(proportionEBP3.df, aes(journalProp, Abbrev)) +
-    theme_bw() + 
-    geom_point(colour="grey40") +
-    geom_segment(aes(yend = Abbrev, xend = 0), colour = "grey40") + 
-    theme(axis.text.y = element_blank(), axis.ticks = element_blank(), 
-          legend.position = "none", 
-          panel.grid.minor = element_blank(), 
-            panel.margin = unit(0,"null")) + 
-    ylab(NULL) +
-    xlab("Proportion") +
-    geom_text(aes(x = journalProp + .07, y = Abbrev, label = journalProp), size = 2.5) +
-    xlim(c(0, .5))  +
-    theme(axis.text.x = element_text(size=8),  
-    title = element_text(size = 8), plot.title=element_text(size=8)) +
-    theme(legend.text = element_text(size = 8))
 ```
@@
 ```
-
-# Methods
-
-## Identification of social work journals
-
-The primary unit of analysis for this study was the bibliographic records of social
-work journal articles (hereafter referred to as ``article records``).  The
-first step in the extraction process involved constructing a comprehensive list
-of social work journal titles.  We used the work of Hodge and Lacasse (2011) as
-our base list.  Hodge and Lacasse (2011) compiled a list of 84 unique social
-work journal titles using a variety of sources, including the book _An
-Author’s Guide to Social Work Journals_ (NASW Press, 1997), Thyer’s (2005) more
-recent listing of social work periodicals, and the website _Genamics
-JournalSeek_ (http://journalseek.net/). Hodge and Lacasse (2011) examined the
-mission and aims of each journal, and eliminated journals that were specific to
-another field or had an inter-disciplinary focus.  All social work journals
-identified by Hodge and Lacasse (2011) were included on our base list.
-
-To ensure comprehensive coverage, we supplemented our base list by searching the Internet and bibliogpraphic databases for journal titles that contained any of the following terms:
-
- + "social work" 
- + "social welfare" 
- + "social casework" 
- + "social service"
- + "human service" 
- + "social development" 
- + "social environment"
-
-Journal titles that were identified with any of these terms were reviewed
-by the study team to determine whether they should be included in the study as a disciplenary social work journal. When disagreements occurred, the authors reviewed the
-mission and aims of the journals, names of editorial board members, and content
-of representative articles.  A consensus was reached on all journal titles to
-be excluded and retained.  In this process, an additional XX journal were
-identified, producing a final target list of XX journals.
-
-## Extraction of article records
-
-After finalizing the target list of social work journals, we extracted article records from three major databases
-on the EbscoHost platform (PsycINFO, Social Science Abstracts, and Social Work
-Abstracts) and xx additional databases on ProQuest (e.g., ERIC, Sociological
-Abstracts, Worldwide Political Science Abstracts).  Using the ``publication
-source`` fields of the search interface, we searched for article records that
-contained the names of each social work journal.  Searches were limited to a
-quarter century time-frame, 1989 to 2013.  We excluded years 2014 and 2015 due
-to delays in indexing of records that were observed.  In the extraction
-process, we also limited the records to only those classified as "journal
-articles," thereby excluding other types of scholarly communications, such as
-editorials, comments on articles, letters to the editor, book reviews, and
-obituaries.
-
-Search results were saved and exported as plain text files in _generic
-bibliographic format_. The article records contained meta-data, including (but
-not limited to): article title, journal title, publication year, author
-name(s), author affiliation(s), abstract, keywords, methodological
-classification, funding source, location of study, subject groups, digital
-object identifier (DOI), number of references, number of pages, etc. It should
-be noted that the databases provided different pieces of meta-data, or
-meta-data in varying formats.  Thus, extensive post-process of the article
-records was necessary to make the article records comparable and analyzable.
-
-## Post-processing of article records
-
-Articles were post-processed from the _generic bibliographic format_ to a
-structured database with computer scripts authored specifically for this study
-using the programming language R. Post-processing of the files involved
-addressing numerous problems that occurred during the original indexing of the
-article records.  For example, journal titles that included the word ``and''
-sometimes used an ampersand (&). Other examples included inconsistent use of the
-word ``The'' at the beginning of the title, or the inconsistent use of
-subtitles.  It should be noted that some journals changed titles over their
-publication history.  For example,  _Journal of Technology in Human Services_
-is formerly known as _Computers in Human Services_.  All historical titles were
-merged with their current titles and analyzed as a single journal in this
-study. The source code provides complete details of all the procedures to
-resolve discrepancies and historical titles.
-
-In addition to the foregoing date quality problem, a variety of other problems were identified and resolved.    For example, the filtering of article
-records did not successfully exclude all other types of documents (e.g.,
-editorials, book reviews, and obituaries).  Thus, we used a set of text
-matching procedures called _regular expressions_ to identify other documents
-that were incorrectly classified as journal articles.  We observed > 95%
-accuracy identifying non-article records using a separate database designed
-specifically for script testing.  We excluded article records if they were
-missing essential meta-data for this study, including author name(s), journal
-title, article title, and year of publication.  Finally, we eliminated all
-social work journals with total article counts of < 10 for the entire 25 year
-window (_Issues in Social Work Education_, _Pediatric Social Work_, and
-_Critical Social Work_).
-
-## Analytic strategy
-
-We conducted a series of descriptive analyses using various types of meta-data to demonstrate the utility of the database.
-Our first set of analyses focused on describing the overall _amount_ and _growth_ of social work research by summarizing the number of unique journal titles and articles published each year throughout the 25-year time frame.
-We then disaggregated these data by examining the number of articles published by each journal.
-We also performed an additional check on the quality of the data by making systematic comparisons with aggregate publication data from Scopus.
-Scopus data was selected because it is the single largest abstract and citation database of scientific journals and was not linked to either the EbscoHost or ProQuest databases in the record
-extraction process.
-
-After describing the _amount_ and _growth_ of social work research, we conducted
-a series of analyses to test the utility of using meta-data to reveal
-publication trends.  As an indicator of the growth of _team science_ we
-summarize counts of the number of authors per article over time.  And, in light 
-of the shift from print to electronic articles, we examined whether the length 
-of articles have changed during this 25-year time frame.
-Finally, we demonstrate the use of full-text abstracts as the basis for topical trend analysis.
-For purposes of demonstration, we use the concept of "evidence-based practices" (and related concepts) to show changes in topics and areas of foci in the social work research.
-
-## Reproducible research
-
-In addition to post-processing original article records, R was also used for all
-other data analysis.  R is an ideal analytic tool because it is open-source and
-has a suite of related tools for producing reproducible research.  More
-specifically, all the source code is written using Rmarkdown -- an open-source
-system that integrates data management, data analysis, and the written report. 
-The source code and data extracts are also curated at openICPSR of the
-Inter-university Consotrium for Political and Social Research of the University
-of Michigan.  The source code is also available from the first author's GitHub
-repository, where the code will be maintained and updated to support future
-research projects. It should be noted that the full data files cannot be made
-publicly available because these are considered proprietary data of the database
-services.  However, to ensure full compliance with the best practices of
-reproducible research (cite King), we have provided the journal editor with the
-following conditions under which we would release the data: (1) the requester
-must be affilitated with an insitution that provides access to both the
-EbscoHost and ProQuest platforms along with the databases used in this study or
-(2) hold a personal subscription to each platform and the databases utilized
-here.  This is designed to meet the standards of maximum allowable data
-transparency while respecting the proprietary nature of the data.
-
-# Results
-
-We collected a total of 3X,XXX article records from XX different databases.
-Extensive cleaning procedures were applied to exclude documents that were not filtered in the original retrieval process.
-More specifically, as described in the Methods section, we filtered documents to include only journals, while excluding editorials, book reviews, table of contents, and other documents that are not considered journal articles.
-This reduced the total number of unique article records in the database to xx,xxxx.
-
-## Size and growth of social work
-
-Figures 1a and 1b are line charts showing the number of unique journal
-titles and journal articles published each year during the study time frame.
-In 1989, XX unique journals published a XX articles.  The number of journal
-titles showed some variability from 1989 to 1996, followed by nine years of
-steady growth.  By 2005, the number of journal titles and journal articles
-being published was more than double than what was observed in 1989. The years
-2005 to 2013 exhibited some variability in the number of titles and articles
-published.  The maximum number of journal titles was observed in 2011 (n = XX)
-and dropped to XX by 2013.  The maximum number of journal articles published
-was in 2012, and this dropped to XX in 2013.  The cumulative number of journal
-articles published over the study time frame was XX,XXX.
-
-### Dis-aggregated summary (Figure 2. Small multiples)
-
-Figure 2 is a small multiples plot, also referred to as a trellis or lattice 
-chart, that dis-aggregates Figures 1a and 1b.  More specifically, the small 
-multiples plot shows the number of articles published each year for each journal
-throughout the study time frame (orange line).  We also included data from
-Scopus for comparative purposes (purple line).  The small multiples are sorted
-in descending order based on the total number of article records in the HD.  The
-sorting was done by row, so the overall plot so the overall plot is read from
-left to right. Abbreviations are used in Figure 2, and the full journal name is
-presented in Appendix A.
-
-The small multiples plot is particularly useful to show the variability in
-publishing for each journal.  In fact, according to Tufte (xxxx), small
-multiples are the best design solution for visually enforcing comparisons of
-change.  The plot shows that _Families in Society_, _Social Work_, and _British
-Journal of Social Work_ published the greatest number of articles throughout
-the study time frame.  However, the number of articles published by _Families
-in Society_ and _Social Work_ appear to be decreasing, while other journals
-show an increase -- e.g., _Research on Social Work Practice_, _International
-Social Work_, and _Journal of Human Behavior and the Social Environment_.
-
-Data from Scopus was used to help show the overall coverage of the HD, in
-addition to revealing possible gaps in indexing.  The HD and Scopus plotted
-values do not show exact alignment for a couple reasons.  More specifically,
-the HD contains article records going back to 1989, whereas Scopus provides
-data starting from 1996.  Additionally, the overall journal coverage of HD is
-much greater than Scopus -- that is, Scopus provides data for only xx% of the
-journal titles contained in the HD.
-
-The Scopus data that are available show a high degree of correspondence with
-the HD.  Small discrepancies between the Scopus and HD can be attributed to
-differences in indexing.  That is, the article record count of Scopus includes
-editorials and book reviews, whereas these were excluded from the HD.  In the
-construction of the HD, we applied a series of cleaning procedures (refer to
-Methods section) that further reduced the article count.  Because Scopus data
-were available only in aggregate form, it was not possible to extract these
-data to make more refined comparisons.
-
-And, finally, the small multiples plot is especially useful for identifying
-potential gaps in indexing, which is a problem that has been previously
-identified with respect to social work journals (see Holden; Holden). For
-example, Scopus appears to be missing article records for the _Journal of
-Gerontological Social Work_ from XX to XX.  And, the HD is missing records for
-various journals including (but not limited to) the _Journal of Ethnic and
-Cultural Diversity in Social Work_, _Journal of Social Work Disability &
-Rehabilitation_.
-
-### Article attributes
-
-Figures 3a and 3b provide summaries of two important article attributes -- that
-is, the number of authors per article and the length of each article.
-Throughout the history of social work research, at least half of all social
-work articles were sole authored until 2008, as indicated by the median value
-in Figure 3a.  Since 2008, at least half of all articles had two authors.
-Throughout the study time frame, the number of authors has increased steadily,
-as shown by the increasing mean value and its standard deviation.  In 2013, the
-mean number of authors was approximately 2.25, with a standard deviation of
-1.4.  The length of the articles increased steadily from approximately 12 pages
-in 1989 to 15 pages in 2004.  The last three years of the study time frame
-shows a fairly stable publishing trend, with half of all articles being 15
-pages (Mean = XX, sd = XX).
-
-### Abstract analysis
-
-The final set of analyses involved text analysis of the article abstracts to
-determine whether trends in publishing could be readily identified based on the
-frequencies of specific words contained in article abstracts.  In this analysis, we selected words that
-represented different _levels of evidence_ within the evidence-based practices
-framework.  EBP was selected as the focus of analysis, given that the topic
-area is a relatively new in social work, compared to other topics like child
-welfare and case management.  Moreover, because EBP has received considerable
-attention in various areas of social work research, it was expected that
-the different _levels of evidence_ would show should both absolute and
-relative changes in their occurrences.
-
-In this analysis, we focused on four different _levels of evidence_:
-Meta-analysis, systematic reviews, randomized controlled trials (RCTs), and
-quasi-experimental designs.  To identify these key words in the article
-abstracts, we created a set of regular expressions of common spellings and
-synonyms for each type of evidence (see Appendix B).  Regular expressions, also
-referred to as regex and regexp, are sequences of characters that define
-specific patterns in text documents and work much like the _find_ functions
-common to word processors.  The regular expressions used to define the _levels
-of evidence_ are presented in Appendix B and the study's source code.
-
-A stacked line chart was used to show absolute change in the number of
-occurrences for each level of evidence in article abstracts.  The line chart
-shows increased numbers of occurrences for each level of evidence, with the
-greatest amount of growth starting in year 2008.  The presence of systematic
-reviews and meta-analyses did not have a sustained presence in  the literature
-until approximately 1995.  In fact, the first occurrence of the key word
-_systematic review_ did not appear until 1997 (cite).
-
-To show relative change, we plotted the proportion of overall articles
-published that contained the target key words for each year.  In 1989, RCTs and
-Quasi-experimental studies were observed in approximately 1/2% of published
-articles.  By 2013, the percentage of RCTs tripled and the percentage of
-quasi-experimental doubled.  Meta-analyses appeared in 1989 and grew to almost
-1/2% by 2013.  Systematic reviews first appeared in 1997, then again in 2003,
-and grew to approximately 1% in 2013.
-
-**Pareto chart**
 

### 2015-08-17 manuscript.Rmd
Tons of stuff changed. Document cannot process yet.

@@
     select(-attributes, -record)
+
+unique.titles
 ```
@@
 cols = c("Observed Growth" = cp[1], "Estimated 3.2% CAGR" = cp[4], "Estimated 5% CAGR" = cp[3])
-(plot.journal.count <- ggplot(n.journals.year, aes(record.y, 
+
+figure2 <- ggplot(n.journals.year, aes(record.y, 
     y = Journal.count)) + 
@@
     ylab("Journals") + 
-    scale_y_continuous(breaks = c(seq(0, 100, 5)), limits = c(20, 95)) +
-    scale_x_continuous(breaks=seq(1989, 2015, 4)) +
+    scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 95)) +
     theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75)) + 
-    geom_line(aes(x = record.y, y = exp.05, colour = "Estimated 5% CAGR"), data = n.journals.year, colour = cp[2], alpha = .80) +
-    geom_line(aes(x = record.y, y = exp.04, colour = "Estimated 4% CAGR"), data = n.journals.year,  colour = cp[2], alpha = .80)+
-    geom_line(aes(x = record.y, y = exp.03, colour = "Estimated 3% CAGR"), data = n.journals.year,  colour = cp[2], alpha = .80) + 
-    geom_line(aes(colour = "Observed Growth"), colour = cp[4], size = 1.5) 
+    geom_line(aes(x = record.y, y = exp.05, colour = "Estimated 5% CAGR"),
+        data = n.journals.year,   colour = cp[2], alpha = .80) +
+    geom_line(aes(x = record.y, y = exp.04, colour = "Estimated 4% CAGR"), 
+        data = n.journals.year,  colour = cp[2], alpha = .80) +
+    geom_line(aes(colour = "Observed Growth"), colour = cp[4], size = 1.5) + 
+    stat_smooth(method = "lm", se = FALSE, colour = cp[3]) +
+    annotate("text", x = 2016.5, y = 60, label = "Observed growth", size = 5) +
+    annotate("text", x = 2016.5, y = 70, label = "Linear growth\n (slope=1.9)", size = 5) + 
+    annotate("text", x = 2016, y = 76, label = "4% CAGR", size = 5) + 
+    annotate("text", x = 2015.5, y = 95, label = "5% CAGR", size = 5) +
+    scale_x_continuous(limits = c(1989, 2020), breaks = c(1989, 1993, 1997, 2001, 2005, 2009, 2013)) +
+    ggtitle("Figure 2. Observed Versus Estimated Growth of Journals (1989-2013)") + 
+   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
+          panel.border = element_blank(), axis.line = element_line(), 
+          axis.text.x = element_text(size = 16), 
+          axis.text.y = element_text(size = 16), 
+          axis.title.x = element_text(size = 16), 
+          axis.title.y = element_text(size = 16)) +
+    theme(plot.title = element_text(size = 19))
+
 ```
@@
 
-ggplot(annualChange.df, aes(year, annualChange.numeric, fill =annualChange.dichotomous)) + 
+figure3 <- ggplot(annualChange.df, aes(year, annualChange.numeric, fill =annualChange.dichotomous)) + 
     theme_bw() + 
@@
     theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
-          panel.border = element_blank(), axis.line = element_line()) + 
+          panel.border = element_blank(), axis.line = element_line(), 
+          axis.text.x = element_text(size = 16), 
+          axis.text.y = element_text(size = 16), 
+          axis.title.x = element_text(size = 16), 
+          axis.title.y = element_text(size = 16)) + 
     geom_hline(yintercept=0, col="gray", lwd=0.6, alpha =.8) +
-    ggtitle("Annual Percentage Change in the Number of Social Work Journals (1989 - 2013")
+    ggtitle("Figure 3. Annual Percentage Change in the Number Journals (1989 - 2013)") +
+    theme(plot.title = element_text(size = 19))
+
+ggsave("figure3.png", figure3, dpi=250)
 ```
@@
      annotate("segment", x = 1989, xend = 1992, y = 215, yend = 215, colour = "#e66101") + 
-     annotate("segment", x = 1989, xend = 1992, y = 190, yend = 190, colour = "#533c99")
+     annotate("segment", x = 1989, xend = 1992, y = 190, yend = 190, colour = "#533c99") +
+     ggtitle("Figure 1. Number of Article Records by Journal (1989 - 2013)")
 
@@
      annotate("segment", x = 1989, xend = 1992, y = 215, yend = 215, colour = "#e66101") + 
-     annotate("segment", x = 1989, xend = 1992, y = 190, yend = 190, colour = "#533c99")
+     annotate("segment", x = 1989, xend = 1992, y = 190, yend = 190, colour = "#533c99") +
+     ggtitle("Figure 1 (cont.). Number of Article Records by Journal (1989 - 2013)")
 ```
@@
         title = element_text(size = 10), plot.title=element_text(size=10)) + 
-    ylab("Cumulative annual growth rate (%)") + 
+    ylab("Compound annual growth rate (%)") + 
     xlab("") + 
-    ggtitle("Cumulative annual growth rates for \nnumber of published articles (1989 - 1998)") + 
+    ggtitle("Figure 4. Compound annual growth rates for \nnumber of published articles (1989 - 1998)") + 
     theme(plot.title = element_text(size = rel(1.5))) + scale_y_continuous(breaks =
@@
         axis.title.y = element_text(size = 15), 
-        title = element_text(size = 16)
+        title = element_text(size = 13)
         ) + 

### 2015-09-16 functions/fewArticles.R
integrate with package and update objects

@@ -1,36 +1,0 @@
-fewArticles.f <- function(){
-
-    titles <- filter(full.df, attributes == "article")
-    journals <- filter(full.df, attributes == "journal")
-    year <- filter(full.df, attributes == "pubYear")
-
-
-
-    year.journal <- dplyr::intersect(year$articleID, journals$articleID)
-    year.journal.titles <- dplyr::intersect(year.journal, titles$articleID)
-    full.df <- full.df[full.df$articleID %in% year.journal.titles, ]
-
-    exclusions.2 <- filter(full.df, attributes == "journal") %>%
-        group_by(record) %>%
-        summarise(N = n()) %>%
-        arrange(N)
-
-    fewArticles <<- exclusions.2 %>% filter(N <=20)
-
-    exclusions.2 <- exclusions.2[exclusions.2$N <=20, "record"]
-    fewArticles <- exclusions.2$record
-
-
-
-
-
-    ebsco.remove <- full.df[full.df$record %in% fewArticles, ]
-    ebsco.remove <- ebsco.remove[, "articleID"]
-    full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
-
-    author<-filter(full.df, attributes=="author")
-    no.author<-filter(author, grepl("authorship|anonymous", record, ignore.case=TRUE))
-    no.author.ID<-no.author$articleID
-    full.df <<- full.df[!(full.df$articleID %in% no.author.ID),]
-
-}

### 2015-09-17 manuscript.Rmd
update initialization

@@
 
-# Read BWR functions for Mac OS
-source("/Users/beperron/Git/BibWrangleR/functions/proquestBWR.R")
+library(BibWrangleR)
 
@@
 rm(list=ls())
-
-# Read BWR functions for Mac OS
-source("/Users/beperron/Git/BibWrangleR/functions/ebscoBWR.R")
 
@@
 
-```{r BGVinitialization, eval=FALSE}
-rm(list=ls())  
-load("/Users/SSW/Documents/GitHub/SocialWork100Years/socialWorkHistory.Rdata")
-
-# Load required packages
-library(ggplot2)
-library(dplyr)
-library(gridExtra)
-```
-
 ```{r cleaningFunctions, comment=NA, echo=FALSE, eval=TRUE, cache=TRUE}
@@
 source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/fewArticles.R")
+source("/Users/beperron/Git/SocialWorkResearch/functions/requireAuthorJournalTitleYear.R")
 source("/Users/beperron/Git/SocialWorkResearch/functions/pretty.R")
@@
 otherDocuments.f()
-fewArticles.f()
+requireAuthorJournalTitleYear.f()
 #save.image(file = "socialWorkHistory.Rdata")

### 2015-09-17 manuscript.Rmd

@@
 
-proQuestBWR.f(csv=FALSE, path=path)
+proQuestBWR.df <- proQuestBWR.f(csv=FALSE, path=path)
 save(proQuestBWR.df, file = "ProQuest.R")
@@
 
-ebscoBWR.f(csv=FALSE, path=path)
+ebscoBWR.df <- ebscoBWR.f(csv=FALSE, path=path)
 save(ebscoBWR.df, file = "ebscoFULL.R")

### 2015-09-17 functions/journalArticleFinder.R
Major reconfiguring of front-end of processing.

@@ -1,15 +1,0 @@
-journalArticleFinder.f <- function(journalTitle, keyword = FALSE, 
-                                   authorAff = FALSE, abstract = FALSE){
-  article.search <- which(full.df$record == journalTitle)
-  article.search <- full.df[article.search,]
-  article.search.ID <- select(article.search, articleID)
-  target.ID <- full.df$articleID %in% article.search.ID$articleID
-  journal.article.df <- full.df[target.ID, ]
-  journal.article.df <- filter(journal.article.df, attributes == "article")
-  journal.article.df <- arrange(journal.article.df, record)
-  #if(keyword == TRUE){journal.article.df <- filter(journal.article.df, attributes == "keyWord")}
-  #if(authorAff == TRUE){journal.article.df <- filter(journal.article.df, attributes == "authorAff")}
-  #if(abstract == TRUE){journal.article.df <- filter(journal.article.df, attributes == "abstract")}
-  x.shortened <- gsub(" ", "", journalTitle)
-  write.csv(journal.article.df, file = paste0(x.shortened, ".csv"), row.names=F)
-}

### 2015-09-17 testing.R

@@ -1,0 +1,26 @@
+# Set working directory to the location of this file
+
+# Clear workspace
+rm(list=ls())
+
+library(BibWrangleR)
+
+# Wrangle the data files
+proQuestBWR.df <- proQuestBWR.f(csv=FALSE, path='./Data/proQuest')
+ebscoBWR.df <- ebscoBWR.f(csv=FALSE, path='./Data/ebscoFULL')
+
+
+# Load additional functions for cleaning
+sapply(list.files(pattern="[.]R$", path="./functions", full.names=TRUE), source)
+
+# Apply cleaning functions
+combineData.f()
+cleaningJournals.f()
+shortArticles.f()
+titleMatching.f()
+otherDocuments.f()
+requireAuthorJournalTitleYear.f()
+
+# Save historical database as R file
+save(full.df, file = "HistoricalDatabase.R")
+

### 2015-09-17 WrangleTheData.R
Name change to files.

@@ -1,0 +1,28 @@
+# Set working directory to the location of this file
+
+# Clear workspace
+rm(list=ls())
+
+library(BibWrangleR)
+
+# Wrangle the data files
+proQuestBWR.df <- proQuestBWR.f(csv=FALSE, path='./Data/proQuest')
+ebscoBWR.df <- ebscoBWR.f(csv=FALSE, path='./Data/ebscoFULL')
+
+
+# Load additional functions for cleaning
+sapply(list.files(pattern="[.]R$", path="./functions", full.names=TRUE), source)
+
+# Apply cleaning functions
+combineData.f()
+cleaningJournals.f()
+shortArticles.f()
+titleMatching.f()
+otherDocuments.f()
+requireAuthorJournalTitleYear.f()
+
+# Save historical database as R file
+save(full.df, file = "HistoricalDatabase.R")
+
+#save(ebscoBWR.df, file = "EbscoDatabase.R")
+#save(proQuest.df, file = "ProQuest.R")

### 2015-09-17 testing.R

@@ -1,26 +1,0 @@
-# Set working directory to the location of this file
-
-# Clear workspace
-rm(list=ls())
-
-library(BibWrangleR)
-
-# Wrangle the data files
-proQuestBWR.df <- proQuestBWR.f(csv=FALSE, path='./Data/proQuest')
-ebscoBWR.df <- ebscoBWR.f(csv=FALSE, path='./Data/ebscoFULL')
-
-
-# Load additional functions for cleaning
-sapply(list.files(pattern="[.]R$", path="./functions", full.names=TRUE), source)
-
-# Apply cleaning functions
-combineData.f()
-cleaningJournals.f()
-shortArticles.f()
-titleMatching.f()
-otherDocuments.f()
-requireAuthorJournalTitleYear.f()
-
-# Save historical database as R file
-save(full.df, file = "HistoricalDatabase.R")
-

### 2015-09-17 manuscript.Rmd

--- 2015-09-17 manuscript.Rmd
@@
 output: html_document
-header-includes:
-- \usepackage{indentfirst}
-- \usepackage{setspace}
-- \doublespacing
-- \setlength{\parindent}{4em}
 ---
@@
 `r knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, comment=NA)`
+
+```{r LoadDatabase}
+rm(list=ls())
+load("HistoricalDatabase.R")
+
+head(full.df)
+dim(full.df)
+```
 
@@
 
-```{r objectMakerProQuest, warning=FALSE, message=FALSE, eval=FALSE, results='hide', cache=TRUE}
-# Clear workspace
-rm(list=ls())
-
-library(BibWrangleR)
-
-# Set the path where original raw data are stored
-setwd("/Users/beperron/Git/SocialWorkResearch/Data")
-
-# Set the working directory to store files created by BWR functions
-path <- "/Users/beperron/Git/SocialWorkResearch/Data/ProQuest"
-
-# Wrangle the data with the BWR function suite
-
-proQuestBWR.f(csv=FALSE, path=path)
-save(proQuestBWR.df, file = "ProQuest.R")
-```
-
-```{r objectMakerEbscoHost,warning=FALSE, message=FALSE, eval=FALSE, results='hide', cache=TRUE}
-# Clear workspace
-rm(list=ls())
-
-# Set the path where original raw data are stored
-setwd("/Users/beperron/Git/SocialWorkResearch/Data")
-
-# Set the working directory to store files created by BWR functions
-path <- "/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL"
-
-# Wrangle the data with the BWR function suite
-
-ebscoBWR.f(csv=FALSE, path=path)
-save(ebscoBWR.df, file = "ebscoFULL.R")
-```
-
-```{r BEPinitialization, eval=TRUE}
-rm(list=ls())
-
-#load("/Users/beperron/Git/SocialWorkResearch/socialWorkHistory.Rdata")
-
-#Load required packages
-library(ggplot2)
-library(dplyr)
-library(gridExtra)
-```
-
-```{r cleaningFunctions, comment=NA, echo=FALSE, eval=TRUE, cache=TRUE}
-# Read data files
-options(stringsAsFactors = FALSE)
-load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
-load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
-hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
-
-source("/Users/beperron/Git/SocialWorkResearch/functions/combineData.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/cleaningJournals.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticlesRevised.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/requireAuthorJournalTitleYear.R")
-source("/Users/beperron/Git/SocialWorkResearch/functions/pretty.R")
-
-combineData.f()
-cleaningJournals.f()
-shortArticles.f()
-titleMatching.f()
-otherDocuments.f()
-requireAuthorJournalTitleYear.f()
-#save.image(file = "socialWorkHistory.Rdata")
-```
-
-```{r summarySetUp, eval=TRUE, cache=TRUE}
+```{r summarySetUp, eval=FALSE, cache=TRUE}
 unique.titles <- filter(full.df, attributes == "journal") %>%
@@
 
-```{r Figure 1a - Journals, cache=TRUE}
+```{r Figure 1a - Journals, cache=TRUE, eval=FALSE}
 cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
@@
 
-```{r Figure 1b - Journals}
+```{r Figure 1b - Journals, eval=FALSE}
 curr <- n.journals.year$Journal.count[-1]
@@
 
-```{r plot02_SmallMultiples, cache=TRUE}
+```{r plot02_SmallMultiples, eval=FALSE}
 # Remove 2014 & 2015
@@
 
-```{r plot03_AuthorPages, eval=TRUE, cache=FALSE}
+```{r plot03_AuthorPages, eval=FALSE, cache=FALSE}
 
@@
 
+```{r eval=FALSE}
 #----------------------------
@@
 
-```{r CAGR comparison}
+```{r CAGR comparison, eval=FALSE}
 
@@
 
-```{r appendix_A_intersection}
+```{r appendix_A_intersection, eval=FALSE}
 unique.swHistory <- filter(full.df, attributes == "journal") %>%
@@
 
-```{r finalArticleListecho=FALSE, comment=NA}
+```{r finalArticleListecho=FALSE, comment=NA, eval=FALSE}
 #print.data.frame(final.list, row.names=FALSE)
@@
 
-```{r}
-#plotIndex
-```
-
-\newpage
-
-```{r}
+```{r, eval=FALSE}
 grid.arrange(plot.journal.count, plot.article.count, ncol=2)
@@
 \newpage
-```{r fig.height=10, fig.width=7.5}
+```{r fig.height=10, fig.width=7.5, eval=FALSE}
 plotSmallMultiples.1
@@
 \newpage
-```{r fig.height=10, fig.width=7.5}
+```{r fig.height=10, fig.width=7.5, eval=FALSE}
 plotSmallMultiples.2
@@
 
-```{r}
+```{r eval=FALSE}
 
@@
 
-```{r}
+```{r eval=FALSE}
 evidence.plot
@@
 
-```{r}
+```{r eval=FALSE}
 stacked.plot
@@
 \newpage
-```{r}
+```{r eval=FALSE}
 grid.arrange(journal.evidence.plot, propPlot, 
@@
 
-```{r appendix_Print, eval=TRUE}
+```{r appendix_Print, eval=FALSE}
 print(sort(hodge.swHistory.diff))

### 2015-09-17 WrangleTheData.R
switch saved objects to RData format

@@ -22,7 +22,7 @@ otherDocuments.f()
 requireAuthorJournalTitleYear.f()
 
 # Save historical database as R file
-save(full.df, file = "HistoricalDatabase.R")
+save(full.df, file = "HistoricalDatabase.RData")
 
-#save(ebscoBWR.df, file = "EbscoDatabase.R")
-#save(proQuest.df, file = "ProQuest.R")
+#save(ebscoBWR.df, file = "EbscoDatabase.RData")
+#save(proQuest.df, file = "ProQuest.RData")

### 2015-09-17 functions/combineData.R
updates functions to pull in correct years

@@ -10,7 +10,7 @@ combineData.f <- function(){
     full.df <- rbind(ebscoBWR.df, proQuestBWR.df)
 
 
-    year.25 <- as.character(c(1920:1988, 2014, 2015))
+    year.25 <- as.character(c(1910:1988, 2014, 2015))
 
     temp.df <- filter(full.df, attributes == "pubYear")
 

### 2015-09-18 manuscript.Rmd
More cleanup on the repo.

@@
 
-```{r LoadDatabase}
+```{r Initialization}
 rm(list=ls())
-load("HistoricalDatabase.R")
+library(dplyr)
+library(ggplot2)
+library(gridExtra)
+source("./Functions/pretty.R")
 
-head(full.df)
-dim(full.df)
-```
+# Load data files
+load("./Data/HistoricalDatabase.RData")
+hodge.df <- readLines("./Data/hodge.txt", n = -1)
+scopus.df <- read.csv("./Data/scopus.csv")
+abb.df <- read.csv("./Data/master.csv")
+sangam.df <- read.csv("./Data/sangam.csv")
 
-```{r colorThemes}
+# Create colour palette for consistent plotting
 # http://colorbrewer2.org/?type=diverging&scheme=PuOr&n=4
-
 cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
@@
 
-```{r summarySetUp, eval=FALSE, cache=TRUE}
+```{r summarySetUp, eval=TRUE}
 unique.titles <- filter(full.df, attributes == "journal") %>%
@@
 
-```{r Figure 1a - Journals, cache=TRUE, eval=FALSE}
-cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
+```{r Figure 1a - Journals, eval=FALSE}
 
@@
 #=======================================
-library(gridExtra)
 
@@
 figure2 <- ggplot(n.journals.year, aes(record.y, 
-    y = Journal.count)) + 
+    y = Journal.count)) + geom_line()
+
     theme_bw() + 
@@
 # Read Scopus database
-scopus.df <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/scopus.csv")
-scopus.df2 <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/scopus_OldHarvest.csv")
+#scopus.df2 <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/scopus_OldHar#vest.csv")
 
@@
 
- abb <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/master.csv")
  abb$ID <- 1:nrow(abb)
@@
 
-```{r plot03_AuthorPages, eval=FALSE, cache=FALSE}
+```{r plot03_AuthorPages, eval=FALSE}
 
@@
 
-setwd("/Users/beperron/Git/SocialWorkResearch/Data")
-sangam <- read.csv("sangam.csv")
-
 sangam.cumsum <-sangam %>%

### 2015-09-18 manuscript.Rmd
Debugged figures.

--- 2015-09-17 manuscript.Rmd
@@
 
-ggsave("figure3.png", figure3, dpi=250)
+#ggsave("figure3.png", figure3, dpi=250)
 ```
@@
 
- abb <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/master.csv")
- abb$ID <- 1:nrow(abb)
- sm.scopus.merged <- full_join(sm.scopus.merged, abb, by = "Journal") %>% 
+ abb.df$ID <- 1:nrow(abb.df)
+ sm.scopus.merged <- full_join(sm.scopus.merged, abb.df, by = "Journal") %>% 
      select(-X) %>%
@@
  lab <- paste(lab1, lab2, sep="\n")
- xpos = rep(1999, 79)
- ypos = rep(200, 79)
+ xpos = rep(1999, 80)
+ ypos = rep(200, 80)
  ldata <- data.frame(xpos, ypos, lab, Overall.N$Abbrev) %>% 

### 2015-09-18 WrangleTheData.R

@@ -4,6 +4,7 @@
 rm(list=ls())
 
 library(BibWrangleR)
+#library(dplyr)
 
 # Wrangle the data files
 proQuestBWR.df <- proQuestBWR.f(csv=FALSE, path='./Data/proQuest')
@@ -14,6 +15,7 @@ ebscoBWR.df <- ebscoBWR.f(csv=FALSE, path='./Data/ebscoFULL')
 sapply(list.files(pattern="[.]R$", path="./functions", full.names=TRUE), source)
 
 # Apply cleaning functions
+library(dplyr)
 combineData.f()
 cleaningJournals.f()
 shortArticles.f()
@@ -22,7 +24,7 @@ otherDocuments.f()
 requireAuthorJournalTitleYear.f()
 
 # Save historical database as R file
-save(full.df, file = "HistoricalDatabase.RData")
+save(full.df, file = "./Data/HistoricalDatabase.RData")
 
 #save(ebscoBWR.df, file = "EbscoDatabase.RData")
 #save(proQuest.df, file = "ProQuest.RData")

### 2015-09-18 manuscript.Rmd

@@
 ```{r summarySetUp, eval=TRUE}
+
+#=======================================
+# Descriptives
+#=======================================
+
+numberArticles <- length(which(full.df$attributes == "article"))
+
+numberJournals <- filter(full.df, attributes == "journal") %>%
+  summarise(Unique = n_distinct(record))
+
+unique.swHistory <- filter(full.df, attributes == "journal") %>%
+    distinct(record)
+
+hodge.swHistory.intersect <- intersect(hodge.df, unique.swHistory$record)
+
+hodge.swHistory.diff <- setdiff(hodge.df, unique.swHistory$record)
+
+```
+
+```{r Table 1 Journal Summary, eval=TRUE }
+#=======================================
+# Table 1. Journal summary 
+#=======================================
+# Integrate min - max years for each journal
 unique.titles <- filter(full.df, attributes == "journal") %>%
   group_by(record) %>%
-  summarise(N = n())
+  mutate(Hodge = ifelse(record %in% hodge.df == TRUE, "Y", "N")) %>%
+  summarise(N = n(), Hodge.list = max(Hodge))
 
-articles.titleMatching <- length(which(full.df$attributes == "article"))
-
-journals.titleMatching <- filter(full.df, attributes == "journal") %>%
-  summarise(Unique = n_distinct(record))
-
-articles.otherDocuments <- length(which(full.df$attributes == "article"))
-
-journals.otherDocuments <- filter(full.df, attributes == "journal") %>% 
-  summarise(Unique = n_distinct(record))
-
-articles.final <- length(which(full.df$attributes == "article"))
-
-journals.final <- filter(full.df, attributes == "journal") %>% 
-  summarise(Unique = n_distinct(record))
-
-unique.titles <- filter(full.df, attributes == "journal") %>%
-  group_by(record) %>%
-  mutate(Hodge.list = ifelse(record %in% hodge == TRUE, 1, 0)) %>%
-  summarise(N = n(), Hodge.list = max(Hodge.list)) %>%
-  mutate(Hodge = ifelse(Hodge.list == 1, "Y", "N"))
-
-n.so.yr <- filter(full.df, attributes == "journal" | attributes == "pubYear")
-
-n.so <- filter(full.df, attributes == "journal") %>% mutate(title = record) %>% 
-  select(-attributes, -record)
-
-n.yr <- filter(full.df, attributes == "pubYear") %>% mutate(year = record ) %>% 
-  select(-attributes, -record)
-
-unique.titles
 ```
 
-```{r Figure 1a - Journals, eval=FALSE}
-
+```{r Figure 2 Journal Growth, eval = TRUE}
 #=======================================
@@
     theme(plot.title = element_text(size = 19))
-
 ```
 
-```{r Figure 1b - Journals, eval=FALSE}
+```{r Figure 3 Annual Change, eval=FALSE}
 curr <- n.journals.year$Journal.count[-1]
@@
 # Remove 2014 & 2015 
+n.so <- filter(full.df, attributes == "journal") %>% mutate(title = record) %>% 
+  select(-attributes, -record)
+
+n.yr <- filter(full.df, attributes == "pubYear") %>% mutate(year = record ) %>% 
+  select(-attributes, -record)
 
@@
 
-```{r plot03_AuthorPages, eval=FALSE}
-
-#----------------------------
-#Authors
-#----------------------------
-
-year.df <- full.df %>%
-    filter(attributes == "pubYear") %>%
-    select(id = articleID, pubYear = record)
-
-authors.df <- full.df %>%
-    filter(attributes == "author") %>%
-    select(id = articleID, author = record)
-
-n_authors <- authors.df %>%
-    group_by(id) %>%
-    summarise(n=n())
-
-n_authors <- n_authors%>% 
-    left_join(year.df) %>%
-    group_by(pubYear) %>%
-    mutate(n = as.numeric(n)) %>%
-    summarise(median.n = median(n),
-        average.n = mean(n),
-        min.n = min(n),
-        max.n = max(n),
-        std.dev  = sd(n) )
-
-n_authors2 <- n_authors%>% 
-   select(median.n, average.n, std.dev) %>%
-   rename(Median = median.n, Average = average.n, Standard_Deviation =std.dev)
-
-n_authors2$year <- c(1989:2013)
-
-cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
-
-n_authors2.melted <- reshape2::melt(n_authors2, id.vars = c("year", "Standard_Deviation"))
-n_authors3.melted <- filter(n_authors2.melted, variable == "Average")
-
-plot.author.count <- ggplot(n_authors2.melted, aes(x = year, y = value, group=variable, colour = variable)) + 
-    theme_bw() + 
-    geom_line() +
-    geom_point(data = n_authors3.melted, aes(size = Standard_Deviation), colour = "#e66101", alpha=.60) + 
-    #theme(axis.text.x = element_text(angle = 45, hjust = 1), 
-    #title = element_text(size = 10)) +  
-    scale_x_continuous(breaks=c(seq(1989, 2013, 4))) +
-    scale_y_continuous(limits = c(.75,2.5)) +
-    ylab("Number of Authors") +
-    xlab("") +
-    labs(size = "SD = ") +
-    labs(colour = NULL) + 
-    scale_colour_manual(values = c("#fdb864", "#e66101")) +
-    theme(axis.title.x = element_text(vjust=-0.5), 
-          axis.title.y = element_text(vjust=.75), 
-          legend.position = "bottom") + 
-       theme(title = element_text(size = 10)) +
-    theme(axis.text.x = element_text(size=8), 
-    title = element_text(size = 10), plot.title=element_text(size=10)) +
-    theme(legend.text = element_text(size = 8), legend.title = element_text(face="plain"))
-
-n_authors_grouped <- n_authors %>%
-    mutate(n = ifelse(n >= 4, 4, n)) %>%
-    group_by(pubYear) %>%
-    mutate(n.year = n()) %>%
-    group_by(pubYear, n) %>%
-    summarize(N =  n()) %>%
-    group_by(pubYear) %>%
-    mutate(N.year.overall = sum(N)) %>%
-    mutate(N.percent = (N/N.year.overall)*100)
-
-ggplot(n_authors_grouped, aes(pubYear, N.percent, group = n, colour = as.factor(n))) + geom_line(size = 1.5) + 
-    scale_colour_manual(values = cp) +
-    labs(colour = "Number of Authors") + 
-    ylim(c(0,100)) + 
-    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75), 
-          legend.position = "bottom") +
-    theme(axis.text.x = element_text(size=8), 
-    title = element_text(size = 10), plot.title=element_text(size=10))
-
-```
-
-```{r eval=FALSE}
-#----------------------------
-#Pages
-#----------------------------
-
-cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
-pages.tmp <- full.df %>% filter(attributes == "pages")
-years.tmp <- full.df %>% filter(attributes == "pubYear")
-pages.df <- left_join(pages.tmp, years.tmp, by = "articleID") %>% 
-    select(record.y, record.x) %>%
-    rename(years = record.y, pages = record.x) %>%
-    mutate(pages = as.numeric(pages), years = as.numeric(years)) %>%
-    group_by(years) %>%
-    summarise(
-        Median = median(pages, na.rm=TRUE), 
-        Average = mean(pages, na.rm=TRUE),
-        Std.Pages = sd(pages, na.rm=TRUE))
-
-pages.df$years <- c(1989:2013)
-
-pages.df.melted <- reshape2::melt(pages.df, id.vars = c("years", "Std.Pages"))
-
-pages.df2.melted <- filter(pages.df.melted, variable == "Average")
-
-page.plot <- ggplot(pages.df.melted, aes(x = years, y = value, group=variable, colour = variable)) + 
-    geom_line() +
-    geom_point(data = pages.df2.melted, aes(size = Std.Pages), colour = "#5e3c99", alpha = .60) + 
-    theme_bw() + 
-    theme(title = element_text(size = 10)) +  
-    scale_x_continuous(breaks=c(seq(1989, 2013, 4))) +
-    ylab("Number of Pages") +
-    xlab("") +
-    labs(size = "SD = ") +
-     labs(colour = NULL) +   
-    scale_colour_manual(values = c("#b2abd2", "#5e3c99"))  +
-    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75), 
-          legend.position = "bottom") +
-    theme(axis.text.x = element_text(size=8), 
-    title = element_text(size = 10), plot.title=element_text(size=10)) +
-    theme(legend.text = element_text(size = 8), legend.title = element_text(face="plain"))
-
-```
-
-```{r CAGR comparison, eval=FALSE}
+```{r Figure 4 CAGR Comparison, eval=FALSE}
 
@@
 ```
-
-```{r appendix_A_intersection, eval=FALSE}
-unique.swHistory <- filter(full.df, attributes == "journal") %>%
-    distinct(record)
-
-hodge.swHistory.intersect <- intersect(hodge, unique.swHistory$record)
-
-hodge.swHistory.diff <- setdiff(hodge, unique.swHistory$record)
-
-```
-
-\newpage
-
-```{r finalArticleListecho=FALSE, comment=NA, eval=FALSE}
-#print.data.frame(final.list, row.names=FALSE)
-```
-
-\newpage
-
-```{r, eval=FALSE}
-grid.arrange(plot.journal.count, plot.article.count, ncol=2)
-
-```
-\newpage
-```{r fig.height=10, fig.width=7.5, eval=FALSE}
-plotSmallMultiples.1
-
-```
-
-\newpage
-```{r fig.height=10, fig.width=7.5, eval=FALSE}
-plotSmallMultiples.2
-
-```
-
-\newpage
-
-```{r eval=FALSE}
-
-grid.arrange(plot.author.count, page.plot, ncol = 2)
-```
-
-\newpage
-
-```{r eval=FALSE}
-evidence.plot
-```
-\newpage
-
-```{r eval=FALSE}
-stacked.plot
-```
-
-\newpage
-```{r eval=FALSE}
-grid.arrange(journal.evidence.plot, propPlot, 
-        ncol=2, nrow=1, widths=c(2, 1), heights=c(1.4, 4))
-```
-
-\newpage
-
-# Appendix A
-
-Articles on Hodge and Lacasse (2011) but not in the current study.
-
-```{r appendix_Print, eval=FALSE}
-print(sort(hodge.swHistory.diff))
-print(fewArticles)
-```

### 2015-09-19 manuscript.Rmd
Clean up journal titles.Get small multiples working.

@@
 
+unique.year <- filter(full.df, attributes == "pubYear") %>%
+  group_by(record)
+
+n.so <- filter(full.df, attributes == "journal") %>% mutate(title = record) %>% 
+    select(-attributes, -record)
+
+n.yr <- filter(full.df, attributes == "pubYear") %>% mutate(year = record ) %>% 
+    select(-attributes, -record)
+
+n.so.yr <- left_join(n.so, n.yr) %>%
+    group_by(title) %>%
+    summarise(first = min(year), last = max(year), n = n()) %>%
+    arrange(desc(n))
+
+```
+
+```{r Figure 1 Small Multiples, cache=TRUE}
+
+# Create an initial data frame from HD
+sm.df <- left_join(n.so, n.yr) %>%
+    group_by(title, year) %>%
+    summarize(N = n()) %>%
+    mutate(Overall.N = sum(N), year = as.numeric(year)) %>%
+    ungroup() %>%
+    arrange(desc(Overall.N), title) %>%
+    rename(Year = year, Journal= title)
+
+scopus.df$Year <- as.numeric(scopus.df$Year)
+scopus.df <- filter(scopus.df, Year <= 2013)
+
+# Join HD with Scopus and join abbreviation names
+sm.scopus.merged <-full_join(sm.df, scopus.df, by = c("Journal", "Year")) %>%
+    select(Year, Journal, N, Overall.N, Documents)
+
+ sm.scopus.merged.table <- group_by(sm.scopus.merged, Journal) %>%
+     summarize(DataBase.N = sum(N, na.rm=TRUE), Scopus.N = sum(Documents, na.rm=TRUE)) %>%
+     arrange(desc(DataBase.N))
+
+ abb <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/master.csv")
+ abb$ID <- 1:nrow(abb)
+ sm.scopus.merged <- full_join(sm.scopus.merged, abb, by = "Journal") %>% 
+     select(-X) %>%
+     mutate(Documents = ifelse(Documents == 0, NA, Documents))
+
+ # Re-order the factor by Overall.N
+ title <- sm.scopus.merged %>% arrange(desc(Overall.N)) %>% 
+     distinct(Abbrev) %>% filter(!is.na(Abbrev)) %>% distinct()
+
+ title.order = title$Abbrev
+
+ sm.scopus.merged$Abbrev <- factor(sm.scopus.merged$Abbrev, levels = (title.order))
+ sm.scopus.merged <- group_by(sm.scopus.merged, Journal) %>%
+     mutate(Overall.Scopus = sum(Documents, na.rm=TRUE)) %>%
+     ungroup()
+# 
+ # Create labels for the facets
+ Overall.N <- distinct(sm.scopus.merged, Abbrev) 
+ lab1 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.N), sep=""))
+ lab2 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.Scopus), sep=""))
+ lab <- paste(lab1, lab2, sep="\n")
+ xpos = rep(1999, 79)
+ ypos = rep(180, 79)
+ ldata <- data.frame(xpos, ypos, lab, Overall.N$Abbrev) %>% 
+     rename(Abbrev = Overall.N.Abbrev)
+
+ ldata <- na.omit(ldata)
+
+ titles.reduced <- unique(sm.scopus.merged$Journal)
+ titles.reduced.a <- titles.reduced[1:8]
+
+  titles.reduced.1 <- titles.reduced[1:40]
+ titles.reduced.2 <- titles.reduced[41:length(titles.reduced)] 
+ cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
+
+ library(grid)
+ library(gridExtra)
+# Plotting function    
+# 
+reduced.ldata <- ldata[1:8, ]
+
+reduced.ldata$Abbrev <- factor(reduced.ldata$Abbrev, levels = c("Families in Society", "Social Work", "British Journal of Social Work", "Journal of Gerontological Social Work", "Research on Social Work Practice", "Social Work in Health Care", "International Social Work", "Health & Social Work") )
+
+reduced.ldata$Abbrev = c("Families in Society", "Social Work", "British Journal of Social Work", "Journal of Gerontological Social Work", "Research on Social Work Practice", "Social Work in Health Care", "International Social Work", "Health & Social Work")
+reduced.smallmult.df <- sm.scopus.merged
+reduced.smallmult.df$Abbrev <- reduced.smallmult.df$Journal
+reduced.smallmult.df <- na.omit(reduced.smallmult.df)
+
+reduced.smallmult.df$Abbrev <- as.factor(reduced.smallmult.df$Abbrev)
+reduced.smallmult.df$Abbrev <- factor(reduced.smallmult.df$Abbrev, levels = c("Families in Society", "Social Work", "British Journal of Social Work", "Journal of Gerontological Social Work", "Research on Social Work Practice", "Social Work in Health Care", "International Social Work", "Health & Social Work") )
+
+ plotSmallMultiples.a <-  ggplot(reduced.smallmult.df[reduced.smallmult.df$Abbrev %in% titles.reduced.a, ],  aes(Year, N)) +
+     geom_line(colour="#e66101") +
+     geom_line(data = reduced.smallmult.df[reduced.smallmult.df$Abbrev %in% titles.reduced.a, ], 
+               aes(Year, Documents), colour = "#533c99", alpha = .80) + 
+     facet_wrap(~ Abbrev) + 
+      geom_text(data = reduced.ldata, aes(x =xpos, y = ypos, label = lab), size = 5) +
+     theme_bw() +
+     theme(strip.text.x = element_text(size = 12)) + 
+     theme(legend.position = "bottom", 
+     panel.grid.minor = element_blank(), 
+     axis.text.x = element_text(angle=45, hjust=1, size = 10)) +
+     ylim(c(0,225)) +
+     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
+     annotate("segment", x = 1992, xend = 1995, y = 190, yend = 190, colour = "#e66101") + 
+     annotate("segment", x = 1992, xend = 1995, y = 170, yend = 170, colour = "#533c99") 
+     #ggtitle("Figure 1. Comparison of Historical Database with Scopus\n for Journals with Highest Output (1989 - 2013)") + 
+     # theme(plot.title = element_text(size = 19))
+     # 
+#ggsave(file = "scopusComparison.png", plotSmallMultiples.a)
+
+ plotSmallMultiples.1 <-  ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.1, ],  aes(Year, N)) +
+     geom_line(colour="#e66101") +
+     geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.1, ], aes(Year, Documents), colour = "#533c99", alpha = .80) + 
+     facet_wrap(~ Abbrev) + 
+     theme_bw() +
+     theme(strip.text.x = element_text(size = 12)) + 
+     theme(legend.position = "bottom", 
+     panel.grid.minor = element_blank(), 
+     axis.text.x = element_text(angle=45, hjust=1, size = 10)) + 
+     geom_text(data = ldata[1:40, ], aes(x =xpos, y = ypos, label = lab), size = 4) +
+     ylim(c(0,225)) +
+     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
+     annotate("segment", x = 1989, xend = 1992, y = 215, yend = 215, colour = "#e66101") + 
+     annotate("segment", x = 1989, xend = 1992, y = 150, yend = 150, colour = "#533c99") +
+     ggtitle("Figure 1. Number of Article Records by Journal (1989 - 2013)")
+
+plotSmallMultiples.2 <- ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ],  
+     aes(Year, N)) +
+     geom_line(colour="#e66101") +
+     geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ], 
+     aes(Year, Documents), colour = "#533c99", alpha = .80) + 
+     facet_wrap(~ Abbrev) + 
+     theme_bw() +
+     theme(strip.text.x = element_text(size = 12)) +  
+     theme(legend.position = "bottom", 
+     panel.grid.minor = element_blank(), 
+     axis.text.x = element_text(angle=45, hjust=1, size =10)) + 
+     geom_text(data = ldata[41:79, ], aes(x =xpos, y = ypos, label = lab), size =4) +
+     ylim(c(0,225)) +
+     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
+     annotate("segment", x = 1989, xend = 1992, y = 215, yend = 215, colour = "#e66101") + 
+     annotate("segment", x = 1989, xend = 1992, y = 190, yend = 190, colour = "#533c99") +
+     ggtitle("Figure 1 (cont.). Number of Article Records by Journal (1989 - 2013)")
 ```

### 2015-09-19 functions/cleaningJournals.R

@@ -76,7 +76,7 @@ cleaningJournals.f <- function(){
                              "Social Work With Groups",
                              full.df$record)
     full.df$record <- ifelse(full.df$record ==
-                                 "Maatskaplike Werk/Social Work",
+                                 "Maatskaplike Werk/Social Work" | full.df$record == "Social Work/Maatskaplike Werk",
                              "Maatskaplike Werk",
                              full.df$record)
 
@@ -179,7 +179,7 @@ cleaningJournals.f <- function(){
                 full.df$record == "Journal of Practice Teaching in Social Work and Health", #Old title
                "Journal of Practice Teaching in Social Work & Health",   #New title
                 full.df$record)
-    
+
     full.df$record <- ifelse(full.df$record==
                                "Human Services in the Rural Environment",
                                "Contemporary Rural Social Work",
@@ -203,6 +203,7 @@ cleaningJournals.f <- function(){
         "Brain & Cognition",
         "Canadian Journal of Community Mental Health",
         "Canadian Journal on Aging",
+        "Critical Social Work", # Problematic record in database - not formally indexed
         "Early Child Development and Care",
         "Early Child Development & Care",
         "Early Education and Development",
@@ -212,6 +213,8 @@ cleaningJournals.f <- function(){
         "Evaluation & Program Planning",
         "General Hospital Psychiatry",
         "International Review of Social Research",
+        "Issues in Social Work Education", #Problematic record in database - not formally indexed
+        "Iowa Journal of School Social Work", #Problematic record in database - not formally indexed
         "Journal of Applied Behavioral Science",
         "Journal of Applied Rehabilitation Counseling",
         "Journal of Community & Applied Social Psychology",
@@ -231,7 +234,8 @@ cleaningJournals.f <- function(){
         "The Scientific Review of Mental Health Practice",
         "The Clinical Supervisor",
         "Arete: Revista de Filosofia",
-        "Arete Revista de Filosofia")
+        "Arete Revista de Filosofia",
+        "Profile")
 
 
     ebsco.remove <- full.df[full.df$record %in% exclusions.1, ]

### 2015-09-19 manuscript.Rmd
Fixed first small multiples plot after finding bug. Reformatting needed and updates to large small multiples necessary.

@@
 
+# Read Scopus data
 scopus.df$Year <- as.numeric(scopus.df$Year)
@@
 
-# Join HD with Scopus and join abbreviation names
+# Join with historical database
 sm.scopus.merged <-full_join(sm.df, scopus.df, by = c("Journal", "Year")) %>%
@@
 
- sm.scopus.merged.table <- group_by(sm.scopus.merged, Journal) %>%
+sm.scopus.merged-counts <- group_by(sm.scopus.merged, Journal) %>%
      summarize(DataBase.N = sum(N, na.rm=TRUE), Scopus.N = sum(Documents, na.rm=TRUE)) %>%
@@
 
- plotSmallMultiples.a <-  ggplot(reduced.smallmult.df[reduced.smallmult.df$Abbrev %in% titles.reduced.a, ],  aes(Year, N)) +
+new.data <- reduced.smallmult.df[reduced.smallmult.df$Abbrev %in% titles.reduced.a, ]
+new.data
+
+ plotSmallMultiples.a <-  ggplot(new.data,  aes(Year, N)) +
      geom_line(colour="#e66101") +
-     geom_line(data = reduced.smallmult.df[reduced.smallmult.df$Abbrev %in% titles.reduced.a, ], 
+     geom_line(data = reduced.smallmult.df[reduced.smallmult.df$Journal %in% titles.reduced.a, ], 
                aes(Year, Documents), colour = "#533c99", alpha = .80) + 

### 2015-09-19 manuscript.Rmd
Forgot to save before push.

@@
 
+lab1 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.N), sep=""))
+lab2 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.Scopus), sep=""))
+
+sm.df.reduced <- sm.df %>% select(-Overall.N)
+
 # Read Scopus data
@@
 scopus.df <- filter(scopus.df, Year <= 2013)
+
+DataBase <- rep("Scopus", nrow(scopus.df))
+scopus.df$DataBase <- DataBase
+scopus.df$Documents <- ifelse(scopus.df$Documents == 0, NA, scopus.df$Documents)
+
+DataBase <- rep("HD", nrow(sm.df.reduced))
+sm.df.reduced$DataBase <- DataBase
+sm.df.reduced <- sm.df.reduced %>% rename(Documents = N) 
+sm.df.reduced$Documents <- ifelse(sm.df.reduced$Documents == 0, NA, sm.df.reduced$Documents)  
+sm.df.reduced <- na.omit(sm.df.reduced)
+
+combined <- rbind(scopus.df, sm.df.reduced)
+combined_reduced <- combined[combined$Journal %in% c("Families in Society", "Social Work", "British Journal of Social Work", "Journal of Gerontological Social Work", "Research on Social Work Practice", "Social Work in Health Care", "International Social Work", "Health & Social Work", "Journal of Social Work Education"), ]
+
+ggplot(combined_reduced,  aes(Year, Documents, colour = DataBase)) +
+     geom_line() + 
+     facet_wrap(~ Journal)
 

### 2015-09-19 manuscript.Rmd
Fixed small multiples. One minor edit still needed.

@@
 
+combined_reduced$Journal <- factor(combined_reduced$Journal, levels = c("Families in Society", "Social Work", "British Journal of Social Work", "Journal of Gerontological Social Work", "Research on Social Work Practice", "Social Work in Health Care", "International Social Work", "Health & Social Work", "Journal of Social Work Education") )
+
+# Create labels for the facets
+journalOutput <- distinct(sm.scopus.merged, Journal)
+
+ann_scopus <- select(journalOutput, Journal, Overall.N)
+ann_scopus <- ann_scopus[1:9, ]
+ann_scopus$label <- paste0("N=", pretty(ann_scopus$Overall.N))
+
 ggplot(combined_reduced,  aes(Year, Documents, colour = DataBase)) +
-     geom_line() + 
-     facet_wrap(~ Journal)
+     geom_line(size = 1, alpha = .80) + 
+     facet_wrap(~ Journal) +
+     theme(strip.text.x = element_text(size = 2.5)) +
+  theme_bw() + 
+  theme(legend.position = "bottom", legend.text = element_text(size = 12)) + 
+     scale_colour_discrete(guide = guide_legend(title = "Database"), breaks = c("HD", "Scopus"), labels = c("Historical Database", "Scopus")) + 
+  scale_colour_manual(values = c(cp[2], cp[4]), labels = c("Historical Database", "Scopus"), guide = guide_legend(title = "")) + 
+  ylab("Number of Articles") + 
+  xlab("\nYear") +
+     annotate("segment", x = 1992, xend = 1995, y = 190, yend = 190, colour = cp[2], size = 1, alpha = .80) + 
+     annotate("segment", x = 1992, xend = 1995, y = 170, yend = 170, colour = cp[4], size = 1, alpha = .80) +
+   geom_text(data = ann_scopus, aes(x = 1999, y =  170, label = label), colour = "black", size = 4)
 
@@
  ypos = rep(180, 79)
- ldata <- data.frame(xpos, ypos, lab, Overall.N$Abbrev) %>% 
-     rename(Abbrev = Overall.N.Abbrev)
+ ldata <- data.frame(xpos, ypos, lab, Overall.N$Journal)
 
@@
                aes(Year, Documents), colour = "#533c99", alpha = .80) +
+
      facet_wrap(~ Abbrev) + 

### 2015-09-20 manuscript.Rmd
Small multiples for paper working. Not fully consistent with larger supplements.

@@
 
-lab1 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.N), sep=""))
-lab2 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.Scopus), sep=""))
-
 sm.df.reduced <- sm.df %>% select(-Overall.N)
 
-# Read Scopus data
-scopus.df$Year <- as.numeric(scopus.df$Year)
-scopus.df <- filter(scopus.df, Year <= 2013)
-
-DataBase <- rep("Scopus", nrow(scopus.df))
-scopus.df$DataBase <- DataBase
-scopus.df$Documents <- ifelse(scopus.df$Documents == 0, NA, scopus.df$Documents)
-
+scopus.df$DataBase <- rep("Scopus", nrow(scopus.df))
 DataBase <- rep("HD", nrow(sm.df.reduced))
@@
 
-# Create labels for the facets
-journalOutput <- distinct(sm.scopus.merged, Journal)
+# Create Scopus labels for the facets
 
-ann_scopus <- select(journalOutput, Journal, Overall.N)
-ann_scopus <- ann_scopus[1:9, ]
-ann_scopus$label <- paste0("N=", pretty(ann_scopus$Overall.N))
+scopus.df$Year <- as.numeric(scopus.df$Year)
+scopus.df <- filter(scopus.df, Year <= 2013)
+scopus.df$Year <- as.numeric(scopus.df$Year)
+scopus_annotate <- filter(scopus.df, Year <= 2013) %>%
+  group_by(Journal) %>%
+  summarize(N = pretty(sum(Documents)))
+
+scopus_annotate_paper <-scopus_annotate[scopus_annotate$Journal %in% combined_reduced$Journal, ]
+scopus_annotate_paper$label <- paste0("N=", pretty(scopus_annotate_paper$N))
+
+# Create HD Labels for the facets
+hd_annotate <- combined_reduced %>% 
+  filter(DataBase == "HD") %>%
+  group_by(Journal) %>%
+  summarize(N = sum(Documents))%>%
+  mutate(label = paste0("N=", pretty(N)))
 
@@
   xlab("\nYear") +
-     annotate("segment", x = 1992, xend = 1995, y = 190, yend = 190, colour = cp[2], size = 1, alpha = .80) + 
-     annotate("segment", x = 1992, xend = 1995, y = 170, yend = 170, colour = cp[4], size = 1, alpha = .80) +
-   geom_text(data = ann_scopus, aes(x = 1999, y =  170, label = label), colour = "black", size = 4)
+     annotate("segment", x = 1992, xend = 1995, y = 140, yend = 140, colour = cp[2], size = 1, alpha = .80) + 
+     annotate("segment", x = 1992, xend = 1995, y = 120, yend = 120, colour = cp[4], size = 1, alpha = .80) +
+   geom_text(data = scopus_annotate_paper, aes(x = 1999, y =  120, label = label), colour = "black", size = 4) +
+  geom_text(data = hd_annotate, aes(x = 1999, y =  140, label = label), colour = "black", size = 4)
 

### 2015-09-20 manuscript.Rmd

@@
 
-```{r Figure 1 Small Multiples, cache=TRUE}
+```{r Figure 1 Small Multiples Paper}
 
@@
      facet_wrap(~ Journal) +
-     theme(strip.text.x = element_text(size = 2.5)) +
   theme_bw() + 
+   theme(strip.text.x = element_text(size = 12)) +
   theme(legend.position = "bottom", legend.text = element_text(size = 12)) + 
@@
 
-# Join with historical database
-sm.scopus.merged <-full_join(sm.df, scopus.df, by = c("Journal", "Year")) %>%
-    select(Year, Journal, N, Overall.N, Documents)
+```
 
-sm.scopus.merged-counts <- group_by(sm.scopus.merged, Journal) %>%
-     summarize(DataBase.N = sum(N, na.rm=TRUE), Scopus.N = sum(Documents, na.rm=TRUE)) %>%
-     arrange(desc(DataBase.N))
+```{r Figure 1 Small Multiples Supplement}
 
- abb$ID <- 1:nrow(abb)
- sm.scopus.merged <- full_join(sm.scopus.merged, abb, by = "Journal") %>% 
-     select(-X) %>%
-     mutate(Documents = ifelse(Documents == 0, NA, Documents))
-
- # Re-order the factor by Overall.N
- title <- sm.scopus.merged %>% arrange(desc(Overall.N)) %>% 
-     distinct(Abbrev) %>% filter(!is.na(Abbrev)) %>% distinct()
-
- title.order = title$Abbrev
-
- sm.scopus.merged$Abbrev <- factor(sm.scopus.merged$Abbrev, levels = (title.order))
- sm.scopus.merged <- group_by(sm.scopus.merged, Journal) %>%
-     mutate(Overall.Scopus = sum(Documents, na.rm=TRUE)) %>%
-     ungroup()
-# 
- # Create labels for the facets
- Overall.N <- distinct(sm.scopus.merged, Abbrev) 
- lab1 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.N), sep=""))
- lab2 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.Scopus), sep=""))
- lab <- paste(lab1, lab2, sep="\n")
- xpos = rep(1999, 79)
- ypos = rep(180, 79)
- ldata <- data.frame(xpos, ypos, lab, Overall.N$Journal)
-
- ldata <- na.omit(ldata)
-
- titles.reduced <- unique(sm.scopus.merged$Journal)
- titles.reduced.a <- titles.reduced[1:8]
-
-  titles.reduced.1 <- titles.reduced[1:40]
- titles.reduced.2 <- titles.reduced[41:length(titles.reduced)] 
- cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
-
- library(grid)
- library(gridExtra)
-# Plotting function    
-# 
-reduced.ldata <- ldata[1:8, ]
-
-reduced.ldata$Abbrev <- factor(reduced.ldata$Abbrev, levels = c("Families in Society", "Social Work", "British Journal of Social Work", "Journal of Gerontological Social Work", "Research on Social Work Practice", "Social Work in Health Care", "International Social Work", "Health & Social Work") )
-
-reduced.ldata$Abbrev = c("Families in Society", "Social Work", "British Journal of Social Work", "Journal of Gerontological Social Work", "Research on Social Work Practice", "Social Work in Health Care", "International Social Work", "Health & Social Work")
-reduced.smallmult.df <- sm.scopus.merged
-reduced.smallmult.df$Abbrev <- reduced.smallmult.df$Journal
-reduced.smallmult.df <- na.omit(reduced.smallmult.df)
-
-reduced.smallmult.df$Abbrev <- as.factor(reduced.smallmult.df$Abbrev)
-reduced.smallmult.df$Abbrev <- factor(reduced.smallmult.df$Abbrev, levels = c("Families in Society", "Social Work", "British Journal of Social Work", "Journal of Gerontological Social Work", "Research on Social Work Practice", "Social Work in Health Care", "International Social Work", "Health & Social Work") )
-
-new.data <- reduced.smallmult.df[reduced.smallmult.df$Abbrev %in% titles.reduced.a, ]
-new.data
-
- plotSmallMultiples.a <-  ggplot(new.data,  aes(Year, N)) +
-     geom_line(colour="#e66101") +
-     geom_line(data = reduced.smallmult.df[reduced.smallmult.df$Journal %in% titles.reduced.a, ], 
-               aes(Year, Documents), colour = "#533c99", alpha = .80) +
-
-     facet_wrap(~ Abbrev) + 
-    geom_text(data = reduced.ldata, aes(x =xpos, y = ypos, label = lab), size = 5) +
-     theme_bw() +
-     theme(strip.text.x = element_text(size = 12)) + 
-     theme(legend.position = "bottom", 
-     panel.grid.minor = element_blank(), 
-     axis.text.x = element_text(angle=45, hjust=1, size = 10)) +
-     ylim(c(0,225)) +
-     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
-     annotate("segment", x = 1992, xend = 1995, y = 190, yend = 190, colour = "#e66101") + 
-     annotate("segment", x = 1992, xend = 1995, y = 170, yend = 170, colour = "#533c99") 
-     #ggtitle("Figure 1. Comparison of Historical Database with Scopus\n for Journals with Highest Output (1989 - 2013)") + 
-     # theme(plot.title = element_text(size = 19))
-     # 
-#ggsave(file = "scopusComparison.png", plotSmallMultiples.a)
-
- plotSmallMultiples.1 <-  ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.1, ],  aes(Year, N)) +
-     geom_line(colour="#e66101") +
-     geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.1, ], aes(Year, Documents), colour = "#533c99", alpha = .80) + 
-     facet_wrap(~ Abbrev) + 
-     theme_bw() +
-     theme(strip.text.x = element_text(size = 12)) + 
-     theme(legend.position = "bottom", 
-     panel.grid.minor = element_blank(), 
-     axis.text.x = element_text(angle=45, hjust=1, size = 10)) + 
-     geom_text(data = ldata[1:40, ], aes(x =xpos, y = ypos, label = lab), size = 4) +
-     ylim(c(0,225)) +
-     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
-     annotate("segment", x = 1989, xend = 1992, y = 215, yend = 215, colour = "#e66101") + 
-     annotate("segment", x = 1989, xend = 1992, y = 150, yend = 150, colour = "#533c99") +
-     ggtitle("Figure 1. Number of Article Records by Journal (1989 - 2013)")
-
-plotSmallMultiples.2 <- ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ],  
-     aes(Year, N)) +
-     geom_line(colour="#e66101") +
-     geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ], 
-     aes(Year, Documents), colour = "#533c99", alpha = .80) + 
-     facet_wrap(~ Abbrev) + 
-     theme_bw() +
-     theme(strip.text.x = element_text(size = 12)) +  
-     theme(legend.position = "bottom", 
-     panel.grid.minor = element_blank(), 
-     axis.text.x = element_text(angle=45, hjust=1, size =10)) + 
-     geom_text(data = ldata[41:79, ], aes(x =xpos, y = ypos, label = lab), size =4) +
-     ylim(c(0,225)) +
-     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
-     annotate("segment", x = 1989, xend = 1992, y = 215, yend = 215, colour = "#e66101") + 
-     annotate("segment", x = 1989, xend = 1992, y = 190, yend = 190, colour = "#533c99") +
-     ggtitle("Figure 1 (cont.). Number of Article Records by Journal (1989 - 2013)")
 ```

### 2015-09-20 manuscript.Rmd
Fixed larger small multiples set.

@@
 ```{r Figure 1 Small Multiples Supplement}
+# Create an initial data frame from HD
+sm.df <- left_join(n.so, n.yr) %>%
+    group_by(title, year) %>%
+    summarize(N = n()) %>%
+    mutate(Overall.N = sum(N), year = as.numeric(year)) %>%
+    ungroup() %>%
+    arrange(desc(Overall.N), title) %>%
+    rename(Year = year, Journal= title)
 
+# Read Scopus database
+scopus.df <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/scopus.csv")
+scopus.df2 <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/scopus_OldHarvest.csv")
+
+scopus.df$Year <- as.numeric(scopus.df$Year)
+scopus.df <- filter(scopus.df, Year <= 2013)
+
+# Join HD with Scopus and join abbreviation names
+sm.scopus.merged <-full_join(sm.df, scopus.df, by = c("Journal", "Year")) %>%
+    select(Year, Journal, N, Overall.N, Documents)
+
+ sm.scopus.merged.table <- group_by(sm.scopus.merged, Journal) %>%
+     summarize(DataBase.N = sum(N, na.rm=TRUE), Scopus.N = sum(Documents, na.rm=TRUE)) %>%
+     arrange(desc(DataBase.N))
+
+ abb <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/master.csv")
+ abb$ID <- 1:nrow(abb)
+ sm.scopus.merged <- full_join(sm.scopus.merged, abb, by = "Journal") %>% 
+     select(-X) %>%
+     mutate(Documents = ifelse(Documents == 0, NA, Documents))
+
+ # Re-order the factor by Overall.N
+ title <- sm.scopus.merged %>% arrange(desc(Overall.N)) %>% 
+     distinct(Abbrev) %>% filter(!is.na(Abbrev)) %>% distinct()
+
+ title.order = title$Abbrev
+
+ sm.scopus.merged$Abbrev <- factor(sm.scopus.merged$Abbrev, levels = (title.order))
+ sm.scopus.merged <- group_by(sm.scopus.merged, Journal) %>%
+     mutate(Overall.Scopus = sum(Documents, na.rm=TRUE)) %>%
+     ungroup()
+# 
+ # Create labels for the facets
+ Overall.N <- distinct(sm.scopus.merged, Abbrev) 
+ lab1 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.N), sep=""))
+ lab2 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.Scopus), sep=""))
+ lab <- paste(lab1, lab2, sep="\n")
+ xpos = rep(1999, 79)
+ ypos = rep(200, 79)
+ ldata <- data.frame(xpos, ypos, lab, Overall.N$Abbrev) %>% 
+     rename(Abbrev = Overall.N.Abbrev)
+
+ ldata <- na.omit(ldata)
+
+ titles.reduced <- unique(sm.scopus.merged$Journal)
+ titles.reduced.1 <- titles.reduced[1:40]
+ titles.reduced.2 <- titles.reduced[41:length(titles.reduced)] 
+ cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
+
+ library(grid)
+ library(gridExtra)
+# Plotting function    
+# 
+ plotSmallMultiples.1 <-  ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.1, ],  aes(Year, N)) +
+     geom_line(colour="#e66101") +
+     geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.1, ], aes(Year, Documents), colour = "#533c99", alpha = .80) + 
+     facet_wrap(~ Abbrev) + 
+     theme_bw() +
+     theme(strip.text.x = element_text(size = 8)) + 
+     theme(legend.position = "bottom", 
+     panel.grid.minor = element_blank(), 
+     axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
+     geom_text(data = ldata[1:40, ], aes(x =xpos, y = ypos, label = lab), size =2.5) +
+     ylim(c(0,225)) +
+     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
+     annotate("segment", x = 1989, xend = 1992, y = 215, yend = 215, colour = "#e66101") + 
+     annotate("segment", x = 1989, xend = 1992, y = 190, yend = 190, colour = "#533c99") +
+     ggtitle("Figure 1. Number of Article Records by Journal (1989 - 2013)")
+
+plotSmallMultiples.2 <- ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ],  
+     aes(Year, N)) +
+     geom_line(colour="#e66101") +
+     geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ], 
+     aes(Year, Documents), colour = "#533c99", alpha = .80) + 
+     facet_wrap(~ Abbrev) + 
+     theme_bw() +
+     theme(strip.text.x = element_text(size = 8)) +  
+     theme(legend.position = "bottom", 
+     panel.grid.minor = element_blank(), 
+     axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
+     geom_text(data = ldata[41:79, ], aes(x =xpos, y = ypos, label = lab), size =2.5) +
+     ylim(c(0,225)) +
+     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
+     annotate("segment", x = 1989, xend = 1992, y = 215, yend = 215, colour = "#e66101") + 
+     annotate("segment", x = 1989, xend = 1992, y = 190, yend = 190, colour = "#533c99") +
+     ggtitle("Figure 1 (cont.). Number of Article Records by Journal (1989 - 2013)")
 ```

### 2015-09-20 manuscript.Rmd

@@
 sangam.df <- read.csv("./Data/sangam.csv")
+proquest_summary.df <- read.csv("./Data/proquest_summary.csv")
 
@@
 ```
+
+```{r}
+
+library(lubridate)
+head(proquest_summary.df)
+pq_summary <- proquest_summary.df
+
+pq_summaryas.character(pq_summary$Citation.First)
+
+  ifelse(proquest_summary.df$Citation.First == "Current", "9/19/15", proquest_summary.df$Citation.First)
+
+proquest_summary.df$Citation.Last <- ifelse(proquest_summary.df$Abstract.Last == "Current", "9/19/15", proquest_summary.df$Citation.Last)
+
+```

### 2015-09-23 manuscript.Rmd
Added and merged historical title for The Social Worker. Wrangled new data. Code is functioning.

--- 2015-09-20 manuscript.Rmd
@@
 ```{r Figure 1 Small Multiples Supplement}
+# Create an initial data frame from HD
+sm.df <- left_join(n.so, n.yr) %>%
+    group_by(title, year) %>%
+    summarize(N = n()) %>%
+    mutate(Overall.N = sum(N), year = as.numeric(year)) %>%
+    ungroup() %>%
+    arrange(desc(Overall.N), title) %>%
+    rename(Year = year, Journal= title)
 
+scopus.df$Year <- as.numeric(scopus.df$Year)
+scopus.df <- filter(scopus.df, Year <= 2013)
+
+# Join HD with Scopus and join abbreviation names
+sm.scopus.merged <-full_join(sm.df, scopus.df, by = c("Journal", "Year")) %>%
+    select(Year, Journal, N, Overall.N, Documents)
+
+ sm.scopus.merged.table <- group_by(sm.scopus.merged, Journal) %>%
+     summarize(DataBase.N = sum(N, na.rm=TRUE), Scopus.N = sum(Documents, na.rm=TRUE)) %>%
+     arrange(desc(DataBase.N))
+
+ abb <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/master.csv")
+ abb$ID <- 1:nrow(abb)
+ sm.scopus.merged <- full_join(sm.scopus.merged, abb, by = "Journal") %>% 
+     select(-X) %>%
+     mutate(Documents = ifelse(Documents == 0, NA, Documents))
+
+ # Re-order the factor by Overall.N
+ title <- sm.scopus.merged %>% arrange(desc(Overall.N)) %>% 
+     distinct(Abbrev) %>% filter(!is.na(Abbrev)) %>% distinct()
+
+ title.order = title$Abbrev
+
+ sm.scopus.merged$Abbrev <- factor(sm.scopus.merged$Abbrev, levels = (title.order))
+ sm.scopus.merged <- group_by(sm.scopus.merged, Journal) %>%
+     mutate(Overall.Scopus = sum(Documents, na.rm=TRUE)) %>%
+     ungroup()
+# 
+ # Create labels for the facets
+ Overall.N <- distinct(sm.scopus.merged, Abbrev) 
+ lab1 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.N), sep=""))
+ lab2 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.Scopus), sep=""))
+ lab <- paste(lab1, lab2, sep="\n")
+ xpos = rep(1999, 80)
+ ypos = rep(200, 80)
+ ldata <- data.frame(xpos, ypos, lab, Overall.N$Abbrev) %>% 
+     rename(Abbrev = Overall.N.Abbrev)
+
+ ldata <- na.omit(ldata)
+
+ titles.reduced <- unique(sm.scopus.merged$Journal)
+ titles.reduced.1 <- titles.reduced[1:40]
+ titles.reduced.2 <- titles.reduced[41:length(titles.reduced)] 
+ cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
+
+ library(grid)
+ library(gridExtra)
+# Plotting function    
+# 
+ plotSmallMultiples.1 <-  ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.1, ],  aes(Year, N)) +
+     geom_line(colour="#e66101") +
+     geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.1, ], aes(Year, Documents), colour = "#533c99", alpha = .80) + 
+     facet_wrap(~ Abbrev) + 
+     theme_bw() +
+     theme(strip.text.x = element_text(size = 8)) + 
+     theme(legend.position = "bottom", 
+     panel.grid.minor = element_blank(), 
+     axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
+     geom_text(data = ldata[1:40, ], aes(x =xpos, y = ypos, label = lab), size =2.5) +
+     ylim(c(0,225)) +
+     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
+     annotate("segment", x = 1989, xend = 1992, y = 215, yend = 215, colour = "#e66101") + 
+     annotate("segment", x = 1989, xend = 1992, y = 190, yend = 190, colour = "#533c99") +
+     ggtitle("Figure 1. Number of Article Records by Journal (1989 - 2013)")
+
+plotSmallMultiples.2 <- ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ],  
+     aes(Year, N)) +
+     geom_line(colour="#e66101") +
+     geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ], 
+     aes(Year, Documents), colour = "#533c99", alpha = .80) + 
+     facet_wrap(~ Abbrev) + 
+     theme_bw() +
+     theme(strip.text.x = element_text(size = 8)) +  
+     theme(legend.position = "bottom", 
+     panel.grid.minor = element_blank(), 
+     axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
+     geom_text(data = ldata[41:79, ], aes(x =xpos, y = ypos, label = lab), size =2.5) +
+     ylim(c(0,225)) +
+     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
+     annotate("segment", x = 1989, xend = 1992, y = 215, yend = 215, colour = "#e66101") + 
+     annotate("segment", x = 1989, xend = 1992, y = 190, yend = 190, colour = "#533c99") +
+     ggtitle("Figure 1 (cont.). Number of Article Records by Journal (1989 - 2013)")
 ```
 
-```{r Figure 2 Journal Growth, eval = TRUE}
+```{r Figure 2 Journal Growth, eval = FALSE}
 #=======================================
@@
  ypos = rep(200, 80)
+
+ Overall.N <- distinct(sm.df, Journal)
+
  ldata <- data.frame(xpos, ypos, lab, Overall.N$Abbrev) %>% 

### 2015-09-23 functions/cleaningJournals.R

@@ -113,6 +113,7 @@ cleaningJournals.f <- function(){
                              full.df$record)
 
 
+
     #shortens Professional Development
     full.df$record <- ifelse(full.df$attributes == "journal",
                              gsub(":.+", "", full.df$record),
@@ -184,6 +185,12 @@ cleaningJournals.f <- function(){
                                "Human Services in the Rural Environment",
                                "Contemporary Rural Social Work",
                                 full.df$record)
+
+    full.df$record <- ifelse(full.df$record ==
+                               "The Social Worker/Le Travailleur social",          # Title Change
+                             "The Social Worker",
+                             full.df$record)
+
 
     # Journals were originally merged after suffixes were eliminated (after the
     # colon).  Thus, Practice: Social Work in Action  (new title) was shortened to

### 2015-09-29 manuscript.Rmd
Updates...
Updated descriptives for the first section.

@@
     summarise(first = min(year), last = max(year), n = n()) %>%
-    arrange(desc(n))
+    arrange(desc(n)) %>%
+    rename(Journal = title)
+
+table1 <- left_join(n.so.yr, abb.df) %>%
+  select(-X) %>%
+  select(Journal, Abbrev, n, first, last)
+
+sum_Articles <- sum(table1$n)
+median_Articles <- median(table1$n)
+mean_Articles <- mean(table1$n)
+sd_Articles <- sd(table1$n)
 
@@
 ```{r Figure 1 Small Multiples Paper}
+scopus.df < scopus.df %>% filter(Year <= 2013)
 

### 2015-09-29 manuscript.Rmd

@@
 
-exp.05 <- c(29, rep(NA, 24)) 
+exp.047 <- c(29, rep(NA, 24)) 
 for(i in 2:25){
-    exp.05[i] <- exp.05[i-1] + exp.05[i-1]*.05
+    exp.047[i] <- exp.047[i-1] + exp.047[i-1]*.047
 }
 
-exp.04 <- c(29, rep(NA, 24)) 
+exp.0321 <- c(29, rep(NA, 24)) 
 for(i in 2:25){
-    exp.04[i] <- exp.04[i-1] + exp.04[i-1]*.04
+    exp.0321[i] <- exp.0321[i-1] + exp.0321[i-1]*.0321
 }
 
-exp.03 <- c(29, rep(NA, 24)) 
-for(i in 2:25){
-    exp.03[i] <- exp.03[i-1] + exp.03[i-1]*.03
-}
-
-n.journals.year$exp.05 <- exp.05
-n.journals.year$exp.04 <- exp.04
-n.journals.year$exp.03 <- exp.03
+n.journals.year$Price <- exp.047
+n.journals.year$SWHD <- exp.0321
 n.journals.year <- mutate(n.journals.year, Journal.count = as.numeric(Journal.count))
@@
 
-cols = c("Observed Growth" = cp[1], "Estimated 3.2% CAGR" = cp[4], "Estimated 5% CAGR" = cp[3])
+cols = c("Observed Growth" = cp[1], "3.21% CAGR" = cp[4], "4.7% CAGR" = cp[3])
 
-figure2 <- ggplot(n.journals.year, aes(record.y, 
+(figure2 <- ggplot(n.journals.year, aes(record.y, 
     y = Journal.count)) + 
@@
     theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75)) + 
-    geom_line(aes(x = record.y, y = exp.05, colour = "Estimated 5% CAGR"),
+    geom_line(aes(x = record.y, y = Price, colour = "Estimated 5% CAGR"),
         data = n.journals.year,   colour = cp[2], alpha = .80) +
-    geom_line(aes(x = record.y, y = exp.04, colour = "Estimated 4% CAGR"), 
+    geom_line(aes(x = record.y, y = SWHD, colour = "Estimated 4% CAGR"), 
         data = n.journals.year,  colour = cp[2], alpha = .80) +
@@
     stat_smooth(method = "lm", se = FALSE, colour = cp[3]) +
-    annotate("text", x = 2016.5, y = 60, label = "Observed growth", size = 5) +
-    annotate("text", x = 2016.5, y = 70, label = "Linear growth\n (slope=1.9)", size = 5) + 
-    annotate("text", x = 2016, y = 76, label = "4% CAGR", size = 5) + 
-    annotate("text", x = 2015.5, y = 95, label = "5% CAGR", size = 5) +
+    annotate("text", x = 2016.5, y = 60, label = "3.2% CAGR", size = 5) +
+    annotate("text", x = 2016.5, y = 73, label = "Linear growth", size = 5) + 
+    annotate("text", x = 2016.5, y = 90, label = "4.7% CAGR", size = 5) + 
+    annotate("text", x = 2017.5, y = 65, label = "Observed growth", size = 5) +
     scale_x_continuous(limits = c(1989, 2020), breaks = c(1989, 1993, 1997, 2001, 2005, 2009, 2013)) +
-    ggtitle("Figure 2. Observed Versus Estimated Growth of Journals (1989-2013)") + 
+    #ggtitle("Figure 2. Observed Versus Estimated Growth of Journals (1989-2013)") + 
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
@@
           axis.title.y = element_text(size = 16)) +
-    theme(plot.title = element_text(size = 19))
+    theme(plot.title = element_text(size = 19)))
 ```
@@
     geom_hline(yintercept=0, col="gray", lwd=0.6, alpha =.8) +
-    ggtitle("Figure 3. Annual Percentage Change in the Number Journals (1989 - 2013)") +
+    #ggtitle("Figure 3. Annual Percentage Change in the Number Journals (1989 - 2013)") +
     theme(plot.title = element_text(size = 19))

### 2015-09-29 manuscript.Rmd
adds boxplot

--- 2015-09-29 manuscript.Rmd
@@
     arrange(desc(n)) %>%
-    rename(Journal = title)
+    rename(Journal = title) %>%
+    mutate(index="index_variable")
 
@@
 sd_Articles <- sd(table1$n)
+
+```
+
+```{r Figure 1 Boxplot of Article Counts}
+
+ggplot(data=n.so.yr, aes(x=index, y=n)) +
+  stat_boxplot(geom="errorbar")+
+  geom_boxplot(outlier.size = 2)+
+  ylab("Cumulative article count") +
+  annotate("text", x = 0.87, y = 1600, label = "Families in Society")+
+  annotate("text", x = 0.91, y = 1400, label = "Social Work") +
+  annotate("text", x = 1.20, y = 1350, label = "British Journal of Social Work")+
+  theme_bw()+
+  theme(axis.title.x = element_blank()) +
+  theme(panel.border = element_blank(), axis.line = element_line())+
+  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
+  scale_x_discrete(breaks=NULL)+
+  theme(plot.title = element_text(size = 18))+
+  theme(axis.text=element_text(size=10), axis.title=element_text(size=16))
 

### 2015-10-04 manuscript.Rmd
Boxplot updates.

--- 2015-09-29 manuscript.Rmd
@@
 sd_Articles <- sd(table1$n)
+
+```
+
+```{r Figure 1 Boxplot of Article Counts}
+library(gridExtra)
+
+set.seed(1237)
+boxplot_swhd <- n.so.yr %>% 
+  select(Journal, n)%>%
+  mutate(index = rep("SWHD")) %>%
+  group_by(Journal)
+
+boxplot_swhd <- data.frame(boxplot_swhd)
+top_3_swhd <- boxplot_swhd %>% slice(1:3)
+
+boxplot_scopus <- scopus.df %>%
+  select(Journal, Documents) %>%
+  filter(Documents > 0) %>%
+  rename(n = Documents) %>%
+  mutate(index = rep("Scopus"))
+boxplot_scopus <- data.frame(boxplot_scopus)  
+boxplot_scopus <- boxplot_scopus %>% group_by(Journal) %>%
+  summarize(n = sum(n)) %>%
+  mutate(index = rep("Scopus"))
+
+boxplot_df <- rbind(boxplot_swhd, boxplot_scopus)
+
+swhd_bp <- ggplot(data=boxplot_swhd, aes(x = index, y=n)) +
+  stat_boxplot(geom="errorbar") +
+  geom_boxplot(outlier.size = 0) +
+  theme_bw() + 
+  geom_jitter(colour = cp[2], alpha = .60, size = 4) + 
+  ylab("Number of Articles") + 
+  #xlab("Database") + 
+  ylim(c(0, 1600)) + 
+  xlab("") + 
+  annotate("text", x = c(1.18, 1.15, .9), y = c(top_3_swhd$n[1], top_3_swhd$n[2], top_3_swhd$n[3]), label = top_3_swhd$Journal)
+
+scopus_bp <- ggplot(data=boxplot_scopus, aes(x = index, y=n)) +
+  stat_boxplot(geom="errorbar") +
+  geom_boxplot(outlier.size = 0) +
+  theme_bw() + 
+  geom_jitter(colour = cp[4], alpha = .60, size = 4) + 
+  ylab("") + 
+  #xlab("Database") + 
+  ylim(c(0, 1600)) + 
+  theme(axis.text.y = element_blank()) +
+  xlab("")
+
+grid.arrange(swhd_bp, scopus_bp, ncol=2)
+
+  ylab("Cumulative article count") +
+  annotate("text", x = 0.87, y = 1600, label = "Families in Society")+
+  annotate("text", x = 0.91, y = 1400, label = "Social Work") +
+  annotate("text", x = 1.20, y = 1350, label = "British Journal of Social Work")+
+  theme_bw()+
+  theme(axis.title.x = element_blank()) +
+  theme(panel.border = element_blank(), axis.line = element_line())+
+  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
+  scale_x_discrete(breaks=NULL)+
+  theme(plot.title = element_text(size = 18))+
+  theme(axis.text=element_text(size=10), axis.title=element_text(size=16))
 

### 2015-10-04 manuscript.Rmd

--- 2015-09-29 manuscript.Rmd
@@
 
-```{r Figure 1 Boxplot of Article Counts}
-
-ggplot(data=n.so.yr, aes(x=index, y=n)) +
-  stat_boxplot(geom="errorbar")+
-  geom_boxplot(outlier.size = 2)+
-  ylab("Cumulative article count") +
-  annotate("text", x = 0.87, y = 1600, label = "Families in Society")+
-  annotate("text", x = 0.91, y = 1400, label = "Social Work") +
-  annotate("text", x = 1.20, y = 1350, label = "British Journal of Social Work")+
-  theme_bw()+
-  theme(axis.title.x = element_blank()) +
-  theme(panel.border = element_blank(), axis.line = element_line())+
-  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
-  scale_x_discrete(breaks=NULL)+
-  theme(plot.title = element_text(size = 18))+
-  theme(axis.text=element_text(size=10), axis.title=element_text(size=16))
-
-```
-
 ```{r Figure 1 Small Multiples Paper}
@@
 
-ggplot(combined_reduced,  aes(Year, Documents, colour = DataBase)) +
+small_multiples_paper <- ggplot(combined_reduced,  aes(Year, Documents, colour = DataBase)) +
      geom_line(size = 1, alpha = .80) + 
@@
   theme_bw() + 
-   theme(strip.text.x = element_text(size = 12)) +
-  theme(legend.position = "bottom", legend.text = element_text(size = 12)) + 
+   theme(strip.text.x = element_text(size = 14)) +
+  theme(legend.position = "bottom", legend.text = element_text(size = 14)) + 
      scale_colour_discrete(guide = guide_legend(title = "Database"), breaks = c("HD", "Scopus"), labels = c("Historical Database", "Scopus")) + 
-  scale_colour_manual(values = c(cp[2], cp[4]), labels = c("Historical Database", "Scopus"), guide = guide_legend(title = "")) + 
+  scale_colour_manual(values = c(cp[2], cp[4]), labels = c("Social Work Research Database", "Scopus"), guide = guide_legend(title = "")) + 
   ylab("Number of Articles") + 
@@
      annotate("segment", x = 1992, xend = 1995, y = 120, yend = 120, colour = cp[4], size = 1, alpha = .80) +
-   geom_text(data = scopus_annotate_paper, aes(x = 1999, y =  120, label = label), colour = "black", size = 4) +
-  geom_text(data = hd_annotate, aes(x = 1999, y =  140, label = label), colour = "black", size = 4)
+   geom_text(data = scopus_annotate_paper, aes(x = 1999, y =  120, label = label), colour = "black", size = 5) +
+  geom_text(data = hd_annotate, aes(x = 1999, y =  140, label = label), colour = "black", size = 5)
 
+ggsave(small_multiples_paper, file = "Figure_1_small_multiples.jpg", dpi = 1200, height = 8, width = 12, units = "in")
 ```
@@
     theme(plot.title = element_text(size = 19)))
+
+ggsave(figure2, file = "figure2.jpeg", width = 7, height = 7, units = "in", dpi = 1200)
 ```
@@
 
-#ggsave("figure3.png", figure3, dpi=250)
+ggsave(figure3, file = "figure3.jpeg", width = 7, height = 7, units = "in", dpi=1200)
 ```

### 2015-10-05 manuscript.Rmd
Cleanup code.

@@
 `r knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, comment=NA)`
+
+### Workspace initialization
+
+Set the working directory of this document to the directory containing the historical database.
 
@@
 
-```{r summarySetUp, eval=TRUE}
+### Descriptive summaries
+
+```{r Descriptive Summary, eval=TRUE}
 
@@
 ```
+
+### Table 1
 
@@
 
+print(table1)
+
 ```
 
+### Figure 1 - Small Multiples
+
+This figure is for the manuscript.  Please note that the rendering is optimized for the manuscript, not an online rendering.
+
 ```{r Figure 1 Small Multiples Paper}
-scopus.df < scopus.df %>% filter(Year <= 2013)
+#scopus.df < scopus.df %>% filter(Year <= 2013)
 
@@
 
-ggsave(small_multiples_paper, file = "Figure_1_small_multiples.jpg", dpi = 1200, height = 8, width = 12, units = "in")
+#------------Create high quality jpeg-----------------
+
+# ggsave(small_multiples_paper, file = "Figure_1_small_multiples.jpg", dpi =  1200, height = 8, width = 12, units = "in")
+
+print(small_multiples_paper)
 ```
+
+### Small Multiples - Online Supplement
 
@@
      ggtitle("Figure 1 (cont.). Number of Article Records by Journal (1989 - 2013)")
+
+print(plotSmallMultiples.1)
+print(plotSmallMultiples.2)
 ```
 
-```{r Figure 2 Journal Growth, eval = FALSE}
+### Figure 2 - Growth of Social Work Research
+
+```{r Figure 2 Journal Growth, eval = TRUE}
 #=======================================
@@
 
-(figure2 <- ggplot(n.journals.year, aes(record.y, 
+figure2 <- ggplot(n.journals.year, aes(record.y, 
     y = Journal.count)) + 
@@
           axis.title.y = element_text(size = 16)) +
-    theme(plot.title = element_text(size = 19)))
+    theme(plot.title = element_text(size = 19))
 
-ggsave(figure2, file = "figure2.jpeg", width = 7, height = 7, units = "in", dpi = 1200)
+#ggsave(figure2, file = "figure2.jpeg", width = 7, height = 7, units = "in", dpi = 1200)
+
+print(figure2)
 ```
 
-```{r Figure 3 Annual Change, eval=FALSE}
+### Figure 3 Annual Change
+
+```{r Figure 3 Annual Change, eval=TRUE}
 curr <- n.journals.year$Journal.count[-1]
@@
 
-ggsave(figure3, file = "figure3.jpeg", width = 7, height = 7, units = "in", dpi=1200)
+#ggsave(figure3, file = "figure3.jpeg", width = 7, height = 7, units = "in", dpi=1200)
+
+print(figure3)
 ```
-
-```{r plot02_SmallMultiples, eval=FALSE}
-# Remove 2014 & 2015 
-n.so <- filter(full.df, attributes == "journal") %>% mutate(title = record) %>% 
-  select(-attributes, -record)
-
-n.yr <- filter(full.df, attributes == "pubYear") %>% mutate(year = record ) %>% 
-  select(-attributes, -record)
-
-# Create an initial data frame from HD
-sm.df <- left_join(n.so, n.yr) %>%
-    group_by(title, year) %>%
-    summarize(N = n()) %>%
-    mutate(Overall.N = sum(N), year = as.numeric(year)) %>%
-    ungroup() %>%
-    arrange(desc(Overall.N), title) %>%
-    rename(Year = year, Journal= title)
-
-# Read Scopus database
-#scopus.df2 <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/scopus_OldHar#vest.csv")
-
-scopus.df$Year <- as.numeric(scopus.df$Year)
-scopus.df <- filter(scopus.df, Year <= 2013)
-
-# Join HD with Scopus and join abbreviation names
-sm.scopus.merged <-full_join(sm.df, scopus.df, by = c("Journal", "Year")) %>%
-    select(Year, Journal, N, Overall.N, Documents)
-
- sm.scopus.merged.table <- group_by(sm.scopus.merged, Journal) %>%
-     summarize(DataBase.N = sum(N, na.rm=TRUE), Scopus.N = sum(Documents, na.rm=TRUE)) %>%
-     arrange(desc(DataBase.N))
-
- abb.df$ID <- 1:nrow(abb.df)
- sm.scopus.merged <- full_join(sm.scopus.merged, abb.df, by = "Journal") %>% 
-     select(-X) %>%
-     mutate(Documents = ifelse(Documents == 0, NA, Documents))
-
- # Re-order the factor by Overall.N
- title <- sm.scopus.merged %>% arrange(desc(Overall.N)) %>% 
-     distinct(Abbrev) %>% filter(!is.na(Abbrev)) %>% distinct()
-
- title.order = title$Abbrev
-
- sm.scopus.merged$Abbrev <- factor(sm.scopus.merged$Abbrev, levels = (title.order))
- sm.scopus.merged <- group_by(sm.scopus.merged, Journal) %>%
-     mutate(Overall.Scopus = sum(Documents, na.rm=TRUE)) %>%
-     ungroup()
-# 
- # Create labels for the facets
- Overall.N <- distinct(sm.scopus.merged, Abbrev) 
- lab1 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.N), sep=""))
- lab2 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.Scopus), sep=""))
- lab <- paste(lab1, lab2, sep="\n")
- xpos = rep(1999, 80)
- ypos = rep(200, 80)
-
- Overall.N <- distinct(sm.df, Journal)
-
- ldata <- data.frame(xpos, ypos, lab, Overall.N$Abbrev) %>% 
-     rename(Abbrev = Overall.N.Abbrev)
-
- ldata <- na.omit(ldata)
-
- titles.reduced <- unique(sm.scopus.merged$Journal)
- titles.reduced.1 <- titles.reduced[1:40]
- titles.reduced.2 <- titles.reduced[41:length(titles.reduced)] 
- cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
-
- library(grid)
- library(gridExtra)
-# Plotting function    
-# 
- plotSmallMultiples.1 <-  ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.1, ],  aes(Year, N)) +
-     geom_line(colour="#e66101") +
-     geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.1, ], aes(Year, Documents), colour = "#533c99", alpha = .80) + 
-     facet_wrap(~ Abbrev) + 
-     theme_bw() +
-     theme(strip.text.x = element_text(size = 8)) + 
-     theme(legend.position = "bottom", 
-     panel.grid.minor = element_blank(), 
-     axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
-     geom_text(data = ldata[1:40, ], aes(x =xpos, y = ypos, label = lab), size =2.5) +
-     ylim(c(0,225)) +
-     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
-     annotate("segment", x = 1989, xend = 1992, y = 215, yend = 215, colour = "#e66101") + 
-     annotate("segment", x = 1989, xend = 1992, y = 190, yend = 190, colour = "#533c99") +
-     ggtitle("Figure 1. Number of Article Records by Journal (1989 - 2013)")
-
-plotSmallMultiples.2 <- ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ],  
-     aes(Year, N)) +
-     geom_line(colour="#e66101") +
-     geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.2, ], 
-     aes(Year, Documents), colour = "#533c99", alpha = .80) + 
-     facet_wrap(~ Abbrev) + 
-     theme_bw() +
-     theme(strip.text.x = element_text(size = 8)) +  
-     theme(legend.position = "bottom", 
-     panel.grid.minor = element_blank(), 
-     axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
-     geom_text(data = ldata[41:79, ], aes(x =xpos, y = ypos, label = lab), size =2.5) +
-     ylim(c(0,225)) +
-     scale_x_continuous(breaks=seq(1989, 2015, 8)) +
-     annotate("segment", x = 1989, xend = 1992, y = 215, yend = 215, colour = "#e66101") + 
-     annotate("segment", x = 1989, xend = 1992, y = 190, yend = 190, colour = "#533c99") +
-     ggtitle("Figure 1 (cont.). Number of Article Records by Journal (1989 - 2013)")
-```
-
-```{r Figure 4 CAGR Comparison, eval=FALSE}
-
-CAGR <- function(start, finish, periods){
-  # Function to compute the CAGR given simple returns
-  #
-  # args:
-  #  start = starting value
-  #  finish = ending cumulative value
-  #  periods = number of time periods over which value was accumulated
-  #
-  # Returns the Compound Annual Growth Rate
-    cagr <- round(((finish/start)^(1 /periods) - 1)*100, digits=1)    
-  return(cagr)
-}
-
-sangam.cumsum <-sangam %>%
-  group_by(field) %>%
-  mutate(CumSum=cumsum(count))
-
-cagr <- sangam.cumsum %>%
-  filter(year==1989 | year==1998)%>%
-  group_by(field)%>%
-  mutate(cagr=CAGR(start=min(CumSum), finish=max(CumSum), periods=9)) %>%
-  select(field, cagr)
-
-cagr<-unique(cagr)
-
-############## Generate comparable social work CAGR, 1989-1998 #################
-
-sw.cagr <- articles.df %>%
-  filter(Year<1999 & Year>1988)%>%
-  mutate(CumSum=cumsum(N)) %>%
-  mutate(field = "socialWork")
-
-sw.cagr <- sw.cagr %>%
-  mutate(cagr=CAGR(start=min(CumSum), finish=max(CumSum), periods=9))%>%
-  select(field, cagr)
-
-sw.cagr<-unique(sw.cagr)
-
-cagr<-rbind(cagr, sw.cagr)
-
-cagr$field<-as.character(cagr$field)
-cagr$field<-reorder(cagr$field, cagr$cagr)
-
-#############PLOT##################
-
-CAGR <- ggplot(cagr, aes(x=field, y=cagr, fill=field, group =1)) + theme_bw() + 
-    geom_bar(width=0.8, stat='identity') + theme(axis.text.x = element_text(size=8),
-        title = element_text(size = 10), plot.title=element_text(size=10)) + 
-    ylab("Compound annual growth rate (%)") + 
-    xlab("") + 
-    ggtitle("Figure 4. Compound annual growth rates for \nnumber of published articles (1989 - 1998)") + 
-    theme(plot.title = element_text(size = rel(1.5))) + scale_y_continuous(breaks =
-        c(seq(0, 40,  15)), limits=c(0, 40)) + theme(axis.title.x =
-        element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75)) + 
-    scale_fill_manual(values=c("#b2abd2", "#b2abd2", "#fdb863", "#b2abd2",
-        "#b2abd2", "#b2abd2", "#b2abd2"))+ theme(legend.position="none") + 
-    scale_x_discrete(labels=c("Psychology","Economics","Social \nWork","Sociology","Political \nScience", "History", "Anthropology")) + 
-    geom_hline(yintercept=seq(0, 40, 15), col="white", lwd=0.6) + 
-    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),  
-        panel.border = element_blank(), axis.line = element_line(), 
-        axis.text.y = element_text(size = 15),
-        axis.text.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15), 
-        title = element_text(size = 13)
-        ) + 
-    geom_text(aes(label =cagr ), vjust = -.5)
-
-```

### 2015-10-05 manuscript.Rmd

@@
 
-n.so <- filter(full.df, attributes == "journal") %>% mutate(title = record) %>% 
+n.so <- filter(full.df, attributes == "journal") %>% 
+  mutate(title = record) %>% 
   select(-attributes, -record)
 
-n.yr <- filter(full.df, attributes == "pubYear") %>% mutate(year = record ) %>% 
+n.yr <- filter(full.df, attributes == "pubYear") %>% 
+  mutate(year = record ) %>% 
   select(-attributes, -record)
@@
 print(table1)
-
 ```
@@
 ```{r Figure 1 Small Multiples Paper}
-#scopus.df < scopus.df %>% filter(Year <= 2013)
 
@@
 # Create Scopus labels for the facets
-
 scopus.df$Year <- as.numeric(scopus.df$Year)
@@
   theme(legend.position = "bottom", legend.text = element_text(size = 14)) + 
-     scale_colour_discrete(guide = guide_legend(title = "Database"), breaks = c("HD", "Scopus"), labels = c("Historical Database", "Scopus")) + 
-  scale_colour_manual(values = c(cp[2], cp[4]), labels = c("Social Work Research Database", "Scopus"), guide = guide_legend(title = "")) + 
+  scale_colour_discrete(guide = guide_legend(title = "Database"), 
+    breaks = c("HD", "Scopus"), labels = c("Historical Database", "Scopus")) + 
+  scale_colour_manual(values = c(cp[2], cp[4]), labels = c("Social Work Research Database", "Scopus"), 
+    guide = guide_legend(title = "")) + 
   ylab("Number of Articles") + 
@@
 
- abb <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/master.csv")
- abb$ID <- 1:nrow(abb)
- sm.scopus.merged <- full_join(sm.scopus.merged, abb, by = "Journal") %>% 
+abb.df$ID <- 1:nrow(abb.df)
+
+sm.scopus.merged <- full_join(sm.scopus.merged, abb.df, by = "Journal") %>% 
   select(-X) %>%
@@
 title <- sm.scopus.merged %>% arrange(desc(Overall.N)) %>% 
-     distinct(Abbrev) %>% filter(!is.na(Abbrev)) %>% distinct()
+  distinct(Abbrev) %>% 
+  filter(!is.na(Abbrev)) %>% 
+  distinct()
 
@@
   ungroup()
-# 
+
  # Create labels for the facets
@@
 xpos = rep(1999, 80)
- ypos = rep(200, 80)
+ypos = rep(190, 80)
 ldata <- data.frame(xpos, ypos, lab, Overall.N$Abbrev) %>% 
@@
 
- library(grid)
- library(gridExtra)
 # Plotting function    
 # 
- plotSmallMultiples.1 <-  ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.1, ],  aes(Year, N)) +
+ plotSmallMultiples.1 <-  ggplot(sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.1, ],  
+   aes(Year, N)) +
   geom_line(colour="#e66101") +
-     geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.1, ], aes(Year, Documents), colour = "#533c99", alpha = .80) + 
+  geom_line(data = sm.scopus.merged[sm.scopus.merged$Journal %in% titles.reduced.1, ], 
+    aes(Year, Documents), colour = "#533c99", alpha = .80) +  
   facet_wrap(~ Abbrev) + 
@@
   scale_x_continuous(breaks=seq(1989, 2015, 8)) +
-     annotate("segment", x = 1989, xend = 1992, y = 215, yend = 215, colour = "#e66101") + 
-     annotate("segment", x = 1989, xend = 1992, y = 190, yend = 190, colour = "#533c99") +
-     ggtitle("Figure 1. Number of Article Records by Journal (1989 - 2013)")
+  annotate("segment", x = 1989, xend = 1992, y = 210, yend = 210, colour = "#e66101") + 
+  annotate("segment", x = 1989, xend = 1992, y = 170, yend = 170, colour = "#533c99") +
+  ggtitle("Number of Article Records by Journal, 1989 - 2013 (Part 1)")
 
@@
   axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
-     geom_text(data = ldata[41:79, ], aes(x =xpos, y = ypos, label = lab), size =2.5) +
+  geom_text(data = ldata[41:80, ], aes(x =xpos, y = ypos, label = lab), size =2.5) +
   ylim(c(0,225)) +
   scale_x_continuous(breaks=seq(1989, 2015, 8)) +
-     annotate("segment", x = 1989, xend = 1992, y = 215, yend = 215, colour = "#e66101") + 
-     annotate("segment", x = 1989, xend = 1992, y = 190, yend = 190, colour = "#533c99") +
-     ggtitle("Figure 1 (cont.). Number of Article Records by Journal (1989 - 2013)")
+  annotate("segment", x = 1989, xend = 1992, y = 210, yend = 210, colour = "#e66101") + 
+  annotate("segment", x = 1989, xend = 1992, y = 170, yend = 170, colour = "#533c99") +
+  ggtitle("Number of Article Records by Journal, 1989 - 2013 (Part 2)")
 
@@
 print(plotSmallMultiples.2)
+
+ggsave(plotSmallMultiples.1, file = "smallMultiples1.jpeg", width = 10, height = 7, units = "in", dpi=1200)
+
+ggsave(plotSmallMultiples.2, file = "smallMultiples2.jpeg", width = 10, height = 7, units = "in", dpi=1200)
 ```
@@
 
-exp.0321 <- c(29, rep(NA, 24)) 
+exp.0307 <- c(29, rep(NA, 24)) 
 for(i in 2:25){
-    exp.0321[i] <- exp.0321[i-1] + exp.0321[i-1]*.0321
+    exp.0307[i] <- exp.0307[i-1] + exp.0307[i-1]*.0307
 }
@@
 n.journals.year$Price <- exp.047
-n.journals.year$SWHD <- exp.0321
+n.journals.year$SWHD <- exp.0307
 n.journals.year <- mutate(n.journals.year, Journal.count = as.numeric(Journal.count))
@@
 
-cols = c("Observed Growth" = cp[1], "3.21% CAGR" = cp[4], "4.7% CAGR" = cp[3])
+cols = c("Observed Growth" = cp[1], "3.07% CAGR" = cp[4], "4.7% CAGR" = cp[3])
 
@@
     stat_smooth(method = "lm", se = FALSE, colour = cp[3]) +
-    annotate("text", x = 2016.5, y = 60, label = "3.2% CAGR", size = 5) +
+    annotate("text", x = 2016.5, y = 60, label = "3.07% CAGR", size = 5) +
     annotate("text", x = 2016.5, y = 73, label = "Linear growth", size = 5) + 
@@
 
-#ggsave(figure2, file = "figure2.jpeg", width = 7, height = 7, units = "in", dpi = 1200)
+ggsave(figure2, file = "figure2.jpeg", width = 7, height = 7, units = "in", dpi = 1200)
 
 print(figure2)
+```
+
+```{r Linear Growth}
+
+n.journals.year <- filter(full.df, attributes == "journal") %>%
+    select(articleID, record)
+
+n.year <- filter(full.df, attributes == "pubYear") %>%
+    select(articleID, record)
+
+n.journals.year <- left_join(n.journals.year, n.year, by = "articleID", copy=TRUE) %>%
+    group_by(record.y) %>%
+    summarise(Journal.count = n_distinct(record.x)) %>%
+    mutate(record.y = as.numeric(record.y))
+
+n.journals.year$yearCount <-  c(1:nrow(n.journals.year))
+
 ```

### 2015-10-06 manuscript.Rmd

@@
 
-exp.047 <- c(29, rep(NA, 24)) 
+exp.047 <- c(31, rep(NA, 24)) 
 for(i in 2:25){
@@
 
-exp.0307 <- c(29, rep(NA, 24)) 
+exp.0307 <- c(31, rep(NA, 24)) 
 for(i in 2:25){
@@
 years <- c(1989, 2005, 2013, 2013)
-points <- c(29, n.journals.year$Journal.count[c(17,25)], max(n.journals.year$exp.05))
+points <- c(31, n.journals.year$Journal.count[c(17,25)], max(n.journals.year$exp.05))
 annotate.df <- data.frame(years, points)
@@
     stat_smooth(method = "lm", se = FALSE, colour = cp[3]) +
-    annotate("text", x = 2016.5, y = 60, label = "3.07% CAGR", size = 5) +
-    annotate("text", x = 2016.5, y = 73, label = "Linear growth", size = 5) + 
-    annotate("text", x = 2016.5, y = 90, label = "4.7% CAGR", size = 5) + 
-    annotate("text", x = 2017.5, y = 65, label = "Observed growth", size = 5) +
+    annotate("text", x = 2014.5, y = 60, label = "3.07% CAGR", size = 4) +
+    annotate("text", x = 2016, y = 74.5, label = "Linear growth", size = 4) + 
+    annotate("text", x = 2015.5, y = 95, label = "4.7% CAGR", size = 4) + 
+    annotate("text", x = 2016.5, y = 67, label = "Observed growth", size = 4) +
     scale_x_continuous(limits = c(1989, 2020), breaks = c(1989, 1993, 1997, 2001, 2005, 2009, 2013)) +

### 2015-12-01 manuscript.Rmd
converts figures to black and white

@@
 small_multiples_paper <- ggplot(combined_reduced,  aes(Year, Documents, colour = DataBase)) +
-  geom_line(size = 1, alpha = .80) + 
+  geom_line(size = .5) + 
   facet_wrap(~ Journal) +
@@
     breaks = c("HD", "Scopus"), labels = c("Historical Database", "Scopus")) + 
-  scale_colour_manual(values = c(cp[2], cp[4]), labels = c("Social Work Research Database", "Scopus"), 
+  scale_colour_manual(values = c("black", "#999999"), labels = c("Social Work Research Database", "Scopus"), 
     guide = guide_legend(title = "")) + 
@@
   xlab("\nYear") +
-  annotate("segment", x = 1992, xend = 1995, y = 140, yend = 140, colour = cp[2], size = 1, alpha = .80) + 
-  annotate("segment", x = 1992, xend = 1995, y = 120, yend = 120, colour = cp[4], size = 1, alpha = .80) +
+  annotate("segment", x = 1992, xend = 1995, y = 140, yend = 140, colour = "black", size = 1, alpha = .80) + 
+  annotate("segment", x = 1992, xend = 1995, y = 120, yend = 120, colour = "#999999", size = 1, alpha = .80) +
   geom_text(data = scopus_annotate_paper, aes(x = 1999, y =  120, label = label), colour = "black", size = 5) +
@@
 
-# ggsave(small_multiples_paper, file = "Figure_1_small_multiples.jpg", dpi =  1200, height = 8, width = 12, units = "in")
+#ggsave(small_multiples_paper, file = "Figure_1_small_multiples.jpg", dpi =  1200, height = 8, width = 12, units = "in")
 
@@
     geom_line(aes(x = record.y, y = Price, colour = "Estimated 5% CAGR"),
-        data = n.journals.year,   colour = cp[2], alpha = .80) +
+        data = n.journals.year,   colour = "#999999", alpha = .80) +
     geom_line(aes(x = record.y, y = SWHD, colour = "Estimated 4% CAGR"), 
-        data = n.journals.year,  colour = cp[2], alpha = .80) +
-    geom_line(aes(colour = "Observed Growth"), colour = cp[4], size = 1.5) + 
-    stat_smooth(method = "lm", se = FALSE, colour = cp[3]) +
+        data = n.journals.year,  colour = "#999999", alpha = .80) +
+    geom_line(aes(colour = "Observed Growth"), colour = "black", size = 1.5) + 
+    stat_smooth(method = "lm", se = FALSE, colour = "#999999") +
     annotate("text", x = 2014.5, y = 60, label = "3.07% CAGR", size = 4) +
@@
 
-ggsave(figure2, file = "figure2.jpeg", width = 7, height = 7, units = "in", dpi = 1200)
+#ggsave(figure2, file = "figure2.jpeg", width = 7, height = 7, units = "in", dpi = 1200)
 
@@
     geom_bar(stat="identity") +
-    scale_fill_manual(values = cp[c(3,1)], limits = c("Increase", "Decrease")) + 
+    scale_fill_manual(values = c("black", "#999999"), limits = c("Increase", "Decrease")) + 
     theme(legend.position = c(1,1), legend.justification = c(1,1), legend.title = element_blank()) + 
